### 2015-10-05 paper/circumvention-experiment.tex
initializing paper

\documentclass{sig-alternate-hotpets15}
\usepackage{color}
\usepackage[hyphens]{url}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{pdfpages}

\def\etal{{\it et al.~}}
\newenvironment{packed_enum}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{enumerate}}
\newenvironment{packed_item}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
}{\end{itemize}}

\begin{document}

\title{Tor's Usability for Censorship Circumvention}
\numberofauthors{1}
\author{
 \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
   \vspace{0.5em}
   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
}
\maketitle

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}

Tor has grown beyond its original purpose as and has 
since become an important Internet circumvention tool.
We specifically examine it usability as a censorship circumvention tool,
an essential facet for adoption and use.  
We focus our analysis on the connection configuration dialog of Tor browser,
as censorship circumvention requires correct transport configurations. %%
Our talk will describe a future study aimed at evaluating 
if and how easily users can circumvent censorship using Tor Browser,
isolating specific browser features to study in the process. 
To this end, we will conduct a large-scale user study examining hundreds of users 
on how they navigate Tor's configuration wizard to complete seven browsing tasks 
in three different adversarial settings. 
We solicit feedback to improve our study's design.
\end{abstract}

\keywords{Censorship, Security, User Studies, Anonymity, Tor}

\section{Tor's Usability}
%Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.

Tor is the most widely used anonymity tool today. However, there are complaints that Tor is not usable. Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, 
finding out when people would get frustrated with Tor so much they would stop using it. 
%redo this next couple sentences into something better
But what about the people who are using Tor? what usability issues would there be if people were not stopped? 
To our knowledge, that has been the only user study of Tor. 
Since then, Tor has had a lot of updates. 
Additionally, there were a lot of features that were untested. 
There have been been no major usability evaluations of
Tor Browser since the introduction of the 4.0 series,
which introduced radical UI changes.

We briefly describe the results of a completed study
that examined the download and installation processes, 
as well as basic browsing behaviors.
This study uncovered a number of bugs and stopping points
which has already effected concrete change in the browser.

We ran a small pilot study of five journalists which involved a cognitive walk through in which 
participants explained the motivation for their actions and any confusion that they had during the process. 
We did this to find new stopping points, and sources of confusion. 
But in the process, we were also able to observe how users would download Tor, 
if they could understand the address bar/menu, how well they were able to complete basic tasks
(searching, setting new circuits, etc.), and generally if they had any usability complaints about the browser.

We recruited five journalists from Berkeley by reaching out to journalist contacts. 
%Demographics here. 
During the study, we made a video recording of each participant's computer screen
and simultaneously projected it
into another room with Tor developers.
We recorded what they were saying out loud in their cognitive walk through,
and later added these words to the screen videos as subtitles.
The participants also took an exit survey which estimated their familiarity with technology and security. On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).  The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening. 
Our talk will feature brief highlights of the screen videos and a summary of interface changes.

After our first  usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management. 
%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
%emphasize how we are aiming for new research, not new test cases for debugging an interface
Rather than selecting the features to study in isolation, 
we decided to focus on an important use case of Tor browser, censorship circumvention. 
%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
%if there are stats on this type of thing.
To our knowledge, this is the first user study investigating the usability of Tor as a 
censorship circumvention tool, rather than an anonymity tool.

\section{Design}
\noindent {\bfseries Overview}
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not. We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in. We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks. To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in. We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc. We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc. \\

\noindent {\bfseries Censorship Environment Simulation}
We plan to simulate three censorship environments.
They are informed by our experience with pluggable transports
and knowledge of commonly seen censorship techniques.
They are not meant perfectly to replicate the network environment
in any particular country; rather, they are abstract simulations
that are nevertheless inspired by reality.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

\noindent {\bfseries List of Tasks} 
The tasks below were originally inspired by the top Alexa sites, 
an indication of representative and relevant browsing behavior. 
We then selected sites which were commonly censored and 
refined the tasks to remove ethical concerns, such as tasks 
which would require a participant to reveal private information 
(such as login information). We hope the resulting tasks convey an idea 
of sites which are censored today, while remaining representative 
of how a user might browse the Internet.

All participants will be given the same set of tasks, 
regardless of the censorship environment. 
Although every participant will attempt the same set of tasks, 
the difficulty of completing these tasks will vary based on 
their chosen censorship environment. 
The tasks are not all intended to be challenging to complete. 
Some may not even require the use or Tor Browser, 
depending on the environment.

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Do a Google web search.
\item Watch a YouTube video.
\item Find the Amazon best-selling books.
\item Find Yahoo's exchange rate between dollars and euros.
\item Read the Wikipedia featured article.
\item Find the Twitter trending topics.
\item Find directions on Bing Maps.
\end{itemize}

\noindent {\bfseries Experiment Execution Details} 
We plan to recruit up to 200 users for the purpose of this study, 
making it largest user study to date examining Tor (check this). 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs.  \\

\section{What we want feedback on}

During the question-and-answer session,
we will be especially interested in soliciting feedback
on these topics:

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item {\bfseries Targeting specific pluggable transports}
Some of Tor's pluggable transports work in censorship environments
where others do not.
Additionally, some of them require additional information
(like bridge addresses) before they work.
Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\item {\bfseries Censorship environments}
Our proposed censorship simulation is informed
by real-world censors.
What other representative environments
should be tested?

\item {\bfseries Browsing tasks}
Circumvention is broader than the stereotypical
``dissident blogger'' use case.
We have invented some tasks that use some of the
most popular web sites.
What other browsing tasks make sense to test?

\item {\bfseries Experimental design}
Our initial study was aimed at a specific subset of users (journalists).
We plan to remove this restriction in order
to have a larger participant population.
We aim to make our results reproducible by publishing
our software and firewall configurations.
\end{itemize}

\section{Resources}

Our online artifacts of our completed pilot study, such as 
the summary, results, and resulting browser changes are below:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
\end{itemize}

Subtitled screen videos:
\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
\end{itemize}

\bibliographystyle{abbrv}
\bibliography{bibliography.bib} 
\end{document}

### 2015-10-05 paper/circumvention-experiment.tex
updated the list of tasks section

@@
-\documentclass{sig-alternate-hotpets15}
+\documentclass{template}
 \usepackage{color}
@@
 
-% is the abstract missing some oomph? 
-% I don't know how much the storyline is showing through.. or what we are testing. 
 \begin{abstract}
@@
 \noindent {\bfseries List of Tasks} 
-The tasks below were originally inspired by the top Alexa sites, 
+In our experimental setup, successful completion of 
+these given tasks requires of correct configuration.
+The difficulty of circumventing  censorship to visit the 
+websites required for the tasks will vary on the 
+simulated censorship environment. Since all participants will be given the 
+same set of tasks, regardless of the censorship environment, 
+the difficulty of completing the tasks remains constant assuming
+correct configuration. The tasks themselves are not intended to
+be challenging.
+
+The tasks were initially inspired by the top Alexa sites, 
 an indication of representative and relevant browsing behavior. 
-We then selected sites which were commonly censored and 
-refined the tasks to remove ethical concerns, such as tasks 
-which would require a participant to reveal private information 
-(such as login information). We hope the resulting tasks convey an idea 
-of sites which are censored today, while remaining representative 
-of how a user might browse the Internet.
-
-All participants will be given the same set of tasks, 
-regardless of the censorship environment. 
-Although every participant will attempt the same set of tasks, 
-the difficulty of completing these tasks will vary based on 
-their chosen censorship environment. 
-The tasks are not all intended to be challenging to complete. 
-Some may not even require the use or Tor Browser, 
-depending on the environment.
+From these, we selected sites which were commonly censored, 
+but filtered tasks that would require a participant to reveal private information 
+(such as login information) for ethical considerations. These tasks
+were further refined after performing a pilot study of the experiment. 
+We hope the tasks convey an example of how of a user might 
+browse the Internet in a censored environment.
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item Do a Google web search.
-\item Watch a YouTube video.
-\item Find the Amazon best-selling books.
-\item Find Yahoo's exchange rate between dollars and euros.
-\item Read the Wikipedia featured article.
-\item Find the Twitter trending topics.
-\item Find directions on Bing Maps.
+\item Do a Google web search for the population of Zimbabwe. 
+\item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
+\item Find the Amazon best-sellers in the ``Movies \& TV'' category.
+\item On Yahoo, find the exchange rate between dollars and euros.
+\item In the Wikipedia ``History'' portal, click on the featured article. 
+\item On Twitter, find the currently trending topics.
+\item On Bing Maps, find directions from Time Square to Carnegie Hall.
 \end{itemize}
@@
 \noindent {\bfseries Experiment Execution Details} 
-We plan to recruit up to 200 users for the purpose of this study, 
-making it largest user study to date examining Tor (check this). 
+We plan to recruit from 200 users for the purpose of this study, 
+making it largest user study to date examining Tor. 
 This study will be conducted at the Experimental Social Science Laboratory (Xlab)

### 2015-10-05 paper/circumvention-experiment.tex
updated Experiment Logistics section

@@
 
+At the start of the study, participants will be informed
+of the role they they will be playing in the study. Particularly,
+they will be informed that they are in a censorship environment
+which prevents them from visiting certain websites, but they
+are people who would like to visit those websites for 
+leisurely purposes.
+
 We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
@@
 
-\noindent {\bfseries Experiment Execution Details} 
-We plan to recruit from 200 users for the purpose of this study, 
-making it largest user study to date examining Tor. 
-This study will be conducted at the Experimental Social Science Laboratory (Xlab)
+\noindent {\bfseries Experiment Logistics} 
+The IRB protocol to run this user study has been approved (2014-12-6995). 
+We plan to recruit from 100-200 users for the purpose of this study, 
+making it largest user study to examine Tor.  This study will be conducted at the 
+Experimental Social Science Laboratory (Xlab)
 at the University of California, Berkeley, which consists of 36 laptops with 
 cubicle walls separating each laptop. We will use individual host firewalls to simulate
-the censorship environments and will write a browser extension to 
-log when user activity, such as what websites they were successfully able to visit. 
-The total length of the experiment, including briefing, completing the censorship 
-circumvention tasks, exit survey, and debriefing, will take less than an hour. 
-Participants will be compensated \$30 for their time, 
-which is more to cover minimum wage and transportation costs.  \\
+censorship environments and will record computer screens to capture 
+user activity. The total length of the experiment, including briefing, completing the censorship 
+circumvention tasks, exit survey, and debriefing, will take about an hour. 
+Participants will be compensated \$30 for their time, which is more to cover 
+minimum wage for an hour and any transportation costs to the lab.  \\
 

### 2015-10-05 paper/circumvention-experiment.tex
updated the resources section

@@
 \usepackage{pdfpages}
+\usepackage{hyperref}
 
@@
 \section{Resources}
+\noindent Our online artifacts of the work done during this class, Fall 2015,
+are below: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, and paper}
+\item \href {https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/1-strict.mp4}{pilot video 1}
+	\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/2-lax.mp4}{pilot video 2}
+\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
+\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
+\end{itemize}
 
-Our online artifacts of our completed pilot study, such as 
+%%  FROM ANONYMITY UX STUDY 
+Our online artifacts of study of Tor as an anonymity tool, such as 
 the summary, results, and resulting browser changes are below:
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item \url{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}
-\item \url{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}
-\end{itemize}
-
-Subtitled screen videos:
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item \url{https://people.torproject.org/~dcf/uxsprint2015/}
+\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
+\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
+\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
 \end{itemize}

### 2015-10-05 paper/circumvention-experiment.tex
added a deliverables section
got rid of the questions section

@@
 
+In certain real censorship environment and our most 
+prohibitive simulated censorship environments, only some of 
+Tor's pluggable transports work in censorship environments
+where others do not. Some of them require additional information
+(like bridge addresses) before they work. Currently, we do not 
+have a way to target test specific transports. However, we 
+do ask why participants chose a specific pluggable 
+transport in our exit survey to gain some insight.
+
 \noindent {\bfseries List of Tasks} 
@@
 
-\section{What we want feedback on}
+\section{What we hope to accomplish}
 
-During the question-and-answer session,
-we will be especially interested in soliciting feedback
-on these topics:
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Targeting specific pluggable transports}
-Some of Tor's pluggable transports work in censorship environments
-where others do not.
-Additionally, some of them require additional information
-(like bridge addresses) before they work.
-Is there a way to target testing of specific transports?
-Is there anything to infer from participants' selection of transports, 
-or do we assume they are trying transports at random?
-
-\item {\bfseries Censorship environments}
-Our proposed censorship simulation is informed
-by real-world censors.
-What other representative environments
-should be tested?
-
-\item {\bfseries Browsing tasks}
-Circumvention is broader than the stereotypical
-``dissident blogger'' use case.
-We have invented some tasks that use some of the
-most popular web sites.
-What other browsing tasks make sense to test?
-
-\item {\bfseries Experimental design}
-Our initial study was aimed at a specific subset of users (journalists).
-We plan to remove this restriction in order
-to have a larger participant population.
-We aim to make our results reproducible by publishing
-our software and firewall configurations.
-\end{itemize}
+We plan to finish the user study by the end of the semester. 
+From this experiment, we hope to accomplish the following:
 

### 2015-10-05 paper/circumvention-experiment.tex
non-atomic commit. Added little todos in multiple sections and switched ordering

@@
 \section{Design}
+
 \noindent {\bfseries Overview}
+% test tor, test improvements, may do followups on demand, push changes.
+
+%improve what is below:
 For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
@@
 
+\noindent {\bfseries Experiment Logistics} 
+The IRB protocol to run this user study has been approved (2014-12-6995). 
+We plan to recruit from 100-200 users for the purpose of this study, 
+making it largest user study to examine Tor.  This study will be conducted at the 
+Experimental Social Science Laboratory (Xlab)
+at the University of California, Berkeley, which consists of 36 laptops with 
+cubicle walls separating each laptop. We will use individual host firewalls to simulate
+censorship environments and will record computer screens to capture 
+user activity. The total length of the experiment, including briefing, completing the censorship 
+circumvention tasks, exit survey, and debriefing, will take about an hour. 
+Participants will be compensated \$30 for their time, which is more to cover 
+minimum wage for an hour and any transportation costs to the lab.  \\
+
+\noindent {\bfseries Experiment Flow} 
+% explain one experiment from start to end. 
 At the start of the study, participants will be informed
@@
 \noindent {\bfseries Censorship Environment Simulation}
+
 We plan to simulate three censorship environments.
@@
 that are nevertheless inspired by reality.
+
+% talk about how these censorship environments cover the UI path
 
@@
 
+%talk about how participants will be motivated to configure to 
+%complete these tasks. participants will write down the answers 
+%on a sheet of paper...
+
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
@@
 
-\noindent {\bfseries Experiment Logistics} 
-The IRB protocol to run this user study has been approved (2014-12-6995). 
-We plan to recruit from 100-200 users for the purpose of this study, 
-making it largest user study to examine Tor.  This study will be conducted at the 
-Experimental Social Science Laboratory (Xlab)
-at the University of California, Berkeley, which consists of 36 laptops with 
-cubicle walls separating each laptop. We will use individual host firewalls to simulate
-censorship environments and will record computer screens to capture 
-user activity. The total length of the experiment, including briefing, completing the censorship 
-circumvention tasks, exit survey, and debriefing, will take about an hour. 
-Participants will be compensated \$30 for their time, which is more to cover 
-minimum wage for an hour and any transportation costs to the lab.  \\
-
 \section{What we hope to accomplish}
@@
 From this experiment, we hope to accomplish the following:
+
+% measure how an average user might configure Tor in various circumention settings
+% test improvement and alternate configuration 
+% make changes!
 

### 2015-10-05 paper/circumvention-experiment.tex
linked correct .bib file
made the tasks fit into one line

@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item Do a Google web search for the population of Zimbabwe. 
+\item Google search for the population of Zimbabwe. 
 \item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
-\item Find the Amazon best-sellers in the ``Movies \& TV'' category.
-\item On Yahoo, find the exchange rate between dollars and euros.
-\item In the Wikipedia ``History'' portal, click on the featured article. 
+\item Find the Amazon best-sellers in ``Movies \& TV.''
+\item On Yahoo, find the exchange rate of dollars to euros.
+\item Find the Wikipedia ``History'' portal's featured article. 
 \item On Twitter, find the currently trending topics.
@@
 \bibliographystyle{abbrv}
-\bibliography{bibliography.bib} 
+\bibliography{circumvention-experiment.bib} 
 \end{document}

### 2015-10-05 paper/circumvention-experiment.tex
moved explaining purpose of tasks to experiment flow
hashed out deliverables
finished deliverables

@@
 
+%talk about how participants will be motivated to configure to 
+%complete these tasks. participants will write down the answers 
+%on a sheet of paper...
+
 We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
@@
 \noindent {\bfseries Censorship Environment Simulation} 
-
 We plan to simulate three censorship environments.
@@
 do ask why participants chose a specific pluggable 
-transport in our exit survey to gain some insight.
+transport in our exit survey to gain some insight.\\
 
@@
 
-%talk about how participants will be motivated to configure to 
-%complete these tasks. participants will write down the answers 
-%on a sheet of paper...
-
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
@@
 
-% measure how an average user might configure Tor in various circumention settings
-% test improvement and alternate configuration 
-% make changes!
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Test the Tor configuration interface} We will perform the largest-scale user study 
+of Tor to date, measuring how users configure Tor in three different adversarial settings. 
+\item {\bfseries Test an improved configuration interface} With the measurements collected
+from testing the interface as-is, Nathan will be designing ways to improve the interface to minimize
+time taken, paths taken, and error states reached.
+\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
+to design a mock-up interface for an alternative configuration interface which will
+greatly automate the process. There are tradeoffs between ease of use and transparency
+of the system's, and ethical considerations with loggable errors resulting from automated configuration. 
+\item {\bfseries Push changes} We have the support of Tor developers
+to improve this interface. Additionally, since the configuration interface does not require 
+any changes to the Tor Browser functionality, improvements to the interface will
+be easy to deploy. 
+\end{itemize}
 

### 2015-10-05 paper/circumvention-experiment.tex
make unfinished things red

@@
 \begin{abstract}
-
+{\color{red}
 Tor has grown beyond its original purpose as and has 
@@
 We focus our analysis on the connection configuration dialog of Tor browser,
-as censorship circumvention requires correct transport configurations. %%
+as censorship circumvention requires correct transport configurations.
 Our talk will describe a future study aimed at evaluating 
@@
 in three different adversarial settings. 
-We solicit feedback to improve our study's design.
+We solicit feedback to improve our study's design.}
 \end{abstract}
@@
 \section{Tor's Usability}
+{\color {red}
 %Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.
@@
 To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool, rather than an anonymity tool.
+censorship circumvention tool, rather than an anonymity tool. }
 
@@
 \noindent {\bfseries Overview}
+{\color {red}
 % test tor, test improvements, may do followups on demand, push changes.
@@
 There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
-The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.
+The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.}\\
 
@@
 \noindent {\bfseries Experiment Flow} 
+{\color {red}
 % explain one experiment from start to end. 
@@
 We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
-We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.
-\\
+We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.} \\
 
 \noindent {\bfseries Censorship Environment Simulation} 
+{\color{red}
 We plan to simulate three censorship environments.
@@
 do ask why participants chose a specific pluggable 
-transport in our exit survey to gain some insight.\\
+transport in our exit survey to gain some insight.}\\
 

### 2015-10-05 paper/circumvention-experiment.tex
added the configuration dialog figure

@@
 The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.}\\
+
+\begin{figure}[t]
+  \centering
+    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
+    \caption{The Tor Bridges Configuration window of the Tor configuration interface.
+Tor users in censored environments and some of our participants will be required to select the correct bridge for circumventing censorship.
+Note that the interface prompts users to choose a transport type, which can be the source of confusion.
+Bridges are non-listed guard relays to the Tor network, and some of them can have transport types which obfuscate traffic in different ways.}
+\end{figure}
 

### 2015-10-05 paper/circumvention-experiment.tex
added the digraph for interface paths

@@
 The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.}\\
+
+\begin{figure*}[t]
+  \centering
+    \includegraphics[width=\textwidth]{../torconfig.png}
+    \caption{This flow chart shows all of the possible paths taken through the Tor configuration interface.
+A state represents a window in the interface, with the exception of the leaves, which indicate the final action taken by the interface (``q'' for quit, ``s'' for success, and ``e'' for error).
+The transitions between the states indicate which user action causes that transition.
+The cause for error is can be found \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
+\end{figure*}
 

### 2015-10-05 paper/circumvention-experiment.tex
updated censorship environment simulation section

@@
 
+% setting up the environment wrt interface paths.
+% setting up motivation: roleplay, tasks to complete
+% follow up with a survey
+
 %improve what is below:
@@
 \begin{figure}[t]
+\label{fig:bridges}
   \centering
@@
 \noindent {\bfseries Censorship Environment Simulation} 
-{\color{red}
 We plan to simulate three censorship environments.
@@
 They are not meant perfectly to replicate the network environment
-in any particular country; rather, they are abstract simulations
-that are nevertheless inspired by reality.
-
-% talk about how these censorship environments cover the UI path
+in any particular country. Although inspired by reality, these
+abstract simulations are intended to require distinct configurations
+of the Tor Browser from our participants.
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item{Corporate network.}
-A simulation of an enterprise or educational firewall.
-Blocks all services but HTTP, HTTPS, and DNS.
-Certain non-work-related domains, like youtube.com and torproject.org,
-are blocked by DNS and HTTP inspection.
-Blocked requests are redirected to a block page.
-\item{DNS-only censor.}
-This censor injects false replies to DNS queries
-for forbidden domain names (DNS poisoning),
-but does not do deep packet inspection on TCP streams.
-Unlike the corporate censor, this censor allows protocols
-outside a small whitelisted set.
-\item{Comprehensive censor.}
-Employs a variety of techniques, depending on the target.
-May do DNS poisoning, IP blocking, and inspection of TCP streams
-(examining the URL of HTTP requests, for example).
-Some domains may be blocked by DNS and deep packet inspection;
-others may additionally be blocked by IP address.
-Tor relays are blocked by IP address.
-Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
-Blocked requests fail silently (no block page).
+\item {\bfseries Mild censorship} 
+(Reflective of countries such as {\color{red}?? and ??}.)
+Certain domain names are blocked. Reaching these 
+domains requires any use of a censorship circumvention 
+tool. The default option to ``connect'' to the Tor network 
+directly will circumvent this censor. Additional correct
+bridge or proxy configuration are optional. 
+\item {\bfseries Intermediate censorship} 
+(Reflective of countries such as {\color{red}?? and ??}.)
+Certain domain names are blocked. Censorship circumvention
+tools are blocked. Since Tor is blocked by blocking all public Tor
+relay nodes, the default option to ``connect'' to the Tor network
+directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
+or a valid non-public bridge is required to circumvent this censor.  
+Additional correct proxy configuration is optional.
+\item {\bfseries Comprehensive censorship} 
+(Reflective of countries such as China and Syria.)
+Certain domain names are blocked. Censorship circumvention tools
+are thoroughly blocked. Tor is blocked by blocking all public
+Tor relay nodes, and the censor has examined source code to block
+all hard-coded bridge relays in the configuration interface. The default option
+to ``connect'' to the Tor network directly will fail. Choosing any other bridges than
+``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
+domain-fronting requires censors to block entire CDNs to also block this
+transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments. Additional details,
+see ~\cite{fifield2015blocking}.\\
 \end{itemize}
-
-In certain real censorship environment and our most 
-prohibitive simulated censorship environments, only some of 
-Tor's pluggable transports work in censorship environments
-where others do not. Some of them require additional information
-(like bridge addresses) before they work. Currently, we do not 
-have a way to target test specific transports. However, we 
-do ask why participants chose a specific pluggable 
-transport in our exit survey to gain some insight.}\\
 
@@
 
-%%  FROM ANONYMITY UX STUDY 
+% from anonymity study
 Our online artifacts of study of Tor as an anonymity tool, such as 

### 2015-10-05 paper/circumvention-experiment.tex
finished up experiment flow section

@@
 \noindent {\bfseries Experiment Flow} 
-{\color {red}
-% explain one experiment from start to end. 
-At the start of the study, participants will be informed
-of the role they they will be playing in the study. Particularly,
-they will be informed that they are in a censorship environment
-which prevents them from visiting certain websites, but they
-are people who would like to visit those websites for 
-leisurely purposes.
+We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
+We will instruct them to visit a non-blocked website and a blocked website on a ``standard'' browser (one that is not used for censorship circumvention, such as Chrome, Safari, or Firefox) to illustrate the situation.
+Then, the participants will be informed of the role they they will be playing in the study. Particularly,
+they will be informed that they are a normal citizen in a censorship environment
+which prevents them from visiting certain websites, that they are visiting the website for non-critical leisurely purposes,
+and that there is a minimal chance of risk.
+This information is given so that the participants can have an idea of the role they are playing, and to achieve consistency across participants.
+Their behavior might be different if they were visiting websites to accomplish a critical task, or if they knew that there were great risks.
 
-%talk about how participants will be motivated to configure to 
-%complete these tasks. participants will write down the answers 
-%on a sheet of paper...
+After explaining the situation and their role, we will explain what Tor is, and how they can use it if necessary, and instruct them to complete the a set of tasks which will require visiting blocked websites.
+Ultimately, the participants will need to configure their Tor Browser to circumvent the simulated censorship environment.
+These tasks have a three-fold purpose of providing participants with feedback (if they did not correctly configure their browser, they cannot reach the website),  motivating the participants to configure the browser correctly, and providing the researchers with an indicator of successful censorship circumvention.
 
-We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
-We will instruct them to visit notblocked.com and also blocked.com to illustrate the situation that they are in.
-We will also explain what Tor is, and how they can use it if necessary, and ask them to complete the set of tasks.
-To complete all the tasks, the participants will ultimately need to get the correct configuration settings for the country they are simulated to be in.
-We will end the experiment with a survey which asks them things like their security background, tech exposure, what was unexpected, what was hard, etc.
-We plan to analyze: which configuration tasks are hard (bridges versus proxies, etc.), how many were successful, how long it took users to configure, if they understood the process, if they were confident that it was working as expected, etc.} \\
+We will end the experiment with a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.
+A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.\\
 

### 2015-10-05 paper/circumvention-experiment.tex
little tweaks to experiment flow section

@@
 These tasks have a three-fold purpose of providing participants with feedback (if they did not correctly configure their browser, they cannot reach the website),  motivating the participants to configure the browser correctly, and providing the researchers with an indicator of successful censorship circumvention.
+While participants are on the computer, their screens will be recorded to capture how participants configure their browser, and to provide additional evidence that they have completed the tasks.
+The participants will be unaware that their screens are being recorded, to prevent deviations in behavior.
 
-We will end the experiment with a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.
-A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.\\
+After completing the browsing tasks, we will administer a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.
+A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.
+
+ The experiment will conclude with a debriefing, which will inform that the participants of their screen capture and obtaining re-consent for the information.  \\
 

### 2015-10-05 paper/circumvention-experiment.tex
updated the authors
Hard wrap LaTeX source code for readability

@@
 \author{
- \alignauthor David Fifield\textsuperscript{1} and Linda N. Lee\textsuperscript{1}, Serge Egelman\textsuperscript{1,2}, David Wagner\textsuperscript{1}\\
+ \alignauthor Linda N. Lee, David Fifield, Nathan Malkin \\
    \vspace{0.5em}
-   \affaddr{\textsuperscript{1}University of California, Berkeley, \{fifield,lnl,egelman,daw\}@cs.berkeley.edu}, \\
-   \affaddr{\textsuperscript{2}International Computer Science Institute, egelman@icsi.berkeley.edu}\\
+   \affaddr{University of California, Berkeley} \\
+   \affaddr{\{lnl,fifield,nmalkin\}@cs.berkeley.edu}\\
 }
@@
 % setting up the environment wrt interface paths.
-% setting up motivation: roleplay, tasks to complete
-% follow up with a survey
 
 %improve what is below:
-For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both.
-There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use.
-The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.}\\
+For users to circumvent censorship in their resident countries, they will need
+to configure Tor to set up a proxy, bridge, or both. There is a configuration
+wizard to help guide users through setting up their connection, but our
+hypothesis is that the average user will not easily be able to configure Tor
+correctly in these adverse settings, as they require the user to provide IP
+addresses of proxies or bridges to use. The goal of our experiment is to see
+how successful users are at carrying out common browsing tasks in an
+adversarial setting using Tor.}\\
 
@@
     \includegraphics[width=\textwidth]{../torconfig.png}
-    \caption{This flow chart shows all of the possible paths taken through the Tor configuration interface.
-A state represents a window in the interface, with the exception of the leaves, which indicate the final action taken by the interface (``q'' for quit, ``s'' for success, and ``e'' for error).
-The transitions between the states indicate which user action causes that transition.
-The cause for error is can be found \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
+    \caption{This flow chart shows all of the possible paths taken through the
+    Tor configuration interface. A state represents a window in the interface,
+    with the exception of the leaves, which indicate the final action taken by
+    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
+    transitions between the states indicate which user action causes that
+    transition. The cause for error is can be found
+\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
 \end{figure*}
@@
     \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
-    \caption{The Tor Bridges Configuration window of the Tor configuration interface.
-Tor users in censored environments and some of our participants will be required to select the correct bridge for circumventing censorship.
-Note that the interface prompts users to choose a transport type, which can be the source of confusion.
-Bridges are non-listed guard relays to the Tor network, and some of them can have transport types which obfuscate traffic in different ways.}
+    \caption{The Tor Bridges Configuration window of the Tor configuration
+    interface. Tor users in censored environments and some of our participants
+    will be required to select the correct bridge for circumventing censorship.
+    Note that the interface prompts users to choose a transport type, which can be
+    the source of confusion. Bridges are non-listed guard relays to the Tor
+    network, and some of them can have transport types which obfuscate traffic in
+    different ways.}
 \end{figure}
@@
 \noindent {\bfseries Experiment Flow} 
-We start off the experiment by telling them that they are in an adversarial setting, and that some websites are blocked and some websites are not.
-We will instruct them to visit a non-blocked website and a blocked website on a ``standard'' browser (one that is not used for censorship circumvention, such as Chrome, Safari, or Firefox) to illustrate the situation.
+We start off the experiment by telling them that they are in an adversarial
+setting, and that some websites are blocked and some websites are not. We will
+instruct them to visit a non-blocked website and a blocked website on a
+``standard'' browser (one that is not used for censorship circumvention, such
+as Chrome, Safari, or Firefox) to illustrate the situation.
 Then, the participants will be informed of the role they they will be playing in the study. Particularly,
@@
 which prevents them from visiting certain websites, that they are visiting the website for non-critical leisurely purposes,
-and that there is a minimal chance of risk.
-This information is given so that the participants can have an idea of the role they are playing, and to achieve consistency across participants.
-Their behavior might be different if they were visiting websites to accomplish a critical task, or if they knew that there were great risks.
+and that there is a minimal chance of risk. This information is given so that
+the participants can have an idea of the role they are playing, and to achieve
+consistency across participants. Their behavior might be different if they were
+visiting websites to accomplish a critical task, or if they knew that there
+were great risks.
 
-After explaining the situation and their role, we will explain what Tor is, and how they can use it if necessary, and instruct them to complete the a set of tasks which will require visiting blocked websites.
-Ultimately, the participants will need to configure their Tor Browser to circumvent the simulated censorship environment.
-These tasks have a three-fold purpose of providing participants with feedback (if they did not correctly configure their browser, they cannot reach the website),  motivating the participants to configure the browser correctly, and providing the researchers with an indicator of successful censorship circumvention.
-While participants are on the computer, their screens will be recorded to capture how participants configure their browser, and to provide additional evidence that they have completed the tasks.
-The participants will be unaware that their screens are being recorded, to prevent deviations in behavior.
+After explaining the situation and their role, we will explain what Tor is, and
+how they can use it if necessary, and instruct them to complete the a set of
+tasks which will require visiting blocked websites. Ultimately, the
+participants will need to configure their Tor Browser to circumvent the
+simulated censorship environment. These tasks have a three-fold purpose of
+providing participants with feedback (if they did not correctly configure their
+browser, they cannot reach the website),  motivating the participants to
+configure the browser correctly, and providing the researchers with an
+indicator of successful censorship circumvention. While participants are on the
+computer, their screens will be recorded to capture how participants configure
+their browser, and to provide additional evidence that they have completed the
+tasks. The participants will be unaware that their screens are being recorded,
+to prevent deviations in behavior.
 
-After completing the browsing tasks, we will administer a survey that 1) measures participant demographics, participant technical fluency, and participant familiarity with Tor and 2) collects qualitative feedback on from participants on their browsing experience, particularly with respect to any parts of the configuration interface which was confusing to them, but also about the browsing experience as a whole.
-A rough draft of the survey can be found \href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.
+After completing the browsing tasks, we will administer a survey that 1)
+measures participant demographics, participant technical fluency, and
+participant familiarity with Tor and 2) collects qualitative feedback on from
+participants on their browsing experience, particularly with respect to any
+parts of the configuration interface which was confusing to them, but also
+about the browsing experience as a whole.  A rough draft of the survey can be
+found
+\href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.
 
- The experiment will conclude with a debriefing, which will inform that the participants of their screen capture and obtaining re-consent for the information.  \\
+The experiment will conclude with a debriefing, which will inform that the
+participants of their screen capture and obtaining re-consent for the
+information.  \\
 

### 2015-10-05 paper/circumvention-experiment.tex
hashed out the abstract.

@@
 \begin{abstract}
-{\color{red}
 Tor has grown beyond its original purpose as and has 
-since become an important Internet circumvention tool.
+since become an important Internet circumvention tool. {\color {red} cite something here..}
 We specifically examine it usability as a censorship circumvention tool,
 an essential facet for adoption and use.  
-We focus our analysis on the connection configuration dialog of Tor browser,
+We focus our analysis on the connection configuration interface of Tor browser,
 as censorship circumvention requires correct transport configurations.
-Our talk will describe a future study aimed at evaluating 
-if and how easily users can circumvent censorship using Tor Browser,
-isolating specific browser features to study in the process. 
-To this end, we will conduct a large-scale user study examining hundreds of users 
+We will conduct a large-scale user study examining 60-100 of users 
 on how they navigate Tor's configuration wizard to complete seven browsing tasks 
-in three different adversarial settings. 
-We solicit feedback to improve our study's design.}
+in three different adversarial settings. Our study combines quantitative measurements (interface
+paths taken to success, time to success, and which configuration was chosen) and
+qualitative measurements (if users were comfortable with use, what was most confusing, and 
+if they would use the browser again). The first phase of the study will evaluate if and how 
+easily users can circumvent censorship using 
+Tor Browser, isolating specific browser features to study in the process. The second phase
+of the study will test improvements to the interface and an alternate interface. 
+Our goal is to integrate positive usability changes into the Tor Browser. Since
+the configuration interface is modular and does not require changes to the Tor Browser
+functionality, these changes will be easy to deploy.
+
 \end{abstract}

### 2015-10-05 paper/circumvention-experiment.tex
grammar errors why

@@
 \begin{abstract}
-Tor has grown beyond its original purpose as and has 
-since become an important Internet circumvention tool. {\color {red} cite something here..}
-We specifically examine it usability as a censorship circumvention tool,
+Tor has grown beyond its original purpose as an anonymity tool and has 
+since become an important censorship circumvention tool. {\color {red} cite something here..}
+We specifically examine its usability as a censorship circumvention tool,
 an essential facet for adoption and use.  

### 2015-10-05 paper/circumvention-experiment.tex
editing down the intro

@@
 
-Tor is the most widely used anonymity tool today.
-However, there are complaints that Tor is not usable.
-Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser,
+Tor is primarily known as an anonymity tool. In fact, it is the most widely used anonymity tool today. 
+However, there are complaints that Tor is not usable. Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, 
 finding out when people would get frustrated with Tor so much they would stop using it. 
 %redo this next couple sentences into something better
-But what about the people who are using Tor? what usability issues would there be if people were not stopped? 
 To our knowledge, that has been the only user study of Tor. 
@@
 We briefly describe the results of a completed study
-that examined the download and installation processes, 
-as well as basic browsing behaviors.
+that examined the download, installation, and basic browsing behaviors.
 This study uncovered a number of bugs and stopping points
@@
 
-We ran a small pilot study of five journalists which involved a cognitive walk through in which 
+We ran a small pilot study of five journalists which involved a talk-aloud in which 
 participants explained the motivation for their actions and any confusion that they had during the process. 
+We recorded what they were saying out loud in their cognitive walk through,
+and later added these words to the screen videos as subtitles.
 We did this to find new stopping points, and sources of confusion. 
@@
 (searching, setting new circuits, etc.), and generally if they had any usability complaints about the browser. 
+The participants also took an exit survey which estimated their familiarity with technology and security.
 
-We recruited five journalists from Berkeley by reaching out to journalist contacts. 
-%Demographics here. 
-During the study, we made a video recording of each participant's computer screen
-and simultaneously projected it
-into another room with Tor developers.
-We recorded what they were saying out loud in their cognitive walk through,
-and later added these words to the screen videos as subtitles.
-The participants also took an exit survey which estimated their familiarity with technology and security.
  On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).
 The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.
-Our talk will feature brief highlights of the screen videos and a summary of interface changes.
 

### 2015-10-05 paper/circumvention-experiment.tex
more intro trimming

@@
 Tor Browser since the introduction of the 4.0 series,
-which introduced radical UI changes.
-
-We briefly describe the results of a completed study
-that examined the download, installation, and basic browsing behaviors.
-This study uncovered a number of bugs and stopping points
-which has already effected concrete change in the browser.
-
-We ran a small pilot study of five journalists which involved a talk-aloud in which 
-participants explained the motivation for their actions and any confusion that they had during the process. 
-We recorded what they were saying out loud in their cognitive walk through,
-and later added these words to the screen videos as subtitles.
-We did this to find new stopping points, and sources of confusion. 
-But in the process, we were also able to observe how users would download Tor, 
-if they could understand the address bar/menu, how well they were able to complete basic tasks
-(searching, setting new circuits, etc.), and generally if they had any usability complaints about the browser. 
-The participants also took an exit survey which estimated their familiarity with technology and security.
-
- On average, participants took 26 minutes to complete the study ($\sigma = 7$~min).
-The result was that people did have difficulty with installing Tor Browser (principally because of the Gatekeeper code-signing feature on OS~X), did not understand what many of the many options meant, and were confused about why certain things were happening.
+which introduced radical UI changes. We ran a small pilot study 
+of five journalists. This study uncovered a number of bugs and 
+stopping points which has already effected concrete change in the browser.
 

### 2015-10-05 paper/circumvention-experiment.tex
Clarify experimental procedure

@@
 We plan to recruit from 100-200 users for the purpose of this study, 
-making it largest user study to examine Tor.  This study will be conducted at the 
+making it the largest user study of Tor to date.  This study will be conducted at the
 Experimental Social Science Laboratory (Xlab)
-at the University of California, Berkeley, which consists of 36 laptops with 
-cubicle walls separating each laptop. We will use individual host firewalls to simulate
+at the University of California, Berkeley, which consists of 36 laptops,
+separated by cubicle walls. We will use individual host firewalls to simulate
 censorship environments and will record computer screens to capture 
 user activity. The total length of the experiment, including briefing, completing the censorship 
-circumvention tasks, exit survey, and debriefing, will take about an hour. 
-Participants will be compensated \$30 for their time, which is more to cover 
+circumvention tasks, exit survey, and debriefing, will be about an hour.
+Participants will be compensated \$30 for their time, which covers
 minimum wage for an hour and any transportation costs to the lab.  \\
@@
 \noindent {\bfseries Experiment Flow} 
-We start off the experiment by telling them that they are in an adversarial
-setting, and that some websites are blocked and some websites are not. We will
+The experiment begins with the participants being informed that they are in a
+simulated censorship
+environment, where some --- but not all --- websites are blocked. We will
 instruct them to visit a non-blocked website and a blocked website on a
@@
 as Chrome, Safari, or Firefox) to illustrate the situation.
-Then, the participants will be informed of the role they they will be playing in the study. Particularly,
-they will be informed that they are a normal citizen in a censorship environment
-which prevents them from visiting certain websites, that they are visiting the website for non-critical leisurely purposes,
-and that there is a minimal chance of risk. This information is given so that
-the participants can have an idea of the role they are playing, and to achieve
-consistency across participants. Their behavior might be different if they were
+Then, the participants will find out the role they they will be playing in the study.
+This role is that of a regular citizen, who is trying to visit blocked websites
+for non-critical leisurely purposes,
+and that there is a minimal chance of risk. This information is given
+to achieve
+consistency across participants: their behavior might be different if they were
 visiting websites to accomplish a critical task, or if they knew that there
@@
 After explaining the situation and their role, we will explain what Tor is, and
-how they can use it if necessary, and instruct them to complete the a set of
+how they can use it if necessary, and instruct them to complete a set of
 tasks which will require visiting blocked websites. Ultimately, the
@@
 configure the browser correctly, and providing the researchers with an
-indicator of successful censorship circumvention. While participants are on the
-computer, their screens will be recorded to capture how participants configure
+indicator of successful censorship circumvention.
+Participants' screens will be recorded to capture how they configure
 their browser, and to provide additional evidence that they have completed the
-tasks. The participants will be unaware that their screens are being recorded,
-to prevent deviations in behavior.
+tasks.
 
-After completing the browsing tasks, we will administer a survey that 1)
-measures participant demographics, participant technical fluency, and
-participant familiarity with Tor and 2) collects qualitative feedback on from
-participants on their browsing experience, particularly with respect to any
-parts of the configuration interface which was confusing to them, but also
-about the browsing experience as a whole.  A rough draft of the survey can be
+After users complete the browsing tasks, we will administer a survey that 1)
+measures demographics, technical fluency, and
+familiarity with Tor and 2) collects qualitative feedback from
+participants about their browsing experience as a whole
+and the configuration interface specifically.
+A rough draft of the survey can be
 found

### 2015-10-05 paper/circumvention-experiment.tex
Fix more style issues

@@
 all hard-coded bridge relays in the configuration interface. The default option
-to ``connect'' to the Tor network directly will fail. Choosing any other bridges than
+to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
 ``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
 domain-fronting requires censors to block entire CDNs to also block this
-transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments. Additional details,
-see ~\cite{fifield2015blocking}.\\
+transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
+(See ~\cite{fifield2015blocking} for additional details.)\\
 \end{itemize}
@@
 The difficulty of circumventing  censorship to visit the 
-websites required for the tasks will vary on the 
+websites required for the tasks will vary depending on the 
 simulated censorship environment. Since all participants will be given the 
@@
 \item {\bfseries Test an improved configuration interface} With the measurements collected
-from testing the interface as-is, Nathan will be designing ways to improve the interface to minimize
+from testing the interface as-is, we will be designing ways to improve the interface to minimize
 time taken, paths taken, and error states reached.
@@
 greatly automate the process. There are tradeoffs between ease of use and transparency
-of the system's, and ethical considerations with loggable errors resulting from automated configuration. 
+of the systems, and ethical considerations with loggable errors resulting from automated configuration. 
 \item {\bfseries Push changes} We have the support of Tor developers

### 2015-10-05 paper/circumvention-experiment.tex
merge

--- 2015-10-05 paper/circumvention-experiment.tex
@@
 {\color {red}
-% test tor, test improvements, may do followups on demand, push changes.
-
-% setting up the environment wrt interface paths.
-
 %improve what is below:
@@
 to configure Tor to set up a proxy, bridge, or both. There is a configuration
-wizard to help guide users through setting up their connection, but our
-hypothesis is that the average user will not easily be able to configure Tor
-correctly in these adverse settings, as they require the user to provide IP
-addresses of proxies or bridges to use. The goal of our experiment is to see
-how successful users are at carrying out common browsing tasks in an
-adversarial setting using Tor.}\\
+wizard to help guide users through setting up their connection, but
+
+Our hypothesis is that the average user does not have knowledge
+knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
+addresses bridges. Certain real-world censorship settings require the user to provide this
+information during configuration, which will affect how successful users are at 
+circumventing censorship using Tor. There are blogs in countries which have extensive
+censorship on how to configure Tor correctly {\color {red} cite something}, and participants may 
+receive additional informatio through word of mouth. Our study will measure if the configuration
+interface successfully guides users to correctly configuring their browser, not accounting 
+for any additional  information that a real user may have.}\\
 
 \begin{figure*}[t]
+\label{fig:interface}
   \centering
@@
 \noindent {\bfseries Experiment Flow} 
+We will run three sets of the experiment, the first set to test the current configuration
+interface, a second set to test the improved interface, and a third set to test the 
+alternate configuration interface. The experiment flow will be the same across all 
+sets of experiments, with the fact that the configuration interface will be altered 
+across sets.
+
 The experiment begins with the participants being informed that they are in a

### 2015-10-05 paper/circumvention-experiment.tex
Copy-edit list of tasks

@@
 \item Google search for the population of Zimbabwe. 
-\item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
+\item On YouTube, find a video playing Bach's ``Ode to Joy.''
 \item Find the Amazon best-sellers in ``Movies \& TV.''
-\item On Yahoo, find the exchange rate of dollars to euros.
+\item On Yahoo, find the exchange rate of Dollars to Euros.
 \item Find the Wikipedia ``History'' portal's featured article. 
 \item On Twitter, find the currently trending topics.
-\item On Bing Maps, find directions from Time Square to Carnegie Hall.
+\item On Bing Maps, find directions from Times Square to Carnegie Hall.
 \end{itemize}

### 2015-10-05 paper/circumvention-experiment.tex
finished design section

--- 2015-10-05 paper/circumvention-experiment.tex
@@
 \noindent {\bfseries Overview}
-{\color {red}
-%improve what is below:
-For users to circumvent censorship in their resident countries, they will need
-to configure Tor to set up a proxy, bridge, or both. There is a configuration
-wizard to help guide users through setting up their connection, but
+There is a configuration interface (Figure ~\ref{fig:interface}) to help guide users through 
+setting up their connection to the Tor network. Through this, users can configure Tor to set up a bridge,
+proxy, or both. Since proxies are not a Tor-specific notion nor explicitly required to circumvent censorship, 
+we will focus our study on bridge configuration. We accomplish this by placing users in crafted simulated 
+censorship environments which require particular bridge configurations to circumvent censorship.
 
@@
 interface successfully guides users to correctly configuring their browser, not accounting 
-for any additional  information that a real user may have.}\\
+for any additional  information that a real user may have.\\
 

### 2015-10-05 paper/circumvention-experiment.tex
fix abstract, hack at intro

@@
 if they would use the browser again). The first phase of the study will evaluate if and how 
-easily users can circumvent censorship using 
-Tor Browser, isolating specific browser features to study in the process. The second phase
+easily users can circumvent censorship using Tor Browser. The second phase
 of the study will test improvements to the interface and an alternate interface. 
@@
 
-Tor is primarily known as an anonymity tool. In fact, it is the most widely used anonymity tool today. 
-However, there are complaints that Tor is not usable. Norcie~\cite{norcie2012eliminating} did an experiment which identified stopping points in Tor browser, 
-finding out when people would get frustrated with Tor so much they would stop using it. 
-%redo this next couple sentences into something better
-To our knowledge, that has been the only user study of Tor. 
+As the most widely used anonymity tool today, Tor is primarily known as an anonymity tool. 
+For this reason, user studies on Tor have been solely about, the usability of Tor as an 
+anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
+``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
+to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
 Since then, Tor has had a lot of updates. 

### 2015-10-05 paper/circumvention-experiment.tex
first paragraph of intro

@@
 \section{Tor's Usability}
-{\color {red}
-%Idea is to cover background on Tor's usability as an anonymity tool, and then highlight the shift in focus to evaluating Tor's usability as a censorship circumvention tool.
-
 As the most widely used anonymity tool today, Tor is primarily known as an anonymity tool. 
@@
 to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
-Since then, Tor has had a lot of updates. 
-Additionally, there were a lot of features that were untested. 
-There have been been no major usability evaluations of
-Tor Browser since the introduction of the 4.0 series,
-which introduced radical UI changes. We ran a small pilot study 
-of five journalists. This study uncovered a number of bugs and 
-stopping points which has already effected concrete change in the browser.
+Since then, Tor has had a lot of updates.There have been been no published usability evaluations of
+Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
+Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
+This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
+5.1 and later.
 
+{\color {red}
 After our first usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management.

### 2015-10-05 paper/circumvention-experiment.tex
finished rough intro

@@
 
-{\color {red}
-After our first usability evaluation of Tor, it was clear to us that so many of the features had been left unevaluated---such as advanced web browsing tasks, the configuration menu, automatic updates, and identity and cookie management.
-%say something about how we resolved this somehow, and how it doesn't necessarily need our attention now
-We found that the most effective way to resolve the problems encountered was more user guidance and interface remodeling rather than continued user observations.
-%emphasize how we are aiming for new research, not new test cases for debugging an interface
+There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management.
 Rather than selecting the features to study in isolation,
 we decided to focus on an important use case of Tor browser, censorship circumvention. 
-%say something along the lines of ``x people are using it for this, and there's no work on it,'' 
-%if there are stats on this type of thing.
+{\color {red} stats on pervasiveness of censorship here}
 To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool, rather than an anonymity tool. }
+censorship circumvention tool, rather than an anonymity tool.
 

### 2015-10-05 paper/circumvention-experiment.tex
add some sources

@@
 we decided to focus on an important use case of Tor browser, censorship circumvention. 
-{\color {red} stats on pervasiveness of censorship here}
+Internet censorship is shown to be pervasive across the world today \ref{faris2008measuring}. 
 To our knowledge, this is the first user study investigating the usability of Tor as a 
@@
 information during configuration, which will affect how successful users are at 
-circumventing censorship using Tor. There are blogs in countries which have extensive
-censorship on how to configure Tor correctly {\color {red} cite something}, and participants may 
-receive additional informatio through word of mouth. Our study will measure if the configuration
+circumventing censorship using Tor. Participants may receive additional information through word 
+of mouth, help from relatives, or blogs. Our study will measure if the configuration
 interface successfully guides users to correctly configuring their browser, not accounting 

### 2015-10-05 paper/circumvention-experiment.tex
Rework configuration overview section

@@
 \noindent {\bfseries Overview}
-There is a configuration interface (Figure ~\ref{fig:interface}) to help guide users through 
-setting up their connection to the Tor network. Through this, users can configure Tor to set up a bridge,
-proxy, or both. Since proxies are not a Tor-specific notion nor explicitly required to circumvent censorship, 
-we will focus our study on bridge configuration. We accomplish this by placing users in crafted simulated 
-censorship environments which require particular bridge configurations to circumvent censorship.
+The Tor Browser provides a configuration interface (Figure
+~\ref{fig:interface}) to guide users through setting up their connection to the
+Tor network. While people in most countries can connect to Tor using the
+dialog's default settings, citizens in certain censorship environments must
+make use of additional settings, such as bridges, proxies, or both.
 
-Our hypothesis is that the average user does not have knowledge
-knowledge on how certain pluggable transports work, or to provide non-publicly listed IP
-addresses bridges. Certain real-world censorship settings require the user to provide this
-information during configuration, which will affect how successful users are at 
-circumventing censorship using Tor. Participants may receive additional information through word 
-of mouth, help from relatives, or blogs. Our study will measure if the configuration
-interface successfully guides users to correctly configuring their browser, not accounting 
-for any additional  information that a real user may have.\\
+Our hypothesis is that, under these circumstances, the average user will
+struggle to connect, because they lack knowledge of the technical terms and
+mechanisms required for circumvention (such as pluggable transports) and cannot
+obtain information not explicitly provided by the user interface (e.g., IP
+addresses of non-publicly listed bridges).
+
+Our study will test this hypotheses by measuring if the connection
+interface successfully guides users to correctly configuring their browser.\\
 

### 2015-10-05 paper/circumvention-experiment.tex
got rid of red stuff

--- 2015-10-05 paper/circumvention-experiment.tex
@@
 Tor has grown beyond its original purpose as an anonymity tool and has 
-since become an important censorship circumvention tool. {\color {red} cite something here..}
+since become an important censorship circumvention tool. It now listed 
+as one of the ways that normal people use Tor \cite{whotor}.
 We specifically examine its usability as a censorship circumvention tool,
@@
 we decided to focus on an important use case of Tor browser, censorship circumvention. 
-Internet censorship is shown to be pervasive across the world today \ref{faris2008measuring}. 
+Internet censorship is shown to be pervasive across the world today \ref{faris2008measuring}, with 
+some countries blocking censorship circumvention tools as well \ref{winter2012great}. 
 To our knowledge, this is the first user study investigating the usability of Tor as a 
@@
 \item {\bfseries Mild censorship} 
-(Reflective of countries such as {\color{red}?? and ??}.)
+%(Reflective of countries such as {\color{red}?? and ??}.)
 Certain domain names are blocked. Reaching these 
@@
 \item {\bfseries Intermediate censorship} 
-(Reflective of countries such as {\color{red}?? and ??}.)
+%(Reflective of countries such as {\color{red}?? and ??}.)
 Certain domain names are blocked. Censorship circumvention
@@
 \item {\bfseries Comprehensive censorship} 
-(Reflective of countries such as China and Syria.)
+%(Reflective of countries such as China and Syria.)
 Certain domain names are blocked. Censorship circumvention tools

### 2015-10-05 paper/circumvention-experiment.tex
fix space
fixing citation linking errors

@@
 we decided to focus on an important use case of Tor browser, censorship circumvention. 
-Internet censorship is shown to be pervasive across the world today \ref{faris2008measuring}, with 
-some countries blocking censorship circumvention tools as well \ref{winter2012great}. 
+Internet censorship is shown to be pervasive across the world today \cite{faris2008measuring}, with 
+some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
 To our knowledge, this is the first user study investigating the usability of Tor as a 
@@
 to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
-``meek-amazon,'' ``meek-azure,'' and``meek-google,'' will fail. This is because 
+``meek-amazon,'' ``meek-azure,'' and ``meek-google,'' will fail. This is because 
 domain-fronting requires censors to block entire CDNs to also block this
@@
 \item On Twitter, find the currently trending topics.
-\item On Bing Maps, find directions from Times Square to Carnegie Hall.
+\item On Bing Maps, find directions from Times Square to Carnegie Hall.\\
 \end{itemize}
+
+\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} blah blah}
 

### 2015-10-05 paper/circumvention-experiment.tex
kill orphans MUAHHAH and making space

@@
 To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool, rather than an anonymity tool.
+censorship circumvention tool.
 
@@
 alternate configuration interface. The experiment flow will be the same across all 
-sets of experiments, with the fact that the configuration interface will be altered 
-across sets.
+sets of experiments, but the configuration interface will be different across sets.
 
@@
 to achieve
-consistency across participants: their behavior might be different if they were
-visiting websites to accomplish a critical task, or if they knew that there
-were great risks.
+consistency across participants: behaviors may change if the tasks were 
+critical or if there were great risks associated with configuration mistakes.
 
@@
 participants of their screen capture and obtaining re-consent for the
-information.  \\
+information.
 
@@
 % from anonymity study
-Our online artifacts of study of Tor as an anonymity tool, such as 
-the summary, results, and resulting browser changes are below:
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
-\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
-\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
-\end{itemize}
+%Our online artifacts of study of Tor as an anonymity tool, such as 
+%the summary, results, and resulting browser changes are below:
+%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+%\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
+%\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
+%\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
+%\end{itemize}
 

### 2015-10-05 paper/circumvention-experiment.tex
make more room

@@
     the source of confusion. Bridges are non-listed guard relays to the Tor
-    network, and some of them can have transport types which obfuscate traffic in
+    network; transports, supported by bridges, obfuscate traffic in
     different ways.}
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Test the Tor configuration interface} We will perform the largest-scale user study 
-of Tor to date, measuring how users configure Tor in three different adversarial settings. 
+\item {\bfseries Test the Tor configuration interface} We will perform the largest user study 
+of Tor, measuring Tor configuration in three different adversarial settings. 
 \item {\bfseries Test an improved configuration interface} With the measurements collected
-from testing the interface as-is, we will be designing ways to improve the interface to minimize
+from testing the interface as-is, we will be design and test improvements to minimize
 time taken, paths taken, and error states reached.

### 2015-10-05 paper/circumvention-experiment.tex
remove section
comment that section back in
add in countries again

@@
 \item {\bfseries Mild censorship} 
-%(Reflective of countries such as {\color{red}?? and ??}.)
-Certain domain names are blocked. Reaching these 
-domains requires any use of a censorship circumvention 
+(Reflective of countries such as France and Australia.)
+Certain domains are blocked. Reaching these 
+domains requires a censorship circumvention 
 tool. The default option to ``connect'' to the Tor network 
 directly will circumvent this censor. Additional correct
-bridge or proxy configuration are optional. 
+bridge or proxy configurations are optional. 
 \item {\bfseries Intermediate censorship} 
-%(Reflective of countries such as {\color{red}?? and ??}.)
-Certain domain names are blocked. Censorship circumvention
+(Reflective of countries such as Tunsia.)
+Certain domains are blocked. Censorship circumvention
 tools are blocked. Since Tor is blocked by blocking all public Tor
 relay nodes, the default option to ``connect'' to the Tor network
-directly will fail. A choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
-or a valid non-public bridge is required to circumvent this censor.  
+directly will fail. Any choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
+or a valid non-public bridge will circumvent this censor.  
 Additional correct proxy configuration is optional.
 \item {\bfseries Comprehensive censorship} 
-%(Reflective of countries such as China and Syria.)
-Certain domain names are blocked. Censorship circumvention tools
+(Reflective of countries such as China and Syria.)
+Certain domains are blocked. Censorship circumvention tools
 are thoroughly blocked. Tor is blocked by blocking all public
@@
 
-\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} blah blah}
+%\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} optional section here.}
 

### 2015-10-05 paper/circumvention-experiment.tex
add a little improvement and alternate interfaces section

@@
 
-%\noindent {\bfseries Improved and Alternative Interfaces} {\color {red} optional section here.}
+\noindent {\bfseries Improved and Alternative Interfaces} We have yet to design the 
+improvements to the interface, as they will be based on the data collected from 
+the user studies on the current configuration interface. In general, we will measure the 
+time it took to configure correctly, and help users avoid common mistakes. An alternate 
+interface to automate the configuration process for the user has been proposed in the 
+community. There issue is that the automation make the connection process less transparent, 
+and since there are countries who log internet activity, automated attempts to obviously
+use the Tor network could have the potential to be incriminating.
 

### 2015-10-06 paper/circumvention-experiment.tex

@@
 Tor has grown beyond its original purpose as an anonymity tool and has 
-since become an important censorship circumvention tool. It now listed 
+since become an important censorship circumvention tool. It is now listed
 as one of the ways that normal people use Tor \cite{whotor}.
@@
 \section{Tor's Usability}
-As the most widely used anonymity tool today, Tor is primarily known as an anonymity tool. 
-For this reason, user studies on Tor have been solely about, the usability of Tor as an 
+As the most widely used anonymity tool today, Tor is primarily known for this aspect of its functionality.
+For this reason, user studies on Tor have been solely about the usability of Tor as an
 anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
@@
 to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
-Since then, Tor has had a lot of updates.There have been been no published usability evaluations of
+Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
 Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
@@
 
-There are still many features of Tor that are left unevaluated through user research---such as advanced web tasks (such as accessing hidden services), the configuration menu to connect to the Tor network, configuring for automatic updates, and identity/cookie management.
-Rather than selecting the features to study in isolation,
-we decided to focus on an important use case of Tor browser, censorship circumvention. 
-Internet censorship is shown to be pervasive across the world today \cite{faris2008measuring}, with 
+There are still many features of Tor that are left unevaluated through user
+research --- such as advanced web tasks (e.g., accessing hidden services), the
+configuration menu to connect to the Tor network, configuring automatic
+updates, and identity/cookie management. Rather than selecting the features to
+study in isolation,
+we decided to focus on an important use case of Tor browser: censorship circumvention. 
+Internet censorship is pervasive across the world today \cite{faris2008measuring}, with 
 some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
@@
 
-Our study will test this hypotheses by measuring if the connection
+Our study will test this hypothesis by measuring if the connection
 interface successfully guides users to correctly configuring their browser.\\
@@
 The IRB protocol to run this user study has been approved (2014-12-6995). 
-We plan to recruit from 100-200 users for the purpose of this study, 
+We plan to recruit 100-200 users for the purpose of this study,
 making it the largest user study of Tor to date.  This study will be conducted at the
@@
 \noindent {\bfseries Experiment Flow} 
-We will run three sets of the experiment, the first set to test the current configuration
+We will conduct three separate experiments as part of this study:
+the first set to test the current configuration
 interface, a second set to test the improved interface, and a third set to test the 
@@
 Then, the participants will find out the role they they will be playing in the study.
-This role is that of a regular citizen, who is trying to visit blocked websites
+This role is that of a regular citizen who is trying to visit blocked websites
 for non-critical leisurely purposes,
-and that there is a minimal chance of risk. This information is given
+and for whom the chance of risk is minimal. This information is given
 to achieve
@@
 and knowledge of commonly seen censorship techniques.
-They are not meant perfectly to replicate the network environment
+They are not meant to perfectly replicate the network environment
 in any particular country. Although inspired by reality, these
@@
 
-The tasks were initially inspired by the top Alexa sites, 
+The tasks were inspired by the top Alexa sites,
 an indication of representative and relevant browsing behavior. 
@@
 \item Find the Amazon best-sellers in ``Movies \& TV.''
-\item On Yahoo, find the exchange rate of Dollars to Euros.
+\item On Yahoo, find the exchange rate of dollars to euros.
 \item Find the Wikipedia ``History'' portal's featured article. 
@@
 interface to automate the configuration process for the user has been proposed in the 
-community. There issue is that the automation make the connection process less transparent, 
+community. One concern about it is that the automation makes the connection process less transparent, 
 and since there are countries who log internet activity, automated attempts to obviously
@@
 \item {\bfseries Test an improved configuration interface} With the measurements collected
-from testing the interface as-is, we will be design and test improvements to minimize
+from testing the interface as-is, we will design and test improvements to minimize
 time taken, paths taken, and error states reached.

### 2015-10-09 paper/circumvention-experiment.tex
added a new section about the configuration interface and a section on the exit survey

@@
 censorship circumvention tool.
+
+\section{The Configuration Interface}
+
+\noindent {\bfseries Hypotheses} {\color {red} how we came up with these hypotheses, how we will measure these hypotheses, etc.}
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item  {\bfseries H1}: people don't know what a bridge or proxy is. > ask participants to define these terms in the survey.  
+\item  {\bfseries H2}: people don't know what the difference between a bridge and a proxy is > ask if people can distinguish them. 
+\item  {\bfseries H3}: people do not know when bridges or proxies are necessary > ask them this in the survey.  
+\item  {\bfseries H4}: proxies cause confusion when configuring bridges. screen recording: see if people click on proxies (none of the enviornments require a proxy)
+\item  {\bfseries H5}: people will favor familiar-sounding transports (i.e.
+meek-google versus meek-azure or scramblesuit) > see screen recordings, ask in survey for which transports were picked in which order and why they chose the final transport.
+\item {\bfseries H6}: (some dialogue is redundant.
+see opening window: "before you connect..." and bridge2 window: "you may use...") > we can try asking if people find these things useful, if they would prefer the interface without it, or if they read it.
+\end{itemize}
 
@@
 community. One concern about it is that the automation makes the connection process less transparent, 
-and since there are countries who log internet activity, automated attempts to obviously
-use the Tor network could have the potential to be incriminating.
+and since there are countries who log Internet activity, automated attempts to obviously
+use the Tor network could have the potential to be incriminating.\\
+
+\noindent {\bfseries Exit Survey}
+{\color {red} talk about the survey here.}
 

### 2015-10-09 paper/circumvention-experiment.tex
refactoring text

@@
 
-\noindent {\bfseries Hypotheses} {\color {red} how we came up with these hypotheses, how we will measure these hypotheses, etc.}
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item  {\bfseries H1}: people don't know what a bridge or proxy is. > ask participants to define these terms in the survey.  
-\item  {\bfseries H2}: people don't know what the difference between a bridge and a proxy is > ask if people can distinguish them. 
-\item  {\bfseries H3}: people do not know when bridges or proxies are necessary > ask them this in the survey.  
-\item  {\bfseries H4}: proxies cause confusion when configuring bridges. screen recording: see if people click on proxies (none of the enviornments require a proxy)
-\item  {\bfseries H5}: people will favor familiar-sounding transports (i.e.
-meek-google versus meek-azure or scramblesuit) > see screen recordings, ask in survey for which transports were picked in which order and why they chose the final transport.
-\item {\bfseries H6}: (some dialogue is redundant.
-see opening window: "before you connect..." and bridge2 window: "you may use...") > we can try asking if people find these things useful, if they would prefer the interface without it, or if they read it.
-\end{itemize}
-
-\section{Design}
-
 \noindent {\bfseries Overview}
@@
 make use of additional settings, such as bridges, proxies, or both.
-
-Our hypothesis is that, under these circumstances, the average user will
-struggle to connect, because they lack knowledge of the technical terms and
-mechanisms required for circumvention (such as pluggable transports) and cannot
-obtain information not explicitly provided by the user interface (e.g., IP
-addresses of non-publicly listed bridges).
 
@@
 \end{figure*}
+
+\noindent {\bfseries Hypotheses} We expect that the average user will
+struggle to connect because they lack knowledge of the technical terms and
+mechanisms required for circumvention (such as pluggable transports) and cannot
+obtain information not explicitly provided by the user interface (e.g., IP
+addresses of non-publicly listed bridges).
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item  {\bfseries H1}: people don't know what a bridge or proxy is. > ask participants to define these terms in the survey.  
+\item  {\bfseries H2}: people don't know what the difference between a bridge and a proxy is > ask if people can distinguish them. 
+\item  {\bfseries H3}: people do not know when bridges or proxies are necessary > ask them this in the survey.  
+\item  {\bfseries H4}: proxies cause confusion when configuring bridges. screen recording: see if people click on proxies (none of the environments require a proxy)
+\item  {\bfseries H5}: people will favor familiar-sounding transports (i.e.
+meek-google versus meek-azure or scramblesuit) > see screen recordings, ask in survey for which transports were picked in which order and why they chose the final transport.
+\item {\bfseries H6}: (some dialogue is redundant.
+see opening window: "before you connect..." and bridge2 window: "you may use...") > we can try asking if people find these things useful, if they would prefer the interface without it, or if they read it.
+\end{itemize}
+
+\section{Design}
 
@@
 participants of their screen capture and obtaining re-consent for the
-information.
+information. \\
 
@@
 abstract simulations are intended to require distinct configurations
-of the Tor Browser from our participants.
+of the Tor Browser from our participants. \\
 

### 2015-10-09 paper/circumvention-experiment.tex
(non-atomic) reformatting intro setion, added motivation section to intro, hacked out the configuration dialogue section

@@
 
-\section{Tor's Usability}
-As the most widely used anonymity tool today, Tor is primarily known for this aspect of its functionality.
+\section{Tor}
+\noindent {\bfseries Usability}
+Tor is primarily known as the most widely used anonymity tool today. 
 For this reason, user studies on Tor have been solely about the usability of Tor as an
@@
 This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
-5.1 and later.
+5.1 and later. \\
 
+\noindent {\bfseries Scoping}
 There are still many features of Tor that are left unevaluated through user
@@
 To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool.
+censorship circumvention tool.\\
+
+\noindent {\bfseries Motivation}
+Changing the configuration interface would not require changes to the 
+Tor Browser functionality, making any suggested improvements very practical to 
+deploy in a short period of time. {\color {red} Additionally, people are just literally
+being censored everywhere so a lot of people are using it for this purpose. So 
+we want this to be usable for that purpose.}
 
@@
 The Tor Browser provides a configuration interface (Figure
-~\ref{fig:interface}) to guide users through setting up their connection to the
+~\ref{fig:bridges}) to guide users through setting up their connection to the
 Tor network. While people in most countries can connect to Tor using the
@@
 make use of additional settings, such as bridges, proxies, or both. 
+%definition of a bridge, defintion of a proxy here. 
+Our study  will explore how well this interface successfully guides users to 
+correctly configuring their browser.\\
 
-Our study will test this hypothesis by measuring if the connection
-interface successfully guides users to correctly configuring their browser.\\
+\begin{figure}[h]
+\label{fig:bridges}
+  \centering
+    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
+    \caption{The Tor Bridges Configuration window of the Tor configuration
+    interface. Tor users in censored environments and some of our participants
+    will be required to select the correct bridge for circumventing censorship.
+    Note that the interface prompts users to choose a transport type, which can be
+    the source of confusion. Bridges are non-listed guard relays to the Tor
+    network; transports, supported by bridges, obfuscate traffic in
+    different ways.}
+\end{figure}
+
+\noindent {\bfseries Configuration Flow}
+{\color {red}
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Path 1}:  Configure directly
+\item {\bfseries Path 2}:  Bridge, no proxy
+\item {\bfseries Path 3}:  Bridge, proxy 
+\item {\bfseries Path 4}:  No bridge, proxy
+\item {\bfseries Path 5}:  No bridge, no proxy
+\end{itemize}
+
+Upon the startup of the configuration interface, a user is asked to describe their 
+current situation. If their Internet connection is censored or proxied, the user 
+clicks ``Configure'' to configure bridge and proxy settings. Otherwise, the user
+clicks ``Connect'' to connect directly to the Tor network.
+
+If a user is not connecting directly to the Tor network, then they are asked to 
+configure a bridge (as seen in TODO, the title of the window during configuration 
+is ``Tor Bridges Configuration''). We suspect that the reason for configuring a bridge
+first before a proxy is that more people need to configure bridges than proxies,
+but this is not known. The bridge configuration asks the users if their ISP blocks
+or censors connections to the Tor Network. The assumption here is that users will 
+not know if they need a bridge or not, but that they are equipped to answer if their
+current network environment censors the Tor Network. The configuration interface 
+uses this answer to deem if the user needs a bridge. A yes to this question would
+require a bridge while a no to this question would not. If they answer yes, they are 
+asked to configure the bridges. If they answer no, then the configuration interface 
+moves on to configuring proxies.
+
+If a user who is not directly connecting to the Tor network is finished configuring
+a bridge or has answered that they do not need a bridge, they are asked to 
+configure a local proxy (as seen in TODO, the title of the window during
+configuration is ``Local Proxy Configuration''). The proxy configuration asks the 
+users if they need to use a local proxy to access the Internet. The assumption 
+is that people will not know the answer to this question, so there is a text instructing
+users how to find the answer to this question below the question. If the answer to
+the question is yes, the user needs a proxy and is taken to a screen where they are
+asked to configure the proxy settings. If the user does not need a proxy, then the 
+configuration interface attempts to connect to the Tor network with all the 
+given inputs up to this point so far.
+
+Note that a user can decide to click ``Configure'' because they believe the 
+Internet connection is censored or proxied, but then answer the bridge and proxy
+questions in such a way that they deemed that they do not need a bridge or proxy 
+after all. In this case, clicking the ``Connect'' button after the above configuration steps
+would be equivalent to clicking ``Connect'' on the first screen. \\
+
+}
 
@@
 \end{figure*}
+
+\noindent {\bfseries Things that are good} %% fix this so it's not so casual
+{\color {red} 
+Talking to users, ``this will work in most situations,'' help button, support email.
+putting the bridge configuration before the proxy, etc.... \\
+}
+
+\noindent {\bfseries Things that could be improved}%% fix this so it's not so casual
+{\color {red} 
+clarify between bridges and proxy, getting rid of redundant text, etc.  \\
+}
 
@@
 \section{Design}
-
-\begin{figure}[t]
-\label{fig:bridges}
-  \centering
-    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
-    \caption{The Tor Bridges Configuration window of the Tor configuration
-    interface. Tor users in censored environments and some of our participants
-    will be required to select the correct bridge for circumventing censorship.
-    Note that the interface prompts users to choose a transport type, which can be
-    the source of confusion. Bridges are non-listed guard relays to the Tor
-    network; transports, supported by bridges, obfuscate traffic in
-    different ways.}
-\end{figure}
 

### 2015-10-09 paper/circumvention-experiment.tex
added more writing and screenshots of the configuration interface

@@
 \noindent {\bfseries Overview}
-The Tor Browser provides a configuration interface (Figure
-~\ref{fig:bridges}) to guide users through setting up their connection to the
+The Tor Browser provides a configuration interface to guide users through setting up 
+their connection to the
 Tor network. While people in most countries can connect to Tor using the
@@
 make use of additional settings, such as bridges, proxies, or both. 
-%definition of a bridge, defintion of a proxy here. 
+{\color {red} definition of a bridge, definition of a proxy}   %%%
 Our study  will explore how well this interface successfully guides users to 
@@
 \noindent {\bfseries Configuration Flow}
-{\color {red}
+There are five general paths a user can take through the Tor Browser connection
+configuration interface. {\color {red} These paths are shown in Figure ~\ref{fig:interface}}. 
+The configuration interface asks a series of questions to 
+the user to determine if the user requires a bridge or proxy when connecting to 
+the Tor network. Depending on how the user answers these questions, a user 
+has give paths through the configuration, as follows:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Path 1}:  Configure directly
-\item {\bfseries Path 2}:  Bridge, no proxy
-\item {\bfseries Path 3}:  Bridge, proxy 
-\item {\bfseries Path 4}:  No bridge, proxy
-\item {\bfseries Path 5}:  No bridge, no proxy
+\item {\bfseries Path 1}:  Connect directly
+\item {\bfseries Path 2}:  Yes bridge, no proxy, connect
+\item {\bfseries Path 3}:  Yes bridge, yes proxy, connect 
+\item {\bfseries Path 4}:  No bridge, yes proxy, connect 
+\item {\bfseries Path 5}:  No bridge, no proxy, connect 
 \end{itemize}
+
+\begin{figure*}[t]
+\label{fig:interface}
+  \centering
+    \includegraphics[width=\textwidth]{../torconfig.png}
+    \caption{This flow chart shows all of the possible paths taken through the
+    Tor configuration interface. A state represents a window in the interface,
+    with the exception of the leaves, which indicate the final action taken by
+    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
+    transitions between the states indicate which user action causes that
+    transition. The cause for error is can be found
+\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
+\end{figure*}
 
@@
 If a user is not connecting directly to the Tor network, then they are asked to 
-configure a bridge (as seen in TODO, the title of the window during configuration 
+configure a bridge (as seen in {\color {red} TODO}, the title of the window during configuration %%%
 is ``Tor Bridges Configuration''). We suspect that the reason for configuring a bridge
@@
 a bridge or has answered that they do not need a bridge, they are asked to 
-configure a local proxy (as seen in TODO, the title of the window during
+configure a local proxy (as seen in {\color {red} TODO}, the title of the window during %%%
 configuration is ``Local Proxy Configuration''). The proxy configuration asks the 
@@
 
-}
-
-\begin{figure*}[t]
-\label{fig:interface}
-  \centering
-    \includegraphics[width=\textwidth]{../torconfig.png}
-    \caption{This flow chart shows all of the possible paths taken through the
-    Tor configuration interface. A state represents a window in the interface,
-    with the exception of the leaves, which indicate the final action taken by
-    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
-    transitions between the states indicate which user action causes that
-    transition. The cause for error is can be found
-\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
-\end{figure*}
-
-\noindent {\bfseries Things that are good} %% fix this so it's not so casual
+\noindent {\bfseries Things that are good about the interface} %% fix this so it's not so casual
 {\color {red} 
@@
 
-\noindent {\bfseries Things that could be improved}%% fix this so it's not so casual
+\noindent {\bfseries Things that could be improved about the interface }%% fix this so it's not so casual
 {\color {red} 
@@
 \bibliography{circumvention-experiment.bib}
+
+\appendix
+\section*{A1: Configuration Interface Windows}
+
+\begin{figure}[h]
+\label{fig:window1}
+  \centering
+    \includegraphics[width=0.5\textwidth]{window1.png}
+    \caption{window1}
+\end{figure}
+
+\begin{figure}[h]
+\label{fig:window2}
+  \centering
+    \includegraphics[width=0.5\textwidth]{window2.png}
+    \caption{window2}
+\end{figure}
+
+\begin{figure}[h]
+\label{fig:window3}
+  \centering
+    \includegraphics[width=0.5\textwidth]{window3.png}
+    \caption{window3}
+\end{figure}
+
+\begin{figure}[h]
+\label{fig:window4}
+  \centering
+    \includegraphics[width=0.5\textwidth]{window4.png}
+    \caption{window4}
+\end{figure}
+
+\begin{figure}[h]
+\label{fig:window5}
+  \centering
+    \includegraphics[width=0.5\textwidth]{window5.png}
+    \caption{window5}
+\end{figure}
 \end{document}

### 2015-10-09 paper/circumvention-experiment.tex
added thorough captions to the configuration window figures

@@
     \includegraphics[width=0.5\textwidth]{window1.png}
-    \caption{window1}
+    \caption{Window 1: the first configuration window shown to the user upon
+    starting Tor Browser for the first time. Note that the interface's default choice
+    is to connect directly through Tor. The interface also gives additional guidance
+    to help users answer this question.}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{window2.png}
-    \caption{window2}
+    \caption{Window 2: This is the next window shown if a user chooses to configure 
+    bridges or proxies. Note that the interface's default answer is ``No,'' 
+    and also advises users to click ``No'' if they are unsure. The user can navigate to the 
+    previous window by clicking ``Go Back,'' and continue configuration by clicking 
+    ``Continue.''}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{window3.png}
-    \caption{window3}
+    \caption{Window 3: This is the window shown when a user answers that a bridge 
+    is required for the connection. Note that the default answer is to connect with a hard-
+    coded bridge rather than to enter in a custom bridge, and to use the recommended 
+    transport (obfs3). A possible source of confusion is that that the user is asked to choose 
+    a transport type, when the interface clearly is asking for bridge configuration. The user 
+    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
+    by clicking  ``Continue.''}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{window4.png}
-    \caption{window4}
+    \caption{Window 4: This is the window shown after a user has deemed that a bridge
+    is not required for the connection, or when the bridge configuration settings have been 
+    chosen. Note that the default answer to if the user requires a proxy is ``No.'' Additionally,
+    there is text to guide the users on how to answer this question. The user 
+    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
+    by clicking  ``Continue.''}
 \end{figure}
@@
     \includegraphics[width=0.5\textwidth]{window5.png}
-    \caption{window5}
+    \caption{Window 5: This is the window shown when a user answers that a proxy is 
+    required for the connection. Note that there are no default values in the answers, 
+    where there were for bridges. Additionally, since this is the last window in the configuration
+    interface, the options to navigate to other windows are to simply ``go back,'' or to 
+    connect to the Tor Network.}
 \end{figure}

### 2015-10-14 paper/circumvention-experiment.tex
added bit about methodology

@@
 
+\section{Methodology}
+
+We are going to aim for 5 users per censorship environment, improvement, 
+and alternate interface. We are going to pre-screen our participants so that 
+we have a good mix of gender, age, technical background, and familiarity 
+with Tor.
+
+Some references to keep in mind when explaining: 
+\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
+\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
+\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
+
 \section{Design}
@@
 The IRB protocol to run this user study has been approved (2014-12-6995). 
-We plan to recruit 100-200 users for the purpose of this study,
+We plan to recruit 35-50 users for the purpose of this study,
 making it the largest user study of Tor to date.  This study will be conducted at the

### 2015-12-08 paper/circumvention-experiment.tex
hacked away at results

@@
 
-\section{Design}
+\section{Methodology}
 
@@
 
-\section{What we hope to accomplish}
+\section{Results}
+
+Problems:
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Problem1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen. 
+\item {\bfseries Problem 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works. 
+\item {\bfseries Problem 3:} When their first attempt to connect fails, people tend to first try changing the proxy settings, because that is the window visible after a failure (an artifact of the fact that it is the last window visible before the failure).
+\item {\bfseries Problem 4:} When the first attempt to connect fails, people don't know what to do or what to try next. 
+\end{itemize}
+
+Proof of problems:
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Proof 1:} TODO
+\item {\bfseries Proof 2:} TODO
+\item {\bfseries Proof 3:} TODO
+\item {\bfseries Proof 4:} TODO
+\end{itemize}
+
+Source of Problems:
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Source 1: Users lack a mental model of how censorship works.} For instance, our participants did not know the difference between a bridge and a proxy or a censored website versus censored Tor relays.
+We suspect that this is the result of an accurate mental model of how the Internet works.
+It would be unreasonable to assume that users should know this information, but some of this may be required to make a correct decision in the current interface.
+\item {\bfseries Source 2: The interface flow does not guide users down the ideal path.} Much of the real estate on bridge configuration is used for the ``custom bridges'' option, which is an option rarely used.
+The interface instructs users to check out Internet settings to see if they would require a proxy, but it turns out that people are not skilled at doing so.
+Because the interface redirects users to the proxy screen after failing to make a connection, most of our participants tried configuring a proxy after a connection had failed due to an assumption that the proxy was the reason for the failure.
+In reality, there was no proxy setup required for any simulated censorship environment in our experiment and participants should have configured a bridge.
+\item {\bfseries Source 3: There is little constructive feedback during failure cases.} When a connection seems to not work, our participants were unsure of if they should wait more or if they should try the connection with the same configuration again, both of which are viable strategies, depending on the situation.
+Although there are certain error messages which were helpful, most of the error messages were technical and not understood by our participants (Figure \ref{fig:error}).
+The interface does not give clear directions on what participants should do next if a connection fails.
+\end{itemize}
+
+\begin{figure*}[t]
+\label{fig:error}
+  \centering
+    \includegraphics[width=\textwidth]{error.png}
+    \caption{An example of a technical error message which our participants did not understand.}
+\end{figure*}
+
+\section{Future Work}
 
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Test the Tor configuration interface} We will perform the largest user study 
-of Tor, measuring Tor configuration in three different adversarial settings. 
 \item {\bfseries Test an improved configuration interface} With the measurements collected
@@
 time taken, paths taken, and error states reached.
-\item {\bfseries Test an alternative configuration interface} A Tor developer has offered
-to design a mock-up interface for an alternative configuration interface which will
-greatly automate the process. There are tradeoffs between ease of use and transparency
-of the systems, and ethical considerations with loggable errors resulting from automated configuration. 
 \item {\bfseries Push changes} We have the support of Tor developers
@@
 \end{itemize}
+
+\section{Discussion}
 

### 2015-12-09 paper/circumvention-experiment.tex
Write configuration, method, and design sections

@@
 make use of additional settings, such as bridges, proxies, or both. 
-{\color {red} definition of a bridge, definition of a proxy}   %%%
-Our study  will explore how well this interface successfully guides users to 
+(Bridges are unlisted Tor relays, with pluggable transports to obfuscate traffic.
+Proxies help bypass local network restrictions and are typically only
+needed in restricted cases such as corporate environments.)
+Our study explores how successfully this interface guides users to
 correctly configuring their browser.\\
+
+\noindent {\bfseries Configuration Flow}
+
+\begin{figure*}[t]
+\label{fig:interface}
+  \centering
+    \includegraphics[width=\textwidth]{../torconfig.png}
+    \caption{This flow chart shows all of the possible paths taken through the
+    Tor configuration interface. A state represents a window in the interface,
+    with the exception of the leaves, which indicate the final action taken by
+    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
+    transitions between the states indicate which user action causes that
+    transition. Annotations for the error states can be found by following
+\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{this hyperlink}.}
+\end{figure*}
+
+As bridges and proxies can be configured independently or together, there are
+four main ways to set up a connection:
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item With a bridge and proxy
+    \item With a bridge but no proxy
+    \item Without a bridge but with a proxy
+    \item Without either a bridge or proxy
+\end{enumerate}
+
+The launcher interface asks a series of questions to
+determine which of these configuration states a user requires.
+The four high-level states correspond to five distinct paths through the
+configuration interface. (The latter option -- connecting with neither a bridge
+nor proxy -- contributes two separate paths.) Each path branches further
+depending on user-specific inputs. Figure \ref{fig:interface} illustrates the
+resulting paths.
+
+When the configuration window opens, a user is given the option to connect
+directly to the Tor network by clicking ``Connect'', or to click ``Configure''
+``if this computer's Internet connection is censored or proxied'' (Figure
+\ref{fig:window1}).
+
+If they choose the latter, the next screen asks, ``Does your Internet Service
+Provider (ISP) block or otherwise censor connection to the Tor network?''
+(Figure \ref{fig:window2}). Though this sounds repetitive, it is meant to
+identify and divert users who need only a proxy (and no bridge).
+This phrasing of the question carries the assumption that people will
+not know if they need a bridge or not, but that they are equipped to answer if their
+current network environment censors the Tor Network.
 
@@
 
-\noindent {\bfseries Configuration Flow}
-There are five general paths a user can take through the Tor Browser connection
-configuration interface. {\color {red} These paths are shown in Figure ~\ref{fig:interface}}. 
-The configuration interface asks a series of questions to 
-the user to determine if the user requires a bridge or proxy when connecting to 
-the Tor network. Depending on how the user answers these questions, a user 
-has give paths through the configuration, as follows:
+Next, users are asked to configure bridges by selecting a transport type from a
+dropdown menu or entering the IP address of a custom bridge in a textbox (Figure
+\ref{fig:bridges}).
+Finally, users are asked whether they need a local proxy (Figure
+\ref{fig:window4}) and (if they answered yes) to configure it (Figure
+\ref{fig:window5}).
 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Path 1}:  Connect directly
-\item {\bfseries Path 2}:  Yes bridge, no proxy, connect
-\item {\bfseries Path 3}:  Yes bridge, yes proxy, connect 
-\item {\bfseries Path 4}:  No bridge, yes proxy, connect 
-\item {\bfseries Path 5}:  No bridge, no proxy, connect 
-\end{itemize}
-
-\begin{figure*}[t]
-\label{fig:interface}
-  \centering
-    \includegraphics[width=\textwidth]{../torconfig.png}
-    \caption{This flow chart shows all of the possible paths taken through the
-    Tor configuration interface. A state represents a window in the interface,
-    with the exception of the leaves, which indicate the final action taken by
-    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
-    transitions between the states indicate which user action causes that
-    transition. The cause for error is can be found
-\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{here}.}
-\end{figure*}
-
-Upon the startup of the configuration interface, a user is asked to describe their 
-current situation. If their Internet connection is censored or proxied, the user 
-clicks ``Configure'' to configure bridge and proxy settings. Otherwise, the user
-clicks ``Connect'' to connect directly to the Tor network.
-
-If a user is not connecting directly to the Tor network, then they are asked to 
-configure a bridge (as seen in {\color {red} TODO}, the title of the window during configuration %%%
-is ``Tor Bridges Configuration''). We suspect that the reason for configuring a bridge
-first before a proxy is that more people need to configure bridges than proxies,
-but this is not known. The bridge configuration asks the users if their ISP blocks
-or censors connections to the Tor Network. The assumption here is that users will 
-not know if they need a bridge or not, but that they are equipped to answer if their
-current network environment censors the Tor Network. The configuration interface 
-uses this answer to deem if the user needs a bridge. A yes to this question would
-require a bridge while a no to this question would not. If they answer yes, they are 
-asked to configure the bridges. If they answer no, then the configuration interface 
-moves on to configuring proxies.
-
-If a user who is not directly connecting to the Tor network is finished configuring
-a bridge or has answered that they do not need a bridge, they are asked to 
-configure a local proxy (as seen in {\color {red} TODO}, the title of the window during %%%
-configuration is ``Local Proxy Configuration''). The proxy configuration asks the 
-users if they need to use a local proxy to access the Internet. The assumption 
-is that people will not know the answer to this question, so there is a text instructing
-users how to find the answer to this question below the question. If the answer to
-the question is yes, the user needs a proxy and is taken to a screen where they are
-asked to configure the proxy settings. If the user does not need a proxy, then the 
-configuration interface attempts to connect to the Tor network with all the 
-given inputs up to this point so far.
-
-Note that a user can decide to click ``Configure'' because they believe the 
-Internet connection is censored or proxied, but then answer the bridge and proxy
-questions in such a way that they deemed that they do not need a bridge or proxy 
-after all. In this case, clicking the ``Connect'' button after the above configuration steps
+Note that a user can decide to click ``Configure'' on the first screen, but then
+opt out of both bridges and proxies.
+In this case, connecting after these configuration steps
 would be equivalent to clicking ``Connect'' on the first screen. \\
 
-\noindent {\bfseries Things that are good about the interface} %% fix this so it's not so casual
-{\color {red} 
-Talking to users, ``this will work in most situations,'' help button, support email.
-putting the bridge configuration before the proxy, etc.... \\
-}
+\noindent {\bfseries Design choices}
+The launcher interface utilizes a number of techniques to aid users and simplify
+the choices they have to make. Help buttons and a support email address that
+appears on every screen are meant to assist users that get stuck in the process.
+The interface also makes good use of defaults, for example by emphasizing that
+certain options ``will work in most situations.''
 
-\noindent {\bfseries Things that could be improved about the interface }%% fix this so it's not so casual
-{\color {red} 
-clarify between bridges and proxy, getting rid of redundant text, etc.  \\
-}
+Still, there remains potential for confusion, especially with the more advanced
+configuration options. Bridges and proxies are not clearly defined, the
+interface doesn't specify when they would need to be used, and there is limited
+guidance for how to correctly choose specific values (e.g., which transport type
+to use or where to find proxy settings).
 
-\noindent {\bfseries Hypotheses} We expect that the average user will
+\section{Hypotheses}
+We expect that the average user will
 struggle to connect because they lack knowledge of the technical terms and
@@
 
-We are going to aim for 5 users per censorship environment, improvement, 
-and alternate interface. We are going to pre-screen our participants so that 
-we have a good mix of gender, age, technical background, and familiarity 
-with Tor.
+To test our hypotheses, we simulated several environments in which people may
+have to use Tor for censorship circumvention. We examined whether users are able
+to join the network and studied how they interact with the launcher interface.
+Based on our findings, we designed improvements to the Tor launcher interface,
+which we test in a large-scale study.
 
-Some references to keep in mind when explaining: 
-\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
-\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
-\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
+\subsection{Simulated censorship environments}
+We simulated three censorship environments.
+They are informed by our experience with pluggable transports
+and knowledge of commonly seen censorship techniques.
+They are not meant to perfectly replicate the network environment
+in any particular country. Although inspired by reality, these
+abstract simulations are intended to require distinct configurations
+of the Tor Browser from our participants.
 
-\section{Methodology}
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Mild censorship} 
+(Representative of countries such as France and Australia.)
+Certain domains are blocked. Reaching these 
+domains requires a censorship circumvention 
+tool. The default option to ``connect'' to the Tor network 
+directly will circumvent this censor. Additional correct
+bridge or proxy configurations are optional.
+
+\item {\bfseries Intermediate censorship} 
+(Representative of countries such as Tunsia.)
+Certain domains are blocked. Censorship circumvention
+tools such as Tor are blocked. Since all public Tor
+relay nodes are blocked, the default option to ``connect'' to the Tor network
+directly will fail. Any choice of a hard-coded bridge
+or a valid non-public bridge will circumvent this censor.  
+Additional correct proxy configuration is optional.
+
+\item {\bfseries Comprehensive censorship} 
+(Representative of countries such as China and Syria.)
+Certain domains are blocked. Censorship circumvention tools
+are thoroughly blocked. Tor is blocked by blocking all public
+Tor relay nodes, and the censor has examined source code to block
+all hard-coded bridge relays in the configuration interface. The default option
+to ``connect'' to the Tor network directly will fail. Most bridges will fail,
+but ``meek-amazon,'' ``meek-azure,'' and ``meek-google'' still work.
+% TODO: meek-google doesn't work either, right? Should we remove it?
+This is because domain-fronting requires censors to block entire CDNs to also
+block this transport (which will cause huge collateral blocking damage), making
+it resistant to aggressive censorship environments.
+(See ~\cite{fifield2015blocking} for additional details.)\\
+\end{itemize}
+
+\subsection{Qualitative interface evaluation}
+To identify problems with the existing interface, we conducted a series of
+qualitative evaluations with a set of users representative of the general
+population.
+
+Using established best practices from the field of user experience research
+(\cite{howmanyusers}), we recruited five users for each censorship environment.
+We pre-screened our participants to have a good mix of gender, age, technical
+background, and familiarity with Tor. \\
+
+%Some references to keep in mind when explaining:
+%\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
+%\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
+%\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
+
+\noindent {\bfseries Procedure}
+The experiment begins with the participants being informed that they are in a
+simulated censorship
+environment, where some --- but not all --- websites are blocked. We
+instruct them to visit a non-blocked website and a blocked website on a
+``standard'' browser (one that is not used for censorship circumvention, such
+as Chrome, Safari, or Firefox) to illustrate the situation.
+Participants are told that their
+role is that of a regular citizen who is trying to visit blocked websites
+for non-critical purposes,
+and for whom the chance of risk is minimal. This information is given
+to achieve
+consistency across participants: behaviors may change if the tasks are
+critical or if there were great risks associated with configuration mistakes.
+
+After explaining the situation and the user's role, we
+instruct them to complete a set of
+tasks which will require visiting blocked websites. Ultimately, the
+participants will need to configure their Tor Browser to circumvent the
+simulated censorship environment. These tasks have a three-fold purpose of
+providing participants with feedback (if they did not correctly configure their
+browser, they cannot reach the website), motivating the participants to
+configure the browser correctly, and providing the researchers with an
+indicator of successful censorship circumvention.
+Participants' screens are recorded to capture how they configure
+their browser.
+
+After users complete the browsing tasks (or time runs out), we conduct an
+interview, collecting qualitative feedback from
+participants about their browsing experience as a whole
+and the configuration interface specifically.
+We ask questions such as
+``What was the most challenging part of connecting?''
+and
+``What is one change you would recommend?''
+
+\subsection{Interface design and iteration}
+After completing the qualitative user studies, we analyzed their results to
+identify common themes and problems. Based on these, we then designed
+improvements to the Tor launcher interface.
+
+To do this, we used an iterative design process, starting with low-fidelity
+(paper and pencil) prototypes and then proceeding to higher-fidelity versions.
+At each stage, the prototype was clickable, allowing for more realistic
+simulation.
+
+We collected feedback from researchers, professors, and Tor users and developers
+through the Tor project's mailing lists. We then iterated on the design by
+incorporating the comments and suggestions we received into the next version of
+the interface.
+
+\subsection{Quantitative evaluation of improvements}
+Once the new design of the user interface is finalized, we will conduct a
+large-scale quantitative evaluation, to test whether the improvements had a
+measurable effect on people's ability to connect to the Tor network.
+
+The experimental procedure will be nearly identical to the procedure for the
+qualitative portion of the study, described above. However, rather than
+conducting open-ended interviews at the end of the tasks, participants will be
+asked to fill out a brief survey. Furthermore, the interface will be
+instrumented to collect metrics and statistics for use in analysis and
+hypothesis testing.
+Some examples of metrics collected include the time spent on each screen, which
+paths the user followed, which interface elements they interacted with, and how
+often they did so. These will be analyzed in conjunction with high-level metrics
+(was the user able to connect to Tor successfully?).
+
+Participants will be split across several different experimental conditions.
+Some will be testing the improved user interface, while those in the control
+group will be completing the same tasks using the old, unimproved interface. \\
+% NOTE: removed mention of the alternate interface, unless there's something to say about it
 
 \noindent {\bfseries Experiment Logistics} 
-The IRB protocol to run this user study has been approved (2014-12-6995). 
 We plan to recruit 35-50 users for the purpose of this study,
@@
 Participants will be compensated \$30 for their time, which covers
-minimum wage for an hour and any transportation costs to the lab.  \\
-
-\noindent {\bfseries Experiment Flow} 
-We will conduct three separate experiments as part of this study:
-the first set to test the current configuration
-interface, a second set to test the improved interface, and a third set to test the 
-alternate configuration interface. The experiment flow will be the same across all 
-sets of experiments, but the configuration interface will be different across sets.
-
-The experiment begins with the participants being informed that they are in a
-simulated censorship
-environment, where some --- but not all --- websites are blocked. We will
-instruct them to visit a non-blocked website and a blocked website on a
-``standard'' browser (one that is not used for censorship circumvention, such
-as Chrome, Safari, or Firefox) to illustrate the situation.
-Then, the participants will find out the role they they will be playing in the study.
-This role is that of a regular citizen who is trying to visit blocked websites
-for non-critical leisurely purposes,
-and for whom the chance of risk is minimal. This information is given
-to achieve
-consistency across participants: behaviors may change if the tasks were 
-critical or if there were great risks associated with configuration mistakes.
-
-After explaining the situation and their role, we will explain what Tor is, and
-how they can use it if necessary, and instruct them to complete a set of
-tasks which will require visiting blocked websites. Ultimately, the
-participants will need to configure their Tor Browser to circumvent the
-simulated censorship environment. These tasks have a three-fold purpose of
-providing participants with feedback (if they did not correctly configure their
-browser, they cannot reach the website),  motivating the participants to
-configure the browser correctly, and providing the researchers with an
-indicator of successful censorship circumvention.
-Participants' screens will be recorded to capture how they configure
-their browser, and to provide additional evidence that they have completed the
-tasks.
-
-After users complete the browsing tasks, we will administer a survey that 1)
-measures demographics, technical fluency, and
-familiarity with Tor and 2) collects qualitative feedback from
-participants about their browsing experience as a whole
-and the configuration interface specifically.
-A rough draft of the survey can be
-found
-\href{http://www.surveygizmo.com/collab/2085559/Tor-Usability-Survey}{here}.
-
-The experiment will conclude with a debriefing, which will inform that the
-participants of their screen capture and obtaining re-consent for the
-information. \\
-
-\noindent {\bfseries Censorship Environment Simulation} 
-We plan to simulate three censorship environments.
-They are informed by our experience with pluggable transports
-and knowledge of commonly seen censorship techniques.
-They are not meant to perfectly replicate the network environment
-in any particular country. Although inspired by reality, these
-abstract simulations are intended to require distinct configurations
-of the Tor Browser from our participants. \\
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Mild censorship} 
-(Reflective of countries such as France and Australia.)
-Certain domains are blocked. Reaching these 
-domains requires a censorship circumvention 
-tool. The default option to ``connect'' to the Tor network 
-directly will circumvent this censor. Additional correct
-bridge or proxy configurations are optional. 
-\item {\bfseries Intermediate censorship} 
-(Reflective of countries such as Tunsia.)
-Certain domains are blocked. Censorship circumvention
-tools are blocked. Since Tor is blocked by blocking all public Tor
-relay nodes, the default option to ``connect'' to the Tor network
-directly will fail. Any choice of a hard-coded bridge (see Figure ~\ref{fig:bridges})
-or a valid non-public bridge will circumvent this censor.  
-Additional correct proxy configuration is optional.
-\item {\bfseries Comprehensive censorship} 
-(Reflective of countries such as China and Syria.)
-Certain domains are blocked. Censorship circumvention tools
-are thoroughly blocked. Tor is blocked by blocking all public
-Tor relay nodes, and the censor has examined source code to block
-all hard-coded bridge relays in the configuration interface. The default option
-to ``connect'' to the Tor network directly will fail. Choosing any bridges other than
-``meek-amazon,'' ``meek-azure,'' and ``meek-google,'' will fail. This is because 
-domain-fronting requires censors to block entire CDNs to also block this
-transport (which will cause huge collateral blocking damage), making it resistant to agressive censorship environments.
-(See ~\cite{fifield2015blocking} for additional details.)\\
-\end{itemize}
-
-\noindent {\bfseries List of Tasks} 
-In our experimental setup, successful completion of 
-these given tasks requires of correct configuration.
-The difficulty of circumventing  censorship to visit the 
-websites required for the tasks will vary depending on the 
-simulated censorship environment. Since all participants will be given the 
-same set of tasks, regardless of the censorship environment, 
-the difficulty of completing the tasks remains constant assuming
-correct configuration. The tasks themselves are not intended to
-be challenging.
-
-The tasks were inspired by the top Alexa sites,
-an indication of representative and relevant browsing behavior. 
-From these, we selected sites which were commonly censored, 
-but filtered tasks that would require a participant to reveal private information 
-(such as login information) for ethical considerations. These tasks
-were further refined after performing a pilot study of the experiment. 
-We hope the tasks convey an example of how of a user might 
-browse the Internet in a censored environment.
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item Google search for the population of Zimbabwe. 
-\item On YouTube, find a video playing Bach's ``Ode to Joy.''
-\item Find the Amazon best-sellers in ``Movies \& TV.''
-\item On Yahoo, find the exchange rate of dollars to euros.
-\item Find the Wikipedia ``History'' portal's featured article. 
-\item On Twitter, find the currently trending topics.
-\item On Bing Maps, find directions from Times Square to Carnegie Hall.\\
-\end{itemize}
-
-\noindent {\bfseries Improved and Alternative Interfaces} We have yet to design the 
-improvements to the interface, as they will be based on the data collected from 
-the user studies on the current configuration interface. In general, we will measure the 
-time it took to configure correctly, and help users avoid common mistakes. An alternate 
-interface to automate the configuration process for the user has been proposed in the 
-community. One concern about it is that the automation makes the connection process less transparent, 
-and since there are countries who log Internet activity, automated attempts to obviously
-use the Tor network could have the potential to be incriminating.\\
-
-\noindent {\bfseries Exit Survey}
-{\color {red} talk about the survey here.}
+minimum wage for an hour and any transportation costs to the lab. 
+The IRB protocol to run this user study has been approved (2014-12-6995).
 
@@
 \end{figure*}
+
+\section{Design}
+Based on the feedback we received and the insights we gathered from our
+participants, we designed improvements to the launcher interface. This section
+discusses our results and the design considerations we employed. \\
+
+\noindent {\bfseries Automation}
+One common piece of feedback, from experts and novices alike, was that the
+connection process could be simplified with automation. At first glance, many
+decisions currently made by the user could be automated. For example, bridge
+selection needs to happen only if a regular connection failed, and bridges could
+be tried automatically until one succeeds. However, there are security
+considerations that make this solution problematic. If the launcher starts by
+trying to make unobscured connections to publicly listed relays, detection is
+trivial in a country that logs Internet traffic, potentially resulting in
+repercussions for citizens. Furthermore, some users may be turned off by the
+lack of transparency in the connection process.
+
+However, other elements of the process can be automated without adverse effects.
+For example, local proxy settings can be imported from other browsers on the
+machine by looking for settings in well-known locations on the filesystem. The
+same can be done to answer the question that led many of our participants
+astray: is a local proxy even needed? Since this piece of automation offers a
+significant potential upside, with no apparent risks, we have incorporated it
+into our design. \\
+
+\noindent {\bfseries Building a better mental model}
+Participants' lack of a mental model of censorship led them to believe their
+connection was censored when, in reality, it was not. It furthermore contributed
+to their confusion between bridges and proxies. Our design directly addresses
+these issues.
+
+Potentially ambiguous text (i.e., referring to censorship) is removed in favor
+of stating the underlying options. Separate screens with binary options (Do you
+need a proxy? Yes/No) are removed; instead the option to opt out is incorporated
+on the configuration screen. This results in a more streamlined interface (fewer
+clicks required) and unified the context of each option: all information about
+bridges (or proxies) is now contained on one screen, so the user has the full
+context of their decision. \\
+
+\noindent {\bfseries Clarifying paths through the interface}
+Many users struggled because the workflow implicitly suggested by the interface
+didn't match the ideal path: crucial steps to follow were unclear or obscured,
+while undue prominence was given to comparatively less important elements.
+Our new design inverts this trend, focusing attention on the interface elements
+that are more important, or more generally applicable.
+
+A clear example of this is the ``Connect'' button on the first screen, which has
+increased in size and become green, making it more prominent as the recommended
+option. A similar aesthetic applies to the connect button seen after custom
+configuration.
+
+Rarely used elements are deemphasized. For example, the custom bridges box,
+which previously took up a significant portion of the bridge configuration
+screen, is now hidden until that option is selected.
+
+A progress indicator at the top of the window indicates which configuration step
+the user is on. It serves to clarify the independence of bridges and proxies,
+which need to be configured separately. In the event of a failure, the user is
+returned to the first step of the process -- the bridge configuration -- to
+avoid misleading users into thinking the proxy settings are the culprit. \\
+
+\noindent {\bfseries Designing for failure cases}
+
+Many users were led astray by interface elements that were unhelpful or
+misleading if the program encountered connection problems. Our design seeks to
+prevent such confusion by gracefully handling failures.
+
+The progress bar in the connection window drew many complaints, because it got
+stuck and didn't offer any guidance for how long users were supposed to wait. We
+address this by providing a countdown timer, indicating how long users should
+expect to wait. We further enhance the progress bar by adding visual indicators
+for major milestones in the connection, providing better feedback about what has
+been accomplished so far. Additionally, the current status of the connection
+attempt (drawn from the log) is displayed, to aid in understanding and
+debugging.
+
+In the event that the connection attempt fails, messages from the log are
+displayed, along with tips and suggestions about what to do next (e.g., try
+another bridge). To make potential the options clearer, the new failure screen
+includes a separate button for retrying without changing settings and another
+for returning to reconfigure the application. \\
+
+\noindent {\bfseries Additional changes}
+In addition to the changes above, we have simplified flows where possible,
+provided clearer definitions of bridges and proxies, and reduced visual clutter.
+{\color {red} Anything else?}
 

### 2015-12-10 paper/circumvention-experiment.tex
save anything
results done

@@
 We pre-screened our participants to have a good mix of gender, age, technical
-background, and familiarity with Tor. \\
+background, and familiarity with Tor in each environment, and also overall. \\
 
@@
 \noindent {\bfseries Experiment Logistics} 
-We plan to recruit 35-50 users for the purpose of this study,
+We plan to recruit up to 100 users for the purpose of this study,
 making it the largest user study of Tor to date.  This study will be conducted at the
@@
 
-Problems:
+The qualitative interface evaluation yielded in hours of observation for a set of 16 pre-selected, diverse participants taking various UI paths in different simulated censorship environments.
+We then interviewed the participants, getting hundreds of words of feedback from our participants.
+In this section, we will be talking about the insights gathered from the qualitative interface evaluation, which has shaped the re-design of the interface.
+All of the results are grounded in participants' experiences and feedback, which are available publicly online.
+The video screen captures from the experiment can be found \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{here}; a summary of each video can be found \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{here}.
+The corresponding notes from the after-experiment interview can be found \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{here}.
+
+We have evaluated at least one Tor user, one participant who has heard of Tor before the study, and three people who had never heard of Tor before in each simulated censorship environment.
+The nature of small-scale qualitative studies yields in rich information about each participant, but making generalizations from these results such as ``Tor users were able to configure quicker'' would be unsound.
+Our observations from our particular three participants were that they were more capable of debugging after failure modes and were more methodological about doing so, but they faced similar difficulties as the other participants.
+
+We noticed four common challenges that our participants have had with the interface:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Problem1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen. 
-\item {\bfseries Problem 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works. 
-\item {\bfseries Problem 3:} When their first attempt to connect fails, people tend to first try changing the proxy settings, because that is the window visible after a failure (an artifact of the fact that it is the last window visible before the failure).
-\item {\bfseries Problem 4:} When the first attempt to connect fails, people don't know what to do or what to try next. 
+\item {\bfseries Challenge1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
+As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
+\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
+Participants knew that they were censored to some degree since we had simulated censorship of websites.
+However, bridges are only necessary when the government has taken active steps to censor Tor itself.
+\item {\bfseries Challenge 3:} When their first attempt to connect fails, people tend to first try changing the proxy settings, because the interface directs people to the last window participants saw before the connection failure.
+This was problematic since the problem is not necessarily where the interface directs users.
+For instance, it was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
+\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
+The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
 \end{itemize}
 
-Proof of problems:
+\begin{figure}[t]
+\label{fig:error}
+  \centering
+    \includegraphics[width=0.5\textwidth]{error.png}
+    \caption{An example of a technical error message which our participants did not understand.}
+\end{figure}
+
+These common four problems were illustrated by our participants concretely:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Proof 1:} TODO
-\item {\bfseries Proof 2:} TODO
-\item {\bfseries Proof 3:} TODO
-\item {\bfseries Proof 4:} TODO
+\item {\bfseries Proof of Challenge 1:} Of the five participants who could click directly to the network, three participants (P3,P4,P10) did not choose to connect directly.
+Of the eleven participants who needed to configure their connection, eight (P1, P5, P6, P7, P8, P11, P13, P14, P16) chose to connect directly.
+One participant (P12) clicks configure, but answers the questions in such a way that it creates a direct connection.
+Only one (P15) was chose to configure when they needed to.
+\item {\bfseries Proof of Challenge 2:} Five participants were placed in a censored environment which did not block Tor.
+Three of the five (P3, P4, P10) configured a bridge for their connection.
+Of the other two, one participant (P2) was convinced that configuring a bridge was the correct course of action, but was intimidated at the thought of doing so and was pleasantly surprised when a direct connection succeeded; only one participant (P9) believed that a direct connection would work.
+\item {\bfseries Proof of Challenge 3:} All three of our participants (P14, P15, P16) who never were able to circumvent the simulated censorship environment spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network.
+Out of the five participants who needed to fix their bridge settings, there were only two participants (P5, P6) who eventually were able to figure out that their bridge settings needed to be adjusted.
+\item {\bfseries Proof of Challenge 4:} One participant (P14) tried the same configuration seven times, even though those settings failed each time.
+Another participant (P12) tries the same configuration three times, and only manages to connect through a technical artifact of the experiment even though that should not have worked.
+Both of these participants emphasized that they did not know what they should be doing.
+Other participants' interview responses also indicate a lack of feedback after failure cases (P8, P15, P16).
 \end{itemize}
 
-Source of Problems:
+The above challenges stemmed from these observations:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Source 1: Users lack a mental model of how censorship works.} For instance, our participants did not know the difference between a bridge and a proxy or a censored website versus censored Tor relays.
+\item {\bfseries Observation 1: Users lack a mental model of how censorship works.} For instance, our participants did not know the difference between a bridge and a proxy or a censored website versus censored Tor relays.
 We suspect that this is the result of an accurate mental model of how the Internet works.
 It would be unreasonable to assume that users should know this information, but some of this may be required to make a correct decision in the current interface.
-\item {\bfseries Source 2: The interface flow does not guide users down the ideal path.} Much of the real estate on bridge configuration is used for the ``custom bridges'' option, which is an option rarely used.
+\item {\bfseries Observation 2: The interface flow does not guide users down the ideal path.} Much of the real estate on bridge configuration is used for the ``custom bridges'' option, which is an option rarely used.
 The interface instructs users to check out Internet settings to see if they would require a proxy, but it turns out that people are not skilled at doing so.
@@
 In reality, there was no proxy setup required for any simulated censorship environment in our experiment and participants should have configured a bridge.
-\item {\bfseries Source 3: There is little constructive feedback during failure cases.} When a connection seems to not work, our participants were unsure of if they should wait more or if they should try the connection with the same configuration again, both of which are viable strategies, depending on the situation.
+\item {\bfseries Observation 3: There is little constructive feedback during failure cases.} When a connection seems to not work, our participants were unsure of if they should wait more or if they should try the connection with the same configuration again, both of which are viable strategies, depending on the situation.
 Although there are certain error messages which were helpful, most of the error messages were technical and not understood by our participants (Figure \ref{fig:error}).
@@
 
-\begin{figure*}[t]
-\label{fig:error}
-  \centering
-    \includegraphics[width=\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
-\end{figure*}
+Although we cannot comment on if the challenges mentioned above will be exactly representative of the Tor user population, it is fair to claim that these challenges are challenges that some Tor users will encounter while configuring Tor.
+Our observations are grounded in user interaction--specifically user mental modes, UI flow, and failure design--giving us high confidence that addressing these observations will make a noticeable impact on the usability of the Tor configuration dialog for censorship circumvention.
 
 \section{Design}
-Based on the feedback we received and the insights we gathered from our
-participants, we designed improvements to the launcher interface. This section
-discusses our results and the design considerations we employed. \\
+Based on the feedback and the insights from our qualitative interface evaluation,
+ we designed improvements to the launcher interface. This section
+discusses design considerations we employed and corresponding justifications. \\
 

### 2015-12-10 paper/circumvention-experiment.tex
edit design

@@
 \noindent {\bfseries Automation}
-One common piece of feedback, from experts and novices alike, was that the
+One common piece of feedback from experts and novices alike was that the
 connection process could be simplified with automation. At first glance, many
@@
 trivial in a country that logs Internet traffic, potentially resulting in
-repercussions for citizens. Furthermore, some users may be turned off by the
+repercussions for citizens. Furthermore, users may be turned off by the
 lack of transparency in the connection process.
@@
 For example, local proxy settings can be imported from other browsers on the
-machine by looking for settings in well-known locations on the filesystem. The
-same can be done to answer the question that led many of our participants
-astray: is a local proxy even needed? Since this piece of automation offers a
-significant potential upside, with no apparent risks, we have incorporated it
+machine by looking for settings in well-known locations on the filesystem. Automatically
+detecting the need for a proxy and importing the proxy settings required would save
+our participants from a task they do not have the background to easily complete. 
+Since this piece of automation offers a significant increase in usability for our users
+(addressing our most common failure case) with no apparent risks, we have incorporated it
 into our design. \\
@@
 Participants' lack of a mental model of censorship led them to believe their
-connection was censored when, in reality, it was not. It furthermore contributed
+Tor connection was censored when, in reality, it was not. It furthermore contributed
 to their confusion between bridges and proxies. Our design directly addresses
@@
 Potentially ambiguous text (i.e., referring to censorship) is removed in favor
-of stating the underlying options. Separate screens with binary options (Do you
-need a proxy? Yes/No) are removed; instead the option to opt out is incorporated
-on the configuration screen. This results in a more streamlined interface (fewer
-clicks required) and unified the context of each option: all information about
-bridges (or proxies) is now contained on one screen, so the user has the full
-context of their decision. \\
+of stating the underlying options, as it was shown to confuse our participants.
+Previously, separate screens with binary options (Do you need a proxy? Yes/No) 
+were provided to help users decide if they needed a bridge or proxy, and skipping
+the configuration windows for bridges and proxies, respectively, when users
+answered that they didn't need one. We have removed these screens
+because our participants did not understand how to answer them correctly. This is 
+anticipated in the old interface, in fact: written text in the interface guides users on to 
+how to answer those questions.
+
+We chose to display all information about bridges and proxies is now contained on one 
+respective screen in the interface, giving the user has the full context of their decision.
+We made the guidance from the last interface (to not choose a bridge, to not choose a proxy)
+more direct by selecting the  option to opt out of a proxy as the default option on those screens. 
+This results in a more streamlined interface with fewer windows
+and fewer clicks required for our participants. \\
 
@@
 increased in size and become green, making it more prominent as the recommended
-option. A similar aesthetic applies to the connect button seen after custom
+option. We believe that this will help the majority of Tor users. 
+Although some of our participants in environments had chosen to connect
+directly when they needed to configure, this is generally seen as low-risk today, and 
+the majority of censorship today can be circumvented with a direct connection. 
+A similar aesthetic applies to the connect button seen after custom
 configuration.
 
-Rarely used elements are deemphasized. For example, the custom bridges box,
-which previously took up a significant portion of the bridge configuration
-screen, is now hidden until that option is selected.
+To help lessen the cognitive load and distribute a representative amount of space
+for options, recommendations are selected as the default option, and rarely used 
+elements are deemphasized. To encourage our users to click on helpful options, 
+the help button on the bridge configuration screen
+has been emphasized to be bigger, since it is a helpful option which people rarely
+clicked. To discourage our users from using an advanced setting only technical users 
+have a chance of  configuring correctly and should only be used in very rare circumstances, 
+we have now incorporated the custom bridge configuration in the dropdown menu; 
+it previously took up a significant portion of the bridge configuration screen.
 
@@
 returned to the first step of the process -- the bridge configuration -- to
-avoid misleading users into thinking the proxy settings are the culprit. \\
+avoid misleading users into thinking the proxy settings are the culprit. Previously,
+the user had to manually click to go backward in the dialog to configure bridges.
+Even in the rare event that the proxy is the issue for the connection setting, the user
+will be directed to the proxy page naturally through the flow of the UI, without
+having the user to defy the natural flow of configuration. \\
 
@@
 misleading if the program encountered connection problems. Our design seeks to
-prevent such confusion by gracefully handling failures.
+prevent such confusion by anticipating failures and providing specific instructions
+for our participants on their next steps.
 
 The progress bar in the connection window drew many complaints, because it got
-stuck and didn't offer any guidance for how long users were supposed to wait. We
-address this by providing a countdown timer, indicating how long users should
-expect to wait. We further enhance the progress bar by adding visual indicators
+stuck and didn't offer any guidance for how long users were supposed to wait. 
+The connection process can take a non-trivial couple of minutes, and users may
+think that the connection isn't working, even when it is making slow progress. We
+address this by providing a countdown timer, indicating that a long wait time does
+not indicate failure. We further encourage waiting by adding visual indicators
 for major milestones in the connection, providing better feedback about what has
@@
 another bridge). To make potential the options clearer, the new failure screen
-includes a separate button for retrying without changing settings and another
-for returning to reconfigure the application. \\
+includes a separate button for common next steps which are able to resolve
+a failed connection, which are to retry without changing settings and to reconfigure 
+the connection. \\
 
@@
 provided clearer definitions of bridges and proxies, and reduced visual clutter.
-{\color {red} Anything else?}
+We believe that all of these changes are cohesive with the other design changes
+made to the interface and will be beneficial for the user.
 

### 2015-12-10 paper/circumvention-experiment.tex
delete phantom discussion section
finished linking resources

@@
 
-\section{Discussion}
-
 \section{Resources}
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, and paper}
-\item \href {https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/1-strict.mp4}{pilot video 1}
-	\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/pilot/2-lax.mp4}{pilot video 2}
+\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
+\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
+\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
+\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
 \item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 

### 2015-12-10 paper/circumvention-experiment.tex
intro fix

@@
 
-\section{Tor}
-\noindent {\bfseries Usability}
+\section{Introduction}
 Tor is primarily known as the most widely used anonymity tool today. 
@@
 This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
-5.1 and later. \\
+5.1 and later. There has been no work done on Tor as a censorship circumvention tool.
 
-\noindent {\bfseries Scoping}
 There are still many features of Tor that are left unevaluated through user
@@
 updates, and identity/cookie management. Rather than selecting the features to
-study in isolation,
-we decided to focus on an important use case of Tor browser: censorship circumvention. 
-Internet censorship is pervasive across the world today \cite{faris2008measuring}, with 
-some countries blocking censorship circumvention tools as well \cite{winter2012great}. 
+study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
+Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
+Although Tor was not designed to be a censorship circumvention tool, users started
+to use Tor as a censorship circumvention tool since Tor's role as a proxy to anonymize
+people also worked to circumvent censorship. Now, circumventing censorship is a
+common use case for Tor, and Tor current censorship circumvention methods are
+incorporated into Tor, making it a viable censorship circumvention tool even in the face
+of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
 To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool.\\
+censorship circumvention tool.
 
-\noindent {\bfseries Motivation}
-Changing the configuration interface would not require changes to the 
-Tor Browser functionality, making any suggested improvements very practical to 
-deploy in a short period of time. {\color {red} Additionally, people are just literally
-being censored everywhere so a lot of people are using it for this purpose. So 
-we want this to be usable for that purpose.}
+We believe that this is a great opportunity for user research. Censorship circumvention
+is not only a common use case, but one Tor was not intended for. Since Tor does not 
+track their users in any way or performs A/B testing, making a user study a more
+uniquely beneficial source of feedback. Since the interface does not depend on the 
+internal functionalities of Tor, changes made to the configuration interface would not 
+require huge changes, making any suggested improvements very practical to 
+deploy.
 

### 2015-12-10 paper/circumvention-experiment.tex
add link to clickable prototype
hypotheses section

@@
 Tor network. While people in most countries can connect to Tor using the
-dialog's default settings, citizens in certain censorship environments must
+dialog's default settings, users in certain censorship environments must
 make use of additional settings, such as bridges, proxies, or both. 
-(Bridges are unlisted Tor relays, with pluggable transports to obfuscate traffic.
+Our study explores how successfully this interface guides users to
+correctly configuring their browser.
+
+For context, we will give the definition of bridges, pluggable transports, and proxies. 
+Keep in mind that this is the kind of information that a user might need to know to be able
+to configure correctly. Note that bridges, pluggable transports, and proxies are technical 
+concepts which may be unfamiliar to the average users, and that bridges and pluggable 
+transports are completely Tor-specific concepts.
+
+Bridges are unlisted Tor relays that make it possible for a user to connect
+to the Tor network even if a censor blocks all publicly listed Tor relays. There used 
+to be plain relays which were exactly similar to public relays, but were unlisted. However, 
+censorship in countries which blocked Tor generally were motivated enough to agressively
+block Tor in other ways, such as traffic analysis. For this reason, a bridge usually associated 
+with a pluggable transport that circumvents deep packet inspection, transports can 
+assist by obfuscating traffic or reflecting traffic through a content distribution network. 
 Proxies help bypass local network restrictions and are typically only
-needed in restricted cases such as corporate environments.)
-Our study explores how successfully this interface guides users to
-correctly configuring their browser.\\
+needed in restricted cases, such as corporate environments.\\
 
@@
 Still, there remains potential for confusion, especially with the more advanced
-configuration options. Bridges and proxies are not clearly defined, the
-interface doesn't specify when they would need to be used, and there is limited
-guidance for how to correctly choose specific values (e.g., which transport type
-to use or where to find proxy settings).
+configuration options. Although arguably for the reason that users may not 
+understand or read, bridges, pluggable transports, and  proxies are never defined 
+for the user. This can lead to users confusing these terms, or not understanding
+the relations between these terms. Additionally, there is limited explanation of 
+what pluggable transport types to choose from if the default one fails or how to 
+find proxy settings, which will be required of some users.
 
 \section{Hypotheses}
-We expect that the average user will
-struggle to connect because they lack knowledge of the technical terms and
-mechanisms required for circumvention (such as pluggable transports) and cannot
-obtain information not explicitly provided by the user interface (e.g., IP
-addresses of non-publicly listed bridges).
+We expected that the average user will struggle to connect because they do not understand censorship circumvention or the  censorship circumvention technologies offered by Tor.
+We also predict that a user will not get the feedback they need to revise their connection configuration if they fail.
+Specifically:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item  {\bfseries H1}: people don't know what a bridge or proxy is. > ask participants to define these terms in the survey.  
-\item  {\bfseries H2}: people don't know what the difference between a bridge and a proxy is > ask if people can distinguish them. 
-\item  {\bfseries H3}: people do not know when bridges or proxies are necessary > ask them this in the survey.  
-\item  {\bfseries H4}: proxies cause confusion when configuring bridges. screen recording: see if people click on proxies (none of the environments require a proxy)
-\item  {\bfseries H5}: people will favor familiar-sounding transports (i.e.
-meek-google versus meek-azure or scramblesuit) > see screen recordings, ask in survey for which transports were picked in which order and why they chose the final transport.
-\item {\bfseries H6}: (some dialogue is redundant.
-see opening window: "before you connect..." and bridge2 window: "you may use...") > we can try asking if people find these things useful, if they would prefer the interface without it, or if they read it.
+\item  {\bfseries Hypothesis 1}: users will generally not know when they need a bridge or proxy is, leading to issues such as choosing to configure a bridge or proxy when it is not necessary, or configuring bridges or proxies incorrectly.
+\item  {\bfseries Hypothesis 2}: people will not know when they need to configure or connect, since they do not understand how censorship works.   
+\item  {\bfseries Hypothesis 3}: proxies will cause confusion when configuring bridges. 
 \end{itemize}
+
+We find these hypotheses to be true for our participants, although sometimes not for the reasons we expected.
+For instance, we believed that proxies will cause confusion when configuring bridges because participants would confuse one as the other; however, the interface redirected users to proxy configuration settings if a participant has chosen to configure a proxy, even if the source of failure was not from the proxy.
+Details of the experiment that has verified our hypotheses is below.
 
@@
 \item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
+\item \href {a clickable prototype of our interface redesign}{https://marvelapp.com/15a2294}
 \item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}

### 2015-12-10 paper/circumvention-experiment.tex
future work

@@
 
-\section{Results}
+\section{Initial Results}
 
@@
 
-We plan to finish the user study by the end of the semester. 
-From this experiment, we hope to accomplish the following:
+The work summarized in the paper is only a part of the process of improving the Tor configuration
+dialog for more usable censorship circumvention. We plan to continue this work by:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Test an improved configuration interface} With the measurements collected
-from testing the interface as-is, we will design and test improvements to minimize
-time taken, paths taken, and error states reached.
-\item {\bfseries Push changes} We have the support of Tor developers
-to improve this interface. Additionally, since the configuration interface does not require 
-any changes to the Tor Browser functionality, improvements to the interface will
-be easy to deploy. 
+\item {\bfseries Testing our design with a small-scale qualitative study.} It is critical to get in-depth data user train of thought as they user the interface, one-on-one interviews, and open-ended feedback.
+For this reason, we plan to run a small-scale qualitative study similar to the one we have run for the old interface.
+We plan to run these studies at the start of Spring 2015.
+\item {\bfseries Testing our design with a large-scale quantitative study.} To test our design alongside the old interface, we will recruit a large number of participants to try out both designs.
+The purpose of this is to get statistically significant results on whether our design choices have helped or not helped a user to configure successfully.
+We plan to run these studies at the start of Spring 2015.
+\item {\bfseries Analyzing which design changes have made a positive impact.} We plan to instrument our interfaces to capture all clicks, window transitions, and other events so that we can analyze if our designs have helped our users connect faster and or with less effort.
+\item {\bfseries Push some changes.} We have the input and support of Tor developers
+to improve this interface. Any improvements will be incorporated into the Tor Browser.
 \end{itemize}
+
+\noindent {\bfseries Quantitative experiment analyses} We want to show a statistically significant improvement in user effort for a successful connection.
+We have deemed this can be measured with various factors such as time, clicks, etc.
+For this reason, we will specifically be collecting data about: the total number of participants who have successfully circumvented censorship, the number of connection attempts for a successful connection, how much time participants spent configuring before a successful connection, the number of windows traversed in the UI, the number of clicks made, if bridge and proxy configuration interfered with each other, and how many people try repeat configuration settings.
+
+One exciting analysis we will perform is to build a Markov model of the UI flow chart (like the one seen in Figure \ref{fig:interface}).
+We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6).
+We have other visualizations in mind, such as displaying the number of windows traversed by each participant as a bar graph.\\
+
+\noindent {\bfseries Deciding which design choices to incorporate} We have discussed how we will decide if a design change is beneficial enough to incorporate.
+Intuitively, changes which lead to higher success rates, faster time to completion, less clicking, less window traversal, and positive changes in behavior will be incorporated.
+If they have the converse of these effects, those changes will not be incorporated.
+However, when changes do result in a statistically significant improvement or challenge, we have chosen to incorporate changes if they provide cohesion with other changes which do have positive effects.
+If changes seem to be uncorrelated to positive effects and do not show statistical significance, we will not incorporate those changes.
+\\
+
+\noindent {\bfseries Looking Forward} We will help incorporate changes into the Tor browser.
+Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make.
+We hope that our work is able to help people more easily access the free Internet.
 

### 2015-12-10 paper/circumvention-experiment.tex
added a figure on visualizing participant workflows

@@
 We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6).
-We have other visualizations in mind, such as displaying the number of windows traversed by each participant as a bar graph.\\
+We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows an illustration), as well as other analyses.\\
+
+\begin{figure}[t]
+\label{fig:error}
+  \centering
+    \includegraphics[width=0.5\textwidth]{error.png}
+    \caption{An example of a technical error message which our participants did not understand.}
+\end{figure}
+
+\begin{figure}[t]
+\label{fig:bar}
+  \centering
+    \includegraphics[width=0.5\textwidth]{screen-bar.png}
+    \caption{An illustration of how we plan to visualize large-scale UI flows as a succinct way to display all participants' window traversal.
+We plan to color code the screens so that the reader can see trends at a glance, such as how the UI path for participants in a mild censorship environment with the old design compare to the UI flow for the participants in a mild censorship environment with a new design.
+It also can communicate how much work was required of a user to configure a connection.}
+\end{figure}
 

### 2015-12-10 paper/circumvention-experiment.tex
visualizing markov complete

@@
 
-One exciting analysis we will perform is to build a Markov model of the UI flow chart (like the one seen in Figure \ref{fig:interface}).
+One exciting analysis we will perform is to build a Markov model of the UI flow chart (Figure \ref{fig:markov} shows a simplified illustration).
 We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6).
-We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows an illustration), as well as other analyses.\\
+We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows a simplified illustration), as well as other analyses.\\
 
 \begin{figure}[t]
-\label{fig:error}
+\label{fig:markov}
   \centering
-    \includegraphics[width=0.5\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
+    \includegraphics[width=0.5\textwidth]{markov.png}
+    \caption{An illustration on a planned analysis using the quantitative survey data.
+This illustration shows two possible user interfaces and uses a Markov model to reflect the aggregate user behavior.
+We believe that this will be an concrete way to predict user behaviors, which is valuable feedback for if the interface is guiding users in a desired UI path.}
 \end{figure}

### 2015-12-10 paper/circumvention-experiment.tex
Fix link to prototype
Add images of new interface

@@
 (addressing our most common failure case) with no apparent risks, we have incorporated it
-into our design. \\
+into our design (Figure \ref{fig:redesign-proxy}). \\
+
+\begin{figure}[h]
+\label{fig:redesign-proxy}
+  \centering
+    \includegraphics[width=0.5\textwidth]{redesign-proxy.png}
+    \caption{the proxy configuration screen, with an option to automatically
+        ``Import from another browser''}
+\end{figure}
 
@@
 We made the guidance from the last interface (to not choose a bridge, to not choose a proxy)
-more direct by selecting the  option to opt out of a proxy as the default option on those screens. 
+more direct by selecting the  option to opt out of a proxy as the default option on those screens
+(Figure \ref{fig:redesign-noproxy}).
 This results in a more streamlined interface with fewer windows
 and fewer clicks required for our participants. \\
+
+\begin{figure}[h]
+\label{fig:redesign-noproxy}
+  \centering
+    \includegraphics[width=0.5\textwidth]{redesign-noproxy.png}
+    \caption{The default option is now to ``Proceed without proxy settings.''}
+\end{figure}
 
@@
 
-A clear example of this is the ``Connect'' button on the first screen, which has
+A clear example of this is the ``Connect'' button on the first screen
+\ref{fig:redesign-firstscreen}, which has
 increased in size and become green, making it more prominent as the recommended
@@
 
+\begin{figure}[h]
+\label{fig:redesign-firstscreen}
+  \centering
+    \includegraphics[width=0.5\textwidth]{redesign-firstscreen.png}
+    \caption{the initial connection screen. Note the prominence given to the
+    ``Connect'' button.}
+\end{figure}
+
 To help lessen the cognitive load and distribute a representative amount of space
@@
 have a chance of  configuring correctly and should only be used in very rare circumstances, 
-we have now incorporated the custom bridge configuration in the dropdown menu; 
+we have now incorporated the custom bridge configuration in the dropdown menu
+(Figure \ref{fig:redesign-bridges});
 it previously took up a significant portion of the bridge configuration screen.
+
+\begin{figure}[h]
+\label{fig:redesign-bridges}
+  \centering
+    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
+    \caption{the bridge selection screen, with the option to ``Add Custom
+    Bridge''}
+\end{figure}
 
@@
 
+\begin{figure}[h]
+\label{fig:redesign-waiting}
+  \centering
+    \includegraphics[width=0.5\textwidth]{redesign-waiting.png}
+    \caption{the new connection screen}
+\end{figure}
+
 In the event that the connection attempt fails, messages from the log are
@@
 the connection. \\
+
+\begin{figure}[h]
+\label{fig:redesign-failure}
+  \centering
+    \includegraphics[width=0.5\textwidth]{redesign-failure.png}
+    \caption{the screen displayed when a connection failed}
+\end{figure}
 
@@
 \item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
-\item \href {a clickable prototype of our interface redesign}{https://marvelapp.com/15a2294}
+\item \href{https://marvelapp.com/15a2294}{a clickable prototype of our interface redesign}
 \item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}

### 2015-12-10 paper/circumvention-experiment.tex
Edit paper

@@
 an essential facet for adoption and use.  
-We focus our analysis on the connection configuration interface of Tor browser,
+We focus our analysis on the connection configuration interface of Tor Browser,
 as censorship circumvention requires correct transport configurations.
-We will conduct a large-scale user study examining 60-100 of users 
-on how they navigate Tor's configuration wizard to complete seven browsing tasks 
+We will conduct a large-scale user study examining how 60-100 users
+navigate Tor's configuration wizard to complete typical browsing tasks
 in three different adversarial settings. Our study combines quantitative measurements (interface
@@
 qualitative measurements (if users were comfortable with use, what was most confusing, and 
-if they would use the browser again). The first phase of the study will evaluate if and how 
+if they would use the browser again). The first phase of the study evaluated if and how
 easily users can circumvent censorship using Tor Browser. The second phase
-of the study will test improvements to the interface and an alternate interface. 
+of the study will test the improvements to the interface. 
 Our goal is to integrate positive usability changes into the Tor Browser. Since
@@
 anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
-``stopping points'' in Tor browser,  documenting points when people would get frustrated enough 
+``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
 to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
@@
 Although Tor was not designed to be a censorship circumvention tool, users started
-to use Tor as a censorship circumvention tool since Tor's role as a proxy to anonymize
+using it as once, since Tor's role as a proxy to anonymize
 people also worked to circumvent censorship. Now, circumventing censorship is a
-common use case for Tor, and Tor current censorship circumvention methods are
+common use case for Tor, and current censorship circumvention methods are
 incorporated into Tor, making it a viable censorship circumvention tool even in the face
@@
 We believe that this is a great opportunity for user research. Censorship circumvention
-is not only a common use case, but one Tor was not intended for. Since Tor does not 
-track their users in any way or performs A/B testing, making a user study a more
+is not only a common use case, but one Tor was not intended for. Tor does not
+track their users in any way or perform A/B testing, making a user study a more
 uniquely beneficial source of feedback. Since the interface does not depend on the 
-internal functionalities of Tor, changes made to the configuration interface would not 
+internal functionality of Tor, changes made to the configuration interface would not
 require huge changes, making any suggested improvements very practical to 
@@
 to configure correctly. Note that bridges, pluggable transports, and proxies are technical 
-concepts which may be unfamiliar to the average users, and that bridges and pluggable 
+concepts which may be unfamiliar to the average user, and that bridges and pluggable
 transports are completely Tor-specific concepts.
@@
 to be plain relays which were exactly similar to public relays, but were unlisted. However, 
-censorship in countries which blocked Tor generally were motivated enough to agressively
-block Tor in other ways, such as traffic analysis. For this reason, a bridge usually associated 
-with a pluggable transport that circumvents deep packet inspection, transports can 
+censors in countries which blocked Tor generally were motivated enough to aggressively
+block Tor in other ways, such as traffic analysis. For this reason, a bridge is usually associated
+with a pluggable transport that circumvents deep packet inspection. Transports can
 assist by obfuscating traffic or reflecting traffic through a content distribution network. 
@@
     \caption{The Tor Bridges Configuration window of the Tor configuration
-    interface. Tor users in censored environments and some of our participants
-    will be required to select the correct bridge for circumventing censorship.
-    Note that the interface prompts users to choose a transport type, which can be
-    the source of confusion. Bridges are non-listed guard relays to the Tor
-    network; transports, supported by bridges, obfuscate traffic in
-    different ways.}
+    interface.}
 \end{figure}
@@
 Still, there remains potential for confusion, especially with the more advanced
-configuration options. Although arguably for the reason that users may not 
-understand or read, bridges, pluggable transports, and  proxies are never defined 
-for the user. This can lead to users confusing these terms, or not understanding
-the relations between these terms. Additionally, there is limited explanation of 
+configuration options.
+Bridges, pluggable transports, and proxies are never defined for the user,
+arguably because they might not read or understand these definitions.
+This can lead to users confusing these terms, or not understanding
+the relations between them. Additionally, there is limited explanation of 
 what pluggable transport types to choose from if the default one fails or how to 
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item  {\bfseries Hypothesis 1}: users will generally not know when they need a bridge or proxy is, leading to issues such as choosing to configure a bridge or proxy when it is not necessary, or configuring bridges or proxies incorrectly.
+\item  {\bfseries Hypothesis 1}: users will generally not know when they need a bridge or proxy, leading to issues such as choosing to configure a bridge or proxy when it is not necessary, or configuring bridges or proxies incorrectly.
 \item  {\bfseries Hypothesis 2}: people will not know when they need to configure or connect, since they do not understand how censorship works.   
@@
 We find these hypotheses to be true for our participants, although sometimes not for the reasons we expected.
-For instance, we believed that proxies will cause confusion when configuring bridges because participants would confuse one as the other; however, the interface redirected users to proxy configuration settings if a participant has chosen to configure a proxy, even if the source of failure was not from the proxy.
+For instance, we believed that proxies will cause confusion when configuring bridges because participants would confuse the two; however, the interface redirected users to proxy configuration settings if a participant had chosen to configure a proxy, even if the source of failure was not from the proxy.
 Details of the experiment that has verified our hypotheses is below.
@@
 
-The qualitative interface evaluation yielded in hours of observation for a set of 16 pre-selected, diverse participants taking various UI paths in different simulated censorship environments.
-We then interviewed the participants, getting hundreds of words of feedback from our participants.
-In this section, we will be talking about the insights gathered from the qualitative interface evaluation, which has shaped the re-design of the interface.
-All of the results are grounded in participants' experiences and feedback, which are available publicly online.
-The video screen captures from the experiment can be found \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{here}; a summary of each video can be found \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{here}.
-The corresponding notes from the after-experiment interview can be found \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{here}.
+The qualitative interface evaluation yielded hours of observations, as well as
+interview data, for a set of 16 pre-selected, diverse participants taking
+various UI paths in different simulated censorship environments. This section
+discusses the insights gathered from the qualitative interface evaluation, which
+has shaped the re-design of the interface. All of the results are grounded in
+participants' experiences and feedback, which are available publicly online. The
+video screen captures from the experiment can be found
+\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{here};
+a summary of each video can be found
+\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{here}.
+The corresponding notes from the after-experiment interview can be found
+\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{here}.
 
-We have evaluated at least one Tor user, one participant who has heard of Tor before the study, and three people who had never heard of Tor before in each simulated censorship environment.
-The nature of small-scale qualitative studies yields in rich information about each participant, but making generalizations from these results such as ``Tor users were able to configure quicker'' would be unsound.
+We evaluated at least one Tor user, one participant who has heard of Tor before the study, and three people who had never heard of Tor before in each simulated censorship environment.
+The nature of small-scale qualitative studies results in rich information about each participant, but making generalizations from these results such as ``Tor users were able to configure quicker'' would be unsound.
 Our observations from our particular three participants were that they were more capable of debugging after failure modes and were more methodological about doing so, but they faced similar difficulties as the other participants.
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Challenge1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
+\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
 As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
@@
 One participant (P12) clicks configure, but answers the questions in such a way that it creates a direct connection.
-Only one (P15) was chose to configure when they needed to.
+Only one (P15) chose to configure when they needed to.
 \item {\bfseries Proof of Challenge 2:} Five participants were placed in a censored environment which did not block Tor.
@@
 Of the other two, one participant (P2) was convinced that configuring a bridge was the correct course of action, but was intimidated at the thought of doing so and was pleasantly surprised when a direct connection succeeded; only one participant (P9) believed that a direct connection would work.
-\item {\bfseries Proof of Challenge 3:} All three of our participants (P14, P15, P16) who never were able to circumvent the simulated censorship environment spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network.
+\item {\bfseries Proof of Challenge 3:} All three of our participants who failed to circumvent the simulated censorship environment (P14, P15, P16) spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network.
 Out of the five participants who needed to fix their bridge settings, there were only two participants (P5, P6) who eventually were able to figure out that their bridge settings needed to be adjusted.
@@
 It would be unreasonable to assume that users should know this information, but some of this may be required to make a correct decision in the current interface.
-\item {\bfseries Observation 2: The interface flow does not guide users down the ideal path.} Much of the real estate on bridge configuration is used for the ``custom bridges'' option, which is an option rarely used.
+\item {\bfseries Observation 2: The interface flow does not guide users down the ideal path.} Much of the real estate on bridge configuration is used for the ``custom bridges'' option, which is rarely used.
 The interface instructs users to check out Internet settings to see if they would require a proxy, but it turns out that people are not skilled at doing so.
@@
 In reality, there was no proxy setup required for any simulated censorship environment in our experiment and participants should have configured a bridge.
-\item {\bfseries Observation 3: There is little constructive feedback during failure cases.} When a connection seems to not work, our participants were unsure of if they should wait more or if they should try the connection with the same configuration again, both of which are viable strategies, depending on the situation.
-Although there are certain error messages which were helpful, most of the error messages were technical and not understood by our participants (Figure \ref{fig:error}).
-The interface does not give clear directions on what participants should do next if a connection fails.
+\item {\bfseries Observation 3: There is little constructive feedback during
+    failure cases.} When a connection seems to not work, our participants were
+    unsure whether they needed to wait longer, or if they should try the
+    connection with the same configuration again. Both of these are viable
+    strategies, depending on the situation. Although there are certain error
+    messages which were helpful, most of the error messages were technical and
+    not understood by our participants (Figure \ref{fig:error}). The interface
+    does not give clear directions on what participants should do next if a
+    connection fails. 
 \end{itemize}
 
-Although we cannot comment on if the challenges mentioned above will be exactly representative of the Tor user population, it is fair to claim that these challenges are challenges that some Tor users will encounter while configuring Tor.
-Our observations are grounded in user interaction--specifically user mental modes, UI flow, and failure design--giving us high confidence that addressing these observations will make a noticeable impact on the usability of the Tor configuration dialog for censorship circumvention.
+Although we cannot comment on whether the challenges mentioned above will be
+exactly representative of the Tor user population, it is fair to claim that some
+Tor users will encounter them while configuring Tor. Our observations are
+grounded in user interaction--specifically user mental modes, UI flow, and
+failure design--giving us high confidence that addressing these observations
+will make a noticeable impact on the usability of the Tor configuration dialog
+for censorship circumvention.
 
@@
 Previously, separate screens with binary options (Do you need a proxy? Yes/No) 
-were provided to help users decide if they needed a bridge or proxy, and skipping
-the configuration windows for bridges and proxies, respectively, when users
-answered that they didn't need one. We have removed these screens
-because our participants did not understand how to answer them correctly. This is 
-anticipated in the old interface, in fact: written text in the interface guides users on to 
-how to answer those questions.
+were provided to help users decide if they needed a bridge or proxy.
+We have removed these screens
+because our participants did not understand how to answer them correctly.
 
-We chose to display all information about bridges and proxies is now contained on one 
-respective screen in the interface, giving the user has the full context of their decision.
-We made the guidance from the last interface (to not choose a bridge, to not choose a proxy)
-more direct by selecting the  option to opt out of a proxy as the default option on those screens
-(Figure \ref{fig:redesign-noproxy}).
+All information about bridges is now contained on one
+screen in the interface, giving the user the full context of their decision.
+The same is done with proxy settings.
+The recommended option (choosing no bridge and no proxy) is now the default on
+the respective configuration screens (Figure \ref{fig:redesign-noproxy}).
 This results in a more streamlined interface with fewer windows
@@
 Although some of our participants in environments had chosen to connect
-directly when they needed to configure, this is generally seen as low-risk today, and 
+directly when they needed to configure,
 the majority of censorship today can be circumvented with a direct connection. 
@@
 
-To help lessen the cognitive load and distribute a representative amount of space
-for options, recommendations are selected as the default option, and rarely used 
-elements are deemphasized. To encourage our users to click on helpful options, 
-the help button on the bridge configuration screen
+To help lessen the cognitive load and use a proportionate amount of space,
+recommended options are selected by default, and rarely used
+elements are deemphasized.
+The help button on the bridge configuration screen
 has been emphasized to be bigger, since it is a helpful option which people rarely
-clicked. To discourage our users from using an advanced setting only technical users 
-have a chance of  configuring correctly and should only be used in very rare circumstances, 
+clicked. To discourage our users from using an advanced setting
+that should only be used in very rare circumstances,
 we have now incorporated the custom bridge configuration in the dropdown menu
@@
 Even in the rare event that the proxy is the issue for the connection setting, the user
-will be directed to the proxy page naturally through the flow of the UI, without
-having the user to defy the natural flow of configuration. \\
+will be directed to the proxy page naturally through the flow of the UI. \\
 
@@
 stuck and didn't offer any guidance for how long users were supposed to wait. 
-The connection process can take a non-trivial couple of minutes, and users may
+The connection process can take a non-trivial amount of time, and users may
 think that the connection isn't working, even when it is making slow progress. We
@@
 displayed, along with tips and suggestions about what to do next (e.g., try
-another bridge). To make potential the options clearer, the new failure screen
+another bridge). To make the potential options clearer, the new failure screen
 includes a separate button for common next steps which are able to resolve
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Testing our design with a small-scale qualitative study.} It is critical to get in-depth data user train of thought as they user the interface, one-on-one interviews, and open-ended feedback.
-For this reason, we plan to run a small-scale qualitative study similar to the one we have run for the old interface.
-We plan to run these studies at the start of Spring 2015.
-\item {\bfseries Testing our design with a large-scale quantitative study.} To test our design alongside the old interface, we will recruit a large number of participants to try out both designs.
-The purpose of this is to get statistically significant results on whether our design choices have helped or not helped a user to configure successfully.
-We plan to run these studies at the start of Spring 2015.
+\item {\bfseries Testing our design with a small-scale qualitative study.} It is
+    critical to get in-depth data from users through one-on-one interviews and
+    open-ended feedback. For this reason, we plan to run a small-scale
+    qualitative study similar to the one we have run for the old interface. We
+    plan to run these studies at the start of Spring 2016.
+\item {\bfseries Testing our design with a large-scale quantitative study.} To
+    test our design alongside the old interface, we will recruit a large number
+    of participants to try out both designs. The purpose of this is to get
+    statistically significant results on whether our design choices have helped
+    users to configure successfully. We plan to run these studies at the start
+    of Spring 2016.
 \item {\bfseries Analyzing which design changes have made a positive impact.} We plan to instrument our interfaces to capture all clicks, window transitions, and other events so that we can analyze if our designs have helped our users connect faster and or with less effort.
@@
 \noindent {\bfseries Quantitative experiment analyses} We want to show a statistically significant improvement in user effort for a successful connection.
-We have deemed this can be measured with various factors such as time, clicks, etc.
+We believe that this can be measured with various factors such as time, clicks, etc.
 For this reason, we will specifically be collecting data about: the total number of participants who have successfully circumvented censorship, the number of connection attempts for a successful connection, how much time participants spent configuring before a successful connection, the number of windows traversed in the UI, the number of clicks made, if bridge and proxy configuration interfered with each other, and how many people try repeat configuration settings.

### 2015-12-11 paper/circumvention-experiment.tex
Fix typos

@@
 Although Tor was not designed to be a censorship circumvention tool, users started
-using it as once, since Tor's role as a proxy to anonymize
+using it as one, since Tor's role as a proxy to anonymize
 people also worked to circumvent censorship. Now, circumventing censorship is a
@@
 \item {\bfseries Intermediate censorship} 
-(Representative of countries such as Tunsia.)
+(Representative of countries such as Tunisia.)
 Certain domains are blocked. Censorship circumvention
@@
 ``standard'' browser (one that is not used for censorship circumvention, such
-as Chrome, Safari, or Firefox) to illustrate the situation.
+as Chrome, Internet Explorer, or Firefox) to illustrate the situation.
 Participants are told that their
@@
 consistency across participants: behaviors may change if the tasks are
-critical or if there were great risks associated with configuration mistakes.
+critical or if there are great risks associated with configuration mistakes.
 
@@
 
-After users complete the browsing tasks (or time runs out), we conduct an
+After users completed the browsing tasks (or time ran out), we conducted an
 interview, collecting qualitative feedback from
@@
 simulation.
+
+% XXX: expect merge conflict here because whitespace was (accidentally?) removed in newer changes
 
@@
 \item {\bfseries Observation 1: Users lack a mental model of how censorship works.} For instance, our participants did not know the difference between a bridge and a proxy or a censored website versus censored Tor relays.
-We suspect that this is the result of an accurate mental model of how the Internet works.
+We suspect that this is the result of an inaccurate mental model of how the Internet works.
 It would be unreasonable to assume that users should know this information, but some of this may be required to make a correct decision in the current interface.
@@
 Tor users will encounter them while configuring Tor. Our observations are
-grounded in user interaction--specifically user mental modes, UI flow, and
-failure design--giving us high confidence that addressing these observations
+grounded in user interaction -- specifically user mental modes, UI flow, and
+failure design -- giving us high confidence that addressing these observations
 will make a noticeable impact on the usability of the Tor configuration dialog
@@
 A clear example of this is the ``Connect'' button on the first screen
-\ref{fig:redesign-firstscreen}, which has
+(Figure \ref{fig:redesign-firstscreen}), which has
 increased in size and become green, making it more prominent as the recommended
@@
 the user is on. It serves to clarify the independence of bridges and proxies,
-which need to be configured separately. In the event of a failure, the user is
+which need to be configured separately
+
+In the event of a failure, the user is
 returned to the first step of the process -- the bridge configuration -- to
@@
 the user had to manually click to go backward in the dialog to configure bridges.
-Even in the rare event that the proxy is the issue for the connection setting, the user
+In the rare event that the proxy is the issue for the connection setting, the user
 will be directed to the proxy page naturally through the flow of the UI. \\
@@
 
-\noindent {\bfseries Looking Forward} We will help incorporate changes into the Tor browser.
+\noindent {\bfseries Looking Forward} We will help incorporate changes into the Tor Browser.
 Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make.

### 2015-12-11 paper/circumvention-experiment.tex
Fix references to figures
In-line references to figures used to refer to the wrong ones when compiled.
(e.g., it would refer to Figure 6 when actually the figure in question was 10)

This was fixed by changing the placement of the \label command within
the figure environment: it's now after the \caption command.
This matters because of how the \label macro is defined.
See: https://tex.stackexchange.com/a/111281
my changes

--- 2015-12-10 paper/circumvention-experiment.tex
@@
 as censorship circumvention requires correct transport configurations.
-We will conduct a large-scale user study examining how 60-100 users
-navigate Tor's configuration wizard to complete typical browsing tasks
-in three different adversarial settings. Our study combines quantitative measurements (interface
-paths taken to success, time to success, and which configuration was chosen) and
-qualitative measurements (if users were comfortable with use, what was most confusing, and 
-if they would use the browser again). The first phase of the study evaluated if and how
-easily users can circumvent censorship using Tor Browser. The second phase
-of the study will test the improvements to the interface. 
-Our goal is to integrate positive usability changes into the Tor Browser. Since
-the configuration interface is modular and does not require changes to the Tor Browser
-functionality, these changes will be easy to deploy.
+The first phase of the study evaluated if and how easily users can circumvent censorship 
+using Tor Browser; the results of conducting our experiment and the interface redesign
+is presented in this paper. The second phase
+of the study will test the improvements to the interface, which has yet to happen. However, we take
+some time to describe our plans. 
+Our goal is to integrate positive usability changes into the Tor Browser, making
+censorship circumvention an easier process for users around the world.
 
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:bridges}
@@
 
-After users complete the browsing tasks (or time runs out), we conduct an
-interview, collecting qualitative feedback from
-participants about their browsing experience as a whole
-and the configuration interface specifically.
-We ask questions such as
+After users complete the browsing tasks (or time runs out), we conducted an
+interview asking participants about their censorship circumvention experience.
+We were able to tailor the interview to the particular participant, since we were able to
+observe our participants' sessions. This way, we could follow up and ask participants
+about reasons for taking particular actions and verify any hypothesis we had about 
+the participant (such as ``they didn't know what to do on window 3'').  We did
+ask a couple question across all participants: 
 ``What was the most challenging part of connecting?''
@@
 \subsection{Interface design and iteration}
-After completing the qualitative user studies, we analyzed their results to
-identify common themes and problems. Based on these, we then designed
-improvements to the Tor launcher interface.
-
-To do this, we used an iterative design process, starting with low-fidelity
-(paper and pencil) prototypes and then proceeding to higher-fidelity versions.
-At each stage, the prototype was clickable, allowing for more realistic
-simulation.
-
-We collected feedback from researchers, professors, and Tor users and developers
+After completing the qualitative user studies, we analyzed the results to
+identify common themes and problems. These were the basis of our interface 
+redesign. To do this, we used an iterative design process, starting with low-fidelity
+(paper and pencil) prototypes and then proceeding to higher-fidelity (realistic clickable mockups)
+prototypes.We collected feedback from researchers, professors, and Tor users and developers
 through the Tor project's mailing lists. We then iterated on the design by
 incorporating the comments and suggestions we received into the next version of
-the interface.
+the interface. We plan to take some qualitative measurements of the new design
+by having some participants think aloud while they use our realistic mockup. This is 
+to get any feedback before we launch our quantitative interface evaluation.
 
-\subsection{Quantitative evaluation of improvements}
+\subsection{Quantitative interface evaluation}
 Once the new design of the user interface is finalized, we will conduct a
@@
 instrumented to collect metrics and statistics for use in analysis and
-hypothesis testing.
-Some examples of metrics collected include the time spent on each screen, which
-paths the user followed, which interface elements they interacted with, and how
-often they did so. These will be analyzed in conjunction with high-level metrics
-(was the user able to connect to Tor successfully?).
+hypothesis testing. Such metrics include the time spent on each screen, which
+paths were taken, which interface elements were interacted with, etc.
 
@@
 
-The qualitative interface evaluation yielded hours of observations, as well as
+The qualitative interface evaluation yielded hours of observations and
 interview data, for a set of 16 pre-selected, diverse participants taking
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:redesign-proxy}
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:redesign-noproxy}
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:redesign-firstscreen}
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:redesign-bridges}
@@
 
-A progress indicator at the top of the window indicates which configuration step
-the user is on. It serves to clarify the independence of bridges and proxies,
-which need to be configured separately. In the event of a failure, the user is
+A progress indicator at the top of the window indicates various steps necessary
+for configuring a connection. In addition to communicating to the user what the various 
+steps of configuration are from the beginning, this indicator also serves to clarify the independence of
+bridges and proxies, which need to be configured separately. In the event of a failure, the user is
 returned to the first step of the process -- the bridge configuration -- to
@@
 
-Many users were led astray by interface elements that were unhelpful or
+Users were led astray by interface elements that were unhelpful or
 misleading if the program encountered connection problems. Our design seeks to
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:redesign-waiting}
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \label{fig:redesign-failure}

### 2015-12-11 paper/circumvention-experiment.tex

@@
 \begin{figure*}[t]
-\label{fig:interface}
   \centering
@@
 \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{this hyperlink}.}
+\label{fig:interface}
 \end{figure*}
@@
     interface.}
+\label{fig:bridges}
 \end{figure}
@@
 (paper and pencil) prototypes and then proceeding to higher-fidelity (realistic clickable mockups)
-prototypes.We collected feedback from researchers, professors, and Tor users and developers
+prototypes.
+
+We collected feedback from researchers, professors, and Tor users and developers
 through the Tor project's mailing lists. We then iterated on the design by
@@
 \begin{figure}[t]
-\label{fig:error}
   \centering
@@
     \caption{An example of a technical error message which our participants did not understand.}
+\label{fig:error}
 \end{figure}
@@
     Bridge''}
+\label{fig:redesign-bridges}
 \end{figure}
@@
 \begin{figure}[t]
-\label{fig:markov}
   \centering
@@
 We believe that this will be an concrete way to predict user behaviors, which is valuable feedback for if the interface is guiding users in a desired UI path.}
+\label{fig:markov}
 \end{figure}
@@
 \begin{figure}[t]
-\label{fig:bar}
   \centering
@@
 It also can communicate how much work was required of a user to configure a connection.}
+\label{fig:bar}
 \end{figure}
@@
 \begin{figure}[h]
-\label{fig:window1}
   \centering
@@
     to help users answer this question.}
+\label{fig:window1}
 \end{figure}
@@
 \begin{figure}[h]
-\label{fig:window2}
   \centering
@@
     ``Continue.''}
+\label{fig:window2}
 \end{figure}
@@
 \begin{figure}[h]
-\label{fig:window3}
   \centering
@@
     by clicking  ``Continue.''}
+\label{fig:window3}
 \end{figure}
@@
 \begin{figure}[h]
-\label{fig:window4}
   \centering
@@
     by clicking  ``Continue.''}
+\label{fig:window4}
 \end{figure}
@@
 \begin{figure}[h]
-\label{fig:window5}
   \centering
@@
     connect to the Tor Network.}
+\label{fig:window5}
 \end{figure}

### 2015-12-11 paper/circumvention-experiment.tex
put back changes Nathan made I accidentally blew away on merge

@@
 
-After users complete the browsing tasks (or time runs out), we conducted an
+After users completed the browsing tasks (or time ran out), we conducted an
 interview asking participants about their censorship circumvention experience.
@@
 steps of configuration are from the beginning, this indicator also serves to clarify the independence of
-bridges and proxies, which need to be configured separately. In the event of a failure, the user is
+bridges and proxies, which need to be configured separately.
+
+In the event of a failure, the user is
 returned to the first step of the process -- the bridge configuration -- to
@@
 
-\noindent {\bfseries Looking Forward} We will help incorporate changes into the Tor Browser.
+\noindent {\bfseries s} We will help incorporate changes into the Tor Browser.
 Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make.

### 2015-12-11 paper/circumvention-experiment.tex
wordsmithing to get colums looking nice and killing orphans

@@
 
-There are still many features of Tor that are left unevaluated through user
+Many features of Tor that are left unevaluated through user
 research --- such as advanced web tasks (e.g., accessing hidden services), the
@@
 their connection to the
-Tor network. While people in most countries can connect to Tor using the
+Tor network. While most can connect to Tor using the
 dialog's default settings, users in certain censorship environments must
 make use of additional settings, such as bridges, proxies, or both. 
-Our study explores how successfully this interface guides users to
-correctly configuring their browser.
+Our study explores how the average user circumvents censorship
+through this interface.
 
@@
 We collected feedback from researchers, professors, and Tor users and developers
-through the Tor project's mailing lists. We then iterated on the design by
+through the Tor project's mailing lists. We iteratively designed by
 incorporating the comments and suggestions we received into the next version of
@@
 
-We evaluated at least one Tor user, one participant who has heard of Tor before the study, and three people who had never heard of Tor before in each simulated censorship environment.
-The nature of small-scale qualitative studies results in rich information about each participant, but making generalizations from these results such as ``Tor users were able to configure quicker'' would be unsound.
-Our observations from our particular three participants were that they were more capable of debugging after failure modes and were more methodological about doing so, but they faced similar difficulties as the other participants.
+In each censorship environment, we evaluated one Tor user, one who has heard of Tor before the study, and at least three people who had never heard of Tor before.
+Small-scale qualitative studies results in rich information about each participant, but making generalizations from these results such as ``Tor users were able to configure quicker'' would be unsound.
+Our observations of our particular three Tor users were that they were more capable of debugging after failure modes and were more methodological about doing so, but they faced similar difficulties as the other participants.
+\\
 
-We noticed four common challenges that our participants have had with the interface:
+We noticed four common challenges:
 
@@
 However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-\item {\bfseries Challenge 3:} When their first attempt to connect fails, people tend to first try changing the proxy settings, because the interface directs people to the last window participants saw before the connection failure.
-This was problematic since the problem is not necessarily where the interface directs users.
-For instance, it was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
+\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window participants saw before the connection failure.
+The problem is not necessarily where the interface directs users, misguiding them.
+It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
 \item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
@@
 
-These common four problems were illustrated by our participants concretely:
+These problems were illustrated by our participants:
 
@@
 
-A progress indicator at the top of the window indicates various steps necessary
-for configuring a connection. In addition to communicating to the user what the various 
+A progress indicator at the top of indicates various steps
+for configuring a connection. In addition to communicating what the various 
 steps of configuration are from the beginning, this indicator also serves to clarify the independence of
@@
 
-In the event of a failure, the user is
-returned to the first step of the process -- the bridge configuration -- to
-avoid misleading users into thinking the proxy settings are the culprit. Previously,
+After a failure, the users are
+returned to the first step of the process -- the bridge configuration -- since this
+is usually the cause for configuration issues. Previously,
 the user had to manually click to go backward in the dialog to configure bridges.
@@
 
-The progress bar in the connection window drew many complaints, because it got
-stuck and didn't offer any guidance for how long users were supposed to wait. 
-The connection process can take a non-trivial amount of time, and users may
-think that the connection isn't working, even when it is making slow progress. We
-address this by providing a countdown timer, indicating that a long wait time does
-not indicate failure. We further encourage waiting by adding visual indicators
+The progress bar in the connection window often was unresponsive 
+and did not offer guidance for to wait. 
+The connection process can take about two minutes long enough that users may
+think that the connection has failed, even when it is making slow and invisible progress. 
+We added a countdown timer to indicate that a long wait time does
+not indicate failure. We also add visual indicators
 for major milestones in the connection, providing better feedback about what has
@@
 In the event that the connection attempt fails, messages from the log are
-displayed, along with tips and suggestions about what to do next (e.g., try
+displayed, along with suggestions about what to do next (e.g., try
 another bridge). To make the potential options clearer, the new failure screen
@@
 \noindent {\bfseries Additional changes}
-In addition to the changes above, we have simplified flows where possible,
-provided clearer definitions of bridges and proxies, and reduced visual clutter.
-We believe that all of these changes are cohesive with the other design changes
-made to the interface and will be beneficial for the user.
+In addition to the changes above, we have simplified flows,
+reduced text, and reduced visual clutter.
+We believe these changes are cohesive with the our design 
+and will be beneficial for the user.\\
 
@@
 
-The work summarized in the paper is only a part of the process of improving the Tor configuration
+The work summarized is only a part of the process of improving the Tor configuration
 dialog for more usable censorship circumvention. We plan to continue this work by:

### 2015-12-11 paper/circumvention-experiment.tex
Fix new typos

@@
 
-Many features of Tor that are left unevaluated through user
+Many features of Tor have not been evaluated through user
 research --- such as advanced web tasks (e.g., accessing hidden services), the
@@
 incorporating the comments and suggestions we received into the next version of
-the interface. We plan to take some qualitative measurements of the new design
-by having some participants think aloud while they use our realistic mockup. This is 
+the interface. We plan to take qualitative measurements of the new design
+by having participants think aloud while they use our realistic mockup. This is
 to get any feedback before we launch our quantitative interface evaluation.
@@
 However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window participants saw before the connection failure.
+\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
 The problem is not necessarily where the interface directs users, misguiding them.
@@
 
-A progress indicator at the top of indicates various steps
+A progress indicator at the top of the window indicates various steps
 for configuring a connection. In addition to communicating what the various 
@@
 
-The progress bar in the connection window often was unresponsive 
-and did not offer guidance for to wait. 
-The connection process can take about two minutes long enough that users may
+The progress bar in the connection window was often unresponsive
+and did not offer guidance for how long users were supposed to wait.
+The connection process can take about two minutes --- long enough that users may
 think that the connection has failed, even when it is making slow and invisible progress. 
@@
 reduced text, and reduced visual clutter.
-We believe these changes are cohesive with the our design 
+We believe these changes are cohesive with our design
 and will be beneficial for the user.\\

### 2016-03-11 pets2017-paper/pets2017-paper.tex
renamed files.

--- 2015-12-11 paper/circumvention-experiment.tex
@@
 
+\section{Quantitative Testing}
+{\color {red} TODO}
+
+\section{Evaluation}
+{\color {red} TODO, write about what worked, what didn't, and what we recommend.}
+
+\section{Discussion}
+{\color {red} 
+Talk about how the design was a conservative version. And why the conservative choices were made. For at-risk users, maintainability, etc.
+
+Additional potential changes that could be made to the browser: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item {\bfseries Tell people to click connect.} On the first screen, there are no instructions for the user on what to do.
+There is a description of what each option means, but there is no guidance on what they should do.
+Ideally, we would people to click connect, and then try the manual configuration if a direct connection fails.
+But communicating this may put some users at risk.
+I would argue that the benefit is higher than the risk.
+\item {\bfseries Auto-configure after connect.} After a person has already clicked connect and the connection was unsuccessful, they have already been logged.
+I am assuming that the significant difference is between being logged trying to connect to Tor or not at all, rather than the number of connection attempts made.
+This would greatly save our users a lot of headache.
+\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
+The amount of people who use proxies is low, but then ...
+this would not give users control in the beginning of the configuration process.
+\item{\bfseries Ask about the risk.} Rather than having the configuration dialog be manual by default, just ask if the users are at risk if the process was automated.
+If they are not at risk, we can do it automatically, and the at-risk users can configure manually.
+The issue with this is that people may not answer this question honestly, or they might not know the correct answer to this question.
+\item{\bfseries Ask if they are qualified to make decisions.} Asking users if they know which bridge to choose, and choosing for them if they say they don't know.
+We probably know better than they do.
+But there are ethical implications of choosing bridges for them rather them making the mistakes themselves.
+The issue with this is that people may not answer honestly.
+\end{itemize}
+}
+
 \section{Future Work}

### 2016-03-11 pets2017-paper/pets2017-paper.tex
created a bare outline and wrote down some initial thoughts.

@@
 
-\title{Tor's Usability for Censorship Circumvention}
+\title{An Inclusive, Usable Redesign of the Tor Configuration Launcher}
 \numberofauthors{1}
@@
 \begin{abstract}
-Tor has grown beyond its original purpose as an anonymity tool and has 
-since become an important censorship circumvention tool. It is now listed
-as one of the ways that normal people use Tor \cite{whotor}.
-We specifically examine its usability as a censorship circumvention tool,
-an essential facet for adoption and use.  
-We focus our analysis on the connection configuration interface of Tor Browser,
-as censorship circumvention requires correct transport configurations.
-The first phase of the study evaluated if and how easily users can circumvent censorship 
-using Tor Browser; the results of conducting our experiment and the interface redesign
-is presented in this paper. The second phase
-of the study will test the improvements to the interface, which has yet to happen. However, we take
-some time to describe our plans. 
-Our goal is to integrate positive usability changes into the Tor Browser, making
-censorship circumvention an easier process for users around the world.
 
@@
 
-\keywords{Censorship, Security, User Studies, Anonymity, Tor}
+\keywords{User Studies, Tor, Security, Censorship, Anonymity}
 
 \section{Introduction}
-Tor is primarily known as the most widely used anonymity tool today. 
-For this reason, user studies on Tor have been solely about the usability of Tor as an
-anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
-``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
-to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
-Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
-Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
-Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
-This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
-5.1 and later. There has been no work done on Tor as a censorship circumvention tool.
+We need to design for at least three types of users: users who use Tor for anonymity, users who use Tor for censorship circumvention who are not at risk, users who use Tor for censorship circumvention who are at risk.
 
-Many features of Tor have not been evaluated through user
-research --- such as advanced web tasks (e.g., accessing hidden services), the
-configuration menu to connect to the Tor network, configuring automatic
-updates, and identity/cookie management. Rather than selecting the features to
-study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
-Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
-Although Tor was not designed to be a censorship circumvention tool, users started
-using it as one, since Tor's role as a proxy to anonymize
-people also worked to circumvent censorship. Now, circumventing censorship is a
-common use case for Tor, and current censorship circumvention methods are
-incorporated into Tor, making it a viable censorship circumvention tool even in the face
-of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
-To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool.
-
-We believe that this is a great opportunity for user research. Censorship circumvention
-is not only a common use case, but one Tor was not intended for. Tor does not
-track their users in any way or perform A/B testing, making a user study a more
-uniquely beneficial source of feedback. Since the interface does not depend on the 
-internal functionality of Tor, changes made to the configuration interface would not
-require huge changes, making any suggested improvements very practical to 
-deploy.
+What makes this design unique is that we have to handle two use cases (anonymity and censorship circumvention) and that there are at-risk users we need to consider.
+We can't lean toward helping them configure their connection all the time because a lot of people use Tor for anonymity or casual browsing, and to do this would be over-fitting to the censorship evasion population (and technically, is a burden on bridges).
+We also cannot automate anything, unless we want to put users at risk.
+Also, for maintainability, we would ideally love it if users could just choose their bridge settings, since any automation or device is bound to be different from country to country and also will become out of date sooner or later.
 
@@
 
-\noindent {\bfseries Overview}
-The Tor Browser provides a configuration interface to guide users through setting up 
-their connection to the
-Tor network. While most can connect to Tor using the
-dialog's default settings, users in certain censorship environments must
-make use of additional settings, such as bridges, proxies, or both. 
-Our study explores how the average user circumvents censorship
-through this interface.
-
-For context, we will give the definition of bridges, pluggable transports, and proxies. 
-Keep in mind that this is the kind of information that a user might need to know to be able
-to configure correctly. Note that bridges, pluggable transports, and proxies are technical 
-concepts which may be unfamiliar to the average user, and that bridges and pluggable
-transports are completely Tor-specific concepts.
-
-Bridges are unlisted Tor relays that make it possible for a user to connect
-to the Tor network even if a censor blocks all publicly listed Tor relays. There used 
-to be plain relays which were exactly similar to public relays, but were unlisted. However, 
-censors in countries which blocked Tor generally were motivated enough to aggressively
-block Tor in other ways, such as traffic analysis. For this reason, a bridge is usually associated
-with a pluggable transport that circumvents deep packet inspection. Transports can
-assist by obfuscating traffic or reflecting traffic through a content distribution network. 
-Proxies help bypass local network restrictions and are typically only
-needed in restricted cases, such as corporate environments.\\
-
-\noindent {\bfseries Configuration Flow}
-
-\begin{figure*}[t]
-  \centering
-    \includegraphics[width=\textwidth]{../torconfig.png}
-    \caption{This flow chart shows all of the possible paths taken through the
-    Tor configuration interface. A state represents a window in the interface,
-    with the exception of the leaves, which indicate the final action taken by
-    the interface (``q'' for quit, ``s'' for success, and ``e'' for error). The
-    transitions between the states indicate which user action causes that
-    transition. Annotations for the error states can be found by following
-\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/torconfig.dot}{this hyperlink}.}
-\label{fig:interface}
-\end{figure*}
-
-As bridges and proxies can be configured independently or together, there are
-four main ways to set up a connection:
-
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item With a bridge and proxy
-    \item With a bridge but no proxy
-    \item Without a bridge but with a proxy
-    \item Without either a bridge or proxy
-\end{enumerate}
-
-The launcher interface asks a series of questions to
-determine which of these configuration states a user requires.
-The four high-level states correspond to five distinct paths through the
-configuration interface. (The latter option -- connecting with neither a bridge
-nor proxy -- contributes two separate paths.) Each path branches further
-depending on user-specific inputs. Figure \ref{fig:interface} illustrates the
-resulting paths.
-
-When the configuration window opens, a user is given the option to connect
-directly to the Tor network by clicking ``Connect'', or to click ``Configure''
-``if this computer's Internet connection is censored or proxied'' (Figure
-\ref{fig:window1}).
-
-If they choose the latter, the next screen asks, ``Does your Internet Service
-Provider (ISP) block or otherwise censor connection to the Tor network?''
-(Figure \ref{fig:window2}). Though this sounds repetitive, it is meant to
-identify and divert users who need only a proxy (and no bridge).
-This phrasing of the question carries the assumption that people will
-not know if they need a bridge or not, but that they are equipped to answer if their
-current network environment censors the Tor Network.
-
-\begin{figure}[t]
-\label{fig:bridges}
-  \centering
-    \includegraphics[width=0.5\textwidth]{configuration-screenshot.png}
-    \caption{The Tor Bridges Configuration window of the Tor configuration
-    interface.}
-\label{fig:bridges}
-\end{figure}
-
-Next, users are asked to configure bridges by selecting a transport type from a
-dropdown menu or entering the IP address of a custom bridge in a textbox (Figure
-\ref{fig:bridges}).
-Finally, users are asked whether they need a local proxy (Figure
-\ref{fig:window4}) and (if they answered yes) to configure it (Figure
-\ref{fig:window5}).
-
-Note that a user can decide to click ``Configure'' on the first screen, but then
-opt out of both bridges and proxies.
-In this case, connecting after these configuration steps
-would be equivalent to clicking ``Connect'' on the first screen. \\
-
-\noindent {\bfseries Design choices}
-The launcher interface utilizes a number of techniques to aid users and simplify
-the choices they have to make. Help buttons and a support email address that
-appears on every screen are meant to assist users that get stuck in the process.
-The interface also makes good use of defaults, for example by emphasizing that
-certain options ``will work in most situations.''
-
-Still, there remains potential for confusion, especially with the more advanced
-configuration options.
-Bridges, pluggable transports, and proxies are never defined for the user,
-arguably because they might not read or understand these definitions.
-This can lead to users confusing these terms, or not understanding
-the relations between them. Additionally, there is limited explanation of 
-what pluggable transport types to choose from if the default one fails or how to 
-find proxy settings, which will be required of some users.
-
-\section{Hypotheses}
-We expected that the average user will struggle to connect because they do not understand censorship circumvention or the  censorship circumvention technologies offered by Tor.
-We also predict that a user will not get the feedback they need to revise their connection configuration if they fail.
-Specifically:
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item  {\bfseries Hypothesis 1}: users will generally not know when they need a bridge or proxy, leading to issues such as choosing to configure a bridge or proxy when it is not necessary, or configuring bridges or proxies incorrectly.
-\item  {\bfseries Hypothesis 2}: people will not know when they need to configure or connect, since they do not understand how censorship works.   
-\item  {\bfseries Hypothesis 3}: proxies will cause confusion when configuring bridges. 
-\end{itemize}
-
-We find these hypotheses to be true for our participants, although sometimes not for the reasons we expected.
-For instance, we believed that proxies will cause confusion when configuring bridges because participants would confuse the two; however, the interface redirected users to proxy configuration settings if a participant had chosen to configure a proxy, even if the source of failure was not from the proxy.
-Details of the experiment that has verified our hypotheses is below.
-
 \section{Methodology}
 
-To test our hypotheses, we simulated several environments in which people may
-have to use Tor for censorship circumvention. We examined whether users are able
-to join the network and studied how they interact with the launcher interface.
-Based on our findings, we designed improvements to the Tor launcher interface,
-which we test in a large-scale study.
-
-\subsection{Simulated censorship environments}
-We simulated three censorship environments.
-They are informed by our experience with pluggable transports
-and knowledge of commonly seen censorship techniques.
-They are not meant to perfectly replicate the network environment
-in any particular country. Although inspired by reality, these
-abstract simulations are intended to require distinct configurations
-of the Tor Browser from our participants.
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Mild censorship} 
-(Representative of countries such as France and Australia.)
-Certain domains are blocked. Reaching these 
-domains requires a censorship circumvention 
-tool. The default option to ``connect'' to the Tor network 
-directly will circumvent this censor. Additional correct
-bridge or proxy configurations are optional.
-
-\item {\bfseries Intermediate censorship} 
-(Representative of countries such as Tunisia.)
-Certain domains are blocked. Censorship circumvention
-tools such as Tor are blocked. Since all public Tor
-relay nodes are blocked, the default option to ``connect'' to the Tor network
-directly will fail. Any choice of a hard-coded bridge
-or a valid non-public bridge will circumvent this censor.  
-Additional correct proxy configuration is optional.
-
-\item {\bfseries Comprehensive censorship} 
-(Representative of countries such as China and Syria.)
-Certain domains are blocked. Censorship circumvention tools
-are thoroughly blocked. Tor is blocked by blocking all public
-Tor relay nodes, and the censor has examined source code to block
-all hard-coded bridge relays in the configuration interface. The default option
-to ``connect'' to the Tor network directly will fail. Most bridges will fail,
-but ``meek-amazon,'' ``meek-azure,'' and ``meek-google'' still work.
-% TODO: meek-google doesn't work either, right? Should we remove it?
-This is because domain-fronting requires censors to block entire CDNs to also
-block this transport (which will cause huge collateral blocking damage), making
-it resistant to aggressive censorship environments.
-(See ~\cite{fifield2015blocking} for additional details.)\\
-\end{itemize}
-
-\subsection{Qualitative interface evaluation}
-To identify problems with the existing interface, we conducted a series of
-qualitative evaluations with a set of users representative of the general
-population.
-
-Using established best practices from the field of user experience research
-(\cite{howmanyusers}), we recruited five users for each censorship environment.
-We pre-screened our participants to have a good mix of gender, age, technical
-background, and familiarity with Tor in each environment, and also overall. \\
-
+\subsection{Evaluation}
 %Some references to keep in mind when explaining:
@@
 
-\noindent {\bfseries Procedure}
-The experiment begins with the participants being informed that they are in a
-simulated censorship
-environment, where some --- but not all --- websites are blocked. We
-instruct them to visit a non-blocked website and a blocked website on a
-``standard'' browser (one that is not used for censorship circumvention, such
-as Chrome, Internet Explorer, or Firefox) to illustrate the situation.
-Participants are told that their
-role is that of a regular citizen who is trying to visit blocked websites
-for non-critical purposes,
-and for whom the chance of risk is minimal. This information is given
-to achieve
-consistency across participants: behaviors may change if the tasks are
-critical or if there are great risks associated with configuration mistakes.
+\subsection{Design}
 
-After explaining the situation and the user's role, we
-instruct them to complete a set of
-tasks which will require visiting blocked websites. Ultimately, the
-participants will need to configure their Tor Browser to circumvent the
-simulated censorship environment. These tasks have a three-fold purpose of
-providing participants with feedback (if they did not correctly configure their
-browser, they cannot reach the website), motivating the participants to
-configure the browser correctly, and providing the researchers with an
-indicator of successful censorship circumvention.
-Participants' screens are recorded to capture how they configure
-their browser.
+\subsection{Testing}
+{\color {red} TODO}
 
-After users completed the browsing tasks (or time ran out), we conducted an
-interview asking participants about their censorship circumvention experience.
-We were able to tailor the interview to the particular participant, since we were able to
-observe our participants' sessions. This way, we could follow up and ask participants
-about reasons for taking particular actions and verify any hypothesis we had about 
-the participant (such as ``they didn't know what to do on window 3'').  We did
-ask a couple question across all participants: 
-``What was the most challenging part of connecting?''
-and
-``What is one change you would recommend?''
+\subsection{Logistics} 
+{\bfseries Simulated censorship environments}
+{\bfseries Online Tasks}
 
-\subsection{Interface design and iteration}
-After completing the qualitative user studies, we analyzed the results to
-identify common themes and problems. These were the basis of our interface 
-redesign. To do this, we used an iterative design process, starting with low-fidelity
-(paper and pencil) prototypes and then proceeding to higher-fidelity (realistic clickable mockups)
-prototypes.
+\section{Results}
 
-We collected feedback from researchers, professors, and Tor users and developers
-through the Tor project's mailing lists. We iteratively designed by
-incorporating the comments and suggestions we received into the next version of
-the interface. We plan to take qualitative measurements of the new design
-by having participants think aloud while they use our realistic mockup. This is
-to get any feedback before we launch our quantitative interface evaluation.
+\subsection{Evaluation} 
+\subsection{Design} 
+\subsection{Validation} 
+\subsection{Recommendations} 
+TODO, write about what worked, what didn't, and what we recommend.
 
-\subsection{Quantitative interface evaluation}
-Once the new design of the user interface is finalized, we will conduct a
-large-scale quantitative evaluation, to test whether the improvements had a
-measurable effect on people's ability to connect to the Tor network.
-
-The experimental procedure will be nearly identical to the procedure for the
-qualitative portion of the study, described above. However, rather than
-conducting open-ended interviews at the end of the tasks, participants will be
-asked to fill out a brief survey. Furthermore, the interface will be
-instrumented to collect metrics and statistics for use in analysis and
-hypothesis testing. Such metrics include the time spent on each screen, which
-paths were taken, which interface elements were interacted with, etc.
-
-Participants will be split across several different experimental conditions.
-Some will be testing the improved user interface, while those in the control
-group will be completing the same tasks using the old, unimproved interface. \\
-% NOTE: removed mention of the alternate interface, unless there's something to say about it
-
-\noindent {\bfseries Experiment Logistics} 
-We plan to recruit up to 100 users for the purpose of this study,
-making it the largest user study of Tor to date.  This study will be conducted at the
-Experimental Social Science Laboratory (Xlab)
-at the University of California, Berkeley, which consists of 36 laptops,
-separated by cubicle walls. We will use individual host firewalls to simulate
-censorship environments and will record computer screens to capture 
-user activity. The total length of the experiment, including briefing, completing the censorship 
-circumvention tasks, exit survey, and debriefing, will be about an hour.
-Participants will be compensated \$30 for their time, which covers
-minimum wage for an hour and any transportation costs to the lab. 
-The IRB protocol to run this user study has been approved (2014-12-6995).
-
-\section{Initial Results}
-
-The qualitative interface evaluation yielded hours of observations and
-interview data, for a set of 16 pre-selected, diverse participants taking
-various UI paths in different simulated censorship environments. This section
-discusses the insights gathered from the qualitative interface evaluation, which
-has shaped the re-design of the interface. All of the results are grounded in
-participants' experiences and feedback, which are available publicly online. The
-video screen captures from the experiment can be found
-\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{here};
-a summary of each video can be found
-\href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{here}.
-The corresponding notes from the after-experiment interview can be found
-\href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{here}.
-
-In each censorship environment, we evaluated one Tor user, one who has heard of Tor before the study, and at least three people who had never heard of Tor before.
-Small-scale qualitative studies results in rich information about each participant, but making generalizations from these results such as ``Tor users were able to configure quicker'' would be unsound.
-Our observations of our particular three Tor users were that they were more capable of debugging after failure modes and were more methodological about doing so, but they faced similar difficulties as the other participants.
-\\
-
-We noticed four common challenges:
+\section{Future Work}
+In addition to merging our code with the source code:
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
-As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
-\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
-Participants knew that they were censored to some degree since we had simulated censorship of websites.
-However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
-The problem is not necessarily where the interface directs users, misguiding them.
-It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
-\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
-The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+\item {\bfseries Detecting the need for proxies.} We hacked this together for now. 
+\item {\bfseries Handling rare error cases.} Mention clock drift and proxy connection cases.
+\item {\bfseries Additional user feedback.} Animation in the progress window. 
 \end{itemize}
 
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
-\label{fig:error}
-\end{figure}
-
-These problems were illustrated by our participants:
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Proof of Challenge 1:} Of the five participants who could click directly to the network, three participants (P3,P4,P10) did not choose to connect directly.
-Of the eleven participants who needed to configure their connection, eight (P1, P5, P6, P7, P8, P11, P13, P14, P16) chose to connect directly.
-One participant (P12) clicks configure, but answers the questions in such a way that it creates a direct connection.
-Only one (P15) chose to configure when they needed to.
-\item {\bfseries Proof of Challenge 2:} Five participants were placed in a censored environment which did not block Tor.
-Three of the five (P3, P4, P10) configured a bridge for their connection.
-Of the other two, one participant (P2) was convinced that configuring a bridge was the correct course of action, but was intimidated at the thought of doing so and was pleasantly surprised when a direct connection succeeded; only one participant (P9) believed that a direct connection would work.
-\item {\bfseries Proof of Challenge 3:} All three of our participants who failed to circumvent the simulated censorship environment (P14, P15, P16) spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network.
-Out of the five participants who needed to fix their bridge settings, there were only two participants (P5, P6) who eventually were able to figure out that their bridge settings needed to be adjusted.
-\item {\bfseries Proof of Challenge 4:} One participant (P14) tried the same configuration seven times, even though those settings failed each time.
-Another participant (P12) tries the same configuration three times, and only manages to connect through a technical artifact of the experiment even though that should not have worked.
-Both of these participants emphasized that they did not know what they should be doing.
-Other participants' interview responses also indicate a lack of feedback after failure cases (P8, P15, P16).
-\end{itemize}
-
-The above challenges stemmed from these observations:
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Observation 1: Users lack a mental model of how censorship works.} For instance, our participants did not know the difference between a bridge and a proxy or a censored website versus censored Tor relays.
-We suspect that this is the result of an inaccurate mental model of how the Internet works.
-It would be unreasonable to assume that users should know this information, but some of this may be required to make a correct decision in the current interface.
-\item {\bfseries Observation 2: The interface flow does not guide users down the ideal path.} Much of the real estate on bridge configuration is used for the ``custom bridges'' option, which is rarely used.
-The interface instructs users to check out Internet settings to see if they would require a proxy, but it turns out that people are not skilled at doing so.
-Because the interface redirects users to the proxy screen after failing to make a connection, most of our participants tried configuring a proxy after a connection had failed due to an assumption that the proxy was the reason for the failure.
-In reality, there was no proxy setup required for any simulated censorship environment in our experiment and participants should have configured a bridge.
-\item {\bfseries Observation 3: There is little constructive feedback during
-    failure cases.} When a connection seems to not work, our participants were
-    unsure whether they needed to wait longer, or if they should try the
-    connection with the same configuration again. Both of these are viable
-    strategies, depending on the situation. Although there are certain error
-    messages which were helpful, most of the error messages were technical and
-    not understood by our participants (Figure \ref{fig:error}). The interface
-    does not give clear directions on what participants should do next if a
-    connection fails. 
-\end{itemize}
-
-Although we cannot comment on whether the challenges mentioned above will be
-exactly representative of the Tor user population, it is fair to claim that some
-Tor users will encounter them while configuring Tor. Our observations are
-grounded in user interaction -- specifically user mental modes, UI flow, and
-failure design -- giving us high confidence that addressing these observations
-will make a noticeable impact on the usability of the Tor configuration dialog
-for censorship circumvention.
-
-\section{Design}
-Based on the feedback and the insights from our qualitative interface evaluation,
- we designed improvements to the launcher interface. This section
-discusses design considerations we employed and corresponding justifications. \\
-
-\noindent {\bfseries Automation}
-One common piece of feedback from experts and novices alike was that the
-connection process could be simplified with automation. At first glance, many
-decisions currently made by the user could be automated. For example, bridge
-selection needs to happen only if a regular connection failed, and bridges could
-be tried automatically until one succeeds. However, there are security
-considerations that make this solution problematic. If the launcher starts by
-trying to make unobscured connections to publicly listed relays, detection is
-trivial in a country that logs Internet traffic, potentially resulting in
-repercussions for citizens. Furthermore, users may be turned off by the
-lack of transparency in the connection process.
-
-However, other elements of the process can be automated without adverse effects.
-For example, local proxy settings can be imported from other browsers on the
-machine by looking for settings in well-known locations on the filesystem. Automatically
-detecting the need for a proxy and importing the proxy settings required would save
-our participants from a task they do not have the background to easily complete. 
-Since this piece of automation offers a significant increase in usability for our users
-(addressing our most common failure case) with no apparent risks, we have incorporated it
-into our design (Figure \ref{fig:redesign-proxy}). \\
-
-\begin{figure}[t]
-\label{fig:redesign-proxy}
-  \centering
-    \includegraphics[width=0.5\textwidth]{redesign-proxy.png}
-    \caption{the proxy configuration screen, with an option to automatically
-        ``Import from another browser''}
-\end{figure}
-
-\noindent {\bfseries Building a better mental model}
-Participants' lack of a mental model of censorship led them to believe their
-Tor connection was censored when, in reality, it was not. It furthermore contributed
-to their confusion between bridges and proxies. Our design directly addresses
-these issues.
-
-Potentially ambiguous text (i.e., referring to censorship) is removed in favor
-of stating the underlying options, as it was shown to confuse our participants.
-Previously, separate screens with binary options (Do you need a proxy? Yes/No) 
-were provided to help users decide if they needed a bridge or proxy.
-We have removed these screens
-because our participants did not understand how to answer them correctly.
-
-All information about bridges is now contained on one
-screen in the interface, giving the user the full context of their decision.
-The same is done with proxy settings.
-The recommended option (choosing no bridge and no proxy) is now the default on
-the respective configuration screens (Figure \ref{fig:redesign-noproxy}).
-This results in a more streamlined interface with fewer windows
-and fewer clicks required for our participants. \\
-
-\begin{figure}[t]
-\label{fig:redesign-noproxy}
-  \centering
-    \includegraphics[width=0.5\textwidth]{redesign-noproxy.png}
-    \caption{The default option is now to ``Proceed without proxy settings.''}
-\end{figure}
-
-\noindent {\bfseries Clarifying paths through the interface}
-Many users struggled because the workflow implicitly suggested by the interface
-didn't match the ideal path: crucial steps to follow were unclear or obscured,
-while undue prominence was given to comparatively less important elements.
-Our new design inverts this trend, focusing attention on the interface elements
-that are more important, or more generally applicable.
-
-A clear example of this is the ``Connect'' button on the first screen
-(Figure \ref{fig:redesign-firstscreen}), which has
-increased in size and become green, making it more prominent as the recommended
-option. We believe that this will help the majority of Tor users. 
-Although some of our participants in environments had chosen to connect
-directly when they needed to configure,
-the majority of censorship today can be circumvented with a direct connection. 
-A similar aesthetic applies to the connect button seen after custom
-configuration.
-
-\begin{figure}[t]
-\label{fig:redesign-firstscreen}
-  \centering
-    \includegraphics[width=0.5\textwidth]{redesign-firstscreen.png}
-    \caption{the initial connection screen. Note the prominence given to the
-    ``Connect'' button.}
-\end{figure}
-
-To help lessen the cognitive load and use a proportionate amount of space,
-recommended options are selected by default, and rarely used
-elements are deemphasized.
-The help button on the bridge configuration screen
-has been emphasized to be bigger, since it is a helpful option which people rarely
-clicked. To discourage our users from using an advanced setting
-that should only be used in very rare circumstances,
-we have now incorporated the custom bridge configuration in the dropdown menu
-(Figure \ref{fig:redesign-bridges});
-it previously took up a significant portion of the bridge configuration screen.
-
-\begin{figure}[t]
-\label{fig:redesign-bridges}
-  \centering
-    \includegraphics[width=0.5\textwidth]{redesign-bridges.png}
-    \caption{the bridge selection screen, with the option to ``Add Custom
-    Bridge''}
-\label{fig:redesign-bridges}
-\end{figure}
-
-A progress indicator at the top of the window indicates various steps
-for configuring a connection. In addition to communicating what the various 
-steps of configuration are from the beginning, this indicator also serves to clarify the independence of
-bridges and proxies, which need to be configured separately.
-
-After a failure, the users are
-returned to the first step of the process -- the bridge configuration -- since this
-is usually the cause for configuration issues. Previously,
-the user had to manually click to go backward in the dialog to configure bridges.
-In the rare event that the proxy is the issue for the connection setting, the user
-will be directed to the proxy page naturally through the flow of the UI. \\
-
-\noindent {\bfseries Designing for failure cases}
-
-Users were led astray by interface elements that were unhelpful or
-misleading if the program encountered connection problems. Our design seeks to
-prevent such confusion by anticipating failures and providing specific instructions
-for our participants on their next steps.
-
-The progress bar in the connection window was often unresponsive
-and did not offer guidance for how long users were supposed to wait.
-The connection process can take about two minutes --- long enough that users may
-think that the connection has failed, even when it is making slow and invisible progress. 
-We added a countdown timer to indicate that a long wait time does
-not indicate failure. We also add visual indicators
-for major milestones in the connection, providing better feedback about what has
-been accomplished so far. Additionally, the current status of the connection
-attempt (drawn from the log) is displayed, to aid in understanding and
-debugging.
-
-\begin{figure}[t]
-\label{fig:redesign-waiting}
-  \centering
-    \includegraphics[width=0.5\textwidth]{redesign-waiting.png}
-    \caption{the new connection screen}
-\end{figure}
-
-In the event that the connection attempt fails, messages from the log are
-displayed, along with suggestions about what to do next (e.g., try
-another bridge). To make the potential options clearer, the new failure screen
-includes a separate button for common next steps which are able to resolve
-a failed connection, which are to retry without changing settings and to reconfigure 
-the connection. \\
-
-\begin{figure}[t]
-\label{fig:redesign-failure}
-  \centering
-    \includegraphics[width=0.5\textwidth]{redesign-failure.png}
-    \caption{the screen displayed when a connection failed}
-\end{figure}
-
-\noindent {\bfseries Additional changes}
-In addition to the changes above, we have simplified flows,
-reduced text, and reduced visual clutter.
-We believe these changes are cohesive with our design
-and will be beneficial for the user.\\
-
-\section{Quantitative Testing}
-{\color {red} TODO}
-
-\section{Evaluation}
-{\color {red} TODO, write about what worked, what didn't, and what we recommend.}
-
 \section{Discussion}
-{\color {red} 
 Talk about how the design was a conservative version. And why the conservative choices were made. For at-risk users, maintainability, etc.
@@
 \end{itemize}
-}
-
-\section{Future Work}
-
-The work summarized is only a part of the process of improving the Tor configuration
-dialog for more usable censorship circumvention. We plan to continue this work by:
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Testing our design with a small-scale qualitative study.} It is
-    critical to get in-depth data from users through one-on-one interviews and
-    open-ended feedback. For this reason, we plan to run a small-scale
-    qualitative study similar to the one we have run for the old interface. We
-    plan to run these studies at the start of Spring 2016.
-\item {\bfseries Testing our design with a large-scale quantitative study.} To
-    test our design alongside the old interface, we will recruit a large number
-    of participants to try out both designs. The purpose of this is to get
-    statistically significant results on whether our design choices have helped
-    users to configure successfully. We plan to run these studies at the start
-    of Spring 2016.
-\item {\bfseries Analyzing which design changes have made a positive impact.} We plan to instrument our interfaces to capture all clicks, window transitions, and other events so that we can analyze if our designs have helped our users connect faster and or with less effort.
-\item {\bfseries Push some changes.} We have the input and support of Tor developers
-to improve this interface. Any improvements will be incorporated into the Tor Browser.
-\end{itemize}
-
-\noindent {\bfseries Quantitative experiment analyses} We want to show a statistically significant improvement in user effort for a successful connection.
-We believe that this can be measured with various factors such as time, clicks, etc.
-For this reason, we will specifically be collecting data about: the total number of participants who have successfully circumvented censorship, the number of connection attempts for a successful connection, how much time participants spent configuring before a successful connection, the number of windows traversed in the UI, the number of clicks made, if bridge and proxy configuration interfered with each other, and how many people try repeat configuration settings.
-
-One exciting analysis we will perform is to build a Markov model of the UI flow chart (Figure \ref{fig:markov} shows a simplified illustration).
-We believe that this will be helpful in communicating participant behavior in aggregate since it will show the change in the UI flow structure, as well as how participants decisions have changed (e.g., in the old interface, a participant in a censorship environment which does not block Tor has a 0.4 chance of choosing ``connect,'' whereas in the new interface, the probability is 0.6).
-We have other visualizations in mind to display all participants' window traversal at a glance (Figure \ref{fig:bar} shows a simplified illustration), as well as other analyses.\\
-
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{markov.png}
-    \caption{An illustration on a planned analysis using the quantitative survey data.
-This illustration shows two possible user interfaces and uses a Markov model to reflect the aggregate user behavior.
-We believe that this will be an concrete way to predict user behaviors, which is valuable feedback for if the interface is guiding users in a desired UI path.}
-\label{fig:markov}
-\end{figure}
-
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{screen-bar.png}
-    \caption{An illustration of how we plan to visualize large-scale UI flows as a succinct way to display all participants' window traversal.
-We plan to color code the screens so that the reader can see trends at a glance, such as how the UI path for participants in a mild censorship environment with the old design compare to the UI flow for the participants in a mild censorship environment with a new design.
-It also can communicate how much work was required of a user to configure a connection.}
-\label{fig:bar}
-\end{figure}
-
-\noindent {\bfseries Deciding which design choices to incorporate} We have discussed how we will decide if a design change is beneficial enough to incorporate.
-Intuitively, changes which lead to higher success rates, faster time to completion, less clicking, less window traversal, and positive changes in behavior will be incorporated.
-If they have the converse of these effects, those changes will not be incorporated.
-However, when changes do result in a statistically significant improvement or challenge, we have chosen to incorporate changes if they provide cohesion with other changes which do have positive effects.
-If changes seem to be uncorrelated to positive effects and do not show statistical significance, we will not incorporate those changes.
-\\
-
-\noindent {\bfseries s} We will help incorporate changes into the Tor Browser.
-Since we have developer support, it is not expected that we implement our changes, but we will advise them on any changes that they make.
-We hope that our work is able to help people more easily access the free Internet.
 
 \section{Resources}
-\noindent Our online artifacts of the work done during this class, Fall 2015,
-are below: 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item \href{https://github.com/lindanlee/circumvention-ux-tor}{github repo with experiment plans, code, videos, interviews, and much more}
-\item \href{https://marvelapp.com/15a2294}{a clickable prototype of our interface redesign}
-\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/videos}{qualitative interface evaluation videos}
-\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/sessions/pre/participant-summaries.txt}{summaries of qualitative interface evaluation videos}
-\item \href{https://github.com/lindanlee/circumvention-ux-tor/tree/master/sessions/pre/notes}{qualitative interface evaluation interview notes}
-\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/setup-environment}{experimental setup code: firewall and screen capture} 
-\item \href{https://github.com/lindanlee/circumvention-ux-tor/blob/master/setup/takedown-environment}{experimental takedown code: saving files and cleanup} 
-\end{itemize}
-
-% from anonymity study
-%Our online artifacts of study of Tor as an anonymity tool, such as 
-%the summary, results, and resulting browser changes are below:
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item \href{https://trac.torproject.org/projects/tor/wiki/org/meetings/2015UXsprint}{blog post summary}
-%\item \href{https://blog.torproject.org/blog/ux-sprint-2015-wrapup}{changes made to Tor}
-%\item \href{https://people.torproject.org/~dcf/uxsprint2015/}{subtitled screen videos}
-%\end{itemize}
+{\color {red} appropriate links here.}
 
 \bibliographystyle{abbrv}
-\bibliography{circumvention-experiment.bib}
+\bibliography{pets-2017-paper.bib}
 
 \appendix
-\section*{A1: Configuration Interface Windows}
+\section*{Old Configuration Interface}
+\section*{New Configuration Interface}
 
-\begin{figure}[h]
-  \centering
-    \includegraphics[width=0.5\textwidth]{window1.png}
-    \caption{Window 1: the first configuration window shown to the user upon
-    starting Tor Browser for the first time. Note that the interface's default choice
-    is to connect directly through Tor. The interface also gives additional guidance
-    to help users answer this question.}
-\label{fig:window1}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-    \includegraphics[width=0.5\textwidth]{window2.png}
-    \caption{Window 2: This is the next window shown if a user chooses to configure 
-    bridges or proxies. Note that the interface's default answer is ``No,'' 
-    and also advises users to click ``No'' if they are unsure. The user can navigate to the 
-    previous window by clicking ``Go Back,'' and continue configuration by clicking 
-    ``Continue.''}
-\label{fig:window2}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-    \includegraphics[width=0.5\textwidth]{window3.png}
-    \caption{Window 3: This is the window shown when a user answers that a bridge 
-    is required for the connection. Note that the default answer is to connect with a hard-
-    coded bridge rather than to enter in a custom bridge, and to use the recommended 
-    transport (obfs3). A possible source of confusion is that that the user is asked to choose 
-    a transport type, when the interface clearly is asking for bridge configuration. The user 
-    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
-    by clicking  ``Continue.''}
-\label{fig:window3}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-    \includegraphics[width=0.5\textwidth]{window4.png}
-    \caption{Window 4: This is the window shown after a user has deemed that a bridge
-    is not required for the connection, or when the bridge configuration settings have been 
-    chosen. Note that the default answer to if the user requires a proxy is ``No.'' Additionally,
-    there is text to guide the users on how to answer this question. The user 
-    can navigate to the previous window by clicking ``Go Back,'' and continue configuration 
-    by clicking  ``Continue.''}
-\label{fig:window4}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-    \includegraphics[width=0.5\textwidth]{window5.png}
-    \caption{Window 5: This is the window shown when a user answers that a proxy is 
-    required for the connection. Note that there are no default values in the answers, 
-    where there were for bridges. Additionally, since this is the last window in the configuration
-    interface, the options to navigate to other windows are to simply ``go back,'' or to 
-    connect to the Tor Network.}
-\label{fig:window5}
-\end{figure}
 \end{document}

### 2016-03-15 pets2017-paper/pets2017-paper.tex
add paper thoughts.

@@
 
-\title{An Inclusive, Usable Redesign of the Tor Configuration Launcher}
+%what I really want to say is that the interesting aspect of this usable design is that we had to 
+%account for people who wouldn't need to use this launcher at all and also for at-risk users.
+%... but in one catchy title. I can't think of one.
+\title{Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher}
 \numberofauthors{1}
@@
 \section{Introduction}
+Introduce what Tor is, and what the configuration interface does in the Tor Browser Bundle.
+Explain the story of how it began as an anonymity tool, but it has since changed to become a censorship circumvention tool.
+Give statistics of how many people use it (although we can't say how many for what reason exactly), and interesting trends, such as a spike in use around election times or some big political event.
+
+Explain the state of censorship circumvention today, and what governments do to Tor (block it, etc.). Mention the current consequences of people if they try to connect to Tor.
+
+Then drive home why it is important for the interface to be usable.
+And that there have been previous work on Tor Browser, but not any previous work done for its usability as a censorship circumvention tool, or anything about the Tor configuration launcher.
+Tor is also an anonymity tool which takes no metrics about how the tor launcher is used.
+
+A couple-sentence summary of our experiment, which had three phases of qualitative testing, iterative design, and quantitative testing.
+We got a new design that does a, b, c, which helped our participant through statistic x, y, z.
+Mention that some changes have already been made to the launcher as a result of this study and that this will be incorporated into the tor browser bundle soon.
+
+\section{The Configuration Interface}
+
+\subsection{What it's trying to do}
+\subsection{Why certain decisions were made}
+\subsection{Observations} 
+Mention here that there are people who do not need to use the interface at all, and there are people who are at risk.
+
 We need to design for at least three types of users: users who use Tor for anonymity, users who use Tor for censorship circumvention who are not at risk, users who use Tor for censorship circumvention who are at risk.
@@
 
-\section{The Configuration Interface}
+\subsection{The ideal user path} 
+Write here what each person should do.
+Casual browsers, anonymity users, censorship circumvention people in various censorship situations, and people who are at risk.
+Mention how the interface would change if it were to only cater to these people one at a time, and how this is merged as a whole.
 
 \section{Methodology}
+Have a figure here which shows the whole process.
+The whole pipeline is problem identification, [qualitative user study, iterative redesign, quantitative study] integration, validation.
+The part in brackets is part of our study, but we have the whole process in mind.
 
@@
 \subsection{Logistics} 
-{\bfseries Simulated censorship environments}
+{\bfseries Simulated Censorship Environments}
+write pseudocode for simulating censorship environments!
+have a figure of: ie e1: block websites, e2: block websites and block all public Tor relays, e3: block websites, public tor relays, hardcoded tor relays in dialog.
 {\bfseries Online Tasks}
+{\bfseries Recruitment and Payment}
 
@@
 \subsection{Design}
+
+Design Goals: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item {\bfseries Accessible:} Simpler words for non english speakers, centered text for non western users.
+\item {\bfseries Gives advice:} Tell users what they should ideally do. 
+\item {\bfseries Small cognitive load:} Less windows, less clicks required, less time to completion. 
+\item {\bfseries Provides feedback:} Roadmap bar, summary screen, progress bar, what to do on error message. 
+\end{itemize}
+
 \subsection{Validation} 
@@
 \section{Future Work}
-In addition to merging our code with the source code:
+{\bfseries Merging Code} In addition to merging our code with the source code:
 
+{\bfseries Finishing Touches} 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
@@
 \item {\bfseries Additional user feedback.} Animation in the progress window. 
+\item {\bfseries Stylization.} Comply with design style guides, if any. 
 \end{itemize}
+
+{\bfseries Measuring Impact} Tor metrics to see if this is helping at the large scale, and for future user study work in general.
 
@@
 I would argue that the benefit is higher than the risk.
+\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
+The amount of people who use proxies is low, but then ...
+this would not give users control in the beginning of the configuration process.
+\item{\bfseries Help the at-risk users.} There are people who would benefit from, on the first attempt, connecting with a meek bridge or custom bridge, without trying a vanilla tor connection or the recommended bridge in the dialog.
+Currently, we guide these people to the correct decision, but after trying the default bridge first.
+Helping these users to make a connection safely without ever being logged as connecting to Tor would be a benefit, but might be a case of overfitting to these types of users.
+A majority of users should not use a meek bridge or custom bridge, so it would be unideal to lead all users to this decision.
+\end{itemize}
+
+Alternative ideas: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item{\bfseries Automate the entire configuration process.} Seriously, this can help load balancing, and all sorts of technicalities, and wouldn't harm most of our users.
+Most users do not configure that well, anyway and would make the same mistakes.
 \item {\bfseries Auto-configure after connect.} After a person has already clicked connect and the connection was unsuccessful, they have already been logged.
@@
 This would greatly save our users a lot of headache.
-\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
-The amount of people who use proxies is low, but then ...
-this would not give users control in the beginning of the configuration process.
 \item{\bfseries Ask about the risk.} Rather than having the configuration dialog be manual by default, just ask if the users are at risk if the process was automated.

### 2016-03-18 cs261-paper/circumvention-experiment.tex
paper outline

--- 2015-12-11 paper/circumvention-experiment.tex
@@
-\documentclass{template}
+x\documentclass{template}
 \usepackage{color}

### 2016-03-18 pets2017-paper/pets2017-paper.tex
paper outline

--- 2016-03-11 pets2017-paper/pets2017-paper.tex
@@
 \begin{abstract}
-
+{\color {red} 
+stuff here
+}
 \end{abstract}
@@
 \section{Introduction}
-We need to design for at least three types of users: users who use Tor for anonymity, users who use Tor for censorship circumvention who are not at risk, users who use Tor for censorship circumvention who are at risk.
+{\color {red} 
+Introduce what Tor is, and what the configuration interface does in the Tor Browser Bundle.
+Explain the story of how it began as an anonymity tool, but it has since changed to become a censorship circumvention tool.
+Give statistics of how many people use it (although we can't say how many for what reason exactly), and interesting trends, such as a spike in use around election times or some big political event.
+}
 
-What makes this design unique is that we have to handle two use cases (anonymity and censorship circumvention) and that there are at-risk users we need to consider.
-We can't lean toward helping them configure their connection all the time because a lot of people use Tor for anonymity or casual browsing, and to do this would be over-fitting to the censorship evasion population (and technically, is a burden on bridges).
-We also cannot automate anything, unless we want to put users at risk.
-Also, for maintainability, we would ideally love it if users could just choose their bridge settings, since any automation or device is bound to be different from country to country and also will become out of date sooner or later.
+This study aims to understand of what is confusing about the configuration process and what find changes make the process easier.
+Our study consists of three stages.
+User interactions with the current interface in various censorship environments generated the problems we address in the study.
+User feedback and observations of users steered the design process for an improved configuration interface.
+User metrics, such as success rate and time to completion, measured how well the interfaces served their purpose.
 
-\section{The Configuration Interface}
+{\color {red}
+Explain the state of censorship circumvention today, and what governments do to Tor (block it, etc.).
+Mention the current consequences of people if they try to connect to Tor.
+Then drive home why it is important for the interface to be usable.
+And that there have been previous work on Tor Browser, but not any previous work done for its usability as a censorship circumvention tool.
+}
 
-\section{Methodology}
+Currently, x\% of users fail and with the current interface for reasons a, b, and c.
+Of those that do succeed, the average time to completion is y.
+This can lead to a bad user experience, users quitting Tor, or causing high-risk users to make mistakes.
+With the new design, only x'\% of users fail to configure successfully and the average time to completion is y'.
+Tor has already implemented some of these changes.
 
-\subsection{Evaluation}
-%Some references to keep in mind when explaining:
-%\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
-%\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
-%\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
+\section{Background} 
+\subsection{The Interface} 
+{\color {red} storyboard of the old interface
 
-\subsection{Design}
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item No bridge, no proxy
+    \item with bridge, no proxy
+    \item No bridge, with proxy
+    \item With bridge, with proxy
+\end{enumerate}
+}
+\subsection{Kinds of Users} 
+\subsection{Network Components} 
+\subsection{Censorship Environments}
 
-\subsection{Testing}
-{\color {red} TODO}
+\section{Goals/Evaluation Criteria} 
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
+    \item {\bfseries Time to Completion} Time to complete, east of user for the average user. 
+    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
+\end{enumerate}
 
-\subsection{Logistics} 
-{\bfseries Simulated censorship environments}
-{\bfseries Online Tasks}
+\section{Qualitative Analysis of the Existing Interface (Study 1)}
+\subsection{Motivation} 
+\subsection{Methodology} 
+{\color {red} 
+What to talk about in this section: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item experiment design
+\item censorship environments
+\item user tasks
+\item user screening and recruitment
+\item payment
+\item no risks to user, irb approved
+\end{itemize} 
+}
 
-\section{Results}
+\subsection{Results} 
+{\color {red}
+We noticed four common challenges:
 
-\subsection{Evaluation} 
-\subsection{Design} 
-\subsection{Validation} 
-\subsection{Recommendations} 
-TODO, write about what worked, what didn't, and what we recommend.
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
+As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
+\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
+Participants knew that they were censored to some degree since we had simulated censorship of websites.
+However, bridges are only necessary when the government has taken active steps to censor Tor itself.
+\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
+The problem is not necessarily where the interface directs users, misguiding them.
+It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
+\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
+The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+\end{itemize}
+}
+
+\section{Redesigning the Configuration Interface}
+
+{\color {red}
+
+Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.
+
+{\bfseries What it's trying to do}
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item separate people who use Tor for anonymity and for censorship 
+    \item if anonymity, to connect people directly
+    \item if censorship, guide users to make the correct configuration
+    \item minimize network traces to protect high-risk users
+\end{enumerate}
+
+{\bfseries Why certain decisions were made}
+{\color {red} 
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item {\bfseries Asking the User} asking users about their situation rather than hardcoding or probing
+    \item {\bfseries No Explicit Advice} no suggestion of what to try and in what order
+    \item {\bfseries No Automation} manual configuration of bridges and proxies required
+    \item {\bfseries Optimizing for the Average Case} connect, bridges before proxy
+\end{enumerate}
+}
+
+What to talk about in this section: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item Talk about the process of translating observations and feedback into feature changes. 
+\item Polishing the interface by working with a designer, using heuristics, and using technical information. 
+\item Iterative design and feedback cycle. 
+\item How we made a functional, instrumented prototype (forking from the interface repo on github and hacking on it) and instrumented the old prototype. 
+\end{itemize}
+
+Talk about how the design as a conservative design. And why the conservative choices were made. For at-risk users, maintainability, etc.
+}
+
+\section{Quantitative Analysis of the Interfaces (Study 2)}
+
+\subsection{Motivation}
+
+\subsection{Methodology} 
+{\color {red} 
+What to talk about in this section: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item experiment design
+\item how we chose our metrics
+\item how we collected our metrics
+\end{itemize} 
+}
+
+\subsection{Results}
 
 \section{Future Work} 
-In addition to merging our code with the source code:
+{\color {red}
+\noindent {\bfseries Changing the Current Interface} merge, push.
 
+\noindent{\bfseries Finishing Touches} 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
@@
 \item {\bfseries Additional user feedback.} Animation in the progress window. 
+\item {\bfseries Stylization.} Comply with design style guides, if any. 
 \end{itemize}
 
+\noindent{\bfseries Measuring Impact} Tor metrics to see if this is helping at the large scale, and for future user study work in general. 
+}
+
 \section{Discussion}
-Talk about how the design was a conservative version. And why the conservative choices were made. For at-risk users, maintainability, etc.
 
-Additional potential changes that could be made to the browser: 
+Additional changes that could be made: 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
@@
 But communicating this may put some users at risk.
-I would argue that the benefit is higher than the risk.
+Based on the results, is the benefit greater than the risk?
+\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
+The amount of people who use proxies is low, but then ...
+this would not give users control in the beginning of the configuration process.
+\item{\bfseries Help the at-risk users.} There are people who would benefit from, on the first attempt, connecting with a meek bridge or custom bridge, without trying a vanilla tor connection or the recommended bridge in the dialog.
+Currently, we guide these people to the correct decision, but after trying the default bridge first.
+Helping these users to make a connection safely without ever being logged as connecting to Tor would be a benefit, but might be a case of overfitting to these types of users.
+A majority of users should not use a meek bridge or custom bridge, so it would be unideal to lead all users to this decision.
+\end{itemize}
+
+Alternative approaches to interacting with the user: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item{\bfseries Automate the entire configuration process.} Seriously, this can help load balancing, and all sorts of technicalities, and wouldn't harm most of our users.
+Most users do not configure that well, anyway and would make the same mistakes.
 \item {\bfseries Auto-configure after connect.} After a person has already clicked connect and the connection was unsuccessful, they have already been logged.
@@
 
-\section{Resources}
-{\color {red} appropriate links here.}
+\section{Related Work}
+
+\section {Acknowledgments}
+
+\section{Conclusion}
 
@@
 \appendix
-\section*{Old Configuration Interface}
-\section*{New Configuration Interface}
+\section{TODO}
+{\color {red} 
+Include: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item participant worksheet
+\item participant survey
+\item participant recruitment prompt
+\item any instructions we gave participants
+\end{itemize} 
+}
 

### 2016-03-23 pets2017-paper/pets2017-paper.tex
We should ack Cecile for helping review UIs.
Note changes in bridges between 5.0.3 and now.

@@
 
+% $ grep 'default_bridge\.' tor-browser_en-US/Browser/TorBrowser/Data/Browser/profile.default/preferences/extension-overrides.js | awk -F. '{print $4}' | sort | uniq -c
+%       5 flashproxy
+%       6 fte
+%       2 fte-ipv6
+%       1 meek-amazon
+%       1 meek-azure
+%       1 meek-google
+%       5 obfs3
+%       3 obfs4
+%       2 scramblesuit
+% The 5 flashproxy lines are effectively 1.
+Tor Browser 5.0.3 came configured with default bridges:
+1 flashproxy;
+8 fte;
+3 meek;
+5 obfs3;
+3 obfs4;
+and 2 scramblesuit.
+In the time since 5.0.3 was released and our later experiment,
+two of the obfs4 bridges and one of the scramblesuit bridges stopped running.
+% These are the bridges that stopped running. schanenlied is known and intentional.
+% mercurius4 is probably not running by accident.
+% schanenlied:
+% obfs4 178.209.52.110:443 67E72FF33D7D41BF11C569646A0A7B4B188340DF cert=Z+cv8z19Qb8RxWlkagp7SxiDQN++b7D2Tntowhf+j4D15/kLuj3EoSSGvuREGPc3h60Ofw iat-mode=0
+% mercurius4:
+% obfs4 104.131.108.182:56880 EF577C30B9F788B0E1801CF7E433B3B77792B77A cert=0SFhfDQrKjUJP8Qq6wrwSICEPf3Vl/nJRsYxWbg3QRoSqhl2EB78MPS2lQxbXY4EW1wwXA iat-mode=0
+% ???:
+% scramblesuit 188.226.213.208:54278 AA5A86C1490296EF4FACA946CC5A182FCD1C5B1E password=MD2VRP7WXAMSG7MKIGMHI4CB4BMSNO7T
+This left enough bridges that participants in the later experiment would be able to connect
+under the same circumstances as those in the earlier experiment.
+We did not modify the set of bridges between the experiments,
+with one exception.
+One of the meek bridges changed its bridge identity fingerprint;
+Tor clients check the identity fingerprint and refuse to connect
+if it does not match.
+Therefore we patched the correct fingerprint in the later experiment.
+
 \subsection{Results}
@@
 
+% Cecile Basnage for review of the UI of circumvention tools.
+
 \section{Conclusion}

### 2016-03-28 pets2017-paper/pets2017-paper.tex
Found the history of 188.226.213.208:54278 bridge deletion.
setup and startup script has env and version

@@
     \item {\bfseries Task Completion} Almost all can successfully connect to Tor
-    \item {\bfseries Time to Completion} Time to complete, east of user for the average user. 
+    \item {\bfseries Time to Completion} Time to completion. 
     \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
@@
 \subsection{Methodology} 
-{\color {red} 
-What to talk about in this section: 
+\subsubsection{Simulated censorship environments}
+We simulated three censorship environments for our experiment.
+These reproducible, stable environments are informed by our experience 
+with pluggable transports and knowledge of commonly seen censorship 
+techniques. Their goal in our user study is not to replicate the network 
+environment in any particular country, but to require our participants to 
+configure Tor Browser in distinct configurations.
+
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item experiment design
-\item censorship environments
-\item user tasks
-\item user screening and recruitment
-\item payment
-\item no risks to user, irb approved
+\item {\bfseries Mild censorship} 
+(Representative of countries such as France and Australia.)
+Certain domains are blocked. Reaching these 
+domains requires a censorship circumvention 
+tool. The default option to ``connect'' to the Tor network 
+directly will circumvent this censor. Additional correct
+bridge or proxy configurations are optional.
+
+\item {\bfseries Intermediate censorship} 
+(Representative of countries such as Tunisia.)
+Certain domains are blocked. Censorship circumvention
+tools such as Tor are blocked. Since all public Tor
+relay nodes are blocked, the default option to ``connect'' to the Tor network
+directly will fail. Any choice of a hard-coded bridge
+or a valid non-public bridge will circumvent this censor.  
+Additional correct proxy configuration is optional.
+
+\item {\bfseries Comprehensive censorship} 
+(Representative of countries such as China and Syria.)
+Certain domains are blocked. Censorship circumvention tools
+are thoroughly blocked. Tor is blocked by blocking all public
+Tor relay nodes, and the censor has examined source code to block
+all hard-coded bridge relays in the configuration interface. The default option
+to ``connect'' to the Tor network directly will fail. Most bridges will fail,
+but ``meek-amazon,'' ``meek-azure,'' and ``meek-google'' still work.
+This is because domain-fronting requires censors to block entire CDNs to also
+block this transport (which will cause huge collateral blocking damage), making
+it resistant to aggressive censorship environments.
+(See ~\cite{fifield2015blocking} for additional details.)\\
 \end{itemize}
-}
 
-\subsection{Results} 
+\subsubsection{Procedure}
+We conducted a qualitative evaluation of the interface by creating an environment 
+for users to interact with the configuration interface in a censored environment, 
+observing their interactions in real time without interacting with the participants, 
+and following up with interviews about their experiences.
+Using established best practices from the field of user experience research
+(\cite{howmanyusers}), we recruited five users for each censorship environment.
+We pre-screened our participants to have a good mix of gender, age, technical
+background, and familiarity with Tor in each environment.
+
+%Some references to keep in mind when explaining:
+%\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
+%\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
+%\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
+
+The 1-hour, single-participant procedure begins when a participant enters a small 
+room with a single computer, which is equipped with Chrome, Firefox, Internet Explorer, 
+Chrome, and VLC (for screen recording). A participant is firstly informed of 
+the risks of the study and consenting to data collection. If they consent, the 
+experiment begins. The participant is informed that they are in a
+simulated censorship environment, where some websites are blocked. We
+instruct them to visit a sample blocked website and a sample non-blocked website on a
+non-Tor browser of their choice to illustrate the situation.
+
+After illustrating the censorship environment, participants are asked to 
+complete a worksheet that asks to visit one blocked website and one non-blocked website. 
+We chose Wikipedia's featured article of the day as the blocked website and 
+the CNN homepage as our non-blocked website because the familiarity 
+that most users have with these websites makes the browsing task relatively easy, 
+which focuses participants' attention to configuring Tor Browser.
+
+After instructions, researchers stepped out of the room so that there was no interaction
+between the participant and researcher for the rest of the session. Participants' screens 
+were recorded and streamed to another room, where the researchers were able to 
+observe how a participant configured their browser. Participants had an 
+average of 45 minutes to complete their worksheet. 
+At this point, the participants do not know the details of their censorship environment,
+only that they are actively being censored. We believe that this is representative 
+of the mental model of users in censored countries, and therefore chose to simulate 
+this for the experiment. Ultimately, participants needed to configure Tor Browser to 
+circumvent the simulated censorship.
+
+After users completed the browsing tasks or have spent the rest of the time
+trying to configure Tor Browser, we interviewed participants about their experience.
+We asked three standard questions asking about their general experience, 
+confusing interface features, and soliciting feedback for improvements. We followed up
+with specific questions we had for a particular participant from observing their screen. 
+This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').
+
+\subsubsection{Results} 
+%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+%    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
+%    \item {\bfseries Time to Completion} Time to complete, ease of user for the average user. 
+%    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak %that they are using Tor. 
+%\end{enumerate}
+
 {\color {red}
@@
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
-As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
-\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
-Participants knew that they were censored to some degree since we had simulated censorship of websites.
-However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
-The problem is not necessarily where the interface directs users, misguiding them.
-It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
-\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
-The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+\item {\bfseries Challenge 1:} Users don't know how to choose between connecting directly to the Tor network or manually configuring their connection (Figure \ref{fig:window1}).
+The text was unread or not understood by most users.
+When the user read the text, they found no instructions, but were given information to make a decision for themselves, which they did not feel equipped to do.
+\item {\bfseries Challenge 2:} Users feel compelled to set up a bridge, even if they don't need one.
+We believe this is due to the text on the first screen, which refers to a ``censored internee connection'' (Figure \ref{fig:window1}).
+Bridges are only necessary when the government actively censored Tor relays, but participants are not able to determine the difference between a censor that blocks websites and a censor that blocks websites and the Tor network.
+\item {\bfseries Challenge 3:} Users did not know what to do after a failure.
+Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+\item {\bfseries Challenge 4:} Users draw incorrect conclusions after a failed connection.
+The interface passively re-displayed the last window seen before the attempted connection (Figure \ref{fig:window4} or \ref{fig:window5}), regardless of the error.
 \end{itemize}
@@
 % These are the bridges that stopped running. schanenlied is known and intentional.
+% 188.226.213.208 in known and intentional: https://bugs.torproject.org/17318. Maybe
+% it was not even running at the time of 5.0.3.
 % mercurius4 is probably not running by accident.
@@
 % obfs4 104.131.108.182:56880 EF577C30B9F788B0E1801CF7E433B3B77792B77A cert=0SFhfDQrKjUJP8Qq6wrwSICEPf3Vl/nJRsYxWbg3QRoSqhl2EB78MPS2lQxbXY4EW1wwXA iat-mode=0
-% ???:
+% (nickname unknown):
 % scramblesuit 188.226.213.208:54278 AA5A86C1490296EF4FACA946CC5A182FCD1C5B1E password=MD2VRP7WXAMSG7MKIGMHI4CB4BMSNO7T
@@
 
-Additional changes that could be made: 
+If we had more concrete information on the number of high-risk users or users who need to configure a proxy, we would have made additional changes in the prototype.
+Since we lacked this information, the following changes did not make it into our prototype, but are worth discussing.
+Depending on the number of high-risk users or proxy-configuring users, these additional changes may be helpful:
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Tell people to click connect.} On the first screen, there are no instructions for the user on what to do.
-There is a description of what each option means, but there is no guidance on what they should do.
+\item {\bfseries Tell people to click connect.} On the first screen, the user needs to decide to connect or configure.
+Although there is a description of what each option entails and when one may consider using that option, there are no instructions for the user on what to do.
 Ideally, we would people to click connect, and then try the manual configuration if a direct connection fails.
-But communicating this may put some users at risk.
-Based on the results, is the benefit greater than the risk?
+We currently do not communicate this because may put some users at risk.
+However, it is believed that a majority of the users will succeed if they click connect on the first screen, and giving them instructions on what to do can lessen their cognitive load during the configuration process.
 \item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
@@
 
-Alternative approaches to interacting with the user: 
+We took an approach that optimized for the average case user yet was conservative in automation to allow at-risk users to possibly connect without leaking that they use Tor.
+We believe that this is a sound approach to interacting with the user and the one we would recommend personally.
+However, there are alternative approaches to interacting with the user that may be of interest:
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item{\bfseries Automate the entire configuration process.} Seriously, this can help load balancing, and all sorts of technicalities, and wouldn't harm most of our users.
-Most users do not configure that well, anyway and would make the same mistakes.
+\item{\bfseries Automate the entire configuration process.} This sounds like a radical idea, but it really isn't.
+Today, this wouldn't harm most of our users.
+Our study finds that most users do not configure better than we do and would leak that they are using Tor anyway.
 \item {\bfseries Auto-configure after connect.} After a person has already clicked connect and the connection was unsuccessful, they have already been logged.

### 2016-03-29 pets2017-paper/pets2017-paper.tex
edit methodology sections.

@@
 \subsection{Methodology} 
-\subsubsection{Simulated censorship environments}
+\subsubsection{Setup}
+\label{sec:setup}
 We simulated three censorship environments for our experiment.
@@
 \end{itemize}
+
+\subsubsection{Recruitment}
 
@@
 
-\section{Quantitative Analysis of the Interfaces (Study 2)}
+\section{Quantitative Analyses of the Interfaces (Study 2)}
 
@@
 \subsection{Methodology} 
-{\color {red} 
-What to talk about in this section: 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item experiment design
-\item how we chose our metrics
-\item how we collected our metrics
-\end{itemize} 
-}
+\subsubsection{Setup}
+For consistency, we simulated the same three censorship environments from 
+our qualitative user study. Details of the mild, intermediate, and advanced 
+censorship environments and what configurations are necessary for a 
+successful connection can be found in Section \ref{sec:setup}.
+
+\subsubsection{Recruitment}
+\subsubsection{Procedure}
+\subsubsection{Results}
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
add resources to the appendix.

@@
 \appendix
-\section{TODO}
-{\color {red} 
-Include: 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item participant worksheet
-\item participant survey
-\item participant recruitment prompt
-\item any instructions we gave participants
-\end{itemize} 
-}
+\section{Participant Worksheet Text} 
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+For instance, www.torproject.org is blocked.
+Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
+It will fail to load, when you can visit other sites.
+
+To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
+If you can visit wikipedia, then you know that you have successfully circumvented censorship.
+
+\section{Qualitative User Study Prescreening Survey} 
+We are recruiting participants for an in-person research study at the University of California, Berkeley.
+You will need to come in to our lab and perform tasks on a computer for an hour or less.
+You will be compensated \$30 for participating.
+No special knowledge and no technical experience is required.
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
+\item{I am able to provide my own transportation to the University of California, Berkeley campus.}
+\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
+\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
+\item{What is your gender?}
+\item{What is your age?}
+\item{Please select your highest completed (or current) level of education.}
+\item{What is your occupation?} 
+\item{Do you speak any languages other than English fluently?}
+\item{If you have a personal computer, what kind do you use?}
+\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
+\item{How often do you use the following software or features?
+\textit{<answer choices: a grid of radio buttons.
+Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption.
+Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
+\end{enumerate}
+Thank you for filling out this form. You are now done!
+
+\section{Post-Experiment Standard Interview Questions}
+We asked our participants these questions after they were given time to configure Tor Browser.
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\item{Can you talk us through what you did along with what you were thinking at the time?}
+\item{What was most challenging part of connecting?}
+\item{Were there any unfamiliar terms?}
+\item{How did you decide which options to choose?}
+\item{What did you think about using Tor?}
+\item{What is one change you would recommend?} 
+\item{Did you need any additional information?} 
+\end{enumerate}
+
+In addition to these questions, we asked our participants about specific questions based on their observation, usually regarding a specific choice in action, a particular screen they seemed stuck on, and any errors they encountered during the configuration process.
+
+\section{Quantitative User Recruitment Posting}
+We are recruiting up to 40 participants for a user study at UC Berkeley.
+The experiment will involve basic Internet browsing tasks.
+You are not eligible if you have participated in a previous session on 3/23.\\
+
+\indent Payment: \$30 Amazon gift card\\
+\indent Duration: 1 hour \\
+\indent Where: Xlab at Hearst Memorial Gymnasium\\
+
+\textit{<list of sessions>}\\
+
+To be eligible, you must be an adult (18 or older). This is to comply with university policies on research.
+
+If you are interested: 1.
+Email lnl@berkeley.edu with the sessions you are able to attend.
+We will confirm your participation and assign you a session.
+2.
+Come to Xlab at the appointed time for the experiment.
+
+\section{Quantitative User Study Introduction Script} 
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
+
+To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
+If you are able to reach the website, then you know that you have successfully circumvented censorship.
+Fill out the question on the worksheet.
+This isn’t intended to be hard, just write what you see.
+We want to just check you saw the website.
+
+Afterward, we ask you to take a short survey to collect some information about you. The link is also on your worksheet.
+We will give you time to complete this task.
+If you finish early, we ask that you sit at your desk until the remainder of the hour.
+Since we are recording your screen, we ask that you don't do anything personal afterward, like checking your email.
+
+Before you start, do you have any questions about what you are asked to do?
+
+\section{Quantitative User Study Exit Survey} 
+We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.
+
+This survey is part of a research project being conducted by the University of California, Berkeley.
+If you have any questions about your rights or treatment as a research participant in this study, please contact the University of California at Berkeley's Committee for Protection of Human Subjects at 510-642-7461, or email subjects@berkeley.edu.
+If you agree to participate, please click Next below.
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\item{What is your participant ID? (This can be found on the sticker ont he left hand corner of the desk you are currently sitting at.)}
+\item{What is your gender?}
+\item{What is your age?}
+\item{Please select your highest completed (or current) level of education}.
+\item{What is your current occupation?}  
+\end{enumerate}
+
+Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
label sections in appendix and add in qualitative user study introduction script section (it's a bit redundant, since it's the quantitative one but with less text).

@@
 \section{Participant Worksheet Text} 
+\label{participant-worksheet}
 Imagine you live in an oppressive country that censors part of the Internet.
@@
 
+\section{Qualitative User Study Recruitment Posting} 
+We are recruiting participants for an in-person research study at the University of California, Berkeley.
+You will need to come in to our lab and perform tasks on a computer for an hour or less.
+You will be compensated \$30 for participating.
+No special knowledge and no technical experience is required.
+
+If you are interested, fill out the survey at \textit{<survey link>}.
+
 \section{Qualitative User Study Prescreening Survey} 
+\label{qualitative-prescreening}
 We are recruiting participants for an in-person research study at the University of California, Berkeley.
@@
 
+\section{Qualitative User Study Introduction Script} 
+\label{qualitative-script} 
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
+
+To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
+If you are able to reach the website, then you know that you have successfully circumvented censorship.
+Fill out the question on the worksheet.
+This isn’t intended to be hard, just write what you see.
+We want to just check you saw the website.
+
+Before you start, do you have any questions about what you are asked to do?
+
 \section{Post-Experiment Standard Interview Questions}
@@
 \section{Quantitative User Recruitment Posting}
+\label{qualitative-recruitment}
 We are recruiting up to 40 participants for a user study at UC Berkeley.
@@
 \section{Quantitative User Study Introduction Script} 
+\label{quantitative-script} 
 Imagine you live in an oppressive country that censors part of the Internet.
@@
 \section{Quantitative User Study Exit Survey} 
+\label{quantitative-exit-survey}
 We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.

### 2016-03-29 pets2017-paper/pets2017-paper.tex
qualitative recruitment section

@@
 \subsubsection{Recruitment}
+Using established best practices from the field of user experience research
+(\cite{howmanyusers}), we recruited 5 participants for each censorship environment.
+We pre-screened our participants for diversity of gender, age, technical expertise,
+and familiarity with Tor in each simluated censorship environment.
+
+We recruited our users from Craigslist. The recruitment text can be found in 
+Appendix \ref{qualitative-recruitment}. The recruitment posting contained a 
+SurveyGizmo online survey that collected information about our participants.
+The complete prescreening survey can be found in Appendix \ref{qualitative-prescreening}.
+
+We chose our participants based on the pre-screening information to have 
+at least one person who has never heard of Tor, at least one person who has 
+only heard of Tor, and exactly one person who has previously used Tor in each
+environment. We also tried to evenly distribute any participants who had technical
+expertise or used particular security tools throughout the censorship environments.
+
+Out of our 16 participants, ages ranged from {\color {red} TODO}
+(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
+a college education, and the most common jobs included {\color {red} TODO} and
+{\color {red} TODO}. {\color {red} TODO} had heard of Tor previously, 
+and {\color {red} TODO} had used Tor previously. {\color {red} TODO} out of 
+16 did not use any circumvention tools, and no more than {\color {red} TODO} 
+knew any more than {\color {red} TODO} technological terms.
+
+%Some references to keep in mind when explaining:
+%\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
+%\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
+%\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
 
@@
 and following up with interviews about their experiences.
-Using established best practices from the field of user experience research
-(\cite{howmanyusers}), we recruited five users for each censorship environment.
-We pre-screened our participants to have a good mix of gender, age, technical
-background, and familiarity with Tor in each environment.
-
-%Some references to keep in mind when explaining:
-%\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
-%\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
-%\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
 
 The 1-hour, single-participant procedure begins when a participant enters a small 
-room with a single computer, which is equipped with Chrome, Firefox, Internet Explorer, 
+room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
 Chrome, and VLC (for screen recording). A participant is firstly informed of 
 the risks of the study and consenting to data collection. If they consent, the 
-experiment begins. The participant is informed that they are in a
-simulated censorship environment, where some websites are blocked. We
+experiment begins. A researcher informs the participant that they are in a
+simulated censorship environment, where some websites and services are blocked. 
+For the full script of what participants have heard, see Appendix \ref{qualitative-script}. We
 instruct them to visit a sample blocked website and a sample non-blocked website on a

### 2016-03-29 pets2017-paper/pets2017-paper.tex
qualitative introduction

@@
 \section{Qualitative Analysis of the Existing Interface (Study 1)}
-\subsection{Motivation} 
+We performed qualitative research as an exploratory effort to gain an 
+understanding of underlying problems, such as reasons for confusion 
+during the configuration process and motivations for particular choices in 
+configuration. We did this through observing each participant as they 
+interacted with Tor Browser 5.0.3. interface and interviewed them about
+their experience. This study provides insights into particular problems with 
+the current Tor Browser configuration interface, and helps us to design
+a new interface which addresses these problems and gives foundation
+for hypotheses to test in quantitative research.
+
 \subsection{Methodology} 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
quantitative intro

@@
 \section{Quantitative Analyses of the Interfaces (Study 2)}
-
-\subsection{Motivation}
+We performed quantitative research to quantify the existing problems
+and the impact of our redesign by generating numerical data to transform
+into usable statistics. Specifically, we collected all events, transitions, 
+and state for Tor Browser 5.0.3 and the redesigned Tor Browser. Participant
+logs of how they interacted with each of these interfaces are used to both
+quantify the issues we encountered in our previous qualitative 
+study and to examine the differences in success rate, time to completion,
+and configuration choices between the two versions.
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
procedure and recruitment.

@@
 This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').  
+After their interview, participants were informed that the experiment was over and 
+given their payment of \$30.
 
@@
 \subsubsection{Recruitment}
+We recruited 20 users for each censorship environment
+and interface combination, resulting in a total of 120 users. This decision 
+was due to both data analysis considerations (large enough to have good effect size, 
+with a minimum of 20 to be able to assume normal distributions) and funding
+limitations.
+
+We recruited half of our users from Craigslist, and half of our participants from 
+the Xlab participant pool. It is standard for Xlab experiments to be run with Xlab
+participants, who have been verified of their identity and have good attendance
+rate. Although Xlab participants are not limited to UC Berkeley students and staff,
+a majority of the participants are from campus. For this reason, we chose to recruit 
+half of our participants from Craigslist to ensure a diverse set of participants. 
+The recruitment text can be found in Appendix \ref{quantitative-recruitment}.
+
+We chose our participants on who had responded to our listing first and their
+availability for experiment sessions. We collected their demographic information
+with an exit survey that participants took after the experiment.
+
+Out of our {\color {red} TODO} participants, ages ranged from {\color {red} TODO}
+(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
+a college education, and the most common jobs included {\color {red} TODO} and
+{\color {red} TODO}.
+
 \subsubsection{Procedure}
+Similarly to the qualitative experiment, we conducted a quantitative evaluation 
+of the interface by creating an environment  for users to interact with the 
+configuration interface in a censored environment. The focus of this environment 
+was to collect a dataset of metrics to evaluate the two interfaces.
+
+The 1-hour, multi-participant procedure begins when all participants are sitting at their
+respective computers in Xlab. Each computer is equipped with an old or modified version
+of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording). 
+Participants are firstly informed of the risks of the study and consenting to data collection.  At
+this time, participants are given the chance to leave the laboratory if they do not consent to 
+the experiment conditions. When every participant left in the room has turned in their consent
+form, the experiment formally begins. A researcher informs the participants that they are in a
+simulated censorship environment, where some websites and services are blocked. 
+For the full script of what participants have heard, see Appendix \ref{quantitative-script}. We
+instruct them to visit a sample blocked website on a non-Tor browser of their choice to illustrate 
+the situation.
+
+After illustrating the censorship environment, participants are asked to 
+complete a worksheet that asks to visit one blocked website. 
+Similar to the qualitative study, we chose Wikipedia's featured article of the day 
+as the blocked website because the familiarity 
+that most users have with these websites makes the browsing task relatively easy, 
+which focuses participants' attention to configuring Tor Browser.
+
+After instructions, researchers maintained minimal interactions with the participants, 
+only answering logistical questions. Participants had an 
+average of 40 minutes to complete their worksheet. 
+The participants do not know the details of their censorship environment,
+only that they are actively being censored. Participants needed to configure Tor Browser to 
+circumvent the simulated censorship.
+
+After users completed the browsing tasks, they take a short exit survey (Appendix \ref{quantitative-exit-survey})
+collecting their demographics. All users were instructed to sit until the end of the experiment,
+regardless of when they had completed their task. This was to ensure that others were not 
+aware of when other participants had finished their tasks. After the 40 minutes were up, 
+participants were officially informed that their time was up, and were given their payment of 
+\$30.
+
 \subsubsection{Results}
@@
 \section{Quantitative User Recruitment Posting}
-\label{qualitative-recruitment}
+\label{quantitative-recruitment}
 We are recruiting up to 40 participants for a user study at UC Berkeley.
 The experiment will involve basic Internet browsing tasks.
-You are not eligible if you have participated in a previous session on 3/23.\\
+You are not eligible if you have participated in our previous sessions.\\
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
add in participant quotes

@@
 \subsubsection{Results}
+
 %\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
@@
 
-{\color {red}
 We noticed four common challenges:
@@
 \end{itemize}
-}
+
+Relevant participant quotes: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item{{\bfseries P1}:``figuring out if the progress bar wasn't moving because the connection was censored, of if it was just slow''}
+\item{{\bfseries P2}: "I don't know what any of those means (list of bridges), I don't know what that (proxy) means at all."}
+\item{{\bfseries P3}: ``The vocabulary is really challenging, for someone not doing IT work. Good thing I'm really curious. because I was able to use trial and error.''} 
+\item{{\bfseries P4}: ``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.'}
+\item{{\bfseries P5}: ``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
+\item{{\bfseries P6}: ``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}
+\item{{\bfseries P6}: ``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
+\item{{\bfseries P7}: ``The bridge screen was the most challenging.
+It seemed very technical to me.
+I don't know what a bridge is.
+Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}
+\item{{\bfseries P8}: ``I have no clue what's the difference between flashrpoxy, fte, etc.
+I need to know why the built-in ones aren't working.
+And why do I need a custom bridge if there are options built in?''}
+\item{{\bfseries P9}: ``Configure seemed manual, so I clicked connect.''} %c1
+\item{{\bfseries P10}: ``I was censored, so I picked the configure.''} %c1
+\item{{\bfseries P11}: ``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
+\item{{\bfseries P11}: ``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance.''}
+\item{{\bfseries P12}: ``I decided which options to choose by process of elimination with trial and error.'' }
+\item{{\bfseries P13}: ``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy.''}
+\item{{\bfseries P14}: ``The words were confusing.
+I don't really understand computers.
+I don't know what configure means in this setting.
+Hmm, is it going to crash?
+When you see connect, you want to click it because you really want it to connect.''}
+\item{{\bfseries P15}: ``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things.''}
+\item{{\bfseries P15}: ``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
+\item{{\bfseries P16}: ``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
+\item{{\bfseries P16}: ``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}
+\end{itemize}
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
abstract

@@
 \begin{abstract}
-{\color {red} 
-stuff here
-}
+\indent \indent
+Tor has grown beyond its original purpose as an anonymity tool and has 
+since become an important censorship circumvention tool. It is now listed
+as one of the ways that normal people use Tor \cite{whotor}.
+We specifically examine its usability as a censorship circumvention tool,
+an essential facet for adoption and use. We focus our analysis on the connection 
+configuration interface of Tor Browser, as censorship circumvention requires 
+correct transport configurations. We find that the Tor Browser 5.0.3. connection
+configuration interface has a success rate of {\color {red} TODO}\% with the 
+successful users having an average completion time of {\color {red} TODO} minutes. 
+In this paper, we explore common challenges users faced during the configuration
+process and redesign the interface to improve success rate to {\color {red} TODO}\% 
+and average completion time to {\color {red} TODO} minutes.
 \end{abstract}

### 2016-03-29 pets2017-paper/pets2017-paper.tex
make TODOs in red in introduction.

@@
 
-Currently, x\% of users fail and with the current interface for reasons a, b, and c.
-Of those that do succeed, the average time to completion is y.
+Currently, {\color {red} TODO}\% of users fail and with the current interface for reasons {\color {red} TODO}, {\color {red} TODO}, and {\color {red} TODO}.
+Of those that do succeed, the average time to completion is {\color {red} TODO}.
 This can lead to a bad user experience, users quitting Tor, or causing high-risk users to make mistakes.
-With the new design, only x'\% of users fail to configure successfully and the average time to completion is y'.
+With the new design, only {\color {red} TODO}\% of users fail to configure successfully and the average time to completion is {\color {red} TODO}.
 Tor has already implemented some of these changes.

### 2016-03-29 pets2017-paper/pets2017-paper.tex
evaluation criteria section

@@
 \section{Goals/Evaluation Criteria}
+We evaluate the existing and redesigned Tor Browser configuration interface 
+through the empirical evaluation and heuristic evaluation criteria below. The
+empirical evaluation criteria were considered during our qualitative and 
+quantitative user studies, whereas the heuristic evaluation was considered during
+the redesign process.
+
+Since there is risk associated with making an unobfuscated 
+connection with the Tor network, the configuration process is not automated.
+Our empirical evaluation criteria for the Tor Browser configuration
+interface are from common metrics that measure ease of use with a special 
+consideration for high-risk users: 
 \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
@@
 \end{enumerate}
+
+A heuristic evaluation is a rule-based evaluation which leverages standards
+developed over trial and error that have shown to work in the User Interface design 
+community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS}
+and other industry standards to form the following heuristic evaluation criteria: 
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item {\bfseries Visibility of System Status} provide feedback on what the system is doing.
+    \item {\bfseries User Control and Freedom} allow users to override system, supports undo and redo actions. 
+    \item {\bfseries Understandable Language} ~6th grade reading level. 
+    \item {\bfseries Minimal Design} surpressing rarely used information to reduce cognitive load. 
+    \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
+    \item {\bfseries Help and Documentation} provide contextual help and easy access to information. 
+\end{enumerate}
+
+An empirical evaluation of the problems with the existing Tor Browser 
+configuration interface through user observation and interviews can be 
+found in section {\color{red} TODO}. A heuristic evaluation of the existing interface
+and new interface can be found  in section {\color{red} TODO}. We empirically show 
+that the redesigned interface improves completion rate, reduces time to completion, 
+and provides a safe path for at-risk users in section {\color{red} TODO}.
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
notes to self for redesign section

@@
 {\color {red} 
+Talk about the problems from the previous results section, and how we plan to change them,
+along with a heuristic evaluation of the interface.
 
-Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.
+Talk about the process of designing a new interface, and how we tested it with BLUES and the
+Tor Developers.
+
+Talk about the improvements in heuristics from the existing to the redesigned interface, along 
+with hopes of what we want our empirical goals to be (to increase success rate and to minimize
+time to completion, which we do by some proxy detection, giving specific directions, etc.).
+
+...
+
+Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.\\
 

### 2016-03-29 pets2017-paper/pets2017-paper.tex
future work and conclusion self-notes.

@@
 {\color {red}
-\noindent {\bfseries Changing the Current Interface} merge, push.
+Wait to fill this section out until we have finished analyzing the data from the quantitative
+user study experiment. A lot of the future work can be in reference to this. Or, we can even
+talk about what is in the discussion section. ... OR, maybe this section isn't even necessary.\\
+
+\noindent {\bfseries Changing the Current Interface} merge, push. \\
 
@@
 \section{Conclusion} 
+{\color {red} I am a fan of not having long, rambling conclusions. I leave
+that for the discussion section. This section is more of a courtesy to the 
+people who read the abstract, look at the figures, and then read the 
+conclusion. Think of something to tell those people here. Something along
+the lines of a tl;dr summary of the paper.}
 

### 2016-03-31 pets2017-paper/pets2017-paper.tex
deleted extra period.
added subsections
added flow figures

@@
 \section{Background}
+
 \subsection{The Interface}
+
+\begin{figure*}[t]
+	\centering
+		\includegraphics[width=1.0\textwidth]{old-flow.pdf} 
+		\caption{old flow} 
+\end{figure*}
+
 {\color {red} storyboard of the old interface
@@
 }
+
 \subsection{Kinds of Users}
+
 \subsection{Network Components}
+
 \subsection{Censorship Environments}
@@
 configuration. We did this through observing each participant as they 
-interacted with Tor Browser 5.0.3. interface and interviewed them about
+interacted with Tor Browser 5.0.3 interface and interviewed them about
 their experience. This study provides insights into particular problems with 
@@
 \section{Redesigning the Configuration Interface}
+
+\begin{figure*}[t]
+	\centering
+		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
+		\caption{new flow} 
+\end{figure*}
 

### 2016-03-31 pets2017-paper/pets2017-paper.tex
pasted over introduction

@@
 \section{Introduction}
-{\color {red} 
-Introduce what Tor is, and what the configuration interface does in the Tor Browser Bundle.
-Explain the story of how it began as an anonymity tool, but it has since changed to become a censorship circumvention tool.
-Give statistics of how many people use it (although we can't say how many for what reason exactly), and interesting trends, such as a spike in use around election times or some big political event.
-}
+Tor is primarily known as the most widely used anonymity tool today. 
+For this reason, user studies on Tor have been solely about the usability of Tor as an
+anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
+``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
+to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
+Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
+Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
+Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
+This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
+5.1 and later. There has been no work done on Tor as a censorship circumvention tool.
 
+Many features of Tor have not been evaluated through user
+research --- such as advanced web tasks (e.g., accessing hidden services), the
+configuration menu to connect to the Tor network, configuring automatic
+updates, and identity/cookie management. Rather than selecting the features to
+study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
+Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
+Although Tor was not designed to be a censorship circumvention tool, users started
+using it as one, since Tor's role as a proxy to anonymize
+people also worked to circumvent censorship. Now, circumventing censorship is a
+common use case for Tor, and current censorship circumvention methods are
+incorporated into Tor, making it a viable censorship circumvention tool even in the face
+of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
+To our knowledge, this is the first user study investigating the usability of Tor as a 
+censorship circumvention tool.
+
+We believe that this is a great opportunity for user research.
 This study aims to understand of what is confusing about the configuration process and what find changes make the process easier.
@@
 User metrics, such as success rate and time to completion, measured how well the interfaces served their purpose.
-
-{\color {red}
-Explain the state of censorship circumvention today, and what governments do to Tor (block it, etc.).
-Mention the current consequences of people if they try to connect to Tor.
-Then drive home why it is important for the interface to be usable.
-And that there have been previous work on Tor Browser, but not any previous work done for its usability as a censorship circumvention tool.
-}
 
@@
 \subsection{Censorship Environments} 
+{\color {red}
+Explain the state of censorship circumvention today, and what governments do to Tor (block it, etc.).
+Mention the current consequences of people if they try to connect to Tor.
+Then drive home why it is important for the interface to be usable.
+And that there have been previous work on Tor Browser, but not any previous work done for its usability as a censorship circumvention tool.
+}
 

### 2016-03-31 experiment/processing/inst.py
Factor out some inst-parsing code.

@@ -1,0 +1,27 @@
+import datetime
+import json
+import re
+
+class Record(object):
+    def __init__(self, exec_id, date, event):
+        self.exec_id = exec_id
+        self.date = date
+        self.event = event
+
+def parse_date_string(s):
+    m = re.match(r'^(.*)(\.\d\d\d)Z$', s)
+    d = datetime.datetime.strptime(m.group(1), "%Y-%m-%dT%H:%M:%S")
+    return d.replace(microsecond=int(float(m.group(2)) * 1000000))
+
+# Returns a list of Records.
+def parse_records(f):
+    records = []
+    for line in f:
+        parts = line.strip().split(" ", 3)
+        if parts[0] != "INST":
+            raise ValueError("expected an INST line: %r" % line)
+        exec_id = parts[1]
+        date = parse_date_string(parts[2])
+        event = json.loads(parts[3])
+        records.append(Record(exec_id, date, event))
+    return records

### 2016-03-31 experiment/processing/inst.py
Let graph read from names files, not just stdin.

@@ -1,6 +1,7 @@
 import datetime
 import json
 import re
+import sys
 
 class Record(object):
     def __init__(self, exec_id, date, event):
@@ -25,3 +26,12 @@ def parse_records(f):
         event = json.loads(parts[3])
         records.append(Record(exec_id, date, event))
     return records
+
+# Return an iterator over input files (stdin if no files are named).
+def input_files(args):
+    if not args:
+        yield sys.stdin
+        return
+    for filename in args:
+        with open(filename) as f:
+            yield f

### 2016-03-31 pets2017-paper/pets2017-paper.tex
paste over background section

@@
 
-\subsection{The Interface}
+\subsection{Interacting Network Components} 
+For context, we will give the definition of bridges, pluggable transports, and proxies. 
+Keep in mind that this is the kind of information that a user might need to know to be able
+to configure correctly. Note that bridges, pluggable transports, and proxies are technical 
+concepts which may be unfamiliar to the average user, and that bridges and pluggable
+transports are completely Tor-specific concepts.
+
+Bridges are unlisted Tor relays that make it possible for a user to connect
+to the Tor network even if a censor blocks all publicly listed Tor relays. There used 
+to be plain relays which were exactly similar to public relays, but were unlisted. However, 
+censors in countries which blocked Tor generally were motivated enough to aggressively
+block Tor in other ways, such as traffic analysis. For this reason, a bridge is usually associated
+with a pluggable transport that circumvents deep packet inspection. Transports can
+assist by obfuscating traffic or reflecting traffic through a content distribution network. 
+Proxies help bypass local network restrictions and are typically only
+needed in restricted cases, such as corporate environments.
+
+\subsection{The Configuration Interface} 
+The Tor Browser provides a configuration interface to guide users through setting up 
+their connection to the
+Tor network. While most can connect to Tor using the
+dialog's default settings, users in certain censorship environments must
+make use of additional settings, such as bridges, proxies, or both. 
+Our study explores how the average user circumvents censorship
+through this interface.
+
+As bridges and proxies can be configured independently or together, there are
+four main ways to set up a connection:
+
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item With a bridge and proxy
+    \item With a bridge but no proxy
+    \item Without a bridge but with a proxy
+    \item Without either a bridge or proxy
+\end{enumerate}
+
+The launcher interface asks a series of questions to
+determine which of these configuration states a user requires.
+The four high-level states correspond to five distinct paths through the
+configuration interface. (The latter option -- connecting with neither a bridge
+nor proxy -- contributes two separate paths.) Each path branches further
+depending on user-specific inputs. Figure \ref{fig:old-flow} illustrates the
+possible paths.
+
+When the configuration window opens, a user is given the option to connect
+directly to the Tor network by clicking ``Connect'', or to click ``Configure''
+``if this computer's Internet connection is censored or proxied'' (Figure
+\ref{fig:window1}).
+
+If they choose the latter, the next screen asks, ``Does your Internet Service
+Provider (ISP) block or otherwise censor connection to the Tor network?''
+(Figure \ref{fig:window2}). Though this sounds repetitive, it is meant to
+identify and divert users who need only a proxy (and no bridge).
+This phrasing of the question carries the assumption that people will
+not know if they need a bridge or not, but that they are equipped to answer if their
+current network environment censors the Tor Network.
+
+Next, users are asked to configure bridges by selecting a transport type from a
+dropdown menu or entering the IP address of a custom bridge in a textbox (Figure
+\ref{fig:bridges}).
+Finally, users are asked whether they need a local proxy (Figure
+\ref{fig:window4}) and (if they answered yes) to configure it (Figure
+\ref{fig:window5}).
+
+Note that a user can decide to click ``Configure'' on the first screen, but then
+opt out of both bridges and proxies.
+In this case, connecting after these configuration steps
+would be equivalent to clicking ``Connect'' on the first screen.
 
 \begin{figure*}[t]
+	\label{fig:old-flow}
 	\centering
@@
 
-{\color {red} storyboard of the old interface
-
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item No bridge, no proxy
-    \item with bridge, no proxy
-    \item No bridge, with proxy
-    \item With bridge, with proxy
-\end{enumerate}
-}
-
-\subsection{Kinds of Users}
-
-\subsection{Network Components}
-
-\subsection{Censorship Environments} 
+\subsection{Censorship Today} 
 {\color {red}
@@
 Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.\\
+
+%\noindent {\bfseries Design choices}
+%The launcher interface utilizes a number of techniques to aid users and simplify
+%the choices they have to make. Help buttons and a support email address that
+%appears on every screen are meant to assist users that get stuck in the process.
+%The interface also makes good use of defaults, for example by emphasizing that
+%certain options ``will work in most situations.''
+%
+%Still, there remains potential for confusion, especially with the more advanced
+%configuration options.
+%Bridges, pluggable transports, and proxies are never defined for the user,
+%arguably because they might not read or understand these definitions.
+%This can lead to users confusing these terms, or not understanding
+%the relations between them. Additionally, there is limited explanation of 
+%what pluggable transport types to choose from if the default one fails or how to 
+%find proxy settings, which will be required of some users.
 

### 2016-03-31 pets2017-paper/pets2017-paper.tex
notes to self on TODOs

@@
 \subsection{Results} 
+{\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment.
+Some of the questions we want to answer are: did the new interface improve success rate?
+did the new interface only help certain people?
+Did people take longer or shorter in the new version?
+Did we shift participants' behaviors in the new interface?
+Are the way people approach trying different configurations affected?
+are there existing problems for both interfaces?
+(we know for sure that users still not receiving feedback is an issue.
+I don't know how many of our participants actually saw our helpful error messages, since they took minutes to pop up, and some never pop up at all..)}
 
@@
 \section{Related Work} 
+{\color {red} TODO}
 
 \section {Acknowledgments}
+{\color {red} TODO}
 

### 2016-04-04 pets2017-paper/pets2017-paper.tex
deleted weird title I thought was a good idea when I was tired.
section 2.2

@@
 %... but in one catchy title. I can't think of one.
-\title{Designing for Multiple Use and At-Risk Users: Tor Configuration Launcher}
+\title{Tor's Usability for Censorship Circumvention}
 \numberofauthors{1}
@@
 
-\subsection{The Configuration Interface} 
+\subsection{The Current Configuration Interface} 
 The Tor Browser provides a configuration interface to guide users through setting up 
@@
 
-The launcher interface asks a series of questions to
-determine which of these configuration states a user requires.
-The four high-level states correspond to five distinct paths through the
-configuration interface. (The latter option -- connecting with neither a bridge
-nor proxy -- contributes two separate paths.) Each path branches further
-depending on user-specific inputs. Figure \ref{fig:old-flow} illustrates the
-possible paths.
+The interface asks a series of questions to determine which of these configuration states a user requires.
+The first decision that a user needs to make is if they should connect directly to the Tor network or go through the process of  configuring a bridge and a proxy.
+The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure.
+For a successful configuration, users are required to know the following:
 
-When the configuration window opens, a user is given the option to connect
-directly to the Tor network by clicking ``Connect'', or to click ``Configure''
-``if this computer's Internet connection is censored or proxied'' (Figure
-\ref{fig:window1}).
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+	\item{Whether to connect directly or configure a connection.} 
+	\item{If the Tor Network is censored by their ISP.}
+	\item{Which bridges work in the current environment.} 
+	\item{If no bridges work, how to get a custom bridge.} 
+	\item{If a proxy is required to access the Internet.}
+	\item{If a proxy is required, the proxy settings.}
+\end{itemize}
 
-If they choose the latter, the next screen asks, ``Does your Internet Service
-Provider (ISP) block or otherwise censor connection to the Tor network?''
-(Figure \ref{fig:window2}). Though this sounds repetitive, it is meant to
-identify and divert users who need only a proxy (and no bridge).
-This phrasing of the question carries the assumption that people will
-not know if they need a bridge or not, but that they are equipped to answer if their
-current network environment censors the Tor Network.
-
-Next, users are asked to configure bridges by selecting a transport type from a
-dropdown menu or entering the IP address of a custom bridge in a textbox (Figure
-\ref{fig:bridges}).
-Finally, users are asked whether they need a local proxy (Figure
-\ref{fig:window4}) and (if they answered yes) to configure it (Figure
-\ref{fig:window5}).
-
-Note that a user can decide to click ``Configure'' on the first screen, but then
-opt out of both bridges and proxies.
-In this case, connecting after these configuration steps
-would be equivalent to clicking ``Connect'' on the first screen.
+This puts the majority of the burden of knowing the correct technical information and configuring the connection correctly on the user.
+Although burdensome, the interface takes the approach of guiding the user through this technical process in order to give users their own agency in configuring their connection.
+No automation means that the user can have control over when there will be network traces of their activity trying to connect to Tor, and being able to connect successfully to the Tor the first time, provided they have all of the relevant information.
 
@@
 %find proxy settings, which will be required of some users.
-
-{\bfseries What it's trying to do}
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item separate people who use Tor for anonymity and for censorship 
-    \item if anonymity, to connect people directly
-    \item if censorship, guide users to make the correct configuration
-    \item minimize network traces to protect high-risk users
-\end{enumerate}
-
-{\bfseries Why certain decisions were made}
-{\color {red} 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item {\bfseries Asking the User} asking users about their situation rather than hardcoding or probing
-    \item {\bfseries No Explicit Advice} no suggestion of what to try and in what order
-    \item {\bfseries No Automation} manual configuration of bridges and proxies required
-    \item {\bfseries Optimizing for the Average Case} connect, bridges before proxy
-\end{enumerate}
-}
 

### 2016-04-04 pets2017-paper/pets2017-paper.tex
add background intro

@@
 \section{Background} 
+In this section, we talk about network components that circumvent censorship, Tor Browser 5.0.3 configuration interface that guides users to configure those network components to make a connection to the Tor Network, and the current state of Internet censorship which had impact on both the deployed and redesigned configuration interface.
 

### 2016-04-04 pets2017-paper/pets2017-paper.tex
reword goals and evaluation criteria section

@@
 
-Since there is risk associated with making an unobfuscated 
-connection with the Tor network, the configuration process is not automated.
 Our empirical evaluation criteria for the Tor Browser configuration
@@
 
-A heuristic evaluation is a rule-based evaluation which leverages standards
-developed over trial and error that have shown to work in the User Interface design 
-community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS}
+A heuristic evaluation is a rule-based evaluation that leverages standards
+that have shown to work in the User Interface design 
+community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS})
 and other industry standards to form the following heuristic evaluation criteria: 

### 2016-04-04 pets2017-paper/pets2017-paper.tex
rough pass over background section

@@
 \section{Background} 
-In this section, we talk about network components that circumvent censorship, Tor Browser 5.0.3 configuration interface that guides users to configure those network components to make a connection to the Tor Network, and the current state of Internet censorship which had impact on both the deployed and redesigned configuration interface.
+In this section, we talk about the current state of Internet censorship, interface network components that circumvent censorship, and the Tor Browser 5.0.3 configuration interface that guides users to configure those network components to make a connection to the Tor Network.
+
+\subsection{Censorship Today} 
+Internet censorship is widespread throughout the world.
+Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation.
+Currently {\color {red} TODO} governments implement some sort of Internet censorship in their country.
+The most commonly censored categories of websites are {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), and {\color {red} TODO} ({\color {red} TODO}\%).
+Reactions from Internet censorship range from feeling safe that bad sites are blocked automatically for their citizens to being outraged that access to information and free speech have been infringed upon.
+The risks associated with circumventing Internet censorship, is largely based on the geographic location, how prevalent censorship circumvention is, and who you are.
+
+{\color{red} Link sources, talk about arms race between censors and censorship circumvention tools.}
 
 \subsection{Interacting Network Components} 
-For context, we will give the definition of bridges, pluggable transports, and proxies. 
-Keep in mind that this is the kind of information that a user might need to know to be able
-to configure correctly. Note that bridges, pluggable transports, and proxies are technical 
-concepts which may be unfamiliar to the average user, and that bridges and pluggable
-transports are completely Tor-specific concepts.
+For context, we define bridges, pluggable transports, and proxies, network components that 
+circumvent censorship and interact with the Tor configuration interface. 
+Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
+This information is necessary to configure connections to Tor in censored environments.
 
@@
 The Tor Browser provides a configuration interface to guide users through setting up 
-their connection to the
-Tor network. While most can connect to Tor using the
+their connection. While most can connect to Tor using the
 dialog's default settings, users in certain censorship environments must
-make use of additional settings, such as bridges, proxies, or both. 
-Our study explores how the average user circumvents censorship
-through this interface.
-
-As bridges and proxies can be configured independently or together, there are
+make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are
 four main ways to set up a connection:
@@
 This puts the majority of the burden of knowing the correct technical information and configuring the connection correctly on the user.
+Note that bridges, pluggable transports, and proxies are technical concepts that probably are unfamiliar to the average user.
 Although burdensome, the interface takes the approach of guiding the user through this technical process in order to give users their own agency in configuring their connection.
+Since there is risk associated with making an unobfuscated connection with the Tor network, the configuration process is not automated.
 No automation means that the user can have control over when there will be network traces of their activity trying to connect to Tor, and being able to connect successfully to the Tor the first time, provided they have all of the relevant information.
@@
 \end{figure*}
-
-\subsection{Censorship Today} 
-{\color {red}
-Explain the state of censorship circumvention today, and what governments do to Tor (block it, etc.).
-Mention the current consequences of people if they try to connect to Tor.
-Then drive home why it is important for the interface to be usable.
-And that there have been previous work on Tor Browser, but not any previous work done for its usability as a censorship circumvention tool.
-}
 

### 2016-04-04 pets2017-paper/pets2017-paper.tex
sorted the participant quotations

@@
 
-Relevant participant quotes: 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item{{\bfseries P1}:``figuring out if the progress bar wasn't moving because the connection was censored, of if it was just slow''}
-\item{{\bfseries P2}: "I don't know what any of those means (list of bridges), I don't know what that (proxy) means at all."}
-\item{{\bfseries P3}: ``The vocabulary is really challenging, for someone not doing IT work. Good thing I'm really curious. because I was able to use trial and error.''} 
-\item{{\bfseries P4}: ``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.'}
-\item{{\bfseries P5}: ``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
-\item{{\bfseries P6}: ``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}
-\item{{\bfseries P6}: ``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
-\item{{\bfseries P7}: ``The bridge screen was the most challenging.
+%configure vs connect
+\begin{quotation}
+\noindent{\bfseries P10}: \textit{``I was censored, so I picked the configure.''}\\
+\noindent{\bfseries P9}: \textit{``Configure seemed manual, so I clicked connect.''}\\
+\noindent{\bfseries P14}:\textit{``The words were confusing.
+I don't really understand computers.
+I don't know what configure means in this setting.
+Hmm, is it going to crash?
+When you see connect, you want to click it because you really want it to connect..''}
+\end{quotation}
+
+%time
+\begin{quotation}
+\noindent{\bfseries P16}:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
+\noindent{\bfseries P6}:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
+\noindent{\bfseries P1}:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
+\end{quotation}
+
+%lack of knowledge 
+\begin{quotation}
+\noindent{\bfseries P16}:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}\\
+\noindent{\bfseries P12}:\textit{``I decided which options to choose by process of elimination with trial and error..''}\\
+\noindent{\bfseries P2}:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
+ means at all."}\\
+ \noindent{\bfseries P3}:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
+ \noindent{\bfseries P4}:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}
+\end{quotation}
+
+%misc
+\begin{quotation}
+\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
+\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''} 
+\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
+\end{quotation}
+
+%bridges
+\begin{quotation} 
+\noindent{\bfseries P7}:\textit{``The bridge screen was the most challenging.
 It seemed very technical to me.
@@
 Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
-I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}
-\item{{\bfseries P8}: ``I have no clue what's the difference between flashrpoxy, fte, etc.
+I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}\\
+\noindent{\bfseries P8}:\textit{``I have no clue what's the difference between flashrpoxy, fte, etc.
 I need to know why the built-in ones aren't working.
-And why do I need a custom bridge if there are options built in?''}
-\item{{\bfseries P9}: ``Configure seemed manual, so I clicked connect.''} %c1
-\item{{\bfseries P10}: ``I was censored, so I picked the configure.''} %c1
-\item{{\bfseries P11}: ``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
-\item{{\bfseries P11}: ``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance.''}
-\item{{\bfseries P12}: ``I decided which options to choose by process of elimination with trial and error.'' }
-\item{{\bfseries P13}: ``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy.''}
-\item{{\bfseries P14}: ``The words were confusing.
-I don't really understand computers.
-I don't know what configure means in this setting.
-Hmm, is it going to crash?
-When you see connect, you want to click it because you really want it to connect.''}
-\item{{\bfseries P15}: ``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things.''}
-\item{{\bfseries P15}: ``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
-\item{{\bfseries P16}: ``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
-\item{{\bfseries P16}: ``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}
-\end{itemize}
+And why do I need a custom bridge if there are options built in?'}
+\end{quotation}
+
+\begin{quotation}
+\noindent{\bfseries P4}:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
+\noindent{\bfseries P5}:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
+\end{quotation}
+
+%proxies
+\begin{quotation}
+\noindent{\bfseries P11}:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
+\noindent{\bfseries P15}:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
+\end{quotation}
 

### 2016-04-04 experiment/processing/info.R
Do an ANOVA of time_to_success.
ANOVA of time_to_success by env and version
             Df   Sum Sq  Mean Sq F value Pr(>F)
env           2 47007790 23503895   56.28 <2e-16 ***
version       1  1457412  1457412    3.49 0.0644 .
Residuals   112 46775797   417641
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1

@@ -49,6 +49,16 @@ summary(aov(success ~ env+version, data=participants))
 
 for (env in levels(participants$env)) {
 	cat("\n")
-	cat(sprintf("t-test of means in env %s\n", as.character(env)))
+	cat(sprintf("t-test of success rate in env %s\n", as.character(env)))
 	try(print(with(participants[participants$env==env, ], t.test(success[version=="NEW"], success[version=="OLD"]))))
+}
+
+cat("\n")
+cat(sprintf("ANOVA of time_to_success by env and version\n"))
+summary(aov(time_to_success ~ env+version, data=participants))
+
+for (env in levels(participants$env)) {
+	cat("\n")
+	cat(sprintf("t-test of time_to_success in env %s\n", as.character(env)))
+	try(print(with(participants[participants$env==env, ], t.test(time_to_success[version=="NEW"], time_to_success[version=="OLD"]))))
 }

### 2016-04-04 experiment/processing/info.R
Only assign the maximum time_to_success in the time_to_success graph.
It was affecting the later stats as well. Now the later stats just deal
with the NAs.

@@ -13,16 +13,20 @@ pctsummary <- function(x) {
 	sprintf("%d/%d = %5.1f%%", sum(x), length(x), 100*mean(x))
 }
 
+# Assign DNFs a maximum time_to_success.
+cap_time_to_success <- function(participants, maxtime) {
+	df <- data.frame(participants)
+	df$time_to_success[is.na(df$time_to_success)] <- maxtime
+	df
+}
+
 cat(sprintf("number of participants: %d (%d good, %d bad)\n",
 	length(participants$good), sum(participants$good), sum(!participants$good)))
 
 # From now on we use only the good participants.
 participants <- participants[participants$good, ]
 
-# Assign DNFs the maximum time.
-participants$time_to_success[is.na(participants$time_to_success)] <- 40*60
-
-p <- ggplot(participants, aes(x=sprintf("%s-%s", env, version), y=time_to_success, color=success))
+p <- ggplot(cap_time_to_success(participants, 40*60), aes(x=sprintf("%s-%s", env, version), y=time_to_success, color=success))
 p <- p + geom_point(size=1, alpha=0.6, position=position_jitter(width=0.2))
 p <- p + coord_flip()
 p <- p + xlab("environment and version")

### 2016-04-04 experiment/processing/common.R
Factor out graph code into graphs.R.

@@ -1,0 +1,15 @@
+# Read all the participant CSV files into one big data frame.
+read_participants <- function() {
+	participants <- read.csv("participants.csv")
+	sessions <- read.csv("sessions.csv")
+	success <- read.csv("success.csv")
+
+	participants <- merge(participants, sessions, by=c("session"), all=T)
+	participants <- merge(participants, success, by=c("seat", "runid"), all=T)
+	participants
+}
+
+# Return only the participants marked "good".
+filter_participants <- function(participants) {
+	participants[participants$good, ]
+}

### 2016-04-04 experiment/processing/graphs.R

@@ -1,0 +1,19 @@
+library(ggplot2)
+
+source("common.R")
+
+# Assign DNFs a maximum time_to_success.
+cap_time_to_success <- function(participants, maxtime) {
+	df <- data.frame(participants)
+	df$time_to_success[is.na(df$time_to_success)] <- maxtime
+	df
+}
+
+participants <- filter_participants(read_participants())
+
+p <- ggplot(cap_time_to_success(participants, 40*60), aes(x=sprintf("%s-%s", env, version), y=time_to_success, color=success))
+p <- p + geom_point(size=1, alpha=0.6, position=position_jitter(width=0.2))
+p <- p + coord_flip()
+p <- p + xlab("environment and version")
+p <- p + theme_minimal()
+ggsave("time_to_success.pdf", p, width=5, height=4)

### 2016-04-04 experiment/processing/info.R

@@ -1,39 +1,16 @@
-library(ggplot2)
+source("common.R")
 
-options(width=160)
-
-participants <- read.csv("participants.csv")
-sessions <- read.csv("sessions.csv")
-success <- read.csv("success.csv")
-
-participants <- merge(participants, sessions, by=c("session"), all=T)
-participants <- merge(participants, success, by=c("seat", "runid"), all=T)
+participants <- read_participants()
 
 pctsummary <- function(x) {
 	sprintf("%d/%d = %5.1f%%", sum(x), length(x), 100*mean(x))
-}
-
-# Assign DNFs a maximum time_to_success.
-cap_time_to_success <- function(participants, maxtime) {
-	df <- data.frame(participants)
-	df$time_to_success[is.na(df$time_to_success)] <- maxtime
-	df
 }
 
 cat(sprintf("number of participants: %d (%d good, %d bad)\n",
 	length(participants$good), sum(participants$good), sum(!participants$good)))
 
 # From now on we use only the good participants.
-participants <- participants[participants$good, ]
-
-p <- ggplot(cap_time_to_success(participants, 40*60), aes(x=sprintf("%s-%s", env, version), y=time_to_success, color=success))
-p <- p + geom_point(size=1, alpha=0.6, position=position_jitter(width=0.2))
-p <- p + coord_flip()
-p <- p + xlab("environment and version")
-p <- p + theme_minimal()
-ggsave("time_to_success.pdf", p, width=5, height=4)
-
-# participants
+participants <- filter_participants(participants)
 
 cat("\n")
 cat(sprintf("number of good participants per condition\n"))

### 2016-04-04 pets2017-paper/pets2017-paper.tex
Fix \bibliography call (wrong filename).

@@
 
-Our empirical evaluation criteria for the Tor Browser configuration
-interface are from common metrics that measure ease of use with a special 
-consideration for high-risk users: 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
-    \item {\bfseries Time to Completion} Time to completion. 
-    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
-\end{enumerate}
-
 A heuristic evaluation is a rule-based evaluation that leverages standards
@@
 
-An empirical evaluation of the problems with the existing Tor Browser 
+Our empirical evaluation criteria for the Tor Browser configuration
+interface are from common metrics that measure ease of use with a special 
+consideration for high-risk users: 
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
+    \item {\bfseries Time to Completion} Time to completion. 
+    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
+\end{enumerate}
+
+An exploration of the problems with the existing Tor Browser 
 configuration interface through user observation and interviews can be 
-found in section {\color{red} TODO}. A heuristic evaluation of the existing interface
-and new interface can be found  in section {\color{red} TODO}. We empirically show 
+found in section {\color{red} TODO}. A heuristic evaluation of the existing interfaceand new interface is in section {\color{red} TODO}. We empirically show 
 that the redesigned interface improves completion rate, reduces time to completion, 
@@
 trying to configure Tor Browser, we interviewed participants about their experience.
+We performed a live transcription of the interview to avoid recording voices, which is
+considered personally identifying information. 
 We asked three standard questions asking about their general experience, 
@@
 \subsubsection{Results} 
+{\color {red} meta couple-sentence summary of the feeling we get from the experiment. All quotes are paraphrase from a live transcription.}\\
 
-%\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-%    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
-%    \item {\bfseries Time to Completion} Time to complete, ease of user for the average user. 
-%    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak %that they are using Tor. 
-%\end{enumerate}
+\noindent {\bfseries Connect vs. Configure} 
+The first task for our participants was to decide between connecting directly to the Tor network or configuring their connection.
+Text in the interface tells people that connecting directly ``will work in most situations'' and instructs to configure a bridge or proxy if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.
 
-We noticed four common challenges:
+The participant across all censorship environments connected directly to the Tor network.
+When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process.
+\begin{quotation}
+\noindent P9: \textit{``Configure seemed manual, so I clicked connect.''}\\
 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Challenge 1:} Users don't know how to choose between connecting directly to the Tor network or manually configuring their connection (Figure \ref{fig:window1}).
-The text was unread or not understood by most users.
-When the user read the text, they found no instructions, but were given information to make a decision for themselves, which they did not feel equipped to do.
-\item {\bfseries Challenge 2:} Users feel compelled to set up a bridge, even if they don't need one.
-We believe this is due to the text on the first screen, which refers to a ``censored internee connection'' (Figure \ref{fig:window1}).
-Bridges are only necessary when the government actively censored Tor relays, but participants are not able to determine the difference between a censor that blocks websites and a censor that blocks websites and the Tor network.
-\item {\bfseries Challenge 3:} Users did not know what to do after a failure.
-Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
-\item {\bfseries Challenge 4:} Users draw incorrect conclusions after a failed connection.
-The interface passively re-displayed the last window seen before the attempted connection (Figure \ref{fig:window4} or \ref{fig:window5}), regardless of the error.
-\end{itemize}
-
-%configure vs connect
-\begin{quotation}
-\noindent{\bfseries P10}: \textit{``I was censored, so I picked the configure.''}\\
-\noindent{\bfseries P9}: \textit{``Configure seemed manual, so I clicked connect.''}\\
-\noindent{\bfseries P14}:\textit{``The words were confusing.
+\noindent P14:\textit{``The words were confusing.
 I don't really understand computers.
@@
 
-%time
+Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this happens, or what the difference between a blocked website and a blocked relay looks like.
+Participant 10 and several other participants in the mild censorship environment opted to configure a connection when a direct connection to the Tor network would have worked.
+
 \begin{quotation}
-\noindent{\bfseries P16}:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
-\noindent{\bfseries P6}:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
-\noindent{\bfseries P1}:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
+\noindent P10: \textit{``I was censored, so I picked the configure.''}
 \end{quotation}
 
-%lack of knowledge 
+This mistake can results in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments.
+Participants in the intermediate and advanced censorship environments who did correctly choose to configure in intermediate did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.
+
+Making the choice between connect and configure clearer for users has the possibility to save time and keep users safer.
+Waiting for a failed connection takes about couple minutes, so users can save at least that time by making the correct decision the first time.
+Users who need to configure can benefit from not clicking connect, which keeps them safer by not leaving a detectable network trace that indicates that they are trying to use Tor to circumvent censorship.\\
+
+\noindent {\bfseries Bridge Configuration} 
+When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary.
+Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen.
+We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error.
+
 \begin{quotation}
-\noindent{\bfseries P16}:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}\\
-\noindent{\bfseries P12}:\textit{``I decided which options to choose by process of elimination with trial and error..''}\\
-\noindent{\bfseries P2}:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
- means at all."}\\
- \noindent{\bfseries P3}:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
- \noindent{\bfseries P4}:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}
+\noindent P7:\textit{``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.''}\\
+\noindent P12:\textit{``I decided which options to choose by process of elimination with trial and error.''}
 \end{quotation}
 
-%misc
+When a participant chooses to configure a bridge, they are faced with a list of options without much explanation. 
 \begin{quotation} 
-\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
-\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''} 
-\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
-\end{quotation}
-
-%bridges
-\begin{quotation} 
-\noindent{\bfseries P7}:\textit{``The bridge screen was the most challenging.
-It seemed very technical to me.
-I don't know what a bridge is.
-Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+\noindent P7:\textit{``Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
 I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}\\
-\noindent{\bfseries P8}:\textit{``I have no clue what's the difference between flashrpoxy, fte, etc.
+\noindent P8:\textit{``I have no clue what's the difference between flashpoxy, fte, etc.
 I need to know why the built-in ones aren't working.
@@
 \begin{quotation}
-\noindent{\bfseries P4}:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
-\noindent{\bfseries P5}:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
+\noindent P4:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
+\noindent P5:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
 \end{quotation}
 
+\noindent {\bfseries Proxy Configuration} 
+If users did not successfully connect on their first attempt, they did not know what to do next.
+Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+Because no information was given, our participants drew their own (incorrect) conclusions after a failed connection.
+Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.
 %proxies
 \begin{quotation}
-\noindent{\bfseries P11}:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
-\noindent{\bfseries P15}:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
+\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
+\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
 \end{quotation}
+
+\noindent{\bfseries Sources of Frustration} 
+%time
+\begin{quotation}
+\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
+\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
+\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
+\end{quotation}
+
+%lack of knowledge 
+\begin{quotation}
+\noindent P2:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
+ means at all."}\\
+ \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
+ \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}\\
+ \noindent P16:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
+\end{quotation}
+
+%\begin{quotation}
+%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
+%\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''}\\
+%\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
+%\end{quotation}
 
@@
 \bibliographystyle{abbrv}
-\bibliography{pets-2017-paper.bib}
+\bibliography{pets2017-paper}
 

### 2016-04-04 pets2017-paper/pets2017-paper.tex
first pass at results section; connect vs configure subsubsubsubsection complete.
second pass through qualitative results section; bridges done

--- 2016-04-04 pets2017-paper/pets2017-paper.tex
@@
 \noindent P7:\textit{``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.''}\\
+
 \noindent P12:\textit{``I decided which options to choose by process of elimination with trial and error.''}
@@
 
-When a participant chooses to configure a bridge, they are faced with a list of options without much explanation. 
+On the bridge configuration screen, participants need to choose between configuring a built-in bridge versus a custom bridge.
+Participants were unsure of the difference between a built-in bridge and a custom bridge and also why one would use a custom bridge.
+Most participants chose to go with the built-in bridge and chose obfs3 as their transport, because those were the default options on the screen.
+
 \begin{quotation} 
-\noindent P7:\textit{``Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
-I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}\\
 \noindent P8:\textit{``I have no clue what's the difference between flashpoxy, fte, etc.
 I need to know why the built-in ones aren't working.
-And why do I need a custom bridge if there are options built in?'}
+And why do I need a custom bridge if there are options built in?'}\\
+
+\noindent P7:\textit{``Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}
 \end{quotation}
+
+Participants in the advanced censorship environment were required to select a meek bridge (not the default) or to configure a custom bridge.
+After the first pluggable transport failed and if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors.
+Participants chose bridges in every order imaginable: at random, in order of the list starting from the default, in order of the list starting from the top, at random, choosing accessible sounding names first (i.e.
+meek-amazon over fte), and choosing non-accessible sounding names first (i.e.
+fte over meek-amazon).
 
@@
 \noindent P4:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
+
 \noindent P5:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
@@
 
+Providing explicit guidance on in which order participants should try the bridges will be critical in helping a user succeed in configuring their connection.
+Rather than letting the user choose, the interface can guide the users by telling them to choose specific bridges if the default doesn't work, and in what order.
+Our participants were resilient in trying to configure a connection for up to 40 minutes, but we believe that this is a byproduct of the experimental setting and compensation.
+\\
+
 \noindent {\bfseries Proxy Configuration} 
-If users did not successfully connect on their first attempt, they did not know what to do next.
-Error messages (see Figure \ref{fig:error}) did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
-Because no information was given, our participants drew their own (incorrect) conclusions after a failed connection.
-Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.
 %proxies
@@
 \noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
+
 \noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
 \end{quotation}
+
+If users did not successfully connect on their first attempt, they did not know what to do next.
+Error messages did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+Because no information was given, our participants drew their own (incorrect) conclusions after a failed connection.
+Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.\\
 
@@
 \noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
+
 \noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
+
 \noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
@@
  means at all."}\\
+
  \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
+
  \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}\\
+
  \noindent P16:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}

### 2016-04-04 pets2017-paper/pets2017-paper.tex
finish qualitative results proxy subsubsubsubsection.

@@
 We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error.
+Most participants with the default option to not configure a bridge.
 
@@
 \noindent {\bfseries Proxy Configuration} 
+After the bridge configuration, the participant again is asked to answer a question to determine if they need a proxy and if so, to configure one.
+This question also was too technical for some participants.
+
+\begin{quotation}
+\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''}
+\end{quotation}
+
+None of our censorship environments required our participants to configure a proxy for a successful connection.
+And upon the first attempt at configuration, most chose the default value of not configuring a proxy.
+However, the most common reason for of failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead.
+Currently, no information was given upon failing to connect, which caused our participants to draw their own (incorrect) conclusions after a failed connection.
+Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.
+
+None of the participants who attempted to configure a proxy were successful.
+Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information.
+What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.
+
 %proxies
 \begin{quotation}
-\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''} \\
-
-\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did..''}\\ 
+\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
 \end{quotation}
 
-If users did not successfully connect on their first attempt, they did not know what to do next.
-Error messages did not guide users into taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
-Because no information was given, our participants drew their own (incorrect) conclusions after a failed connection.
-Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.\\
+Providing participants with feedback about taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.
+can prevent participants from unnecessarily configuring a proxy and to connect successfully.
+\\
 

### 2016-04-04 experiment/processing/common.R
Fiddle with time_to_success graph styling.

@@ -1,3 +1,10 @@
+library(ggplot2)
+
+# From template.cls:
+# %%% 2)  Side and top margins of 4.5pc, bottom margin of 6pc, column gutter of
+# %%%     2pc, hence columns are 20pc wide and 55.5pc tall.  (6pc = 1in, approx)
+textwidth <- 20 / 6
+
 # Read all the participant CSV files into one big data frame.
 read_participants <- function() {
 	participants <- read.csv("participants.csv")
@@ -12,4 +19,11 @@ read_participants <- function() {
 # Return only the participants marked "good".
 filter_participants <- function(participants) {
 	participants[participants$good, ]
+}
+
+common_theme <- function(p) {
+	p <- p + theme_minimal()
+	p <- p + theme(text=element_text(size=8))
+	p <- p + theme(plot.margin=margin(0,0,0,0,"mm"))
+	p
 }

### 2016-04-04 experiment/processing/graphs.R

@@ -2,6 +2,8 @@ library(ggplot2)
 
 source("common.R")
 
+height <- 1.5
+
 # Assign DNFs a maximum time_to_success.
 cap_time_to_success <- function(participants, maxtime) {
 	df <- data.frame(participants)
@@ -9,11 +11,18 @@ cap_time_to_success <- function(participants, maxtime) {
 	df
 }
 
-participants <- filter_participants(read_participants())
+time_to_success_plot <- function(participants) {
+	p <- ggplot(participants, aes(x=label, y=time_to_success/60))
+	p <- p + geom_boxplot(color="gray70", outlier.size=0)
+	p <- p + geom_point(size=0.8, alpha=0.6)
+	p <- p + coord_flip()
+	p <- p + labs(title=NULL, x=NULL, y="Minutes to first success")
+	p <- common_theme(p)
+	p
+}
 
-p <- ggplot(cap_time_to_success(participants, 40*60), aes(x=sprintf("%s-%s", env, version), y=time_to_success, color=success))
-p <- p + geom_point(size=1, alpha=0.6, position=position_jitter(width=0.2))
-p <- p + coord_flip()
-p <- p + xlab("environment and version")
-p <- p + theme_minimal()
-ggsave("time_to_success.pdf", p, width=5, height=4)
+participants <- filter_participants(read_participants())
+participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E3-OLD", "E3-NEW", "E2-OLD", "E2-NEW", "E1-OLD", "E1-NEW"))
+
+p <- time_to_success_plot(participants)
+ggsave("time_to_success.pdf", p, width=textwidth, height=height)

### 2016-04-04 experiment/processing/graphs.R
Also make a time_to_success_clamped graph.
This one assigns non-finishers a time of 40 minutes.

@@ -5,7 +5,7 @@ source("common.R")
 height <- 1.5
 
 # Assign DNFs a maximum time_to_success.
-cap_time_to_success <- function(participants, maxtime) {
+clamp_time_to_success <- function(participants, maxtime) {
 	df <- data.frame(participants)
 	df$time_to_success[is.na(df$time_to_success)] <- maxtime
 	df
@@ -26,3 +26,6 @@ participants$label <- factor(sprintf("%s-%s", participants$env, participants$ver
 
 p <- time_to_success_plot(participants)
 ggsave("time_to_success.pdf", p, width=textwidth, height=height)
+
+p <- time_to_success_plot(clamp_time_to_success(participants, 40*60))
+ggsave("time_to_success_clamped.pdf", p, width=textwidth, height=height)

### 2016-04-04 pets2017-paper/pets2017-paper.tex
Include time_to_success and time_to_success_clamped figures.

@@
 \subsection{Results}
+
+\begin{figure}
+\centering
+\includegraphics{time_to_success}
+\caption{
+Time to first success, by censorship environment and interface.
+The dots show the raw completion times;
+while the boxplots show the medians and interquartile ranges.
+}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{time_to_success_clamped}
+\caption{
+Time to first success, by censorship environment and interface.
+Here, non-finishing participants are assigned a time of 40 minutes.
+}
+\end{figure}
+
 {\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment.

### 2016-04-05 pets2017-paper/pets2017-paper.tex
finish up qualitative results section

@@
 \subsubsection{Results} 
-{\color {red} meta couple-sentence summary of the feeling we get from the experiment. All quotes are paraphrase from a live transcription.}\\
+In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems.
+We conclude with our goals for improving the configuration interface.
+Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring.
+We confirm the statistical significance of some of the problems in our quantitative study (section ~\ref {sec:quantitative}.
+All quotes are paraphrased from live transcriptions of participant interviews.\\
 
@@
 Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information.
-What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.
+What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.\\
 
-%proxies
+\noindent{\bfseries Progress Bar} 
+Users were generally displeased with the lack of feedback on the progress bar.
+The process seemed to take too long for them, even in the ideal case in which a user chose the correct configuration in the first attempt.
+If users chose particular wrong configurations (i.e.
+a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time, because there is no timeout.
+
+\begin{quotation}
+\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
+
+\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
+\end{quotation}
+
+As a technical artifact of how the progress bar is implemented, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e.
+a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress).
+The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct.
+\begin{quotation}
+\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}
+\end{quotation}
+
+Ensuring that the progress bar faithfully displays the current status can encourage users to wait for correct configurations to successfully connect to the Tor network.
+
 \begin{quotation}
@@
 Providing participants with feedback about taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.
-can prevent participants from unnecessarily configuring a proxy and to connect successfully.
-\\
+can prevent participants from unnecessarily configuring a proxy and to connect successfully.\\
 
-\noindent{\bfseries Sources of Frustration} 
-%time
+\noindent{\bfseries User Communication Failure} Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary.
 \begin{quotation}
-\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
-
-\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}\\
-
-\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}\\
-\end{quotation}
-
-%lack of knowledge 
-\begin{quotation}
-\noindent P2:\textit{"I don't know what any of those means (list of bridges), I don't know what that (proxy)
+\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
  means at all."}\\
@@
 
- \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean for me?''}\\
+ \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
 
@@
 \end{quotation} 
+In addition to the text being not as helpful as it would have been had users been able to understand, this discouraged our users during the process.\\
+
+\noindent{\bfseries Final Thoughts}
+We believe that the interface is too technical for users to understand and overburdens users with tasks.
+From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.
 
@@
 \section{Quantitative Analyses of the Interfaces (Study 2)}
+\label{sec:quantitative}
 We performed quantitative research to quantify the existing problems

### 2016-04-05 pets2017-paper/pets2017-paper.tex
outlined redesign section

@@
 
-{\color {red} 
-Talk about the problems from the previous results section, and how we plan to change them,
-along with a heuristic evaluation of the interface.
+%skip talking about the process of redesigning the interface. It isn't that interesting.
 
-Talk about the process of designing a new interface, and how we tested it with BLUES and the
-Tor Developers.
-
-Talk about the improvements in heuristics from the existing to the redesigned interface, along 
-with hopes of what we want our empirical goals to be (to increase success rate and to minimize
-time to completion, which we do by some proxy detection, giving specific directions, etc.).
-
-...
-
-Only use the following if it helps explain some things. Make sure the tone of things are positive, and explain that making a good interface is harder than it seems.\\
-
-%\noindent {\bfseries Design choices}
-%The launcher interface utilizes a number of techniques to aid users and simplify
-%the choices they have to make. Help buttons and a support email address that
-%appears on every screen are meant to assist users that get stuck in the process.
-%The interface also makes good use of defaults, for example by emphasizing that
-%certain options ``will work in most situations.''
-%
-%Still, there remains potential for confusion, especially with the more advanced
-%configuration options.
-%Bridges, pluggable transports, and proxies are never defined for the user,
-%arguably because they might not read or understand these definitions.
-%This can lead to users confusing these terms, or not understanding
-%the relations between them. Additionally, there is limited explanation of 
-%what pluggable transport types to choose from if the default one fails or how to 
-%find proxy settings, which will be required of some users.
-
-What to talk about in this section: 
+Changes made: 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item Talk about the process of translating observations and feedback into feature changes. 
-\item Polishing the interface by working with a designer, using heuristics, and using technical information. 
-\item Iterative design and feedback cycle. 
-\item How we made a functional, instrumented prototype (forking from the interface repo on github and hacking on it) and instrumented the old prototype. 
+\item Made first screen more clear to help users decide on connect vs configure. 
+\item Got rid of question screens. 
+\item Put the proxy first. It makes sense topologically. 
+\item Added auto-detect for proxies. 
+\item Gave explicit advice on how to choose bridges. 
+\item Added a summary screen. 
+\item Added a topological progress bar that works every time. 
+\item Gives instructions on what to try next after failure. 
+\item Greatly reduced text and made text easier to read. 
+\item Less visual clutter for users. Hide things until user clicks on them. 
 \end{itemize}
@@
 Talk about how the design as a conservative design. And why the conservative choices were made. For at-risk users, maintainability, etc.
-}
 

### 2016-04-05 experiment/processing/graphs.R
Add # of DNFs to time_to_success graphs.

@@ -12,11 +12,15 @@ clamp_time_to_success <- function(participants, maxtime) {
 }
 
 time_to_success_plot <- function(participants) {
-	p <- ggplot(participants, aes(x=label, y=time_to_success/60))
+	minutes_to_success <- participants$time_to_success/60
+	p <- ggplot(data.frame(participants, minutes_to_success), aes(x=label, y=minutes_to_success), environment=environment())
 	p <- p + geom_boxplot(color="gray70", outlier.size=0)
 	p <- p + geom_point(size=0.8, alpha=0.6)
 	p <- p + coord_flip()
+	p <- p + scale_y_continuous(limits=c(0, max(minutes_to_success, na.rm=T)+9))
 	p <- p + labs(title=NULL, x=NULL, y="Minutes to first success")
+	counts <- aggregate(data.frame(participants, n=1)[, c("success", "n")], by=list(label=participants$label), sum)
+	p <- p + geom_text(data=counts, aes(x=label, y=max(minutes_to_success, na.rm=T)+9, label=sprintf("%d/%d DNF", n-success, n)), hjust=1, size=2, alpha=0.6)
 	p <- common_theme(p)
 	p
 }

### 2016-04-05 pets2017-paper/pets2017-paper.tex
Explain DNFs in the figure caption.
formatting tweaks, intros, and todos

@@
 \subsection{Methodology} 
+In this section, we talk about the details of our qualitative user study, such as the censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.
+
 \subsubsection{Setup}
@@
 
-\subsubsection{Results} 
+\subsection{Results} 
 In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems.
@@
 
-\noindent {\bfseries Connect vs. Configure} 
+\subsubsection{Connect vs. Configure} 
 The first task for our participants was to decide between connecting directly to the Tor network or configuring their connection.
@@
 
-\noindent {\bfseries Bridge Configuration} 
+\subsubsection{Bridge Configuration} 
 When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary.
@@
 
-\noindent {\bfseries Proxy Configuration} 
+\subsubsection{Proxy Configuration} 
 After the bridge configuration, the participant again is asked to answer a question to determine if they need a proxy and if so, to configure one.
@@
 
-\noindent{\bfseries Progress Bar} 
+\subsubsection{Progress Bar} 
 Users were generally displeased with the lack of feedback on the progress bar.
@@
 
-\noindent{\bfseries User Communication Failure} Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary.
+\subsubsection{User Communication} 
+Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary. 
 \begin{quotation}
@@
 
-\noindent{\bfseries Final Thoughts}
-We believe that the interface is too technical for users to understand and overburdens users with tasks.
-From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.
-
 %\begin{quotation}
@@
 \section{Redesigning the Configuration Interface}
+We believe that the interface is too technical for users to understand and overburdens users with tasks.
+From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.
 
@@
 Changes made:
+
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
@@
 
-Talk about how the design as a conservative design. And why the conservative choices were made. For at-risk users, maintainability, etc.
+The design is a conservative design which accounts for at-risk users, backward compatibility, and maintainability.
 
@@
 \subsection{Methodology} 
+In this section, we talk about the details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.
+
 \subsubsection{Setup}
@@
 while the boxplots show the medians and interquartile ranges.
+The ``DNF'' figures at the right
+show the number of participants who did not finish
+in the time alloted.
 }
@@
 
-{\color {red} This will be the main part of the paper--where we report on the data that we collected through the xlab experiment.
-Some of the questions we want to answer are: did the new interface improve success rate?
-did the new interface only help certain people?
-Did people take longer or shorter in the new version?
-Did we shift participants' behaviors in the new interface?
-Are the way people approach trying different configurations affected?
-are there existing problems for both interfaces?
-(we know for sure that users still not receiving feedback is an issue.
-I don't know how many of our participants actually saw our helpful error messages, since they took minutes to pop up, and some never pop up at all..)}
+{\color {red} 
+What to talk about: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item{Did the new interface improve the success rate?}
+\item{Did the new interface help in only certain environments or certain people?}
+\item{Did the new interface improve the time to success?}
+\item{What are remaining issues?} 
+\item{What people did while configuring the interface}
+\item{Where people downloaded Tor browser if they did it themselves} 
+\item{Xlab versus craigslist} 
+\end{itemize}
+
+Graph: 
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\item{success rate}
+\item{time to success: distribution}
+\item{time to success: cdf and cutoffs at 2 min, 10 min, 20 min?}  
+\item{time spent on each screen}
+\item{order pluggable transports were chosen}
+\item{transitions between windows for all participants}
+\end{itemize} 
+}
 
@@
 Wait to fill this section out until we have finished analyzing the data from the quantitative
-user study experiment. A lot of the future work can be in reference to this. Or, we can even
-talk about what is in the discussion section. ... OR, maybe this section isn't even necessary.\\
+user study experiment. OR, maybe this section isn't even necessary.\\
 

### 2016-04-05 experiment/processing/graphs.R
Use device=cairo_pdf in graphs.
I have found this necessary in the past to get fonts embedded correctly.
The text in the graphs is not showing up on lnl's TeXworks previewer.

@@ -29,7 +29,7 @@ participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E3-OLD", "E3-NEW", "E2-OLD", "E2-NEW", "E1-OLD", "E1-NEW"))
 
 p <- time_to_success_plot(participants)
-ggsave("time_to_success.pdf", p, width=textwidth, height=height)
+ggsave("time_to_success.pdf", p, width=textwidth, height=height, device=cairo_pdf)
 
 p <- time_to_success_plot(clamp_time_to_success(participants, 40*60))
-ggsave("time_to_success_clamped.pdf", p, width=textwidth, height=height)
+ggsave("time_to_success_clamped.pdf", p, width=textwidth, height=height, device=cairo_pdf)

### 2016-04-05 experiment/processing/graphs.R
Make a time_to_success_ecdf graph.

@@ -1,4 +1,6 @@
 library(ggplot2)
+library(scales)
+library(RColorBrewer)
 
 source("common.R")
 
@@ -35,3 +37,33 @@ ggsave("time_to_success.pdf", p, width=textwidth, height=height, device=cairo_pd
 
 p <- time_to_success_plot(clamp_time_to_success(participants, 40*60))
 ggsave("time_to_success_clamped.pdf", p, width=textwidth, height=height, device=cairo_pdf)
+
+
+# Assign each environment a color (E1=blue, E2=orange, E3=green), with NEW
+# being more saturated and OLD being less saturated.
+palette <- c(
+	brewer.pal(3, "Blues")[c(3,2)],
+	brewer.pal(3, "Oranges")[c(3,2)],
+	brewer.pal(3, "BuGn")[c(3,2)]
+)
+names(palette) <- levels(participants$label)
+
+max_minutes <- max(participants$time_to_success, na.rm=T) / 60
+# Artificially add a success time that is way off the scale for all
+# participants that were not successful. Otherwise the ecdf will ignore the NAs
+# and cause all the curves to rise to 100%. The artificial points will be
+# hidden off the edge of the graph by coord_cartesian.
+participants$time_to_success[is.na(participants$time_to_success)] <- max(participants$time_to_success, na.rm=T)*2
+minutes_to_success <- participants$time_to_success/60
+p <- ggplot(participants, aes(x=minutes_to_success, color=label))
+p <- p + geom_step(stat="ecdf", size=0.5)
+p <- p + coord_cartesian(xlim=c(0, max_minutes))
+p <- p + scale_y_continuous(labels=percent)
+p <- p + scale_color_manual(values=palette)
+# p <- p + guides(color=guide_legend(override.aes=list(size=2, title=NULL)))
+p <- p + guides(color=F)
+p <- p + labs(title=NULL, x="Minutes elapsed", y="Successful participants")
+p <- p + annotate(geom="text", x=c(1), y=c(0.86), label=c("E1-\nNEW"), hjust=1, vjust=0, size=2, lineheight=0.8, alpha=0.6)
[…]

### 2016-04-05 pets2017-paper/pets2017-paper.tex
mark undone red
Add labels to figures.
Include time_to_success_ecdf figure.

@@
 %skip talking about the process of redesigning the interface. It isn't that interesting. 
+{\color {red}
 
@@
 The design is a conservative design which accounts for at-risk users, backward compatibility, and maintainability. 
+}
 
@@
 }
+\label{fig:time_to_success}
 \end{figure}
@@
 }
+\label{fig:time_to_success_clamped}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{time_to_success_ecdf}
+% From info.R:
+% success rate of E1-NEW after 1m30.0s: 100.0%
+% success rate of E1-OLD after 1m30.0s:  57.9%
+% success rate of E2-NEW after 10m00.0s:  78.9%
+% success rate of E2-OLD after 10m00.0s:  68.4%
+% success rate of E3-NEW after 10m00.0s:  25.0%
+% success rate of E3-OLD after 10m00.0s:  20.0%
+% success rate of E2-NEW after 20m00.0s:  89.5%
+% success rate of E2-OLD after 20m00.0s:  78.9%
+% success rate of E3-NEW after 20m00.0s:  45.0%
+% success rate of E3-OLD after 20m00.0s:  25.0%
+\caption{
+Cumulative success rates over time.
+We stopped participants after 40 minutes;
+this graph shows what the success rate would have been
+at different cutoff times.
+For example, every E1-NEW participant finished within 90 seconds,
+but only 58\% of E1-OLD had finished by that time.
+After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
+After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
+}
+\label{fig:time_to_success_ecdf}
 \end{figure}

### 2016-04-05 experiment/processing/info.R
Output a table of median times to success.
median time to success per condition
  env version        x
1  E1     NEW  0m20.4s
2  E2     NEW  3m21.6s
3  E3     NEW 12m38.1s
4  E1     OLD  1m00.7s
5  E2     OLD  4m00.6s
6  E3     OLD 18m15.7s

@@ -6,6 +6,14 @@ pctsummary <- function(x) {
 	sprintf("%d/%d = %5.1f%%", sum(x), length(x), 100*mean(x))
 }
 
+format_minutes <- function(x) {
+	sprintf("%dm%04.1fs", x %/% 60, x %% 60)
+}
+
+median_time_summary <- function(x) {
+	format_minutes(median(x, na.rm=T))
+}
+
 cat(sprintf("number of participants: %d (%d good, %d bad)\n",
 	length(participants$good), sum(participants$good), sum(!participants$good)))
 
@@ -43,3 +51,8 @@ for (env in levels(participants$env)) {
 	cat(sprintf("t-test of time_to_success in env %s\n", as.character(env)))
 	try(print(with(participants[participants$env==env, ], t.test(time_to_success[version=="NEW"], time_to_success[version=="OLD"]))))
 }
+
+
+cat("\n")
+cat(sprintf("median time to success per condition\n"))
+with(participants, aggregate(time_to_success, list(env=env, version=version), median_time_summary))

### 2016-04-05 experiment/processing/info.R
Output completion rates at some selected times.

@@ -2,8 +2,12 @@ source("common.R")
 
 participants <- read_participants()
 
+format_percent <- function(x) {
+	sprintf("%5.1f%%", 100*x)
+}
+
 pctsummary <- function(x) {
-	sprintf("%d/%d = %5.1f%%", sum(x), length(x), 100*mean(x))
+	sprintf("%d/%d = %s", sum(x), length(x), format_percent(mean(x)))
 }
 
 format_minutes <- function(x) {
@@ -56,3 +60,33 @@ for (env in levels(participants$env)) {
 cat("\n")
 cat(sprintf("median time to success per condition\n"))
 with(participants, aggregate(time_to_success, list(env=env, version=version), median_time_summary))
+
+
+time_ecdf <- function(participants, env, version) {
+	ecdf(
+		ifelse(!is.na(participants$time_to_success),
+			participants$time_to_success,
+			2*max(participants$time_to_success, na.rm=T)
+		)[participants$env==env & participants$version==version]
+	)
+}
+
+ecdf.e1.new <- time_ecdf(participants, "E1", "NEW")
+ecdf.e1.old <- time_ecdf(participants, "E1", "OLD")
+ecdf.e2.new <- time_ecdf(participants, "E2", "NEW")
+ecdf.e2.old <- time_ecdf(participants, "E2", "OLD")
+ecdf.e3.new <- time_ecdf(participants, "E3", "NEW")
+ecdf.e3.old <- time_ecdf(participants, "E3", "OLD")
+
+cat("\n")
+max.e1.new <- max(participants$time_to_success[participants$env=="E1" & participants$version=="NEW"])
+cat(sprintf("maximum time for E1-NEW: %s\n", format_minutes(max.e1.new)))
+for (t in c(max.e1.new, 90, 10*60, 20*60)) {
+	cat("\n")
+	cat(sprintf("success rate of E1-NEW after %s: %s\n", format_minutes(t), format_percent(ecdf.e1.new(t))))
+	cat(sprintf("success rate of E1-OLD after %s: %s\n", format_minutes(t), format_percent(ecdf.e1.old(t))))
+	cat(sprintf("success rate of E2-NEW after %s: %s\n", format_minutes(t), format_percent(ecdf.e2.new(t))))
+	cat(sprintf("success rate of E2-OLD after %s: %s\n", format_minutes(t), format_percent(ecdf.e2.old(t))))
[…]

### 2016-04-05 experiment/processing/info.R
Have info.R output a LaTeX table of ECDF values.

@@ -81,12 +81,26 @@ ecdf.e3.old <- time_ecdf(participants, "E3", "OLD")
 cat("\n")
 max.e1.new <- max(participants$time_to_success[participants$env=="E1" & participants$version=="NEW"])
 cat(sprintf("maximum time for E1-NEW: %s\n", format_minutes(max.e1.new)))
-for (t in c(max.e1.new, 90, 10*60, 20*60)) {
-	cat("\n")
-	cat(sprintf("success rate of E1-NEW after %s: %s\n", format_minutes(t), format_percent(ecdf.e1.new(t))))
-	cat(sprintf("success rate of E1-OLD after %s: %s\n", format_minutes(t), format_percent(ecdf.e1.old(t))))
-	cat(sprintf("success rate of E2-NEW after %s: %s\n", format_minutes(t), format_percent(ecdf.e2.new(t))))
-	cat(sprintf("success rate of E2-OLD after %s: %s\n", format_minutes(t), format_percent(ecdf.e2.old(t))))
-	cat(sprintf("success rate of E3-NEW after %s: %s\n", format_minutes(t), format_percent(ecdf.e3.new(t))))
-	cat(sprintf("success rate of E3-OLD after %s: %s\n", format_minutes(t), format_percent(ecdf.e3.old(t))))
+
+ecdfs <- list(
+	"E1-NEW"=ecdf.e1.new,
+	"E1-OLD"=ecdf.e1.old,
+	"E2-NEW"=ecdf.e2.new,
+	"E2-OLD"=ecdf.e2.old,
+	"E3-NEW"=ecdf.e3.new,
+	"E3-OLD"=ecdf.e3.old
+)
+
+cat("\n")
+cat("\\begin{tabular}{l r r r r}\n")
+cat("& \\multicolumn{1}{c}{1.5~m} & \\multicolumn{1}{c}{10~m} & \\multicolumn{1}{c}{20~m} & \\multicolumn{1}{c}{40~m} \\\\\n")
+cat("\\noalign{\\hrule}\n")
+for (e in names(ecdfs)) {
+	cat(e)
+	# We fudge the 40 minute column because the last E3-OLD finished just a few seconds after.
+	for (t in c(90, 10*60, 20*60, max(participants$time_to_success, na.rm=T))) {
+		cat(sprintf(" & %.f\\%%", 100*ecdfs[[e]](t)))
+	}
+	cat(sprintf(" \\\\\n"))
 }
+cat("\\end{tabular}\n")

### 2016-04-05 pets2017-paper/pets2017-paper.tex
Include a table in the time_to_success_ecdf figure.
The code for the table is output by info.R.
finish redesign section

@@
 \section{Goals/Evaluation Criteria}
+\label{sec:goals}
 We evaluate the existing and redesigned Tor Browser configuration interface 
@@
     \item {\bfseries User Control and Freedom} allow users to override system, supports undo and redo actions. 
+    \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
     \item {\bfseries Understandable Language} ~6th grade reading level. 
-    \item {\bfseries Minimal Design} surpressing rarely used information to reduce cognitive load. 
-    \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
-    \item {\bfseries Help and Documentation} provide contextual help and easy access to information. 
+    \item {\bfseries Minimal Design} suppressing rarely used information to reduce cognitive load. 
 \end{enumerate}
@@
 \section{Redesigning the Configuration Interface}
-We believe that the interface is too technical for users to understand and overburdens users with tasks.
-From our observations in this qualitative study, our goal in redesigning the interface was to making the vocabulary more accessible to the average user, requiring the user to make fewer decisions, and automating parts of configuration that don't increase risk to high-risk users.
+%skip talking about the process of redesigning the interface. It isn't that interesting.
+
+% Heuristic evaluation metrics, from above: 
+% \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+%     \item {\bfseries Visibility of System Status} provide feedback on what the system is doing.
+%     \item {\bfseries User Control and Freedom} allow users to override system, supports undo and redo actions. 
+%     \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
+%     \item {\bfseries Understandable Language} ~6th grade reading level. 
+%     \item {\bfseries Minimal Design} suppressing rarely used information to reduce cognitive load. 
+% \end{enumerate}
+
+Tor Browser 5.0.3.
+configuration interface does not adequately meet our heuristic evaluation criteria from Section ~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+The configuration used for a connection is not visible to the users before they connect or while they are connecting, full control but little guidance through the configuration process confuse users, error messages do not express errors in plain language of offers solutions, the text was too technical for an average user to understand, and the interface has room be simplified visually.
+
+Currently, the interface overburdens users.
+Our goals in redesigning the interface was to making the system status visible to the user, retain user freedom but give guidance, make the vocabulary more accessible, offer solutions upon errors, and to require the user to make fewer decisions overall.
+To achieve these goals, we made the following changes:
 
@@
 
-%skip talking about the process of redesigning the interface. It isn't that interesting. 
-{\color {red}
+\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\item {\bfseries Added system status visibility.} Before any attempt to connect to the Tor network, a summary screen displays if a bridge or proxy is configured, and if so, what the configurations are.
+The progress screen also displays the configurations while the connection attempt is being made.
+\item {\bfseries Added guidance on choosing connect vs configure.} We labeled the configure option as advanced, manual, and only for heavily censored situations. 
+\item {\bfseries Got rid of proxy and bridge questions.}  We removed the bridge and proxy questions, which were highly technical and challenging for users to answer.
+There are two less windows in the interface.
+\item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files.
+This is safe even for at-risk users, and greatly simplifies the configuration process.
+\item {\bfseries Switched ordering to configure proxies first.} To build up the users' mental model, we configure network components in a topologically sequential.
+Proxies were put after bridge configuration because only a small fraction of users require proxies.
+With auto-detection, configuring a proxy before a bridge will not burden the users.
+\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3.
+There is added text that advises users to try a meek bridge if obfs3 does not work.
+This advice is tailored for our participants who were in the advanced censorship environment.
+\item {\bfseries Added more feedback to the progress bar.} The progress bar shows network components involved in connecting to the Tor network and gives feedback to the user as they are correctly configured.
+For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network.
+Upon failure, users can see which components that have succeeded and which have failed.
+\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, advice on what to try next is shown to the user.
+Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy.
+\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more accessible by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users.
+Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
+\item {\bfseries Reduced visual clutter.} Whenever we could, we minimized the amount of text on the screen, hid additional fields until the relevant options were chosen, and made additional stylistic simplifications.
+\end{enumerate}
 
-Changes made:
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item Made first screen more clear to help users decide on connect vs configure. 
-\item Got rid of question screens. 
-\item Put the proxy first. It makes sense topologically. 
-\item Added auto-detect for proxies. 
-\item Gave explicit advice on how to choose bridges. 
-\item Added a summary screen. 
-\item Added a topological progress bar that works every time. 
-\item Gives instructions on what to try next after failure. 
-\item Greatly reduced text and made text easier to read. 
-\item Less visual clutter for users. Hide things until user clicks on them. 
-\end{itemize}
-
-The design is a conservative design which accounts for at-risk users, backward compatibility, and maintainability. 
-}
+The redesigned interface maintains the approach taken by the deployed interface of asking the users about their situation, which is in the spirit of the deployed interface.
+The designed interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components.
+The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may changes as the censorship environments change.
+For additional changes that can be made and alternate approaches for interacting with the user, see Section ~\ref{sec:discussion}.
 
@@
 \includegraphics{time_to_success_ecdf}
-% From info.R:
-% success rate of E1-NEW after 1m30.0s: 100.0%
-% success rate of E1-OLD after 1m30.0s:  57.9%
-% success rate of E2-NEW after 10m00.0s:  78.9%
-% success rate of E2-OLD after 10m00.0s:  68.4%
-% success rate of E3-NEW after 10m00.0s:  25.0%
-% success rate of E3-OLD after 10m00.0s:  20.0%
-% success rate of E2-NEW after 20m00.0s:  89.5%
-% success rate of E2-OLD after 20m00.0s:  78.9%
-% success rate of E3-NEW after 20m00.0s:  45.0%
-% success rate of E3-OLD after 20m00.0s:  25.0%
+
+% Generated by info.R:
+\begin{tabular}{l r r r r}
+& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
+\noalign{\hrule}
+E1-NEW & 100\% & 100\% & 100\% & 100\% \\
+E1-OLD & 58\% & 100\% & 100\% & 100\% \\
+E2-NEW & 11\% & 79\% & 89\% & 95\% \\
+E2-OLD & 16\% & 68\% & 79\% & 84\% \\
+E3-NEW & 0\% & 25\% & 45\% & 65\% \\
+E3-OLD & 0\% & 20\% & 25\% & 50\% \\
+\end{tabular}
+
 \caption{
@@
 \section{Discussion} 
-
+\label{sec:discussion}
 If we had more concrete information on the number of high-risk users or users who need to configure a proxy, we would have made additional changes in the prototype.

### 2016-04-05 pets2017-paper/pets2017-paper.tex
rename weird results subsubsubsection
future work section

@@
 
-\subsubsection{Results}
+\subsubsection{Changes During the Experiment}
 
@@
 \section{Future Work} 
-{\color {red}
-Wait to fill this section out until we have finished analyzing the data from the quantitative
-user study experiment. OR, maybe this section isn't even necessary.\\
+Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers.
+Redesigning the configuration interface was a mutual interest.
+In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface.
+We plan to continue our work with Tor developers to integrate changes we found to be helpful.
+This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.
 
-\noindent {\bfseries Changing the Current Interface} merge, push. \\
-
-\noindent{\bfseries Finishing Touches} 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
-\item {\bfseries Detecting the need for proxies.} We hacked this together for now. 
-\item {\bfseries Handling rare error cases.} Mention clock drift and proxy connection cases.
-\item {\bfseries Additional user feedback.} Animation in the progress window. 
-\item {\bfseries Stylization.} Comply with design style guides, if any. 
-\end{itemize}
-
-\noindent{\bfseries Measuring Impact} Tor metrics to see if this is helping at the large scale, and for future user study work in general. 
-}
+Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes.
+Currently, the deployed nor redesigned interface achieves this goal.
+Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
+We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section \ref{sec:discussion}.
 

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Fix typo and note TODO

@@
 
-This mistake can results in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments.
+This mistake can result in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments.
+% FIXME:
 Participants in the intermediate and advanced censorship environments who did correctly choose to configure in intermediate did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.

### 2016-04-06 pets2017-paper/pets2017-paper.tex
add acknowledgements and uncited references
PETS2017 style.

@@
-\documentclass{template}
+\documentclass[USenglish,oneside,twocolumn]{article}
 \usepackage{color}
@@
 \usepackage{pdfpages}
-\usepackage{hyperref}
+%\usepackage{hyperref}
 
-\def\etal{{\it et al.~}}
-\newenvironment{packed_enum}{
-\begin{enumerate}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{enumerate}}
-\newenvironment{packed_item}{
-\begin{itemize}
-  \setlength{\itemsep}{1pt}
-  \setlength{\parskip}{0pt}
-  \setlength{\parsep}{0pt}
-}{\end{itemize}}
+\usepackage[utf8]{inputenc}%(only for the pdftex engine)
+%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
+\usepackage[big]{dgruyter_NEW}
+
+\DOI{foobar}
+
+\cclogo{\includegraphics{by-nc-nd.pdf}}
 
@@
 
-%what I really want to say is that the interesting aspect of this usable design is that we had to 
-%account for people who wouldn't need to use this launcher at all and also for at-risk users.
-%... but in one catchy title. I can't think of one.
-\title{Tor's Usability for Censorship Circumvention}
-\numberofauthors{1}
-\author{
- \alignauthor Linda N. Lee, David Fifield, Nathan Malkin \\
-   \vspace{0.5em}
-   \affaddr{University of California, Berkeley} \\
-   \affaddr{\{lnl,fifield,nmalkin\}@cs.berkeley.edu}\\
-}
-\maketitle
+  \author*[1]{Linda Lee}
+
+  \author[2]{David Fifield}
+
+  \author[3]{Nathan Malkin}
+
+  \author[4]{Ganesh Iver}
+
+  \author[5]{Serge Egelman}
+
+  \author[6]{David Wagner}
+
+  \affil[1]{Affil, E-mail: lnl@cs.berkeley.edu}
+
+  \affil[2]{Affil, E-mail: fifield@eecs.berkeley.edu}
+
+  \affil[3]{Affil, E-mail: nmalkin@cs.berkeley.edu}
+
+  \affil[4]{Affil, E-mail: ganesh.v@berkeley.edu}
+
+  \affil[5]{Affil, E-mail: egelman@cs.berkeley.edu}
+
+  \affil[6]{Affil, E-mail: daw@cs.berkeley.edu}
+
+  \title{\huge Tor's Usability for Censorship Circumvention}
+
+  \runningtitle{Tor's Usability for Censorship Circumvention}
+
+  %\subtitle{...}
 
   \begin{abstract}
-\indent \indent
-Tor has grown beyond its original purpose as an anonymity tool and has 
+{Tor has grown beyond its original purpose as an anonymity tool and has 
 since become an important censorship circumvention tool. It is now listed
@@
 process and redesign the interface to improve success rate to {\color {red} TODO}\% 
-and average completion time to {\color {red} TODO} minutes.
+and average completion time to {\color {red} TODO} minutes.}
 \end{abstract}
+  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
+%  \classification[PACS]{}
+ % \communicated{...}
+ % \dedication{...}
 
-\keywords{User Studies, Tor, Security, Censorship, Anonymity}
+  \journalname{Proceedings on Privacy Enhancing Technologies}
+\DOI{Editor to enter DOI}
+  \startpage{1}
+  \received{..}
+  \revised{..}
+  \accepted{..}
+
+  \journalyear{2015}
+  \journalvolume{2015}
+  \journalissue{2}
+
+\maketitle
 
@@
 \section {Acknowledgments}
-{\color {red} TODO}
+{\color {red} Rowie for setting up Xlab, Ganesh for helping us redesign the Interface, Nima, Isa, Georg, and the UX team for giving feedback, and Cecile for reviewing the UI of circumvention tools.}
 
+% Rowie
+% Ganesh
+% Nima, Isa, Georg, Tor UX team. 
 % Cecile Basnage for review of the UI of circumvention tools.
@@
 \bibliographystyle{abbrv}
+\nocite{*}
 \bibliography{pets2017-paper}
@@
 Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment. 
-
 \end{document}

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Miscellaneous tiny fixes.

@@
 since become an important censorship circumvention tool. It is now listed
-as one of the ways that normal people use Tor \cite{whotor}.
+as one of the ways that normal people use Tor~\cite{whotor}.
 We specifically examine its usability as a censorship circumvention tool,
@@
 Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
-Lee and Fifield \cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
+Lee and Fifield~\cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
 This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
@@
 study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
-Internet censorship is pervasive across the world today \cite{faris2008measuring}. 
+Internet censorship is pervasive across the world today~\cite{faris2008measuring}. 
 Although Tor was not designed to be a censorship circumvention tool, users started
@@
 incorporated into Tor, making it a viable censorship circumvention tool even in the face
-of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason \cite{winter2012great}. 
+of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
 To our knowledge, this is the first user study investigating the usability of Tor as a 
@@
 \subsection{The Current Configuration Interface} 
-The Tor Browser provides a configuration interface to guide users through setting up 
+Tor Browser provides a configuration interface to guide users through setting up 
 their connection. While most can connect to Tor using the
@@
 The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure.
-For a successful configuration, users are required to know the following:
+For a successful configuration, users are required to know (or find out) the following:
 
@@
 configuration interface through user observation and interviews can be 
-found in section {\color{red} TODO}. A heuristic evaluation of the existing interfaceand new interface is in section {\color{red} TODO}. We empirically show 
+found in Section~{\color{red} TODO}. A heuristic evaluation of the existing interface and new interface is in Section~{\color{red} TODO}. We empirically show 
 that the redesigned interface improves completion rate, reduces time to completion, 
-and provides a safe path for at-risk users in section {\color{red} TODO}.
+and provides a safe path for at-risk users in Section~{\color{red} TODO}.
 
@@
 \subsubsection{Recruitment}
-Using established best practices from the field of user experience research
-(\cite{howmanyusers}), we recruited 5 participants for each censorship environment.
+Using established best practices from the field of user experience research~\cite{howmanyusers},
+we recruited 5 participants for each censorship environment.
 We pre-screened our participants for diversity of gender, age, technical expertise,
@@
 We recruited our users from Craigslist. The recruitment text can be found in 
-Appendix \ref{qualitative-recruitment}. The recruitment posting contained a 
+Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
 SurveyGizmo online survey that collected information about our participants.
-The complete prescreening survey can be found in Appendix \ref{qualitative-prescreening}.
+The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.
 
@@
 
-The 1-hour, single-participant procedure begins when a participant enters a small 
+The one-hour, single-participant procedure begins when a participant enters a small 
 room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
@@
 simulated censorship environment, where some websites and services are blocked. 
-For the full script of what participants have heard, see Appendix \ref{qualitative-script}. We
+For the full script of what participants have heard, see Appendix~\ref{qualitative-script}. We
 instruct them to visit a sample blocked website and a sample non-blocked website on a
@@
 with specific questions we had for a particular participant from observing their screen. 
-This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window 3'').  
+This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window~3'').  
 After their interview, participants were informed that the experiment was over and 
-given their payment of \$30.
+given their payment of~\$30.
 
@@
 Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring.
-We confirm the statistical significance of some of the problems in our quantitative study (section ~\ref {sec:quantitative}.
+We confirm the statistical significance of some of the problems in our quantitative study (Section~\ref{sec:quantitative}).
 All quotes are paraphrased from live transcriptions of participant interviews.\\
@@
 Hmm, is it going to crash?
-When you see connect, you want to click it because you really want it to connect..''}
+When you see connect, you want to click it because you really want it to connect.''}
 \end{quotation}
@@
 When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary.
-Answering yes to ``Does your Internet Service Provider (ISP) block of otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen.
+Answering yes to ``Does your Internet Service Provider (ISP) block or otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen.
 We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error.
@@
 And upon the first attempt at configuration, most chose the default value of not configuring a proxy.
-However, the most common reason for of failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead.
+However, the most common reason for failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead.
 Currently, no information was given upon failing to connect, which caused our participants to draw their own (incorrect) conclusions after a failed connection.
@@
 \begin{quotation}
-\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, of if it was just slow.''}
+\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
 \end{quotation}
@@
 %\begin{quotation}
-%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite... they only want the elite to use some computer things..''} \\
+%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite\ldots they only want the elite to use some computer things..''} \\
 %\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''}\\
@@
 Tor Browser 5.0.3.
-configuration interface does not adequately meet our heuristic evaluation criteria from Section ~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-The configuration used for a connection is not visible to the users before they connect or while they are connecting, full control but little guidance through the configuration process confuse users, error messages do not express errors in plain language of offers solutions, the text was too technical for an average user to understand, and the interface has room be simplified visually.
+configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+The configuration used for a connection is not visible to the users before they connect or while they are connecting, full control but little guidance through the configuration process confuse users, error messages do not express errors in plain language nor offer solutions, the text was too technical for an average user to understand, and the interface has room to be simplified visually.
 
@@
 The designed interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components.
-The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may changes as the censorship environments change.
-For additional changes that can be made and alternate approaches for interacting with the user, see Section ~\ref{sec:discussion}.
+The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change.
+For additional changes that can be made and alternate approaches for interacting with the user, see Section~\ref{sec:discussion}.
 
@@
 censorship environments and what configurations are necessary for a 
-successful connection can be found in Section \ref{sec:setup}.
+successful connection can be found in Section~\ref{sec:setup}.
 
@@
 was due to both data analysis considerations (large enough to have good effect size, 
-with a minimum of 20 to be able to assume normal distributions) and funding
-limitations.
+with a minimum of 20 to be able to assume normal distributions) and
+available funding.
 
@@
 half of our participants from Craigslist to ensure a diverse set of participants. 
-The recruitment text can be found in Appendix \ref{quantitative-recruitment}.
+The recruitment text can be found in Appendix~\ref{quantitative-recruitment}.
 
@@
 
-The 1-hour, multi-participant procedure begins when all participants are sitting at their
+The one-hour, multi-participant procedure begins when all participants are sitting at their
 respective computers in Xlab. Each computer is equipped with an old or modified version
@@
 simulated censorship environment, where some websites and services are blocked. 
-For the full script of what participants have heard, see Appendix \ref{quantitative-script}. We
+For the full script of what participants have heard, see Appendix~\ref{quantitative-script}. We
 instruct them to visit a sample blocked website on a non-Tor browser of their choice to illustrate 
@@
 After instructions, researchers maintained minimal interactions with the participants, 
-only answering logistical questions. Participants had an 
-average of 40 minutes to complete their worksheet. 
+only answering logistical questions. Participants had
+40 minutes to complete their worksheet. 
 The participants do not know the details of their censorship environment,
@@
 
-After users completed the browsing tasks, they take a short exit survey (Appendix \ref{quantitative-exit-survey})
+After users completed the browsing tasks, they take a short exit survey (Appendix~\ref{quantitative-exit-survey})
 collecting their demographics. All users were instructed to sit until the end of the experiment,
@@
 \item{success rate}
-\item{time to success: distribution}
-\item{time to success: cdf and cutoffs at 2 min, 10 min, 20 min?}  
 \item{time spent on each screen}
@@
 Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
-We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section \ref{sec:discussion}.
+We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section~\ref{sec:discussion}.
 
@@
 Ideally, we would people to click connect, and then try the manual configuration if a direct connection fails.
-We currently do not communicate this because may put some users at risk.
+We currently do not communicate this because it may put some users at risk.
 However, it is believed that a majority of the users will succeed if they click connect on the first screen, and giving them instructions on what to do can lessen their cognitive load during the configuration process.
 \item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
-The amount of people who use proxies is low, but then ...
-this would not give users control in the beginning of the configuration process.
+The amount of people who use proxies is low, but then \ldots this would not give users control in the beginning of the configuration process.
 \item{\bfseries Help the at-risk users.} There are people who would benefit from, on the first attempt, connecting with a meek bridge or custom bridge, without trying a vanilla tor connection or the recommended bridge in the dialog.
@@
 \section{Qualitative User Study Recruitment Posting} 
+\label{qualitative-recruitment}
 We are recruiting participants for an in-person research study at the University of California, Berkeley.
@@
 Fill out the question on the worksheet.
-This isn’t intended to be hard, just write what you see.
+This isn't intended to be hard, just write what you see.
 We want to just check you saw the website.

### 2016-04-06 pets2017-paper/pets2017-paper.tex
linda's insignificant changes. Mostly formatting.

@@
 
-  \affil[1]{Affil, E-mail: lnl@cs.berkeley.edu}
+  \affil[1]{University of Caifornia Berkeley, E-mail: lnl@cs.berkeley.edu}
 
-  \affil[2]{Affil, E-mail: fifield@eecs.berkeley.edu}
+  \affil[2]{University of Caifornia Berkeley, E-mail: fifield@eecs.berkeley.edu}
 
-  \affil[3]{Affil, E-mail: nmalkin@cs.berkeley.edu}
+  \affil[3]{University of Caifornia Berkeley, E-mail: nmalkin@cs.berkeley.edu}
 
-  \affil[4]{Affil, E-mail: ganesh.v@berkeley.edu}
+  \affil[4]{University of Caifornia Berkeley, E-mail: ganesh.v@berkeley.edu}
 
-  \affil[5]{Affil, E-mail: egelman@cs.berkeley.edu}
+  \affil[5]{University of Caifornia Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}
 
-  \affil[6]{Affil, E-mail: daw@cs.berkeley.edu}
+  \affil[6]{University of Caifornia Berkeley, E-mail: daw@cs.berkeley.edu}
 
@@
 make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are
-four main ways to set up a connection:
+four ways to set up a connection:\\
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
+\begin{enumerate}
     \item With a bridge and proxy
@@
 The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure.
-For a successful configuration, users are required to know (or find out) the following:
+For a successful configuration, users are required to know (or find out) the following:\\
 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-	\item{Whether to connect directly or configure a connection.} 
+\begin{itemize}
+	\item{Whether they need to configure a connection.} 
 	\item{If the Tor Network is censored by their ISP.}
@@
 community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS})
-and other industry standards to form the following heuristic evaluation criteria: 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item {\bfseries Visibility of System Status} provide feedback on what the system is doing.
-    \item {\bfseries User Control and Freedom} allow users to override system, supports undo and redo actions. 
-    \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
-    \item {\bfseries Understandable Language} ~6th grade reading level. 
-    \item {\bfseries Minimal Design} suppressing rarely used information to reduce cognitive load. 
+and other industry standards to form the following heuristic evaluation criteria: \\
+
+\begin{enumerate}
+    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing.
+    \item  {\bfseries User control and freedom}: allow users to override system, supports undo and redo actions. 
+    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
+    \item  {\bfseries Understandable language}: ~6th grade reading level. 
+    \item  {\bfseries Minimal design}: suppressing rarely used information to reduce cognitive load. 
 \end{enumerate}
@@
 interface are from common metrics that measure ease of use with a special 
-consideration for high-risk users: 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-    \item {\bfseries Task Completion} Almost all can successfully connect to Tor
-    \item {\bfseries Time to Completion} Time to completion. 
-    \item {\bfseries Safe for High-Risk Users} It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
+consideration for high-risk users: \\
+
+\begin{enumerate}
+    \item {\bfseries Task Completion}: Almost all can successfully connect to Tor
+    \item {\bfseries  Time to Completion}: Time to completion. 
+    \item {\bfseries Safe for High-Risk Users}: It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
 \end{enumerate}
@@
 environment in any particular country, but to require our participants to 
-configure Tor Browser in distinct configurations.
+configure Tor Browser in distinct configurations. \\
 
 \begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Mild censorship} 
+\item {\bfseries Mild censorship (E1)}: 
 (Representative of countries such as France and Australia.)
@@
 
-\item {\bfseries Intermediate censorship} 
+\item {\bfseries Intermediate censorship (E2)}: 
 (Representative of countries such as Tunisia.)
@@
 
-\item {\bfseries Comprehensive censorship} 
+\item {\bfseries Comprehensive censorship (E3)}:
 (Representative of countries such as China and Syria.)
@@
 Our goals in redesigning the interface was to making the system status visible to the user, retain user freedom but give guidance, make the vocabulary more accessible, offer solutions upon errors, and to require the user to make fewer decisions overall.
-To achieve these goals, we made the following changes:
+To achieve these goals, we made the following changes: \\
 
@@
 What to talk about: 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\begin{itemize}
 \item{Did the new interface improve the success rate?}
@@
 Graph: 
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+\begin{itemize}
 \item{success rate}
@@
 Since we lacked this information, the following changes did not make it into our prototype, but are worth discussing.
-Depending on the number of high-risk users or proxy-configuring users, these additional changes may be helpful:
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+Depending on the number of high-risk users or proxy-configuring users, these additional changes may be helpful: \\
+
+\begin{itemize}
 \item {\bfseries Tell people to click connect.} On the first screen, the user needs to decide to connect or configure.
@@
 We believe that this is a sound approach to interacting with the user and the one we would recommend personally.
-However, there are alternative approaches to interacting with the user that may be of interest:
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt 
+However, there are alternative approaches to interacting with the user that may be of interest:  \\
+
+\begin{itemize}
 \item{\bfseries Automate the entire configuration process.} This sounds like a radical idea, but it really isn't.
@@
 You will be compensated \$30 for participating.
-No special knowledge and no technical experience is required.
-
-If you are interested, fill out the survey at \textit{<survey link>}.
+No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.
 
@@
 You will be compensated \$30 for participating.
-No special knowledge and no technical experience is required.
+No special knowledge and no technical experience is required.\\
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\begin{enumerate}
 \item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
@@
 \section{Post-Experiment Standard Interview Questions}
-We asked our participants these questions after they were given time to configure Tor Browser.
+We asked our participants these questions after they were given time to configure Tor Browser. \\
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\begin{enumerate}
 \item{Can you talk us through what you did along with what you were thinking at the time?}
@@
 If you have any questions about your rights or treatment as a research participant in this study, please contact the University of California at Berkeley's Committee for Protection of Human Subjects at 510-642-7461, or email subjects@berkeley.edu.
-If you agree to participate, please click Next below.
+If you agree to participate, please click Next below.\\
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\begin{enumerate}
 \item{What is your participant ID? (This can be found on the sticker ont he left hand corner of the desk you are currently sitting at.)}

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Typo.

@@
 
-  \affil[1]{University of Caifornia Berkeley, E-mail: lnl@cs.berkeley.edu}
+  \affil[1]{University of California Berkeley, E-mail: lnl@cs.berkeley.edu}
 
-  \affil[2]{University of Caifornia Berkeley, E-mail: fifield@eecs.berkeley.edu}
+  \affil[2]{University of California Berkeley, E-mail: fifield@eecs.berkeley.edu}
 
-  \affil[3]{University of Caifornia Berkeley, E-mail: nmalkin@cs.berkeley.edu}
+  \affil[3]{University of California Berkeley, E-mail: nmalkin@cs.berkeley.edu}
 
-  \affil[4]{University of Caifornia Berkeley, E-mail: ganesh.v@berkeley.edu}
+  \affil[4]{University of California Berkeley, E-mail: ganesh.v@berkeley.edu}
 
-  \affil[5]{University of Caifornia Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}
+  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}
 
-  \affil[6]{University of Caifornia Berkeley, E-mail: daw@cs.berkeley.edu}
+  \affil[6]{University of California Berkeley, E-mail: daw@cs.berkeley.edu}
 

### 2016-04-06 pets2017-paper/pets2017-paper.tex
\mbox email address to prevent line breaking.
It looked bad (and was ambiguous) to have lines broken like:

David Fifield: University of California Berkeley, E-mail: fi-
field@eecs.berkeley.edu

Serge Egelman: University of California Berkeley
and International Computer Science Institute, E-mail: egel-
man@cs.berkeley.edu

--- 2016-04-06 pets2017-paper/pets2017-paper.tex
@@
 
-  \affil[1]{University of Caifornia Berkeley, E-mail: lnl@cs.berkeley.edu}
+  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
 
-  \affil[2]{University of Caifornia Berkeley, E-mail: fifield@eecs.berkeley.edu}
+  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@eecs.berkeley.edu}}
 
-  \affil[3]{University of Caifornia Berkeley, E-mail: nmalkin@cs.berkeley.edu}
+  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
 
-  \affil[4]{University of Caifornia Berkeley, E-mail: ganesh.v@berkeley.edu}
+  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
 
-  \affil[5]{University of Caifornia Berkeley and International Computer Science Institute, E-mail: egelman@cs.berkeley.edu}
+  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
 
-  \affil[6]{University of Caifornia Berkeley, E-mail: daw@cs.berkeley.edu}
+  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
 

### 2016-04-06 experiment/processing/graphs.R
Use full-alpha for the line labels in time_to_success_ecdf graph.

@@ -63,7 +63,7 @@ p <- p + scale_color_manual(values=palette)
 # p <- p + guides(color=guide_legend(override.aes=list(size=2, title=NULL)))
 p <- p + guides(color=F)
 p <- p + labs(title=NULL, x="Minutes elapsed", y="Successful participants")
-p <- p + annotate(geom="text", x=c(1), y=c(0.86), label=c("E1-\nNEW"), hjust=1, vjust=0, size=2, lineheight=0.8, alpha=0.6)
-p <- p + annotate(geom="text", x=c(3.3, 14, 15.3, 23, 24.7), y=c(0.87, 0.91, 0.71, 0.61, 0.32), label=c("E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=0, vjust=0, size=2, alpha=0.6)
+p <- p + annotate(geom="text", x=c(1), y=c(0.86), label=c("E1-\nNEW"), hjust=1, vjust=0, size=2, lineheight=0.8)
+p <- p + annotate(geom="text", x=c(3.3, 14, 15.3, 23, 24.7), y=c(0.87, 0.91, 0.71, 0.61, 0.32), label=c("E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=0, vjust=0, size=2)
 p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=textwidth, height=height, device=cairo_pdf)

### 2016-04-06 experiment/processing/graphs.R
Do all the time_to_success_ecdf labels in one annotate call.
Previously I had two calls because some labels had hjust=0 and some had
hjust=1, but it turns out you can pass a vector for the hjust.

@@ -63,7 +63,6 @@ p <- p + scale_color_manual(values=palette)
 # p <- p + guides(color=guide_legend(override.aes=list(size=2, title=NULL)))
 p <- p + guides(color=F)
 p <- p + labs(title=NULL, x="Minutes elapsed", y="Successful participants")
-p <- p + annotate(geom="text", x=c(1), y=c(0.86), label=c("E1-\nNEW"), hjust=1, vjust=0, size=2, lineheight=0.8)
-p <- p + annotate(geom="text", x=c(3.3, 14, 15.3, 23, 24.7), y=c(0.87, 0.91, 0.71, 0.61, 0.32), label=c("E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=0, vjust=0, size=2)
+p <- p + annotate(geom="text", x=c(1, 3.3, 14, 15.3, 23, 24.7), y=c(0.86, 0.87, 0.91, 0.71, 0.61, 0.32), label=c("E1-\nNEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=c(1, 0, 0, 0, 0, 0), vjust=0, size=2, lineheight=0.8)
 p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=textwidth, height=height, device=cairo_pdf)

### 2016-04-06 pets2017-paper/pets2017-paper.tex
Use fifield@cs, not fifield@eecs, to match others.
refactor intro into intro and related work

@@
 
-  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@eecs.berkeley.edu}}
+  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
 
@@
 \section{Introduction}
-Tor is primarily known as the most widely used anonymity tool today. 
-For this reason, user studies on Tor have been solely about the usability of Tor as an
-anonymity tool. Norcie~\cite{norcie2012eliminating} conducted an experiment which identified 
-``stopping points'' in Tor Browser, documenting points when people would get frustrated enough
-to stop using Tor. To our knowledge, that has been the only published user study of Tor. 
-Since then, Tor has had a lot of updates. There have been been no published usability evaluations of
-Tor Browser since the introduction of the 4.0 series, which introduced radical UI changes. 
-Lee and Fifield~\cite {uxsprint} ran a small pilot study testing the download, install, and user interface of Tor Browser. 
-This study uncovered a number of bugs and stopping points. Changes made are reflected in series 
-5.1 and later. There has been no work done on Tor as a censorship circumvention tool.
 
-Many features of Tor have not been evaluated through user
-research --- such as advanced web tasks (e.g., accessing hidden services), the
-configuration menu to connect to the Tor network, configuring automatic
-updates, and identity/cookie management. Rather than selecting the features to
-study in isolation, we decided to focus on an important use case of Tor browser: censorship circumvention. 
-Internet censorship is pervasive across the world today~\cite{faris2008measuring}. 
-Although Tor was not designed to be a censorship circumvention tool, users started
+Although Tor ~/cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
 using it as one, since Tor's role as a proxy to anonymize
@@
 We believe that this is a great opportunity for user research.
+We have the opportunity to help users circumvent censorship more easily and provide them with extra security features, such as anonymity.
+Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users ~\cite{dingledine2006anonymity}.
 This study aims to understand of what is confusing about the configuration process and what find changes make the process easier.
@@
 
+\section{Related Work} 
+There have been been no published usability evaluations of
+Tor Browser since the 4.0 series, which introduced radical UI changes. 
+The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
+that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of bugs~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.
+
+There have been three published user studies on Tor to our knowledge. Clark et. al examines various deployment
+options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
+were satisfactory from a usability perspective. Fabian et. al show that Tor's added latency 
+~\cite{dingledine2009performance} causes users
+to be frustrated, cancel requests more often, and prevent user adoption. Norcie et. al found found that 
+64\% of users are unable to continue with installation or browsing at least once due to difficulties.
+
+Previous user studies have not focused on specific features in isolation, while we choose to focus our study on 
+the configuration interface. The configuration interface in isolation is the censorship circumvention 
+interface, as it guides users through setting up network components required to circumvent censorship. 
+This study examines that interface, and effectively, the usability of Tor as a censorship circumvention tool.
+
 \section{Background} 
@@
 \subsection{Censorship Today} 
-Internet censorship is widespread throughout the world.
+Internet censorship is widespread throughout the world ~\cite{faris2008measuring}.
 Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation.
@@
 that have shown to work in the User Interface design 
-community. We draw from Jacob Nielsen's ten heuristics ({\color {red} CITE THIS})
+community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
 and other industry standards to form the following heuristic evaluation criteria: \\
@@
 \subsection{Methodology} 
-In this section, we talk about the details of our qualitative user study, such as the censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.
+In this section, we talk about the details of our qualitative user study, such as the inspection of the interface, censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.
+
+\subsubsection{Inspection} 
+A combination of usability inspection methods~\cite{nielsen1994usability}
+ were used prepare for the user study. Two researchers conducted a pluralistic 
+walkthrough and stepped through various censorship
+scenarios, discussing which elements would be involved for that use case, and walking 
+through the configuration process. After compiling all the possible paths through the 
+interface {\color {red} digraph here?}, feature inspection was performed to list sequences
+of features used to accomplish typical tasks, taking note of long sequences or cumbersome
+steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
+that may cause confusion for users during our study.
 
@@
 
+\section{Limitations} 
+{\color {red} our study was only run on windows machines.
+our participants were not motivated like real users would be in real environments to succeed, but also may have been too motivated since they were getting paid.
+We didn't intentionally test the cases in which the user is required to configure a custom bridge or proxy.
+Our users were recruited from one geographic location, and their first language is English.}
+
 \section{Future Work} 
@@
 
-\section{Related Work} 
-{\color {red} TODO}
-
 \section {Acknowledgments}
-{\color {red} Rowie for setting up Xlab, Ganesh for helping us redesign the Interface, Nima, Isa, Georg, and the UX team for giving feedback, and Cecile for reviewing the UI of circumvention tools.}
-
-% Rowie
-% Ganesh
-% Nima, Isa, Georg, Tor UX team. 
-% Cecile Basnage for review of the UI of circumvention tools.
+{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isa (?), Georg (?), and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
 

### 2016-04-06 experiment/processing/graph.py
Move all the log-parsing junk into all_edges.
Have the graph program read from the CSV that all_edges produces.

@@ -1,93 +1,0 @@
-#!/usr/bin/env python
-
-# * if the configuration was eventually successful
-# * total time to successful configuration
-# * if failure, ultimate reason for failure
-# * number of tries until success
-# * causes for errors
-# * if participants listened to our directions (ie choosing the next bridge, or anything on the error screen)
-# * all paths taken through the interface
-
-import collections
-import datetime
-import getopt
-import json
-import re
-import sys
-
-import inst
-
-# src and dst are vertices; i.e. pages or states in the interface.
-# via is a string indicating an action that moved you from src to dst.
-# src and dst can be the same.
-Edge = collections.namedtuple('Edge', ['run', 'timestamp', 'src', 'dst', 'via'])
-
-def is_event_wanted(event):
-    if event["type"] in ("mouseover", "mouseout"):
-        return False
-    if event["type"] in ("popupshown", "popuphidden"):
-        return False
-    if event["type"] in ("pagehide", "pageadvanced", "pagerewound"):
-        return False
-    if event["type"] in ("load", "unload") and event["target_id"] == "configuration":
-        return False
-    if event["type"] in ("click", "command") and event.get("target_tagname") in ("menuitem", "wizard", None):
-        return False
-    if event["type"] == "command" and event["target_tagname"] == "button":
-        return False
-    return True
-
-def get_id(event):
-    """
-    Canonicalizes event target
-    """
-    if event["type"] == "start":
-        return ""
-    elif event["type"] in ("mouseover", "mouseout"):
-        return event["value"]
-    elif event["type"] == "select":
-        return "%s.%s" % (event["target_id"], event.get("value", '""'))
-    elif event["type"] == "progresschanged" or (event["type"] == "click" and event["target_tagname"] == "menuitem"):
-        return event["value"]
-    elif event["type"] == "unload" and event["target_id"] == "progress_bar":
-        return "finish"
-    else:
-        return event["target_id"]
-
-def parse_inst_log(f):
-    records = inst.parse_records(f)
-    # For now, assert that we have exactly one "start" event, in the first
-    # record.
-    assert len(records) > 0
-    assert records[0].event["type"] == "start"
-    #for record in records[1:]:
-    #    assert record.event["type"] != "start"
-
-    records = [record for record in records if is_event_wanted(record.event)]
-
-    edges = []
-
-    current_state = "start"
[…]

### 2016-04-07 pets2017-paper/pets2017-paper.tex
added sources that I could.

@@
 Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users ~\cite{dingledine2006anonymity}.
+
 This study aims to understand of what is confusing about the configuration process and what find changes make the process easier.
@@
 we recruited 5 participants for each censorship environment.
-We pre-screened our participants for diversity of gender, age, technical expertise,
-and familiarity with Tor in each simluated censorship environment.
+We pre-screened ~\cite{screening} our participants for diversity of gender, age, technical expertise,
+and familiarity with Tor in each simluated censorship environment for our summative
+usability test~\cite{summative}.
 
@@
 knew any more than {\color {red} TODO} technological terms.
-
-%Some references to keep in mind when explaining:
-%\href{why 5 users}{http://www.nngroup.com/articles/how-many-test-users/}
-%\href{screening}{http://www.userfocus.co.uk/articles/screeners.html}
-%\href{summative and usability mixed model}{http://www.usabilitybok.org/summative-usability-testing}
 
@@
 
+All who chose to configure a proxy were successful.
+Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information.
+What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.
+
 None of our censorship environments required our participants to configure a proxy for a successful connection.
-And upon the first attempt at configuration, most chose the default value of not configuring a proxy.
-However, the most common reason for failing to connect was that participants spent time configuring a proxy when they needed to adjust  bridge settings instead.
-Currently, no information was given upon failing to connect, which caused our participants to draw their own (incorrect) conclusions after a failed connection.
+Upon the first attempt at configuration, most chose the default value of not configuring a proxy.
+However, trying to unsuccessfuly configure a proxy was the most common reason for failing to connect.
 Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.
-
-None of the participants who attempted to configure a proxy were successful.
-Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information.
-What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.\\
+Users did not check their incorrect assumption ~\cite{wason1960failure}.
+This false assumption can be fixed by giving information on what needs to be configured~\cite{reeder2005user}.
+\\
 
@@
 Users were generally displeased with the lack of feedback on the progress bar.
-The process seemed to take too long for them, even in the ideal case in which a user chose the correct configuration in the first attempt.
+Users do tolerate delays if they are for security reasons, but only to a certain extent and if they understand the security reason ~\cite{egelmanplease}.
+Participants in our study usually did not understand the security reason, and experienced huge delays on the order of minutes, even in the ideal case in which a user chose the correct configuration in the first attempt.
 If users chose particular wrong configurations (i.e.
@@
 The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct.
+
 \begin{quotation}
@@
 \end{quotation} 
-In addition to the text being not as helpful as it would have been had users been able to understand, this discouraged our users during the process.\\
+In addition to the text being not as helpful as it would have been had users been able to understand, this discouraged our users during the process.
+Communicating the relevant information in an understandable way is difficult, bu is critical for the usability of a system ~\cite{molich1990improving}.\\
 

### 2016-04-07 pets2017-paper/pets2017-paper.tex
limitations

@@
 \section{Limitations} 
-{\color {red} our study was only run on windows machines.
-our participants were not motivated like real users would be in real environments to succeed, but also may have been too motivated since they were getting paid.
-We didn't intentionally test the cases in which the user is required to configure a custom bridge or proxy.
-Our users were recruited from one geographic location, and their first language is English.}
+The interface was only tested on windows machines, which were the only types of machines available machines in Xlab.
+The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
+Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this effect should affect all of our conditions equally.
+
+Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated.
+Our participants had a monetary incentive  to connect to Tor, whereas as a real user in a censored environment would Tor to reach a particular website or service.
+Additionally, the presence of researchers may have placed social pressure to attempt connect for the whole duration of the session, when they would have given up if they were not in a laboratory setting.
+
+We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.
 

### 2016-04-07 pets2017-paper/pets2017-paper.tex
add new figures

@@
 
-Although Tor ~/cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
+Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
 using it as one, since Tor's role as a proxy to anonymize
@@
 
+\begin{figure*}[t]
+	\centering
+		\includegraphics[width=1.0\textwidth]{bridge-screens.pdf} 
+		\caption{bridge screens} 
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+		\includegraphics[width=1.0\textwidth]{proxy-screens.pdf} 
+		\caption{proxy-screens} 
+\end{figure*}
+
 \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
@@
 \section {Acknowledgments}
-{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isa (?), Georg (?), and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
+{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
 

### 2016-04-07 pets2017-paper/pets2017-paper.tex
Mention instrumentation and video recording.

@@
 successful connection can be found in Section~\ref{sec:setup}.
+
+We prepared special instrumented versions of both versions of Tor Launcher.
+The instrumentation logs recorded every meaningful interaction with the interface---every
+button press, every menu selection, every screen change---along with a timestamp.
+The logs enabled us to calculate statistics such as the success rate
+for each condition.
+
+We recorded a video of the contents of the computer screen throughout each session.
+Review of the videos revealed details not captured by the instrumentation logs alone,
+such as participants' web searching and inspection of system networking settings.
 

### 2016-04-08 pets2017-paper/pets2017-paper.tex
Move a \label after a \caption.
This is needed for cross-references to work right; otherwise the \label
will refer to the previous labelable thing in the text.
Caption for the topology graphic I want to add.
Maybe this should just be inline, not a floating figure.

@@
 circumvent censorship and interact with the Tor configuration interface. 
+These components are shown in Fig.~\ref{fig:topology}.
 Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
 This information is necessary to configure connections to Tor in censored environments.
+
+\begin{figure}
+\centering
+{\color{red} TODO}
+% \includegraphics{topology}
+\caption{
+The chain of components involved in connecting to a website over Tor.
+Most users do not need a proxy;
+similarly only those users who face a censor need a bridge.
+In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
+We have shown the bridge as separate component
+because of the special role it plays.
+When a bridge is used, it takes the place of the first Tor hop.
+}
+\label{fig:topology}
+\end{figure}
 
@@
 \begin{figure*}[t]
-	\label{fig:old-flow}
 	\centering
@@
 		\caption{old flow} 
+	\label{fig:old-flow}
 \end{figure*}

### 2016-04-08 pets2017-paper/pets2017-paper.tex
Should ack TB devs (apart from Georg).

@@
 {\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
+{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
 

### 2016-04-08 experiment/processing/common.R
first attempt at generating participant graphs

@@ -10,9 +10,13 @@ read_participants <- function() {
 	participants <- read.csv("participants.csv")
 	sessions <- read.csv("sessions.csv")
 	success <- read.csv("success.csv")
+	edges <- read.csv("edges.csv")
 
 	participants <- merge(participants, sessions, by=c("session"), all=T)
 	participants <- merge(participants, success, by=c("seat", "runid"), all=T)
+	participants.edges <- merge(participants, edges, by=c("seat","runid"), all.y=T)
+	participants.edges.order = participants.edges[order(
+	  participants.edges$env,participants.edges$version,participants.edges$time_to_success),]
 	participants
 }
 

### 2016-04-08 experiment/processing/graphs.R

@@ -66,3 +66,11 @@ p <- p + labs(title=NULL, x="Minutes elapsed", y="Successful participants")
 p <- p + annotate(geom="text", x=c(1, 3.3, 14, 15.3, 23, 24.7), y=c(0.86, 0.87, 0.91, 0.71, 0.61, 0.32), label=c("E1-\nNEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=c(1, 0, 0, 0, 0, 0), vjust=0, size=2, lineheight=0.8)
 p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=textwidth, height=height, device=cairo_pdf)
+
+#only plot data before first success
+participants.edges.order <- participants.edges.order[participants.edges.order$time_from_start <= participants.edges.order$time_to_success, ]
+p <- ggplot(data=participants.edges.order, aes(x=time_from_start/60, y=interaction(time_to_success,version,env), color=(src)))
+p <- p + geom_path()
+p <- p + labs(title=NULL, x="Minutes", y="Participants")
+p <- p + scale_y_reverse()
+ggsave("all-participant-edges.pdf", p, width=textwidth*2, height=height*5, device=cairo_pdf)

### 2016-04-08 pets2017-paper/pets2017-paper.tex
add in previous results text
fix weird sentence

@@
 
+%% The old initial results section. Dave prefers this one.
+
+%We noticed four common challenges:
+
+%\begin{itemize}
+%\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
+As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
+%\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
+Participants knew that they were censored to some degree since we had simulated censorship of websites.
+However, bridges are only necessary when the government has taken active steps to censor Tor itself.
+%\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
+The problem is not necessarily where the interface directs users, misguiding them.
+It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
+%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
+The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+%\end{itemize}
+
+%\begin{figure}[t]
+%  \centering
+%    \includegraphics[width=0.5\textwidth]{error.png}
+%    \caption{An example of a technical error message which our participants did not understand.}
+%\label{fig:error}
+%\end{figure}
+
+%These problems were illustrated by our participants:
+
+%\begin{itemize}
+%\item {\bfseries Proof of Challenge 1:} Of the five participants who could click directly to the network, three participants (P3,P4,P10) did not choose to connect directly.
+Of the eleven participants who needed to configure their connection, eight (P1, P5, P6, P7, P8, P11, P13, P14, P16) chose to connect directly.
+One participant (P12) clicks configure, but answers the questions in such a way that it creates a direct connection.
+Only one (P15) chose to configure when they needed to.
+%\item {\bfseries Proof of Challenge 2:} Five participants were placed in a censored environment which did not block Tor.
+Three of the five (P3, P4, P10) configured a bridge for their connection.
+Of the other two, one participant (P2) was convinced that configuring a bridge was the correct course of action, but was intimidated at the thought of doing so and was pleasantly surprised when a direct connection succeeded; only one participant (P9) believed that a direct connection would work.
+%\item {\bfseries Proof of Challenge 3:} All three of our participants who failed to circumvent the simulated censorship environment (P14, P15, P16) spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network.
+Out of the five participants who needed to fix their bridge settings, there were only two participants (P5, P6) who eventually were able to figure out that their bridge settings needed to be adjusted.
+%\item {\bfseries Proof of Challenge 4:} One participant (P14) tried the same configuration seven times, even though those settings failed each time.
+Another participant (P12) tries the same configuration three times, and only manages to connect through a technical artifact of the experiment even though that should not have worked.
+Both of these participants emphasized that they did not know what they should be doing.
+Other participants' interview responses also indicate a lack of feedback after failure cases (P8, P15, P16).
+%\end{itemize}
+
 \subsubsection{Connect vs. Configure} 
@@
 This mistake can result in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments.
-% FIXME:
-Participants in the intermediate and advanced censorship environments who did correctly choose to configure in intermediate did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.
+Participants did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.
 

### 2016-04-11 pets2017-paper/pets2017-paper.tex
some of ganesh's feedback.

@@
 
-  \author[4]{Ganesh Iver}
+  \author[4]{Ganesh Iyer}
 
@@
 options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
-were satisfactory from a usability perspective. Fabian et. al show that Tor's added latency 
+were satisfactory from a usability perspective ~\cite{clark2007usability}. Fabian et. al show that Tor's added latency 
 ~\cite{dingledine2009performance} causes users
 to be frustrated, cancel requests more often, and prevent user adoption. Norcie et. al found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties.
+64\% of users are unable to continue with installation or browsing at least once due to difficulties ~\cite{norcie2012eliminating}.
 
@@
 Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation.
-Currently {\color {red} TODO} governments implement some sort of Internet censorship in their country.
-The most commonly censored categories of websites are {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), {\color {red} TODO} ({\color {red} TODO}\%), and {\color {red} TODO} ({\color {red} TODO}\%).
 Reactions from Internet censorship range from feeling safe that bad sites are blocked automatically for their citizens to being outraged that access to information and free speech have been infringed upon.
 The risks associated with circumventing Internet censorship, is largely based on the geographic location, how prevalent censorship circumvention is, and who you are.
-
-{\color{red} Link sources, talk about arms race between censors and censorship circumvention tools.}
 
@@
 \centering
-{\color{red} TODO}
-% \includegraphics{topology}
+ \includegraphics[width=0.5\textwidth]{topology.png}
 \caption{
@@
 \label{sec:discussion}
-If we had more concrete information on the number of high-risk users or users who need to configure a proxy, we would have made additional changes in the prototype.
-Since we lacked this information, the following changes did not make it into our prototype, but are worth discussing.
-Depending on the number of high-risk users or proxy-configuring users, these additional changes may be helpful: \\
+The following additional changes may be helpful: \\
 
 \begin{itemize}
-\item {\bfseries Tell people to click connect.} On the first screen, the user needs to decide to connect or configure.
-Although there is a description of what each option entails and when one may consider using that option, there are no instructions for the user on what to do.
-Ideally, we would people to click connect, and then try the manual configuration if a direct connection fails.
-We currently do not communicate this because it may put some users at risk.
-However, it is believed that a majority of the users will succeed if they click connect on the first screen, and giving them instructions on what to do can lessen their cognitive load during the configuration process.
-\item{\bfseries Hide the proxy screen.} Don't give users the option to configure a proxy unless it has been detected that it would be necessary.
-The amount of people who use proxies is low, but then \ldots this would not give users control in the beginning of the configuration process.
-\item{\bfseries Help the at-risk users.} There are people who would benefit from, on the first attempt, connecting with a meek bridge or custom bridge, without trying a vanilla tor connection or the recommended bridge in the dialog.
-Currently, we guide these people to the correct decision, but after trying the default bridge first.
-Helping these users to make a connection safely without ever being logged as connecting to Tor would be a benefit, but might be a case of overfitting to these types of users.
-A majority of users should not use a meek bridge or custom bridge, so it would be unideal to lead all users to this decision.
+\item {\bfseries Tell people what to do.} Since a majority of the users will succeed if they click connect on the first screen, replacing the information about choices with explicit instructions to connect can lessen their cognitive load during the configuration process.
+\item{\bfseries Hide infrequently used options.} Hide the proxy screen and do not the option to configure a proxy unless it has been detected as necessary.
+\item{\bfseries Tailor for at-risk users.} Currently, the interface is for the average user.
+We guide at-risk users to the correct configuration, but suggesting that they try the default first.
+However, this isn't ideal.
 \end{itemize}
 
-We took an approach that optimized for the average case user yet was conservative in automation to allow at-risk users to possibly connect without leaking that they use Tor.
-We believe that this is a sound approach to interacting with the user and the one we would recommend personally.
-However, there are alternative approaches to interacting with the user that may be of interest: \\
+We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor.
+However, there are alternative approaches: \\
 
 \begin{itemize}
-\item{\bfseries Automate the entire configuration process.} This sounds like a radical idea, but it really isn't.
+\item{\bfseries Automate the configuration.} This sounds like a radical idea, but it really isn't.
 Today, this wouldn't harm most of our users.
 Our study finds that most users do not configure better than we do and would leak that they are using Tor anyway.
-\item {\bfseries Auto-configure after connect.} After a person has already clicked connect and the connection was unsuccessful, they have already been logged.
-I am assuming that the significant difference is between being logged trying to connect to Tor or not at all, rather than the number of connection attempts made.
-This would greatly save our users a lot of headache.
-\item{\bfseries Ask about the risk.} Rather than having the configuration dialog be manual by default, just ask if the users are at risk if the process was automated.
-If they are not at risk, we can do it automatically, and the at-risk users can configure manually.
-The issue with this is that people may not answer this question honestly, or they might not know the correct answer to this question.
-\item{\bfseries Ask if they are qualified to make decisions.} Asking users if they know which bridge to choose, and choosing for them if they say they don't know.
-We probably know better than they do.
-But there are ethical implications of choosing bridges for them rather them making the mistakes themselves.
-The issue with this is that people may not answer honestly.
+\item {\bfseries Automate after failure.} After an unsuccessful connection attempt, the user has already indicated that they are connecting to Tor on the network.
+Assuming that the significant difference is between being logged trying to connect to Tor or not at all, we can automate the entire configuration process thereafter without increasing risk.
+This may save our users a lot of headache.
+\item{\bfseries Ask about the risk.} Ask if the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk.
+The ones at risk will configure manually.
+The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly.
+\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not.
+However, there are ethical implications of making mistakes on behalf of the users if there is risk involved.
 \end{itemize}

### 2016-04-11 pets2017-paper/pets2017-paper.tex
take out leading suggestions and tweak qualitative results section

@@
 Tor Browser provides a configuration interface to guide users through setting up 
-their connection. While most can connect to Tor using the
-dialog's default settings, users in certain censorship environments must
-make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are
-four ways to set up a connection:\\
+their connection. While most can connect to Tor using a direct connection, users in certain censorship environments must
+make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are four ways to set up a connection:\\
 
@@
 
-The interface asks a series of questions to determine which of these configuration states a user requires.
-The first decision that a user needs to make is if they should connect directly to the Tor network or go through the process of  configuring a bridge and a proxy.
+A series of questions determines which configuration a user requires.
 The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure.
@@
 
-This puts the majority of the burden of knowing the correct technical information and configuring the connection correctly on the user.
-Note that bridges, pluggable transports, and proxies are technical concepts that probably are unfamiliar to the average user.
+This puts the burden of knowing technical information and configuring correctly on the user.
+Note that bridges, pluggable transports, and proxies are technical concepts that are likely unfamiliar to the average user.
 Although burdensome, the interface takes the approach of guiding the user through this technical process in order to give users their own agency in configuring their connection.
-Since there is risk associated with making an unobfuscated connection with the Tor network, the configuration process is not automated.
 No automation means that the user can have control over when there will be network traces of their activity trying to connect to Tor, and being able to connect successfully to the Tor the first time, provided they have all of the relevant information.
@@
     \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
-    \item  {\bfseries Understandable language}: ~6th grade reading level. 
-    \item  {\bfseries Minimal design}: suppressing rarely used information to reduce cognitive load. 
+    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
+    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
 \end{enumerate}
@@
 A combination of usability inspection methods~\cite{nielsen1994usability}
- were used prepare for the user study. Two researchers conducted a pluralistic 
+ were used to prepare for the user study. Two researchers conducted a pluralistic 
 walkthrough and stepped through various censorship
@@
 through the configuration process. After compiling all the possible paths through the 
-interface {\color {red} digraph here?}, feature inspection was performed to list sequences
+interface, feature inspection was performed to list sequences
 of features used to accomplish typical tasks, taking note of long sequences or cumbersome
@@
 \subsubsection{Recruitment}
-Using established best practices from the field of user experience research~\cite{howmanyusers},
+Using established practices from the field of user experience research~\cite{howmanyusers},
 we recruited 5 participants for each censorship environment.
 We pre-screened ~\cite{screening} our participants for diversity of gender, age, technical expertise,
-and familiarity with Tor in each simluated censorship environment for our summative
+and self-reported familiarity with Tor in each simluated censorship environment for our summative
 usability test~\cite{summative}.
@@
 (sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
-a college education, and the most common jobs included {\color {red} TODO} and
-{\color {red} TODO}. {\color {red} TODO} had heard of Tor previously, 
+a college education. {\color {red} TODO} had heard of Tor previously, 
 and {\color {red} TODO} had used Tor previously. {\color {red} TODO} out of 
-16 did not use any circumvention tools, and no more than {\color {red} TODO} 
-knew any more than {\color {red} TODO} technological terms.
+16 did not use any circumvention tools.
 
@@
 experiment begins. A researcher informs the participant that they are in a
-simulated censorship environment, where some websites and services are blocked. 
-For the full script of what participants have heard, see Appendix~\ref{qualitative-script}. We
+simulated censorship environment, where some websites and services are blocked. We
 instruct them to visit a sample blocked website and a sample non-blocked website on a
 non-Tor browser of their choice to illustrate the situation.
+For the full script of what participants have heard, see Appendix~\ref{qualitative-script}.
 
@@
 At this point, the participants do not know the details of their censorship environment,
-only that they are actively being censored. We believe that this is representative 
-of the mental model of users in censored countries, and therefore chose to simulate 
-this for the experiment. Ultimately, participants needed to configure Tor Browser to 
+only that they are actively being censored. Ultimately, participants needed to configure Tor Browser to 
 circumvent the simulated censorship.
@@
 After their interview, participants were informed that the experiment was over and 
-given their payment of~\$30.
+given their payment of~\$30 for their time.
 
@@
 
-The participant across all censorship environments connected directly to the Tor network.
+Participants across all censorship environments connected directly to the Tor network.
 When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process.
@@
 
-Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this happens, or what the difference between a blocked website and a blocked relay looks like.
+Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this happens, or what the difference between a blocked website and a blocked relay.
 Participant 10 and several other participants in the mild censorship environment opted to configure a connection when a direct connection to the Tor network would have worked.
@@
 
-This mistake can result in users struggling through the rest of the interface similarly to those in the intermediate and advanced censorship environments.
-Participants did not actively display an understanding between the difference between censorship of websites versus censorship of the Tor relays.
-
-Making the choice between connect and configure clearer for users has the possibility to save time and keep users safer.
-Waiting for a failed connection takes about couple minutes, so users can save at least that time by making the correct decision the first time.
-Users who need to configure can benefit from not clicking connect, which keeps them safer by not leaving a detectable network trace that indicates that they are trying to use Tor to circumvent censorship.\\
+Users do not make the optimal choice between connect and configure.
+This leads to discouragement from attempting a failed connection and wasted time spent waiting for feedback, which lessen the chance for a successful connection.
 
@@
 Answering yes to ``Does your Internet Service Provider (ISP) block or otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen.
-We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try trial and error.
+We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try process of elimination.
 Most participants with the default option to not configure a bridge.
@@
 Participants were unsure of the difference between a built-in bridge and a custom bridge and also why one would use a custom bridge.
-Most participants chose to go with the built-in bridge and chose obfs3 as their transport, because those were the default options on the screen.
+Most chose obfs3 as their transport, because those were the default options on the screen.
 
@@
 Participants in the advanced censorship environment were required to select a meek bridge (not the default) or to configure a custom bridge.
-After the first pluggable transport failed and if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors.
-Participants chose bridges in every order imaginable: at random, in order of the list starting from the default, in order of the list starting from the top, at random, choosing accessible sounding names first (i.e.
-meek-amazon over fte), and choosing non-accessible sounding names first (i.e.
+After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors.
+Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e.
+meek-amazon over fte), and choosing technical-sounding transports first (i.e.
 fte over meek-amazon).
@@
 
-Providing explicit guidance on in which order participants should try the bridges will be critical in helping a user succeed in configuring their connection.
-Rather than letting the user choose, the interface can guide the users by telling them to choose specific bridges if the default doesn't work, and in what order.
-Our participants were resilient in trying to configure a connection for up to 40 minutes, but we believe that this is a byproduct of the experimental setting and compensation.
-\\
+ Letting the user choose is unreliable, and also discouraging if users fail.
+Our participants were resilient and tried for 40 minutes, but we believe that this is a byproduct of the experimental setting and compensation.
 
@@
 
-All who chose to configure a proxy were successful.
-Many of the participants followed the directions in the interface to look at the Internet settings in another browser to see whether it is configure to use a local proxy, but they never found the proxy information since none of the other browsers had the information.
-What further frustrated the situation was that the other browsers did not explicitly state that no proxy was configured, which caused many of our participants to search for proxy settings.
-
-None of our censorship environments required our participants to configure a proxy for a successful connection.
-Upon the first attempt at configuration, most chose the default value of not configuring a proxy.
-However, trying to unsuccessfuly configure a proxy was the most common reason for failing to connect.
-Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, many participants were convinced that they needed a proxy to connect to the Tor network.
-Users did not check their incorrect assumption ~\cite{wason1960failure}.
-This false assumption can be fixed by giving information on what needs to be configured~\cite{reeder2005user}.
-\\
-
-\subsubsection{Progress Bar} 
-Users were generally displeased with the lack of feedback on the progress bar.
-Users do tolerate delays if they are for security reasons, but only to a certain extent and if they understand the security reason ~\cite{egelmanplease}.
-Participants in our study usually did not understand the security reason, and experienced huge delays on the order of minutes, even in the ideal case in which a user chose the correct configuration in the first attempt.
-If users chose particular wrong configurations (i.e.
-a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time, because there is no timeout.
-
-\begin{quotation}
-\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
-
-\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
-\end{quotation}
-
-As a technical artifact of how the progress bar is implemented, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e.
-a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress).
-The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct.
-
-\begin{quotation}
-\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
-\end{quotation}
-
-Ensuring that the progress bar faithfully displays the current status can encourage users to wait for correct configurations to successfully connect to the Tor network.
+Upon the first attempt at configuration, most chose to not configure a proxy.
+However, trying to unsuccessfully configure a proxy was the most common reason for failing to connect.
+Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, participants incorrectly assumed that they needed a proxy.
+Participants did not check their incorrect assumption ~\cite{wason1960failure}.
+All who chose to configure a proxy were unsuccessful.
 
@@
 
-Providing participants with feedback about taking specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.
-can prevent participants from unnecessarily configuring a proxy and to connect successfully.\\
+None of our censorship environments required our participants to configure a proxy for a successful connection.
+Participants followed the directions to look at the Internet settings, but they never found the (nonexistent) information.
+
+\subsubsection{Progress Bar} 
+Users were generally displeased with the lack of feedback on the progress bar.
+Users do tolerate delays if they are for security reasons, but if they understand the reason ~\cite{egelmanplease}.
+Participants in our study usually did not understand the security reason, and experienced delays up to 2 minutes, even in the ideal case in which a user chose the correct configuration in the first attempt.
+If users chose particular wrong configurations (i.e.
+a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time.
+
+\begin{quotation}
+\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
+
+\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
+
+\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
+\end{quotation}
+
+Additionally, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e.
+a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress).
+The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct.
 
@@
  \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
-
- \noindent P16:\textit{``Because I never configured a proxy or worked with that stuff, I was just going to keep clicking and pray.''}
 \end{quotation} 
-In addition to the text being not as helpful as it would have been had users been able to understand, this discouraged our users during the process.
-Communicating the relevant information in an understandable way is difficult, bu is critical for the usability of a system ~\cite{molich1990improving}.\\
+This discouraged our users during the process and did not communicate its intended message.
 

### 2016-04-11 pets2017-paper/pets2017-paper.tex
last ganesh suggestions

@@
 \subsubsection{User Communication} 
-Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary. 
+Many participants, including participants who were pre-screened as having high technical ability and previous experience with using Tor, were not familiar with the vocabulary. 
 \begin{quotation}
@@
 configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-The configuration used for a connection is not visible to the users before they connect or while they are connecting, full control but little guidance through the configuration process confuse users, error messages do not express errors in plain language nor offer solutions, the text was too technical for an average user to understand, and the interface has room to be simplified visually.
-
-Currently, the interface overburdens users.
+The configuration used for a connection is not visible to the users before they connect or while they are connecting.
+Users had full control but little guidance.
+Error messages do not express errors in plain language nor offer solutions.
+The text was too technical for an average user to understand.
+The interface can be simplified visually.
+
 Our goals in redesigning the interface was to making the system status visible to the user, retain user freedom but give guidance, make the vocabulary more accessible, offer solutions upon errors, and to require the user to make fewer decisions overall.
@@
 \item {\bfseries Got rid of proxy and bridge questions.}  We removed the bridge and proxy questions, which were highly technical and challenging for users to answer.
-There are two less windows in the interface.
+There are two less screens in the interface.
 \item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files.
@@
 \item {\bfseries Switched ordering to configure proxies first.} To build up the users' mental model, we configure network components in a topologically sequential.
-Proxies were put after bridge configuration because only a small fraction of users require proxies.
+Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
 With auto-detection, configuring a proxy before a bridge will not burden the users.
@@
 This advice is tailored for our participants who were in the advanced censorship environment.
-\item {\bfseries Added more feedback to the progress bar.} The progress bar shows network components involved in connecting to the Tor network and gives feedback to the user as they are correctly configured.
+\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bat that network components involved in connecting to the Tor network.
+This aligns with the metal model we are trying to build.
+As connections are made with components, the progress bar displays a green check, giving immediate feedback to the user.
 For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network.
 Upon failure, users can see which components that have succeeded and which have failed.
-\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, advice on what to try next is shown to the user.
+\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user.
 Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy.
-\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more accessible by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users.
+\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users.
 Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
-\item {\bfseries Reduced visual clutter.} Whenever we could, we minimized the amount of text on the screen, hid additional fields until the relevant options were chosen, and made additional stylistic simplifications.
+\item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen.
+For instance, additional fields were hidden until the relevant options were chosen.
+Additional stylistic simplifications were made, such as removing grouping boxes.
 \end{enumerate}
 
-The redesigned interface maintains the approach taken by the deployed interface of asking the users about their situation, which is in the spirit of the deployed interface.
-The designed interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components.
+The redesigned interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components.
 The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change.
@@
 complete a worksheet that asks to visit one blocked website. 
-Similar to the qualitative study, we chose Wikipedia's featured article of the day 
-as the blocked website because the familiarity 
-that most users have with these websites makes the browsing task relatively easy, 
-which focuses participants' attention to configuring Tor Browser.
+To mirror the qualitative study, we chose Wikipedia's featured article of the day 
+as the blocked website.
 
@@
 participants were officially informed that their time was up, and were given their payment of 
-\$30.
+\$30 for their time.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{time_to_success_clamped}
-\caption{
-Time to first success, by censorship environment and interface.
-Here, non-finishing participants are assigned a time of 40 minutes.
-}
-\label{fig:time_to_success_clamped}
-\end{figure}
+%\begin{figure}
+%\centering
+%\includegraphics{time_to_success_clamped}
+%\caption{
+%Time to first success, by censorship environment and interface.
+%Here, non-finishing participants are assigned a time of 40 minutes.
+%}
+%\label{fig:time_to_success_clamped}
+%\end{figure}
 
@@
 Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated.
-Our participants had a monetary incentive  to connect to Tor, whereas as a real user in a censored environment would Tor to reach a particular website or service.
-Additionally, the presence of researchers may have placed social pressure to attempt connect for the whole duration of the session, when they would have given up if they were not in a laboratory setting.
+Our participants had a monetary incentive to connect to Tor, whereas as a real user in a censored environment would want to reach a particular website or service.
+Additionally, the presence of researchers may have placed social pressure to attempt connect for the whole duration of the session, when they may have given up if they were not in a laboratory setting.
 

### 2016-04-11 pets2017-paper/pets2017-paper.tex
restructure redesign section

@@
     \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
-    \item  {\bfseries User control and freedom}: allow users to override system, supports undo and redo actions. 
     \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
@@
 configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-The configuration used for a connection is not visible to the users before they connect or while they are connecting.
-Users had full control but little guidance.
-Error messages do not express errors in plain language nor offer solutions.
-The text was too technical for an average user to understand.
-The interface can be simplified visually.
-
-Our goals in redesigning the interface was to making the system status visible to the user, retain user freedom but give guidance, make the vocabulary more accessible, offer solutions upon errors, and to require the user to make fewer decisions overall.
-To achieve these goals, we made the following changes: \\
+We rate the severity of the issue by its frequency, impact, and persistence ~\cite{nielsen1994heuristic}:\\
+
+\begin{enumerate}
+\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
+\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
+\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
+\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
+ \end{enumerate}
+
+To fix the aforementioned problems, we made the following changes: \\
 
@@
 
-\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
+\begin{enumerate}
+\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user.
+Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy.
+\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users.
+Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
 \item {\bfseries Added system status visibility.} Before any attempt to connect to the Tor network, a summary screen displays if a bridge or proxy is configured, and if so, what the configurations are.
 The progress screen also displays the configurations while the connection attempt is being made.
+\item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen.
+For instance, additional fields were hidden until the relevant options were chosen.
+Additional stylistic simplifications were made, such as removing grouping boxes.
+\end{enumerate}
+
+We also made additional changes to unburden the user (5-8) and build a mental model (9-10):\\
+
+\begin{enumerate}
+\setcounter{enumi}{4}
 \item {\bfseries Added guidance on choosing connect vs configure.} We labeled the configure option as advanced, manual, and only for heavily censored situations. 
@@
 This is safe even for at-risk users, and greatly simplifies the configuration process.
+\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3.
+There is added text that advises users to try a meek bridge if obfs3 does not work.
+This advice is tailored for our participants who were in the advanced censorship environment.
+
 \item {\bfseries Switched ordering to configure proxies first.} To build up the users' mental model, we configure network components in a topologically sequential.
@@
 With auto-detection, configuring a proxy before a bridge will not burden the users.
-\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3.
-There is added text that advises users to try a meek bridge if obfs3 does not work.
-This advice is tailored for our participants who were in the advanced censorship environment.
 \item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bat that network components involved in connecting to the Tor network.
@@
 Upon failure, users can see which components that have succeeded and which have failed.
-\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user.
-Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy.
-\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users.
-Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
-\item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen.
-For instance, additional fields were hidden until the relevant options were chosen.
-Additional stylistic simplifications were made, such as removing grouping boxes.
 \end{enumerate}

### 2016-04-12 pets2017-paper/pets2017-paper.tex
minor paper tweaks

@@
 Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring.
-We confirm the statistical significance of some of the problems in our quantitative study (Section~\ref{sec:quantitative}).
 All quotes are paraphrased from live transcriptions of participant interviews.\\
 
-%% The old initial results section. Dave prefers this one.
-
 %We noticed four common challenges:  
-
+%
 %\begin{itemize}
-%\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
-As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
-%\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
-Participants knew that they were censored to some degree since we had simulated censorship of websites.
-However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-%\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
-The problem is not necessarily where the interface directs users, misguiding them.
-It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
-%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
-The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+%\item {\bfseries Challenge 1:} People are not qualified to answer the bridge and proxy questions asked or to choose between the transport choices given.  
+%\item {\bfseries Challenge 2:} People feel compelled to configure a connection, even if they don't need one. 
+%\item {\bfseries Challenge 3:} It was common for users to configure proxies, rather than trouble shooting bridges. 
+%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next. The feedback did not guide users into specific actions.
 %\end{itemize}
-
-%\begin{figure}[t]
-%  \centering
-%    \includegraphics[width=0.5\textwidth]{error.png}
-%    \caption{An example of a technical error message which our participants did not understand.}
-%\label{fig:error}
-%\end{figure}
 
@@
 Many participants, including participants who were pre-screened as having high technical ability and previous experience with using Tor, were not familiar with the vocabulary.
+
+\begin{figure}[t]
+  \centering
+    \includegraphics[width=0.5\textwidth]{error.png}
+    \caption{An example of a technical error message which our participants did not understand.}
+\label{fig:error}
+\end{figure}
+
 \begin{quotation}
@@
 
- \noindent P4:\textit{``The progress bar had no feedback for me. I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
+ \noindent P4:\textit{``I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
 \end{quotation} 
@@
 \label{sec:discussion}
-The following additional changes may be helpful: \\
+The following changes were considered, but not tested. We chose to redesign the interface in a conservative way for deployability reasons. However, these changes may be helpful for a user: \\
 

### 2016-04-12 experiment/processing/common.R
My and Linda's refinements to all-participant-edges.pdf.
Sort it the way we wanted, fill in gaps between adjacent screen
transitions.

@@ -10,19 +10,20 @@ read_participants <- function() {
 	participants <- read.csv("participants.csv")
 	sessions <- read.csv("sessions.csv")
 	success <- read.csv("success.csv")
-	edges <- read.csv("edges.csv")
 
 	participants <- merge(participants, sessions, by=c("session"), all=T)
 	participants <- merge(participants, success, by=c("seat", "runid"), all=T)
-	participants.edges <- merge(participants, edges, by=c("seat","runid"), all.y=T)
-	participants.edges.order = participants.edges[order(
-	  participants.edges$env,participants.edges$version,participants.edges$time_to_success),]
 	participants
 }
 
 # Return only the participants marked "good".
 filter_participants <- function(participants) {
 	participants[participants$good, ]
+}
+
+# Read edges.csv into one big data frame.
+read_edges <- function() {
+	read.csv("edges.csv")
 }
 
 common_theme <- function(p) {

### 2016-04-12 experiment/processing/graphs.R

@@ -31,6 +31,11 @@ time_to_success_plot <- function(participants) {
 
 participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E1-NEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"))
+participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$runid))
+participants$pid <- factor(participants$pid, levels=participants$pid[order(participants$env, participants$version, participants$time_to_success)])
+
+edges <- read_edges()
+edges <- merge(edges, participants, by=c("seat", "runid"), all=T)
 
 p <- time_to_success_plot(participants)
 ggsave("time_to_success.pdf", p, width=textwidth, height=height, device=cairo_pdf)
@@ -67,10 +72,19 @@ p <- p + annotate(geom="text", x=c(1, 3.3, 14, 15.3, 23, 24.7), y=c(0.86, 0.87, 
 p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=textwidth, height=height, device=cairo_pdf)
 
-#only plot data before first success
-participants.edges.order <- participants.edges.order[participants.edges.order$time_from_start <= participants.edges.order$time_to_success, ]
-p <- ggplot(data=participants.edges.order, aes(x=time_from_start/60, y=interaction(time_to_success,version,env), color=(src)))
-p <- p + geom_path()
-p <- p + labs(title=NULL, x="Minutes", y="Participants")
-p <- p + scale_y_reverse()
-ggsave("all-participant-edges.pdf", p, width=textwidth*2, height=height*5, device=cairo_pdf)
+
+edges <- edges[order(edges$time_from_start), ]
+# Keep only the edges up to the first success.
+edges <- edges[is.na(edges$time_to_success) | edges$time_from_start <= edges$time_to_success, ]
+edges$duration <- ave(edges$time_from_start, edges$seat, edges$runid, FUN=function(z) {
+	c(z[2:length(z)], z[length(z)]) - z
+})
+
+# TODO: Make DNFs go all the way to 40 minutes.
+p <- ggplot(edges, aes(x=pid, xend=pid, y=time_from_start/60, yend=(time_from_start+duration)/60, color=src))
+p <- p + geom_segment(size=1.5, lineend="butt")
[…]

### 2016-04-12 experiment/processing/graphs.R
Don't include edges from non-good participants.
These were the cause of an NA row in the graph.

@@ -35,7 +35,10 @@ participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants
 participants$pid <- factor(participants$pid, levels=participants$pid[order(participants$env, participants$version, participants$time_to_success)])
 
 edges <- read_edges()
-edges <- merge(edges, participants, by=c("seat", "runid"), all=T)
+edges <- merge(edges, participants, by=c("seat", "runid"), all.y=T)
+if (any(is.na(edges$pid))) {
+	stop("found NAs in edges$pid")
+}
 
 p <- time_to_success_plot(participants)
 ggsave("time_to_success.pdf", p, width=textwidth, height=height, device=cairo_pdf)

### 2016-04-12 pets2017-paper/pets2017-paper.tex
Add all-participant-edges.pdf to the paper.
Temporarily disable topology.png; it's not yet checked in.
Spelling of Isabela.

@@
 \centering
- \includegraphics[width=0.5\textwidth]{topology.png}
+% \includegraphics[width=0.5\textwidth]{topology.png}
 \caption{
@@
 
+\begin{figure*}
+\centering
+\includegraphics{all-participant-edges}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes.
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
 {\color {red} 
@@
 \section {Acknowledgments}
-{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabella Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
+{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
 {\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}

### 2016-04-12 pets2017-paper/pets2017-paper.tex
Nathan feedback changes.

@@
   \title{\huge Tor's Usability for Censorship Circumvention}
+  %Internet Freedom Made Easy: On Improving Tor’s Usability for Censorship Circumvention
+  %Towards Usable Censorship Circumvention
 
@@
 since become an important censorship circumvention tool. It is now listed
-as one of the ways that normal people use Tor~\cite{whotor}.
+as one of the ways that normal people use Tor.
 We specifically examine its usability as a censorship circumvention tool,
 an essential facet for adoption and use. We focus our analysis on the connection 
-configuration interface of Tor Browser, as censorship circumvention requires 
-correct transport configurations. We find that the Tor Browser 5.0.3. connection
+configuration interface of Tor Browser. We find that the Tor Browser 5.0.3. connection
 configuration interface has a success rate of {\color {red} TODO}\% with the 
@@
 The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
-that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of bugs~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.
-
-There have been three published user studies on Tor to our knowledge. Clark et. al examines various deployment
+that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.
+
+There have been three published user studies on Tor. Clark et. al examined various deployment
 options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
@@
 ~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests more often, and prevent user adoption. Norcie et. al found found that 
+to be frustrated, cancel requests more often, and prevents user adoption ~\cite{fabian2010privately}. 
+Norcie et. al found found that 
 64\% of users are unable to continue with installation or browsing at least once due to difficulties ~\cite{norcie2012eliminating}.
@@
 Previous user studies have not focused on specific features in isolation, while we choose to focus our study on 
-the configuration interface. The configuration interface in isolation is the censorship circumvention 
-interface, as it guides users through setting up network components required to circumvent censorship. 
+the configuration interface. The configuration interface guides users through setting up network components required to circumvent censorship. 
 This study examines that interface, and effectively, the usability of Tor as a censorship circumvention tool.
@@
 \section{Background} 
-In this section, we talk about the current state of Internet censorship, interface network components that circumvent censorship, and the Tor Browser 5.0.3 configuration interface that guides users to configure those network components to make a connection to the Tor Network.
+This section examines Internet censorship, interface network components that circumvent censorship, and the Tor Browser 5.0.3 configuration interface.
 
@@
 Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation.
-Reactions from Internet censorship range from feeling safe that bad sites are blocked automatically for their citizens to being outraged that access to information and free speech have been infringed upon.
-The risks associated with circumventing Internet censorship, is largely based on the geographic location, how prevalent censorship circumvention is, and who you are.
+The risks associated with circumventing Internet censorship are largely based on geographic location, prevalence of censorship circumvention, and political status.
 
 \subsection{Interacting Network Components} 
-For context, we define bridges, pluggable transports, and proxies, network components that 
+Bridges, pluggable transports, and proxies are network components that 
 circumvent censorship and interact with the Tor configuration interface. 
@@
 % \includegraphics[width=0.5\textwidth]{topology.png}
+{\color {red} TODO}
 \caption{
@@
 Bridges are unlisted Tor relays that make it possible for a user to connect
-to the Tor network even if a censor blocks all publicly listed Tor relays. There used 
-to be plain relays which were exactly similar to public relays, but were unlisted. However, 
-censors in countries which blocked Tor generally were motivated enough to aggressively
+to the Tor network even if a censor blocks all publicly listed Tor relays. 
+Censors in countries which blocked Tor generally were motivated enough to aggressively
 block Tor in other ways, such as traffic analysis. For this reason, a bridge is usually associated
@@
 Proxies help bypass local network restrictions and are typically only
-needed in restricted cases, such as corporate environments.
+needed in certain cases, such as corporate environments.
 
@@
 A series of questions determines which configuration a user requires.
-The interface asks users questions along the way throughout the configuration to help guide their process on what components they would need to configure.
+The interface asks users questions along the way throughout the configuration to select components they would need to configure.
 For a successful configuration, users are required to know (or find out) the following:\\
@@
 \begin{itemize}
-	\item{Whether they need to configure a connection.} 
-	\item{If the Tor Network is censored by their ISP.}
-	\item{Which bridges work in the current environment.} 
-	\item{If no bridges work, how to get a custom bridge.} 
-	\item{If a proxy is required to access the Internet.}
-	\item{If a proxy is required, the proxy settings.}
+	\item{Whether they are censored} 
+	\item{If the Tor Network is censored by their ISP}
+	\item{Which bridges work in the current environment} 
+	\item{If no bridges work, how to get a custom bridge} 
+	\item{If a proxy is required to access the Internet}
+	\item{If a proxy is required, the proxy settings}
 \end{itemize}
@@
 techniques. Their goal in our user study is not to replicate the network 
-environment in any particular country, but to require our participants to 
-configure Tor Browser in distinct configurations. \\
+environment in any particular country, but to require our distinct configurations
+so that interface paths are tested. \\
 
@@
 
+\subsubsection{User Communication} 
+Many participants, including participants who were pre-screened as having high technical ability and previous experience with using Tor, were not familiar with the vocabulary.
+
+\begin{figure}[t]
+  \centering
+    \includegraphics[width=0.5\textwidth]{error.png}
+    \caption{An example of a technical error message which our participants did not understand.}
+\label{fig:error}
+\end{figure}
+
+\begin{quotation}
+\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
+ means at all."}\\
+
+ \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
+
+ \noindent P4:\textit{``I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
+\end{quotation} 
+The text in the interface intended to guide users through the process was not understood by our participants.
+The text also gave our participants a sense that the process intimidating for people who did not have a technical background.
+
 \subsubsection{Connect vs. Configure} 
@@
 
- Letting the user choose is unreliable, and also discouraging if users fail.
+Users are not qualified to choose transports in an educated order.
+When our participants chose incorrectly, they spent time testing their wrong hypothesis and got discouraged with each wrong decision.
 Our participants were resilient and tried for 40 minutes, but we believe that this is a byproduct of the experimental setting and compensation.
@@
 \subsubsection{Proxy Configuration} 
-After the bridge configuration, the participant again is asked to answer a question to determine if they need a proxy and if so, to configure one.
-This question also was too technical for some participants.
+After the bridge configuration, the participant is asked if they need a proxy and if so, to configure one. This question also was too technical for most participants.
 
@@
 
-Upon the first attempt at configuration, most chose to not configure a proxy.
-However, trying to unsuccessfully configure a proxy was the most common reason for failing to connect.
-Since the interface passively re-displayed a proxy-related window seen after an attempted connection regardless of the error, participants incorrectly assumed that they needed a proxy.
+For our participants, trying to unsuccessfully configure a proxy was the only mistake that resulted in failure.
+On the first attempt at configuration, most chose to not configure a proxy.
+Since the interface passively re-displayed a proxy-related window after an attempted connection regardless of the error, participants incorrectly assumed that they needed a proxy.
 Participants did not check their incorrect assumption ~\cite{wason1960failure}.
@@
 Users were generally displeased with the lack of feedback on the progress bar.
-Users do tolerate delays if they are for security reasons, but if they understand the reason ~\cite{egelmanplease}.
-Participants in our study usually did not understand the security reason, and experienced delays up to 2 minutes, even in the ideal case in which a user chose the correct configuration in the first attempt.
+Users do tolerate delays if they are for security reasons, but only if they understand the reason ~\cite{egelmanplease}.
+Participants in our study usually did not understand the security reason, and experienced delays up to 2 minutes, even in the ideal case in which a user chose the correct configuration on the first attempt.
 If users chose particular wrong configurations (i.e.
@@
 The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct.
-
-\subsubsection{User Communication} 
-Many participants, including participants who were pre-screened as having high technical ability and previous experience with using Tor, were not familiar with the vocabulary.
-
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
-\label{fig:error}
-\end{figure}
-
-\begin{quotation}
-\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
- means at all."}\\
-
- \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
-
- \noindent P4:\textit{``I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
-\end{quotation} 
-This discouraged our users during the process and did not communicate its intended message.
-
-%\begin{quotation}
-%\noindent{\bfseries P15}:\textit{``Give this to a couple of people who know how to do this. They can feel elite\ldots they only want the elite to use some computer things..''} \\
-%\noindent{\bfseries P13}:\textit{``I don't remember what I did. I figured it out? What? <laughs> Oh man, that's crazy..''}\\
-%\noindent{\bfseries P11}:\textit{``Is this question (does your ISP censor your Internet connection) really necessary? I just selected that I have a censored connection, why do they ask me again?''}
-%\end{quotation}
 
@@
 Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy.
-\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users.
+\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process.
 Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
@@
 \item {\bfseries Got rid of proxy and bridge questions.}  We removed the bridge and proxy questions, which were highly technical and challenging for users to answer.
-There are two less screens in the interface.
+There are two fewer screens in the interface.
 \item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files.
 This is safe even for at-risk users, and greatly simplifies the configuration process.
-\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3.
-There is added text that advises users to try a meek bridge if obfs3 does not work.
-This advice is tailored for our participants who were in the advanced censorship environment.
-
-\item {\bfseries Switched ordering to configure proxies first.} To build up the users' mental model, we configure network components in a topologically sequential.
+\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3. There is added text that advises users to try a meek bridge if obfs3 does not work.
+
+\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are configured in a topologically sequential order.
 Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
 With auto-detection, configuring a proxy before a bridge will not burden the users.
-\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bat that network components involved in connecting to the Tor network.
-This aligns with the metal model we are trying to build.
+\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bar that shows network components involved in connecting to the Tor network.
+This aligns with the mental model we are trying to build.
 As connections are made with components, the progress bar displays a green check, giving immediate feedback to the user.
 For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network.
-Upon failure, users can see which components that have succeeded and which have failed.
+Upon failure, users can see which components have succeeded and which have failed.
 \end{enumerate}
@@
 We performed quantitative research to quantify the existing problems
-and the impact of our redesign by generating numerical data to transform
-into usable statistics. Specifically, we collected all events, transitions, 
-and state for Tor Browser 5.0.3 and the redesigned Tor Browser. Participant
-logs of how they interacted with each of these interfaces are used to both
-quantify the issues we encountered in our previous qualitative 
-study and to examine the differences in success rate, time to completion,
-and configuration choices between the two versions.
+and the impact of our redesign. Specifically, we collected all events, transitions, 
+and state for Tor Browser 5.0.3 and the redesigned Tor Browser.
 
 \subsection{Methodology} 
-In this section, we talk about the details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.
+This section shows the details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.
 
 \subsubsection{Setup}
-For consistency, we simulated the same three censorship environments from 
+We simulated the same three censorship environments from 
 our qualitative user study. Details of the mild, intermediate, and advanced 
@@
 
-We prepared special instrumented versions of both versions of Tor Launcher.
+We instrumented Tor Launcher 5.0.3 and our redesigned Tor Launcher.
 The instrumentation logs recorded every meaningful interaction with the interface---every
@@
 
-We recorded a video of the contents of the computer screen throughout each session.
+We recorded the computer screen throughout each session.
 Review of the videos revealed details not captured by the instrumentation logs alone,
@@
 \subsubsection{Recruitment}
-We recruited 20 users for each censorship environment
-and interface combination, resulting in a total of 120 users. This decision 
-was due to both data analysis considerations (large enough to have good effect size, 
-with a minimum of 20 to be able to assume normal distributions) and
-available funding.
+We recruited about 20 users for each censorship environment
+and interface combination, resulting in a total of 124 users. 
+Data analysis considerations deem 20 participants in each 
+6 interface version and simulated censorship combination a 
+minimum to be able to assume normal distributions and 60 participants
+testing each interface is large enough to have adequate effect size.
 
 We recruited half of our users from Craigslist, and half of our participants from 
-the Xlab participant pool. It is standard for Xlab experiments to be run with Xlab
-participants, who have been verified of their identity and have good attendance
-rate. Although Xlab participants are not limited to UC Berkeley students and staff,
+the Xlab participant pool. Although Xlab participants are not limited to UC Berkeley students and staff,
 a majority of the participants are from campus. For this reason, we chose to recruit 
@@
 
-We chose our participants on who had responded to our listing first and their
-availability for experiment sessions. We collected their demographic information
-with an exit survey that participants took after the experiment.
-
 Out of our {\color {red} TODO} participants, ages ranged from {\color {red} TODO}
 (sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
-a college education, and the most common jobs included {\color {red} TODO} and
-{\color {red} TODO}.
+a college education.
 
 \subsubsection{Procedure}
-Similarly to the qualitative experiment, we conducted a quantitative evaluation 
-of the interface by creating an environment  for users to interact with the 
-configuration interface in a censored environment. The focus of this environment 
-was to collect a dataset of metrics to evaluate the two interfaces.
-
 The one-hour, multi-participant procedure begins when all participants are sitting at their
@@
 of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
+Each computer was assigned one of the 6 conditions in the beginning of the study. Participants
+were assigned to the seats at random, effectively being assigned a configuration launcher and
+simulated censorship environment combination at random.
+
 Participants are firstly informed of the risks of the study and consenting to data collection.  At
@@
 
-After users completed the browsing tasks, they take a short exit survey (Appendix~\ref{quantitative-exit-survey})
+After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
 collecting their demographics. All users were instructed to sit until the end of the experiment,
-regardless of when they had completed their task. This was to ensure that others were not 
-aware of when other participants had finished their tasks. After the 40 minutes were up, 
+regardless of when they had completed their task. After the 40 minutes were up, 
 participants were officially informed that their time was up, and were given their payment of 
@@
 
+\section{Discussion} 
+{\color {red} process the results, talking about the speculative here.}
+
 \section{Limitations} 
-The interface was only tested on windows machines, which were the only types of machines available machines in Xlab.
+The interface was only tested on Windows machines, which were the only types of machines in Xlab.
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
@@
 Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated.
-Our participants had a monetary incentive to connect to Tor, whereas as a real user in a censored environment would want to reach a particular website or service.
-Additionally, the presence of researchers may have placed social pressure to attempt connect for the whole duration of the session, when they may have given up if they were not in a laboratory setting.
+Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website or service.
+The nature of the experiment places social pressure to attempt connect for the whole duration of the session, whereas participants may have given up earlier if they were not in an organic setting.
 
@@
 
-Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes.
-Currently, the deployed nor redesigned interface achieves this goal.
+We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor.
 Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
-We encourage future work to explore some of the non-conservative changes and alternative approaches that we were not able to test in these series of experiment, which are listed in Section~\ref{sec:discussion}.
-
-\section{Discussion} 
-\label{sec:discussion}
-The following changes were considered, but not tested. We chose to redesign the interface in a conservative way for deployability reasons. However, these changes may be helpful for a user: \\
+We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.
+
+These non-conservative changes may be helpful for a user, and would benefit from future research: \\
 
@@
 
-We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor.
-However, there are alternative approaches: \\
+On a fundamental level, there are alternative approaches to manual configuration. An alternative approach has the potential to be highly effective, but would warrant future research: \\
 
 \begin{itemize}
-\item{\bfseries Automate the configuration.} This sounds like a radical idea, but it really isn't.
-Today, this wouldn't harm most of our users.
-Our study finds that most users do not configure better than we do and would leak that they are using Tor anyway.
+\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today.
+Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor.
 \item {\bfseries Automate after failure.} After an unsuccessful connection attempt, the user has already indicated that they are connecting to Tor on the network.
@@
 This may save our users a lot of headache.
-\item{\bfseries Ask about the risk.} Ask if the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk.
+\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk.
 The ones at risk will configure manually.
@@
 \end{itemize}
+
+Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes.
+We believe that this is possible with continued improvements to the interface.
 

### 2016-04-12 pets2017-paper/pets2017-paper.tex
serge minor feedback changes.

@@
 
+The qualitative user study gives insight into possible issues with
+the deployed interface. 
+The redesign process was guided by the participant observations, 
+heuristic evaluations and empirical goals. 
+Quantitative user studies provide empirical evaluations of the deployed
+and redesigned interface.
+
+An exploration of the problems with the existing Tor Browser 
+configuration interface through user observation and interviews can be 
+found in Section~{\color{red} TODO}. A heuristic evaluation of the existing interface and new interface is in Section~{\color{red} TODO}. We empirically show 
+that the redesigned interface improves completion rate, reduces time to completion, 
+and provides a safe path for at-risk users in Section~{\color{red} TODO}.
+
 \section{Related Work} 
-There have been been no published usability evaluations of
-Tor Browser since the 4.0 series, which introduced radical UI changes. 
-The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
-that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.
-
 There have been three published user studies on Tor. Clark et. al examined various deployment
@@
 64\% of users are unable to continue with installation or browsing at least once due to difficulties ~\cite{norcie2012eliminating}.
+
+There have been been no published usability evaluations of
+Tor Browser since the 4.0 series, which introduced radical UI changes. 
+The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
+that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.
 
@@
 Although burdensome, the interface takes the approach of guiding the user through this technical process in order to give users their own agency in configuring their connection.
-No automation means that the user can have control over when there will be network traces of their activity trying to connect to Tor, and being able to connect successfully to the Tor the first time, provided they have all of the relevant information.
+There has been no previous work to explore the option of automation, but a manual configuration was preferred by Tor developers since it allows the user can have control over the process.
+If a user had all the relevant information, they would be able to connect without obvious network traces of attempting to connect to Tor.
 
@@
 We evaluate the existing and redesigned Tor Browser configuration interface 
-through the empirical evaluation and heuristic evaluation criteria below. The
-empirical evaluation criteria were considered during our qualitative and 
-quantitative user studies, whereas the heuristic evaluation was considered during
-the redesign process.
-
-A heuristic evaluation is a rule-based evaluation that leverages standards
-that have shown to work in the User Interface design 
-community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
+through the empirical evaluation and heuristic evaluation criteria below.
+
+A heuristic evaluation is a rule-based evaluation based on time-tested standards
+in the user interface design community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
 and other industry standards to form the following heuristic evaluation criteria: \\
@@
 \end{enumerate}
-
-An exploration of the problems with the existing Tor Browser 
-configuration interface through user observation and interviews can be 
-found in Section~{\color{red} TODO}. A heuristic evaluation of the existing interface and new interface is in Section~{\color{red} TODO}. We empirically show 
-that the redesigned interface improves completion rate, reduces time to completion, 
-and provides a safe path for at-risk users in Section~{\color{red} TODO}.
 
@@
 \label{sec:setup}
-We simulated three censorship environments for our experiment.
-These reproducible, stable environments are informed by our experience 
-with pluggable transports and knowledge of commonly seen censorship 
-techniques. Their goal in our user study is not to replicate the network 
-environment in any particular country, but to require our distinct configurations
-so that interface paths are tested. \\
+We simulated three censorship environments for our qualitative and quantitative user studies. \\
 
@@
 domains requires a censorship circumvention 
-tool. The default option to ``connect'' to the Tor network 
+tool like Tor, but Tor is not explicitly blocked. 
+The default option to ``connect'' to the Tor network 
 directly will circumvent this censor. Additional correct
@@
 This is because domain-fronting requires censors to block entire CDNs to also
-block this transport (which will cause huge collateral blocking damage), making
-it resistant to aggressive censorship environments.
-(See ~\cite{fifield2015blocking} for additional details.)\\
+block this transport, which causes huge collateral blocking damage that
+makes the censorship very visible and inconvenient. Currently, even
+aggressive censorship environments resistant blocking entire CDNs.
+(See ~\cite{fifield2015blocking} for additional details.)
 \end{itemize}
+
+These reproducible, stable environments are informed by our experience 
+with pluggable transports and knowledge of commonly seen censorship 
+techniques. Their goal in our user study is not to replicate the network 
+environment in any particular country, but to require our distinct configurations
+so that interface paths are tested.
 
@@
 \subsubsection{Procedure}
-We conducted a qualitative evaluation of the interface by creating an environment 
-for users to interact with the configuration interface in a censored environment, 
-observing their interactions in real time without interacting with the participants, 
-and following up with interviews about their experiences.
+We conducted a qualitative evaluation of the interface through real-time observations of 
+users interacting with the configuration interface in a simulated censored environment.
+There was no researcher-user interaction during the experiment. A follow-up interview 
+detailed their thoughts about the configuration process.
 
@@
 room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
-Chrome, and VLC (for screen recording). A participant is firstly informed of 
+and VLC (for screen recording). A participant is firstly informed of 
 the risks of the study and consenting to data collection. If they consent, the 
-experiment begins. A researcher informs the participant that they are in a
-simulated censorship environment, where some websites and services are blocked. We
+experiment begins. A researcher reads a script (Appendix~\ref{qualitative-script}) that 
+informs the participant of the simulated censorship environment and
 instruct them to visit a sample blocked website and a sample non-blocked website on a
-non-Tor browser of their choice to illustrate the situation.
-For the full script of what participants have heard, see Appendix~\ref{qualitative-script}.
-
-After illustrating the censorship environment, participants are asked to 
-complete a worksheet that asks to visit one blocked website and one non-blocked website. 
+non-Tor browser of their choice to illustrate the situation. Then, participants are asked to 
+complete a worksheet (Appendix ~\ref{participant-worksheet}) that gives information
+on their censorship environment and instructs them
+to visit one blocked website and one non-blocked website.
+
 We chose Wikipedia's featured article of the day as the blocked website and 
@@
 which focuses participants' attention to configuring Tor Browser. 
-
 After instructions, researchers stepped out of the room so that there was no interaction
@@
 average of 45 minutes to complete their worksheet.
+
 At this point, the participants do not know the details of their censorship environment,
@@
 Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring.
-All quotes are paraphrased from live transcriptions of participant interviews.\\
+All quotes are not verbatim, but from best-effort live transcriptions of participant interviews.
 
@@
 We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try process of elimination.
-Most participants with the default option to not configure a bridge.
+Most participants went with the default option to not configure a bridge.
 
@@
 \section{Redesigning the Configuration Interface}
-%skip talking about the process of redesigning the interface. It isn't that interesting.
-
-% Heuristic evaluation metrics, from above: 
-% \begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt
-%     \item {\bfseries Visibility of System Status} provide feedback on what the system is doing.
-%     \item {\bfseries User Control and Freedom} allow users to override system, supports undo and redo actions. 
-%     \item {\bfseries Error Management} expressing errors in plain language and offering a solution. 
-%     \item {\bfseries Understandable Language} ~6th grade reading level. 
-%     \item {\bfseries Minimal Design} suppressing rarely used information to reduce cognitive load. 
-% \end{enumerate}
-
-Tor Browser 5.0.3.
-configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-We rate the severity of the issue by its frequency, impact, and persistence ~\cite{nielsen1994heuristic}:\\
-
-\begin{enumerate}
-\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
-\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
-\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
- \end{enumerate}
-
-To fix the aforementioned problems, we made the following changes: \\
-
 \begin{figure*}[t]
@@
 \end{figure*}
+
+Tor Browser 5.0.3.
+configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+We rate the severity of the issue by its frequency, impact, and persistence ~\cite{nielsen1994heuristic}:\\
+
+\begin{itemize}
+\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
+\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
+\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
+\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
+ \end{itemize}
+
+%HEURISTICS
+%\begin{enumerate}
+%    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
+%    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
+%    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
+%    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
+%\end{enumerate}
+
+To fix the aforementioned problems, we made the following changes: \\
 
@@
 
-We also made additional changes to unburden the user (5-8) and build a mental model (9-10):\\
+%EMPIRICALS
+%\begin{enumerate}
+%    \item {\bfseries Task Completion}: Almost all can successfully connect to Tor
+%    \item {\bfseries  Time to Completion}: Time to completion. 
+%    \item {\bfseries Safe for High-Risk Users}: It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
+%\end{enumerate}
+
+Other changes improve empirical goals from Section~\ref{sec:goals}: task completion, time to completion, and safe for high-risk users.
+5-6 improve task completion, 7-8 reduce time to completion, and 9-10 builds users' mental models of censorship circumvention and network components involved.
+Users' full control of the configuration process remains preserved.\\
 
@@
 \item {\bfseries Added guidance on choosing connect vs configure.} We labeled the configure option as advanced, manual, and only for heavily censored situations. 
-\item {\bfseries Got rid of proxy and bridge questions.}  We removed the bridge and proxy questions, which were highly technical and challenging for users to answer.
+\item {\bfseries Added explicit advice on choosing bridge transports.} The default bridge is still obfs3. There is added text that advises users to try a meek bridge if obfs3 does not work.
+
+\item {\bfseries Eliminated technical questions.}  We removed questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
 There are two fewer screens in the interface.
@@
 This is safe even for at-risk users, and greatly simplifies the configuration process.
-\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3. There is added text that advises users to try a meek bridge if obfs3 does not work.
 
@@
 The logs enabled us to calculate statistics such as the success rate
-for each condition.
-
-We recorded the computer screen throughout each session.
-Review of the videos revealed details not captured by the instrumentation logs alone,
-such as participants' web searching and inspection of system networking settings.
+for each condition. We also recorded the particiapants' computer screens 
+throughout the experiment to capture non-interface activity such as 
+web searching and inspection of system networking settings.
+
+We ran our experiment at Xlab, the Experimental Social Science Laboratory at University of 
+California, Berkeley. The Xlab allows researchers to run experiments on 36 participants at a time.
+There are 36 Windows machines in rows of 4, which are separated by cubicle walls. 
+We provided the scripts to set up the simulated censorship environment, install necessary software, 
+start the video recording, and save the logs and videos. Our experiment was not limited by Xlab
+requirements. However, the configuration interface relies on OS-provided features but testing 
+was only done on Windows machines, as a byproduct of using Xlab.
 
@@
 
-Out of our {\color {red} TODO} participants, ages ranged from {\color {red} TODO}
-(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
-a college education.
+Out of our 124 participants, ages ranged from {\color {red} TODO}
+(sigma = {\color {red} TODO}). {\color {red} TODO} were male and 
+{\color {red} TODO} of our participants had at least a college education.
 

### 2016-04-14 experiment/processing/info.R
redid stat tests

@@ -10,6 +10,10 @@ pctsummary <- function(x) {
 	sprintf("%d/%d = %s", sum(x), length(x), format_percent(mean(x)))
 }
 
+pct <- function(x) {
+  mean(x)
+}
+
 format_minutes <- function(x) {
 	sprintf("%dm%04.1fs", x %/% 60, x %% 60)
 }
@@ -17,6 +21,11 @@ format_minutes <- function(x) {
 median_time_summary <- function(x) {
 	format_minutes(median(x, na.rm=T))
 }
+
+cat("\n\n\n\n\n\n")
+cat("***********\n")
+cat("* SUMMARY *\n")
+cat("***********\n")
 
 cat(sprintf("number of participants: %d (%d good, %d bad)\n",
 	length(participants$good), sum(participants$good), sum(!participants$good)))
@@ -37,30 +46,62 @@ cat(sprintf("success rate per condition per pool\n"))
 with(participants, aggregate(success, list(env=env, version=version, pool=pool), pctsummary))
 
 cat("\n")
-cat(sprintf("ANOVA of success by env and version\n"))
-summary(aov(success ~ env+version, data=participants))
-
-for (env in levels(participants$env)) {
-	cat("\n")
-	cat(sprintf("t-test of success rate in env %s\n", as.character(env)))
-	try(print(with(participants[participants$env==env, ], t.test(success[version=="NEW"], success[version=="OLD"]))))
-}
-
-cat("\n")
-cat(sprintf("ANOVA of time_to_success by env and version\n"))
-summary(aov(time_to_success ~ env+version, data=participants))
-
-for (env in levels(participants$env)) {
-	cat("\n")
-	cat(sprintf("t-test of time_to_success in env %s\n", as.character(env)))
-	try(print(with(participants[participants$env==env, ], t.test(time_to_success[version=="NEW"], time_to_success[version=="OLD"]))))
-}
-
-
-cat("\n")
 cat(sprintf("median time to success per condition\n"))
 with(participants, aggregate(time_to_success, list(env=env, version=version), median_time_summary))
 
+cat("\n")
+max.e1.new <- max(participants$time_to_success[participants$env=="E1" & participants$version=="NEW"])
+cat(sprintf("maximum time for E1-NEW: %s\n", format_minutes(max.e1.new)))
+
+cat("\n\n\n\n\n\n")
+cat("*********************\n")
+cat("* STATISTICAL TESTS *\n")
[…]

### 2016-04-14 experiment/processing/info.R
Output a LaTeX table of success rate and time.

@@ -18,6 +18,10 @@ format_minutes <- function(x) {
 	sprintf("%dm%04.1fs", x %/% 60, x %% 60)
 }
 
+format_minutes_colons <- function(x) {
+	sprintf("%d:%02.f", x %/% 60, x %% 60)
+}
+
 median_time_summary <- function(x) {
 	format_minutes(median(x, na.rm=T))
 }
@@ -102,6 +106,26 @@ cat("\n\n\n\n\n\n")
 cat("***************\n")
 cat("* OTHER STUFF *\n")
 cat("***************\n")
+
+cat("\n")
+tt <- with(participants, aggregate(success, list(env=env, version=version), FUN=length))
+tt <- merge(tt, with(participants, aggregate(success, list(env=env, version=version), FUN=sum)), by=c("env", "version"))
+tt <- merge(tt, with(participants, aggregate(time_to_success, list(env=env, version=version), FUN=function(z) {median(z, na.rm=T)})), by=c("env", "version"))
+names(tt) <- c("env", "version", "n", "n_success", "median_time_to_success")
+
+cat("\n")
+cat("\\begin{tabular}{l r r r r}\n")
+cat("& \\multicolumn{2}{c}{success rate} & \\multicolumn{1}{c}{median time} \\\\\n")
+cat("& \\multicolumn{2}{c}{after 40 minutes} & \\multicolumn{1}{c}{to success} \\\\\n")
+cat("\\noalign{\\hrule}\n")
+for (i in 1:nrow(tt)) {
+	cat(sprintf("%s-%s & %d/%d & %.f\\%% & %s \\\\\n",
+		tt$env[[i]], tt$version[[i]],
+		tt$n_success[[i]], tt$n[[i]], 100 * tt$n_success[[i]] / tt$n[[i]],
+		format_minutes_colons(tt$median_time_to_success[[i]])))
+}
+cat("\\end{tabular}\n")
+
 
 time_ecdf <- function(participants, env, version) {
 	ecdf(

### 2016-04-14 pets2017-paper/pets2017-paper.tex
remove extra sentence.
Dump a table of completion rates and times into the paper.

@@
 The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change.
-For additional changes that can be made and alternate approaches for interacting with the user, see Section~\ref{sec:discussion}.
 
@@
 
+% This table is generated by info.R.
+\begin{tabular}{l r r r r}
+& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
+& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
+\noalign{\hrule}
+E1-NEW & 19/19 & 100\% & 0:20 \\
+E1-OLD & 19/19 & 100\% & 1:01 \\
+E2-NEW & 18/19 & 95\% & 3:22 \\
+E2-OLD & 16/19 & 84\% & 4:01 \\
+E3-NEW & 13/20 & 65\% & 12:38 \\
+E3-OLD & 10/20 & 50\% & 18:16 \\
+\end{tabular}
+
 \begin{figure}

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Summary table of environments.

@@
 \end{itemize}
+
+\begin{figure}
+\centering
+\begin{tabular}{r c c c}
+& E1 & E2 & E3 \\
+% \noalign{\hrule}
+websites blocked & X & & \\
+public relays blocked & X & X & \\
+default bridges blocked & X & X & X \\
+\end{tabular}
+\caption{
+Summary of our simulated censorship environments.
+E1 only requires participants to click ``Connect'';
+E2 requires selection of an included bridge;
+and E3 requires selection of a specific included bridge,
+or manual configuration of a custom bridge.
+E2's blocking is a superset of E1's;
+similarly E3's is a superset of E2's.
+}
+\label{tab:environments}
+\end{figure}
 

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Collapse a layer of hierarchy in sec:qualitative.

@@
 \section{Qualitative Analysis of the Existing Interface (Study 1)}
+\label{sec:qualitative}
+
 We performed qualitative research as an exploratory effort to gain an 
@@
 
-\subsection{Methodology} 
-In this section, we talk about the details of our qualitative user study, such as the inspection of the interface, censorship environments we placed our users in, how we pre-screened and selected our participants, and the procedure for the experiment.
-
-\subsubsection{Inspection} 
+\subsection{Inspection}
 A combination of usability inspection methods~\cite{nielsen1994usability}
@@
 
-\subsubsection{Setup}
+\subsection{Setup}
 \label{sec:setup}
@@
 
-\subsubsection{Recruitment}
+\subsection{Recruitment}
 Using established practices from the field of user experience research~\cite{howmanyusers},
@@
 
-\subsubsection{Procedure}
+\subsection{Procedure}
 We conducted a qualitative evaluation of the interface through real-time observations of 

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Fix space before cites.

@@
 We have the opportunity to help users circumvent censorship more easily and provide them with extra security features, such as anonymity.
-Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users ~\cite{dingledine2006anonymity}.
+Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users~\cite{dingledine2006anonymity}.
 
@@
 options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
-were satisfactory from a usability perspective ~\cite{clark2007usability}. Fabian et. al show that Tor's added latency 
+were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added latency 
 ~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests more often, and prevents user adoption ~\cite{fabian2010privately}. 
+to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 
 Norcie et. al found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties ~\cite{norcie2012eliminating}.
+64\% of users are unable to continue with installation or browsing at least once due to difficulties~\cite{norcie2012eliminating}.
 
@@
 \subsection{Censorship Today} 
-Internet censorship is widespread throughout the world ~\cite{faris2008measuring}.
+Internet censorship is widespread throughout the world~\cite{faris2008measuring}.
 Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation.
@@
 aggressive censorship environments resistant blocking entire CDNs.
-(See ~\cite{fifield2015blocking} for additional details.)
+(See~\cite{fifield2015blocking} for additional details.)
 \end{itemize}
@@
 we recruited 5 participants for each censorship environment.
-We pre-screened ~\cite{screening} our participants for diversity of gender, age, technical expertise,
+We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
 and self-reported familiarity with Tor in each simluated censorship environment for our summative
@@
 non-Tor browser of their choice to illustrate the situation. Then, participants are asked to 
-complete a worksheet (Appendix ~\ref{participant-worksheet}) that gives information
+complete a worksheet (Appendix~\ref{participant-worksheet}) that gives information
 on their censorship environment and instructs them
@@
 Since the interface passively re-displayed a proxy-related window after an attempted connection regardless of the error, participants incorrectly assumed that they needed a proxy.
-Participants did not check their incorrect assumption ~\cite{wason1960failure}.
+Participants did not check their incorrect assumption~\cite{wason1960failure}.
 All who chose to configure a proxy were unsuccessful.
@@
 Users were generally displeased with the lack of feedback on the progress bar.
-Users do tolerate delays if they are for security reasons, but only if they understand the reason ~\cite{egelmanplease}.
+Users do tolerate delays if they are for security reasons, but only if they understand the reason~\cite{egelmanplease}.
 Participants in our study usually did not understand the security reason, and experienced delays up to 2 minutes, even in the ideal case in which a user chose the correct configuration on the first attempt.
@@
 configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-We rate the severity of the issue by its frequency, impact, and persistence ~\cite{nielsen1994heuristic}:\\
+We rate the severity of the issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
 

### 2016-04-14 pets2017-paper/pets2017-paper.tex
fill in some results.

@@
 
-\begin{figure}
+\begin{table}
 \centering
@@
 \label{tab:environments}
-\end{figure}
+\end{table}
 
@@
 \subsection{Results} 
-
-% This table is generated by info.R.
+Results from statistical analyses say: 
+\begin{itemize} 
+	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
+	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
+	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
+	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
+	\item{{\bfseries impact of configuration version on success rate is not significant.}
+	Mann-Whitney, W = 5.5, p-value = 0.8248}
+	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
+	Mann-Whitney, W = 991, p-value = 0.3197}
+\end{itemize}
+
+A logistic regression model showing effects of censorship environment, interface version,
+and recruitment pool on success finds that a difficult censorship environment is the most
+significant factor in a participant failing. Xlab participants were more likely to succeed. 
+Participants with the old version of the interface were more likely to fail.
+
+Coefficients:
+             Estimate Std. Error z value Pr(>|z|)  
+(Intercept)   19.4556  1684.3342   0.012   0.9908  
+envE2        -17.3458  1684.3342  -0.010   0.9918  
+envE3        -19.2652  1684.3341  -0.011   0.9909  
+versionOLD    -0.7095     0.5793  -1.225   0.2206  
+poolxlab       1.1218     0.5968   1.880   0.0601 .
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+A linear regression model showing effects of censorship environment, interface version, 
+and recruitment pool on success finds that a difficult censorship environment is the most
+significant factor in taking a long time to complete the task. Participants with the old version
+of the interface and participants recruited from Xlab were likely to take longer.
+
+Coefficients:
+            Estimate Std. Error t value Pr(>|t|)    
+(Intercept)   -42.79      86.70  -0.494  0.62280    
+envE2         300.65      90.13   3.336  0.00124 ** 
+envE3         923.66     100.94   9.150 1.68e-14 ***
+versionOLD    104.78      78.70   1.331  0.18642    
+poolxlab       92.41      78.88   1.172  0.24445    
+---
+Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+\begin{table}
+\centering
+	% Generated by info.R.
 	\begin{tabular}{l r r r r}
@@
 	\end{tabular}
+\caption{A summary of partipants' success in circumventing censorship
+given their simulated censorship environment and version of Tor. Those who
+failed to connect successfully were not used to calculate the median time
+to success.}
+\end{table}
 
@@
 \includegraphics{time_to_success_ecdf}
-
+\caption{
+Cumulative success rates over time, by censorship environment and interface.
+We stopped participants after 40 minutes. Those who did not finish were assigned
+an arbitrarily high number greater than 40 minutes. 
+}
+\label{fig:time_to_success_ecdf}
+\end{figure}
+
+\begin{table}
+\centering 
 	% Generated by info.R:
@@
 	\end{tabular}
-
-\caption{
-Cumulative success rates over time.
-We stopped participants after 40 minutes;
-this graph shows what the success rate would have been
+\caption{This Table shows what the success rate would have been
 at different cutoff times.
@@
 After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
-After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
-}
-\label{fig:time_to_success_ecdf}
-\end{figure}
+After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
+\end{table}
 
@@
 
-{\color {red} 
-What to talk about: 
-\begin{itemize}
-\item{Did the new interface improve the success rate?}
-\item{Did the new interface help in only certain environments or certain people?}
-\item{Did the new interface improve the time to success?}
-\item{What are remaining issues?} 
-\item{What people did while configuring the interface}
-\item{Where people downloaded Tor browser if they did it themselves} 
-\item{Xlab versus craigslist} 
-\end{itemize}
-
-Graph: 
-\begin{itemize}
-\item{success rate}
-\item{time spent on each screen}
-\item{order pluggable transports were chosen}
-\item{transitions between windows for all participants}
-\end{itemize} 
-}
+\begin{figure} 
+%\includegraphics{}
+{\color {red} TODO} 
+\caption{time spent on each screen}
+\end{figure}
+
+\begin{figure} 
+%\includegraphics{}
+{\color {red} TODO} 
+\caption{order pluggable transports were chosen}
+\end{figure}
 
 \section{Discussion} 
-{\color {red} process the results, talking about the speculative here.}
-
-\section{Limitations} 
-The interface was only tested on Windows machines, which were the only types of machines in Xlab.
-The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
-Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this effect should affect all of our conditions equally.
-
-Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated.
-Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website or service.
-The nature of the experiment places social pressure to attempt connect for the whole duration of the session, whereas participants may have given up earlier if they were not in an organic setting.
-
-We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.
-
-\section{Future Work} 
-Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers.
-Redesigning the configuration interface was a mutual interest.
-In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface.
-We plan to continue our work with Tor developers to integrate changes we found to be helpful.
-This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.
-
-We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor.
-Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
-We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.
+{\color {red} TODO: improvements.} \\
+{\color {red} TODO: subjective observations.} \\
+{\color {red} TODO: remaining issues.} \\
+{\color {red} recommendations are below.} \\
 
@@
 
-On a fundamental level, there are alternative approaches to manual configuration. An alternative approach has the potential to be highly effective, but would warrant future research: \\
+{\color {red} Speculation of why certain things happened--long progress bar (there was no feedback so people assumed that they had to wait), transport selections (people in the new interface didn't see the advice sometimes), etc.}
+
+\section{Limitations} 
+The interface was only tested on Windows machines, which were the only types of machines in Xlab.
+The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
+Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this effect should affect all of our conditions equally.
+
+Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated.
+Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website or service.
+The nature of the experiment places social pressure to attempt connect for the whole duration of the session, whereas participants may have given up earlier if they were not in an organic setting.
+
+We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.
+
+\section{Future Work} 
+Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers.
+Redesigning the configuration interface was a mutual interest.
+In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface.
+We plan to continue our work with Tor developers to integrate changes we found to be helpful.
+This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.
+
+We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor.
+Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
+We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.\\
 

### 2016-04-14 experiment/processing/info.R

@@ -78,20 +78,21 @@ cat("*********************\n")
 # Linear regression: 
     # is a model (can predict time to success based on ver, env, pool)
 
+# x is success rate
 success_rates = with(participants, aggregate(success, list(env=env, version=version), pct))
 
 cat("\n")
-cat("success rates and env \n")
+cat("impact of environment on success rates\n")
 kruskal.test(x ~ env, data=success_rates)
 
-cat("success rate and version \n")
+cat("impact of version on success rates \n")
 wilcox.test(x ~ version, data=success_rates)
 
 cat("\n\n\n\n")
-cat("time to completion and env \n")
+cat("impact of environment on times to completion \n")
 kruskal.test(time_to_success ~ env, data=participants)
 
-cat("time to completion and version \n")
+cat("impact of version on times to completion \n")
 wilcox.test(time_to_success ~ version, data=participants)
 
 cat("\n\n\n\n")

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Add a figure with transport names.

@@
 If a user had all the relevant information, they would be able to connect without obvious network traces of attempting to connect to Tor.
+
+\begin{figure}
+\small
+\begin{itemize}
+\renewcommand{\labelitemi}{$\circ$}
+\item Connect with provided bridges\\
+Transport type:
+\begin{itemize}
+\item flashproxy
+\item fte
+\item fte-ipv6
+\item meek-amazon
+\item meek-azure
+\item meek-google
+\item obfs3 (recommended)
+\item obfs4
+\item scramblesuit
+\end{itemize}
+\item Enter custom bridges\qquad\fbox{Help}\\
+\end{itemize}
+\caption{
+Bridge selection options in Tor Browser~5.0.3.
+The obscure strings under ``Connect with provided bridges'' denote various
+built-in circumvention technologies (``pluggable transports'').
+Under ``Enter custom bridges'', there is a space to paste in
+a bridge specification that was obtained out of band.
+The ``Help'' button displays instructions on obtaining such
+bridge specifications.
+}
+\label{fig:bridge-options}
+\end{figure}
+
+Fig.~\ref{fig:bridge-options} shows the bridge options
+presented to a user in Tor Browser~5.0.3.
 

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Fix tab:environments.
I had transposed it.
add in demographic information.

@@
 % \noalign{\hrule}
-websites blocked & X & & \\
-public relays blocked & X & X & \\
-default bridges blocked & X & X & X \\
+websites blocked & X & X & X \\
+public relays blocked & & X & X \\
+default bridges blocked & & & X \\
 \end{tabular}
@@
 
-Out of our 16 participants, ages ranged from {\color {red} TODO}
-(sigma = {\color {red} TODO}). {\color {red} TODO} of our participants had at least
-a college education. {\color {red} TODO} had heard of Tor previously, 
-and {\color {red} TODO} had used Tor previously. {\color {red} TODO} out of 
-16 did not use any circumvention tools.
+Out of our 16 participants, ages ranged from 20 to 62
+(mu= 24.5, sigma = 12.6). 53.3\% were male. 
+93.3\% of our participants had at least
+a college education. 5 had previously heard of Tor but not used it, while 
+and 5 had used Tor previously.
 
@@
 
-Out of our 124 participants, ages ranged from {\color {red} TODO}
-(sigma = {\color {red} TODO}). {\color {red} TODO} were male and 
-{\color {red} TODO} of our participants had at least a college education.
+Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
+recruited from Craiglist. Ages ranged from 18 to 68
+(mu = 28.9, sigma = 12). 56.8\% were male and 
+84.8\% of our participants had at least a college education.
 

### 2016-04-14 pets2017-paper/pets2017-paper.tex
get rid of comments.
move flow figures next to each other; resize flow and redesign figures.
Merge both flow diagrams into one figure and write a caption.

@@
 \subsection{Interacting Network Components} 
+\label{sec:components}
 Bridges, pluggable transports, and proxies are network components that 
@@
 
-\begin{figure*}[t]
-	\centering
-		\includegraphics[width=1.0\textwidth]{old-flow.pdf} 
-		\caption{old flow} 
-	\label{fig:old-flow}
-\end{figure*}
-
 \section{Goals/Evaluation Criteria}
@@
 \end{itemize}
+
+These reproducible, stable environments are informed by our experience 
+with pluggable transports and knowledge of commonly seen censorship 
+techniques. Their goal in our user study is not to replicate the network 
+environment in any particular country, but to require our distinct configurations
+so that interface paths are tested.
 
@@
 
-These reproducible, stable environments are informed by our experience 
-with pluggable transports and knowledge of commonly seen censorship 
-techniques. Their goal in our user study is not to replicate the network 
-environment in any particular country, but to require our distinct configurations
-so that interface paths are tested.
-
 \subsection{Recruitment}
@@
 
-%We noticed four common challenges:  
-%
-%\begin{itemize}
-%\item {\bfseries Challenge 1:} People are not qualified to answer the bridge and proxy questions asked or to choose between the transport choices given.  
-%\item {\bfseries Challenge 2:} People feel compelled to configure a connection, even if they don't need one. 
-%\item {\bfseries Challenge 3:} It was common for users to configure proxies, rather than trouble shooting bridges. 
-%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next. The feedback did not guide users into specific actions.
-%\end{itemize}
-
-%These problems were illustrated by our participants:
-
-%\begin{itemize}
-%\item {\bfseries Proof of Challenge 1:} Of the five participants who could click directly to the network, three participants (P3,P4,P10) did not choose to connect directly.
-Of the eleven participants who needed to configure their connection, eight (P1, P5, P6, P7, P8, P11, P13, P14, P16) chose to connect directly.
-One participant (P12) clicks configure, but answers the questions in such a way that it creates a direct connection.
-Only one (P15) chose to configure when they needed to.
-%\item {\bfseries Proof of Challenge 2:} Five participants were placed in a censored environment which did not block Tor.
-Three of the five (P3, P4, P10) configured a bridge for their connection.
-Of the other two, one participant (P2) was convinced that configuring a bridge was the correct course of action, but was intimidated at the thought of doing so and was pleasantly surprised when a direct connection succeeded; only one participant (P9) believed that a direct connection would work.
-%\item {\bfseries Proof of Challenge 3:} All three of our participants who failed to circumvent the simulated censorship environment (P14, P15, P16) spent 25-30 minutes trying to correctly configure a proxy, which was never necessary to connect to the Tor network.
-Out of the five participants who needed to fix their bridge settings, there were only two participants (P5, P6) who eventually were able to figure out that their bridge settings needed to be adjusted.
-%\item {\bfseries Proof of Challenge 4:} One participant (P14) tried the same configuration seven times, even though those settings failed each time.
-Another participant (P12) tries the same configuration three times, and only manages to connect through a technical artifact of the experiment even though that should not have worked.
-Both of these participants emphasized that they did not know what they should be doing.
-Other participants' interview responses also indicate a lack of feedback after failure cases (P8, P15, P16).
-%\end{itemize}
-
 \subsubsection{User Communication} 
@@
 \section{Redesigning the Configuration Interface}
+
 \begin{figure*}[t]
 	\centering
+		\includegraphics[width=.85\textwidth]{old-flow.pdf}
+\hrule
 		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
-		\caption{new flow} 
+\caption{
+Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
+We collapsed the two bridge screens into one;
+similarly the two proxy screens.
+We swapped the order of the bridge and proxy configuration
+so it matches the order of network components (Section~\ref{sec:components}).
+We added a summary screen as a last step before initiating a connection.\\
+\textbf{F}: first screen;
+\textbf{B/B1/B2}: bridge screens;
+\textbf{P/P1/P2}: proxy screens;
+\textbf{S}: summary screen;
+\textbf{Pr}: progress bar.
+}
+\label{fig:flow}
 \end{figure*}
@@
 	\centering
-		\includegraphics[width=1.0\textwidth]{bridge-screens.pdf} 
+		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
 		\caption{bridge screens} 
@@
 	\centering
-		\includegraphics[width=1.0\textwidth]{proxy-screens.pdf} 
+		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
 		\caption{proxy-screens} 
@@
  \end{itemize}
-
-%HEURISTICS
-%\begin{enumerate}
-%    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
-%    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
-%    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
-%    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
-%\end{enumerate}
 
@@
 \end{enumerate}
-
-%EMPIRICALS
-%\begin{enumerate}
-%    \item {\bfseries Task Completion}: Almost all can successfully connect to Tor
-%    \item {\bfseries  Time to Completion}: Time to completion. 
-%    \item {\bfseries Safe for High-Risk Users}: It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
-%\end{enumerate}
 

### 2016-04-14 pets2017-paper/pets2017-paper.tex
this fixes a weird page break error.

@@
 \subsection{Interacting Network Components} 
-\label{sec:components}
 Bridges, pluggable transports, and proxies are network components that 
@@
 		\includegraphics[width=.85\textwidth]{old-flow.pdf} 
-\hrule
+		\caption{old flow} 
+	\label{fig:old-flow}
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
 		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
-\caption{
-Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
-We collapsed the two bridge screens into one;
-similarly the two proxy screens.
-We swapped the order of the bridge and proxy configuration
-so it matches the order of network components (Section~\ref{sec:components}).
-We added a summary screen as a last step before initiating a connection.\\
-\textbf{F}: first screen;
-\textbf{B/B1/B2}: bridge screens;
-\textbf{P/P1/P2}: proxy screens;
-\textbf{S}: summary screen;
-\textbf{Pr}: progress bar.
-}
-\label{fig:flow}
+		\caption{new flow} 
 \end{figure*}

### 2016-04-14 pets2017-paper/pets2017-paper.tex
add captions to flow images.

@@
 		\includegraphics[width=.85\textwidth]{old-flow.pdf} 
-		\caption{old flow} 
+		\caption{The current configuration interface has six screens. The first screen (F), bridge 
+		question screen (B1), bridge configuration screen (B2), proxy question screen (P1), proxy configuration
+		screen (P2), and a progress bar (Pr). If users answer yes to questions on B1 and P1, the 
+		interface deems that they do need to configure a bridge or proxy and direct users to B2 and P2, respectively. 
+		If they answer no, the interface deems that they do not need to configure a bridge or proxy and 
+		they are directed to P1, Pr, respectively.}
 	\label{fig:old-flow}
@@
 		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
-		\caption{new flow} 
+		\caption{The redesigned configuration interface has five screens. The first screen (F), proxy configuration
+		screen (P), a bridge configuration screen (B), summary screen (S), and a progress bar (Pr). The proxy 
+		screen detects the need for a proxy and tells participants if they need to configure one, eliminating the need
+		for a proxy question. The bridge configuration screen has the option to not configure a bridge, which 
+		eliminates the need for a bridge question screen.} 
 \end{figure*}

### 2016-04-14 experiment/processing/graphs.R
Diminish grid lines in all-participant-edges.pdf.

@@ -125,6 +125,9 @@ p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid,
 # p <- p + geom_point(color="black", size=1.5, shape="|")
 p <- p + geom_point(data=participants[is.na(participants$time_to_success), ], aes(x=pid, y=maxtime/60), shape=4)
 p <- p + coord_flip()
+p <- p + scale_y_continuous(breaks=pretty_breaks(n=10))
 p <- p + labs(title=NULL, x="Participants", y="Minutes elapsed")
 p <- common_theme(p)
+p <- p + theme(panel.grid.minor.x=element_blank())
+p <- p + theme(panel.grid.major.y=element_blank())
 ggsave("all-participant-edges.pdf", p, width=textwidth, height=textheight-0.75)

### 2016-04-14 experiment/processing/graphs.R
Use ColorBrewer "Set1" for all-participant-edges.pdf palette.
It's not perfect but it's more distinguishable than the default.

@@ -95,7 +95,7 @@ map_screens <- function(x) {
 		"progress"=c("progress_bar", "inlineprogress"),
 		"error"="errorPanel"
 	)
-	y
+	droplevels(y)
 }
 
 # Remove edges that start after maxtime, and trim those that overlap it
@@ -119,6 +119,8 @@ edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
 edges$src <- map_screens(edges$src)
 edges$dst <- map_screens(edges$dst)
 
+state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
+
 p <- ggplot()
 p <- p + geom_segment(data=participants, size=0.2, color="black", aes(x=pid, xend=pid, y=0, yend=ifelse(!is.na(time_to_success), time_to_success, maxtime)/60))
 p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid, y=time_from_start/60, yend=(time_from_start+duration)/60, color=dst))
@@ -126,6 +128,7 @@ p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid,
 p <- p + geom_point(data=participants[is.na(participants$time_to_success), ], aes(x=pid, y=maxtime/60), shape=4)
 p <- p + coord_flip()
 p <- p + scale_y_continuous(breaks=pretty_breaks(n=10))
+p <- p + scale_color_manual(values=state.palette)
 p <- p + labs(title=NULL, x="Participants", y="Minutes elapsed")
 p <- common_theme(p)
 p <- p + theme(panel.grid.minor.x=element_blank())

### 2016-04-14 experiment/processing/graphs.R
Provide short keys (e.g. P, B1, B2, etc.) in graph legend.

@@ -79,18 +79,24 @@ p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 
 
-# Maps instrumentation screen names into something presentable.
-map_screens <- function(x) {
+# Canonicalize screen names from the OLD and NEW interfaces.
+canonicalize_screens <- function(version, x) {
 	y <- factor(x)
+	# In the NEW interface, the screen that's logged as "bridges"
+	# corresponds more closely to the "bridgeSettings" screen in the OLD
+	# interface than it does the OLD "bridges" screen. Similarly NEW
+	# "proxy" corresponds to OLD "proxyYES".
+	y[version=="NEW" & y=="bridges"] <- "bridgeSettings"
+	y[version=="NEW" & y=="proxy"] <- "proxyYES"
 	levels(y) <- list(
-		"not running"="not_running",
+		"not_running"="not_running",
 		"starting"="starting",
 		"first"="first",
-		"bridge 1"="bridges",
-		"bridge 2"="bridgeSettings",
-		"bridge help"="bridgeHelp",
-		"proxy 1"="proxy",
-		"proxy 2"="proxyYES",
+		"bridges"="bridges",
+		"bridgeSettings"="bridgeSettings",
+		"bridgeHelp"="bridgeHelp",
+		"proxy"="proxy",
+		"proxyYES"="proxyYES",
 		"summary"="summary",
 		"progress"=c("progress_bar", "inlineprogress"),
 		"error"="errorPanel"
@@ -116,8 +122,8 @@ edges <- edges[is.na(edges$time_to_success) | edges$time_from_start <= edges$tim
 edges <- trim_edges(edges, maxtime)
 # Ignore "not_running" and "starting", so they just show up as blank.
 edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
-edges$src <- map_screens(edges$src)
-edges$dst <- map_screens(edges$dst)
+edges$src <- canonicalize_screens(edges$version, edges$src)
+edges$dst <- canonicalize_screens(edges$version, edges$dst)
 
 state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
 
@@ -128,7 +134,17 @@ p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid,
[…]

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Include topology.pdf.
use clamped success time graph.
add captions to redesigned bridge and proxy screens.

--- 2016-04-14 pets2017-paper/pets2017-paper.tex
@@
 \centering
-% \includegraphics[width=0.5\textwidth]{topology.png}
-{\color {red} TODO}
+\includegraphics[width=0.5\textwidth]{topology}
 \caption{
@@
 Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
-We collapsed the two bridge screens into one;
-similarly the two proxy screens.
+We collapsed the two bridge screens into one 
+and also collapsed the two proxy screens into one.
 We swapped the order of the bridge and proxy configuration
@@
 		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
-		\caption{bridge screens} 
+		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
+		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
+		be configured and directs to the bridge configuration screen (B2). 
+		The ``NEW'' interface gives users advice on configuring bridges
+		while giving the option of not configuring a bridge, on one screen (B).} 
 \end{figure*}
@@
 		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
-		\caption{proxy-screens} 
+		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
+		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
+		proxy configuration screen (P2). The ``NEW'' interface checks the local machine for if a proxy configured,
+		and informs the user if the proxy is required, and if so, what those settings are (P).'' }
 \end{figure*}
@@
 
+%\begin{figure}
+%\centering
+%\includegraphics{time_to_success}
+%\caption{
+%Time to first success, by censorship environment and interface.
+%The dots show the raw completion times;
+%while the boxplots show the medians and interquartile ranges.
+%The ``DNF'' figures at the right
+%show the number of participants who did not finish
+%in the time alloted.
+%}
+%\label{fig:time_to_success}
+%\end{figure}
+
 \begin{figure}
 \centering
-\includegraphics{time_to_success}
+\includegraphics{time_to_success_clamped}
 \caption{
 Time to first success, by censorship environment and interface.
-The dots show the raw completion times;
+The dots show the raw completion times,
 while the boxplots show the medians and interquartile ranges.
-The ``DNF'' figures at the right
-show the number of participants who did not finish
-in the time alloted.
+The ``DNF'' figures at the right show the number of participants 
+who did not finish in the time alloted.
+Here, non-finishing participants are assigned a time of 40 minutes.
 }
-\label{fig:time_to_success}
+\label{fig:time_to_success_clamped}
 \end{figure}
-
-%\begin{figure}
-%\centering
-%\includegraphics{time_to_success_clamped}
-%\caption{
-%Time to first success, by censorship environment and interface.
-%Here, non-finishing participants are assigned a time of 40 minutes.
-%}
-%\label{fig:time_to_success_clamped}
-%\end{figure}
 
@@
 \section{Discussion} 
-{\color {red} TODO: improvements.} \\
-{\color {red} TODO: subjective observations.} \\
 {\color {red} TODO: remaining issues.} \\

### 2016-04-14 pets2017-paper/pets2017-paper.tex
Revise description of environments.

@@
 
-\subsection{Setup}
-\label{sec:setup}
-We simulated three censorship environments for our qualitative and quantitative user studies. \\
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Mild censorship (E1)}: 
-(Representative of countries such as France and Australia.)
-Certain domains are blocked. Reaching these 
-domains requires a censorship circumvention 
-tool like Tor, but Tor is not explicitly blocked. 
-The default option to ``connect'' to the Tor network 
-directly will circumvent this censor. Additional correct
-bridge or proxy configurations are optional.
-
-\item {\bfseries Intermediate censorship (E2)}: 
-(Representative of countries such as Tunisia.)
-Certain domains are blocked. Censorship circumvention
-tools such as Tor are blocked. Since all public Tor
-relay nodes are blocked, the default option to ``connect'' to the Tor network
-directly will fail. Any choice of a hard-coded bridge
-or a valid non-public bridge will circumvent this censor.  
-Additional correct proxy configuration is optional.
-
-\item {\bfseries Comprehensive censorship (E3)}:
-(Representative of countries such as China and Syria.)
-Certain domains are blocked. Censorship circumvention tools
-are thoroughly blocked. Tor is blocked by blocking all public
-Tor relay nodes, and the censor has examined source code to block
-all hard-coded bridge relays in the configuration interface. The default option
-to ``connect'' to the Tor network directly will fail. Most bridges will fail,
-but ``meek-amazon,'' ``meek-azure,'' and ``meek-google'' still work.
-This is because domain-fronting requires censors to block entire CDNs to also
-block this transport, which causes huge collateral blocking damage that
-makes the censorship very visible and inconvenient. Currently, even
-aggressive censorship environments resistant blocking entire CDNs.
-(See~\cite{fifield2015blocking} for additional details.)
-\end{itemize}
-
-These reproducible, stable environments are informed by our experience 
-with pluggable transports and knowledge of commonly seen censorship 
-techniques. Their goal in our user study is not to replicate the network 
-environment in any particular country, but to require our distinct configurations
-so that interface paths are tested.
+\subsection{Censorship Environments}
+\label{sec:environments}
+We simulated three censorship environments,
+which we labeled ``E1,'' ``E2,'' and ``E3''
+in order of increasing severity.
+We designed the environments to be representative
+of what, in our estimation, are important real-world
+cases of censorship, but they are not intended to imitate
+any particular country's censorship exactly.
+
+\smallskip
+
+\begin{description}
+\item[E1: Mild censorship]
+The E1 environment only blocks some websites,
+as if by DNS poisoning.
+We blocked subdomains of torproject.org
+and wikipedia.org.
+(Reading a page on en.wikipedia.org was the participants' main goal.)
+To succeed in this environment,
+participants had only to click ``Connect'' on the first screen;
+additional configuration was possible but unnecessary.
+% (Representative of countries such as France and Australia.)
+
+\item[E2: Intermediate censorship]
+The E2 environment blocks websites as in E1;
+and additionally blocks the IP addresses of public Tor relays
+and directory authorities, simulating a censor that knows
+about circumvention and tries to stop it.
+In this environment, simply clicking ``Connect'' will not work;
+participants had at least to select a built-in bridge
+(any type other than ``flashproxy'' would work).
+A custom bridge would work but was not necessary.
+% (Representative of countries such as Tunisia.)
+
+\item[E3: Comprehensive censorship]
+The E3 environment blocks websites and Tor relays as in E1 and E2;
+and additionally blocks the built-in default bridge IP addresses
+found in the Tor Browser source code.
+To succeed in this environment, participants had either to select
+one of the ``meek'' built-in bridges (no other type would work),
+or to acquire their own custom bridge and enter it manually.
+% (Representative of countries such as China and Syria.)
+\end{description}
+
+\smallskip
+
+Table~\ref{tab:environments} summarizes what is blocked
+in each environment.
+We used features of the Windows operating system to implement
+the above environments.
+To simulate website blocking, we added entries to the hosts file,
+mapping domain names to the address 127.0.0.1.
+For IP address blocking, we used Windows Firewall rules.
 
@@
 E1 only requires participants to click ``Connect'';
-E2 requires selection of an included bridge;
-and E3 requires selection of a specific included bridge,
+E2 requires selection of a built-in bridge;
+and E3 requires selection of a specific type of built-in bridge,
 or manual configuration of a custom bridge.
@@
 censorship environments and what configurations are necessary for a 
-successful connection can be found in Section~\ref{sec:setup}.
+successful connection can be found in Section~\ref{sec:environments}.
 

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Reverse the row order of tab:environments.
This way, it looks like a bar chart getting higher from E1 to E3.
edit flow figures
typo

@@
 In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
-We have shown the bridge as separate component
+We have shown the bridge as a separate component
 because of the special role it plays.
@@
 % \noalign{\hrule}
+default bridges blocked & & & X \\
+public relays blocked & & X & X \\
 websites blocked & X & X & X \\
-public relays blocked & & X & X \\
-default bridges blocked & & & X \\
 \end{tabular}
@@
 \centering
-		\includegraphics[width=.85\textwidth]{old-flow.pdf}
-\hrule
-		\includegraphics[width=1.0\textwidth]{new-flow.pdf} 
+\includegraphics[width=.85\textwidth]{old-and-new-flows.png}
 \caption{

### 2016-04-15 experiment/processing/graphs.R
Add a proper legend title to all-participant-edges.pdf.

@@ -134,7 +134,7 @@ p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid,
 p <- p + geom_point(data=participants[is.na(participants$time_to_success), ], aes(x=pid, y=maxtime/60), shape=4)
 p <- p + coord_flip()
 p <- p + scale_y_continuous(breaks=pretty_breaks(n=10))
-p <- p + scale_color_manual(values=state.palette, labels=c(
+p <- p + scale_color_manual("Current screen", values=state.palette, labels=c(
 	"first"="first (F)",
 	"bridges"="bridge yes/no (B1)",
 	"bridgeSettings"="bridge settings (B2/B)",

### 2016-04-15 experiment/processing/graphs.R
make all-participants-edges visitble to macs

@@ -149,4 +149,4 @@ p <- p + labs(title=NULL, x="Participants", y="Minutes elapsed")
 p <- common_theme(p)
 p <- p + theme(panel.grid.minor.x=element_blank())
 p <- p + theme(panel.grid.major.y=element_blank())
-ggsave("all-participant-edges.pdf", p, width=textwidth, height=textheight-0.75)
+ggsave("all-participant-edges.pdf", p, width=textwidth, height=textheight-0.75, device=cairo_pdf)

### 2016-04-15 pets2017-paper/pets2017-paper.tex
This diagram should be properly sized already.
Revise section on the current interface; say more about Tor Launcher.

@@
 \centering
-\includegraphics[width=0.5\textwidth]{topology}
+\includegraphics{topology}
 \caption{
@@
 \subsection{The Current Configuration Interface}
-Tor Browser provides a configuration interface to guide users through setting up 
-their connection. While most can connect to Tor using a direct connection, users in certain censorship environments must
-make use of additional settings, such as bridges, proxies, or both. As bridges and proxies can be configured independently or together, there are four ways to set up a connection:\\
-
-\begin{enumerate}
-    \item With a bridge and proxy
-    \item With a bridge but no proxy
-    \item Without a bridge but with a proxy
-    \item Without either a bridge or proxy
-\end{enumerate}
-
-A series of questions determines which configuration a user requires.
-The interface asks users questions along the way throughout the configuration to select components they would need to configure.
-For a successful configuration, users are required to know (or find out) the following:\\
+
+For most users, the recommended way to use Tor is through Tor Browser~\cite{torbrowser},
+a modified Firefox browser that includes a built-in Tor client.
+Tor Browser has a special software component that
+Tor Launcher starts, stops, and otherwise controls
+an underlying Tor process.
+This component is called Tor Launcher
+and it is the primary target of our study.
+% Tor Launcher is also used by Tor Messenger~\cite{tormessenger},
+% an instant messaging client.
+
+Tor Launcher has a graphical user interface,
+displayed at its first startup, that asks the user
+to configure two important settings before connecting to Tor
+for the first time:
+what proxy to use (if any) and what bridge to use (if any).
+The correct configuration settings will vary depending
+on the user and their circumstances.
+A graphical wizard asks a series of questions to guide
+users in finding the correct configuration.
+Most Tor users do not require a bridge nor a proxy and
+can simply click the ``Connect'' shortcut on
+the first page to bypass all configuration.
+Others, though, need to know or find out
+all these pieces of information:
 
@@
 	\item{Whether they are censored} 
-	\item{If the Tor Network is censored by their ISP}
+	\item{Whether the Tor network is censored by their ISP}
 	\item{Which bridges work in the current environment} 
 	\item{If no bridges work, how to get a custom bridge} 
-	\item{If a proxy is required to access the Internet}
+	\item{Whether a proxy is required to access the Internet}
 	\item{If a proxy is required, the proxy settings}
@@
 
-This puts the burden of knowing technical information and configuring correctly on the user.
-Note that bridges, pluggable transports, and proxies are technical concepts that are likely unfamiliar to the average user.
-Although burdensome, the interface takes the approach of guiding the user through this technical process in order to give users their own agency in configuring their connection.
-There has been no previous work to explore the option of automation, but a manual configuration was preferred by Tor developers since it allows the user can have control over the process.
-If a user had all the relevant information, they would be able to connect without obvious network traces of attempting to connect to Tor.
+While these steps can in principle be automated to some degree,
+the interface eschews automatic configuration through network probing
+in favor of guided manual configuration,
+in order to give users their own agency in configuring their connection.
+A knowledgeable user can connect while minimizing their network trace
+and not make it obvious that they are using Tor.
+However, this design decision puts the burden of technical knowledge and correct configuration on the user.
+The technical concepts of bridges, pluggable transports, and proxies are likely unfamiliar to the average user.
 
@@
 \caption{
-Bridge selection options in Tor Browser~5.0.3.
+Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
 The obscure strings under ``Connect with provided bridges'' denote various

### 2016-04-15 pets2017-paper/pets2017-paper.tex
add in fail and download appendix

@@
 
-{\color {red} Speculation of why certain things happened--long progress bar (there was no feedback so people assumed that they had to wait), transport selections (people in the new interface didn't see the advice sometimes), etc.}
+Despite giving 5 of the participants downloaded Tor
 
@@
 To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
-If you are able to reach the website, then you know that you have successfully circumvented censorship.
+Tor is already installed for you.
+On the desktop, you should see a globe icon that says ``Start Tor Browser.'' If you are able to reach the website, then you know that you have successfully circumvented censorship.
 Fill out the question on the worksheet.
@@
 Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
+
+\section{Failed Participants} 
+\label{failed-participants}
+
+Thought that they needed a proxy: 
+\begin{enumerate}
+\item E2-OLD-X10-20160328-132828
+\item E3-NEW-X18-20160330-170145
+\item E3-NEW-X17-20160328-160037
+\item E3-OLD-X06-20160325-175101
+\item E3-OLD-X06-20160330-181926
+\item E3-OLD-X24-20160328-155926
+\end{enumerate}
+
+Only tried connecting directly: 
+\begin{enumerate}
+\item E2-NEW-X21-20160323-133257 
+\item E2-OLD-X04-20160330-181928
+\item E2-OLD-X10-20160331-153028
+\item E3-NEW-X05-20160324-132535
+\item E3-NEW-X17-20160323-133002
+\item E3-OLD-X06-20160328-132053
+\item E3-OLD-X06-20160330-161525 
+\item E3-OLD-X12-20160330-182011
+\end{enumerate}
+
+Didn't know what to do after connecting directly and default bridge: 
+\begin{enumerate}
+\item E3-NEW-X11-20160330-161511
+\item E3-NEW-X11-20160331-174655
+\item E3-NEW-X23-20160323-133346
+\item E3-OLD-X06-20160331-174650
+\item E3-OLD-X12-20160331-153055
+\item E3-OLD-X30-20160328-134412
+\end{enumerate}
+
+Failed to use the bridges@torproject.org autoresponder: 
+\begin{enumerate}
+\item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
+\item E3-OLD-X12-20160325-140813 (Figure \ref{autoresponder2})
+\item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
+\end{enumerate}
+
+\begin{figure}[h]
+\label{autoresponder1}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
+\caption{The message that E3-NEW-X23-20160328-155924 sent to the bridge auto-responder.
+A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
+Since this request was incorrectly formatted, there was no reply.}
+\end{figure}
+
+\begin{figure}[h]
+\label{autoresponder2}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
+\caption{The message that E3-OLD-X12-20160325-140813 sent to the bridge auto-responder.
+A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
+Since this request was incorrectly formatted, there was no reply.}
+\end{figure}
+
+\begin{figure}[h]
+\label{autoresponder3}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
+\caption{The message that E3-OLD-X24-20160328-133857 sent to the bridge auto-responder.
+A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
+Since this request was incorrectly formatted, there was no reply.}
+\end{figure}
+
+\section{Tor Downloads}
+\label{tor-downloads}
+
+Participants that downloaded Tor: 
+\begin{enumerate}
+\item E1-OLD-X32-20160328-134531(Figure \ref{mirror})
+\item E2-NEW-X21-20160323-133257 (Figure \ref{techspot})
+\item E2-OLD-X10-20160323-132505 (Figure \ref{downloadio})
+\item E2-OLD-X28-20160328-134111 (Figure \ref{driverupdate})
+\item E3-NEW-X11-20160330-161511 (Figure \ref{softsonic})
+\end{enumerate}
+
+\begin{figure}[h]
+\label{downloadio}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
+\caption{X10-20160323-132505 attempted downloaded Tor Browser from TechSpot.com, but clicked on one 
+a download link which was not from TechSpot.com. The download was from 1download.io, a suspicious source.}
+\end{figure}
+
+\begin{figure}[h]
+\label{driverupdate}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
+\caption{X28-20160328-134111 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
+are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
+participant dutifully does before running the Tor Browser executable.}
+\end{figure}
+
+\begin{figure}[h]
+\label{mirror}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
+\caption{X32-20160328-134531 downloaded Tor Browser from a legitimate Tor Browser mirror,www.torservers.net/mirrors.}
+\end{figure}
+
+\begin{figure}[h]
+\label{techspot}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
+\caption{E2-NEW-X21-20160323-133257 downloaded Tor Browser from TechSpot, clicking on the download link from 
+TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Figure \ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
+\end{figure}
+
+\begin{figure}[h]
+\label{softsonic}
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
+\caption{E3-NEW-X11-20160330-161511 downloaded Tor Browser from Softsonic, a reputable-looking but
+unconfirmed site.}
+\end{figure}
+
 \end{document}

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Fix extra space before a cite.

@@
 options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
-were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added latency 
-~\cite{dingledine2009performance} causes users
+were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added
+latency~\cite{dingledine2009performance} causes users
 to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 
@@
 
-\begin{itemize}
+\begin{description}
 \item {\bfseries Tell people what to do.} Since a majority of the users will succeed if they click connect on the first screen, replacing the information about choices with explicit instructions to connect can lessen their cognitive load during the configuration process.
@@
 However, this isn't ideal.
-\end{itemize}
+\end{description}
 
@@
 
-\begin{itemize}
+\begin{description}
 \item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today.
@@
 However, there are ethical implications of making mistakes on behalf of the users if there is risk involved.
-\end{itemize}
+\end{description}
 
@@
 
-Thought that they needed a proxy: 
-\begin{enumerate}
-\item E2-OLD-X10-20160328-132828
-\item E3-NEW-X18-20160330-170145
-\item E3-NEW-X17-20160328-160037
-\item E3-OLD-X06-20160325-175101
-\item E3-OLD-X06-20160330-181926
-\item E3-OLD-X24-20160328-155926
-\end{enumerate}
-
-Only tried connecting directly: 
-\begin{enumerate}
+{\bfseries Cause 1}: only tried connecting directly (8/23): 
+\begin{itemize}
 \item E2-NEW-X21-20160323-133257 
@@
 \item E3-OLD-X12-20160330-182011
-\end{enumerate}
-
-Didn't know what to do after connecting directly and default bridge: 
-\begin{enumerate}
+\end{itemize}
+
+{\bfseries Cause 2}: didn't know what to do after connecting directly and default bridge (6/23): 
+\begin{itemize}
 \item E3-NEW-X11-20160330-161511
@@
 \item E3-OLD-X30-20160328-134412
-\end{enumerate}
-
-Failed to use the bridges@torproject.org autoresponder: 
-\begin{enumerate}
+\end{itemize}
+
+{\bfseries Cause 3}: Thought that they needed a proxy (6/23): 
+\begin{itemize}
+\item E2-OLD-X10-20160328-132828
+\item E3-NEW-X18-20160330-170145
+\item E3-NEW-X17-20160328-160037
+\item E3-OLD-X06-20160325-175101
+\item E3-OLD-X06-20160330-181926
+\item E3-OLD-X24-20160328-155926
+\end{itemize}
+
+{\bfseries Cause 4}: used the bridges autoresponder incorrectly (3/23): 
+\begin{itemize}
 \item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
@@
 \item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
-\end{enumerate}
+\end{itemize}
 
@@
 
-Participants that downloaded Tor: 
-\begin{enumerate}
+Participants that downloaded Tor (5/124): 
+\begin{itemize}
 \item E1-OLD-X32-20160328-134531(Figure \ref{mirror})
@@
 \item E3-NEW-X11-20160330-161511 (Figure \ref{softsonic})
-\end{enumerate}
+\end{itemize}
+
+Sources of downloads: 
+\begin{itemize}
+\item {\bfseries techspot.com -> 1download.io}: the ad firefox yahoo ad result for ``tor browser downloads.'' 
+\item {\bfseries driverupdate.net}: the 5th chrome google search result for ``tor browser download.'' 
+\item {\bfseries www.torservers.net/mirrors}: the first chrome google search result for ``tor browser mirror.''
+\item {\bfseries techspot.com}: the 5th chrome google search result for ``tor browser download.''
+\item {\bfseries softsonic.com}: the 2nd firefox yahoo search result for ``tor browser.''
+\end{itemize}
 

### 2016-04-15 pets2017-paper/pets2017-paper.tex
okay I'm just procrastinating at this point.

@@
 options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
-were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added
-latency~\cite{dingledine2009performance} causes users
+were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added latency 
+~\cite{dingledine2009performance} causes users
 to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Define a \pquote macro for formatting participant quotes.

--- 2016-04-15 pets2017-paper/pets2017-paper.tex
@@
 \cclogo{\includegraphics{by-nc-nd.pdf}}
+
+% Format a participant quotation. It should be inside a quotation environment.
+\newcommand{\pquote}[2]{
+\begin{quotation}
+\noindent #1:~\textit{``#2''}
+\end{quotation}
+}
 
@@
 
-\begin{quotation}
-\noindent P2:\textit{"I don't know what any of those means (list of bridges),or what that (proxy)
- means at all."}\\
-
- \noindent P3:\textit{``The vocabulary is really challenging, for someone not doing IT work.''}\\
-
- \noindent P4:\textit{``I didn't know why I was getting back `establishing encrypted directory'--what does that mean?''}\\
-\end{quotation} 
+\pquote{P2}{I don't know what any of those means (list of bridges),or what that (proxy) means at all.}
+\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
+\pquote{P4}{I didn't know why I was getting back `establishing encrypted directory'---what does that mean?}
 The text in the interface intended to guide users through the process was not understood by our participants.
@@
 When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process.
-\begin{quotation}
-\noindent P9: \textit{``Configure seemed manual, so I clicked connect.''}\\
-
-\noindent P14:\textit{``The words were confusing.
+\pquote{P9}{Configure seemed manual, so I clicked connect.}
+\pquote{P14}{The words were confusing.
 I don't really understand computers.
@@
 Hmm, is it going to crash?
-When you see connect, you want to click it because you really want it to connect.''}
-\end{quotation}
+When you see connect, you want to click it because you really want it to connect.}
 
@@
 
-\begin{quotation}
-\noindent P10: \textit{``I was censored, so I picked the configure.''}
-\end{quotation}
+\pquote{P10}{I was censored, so I picked the configure.}
 
@@
 
-\begin{quotation}
-\noindent P7:\textit{``The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.''}\\
-
-\noindent P12:\textit{``I decided which options to choose by process of elimination with trial and error.''}
-\end{quotation}
+\pquote{P7}{The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.}
+\pquote{P12}{I decided which options to choose by process of elimination with trial and error.}
 
@@
 
-\begin{quotation} 
-\noindent P8:\textit{``I have no clue what's the difference between flashpoxy, fte, etc.
-I need to know why the built-in ones aren't working.
-And why do I need a custom bridge if there are options built in?'}\\
-
-\noindent P7:\textit{``Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
-I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).''}
-\end{quotation}
+\pquote{P8}{I have no clue what's the difference between flashpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
+\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
 
@@
 
-\begin{quotation}
-\noindent P4:\textit{``When I saw obfs3 as the recommended option, the next option logically for me was obfs4.''}\\
-
-\noindent P5:\textit{``I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).''}
-\end{quotation}
+\pquote{P4}{When I saw obfs3 as the recommended option, the next option logically for me was obfs4.}
+\pquote{P5}{I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).}
 
@@
 
-\begin{quotation}
-\noindent P11:\textit{``I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..''}
-\end{quotation}
+\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..}
 
@@
 
-\begin{quotation}
-\noindent P15:\textit{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
-\end{quotation}
+\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
 
@@
 
-\begin{quotation}
-\noindent P16:\textit{``There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.''}\\
-
-\noindent P6:\textit{``How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.''}
-
-\noindent P1:\textit{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
-\end{quotation}
+\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
+\pquote{P6}{How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.}
+\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
 

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Fix some typos in participant quotes.
Reminder of E1, E2, E3 names.

@@
 
-\pquote{P8}{I have no clue what's the difference between flashpoxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
+\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
 \pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
@@
 
-Participants in the advanced censorship environment were required to select a meek bridge (not the default) or to configure a custom bridge.
+Participants in E3, the most advanced censorship environment, were required to select a meek bridge (not the default) or to configure a custom bridge.
 After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors.
@@
 
-\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance..}
+\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance.}
 
@@
 We simulated the same three censorship environments from 
-our qualitative user study. Details of the mild, intermediate, and advanced 
+our qualitative user study. Details of the E1, E2, and E3
 censorship environments and what configurations are necessary for a 

### 2016-04-15 experiment/processing/graphs.R
Use the session date+time as the participant ID, not the runid.

@@ -12,7 +12,7 @@ height <- 1.5
 
 participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E1-NEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"))
-participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$runid))
+participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$session))
 participants$pid <- factor(participants$pid, levels=participants$pid[order(participants$env, participants$version, participants$time_to_success)])
 
 # This is the length of the experiment, after which to cut off measurements.

### 2016-04-15 pets2017-paper/pets2017-paper.tex
find out basics on summary, proxy, and progress edges.

@@
 \centering
-\includegraphics{topology}
+\includegraphics{topology.pdf}
 \caption{
@@
 \subsection{Results}
+
+%basic statistics (BAD SO FAR)
 Results from statistical analyses say: 
@@
 
+% impacts of adding in a summary page 
+adding in a summary screen causes people to think about their configuration.
+summary to bridge settings: 13 \% (15/119)
+summary to progress: 86 \% (102/119)
+summary to summary: 1 \% (2/119)
+
+%how much time participants in aggregate spent in progress bar 
+overall, participants spent 65\% of their time in the progress bar. 
+e1 participants spent 28\% of their time in the progress bar. 
+e2 participants spent 74\% of their time in the progress bar. 
+e3 participants spent 63\% of their time in the progress bar. 
+new participants spent 78\% of their time in the progress bar. 
+old participants spent 57 \% of their time in the progress bar.
+
+% how much time participants spent on average would be nice. (maybe I can do this later). 
+%	i.e. the average participant in e1 spent x\% of their time in the progress bar.
+
+% overall time spent configuring a proxy
+overall, participants spent 18\% of their overall time configuring a proxy. 
+e1 participants spent 16\% of their overall time configuring a proxy. 
+e2 participants spent 10\% of their overall time configuring a proxy. 
+e3 participants spent 21\% of their overall time configuring a proxy.  
+new participants spent 7\% of their overall time configuring a proxy.  
+old participants spent 25 \% of their overall time configuring a proxy.
+
+% ``active'' time spent configuring a proxy
+overall, participants spent 52\% of their active time configuring a proxy. 
+e1 participants spent 22\% of their active time configuring a proxy. 
+e2 participants spent 40\% of their active time configuring a proxy. 
+e3 participants spent 57\% of their active time configuring a proxy.  
+new participants spent 31\% of their active time configuring a proxy.  
+old participants spent 58\% of their active time configuring a proxy.
+
+> sum(proxy_edges$duration)/sum(active_edges$duration)*100
+[1] 51.5947
+> sum(proxy_edges[proxy_edges[,"env"]=="E1",]$duration)/sum(active_edges[active_edges[,"env"]=="E1",]$duration)*100
+[1] 22.37932
+> sum(proxy_edges[proxy_edges[,"env"]=="E2",]$duration)/sum(active_edges[active_edges[,"env"]=="E2",]$duration)*100
+[1] 40.37673
+> # e3 % on proxy screen ("active time")
+> sum(proxy_edges[proxy_edges[,"env"]=="E3",]$duration)/sum(active_edges[active_edges[,"env"]=="E3",]$duration)*100
+[1] 56.61874
+> # new % on proxy screen ("active time")
+> sum(proxy_edges[proxy_edges[,"version"]=="NEW",]$duration)/sum(active_edges[active_edges[,"version"]=="NEW",]$duration)*100
+[1] 31.20091
+> # old % on proxy screen ("active time")
+> sum(proxy_edges[proxy_edges[,"version"]=="OLD",]$duration)/sum(active_edges[active_edges[,"version"]=="OLD",]$duration)*100
+[1] 58.14161
+
+% how much time participants spent on average during their ``active time'' would be nice (maybe I can do this later). 
+% 	i.e. the average participant in new spent x\% of their active time configuring a proxy.
+
+% looking at all factors' impact on success rate
 A logistic regression model showing effects of censorship environment, interface version,
@@
 
+% looking at all factors' impact on time to completion
 A linear regression model showing effects of censorship environment, interface version, 

### 2016-04-15 experiment/processing/graphs.R

@@ -4,30 +4,11 @@ library(RColorBrewer)
 
 source("common.R")
 
+##################
+# INITIALIZATION #
+##################
+
 height <- 1.5
-
-# Assign DNFs a maximum time_to_success.
-clamp_time_to_success <- function(participants, maxtime) {
-	df <- data.frame(participants)
-	df$time_to_success[is.na(df$time_to_success)] <- maxtime
-	df
-}
-
-time_to_success_plot <- function(participants) {
-	minutes_to_success <- participants$time_to_success/60
-	max_minutes <- max(minutes_to_success, na.rm=T)+9
-	p <- ggplot(data.frame(participants, minutes_to_success), aes(x=label, y=minutes_to_success), environment=environment())
-	p <- p + geom_boxplot(color="gray70", outlier.size=0)
-	p <- p + geom_point(size=0.8, alpha=0.6)
-	p <- p + coord_cartesian(ylim=c(0, max_minutes))
-	p <- p + coord_flip()
-	p <- p + scale_x_discrete(limits=rev(levels(participants$label)))
-	p <- p + labs(title=NULL, x=NULL, y="Minutes to first success")
-	counts <- aggregate(data.frame(participants, n=1)[, c("success", "n")], by=list(label=participants$label), sum)
-	p <- p + geom_text(data=counts, aes(x=label, y=max_minutes, label=sprintf("%d/%d DNF", n-success, n)), hjust=1, size=2, alpha=0.6)
-	p <- common_theme(p)
-	p
-}
 
 participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E1-NEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"))
@@ -42,7 +23,34 @@ maxtime <- max(40*60, participants$time_to_success, na.rm=T)
 edges <- read_edges()
 edges <- merge(edges, participants, by=c("seat", "runid"), all.y=T)
 if (any(is.na(edges$pid))) {
-	stop("found NAs in edges$pid")
+  stop("found NAs in edges$pid")
+}
+
+###################
+# TIME TO SUCCESS #
+###################
+
+# Assign DNFs a maximum time_to_success.
+clamp_time_to_success <- function(participants, maxtime) {
+  df <- data.frame(participants)
[…]

### 2016-04-15 pets2017-paper/pets2017-paper.tex
oops, delete leftover copy paste junk from R.

@@
 
-> sum(proxy_edges$duration)/sum(active_edges$duration)*100
-[1] 51.5947
-> sum(proxy_edges[proxy_edges[,"env"]=="E1",]$duration)/sum(active_edges[active_edges[,"env"]=="E1",]$duration)*100
-[1] 22.37932
-> sum(proxy_edges[proxy_edges[,"env"]=="E2",]$duration)/sum(active_edges[active_edges[,"env"]=="E2",]$duration)*100
-[1] 40.37673
-> # e3 % on proxy screen ("active time")
-> sum(proxy_edges[proxy_edges[,"env"]=="E3",]$duration)/sum(active_edges[active_edges[,"env"]=="E3",]$duration)*100
-[1] 56.61874
-> # new % on proxy screen ("active time")
-> sum(proxy_edges[proxy_edges[,"version"]=="NEW",]$duration)/sum(active_edges[active_edges[,"version"]=="NEW",]$duration)*100
-[1] 31.20091
-> # old % on proxy screen ("active time")
-> sum(proxy_edges[proxy_edges[,"version"]=="OLD",]$duration)/sum(active_edges[active_edges[,"version"]=="OLD",]$duration)*100
-[1] 58.14161
-
 % how much time participants spent on average during their ``active time'' would be nice (maybe I can do this later). 

### 2016-04-15 pets2017-paper/pets2017-paper.tex
last commit of today: rearrange results section and add TODOs in comments.

@@
 
-%basic statistics (BAD SO FAR)
-Results from statistical analyses say: 
-\begin{itemize} 
-	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
-	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
-	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
-	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
-	\item{{\bfseries impact of configuration version on success rate is not significant.}
-	Mann-Whitney, W = 5.5, p-value = 0.8248}
-	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
-	Mann-Whitney, W = 991, p-value = 0.3197}
-\end{itemize}
-
-% impacts of adding in a summary page 
-adding in a summary screen causes people to think about their configuration.
-summary to bridge settings: 13 \% (15/119)
-summary to progress: 86 \% (102/119)
-summary to summary: 1 \% (2/119)
-
 %how much time participants in aggregate spent in progress bar 
@@
 
-% looking at all factors' impact on success rate
-A logistic regression model showing effects of censorship environment, interface version,
-and recruitment pool on success finds that a difficult censorship environment is the most
-significant factor in a participant failing. Xlab participants were more likely to succeed. 
-Participants with the old version of the interface were more likely to fail.
-
-Coefficients:
-             Estimate Std. Error z value Pr(>|z|)  
-(Intercept)   19.4556  1684.3342   0.012   0.9908  
-envE2        -17.3458  1684.3342  -0.010   0.9918  
-envE3        -19.2652  1684.3341  -0.011   0.9909  
-versionOLD    -0.7095     0.5793  -1.225   0.2206  
-poolxlab       1.1218     0.5968   1.880   0.0601 .
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-% looking at all factors' impact on time to completion
-A linear regression model showing effects of censorship environment, interface version, 
-and recruitment pool on success finds that a difficult censorship environment is the most
-significant factor in taking a long time to complete the task. Participants with the old version
-of the interface and participants recruited from Xlab were likely to take longer.
-
-Coefficients:
-            Estimate Std. Error t value Pr(>|t|)    
-(Intercept)   -42.79      86.70  -0.494  0.62280    
-envE2         300.65      90.13   3.336  0.00124 ** 
-envE3         923.66     100.94   9.150 1.68e-14 ***
-versionOLD    104.78      78.70   1.331  0.18642    
-poolxlab       92.41      78.88   1.172  0.24445    
----
-Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+% impacts of adding in a summary page 
+adding in a summary screen causes people to think about their configuration.
+summary to bridge settings: 13 \% (15/119)
+summary to progress: 86 \% (102/119)
+summary to summary: 1 \% (2/119)
+
+%%% SUCCESS RATE 
+% TODO: impact of env on success (chi squared?.. Serge might be wrong on this) 
+% TODO: impact of version on success (chi squared?.. Serge might be wrong on this)
+
+%%% RIGHT CLAMP TIME 
+% done
+% TODO:  impact of env on time to success 
+% TODO: impact of version on time to success
+
+%%% RIGHT CLAMP ACTIVE TIME 
+% TODO:  time to success graph with right clamped ``active time''
+% TODO:  impact of env on time to success 
+% TODO: impact of version on time to success
+
+% basic statistics (BAD, NEED CHI SQUARED NOT KRUSKAL AND EXCLUDED DNFs)
+%Results from statistical analyses say: 
+%\begin{itemize} 
+%	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
+%	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
+%	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
+%	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
+%	\item{{\bfseries impact of configuration version on success rate is not significant.}
+%	Mann-Whitney, W = 5.5, p-value = 0.8248}
+%	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
+%	Mann-Whitney, W = 991, p-value = 0.3197}
+%\end{itemize}
+
+% looking at all factors' impact on success rate (SUCCESS RATHER THAN SUCCESS RATE?)
+%A logistic regression model showing effects of censorship environment, interface version,
+%and recruitment pool on success finds that a difficult censorship environment is the most
+%significant factor in a participant failing. Xlab participants were more likely to succeed. 
+%Participants with the old version of the interface were more likely to fail. 
+%
+%Coefficients:
+%             Estimate Std. Error z value Pr(>|z|)  
+%(Intercept)   19.4556  1684.3342   0.012   0.9908  
+%envE2        -17.3458  1684.3342  -0.010   0.9918  
+%envE3        -19.2652  1684.3341  -0.011   0.9909  
+%versionOLD    -0.7095     0.5793  -1.225   0.2206  
+%poolxlab       1.1218     0.5968   1.880   0.0601 .
+%---
+%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
+
+% looking at all factors' impact on time to completion (BAD, EXCLUDED DNFs)
+%A linear regression model showing effects of censorship environment, interface version, 
+%and recruitment pool on success finds that a difficult censorship environment is the most
+%significant factor in taking a long time to complete the task. Participants with the old version
+%of the interface and participants recruited from Xlab were likely to take longer. 
+%
+%Coefficients:
+%            Estimate Std. Error t value Pr(>|t|)    
+%(Intercept)   -42.79      86.70  -0.494  0.62280    
+%envE2         300.65      90.13   3.336  0.00124 ** 
+%envE3         923.66     100.94   9.150 1.68e-14 ***
+%versionOLD    104.78      78.70   1.331  0.18642    
+%poolxlab       92.41      78.88   1.172  0.24445    
+%---
+%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
 

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Update failure reasons for bridges@ mailers.
Looking at the screenshots, it's clear now why two of these failed. They
sent to the wrong addresses:
	bridges@bridges.torproject.org
	help@rt.torproject.org

@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that E3-NEW-X23-20160328-155924 sent to the bridge auto-responder.
-A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
-Since this request was incorrectly formatted, there was no reply.}
+\caption{The message that E3-NEW-X23-20160328-155924 attempted to send to the bridge auto-responder.
+The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
 \end{figure}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that E3-OLD-X12-20160325-140813 sent to the bridge auto-responder.
-A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
-Since this request was incorrectly formatted, there was no reply.}
+\caption{The message that E3-OLD-X12-20160325-140813 accidentally sent to the helpdesk rather than the bridge auto-responder.
+The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
+Since the helpdesk address is not an auto-responder, there was no reply.}
 \end{figure}

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Better phrasing.
Revise background section.
More on pluggable transports.

@@
 
-\section{Background} 
-This section examines Internet censorship, interface network components that circumvent censorship, and the Tor Browser 5.0.3 configuration interface.
-
-\subsection{Censorship Today} 
-Internet censorship is widespread throughout the world~\cite{faris2008measuring}.
-Although there are corporations, parental controls, and other forms of censorship, the most common form of censorship is done by a nation-state power, usually without the consent of the people in that residing nation.
-The risks associated with circumventing Internet censorship are largely based on geographic location, prevalence of censorship circumvention, and political status.
-
-\subsection{Interacting Network Components} 
-\label{sec:components}
-Bridges, pluggable transports, and proxies are network components that 
-circumvent censorship and interact with the Tor configuration interface. 
-These components are shown in Fig.~\ref{fig:topology}.
-Bridges and pluggable transports are completely Tor-specific concepts, whereas a proxy is not.  
-This information is necessary to configure connections to Tor in censored environments.
+\section{Circumvention and Tor}
+
+Censors of the Internet typically seek to block certain network resources such as websites.
+They use various technical means, for example falsifying DNS responses,
+blocking IP addresses, filtering keywords, and detecting protocols by deep packet inspection.
+Internet users, naturally, try to evade a censor's blocks,
+also employing a variety of technical means.
+
+Tor is an anonymity network that has also grown into
+a role as a vehicle for censorship circumvention.
+Tor routes user traffic through a random series of relays
+in a way that makes it difficult for an observer to connect source and destination.
+Tor, in its native form, is easy for censors to block,
+because the list of relays and their IP addresses is public.
+However, combined with \emph{bridges} and
+\emph{pluggable transports}, it becomes challenging to block access to Tor.
+
+Bridges are unlisted Tor relays that make it possible for a user to connect
+to the Tor network even if a censor blocks all publicly listed Tor relays.
+Pluggable transports are special protocols that run on bridges and obfuscate
+Tor's network protocol to make it difficult to detect.
 
@@
 
-Bridges are unlisted Tor relays that make it possible for a user to connect
-to the Tor network even if a censor blocks all publicly listed Tor relays. 
-Censors in countries which blocked Tor generally were motivated enough to aggressively
-block Tor in other ways, such as traffic analysis. For this reason, a bridge is usually associated
-with a pluggable transport that circumvents deep packet inspection. Transports can
-assist by obfuscating traffic or reflecting traffic through a content distribution network. 
-Proxies help bypass local network restrictions and are typically only
-needed in certain cases, such as corporate environments.
-
-\subsection{The Current Configuration Interface}
+Fig.~\ref{fig:topology} illustrates the interacting components.
+In addition to those components already mentioned,
+a user may need a local proxy in order to connect outside the local network.
+The terminology can be confusing:
+technically a Tor client is also a proxy,
+and so is a pluggable transport bridge.
+By ``proxy'' we mean an ordinary unobfuscated proxy such
+as a SOCKS or HTTP proxy.
+A proxy is only needed in certain managed networks,
+such as some corporate or university networks.
+An important distinction is that the proxy usually lies within the censor's control;
+the bridge outside.
+
+% Bridges and pluggable transports are not limited to Tor...
+
+\subsection{Tor Browser and Tor Launcher}
 
@@
 The technical concepts of bridges, pluggable transports, and proxies are likely unfamiliar to the average user.
+
+\subsection{Bridges and pluggable transports}
 
@@
 
-Fig.~\ref{fig:bridge-options} shows the bridge options
-presented to a user in Tor Browser~5.0.3.
+Tor Launcher gives access to a variety of sophisticated
+circumvention mechanisms.
+Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
+interface as it existed at the time we did our study
+and lists the available pluggable transports.
+Some transports connect directly to a static IP address,
+transforming traffic to defeat its on-the-wire identification as Tor;
+they rely on the secrecy of their IP addresses for their effectiveness.
+These include ``fte'' and ``fte-ipv6''~\cite{fte},
+which make Tor look like another protocol such as HTTP; and
+``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
+which encrypt Tor to look like random noise.
+Other transports do not depend on connecting to a static IP address:
+``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
+and the three ``meek''~\cite{fifield2015blocking} options route traffic
+through content delivery networks.
+
+Configuring a bridge requires providing one or more
+``bridge lines,'' short specifications of a bridge
+including its IP address, transport type, and other metadata.
+For ease of use, the options under ``Connect with provided bridges''
+activate ready-made, built-in bridge lines,
+hard-coded into the browser.
+Choosing ``obfs3,'' for example, activates a handful
+of bridges that use obfs3, without the user needing
+to find and paste in obfs3 bridge lines.
+A censor can of course block the IP addresses of the default bridge lines
+(except ``flashproxy'' and ``meek,'' which work differently).
+If the built-in bridges do not work, a user can obtain bridge lines
+through out-of-band channels, for instance by email~\cite{bridgedb}.
+
+The ``flashproxy'' transport, because of the way it works,
+requires users to take special technical steps before using it.
+Unlike the other options, it does not work out of the box
+in most situations, including during our experiments.
+For our participants, its presence at the top of the list
+was an inviting failure mode.
 
@@
 for hypotheses to test in quantitative research.
+
+All our experiments use (modified versions of)
+Tor Browser~5.0.3, which was the current stable release at the time we began.
+Though there were new releases during the course of the experiments,
+we stuck with 5.0.3 so as not to introduce potential confounding factors.
 
@@
 We swapped the order of the bridge and proxy configuration
-so it matches the order of network components (Section~\ref{sec:components}).
+so it matches the order of network components (compare with Fig.~\ref{fig:topology}).
 We added a summary screen as a last step before initiating a connection.\\
@@
 who did not finish in the time alloted.
-Here, non-finishing participants are assigned a time of 40 minutes.
+Here, non-finishing participants are assigned the maximum time of 40 minutes.
 }

### 2016-04-15 pets2017-paper/pets2017-paper.tex
spellcheck

@@
 We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
-and self-reported familiarity with Tor in each simluated censorship environment for our summative
+and self-reported familiarity with Tor in each simulated censorship environment for our summative
 usability test~\cite{summative}.
@@
 The logs enabled us to calculate statistics such as the success rate
-for each condition. We also recorded the particiapants' computer screens 
+for each condition. We also recorded the participants' computer screens 
 throughout the experiment to capture non-interface activity such as 
@@
 Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
-recruited from Craiglist. Ages ranged from 18 to 68
+recruited from Craigslist. Ages ranged from 18 to 68
 (mu = 28.9, sigma = 12). 56.8\% were male and 
@@
 	\end{tabular}
-\caption{A summary of partipants' success in circumventing censorship
+\caption{A summary of participants' success in circumventing censorship
 given their simulated censorship environment and version of Tor. Those who
@@
 The ``DNF'' figures at the right show the number of participants 
-who did not finish in the time alloted.
+who did not finish in the time allotted.
 Here, non-finishing participants are assigned the maximum time of 40 minutes.
@@
 \begin{enumerate}
-\item{What is your participant ID? (This can be found on the sticker ont he left hand corner of the desk you are currently sitting at.)}
+\item{What is your participant ID? (This can be found on the sticker on the left hand corner of the desk you are currently sitting at.)}
 \item{What is your gender?}

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Cite for Tor Browser 5.0.3.
Move the environments into the section on eval criteria.
This may not be the best place for it, but I feel it needs a place
outside of the section on Study 1, as it belongs equally to Study 1 and
Study 2.

@@
 
-\section{Qualitative Analysis of the Existing Interface (Study 1)}
-\label{sec:qualitative}
-
-We performed qualitative research as an exploratory effort to gain an 
-understanding of underlying problems, such as reasons for confusion 
-during the configuration process and motivations for particular choices in 
-configuration. We did this through observing each participant as they 
-interacted with Tor Browser 5.0.3 interface and interviewed them about
-their experience. This study provides insights into particular problems with 
-the current Tor Browser configuration interface, and helps us to design
-a new interface which addresses these problems and gives foundation
-for hypotheses to test in quantitative research.
-
-All our experiments use (modified versions of)
-Tor Browser~5.0.3, which was the current stable release at the time we began.
-Though there were new releases during the course of the experiments,
-we stuck with 5.0.3 so as not to introduce potential confounding factors.
-
-\subsection{Inspection}
-A combination of usability inspection methods~\cite{nielsen1994usability}
-were used to prepare for the user study. Two researchers conducted a pluralistic 
-walkthrough and stepped through various censorship
-scenarios, discussing which elements would be involved for that use case, and walking 
-through the configuration process. After compiling all the possible paths through the 
-interface, feature inspection was performed to list sequences
-of features used to accomplish typical tasks, taking note of long sequences or cumbersome
-steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
-that may cause confusion for users during our study.
-
 \subsection{Censorship Environments}
 \label{sec:environments}
-We simulated three censorship environments,
+In each experiment, we simulated three censorship environments,
 which we labeled ``E1,'' ``E2,'' and ``E3''
@@
 \end{table}
+
+\section{Qualitative Analysis of the Existing Interface (Study 1)}
+\label{sec:qualitative}
+
+We performed qualitative research as an exploratory effort to gain an 
+understanding of underlying problems, such as reasons for confusion 
+during the configuration process and motivations for particular choices in 
+configuration. We did this through observing each participant as they 
+interacted with Tor Browser 5.0.3 interface and interviewed them about
+their experience. This study provides insights into particular problems with 
+the current Tor Browser configuration interface, and helps us to design
+a new interface which addresses these problems and gives foundation
+for hypotheses to test in quantitative research.
+
+All our experiments use (modified versions of)
+Tor Browser~5.0.3, which was the current stable release at the time we began~\cite{torbrowser-503}.
+Though there were new releases during the course of the experiments,
+we stuck with 5.0.3 so as not to introduce potential confounding factors.
+
+\subsection{Inspection}
+A combination of usability inspection methods~\cite{nielsen1994usability}
+were used to prepare for the user study. Two researchers conducted a pluralistic 
+walkthrough and stepped through various censorship
+scenarios, discussing which elements would be involved for that use case, and walking 
+through the configuration process. After compiling all the possible paths through the 
+interface, feature inspection was performed to list sequences
+of features used to accomplish typical tasks, taking note of long sequences or cumbersome
+steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
+that may cause confusion for users during our study.
 

### 2016-04-15 experiment/processing/graphs.R
finish analyzing time on screens

@@ -143,6 +143,7 @@ ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=c
 # 1: group edges by their source
 # 2: get the total time each user spent on a particular screen 
 # 3: create data frame "screen time per user" which has the time a user spent on each screen 
+# 4: (TODO) historgram plot function
 
 # 1 
 active_edges <- edges[edges[,"src"] != "progress",] # "active time" is anytime that people are not on the progress screen.
@@ -169,11 +170,22 @@ screen_time_per_user <- merge(screen_time_per_user, bridge_time_per_user, by=c(1
 screen_time_per_user <- merge(screen_time_per_user, summary_time_per_user, by=c(1), all=T)
 screen_time_per_user[is.na(screen_time_per_user)] <- 0
 
+# 4
+# time_histogram <- function(time) {
+#   p <- hist(time)
+#   p <- p + xlim=c(0,40)
+#   p <- p + ylim=c(0,120)
+#   p <- p + xlab="Minutes" 
+#   p <- p + ylab="Number of Participants"
+#   p <- common_theme(p)
+#   p
+# }
+
 # PROGRESS SCREEN 
-  # 1: minutes  TOTAL time was spent on the PROGRESS screen, across users. (total, e1, e2, e3,new, old)
-  # 2: % TOTAL time was spent on the PROGRESS screen, across users. (total, e1, e2, e3,new, old)
-  # 3: minutes TOTAL time was spent on the PROGRESS screen, by each user. (total, e1, e2, e3,new, old)
-  # 4: % TOTAL time was spent on the PROGRESS screen, by each user. (total, e1, e2, e3,new, old)
+  # 1: minutes  TOTAL time on PROGRESS screen, across users. (total, e1, e2, e3,new, old)
+  # 2: % TOTAL time on PROGRESS screen, across users. (total, e1, e2, e3,new, old)
+  # 3: minutes TOTAL time on PROGRESS screen, by user. (total, e1, e2, e3,new, old)
+  # 4: % TOTAL time on PROGRESS screen, by user. (total, e1, e2, e3,new, old)
 
 # 1 
 progress_time_all = sum(progress_edges$duration)/60
[…]

### 2016-04-15 pets2017-paper/pets2017-paper.tex
Grammar fix.

@@
 		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
-		proxy configuration screen (P2). The ``NEW'' interface checks the local machine for if a proxy configured,
-		and informs the user if the proxy is required, and if so, what those settings are (P).'' }
+		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
+		and informs the user whether a proxy is required, and if so, what those settings are (P).}
 \end{figure*}

### 2016-04-15 pets2017-paper/pets2017-paper.tex
put in rough screentime stats

@@
 
-%how much time participants in aggregate spent in progress bar 
-overall, participants spent 65\% of their time in the progress bar. 
-e1 participants spent 28\% of their time in the progress bar. 
-e2 participants spent 74\% of their time in the progress bar. 
-e3 participants spent 63\% of their time in the progress bar. 
-new participants spent 78\% of their time in the progress bar. 
-old participants spent 57 \% of their time in the progress bar.
-
-% how much time participants spent on average would be nice. (maybe I can do this later). 
-%	i.e. the average participant in e1 spent x\% of their time in the progress bar.
-
-% overall time spent configuring a proxy
-overall, participants spent 18\% of their overall time configuring a proxy. 
-e1 participants spent 16\% of their overall time configuring a proxy. 
-e2 participants spent 10\% of their overall time configuring a proxy. 
-e3 participants spent 21\% of their overall time configuring a proxy.  
-new participants spent 7\% of their overall time configuring a proxy.  
-old participants spent 25 \% of their overall time configuring a proxy.
-
-% ``active'' time spent configuring a proxy
-overall, participants spent 52\% of their active time configuring a proxy. 
-e1 participants spent 22\% of their active time configuring a proxy. 
-e2 participants spent 40\% of their active time configuring a proxy. 
-e3 participants spent 57\% of their active time configuring a proxy.  
-new participants spent 31\% of their active time configuring a proxy.  
-old participants spent 58\% of their active time configuring a proxy.
-
-% how much time participants spent on average during their ``active time'' would be nice (maybe I can do this later). 
-% 	i.e. the average participant in new spent x\% of their active time configuring a proxy.
+\begin{table}
+\centering
+	\begin{tabular}{c r r r r r}
+	 & First & Proxy & Bridge & Summary & Progress \\
+	\noalign{\hrule}
+	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
+	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
+	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
+	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
+	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
+	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
+	\end{tabular}
+\caption{overall time} 
+\end{table}
+
+\begin{table}
+\centering
+	\begin{tabular}{c r r r r }
+	 & First & Proxy & Bridge & Summary \\
+	\noalign{\hrule}
+	All & 23\% & 52\% & 23\% & 2\% \\
+	NEW & 40\% & 31\% & 19\% & 9\% \\ 
+	OLD & 17\% & 58\% & 25\% & 0\% \\
+	E1 & 45\% & 22\% & 32\% & 1\% \\
+	E2 & 27\% & 40\% & 29\% & 3\% \\
+	E3 & 20\% & 57\% & 21\% & 2\% \\
+	\end{tabular}
+\caption{active time} 
+\end{table}
 
@@
 
+% new people still spent time configuring their proxy!
+
 %%% SUCCESS RATE 
@@
 % TODO: impact of version on time to success
-
-% basic statistics (BAD, NEED CHI SQUARED NOT KRUSKAL AND EXCLUDED DNFs)
-%Results from statistical analyses say: 
-%\begin{itemize} 
-%	\item{{\bfseries impact of censorship environment on success rate is not significant.} 
-%	Kruskal-Wallis, chi-squared = 4.7059, df = 2, p-value = 0.09509}
-%	\item{{\bfseries impact of censorship environment on time to completion is significant.} 
-%	Kruskal-Wallis, chi-squared = 64.565, df = 2, p-value = 9.547e-15}
-%	\item{{\bfseries impact of configuration version on success rate is not significant.}
-%	Mann-Whitney, W = 5.5, p-value = 0.8248}
-%	\item{{\bfseries impact of configuration interface on time to completion is not significant.} 
-%	Mann-Whitney, W = 991, p-value = 0.3197}
-%\end{itemize}
-
-% looking at all factors' impact on success rate (SUCCESS RATHER THAN SUCCESS RATE?)
-%A logistic regression model showing effects of censorship environment, interface version,
-%and recruitment pool on success finds that a difficult censorship environment is the most
-%significant factor in a participant failing. Xlab participants were more likely to succeed. 
-%Participants with the old version of the interface were more likely to fail. 
-%
-%Coefficients:
-%             Estimate Std. Error z value Pr(>|z|)  
-%(Intercept)   19.4556  1684.3342   0.012   0.9908  
-%envE2        -17.3458  1684.3342  -0.010   0.9918  
-%envE3        -19.2652  1684.3341  -0.011   0.9909  
-%versionOLD    -0.7095     0.5793  -1.225   0.2206  
-%poolxlab       1.1218     0.5968   1.880   0.0601 .
-%---
-%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
-
-% looking at all factors' impact on time to completion (BAD, EXCLUDED DNFs)
-%A linear regression model showing effects of censorship environment, interface version, 
-%and recruitment pool on success finds that a difficult censorship environment is the most
-%significant factor in taking a long time to complete the task. Participants with the old version
-%of the interface and participants recruited from Xlab were likely to take longer. 
-%
-%Coefficients:
-%            Estimate Std. Error t value Pr(>|t|)    
-%(Intercept)   -42.79      86.70  -0.494  0.62280    
-%envE2         300.65      90.13   3.336  0.00124 ** 
-%envE3         923.66     100.94   9.150 1.68e-14 ***
-%versionOLD    104.78      78.70   1.331  0.18642    
-%poolxlab       92.41      78.88   1.172  0.24445    
-%---
-%Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1
 

### 2016-04-15 experiment/processing/graphs.R

@@ -73,7 +73,7 @@ canonicalize_screens <- function(version, x) {
 edges$src <- canonicalize_screens(edges$version, edges$src)
 edges$dst <- canonicalize_screens(edges$version, edges$dst)
 
-
+state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
 
 ###################
 # TIME TO SUCCESS #
@@ -148,6 +148,7 @@ ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=c
 # 1 
 active_edges <- edges[edges[,"src"] != "progress",] # "active time" is anytime that people are not on the progress screen.
 progress_edges <- edges[edges[,"src"]== "progress",]
+first_edges <- edges[edges[,"src"]== "first",]
 proxy_edges <- edges[edges[,"src"] %in% c("proxy","proxyYES"),]
 bridge_edges <-  edges[edges[,"src"] %in% c("bridges","bridgeSettings","bridgeHelp"),]
 summary_edges <- edges[edges[,"src"]== "summary",]
@@ -156,6 +157,7 @@ summary_edges <- edges[edges[,"src"]== "summary",]
 total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)
 active_time_per_user <- aggregate(active_edges$duration ~ active_edges$userid, active_edges, sum)
 progress_time_per_user <- aggregate(progress_edges$duration ~ progress_edges$userid, progress_edges, sum)
+first_time_per_user <- aggregate(first_edges$duration ~ first_edges$userid, first_edges, sum)
 proxy_time_per_user <- aggregate(proxy_edges$duration ~ proxy_edges$userid, proxy_edges, sum)
 bridge_time_per_user <- aggregate(bridge_edges$duration ~ bridge_edges$userid, bridge_edges, sum)
 summary_time_per_user <- aggregate(summary_edges$duration ~ summary_edges$userid, summary_edges, sum)
@@ -234,10 +236,29 @@ hist(p_user_progress_time_e3, xlim=c(0,100), ylim=c(0,15))
 hist(p_user_progress_time_new, xlim=c(0,100), ylim=c(0,15))
 hist(p_user_progress_time_old, xlim=c(0,100), ylim=c(0,15))
 
+# FIRST SCREEN
[…]

### 2016-04-15 pets2017-paper/pets2017-paper.tex
structure results and discussion section

@@
 \subsection{Results} 
-
-\begin{table}
-\centering
-	\begin{tabular}{c r r r r r}
-	 & First & Proxy & Bridge & Summary & Progress \\
-	\noalign{\hrule}
-	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
-	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
-	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
-	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
-	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
-	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
-	\end{tabular}
-\caption{overall time} 
-\end{table}
-
-\begin{table}
-\centering
-	\begin{tabular}{c r r r r }
-	 & First & Proxy & Bridge & Summary \\
-	\noalign{\hrule}
-	All & 23\% & 52\% & 23\% & 2\% \\
-	NEW & 40\% & 31\% & 19\% & 9\% \\ 
-	OLD & 17\% & 58\% & 25\% & 0\% \\
-	E1 & 45\% & 22\% & 32\% & 1\% \\
-	E2 & 27\% & 40\% & 29\% & 3\% \\
-	E3 & 20\% & 57\% & 21\% & 2\% \\
-	\end{tabular}
-\caption{active time} 
-\end{table}
-
-% impacts of adding in a summary page 
-adding in a summary screen causes people to think about their configuration.
-summary to bridge settings: 13 \% (15/119)
-summary to progress: 86 \% (102/119)
-summary to summary: 1 \% (2/119)
-
-% new people still spent time configuring their proxy!
-
-%%% SUCCESS RATE 
+Out of our 124 participants,  we have 116 valid data points.
+{\color {red} TODO} participants downloaded their own version of Tor, and {\color {red} TODO} participants did not sign the consent form.
+We have 58 valid participants who tested the new interface, and 58 who tested the old interface.
+38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
+Table~\ref{table:participant-summary} summarizes participants' success based on their interface version and environment combination.
+
+The impact of the version on success rate is (significant,not significant). 
+The impact of the environment on success rate is (significant,not significant). 
+% SUCCESS
+% TODO: impact of version on success (chi squared?.. Serge might be wrong on this) 
 % TODO: impact of env on success (chi squared?.. Serge might be wrong on this)
-% TODO: impact of version on success (chi squared?.. Serge might be wrong on this)
-
+
+Talk about why we chose to assign the max time of 40 minutes to did not finish. 
+The impact of the version on time to completion is (significant,not significant). 
+The impact of the environment on time to completion is (significant,not significant).
+Figure~\ref{fig:time_to_success_clamped}
 %%% RIGHT CLAMP TIME 
-% done
 % TODO:  impact of env on time to success 
@@
 
-%%% RIGHT CLAMP ACTIVE TIME 
-% TODO:  time to success graph with right clamped ``active time''
-% TODO:  impact of env on time to success 
-% TODO: impact of version on time to success
-
+%TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.
 \begin{table}
@@
 	\end{tabular}
-\caption{A summary of participants' success in circumventing censorship
+\caption{{\color{red} TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.}
+A summary of participants' success in circumventing censorship
 given their simulated censorship environment and version of Tor. Those who
@@
 to success.}
+\label{table:participant-summary}
 \end{table}
-
-%\begin{figure}
-%\centering
-%\includegraphics{time_to_success}
-%\caption{
-%Time to first success, by censorship environment and interface.
-%The dots show the raw completion times;
-%while the boxplots show the medians and interquartile ranges.
-%The ``DNF'' figures at the right
-%show the number of participants who did not finish
-%in the time alloted.
-%}
-%\label{fig:time_to_success}
-%\end{figure}
 
@@
 \end{figure}
+
+Our participants had 40 minutes. In real life, people may give up a lot sooner. 
+Figure~\ref{fig:time_to_success_ecdf}. Table~\ref{table:less_time}.
 
@@
 After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
+\label{table:less_time}
 \end{table}
@@
 {\color {red} TODO} 
-\caption{time spent on each screen}
-\end{figure}
+\caption{order pluggable transports were chosen}
+\end{figure}
+
+\section{Discussion}
+
+People spent a lot of time just waiting at the progress bar.
+
+Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
+The impact of the version on active time is (significant,not significant). 
+The impact of the environment on active time is (significant,not significant).
+%%% RIGHT CLAMP ACTIVE TIME 
+% TODO:  impact of env on time to success 
+% TODO: impact of version on time to success
 
 \begin{figure}
-%\includegraphics{}
-{\color {red} TODO} 
-\caption{order pluggable transports were chosen}
-\end{figure}
-
-\section{Discussion} 
-{\color {red} TODO: remaining issues.} \\
-{\color {red} recommendations are below.} \\
+\centering
+\includegraphics{time_to_success_clamped}
+\caption{
+{\color{red} MAKE THIS FOR ACTIVE TIME}
+}
+\label{fig:active_time_clamped}
+\end{figure}
+
+%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
+\begin{table}
+\centering
+	\begin{tabular}{c r r r r r}
+	 & First & Proxy & Bridge & Summary & Progress \\
+	\noalign{\hrule}
+	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
+	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
+	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
+	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
+	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
+	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
+	\end{tabular}
+\caption{overall time} 
+\label{table:overall_time}
+\end{table}
+
+%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
+\begin{table}
+\centering
+	\begin{tabular}{c r r r r }
+	 & First & Proxy & Bridge & Summary \\
+	\noalign{\hrule}
+	All & 23\% & 52\% & 23\% & 2\% \\
+	NEW & 40\% & 31\% & 19\% & 9\% \\ 
+	OLD & 17\% & 58\% & 25\% & 0\% \\
+	E1 & 45\% & 22\% & 32\% & 1\% \\
+	E2 & 27\% & 40\% & 29\% & 3\% \\
+	E3 & 20\% & 57\% & 21\% & 2\% \\
+	\end{tabular}
+\caption{active time} 
+\label{table:active_time}
+\end{table}
+
+% impacts of making the proxy page ``automated'' 
+New people still spent time configuring their proxy!
+
+% impacts of making bridge page collapsed 
+This is unclear. And people didn't really see our advice that we put on the page.
+
+% impacts of adding in a summary page 
+adding in a summary screen causes people to think about their configuration.
+summary to bridge settings: 13 \% (15/119)
+summary to progress: 86 \% (102/119)
+summary to summary: 1 \% (2/119)
+
+%FAILURES
+Elaborate on why people failed:  
+\begin{enumerate}
+\item only tried connecting directly (8/23)
+\item didn't know what to do after connecting directly and default bridge (6/23)
+\item Thought that they needed a proxy (6/23)
+\item used the bridges auto-responder incorrectly (3/23)
+\end{enumerate}
 
@@
 
-Despite giving 5 of the participants downloaded Tor
+Mention of people downloading their own Tor.
 

### 2016-04-17 experiment/processing/attempts.R
Have attempts.R output a table of success mechanisms.

@@ -1,20 +1,68 @@
 source("common.R")
 
-options(width=400)
-
 participants <- filter_participants(read_participants())
 attempts <- read.csv("attempts.csv")
-attempts$bridge_custom_entry = substr(attempts$bridge_custom_entry, 1, 30)
 
 attempts <- merge(attempts, participants, by=c("seat", "runid"), all.y=T)
 
 attempts <- attempts[order(attempts$seat, attempts$runid, attempts$time_from_start), ]
+# Remove attempts after the first successful one.
 attempts <- attempts[is.na(attempts$time_to_success) | attempts$time_from_start <= attempts$time_to_success, ]
 
 attempts$bridge_default_selection[!attempts$bridge_yesno] <- NA
 
 # Show all attempts (up to first success).
-attempts[, c("env", "version", "runid", "attempt_successful", "time_from_start", "bridge_yesno", "bridge_radio_state", "bridge_default_selection", "bridge_custom_entry", "proxy_yesno", "proxy_type", "proxy_addr", "proxy_port")]
+# attempts[, c("env", "version", "runid", "attempt_successful", "time_from_start", "bridge_yesno", "bridge_radio_state", "bridge_default_selection", "bridge_custom_entry", "proxy_yesno", "proxy_type", "proxy_addr", "proxy_port")]
 
 # Show first successful attempts.
 # attempts[attempts$attempt_successful, c("env", "version", "runid", "attempt_successful", "time_from_start", "bridge_yesno", "bridge_radio_state", "bridge_default_selection", "bridge_custom_entry", "proxy_yesno", "proxy_type", "proxy_addr", "proxy_port")]
+
+successful.attempts <- attempts[attempts$attempt_successful, ]
+successful.attempts$label <- sprintf("%s, %s",
+	# bridge label
+	ifelse(successful.attempts$bridge_yesno,
+		ifelse(successful.attempts$bridge_radio_state == "default",
+			as.character(successful.attempts$bridge_default_selection),
+			"custom bridge"),
+		"no bridge"),
+	# proxy label
+	ifelse(successful.attempts$proxy_yesno,
+		"3rd-party proxy",
+		"no proxy")
+)
+
+# Convert a number to a decimal string, but map 0 to "".
+omitzero <- function(n) {
[…]

### 2016-04-17 pets2017-paper/pets2017-paper.tex
Add a table of successful bridge–proxy combinations.

@@
 
+\begin{table}
+\centering
+% Generated by attempts.R, and manually reordered:
+\begin{tabular}{r c c c c c c}
+& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
+no bridge, no proxy & 17 & 13 &  &  &  &  \\
+obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
+meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
+meek-google, no proxy &  &  &  &  & 5 & 4 \\
+meek-azure, no proxy &  &  &  &  & 1 & 1 \\
+no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
+DNF &  &  & 1 & 3 & 7 & 10 \\
+\end{tabular}
+\caption{
+Bridge--proxy combinations that led to the first successful bootstrap
+in each environment and interface.
+Most E1 participants used a direct connection,
+but a few tried a built-in obfs3 bridge.
+All the E2 participants who succeeded,
+did so with obfs3 (the recommended bridge type)---none tried
+a different bridge before obfs3.
+All of the successful E3 participants, but one,
+used one of the meek bridges.
+The remaining E3 participant succeeded in an unexpected way:
+by searching the web for an open proxy and configuring it
+as the proxy setting.
+}
+\label{tab:attempts-bridge-proxy}
+\end{table}
+
 \begin{figure*}

### 2016-04-17 experiment/processing/graphs.R
deleting comments

@@ -172,17 +172,6 @@ screen_time_per_user <- merge(screen_time_per_user, bridge_time_per_user, by=c(1
 screen_time_per_user <- merge(screen_time_per_user, summary_time_per_user, by=c(1), all=T)
 screen_time_per_user[is.na(screen_time_per_user)] <- 0
 
-# 4
-# time_histogram <- function(time) {
-#   p <- hist(time)
-#   p <- p + xlim=c(0,40)
-#   p <- p + ylim=c(0,120)
-#   p <- p + xlab="Minutes" 
-#   p <- p + ylab="Number of Participants"
-#   p <- common_theme(p)
-#   p
-# }
-
 # PROGRESS SCREEN 
   # 1: minutes  TOTAL time on PROGRESS screen, across users. (total, e1, e2, e3,new, old)
   # 2: % TOTAL time on PROGRESS screen, across users. (total, e1, e2, e3,new, old)
@@ -214,13 +203,6 @@ user_progress_time_e3 <- screen_time_per_user[screen_time_per_user[,"env"]=="E3"
 user_progress_time_new <- screen_time_per_user[screen_time_per_user[,"version"]=="NEW",]$`progress_edges$duration`/60
 user_progress_time_old <- screen_time_per_user[screen_time_per_user[,"version"]=="OLD",]$`progress_edges$duration`/60
 
-hist(user_progress_time_all, xlim=c(0,40), ylim=c(0,80))
-hist(user_progress_time_e1, xlim=c(0,40), ylim=c(0,40))
-hist(user_progress_time_e2, xlim=c(0,40), ylim=c(0,40))
-hist(user_progress_time_e3, xlim=c(0,40), ylim=c(0,40))
-hist(user_progress_time_new, xlim=c(0,40), ylim=c(0,40))
-hist(user_progress_time_old, xlim=c(0,40), ylim=c(0,40))
-
 # 4
 p_user_progress_time_all <- screen_time_per_user$`progress_edges$duration`/screen_time_per_user$`edges$duration`*100
 p_user_progress_time_e1 <- screen_time_per_user[screen_time_per_user[,"env"]=="E1",]$`progress_edges$duration`/screen_time_per_user[screen_time_per_user[,"env"]=="E1",]$`edges$duration`*100
@@ -228,13 +210,6 @@ p_user_progress_time_e2 <- screen_time_per_user[screen_time_per_user[,"env"]=="E
[…]

### 2016-04-17 experiment/processing/graphs.R
update numbers to correct for overestimating time on progress bar

@@ -179,20 +179,20 @@ screen_time_per_user[is.na(screen_time_per_user)] <- 0
   # 4: % TOTAL time on PROGRESS screen, by user. (total, e1, e2, e3,new, old)
 
 # 1 
-progress_time_all = sum(progress_edges$duration)/60
-progress_time_e1 = sum(progress_edges[progress_edges[,"env"]=="E1",]$duration)/60
-progress_time_e2 =sum(progress_edges[progress_edges[,"env"]=="E2",]$duration)/60
-progress_time_e3 =sum(progress_edges[progress_edges[,"env"]=="E3",]$duration)/60
-progress_time_new =sum(progress_edges[progress_edges[,"version"]=="NEW",]$duration)/60
-progress_time_old =sum(progress_edges[progress_edges[,"version"]=="OLD",]$duration)/60
+sum(progress_edges$duration)/60
+sum(progress_edges[progress_edges[,"env"]=="E1",]$duration)/60
+sum(progress_edges[progress_edges[,"env"]=="E2",]$duration)/60
+sum(progress_edges[progress_edges[,"env"]=="E3",]$duration)/60
+sum(progress_edges[progress_edges[,"version"]=="NEW",]$duration)/60
+sum(progress_edges[progress_edges[,"version"]=="OLD",]$duration)/60
 
 # 2
-p_progress_time_all = sum(progress_edges$duration)/sum(edges$duration)*100
-p_progress_time_e1 = sum(progress_edges[progress_edges[,"env"]=="E1",]$duration)/sum(edges[edges[,"env"]=="E1",]$duration)*100
-p_progress_time_e2 =sum(progress_edges[progress_edges[,"env"]=="E2",]$duration)/sum(edges[edges[,"env"]=="E2",]$duration)*100
-p_progress_time_e3 =sum(progress_edges[progress_edges[,"env"]=="E3",]$duration)/sum(edges[edges[,"env"]=="E3",]$duration)*100
-p_progress_time_new =sum(progress_edges[progress_edges[,"version"]=="NEW",]$duration)/sum(edges[edges[,"version"]=="NEW",]$duration)*100
-p_progress_time_old =sum(progress_edges[progress_edges[,"version"]=="OLD",]$duration)/sum(edges[edges[,"version"]=="OLD",]$duration)*100
+sum(progress_edges$duration)/sum(edges$duration)*100
[…]

### 2016-04-17 pets2017-paper/pets2017-paper.tex
deleting comments
update numbers to correct for overestimating time on progress bar
count bridge choices from attempts.csv
calculate median times with DNFs

@@
 
-%TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.
 \begin{table}
@@
 	E1-NEW & 19/19 & 100\% & 0:20 \\
-	E1-OLD & 19/19 & 100\% & 1:01 \\
+	E1-OLD & 19/19 & 100\% & 1:05 \\
 	E2-NEW & 18/19 & 95\% & 3:22 \\
-	E2-OLD & 16/19 & 84\% & 4:01 \\
-	E3-NEW & 13/20 & 65\% & 12:38 \\
-	E3-OLD & 10/20 & 50\% & 18:16 \\
+	E2-OLD & 16/19 & 84\% & 5:07 \\
+	E3-NEW & 13/20 & 65\% & 22:19 \\
+	E3-OLD & 10/20 & 50\% & 40:08 \\
 	\end{tabular}
-\caption{{\color{red} TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.}
+\caption{
 A summary of participants' success in circumventing censorship
 given their simulated censorship environment and version of Tor. Those who
-failed to connect successfully were not used to calculate the median time
-to success.}
+failed to connect successfully were assigned success time for 40 minutes.}
 \label{table:participant-summary}
@@
 
-\begin{figure} 
-%\includegraphics{}
-{\color {red} TODO} 
-\caption{order pluggable transports were chosen}
-\end{figure}
-
 \section{Discussion}
@@
 
-\begin{figure}
-\centering
-\includegraphics{time_to_success_clamped}
-\caption{
-{\color{red} MAKE THIS FOR ACTIVE TIME}
-}
-\label{fig:active_time_clamped}
-\end{figure}
-
-%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
 \begin{table}
@@
 	\noalign{\hrule}
-	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
+	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
 	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
-	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
-	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
-	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
-	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
+	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
+	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
+	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
+	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
 	\end{tabular}
@@
 
-%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
 \begin{table}
@@
 	\noalign{\hrule}
-	All & 23\% & 52\% & 23\% & 2\% \\
+	All & 22\% & 57\% & 19\% & 2\% \\
 	NEW & 40\% & 31\% & 19\% & 9\% \\ 
-	OLD & 17\% & 58\% & 25\% & 0\% \\
+	OLD & 18\% & 63\% & 19\% & 0\% \\
 	E1 & 45\% & 22\% & 32\% & 1\% \\
-	E2 & 27\% & 40\% & 29\% & 3\% \\
-	E3 & 20\% & 57\% & 21\% & 2\% \\
+	E2 & 29\% & 48\% & 20\% & 2\% \\
+	E3 & 19\% & 61\% & 18\% & 2\% \\
 	\end{tabular}
@@
 This is unclear. And people didn't really see our advice that we put on the page.
+
+% impacts of giving people advice on which transport to choose.
+10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
+5 people in the old interface chose meek as their second bridge (5/13, 38\%).
 

### 2016-04-17 experiment/processing/info.R

@@ -117,6 +117,7 @@ cat("* OTHER STUFF *\n")
 cat("***************\n")
 
 cat("\n")
+# replace "participants" with "clamp_time_to_success(participants, maxtime)" to get median success times with DNFs = 40mins.
 tt <- with(participants, aggregate(success, list(env=env, version=version), FUN=length))
 tt <- merge(tt, with(participants, aggregate(success, list(env=env, version=version), FUN=sum)), by=c("env", "version"))
 tt <- merge(tt, with(participants, aggregate(time_to_success, list(env=env, version=version), FUN=function(z) {median(z, na.rm=T)})), by=c("env", "version"))

### 2016-04-17 experiment/processing/graphs.R
Remove horizontal guide lines in time_to_success graphs.

@@ -99,6 +99,7 @@ time_to_success_plot <- function(participants) {
   counts <- aggregate(data.frame(participants, n=1)[, c("success", "n")], by=list(label=participants$label), sum)
   p <- p + geom_text(data=counts, aes(x=label, y=max_minutes, label=sprintf("%d/%d DNF", n-success, n)), hjust=1, size=2, alpha=0.6)
   p <- common_theme(p)
+  p <- p + theme(panel.grid.major.y=element_blank())
   p
 }
 

### 2016-04-17 experiment/processing/graphs.R
Change the point style of DNFs in time_to_success graphs.

@@ -91,7 +91,10 @@ time_to_success_plot <- function(participants) {
   max_minutes <- max(minutes_to_success, na.rm=T)+9
   p <- ggplot(data.frame(participants, minutes_to_success), aes(x=label, y=minutes_to_success), environment=environment())
   p <- p + geom_boxplot(color="gray70", outlier.size=0)
-  p <- p + geom_point(size=0.8, alpha=0.6)
+  p <- p + geom_point(alpha=0.6, aes(size=success, color=success, shape=success))
+  p <- p + scale_size_manual(values=c("TRUE"=0.8, "FALSE"=1.0), guide=F)
+  p <- p + scale_color_manual(values=c("TRUE"="black", "FALSE"="red3"), guide=F)
+  p <- p + scale_shape_manual(values=c("TRUE"=19, "FALSE"=4), guide=F)
   p <- p + coord_cartesian(ylim=c(0, max_minutes))
   p <- p + coord_flip()
   p <- p + scale_x_discrete(limits=rev(levels(participants$label)))

### 2016-04-17 experiment/processing/graphs.R
statistical tests on active time. Serge keeps telling me not to use Kruskal-Wallis, but I am sure I shouldn't used Chi-Squared.

@@ -135,171 +135,6 @@ p <- p + annotate(geom="text", x=c(1, 3.3, 14, 15.3, 23, 24.7), y=c(0.86, 0.87, 
 p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 
-############################
-# SCREEN SPECIFIC ANALYSES #
-############################
-
-# SETUP 
-# 1: group edges by their source
-# 2: get the total time each user spent on a particular screen 
-# 3: create data frame "screen time per user" which has the time a user spent on each screen 
-# 4: (TODO) historgram plot function
-
-# 1 
-active_edges <- edges[edges[,"src"] != "progress",] # "active time" is anytime that people are not on the progress screen.
-progress_edges <- edges[edges[,"src"]== "progress",]
-first_edges <- edges[edges[,"src"]== "first",]
-proxy_edges <- edges[edges[,"src"] %in% c("proxy","proxyYES"),]
-bridge_edges <-  edges[edges[,"src"] %in% c("bridges","bridgeSettings","bridgeHelp"),]
-summary_edges <- edges[edges[,"src"]== "summary",]
-
-# 2
-total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)
-active_time_per_user <- aggregate(active_edges$duration ~ active_edges$userid, active_edges, sum)
-progress_time_per_user <- aggregate(progress_edges$duration ~ progress_edges$userid, progress_edges, sum)
-first_time_per_user <- aggregate(first_edges$duration ~ first_edges$userid, first_edges, sum)
-proxy_time_per_user <- aggregate(proxy_edges$duration ~ proxy_edges$userid, proxy_edges, sum)
-bridge_time_per_user <- aggregate(bridge_edges$duration ~ bridge_edges$userid, bridge_edges, sum)
-summary_time_per_user <- aggregate(summary_edges$duration ~ summary_edges$userid, summary_edges, sum)
-
-# 3 
-screen_time_per_user <- participants[c("userid","env","version","pool")]
-screen_time_per_user <- merge(screen_time_per_user, total_time_per_user, by=c(1), all=T)
[…]

### 2016-04-17 experiment/processing/info.R

@@ -58,6 +58,173 @@ max.e1.new <- max(participants$time_to_success[participants$env=="E1" & particip
 cat(sprintf("maximum time for E1-NEW: %s\n", format_minutes(max.e1.new)))
 
 cat("\n\n\n\n\n\n")
+cat("****************************\n")
+cat("* SCREEN SPECIFIC ANALYSES *\n")
+cat("****************************\n")
+
+# SETUP 
+# 1: group edges by their source
+# 2: get the total time each user spent on a particular screen 
+# 3: create data frame "screen time per user" which has the time a user spent on each screen 
+# 4: (TODO) historgram plot function
+
+# 1 
+active_edges <- edges[edges[,"src"] != "progress",] # "active time" is anytime that people are not on the progress screen.
+progress_edges <- edges[edges[,"src"]== "progress",]
+first_edges <- edges[edges[,"src"]== "first",]
+proxy_edges <- edges[edges[,"src"] %in% c("proxy","proxyYES"),]
+bridge_edges <-  edges[edges[,"src"] %in% c("bridges","bridgeSettings","bridgeHelp"),]
+summary_edges <- edges[edges[,"src"]== "summary",]
+
+# 2
+total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)
+active_time_per_user <- aggregate(active_edges$duration ~ active_edges$userid, active_edges, sum)
+progress_time_per_user <- aggregate(progress_edges$duration ~ progress_edges$userid, progress_edges, sum)
+first_time_per_user <- aggregate(first_edges$duration ~ first_edges$userid, first_edges, sum)
+proxy_time_per_user <- aggregate(proxy_edges$duration ~ proxy_edges$userid, proxy_edges, sum)
+bridge_time_per_user <- aggregate(bridge_edges$duration ~ bridge_edges$userid, bridge_edges, sum)
+summary_time_per_user <- aggregate(summary_edges$duration ~ summary_edges$userid, summary_edges, sum)
+
+# 3 
+screen_time_per_user <- participants[c("userid","env","version","pool")]
+screen_time_per_user <- merge(screen_time_per_user, total_time_per_user, by=c(1), all=T)
[…]

### 2016-04-17 pets2017-paper/pets2017-paper.tex
edit comments.

@@
 	\noalign{\hrule}
-	E1-NEW & 19/19 & 100\% & 0:20 \\
-	E1-OLD & 19/19 & 100\% & 1:05 \\
-	E2-NEW & 18/19 & 95\% & 3:22 \\
-	E2-OLD & 16/19 & 84\% & 5:07 \\
-	E3-NEW & 13/20 & 65\% & 22:19 \\
-	E3-OLD & 10/20 & 50\% & 40:08 \\
+	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
+	E1-OLD & 19/19 & 100\% & 1:05 \\ %medians of only finished: 1:01
+	E2-NEW & 18/19 & 95\% & 3:22 \\ %medians of only finished: 3:22
+	E2-OLD & 16/19 & 84\% & 5:07 \\ %medians of only finished: 3:13
+	E3-NEW & 13/20 & 65\% & 22:19 \\ %medians of only finished: 12:38
+	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
 	\end{tabular}
@@
 % impacts of making bridge page collapsed 
-This is unclear. And people didn't really see our advice that we put on the page.
+This is unclear.
 

### 2016-04-17 experiment/processing/graphs.R
Sort all-participant-edges in the opposite order.
This makes it match the order of our other graphs and tables.

@@ -13,7 +13,7 @@ height <- 1.5
 participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E1-NEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"))
 participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$session))
-participants$pid <- factor(participants$pid, levels=participants$pid[order(participants$env, participants$version, participants$time_to_success)])
+participants$pid <- factor(participants$pid, levels=participants$pid[rev(order(participants$env, participants$version, participants$time_to_success))])
 
 # This is the length of the experiment, after which to cut off measurements.
 # It's actually just a few seconds after 40 minutes, because one E3 just

### 2016-04-17 pets2017-paper/pets2017-paper.tex
insert statistical significane results

@@
 
-The impact of the version on success rate is (significant,not significant). 
-The impact of the environment on success rate is (significant,not significant). 
-% SUCCESS
-% TODO: impact of version on success (chi squared?.. Serge might be wrong on this) 
-% TODO: impact of env on success (chi squared?.. Serge might be wrong on this)
-
 Talk about why we chose to assign the max time of 40 minutes to did not finish. 
@@
 Figure~\ref{fig:time_to_success_clamped}
-%%% RIGHT CLAMP TIME 
-% TODO:  impact of env on time to success 
-% TODO: impact of version on time to success
+
+%stats
+impact of version on success: not significant (W = 5.5, p-value = 0.8248)
+impact of version on time to success: not significant (W = 1399, p-value = 0.1175)
+
+impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
+impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
 
@@
 Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
-The impact of the version on active time is (significant,not significant). 
-The impact of the environment on active time is (significant,not significant).
-%%% RIGHT CLAMP ACTIVE TIME 
-% TODO:  impact of env on time to success 
-% TODO: impact of version on time to success
+The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
+The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
 

### 2016-04-17 experiment/processing/info.R

@@ -272,7 +272,7 @@ kruskal.test(screen_time_per_user$`active_edges$duration` ~ env, data=screen_tim
 cat("\n\n\n\n")
 cat("logistic regression predicting success by ver, env, pool \n")
 #just env, version, pool, and success columns
-participants_glm_subset <- subset(participants,select=c(5,6,9,10))
+participants_glm_subset <- subset(clamp_time_to_success(participants, maxtime),select=c(5,6,9,10))
 model <- glm(success ~.,family=binomial(link='logit'),data=participants_glm_subset)
 summary(model)
 #cat("\n\n\n")
@@ -281,7 +281,7 @@ summary(model)
 cat("\n\n\n\n")
 cat("linear regression predicting time to success by ver, env, pool \n")
 #just env, version, pool, and time_to_success columns
-participants_lm_subset <- subset(participants,select=c(5,6,9,11))
+participants_lm_subset <- subset(clamp_time_to_success(participants, maxtime),select=c(5,6,9,11))
 model <- lm(time_to_success ~.,data=participants_lm_subset)
 summary(model)
 

### 2016-04-18 experiment/processing/common.R
Move maxtime into common.R and make it static.

@@ -8,6 +8,11 @@ textwidth <- 483.6967 / 72.27
 textheight <- 661.97234 / 72.27
 columnwidth <- 236.1578 / 72.27
 
+# This is the length of the experiment, after which to cut off measurements.
+# It's actually just a few seconds after 40 minutes, because one E3 just
+# squeaked by.
+maxtime <- 40*60 + 8
+
 # Read all the participant CSV files into one big data frame.
 read_participants <- function() {
 	participants <- read.csv("participants.csv")

### 2016-04-18 experiment/processing/graphs.R

@@ -15,11 +15,6 @@ participants$label <- factor(sprintf("%s-%s", participants$env, participants$ver
 participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$session))
 participants$pid <- factor(participants$pid, levels=participants$pid[rev(order(participants$env, participants$version, participants$time_to_success))])
 
-# This is the length of the experiment, after which to cut off measurements.
-# It's actually just a few seconds after 40 minutes, because one E3 just
-# squeaked by.
-maxtime <- max(40*60, participants$time_to_success, na.rm=T)
-
 edges <- read_edges()
 edges <- merge(edges, participants, by=c("seat", "runid"), all.y=T)
 if (any(is.na(edges$pid))) {

### 2016-04-18 experiment/processing/common.R
Make table:participant-summary output use clamped time.

@@ -34,6 +34,13 @@ read_edges <- function() {
 	read.csv("edges.csv")
 }
 
+# Assign DNFs a maximum time_to_success.
+clamp_time_to_success <- function(participants, maxtime) {
+  df <- data.frame(participants)
+  df$time_to_success[is.na(df$time_to_success)] <- maxtime
+  df
+}
+
 common_theme <- function(p) {
 	p <- p + theme_minimal()
 	p <- p + theme(text=element_text(size=8))

### 2016-04-18 experiment/processing/graphs.R

@@ -74,13 +74,6 @@ state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
 # TIME TO SUCCESS #
 ###################
 
-# Assign DNFs a maximum time_to_success.
-clamp_time_to_success <- function(participants, maxtime) {
-  df <- data.frame(participants)
-  df$time_to_success[is.na(df$time_to_success)] <- maxtime
-  df
-}
-
 time_to_success_plot <- function(participants) {
   minutes_to_success <- participants$time_to_success/60
   max_minutes <- max(minutes_to_success, na.rm=T)+9

### 2016-04-18 experiment/processing/info.R

@@ -117,9 +117,10 @@ cat("* OTHER STUFF *\n")
 cat("***************\n")
 
 cat("\n")
-tt <- with(participants, aggregate(success, list(env=env, version=version), FUN=length))
-tt <- merge(tt, with(participants, aggregate(success, list(env=env, version=version), FUN=sum)), by=c("env", "version"))
-tt <- merge(tt, with(participants, aggregate(time_to_success, list(env=env, version=version), FUN=function(z) {median(z, na.rm=T)})), by=c("env", "version"))
+tt <- with(clamp_time_to_success(participants, maxtime), merge(merge(
+	aggregate(success, list(env=env, version=version), FUN=length),
+	aggregate(success, list(env=env, version=version), FUN=sum), by=c("env", "version")),
+	aggregate(time_to_success, list(env=env, version=version), FUN=function(z) {median(z, na.rm=T)}), by=c("env", "version")))
 names(tt) <- c("env", "version", "n", "n_success", "median_time_to_success")
 
 cat("\n")

### 2016-04-18 pets2017-paper/pets2017-paper.tex
Regen table:participant-summary.

--- 2016-04-17 pets2017-paper/pets2017-paper.tex
@@
 	E1-NEW & 19/19 & 100\% & 0:20 \\
-	E1-OLD & 19/19 & 100\% & 1:05 \\
-	E2-NEW & 18/19 & 95\% & 3:22 \\
-	E2-OLD & 16/19 & 84\% & 5:07 \\
-	E3-NEW & 13/20 & 65\% & 22:19 \\
+	E1-OLD & 19/19 & 100\% & 1:01 \\
+	E2-NEW & 18/19 & 95\% & 3:32 \\
+	E2-OLD & 16/19 & 84\% & 5:00 \\
+	E3-NEW & 13/20 & 65\% & 20:56 \\
 	E3-OLD & 10/20 & 50\% & 40:08 \\
@@
 given their simulated censorship environment and version of Tor. Those who
-failed to connect successfully were assigned success time for 40 minutes.}
+failed to connect successfully were assigned the maximum time of 40:08.
+}
 \label{table:participant-summary}
@@
 who did not finish in the time allotted.
-Here, non-finishing participants are assigned the maximum time of 40 minutes.
+Here, non-finishing participants are assigned the maximum time of 40:08
+for the purpose of computing the median.
 }
@@
 
+\begin{figure} 
+%\includegraphics{}
+{\color {red} TODO} 
+\caption{order pluggable transports were chosen}
+\end{figure}
+
 \section{Discussion}
@@
 
+\begin{figure}
+\centering
+\includegraphics{time_to_success_clamped}
+\caption{
+{\color{red} MAKE THIS FOR ACTIVE TIME}
+}
+\label{fig:active_time_clamped}
+\end{figure}
+
+%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
 \begin{table}
@@
 	\noalign{\hrule}
-	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
+	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
 	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
-	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
-	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
-	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
-	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
+	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
+	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
+	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
+	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
 	\end{tabular}
@@
 
+%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
 \begin{table}
@@
 	\noalign{\hrule}
-	All & 22\% & 57\% & 19\% & 2\% \\
+	All & 23\% & 52\% & 23\% & 2\% \\
 	NEW & 40\% & 31\% & 19\% & 9\% \\ 
-	OLD & 18\% & 63\% & 19\% & 0\% \\
+	OLD & 17\% & 58\% & 25\% & 0\% \\
 	E1 & 45\% & 22\% & 32\% & 1\% \\
-	E2 & 29\% & 48\% & 20\% & 2\% \\
-	E3 & 19\% & 61\% & 18\% & 2\% \\
+	E2 & 27\% & 40\% & 29\% & 3\% \\
+	E3 & 20\% & 57\% & 21\% & 2\% \\
 	\end{tabular}
@@
 This is unclear. And people didn't really see our advice that we put on the page.
-
-% impacts of giving people advice on which transport to choose.
-10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
-5 people in the old interface chose meek as their second bridge (5/13, 38\%).
 

### 2016-04-18 experiment/processing/graphs.R
Change "Minutes to first success" to "Minutes to success" in label.

@@ -86,7 +86,7 @@ time_to_success_plot <- function(participants) {
   p <- p + coord_cartesian(ylim=c(0, max_minutes))
   p <- p + coord_flip()
   p <- p + scale_x_discrete(limits=rev(levels(participants$label)))
-  p <- p + labs(title=NULL, x=NULL, y="Minutes to first success")
+  p <- p + labs(title=NULL, x=NULL, y="Minutes to success")
   counts <- aggregate(data.frame(participants, n=1)[, c("success", "n")], by=list(label=participants$label), sum)
   p <- p + geom_text(data=counts, aes(x=label, y=max_minutes, label=sprintf("%d/%d DNF", n-success, n)), hjust=1, size=2, alpha=0.6)
   p <- common_theme(p)

### 2016-04-18 pets2017-paper/pets2017-paper.tex
Note that we cut off at 40:08.

@@
 only answering logistical questions. Participants had
-40 minutes to complete their worksheet. 
+about 40 minutes to complete their worksheet.
+(In our analysis we defined the cutoff time to be 40 minutes and 8~seconds
+in order to include a participant who finished at the wire.)
 The participants do not know the details of their censorship environment,

### 2016-04-18 pets2017-paper/pets2017-paper.tex
On second thought I like this order better (cf. d6fa8963).
This way, it matches the order in which blocking behaviors are
introduced in the text.
Explain the narrow black line in fig:all-participant-edges caption.

@@
 % \noalign{\hrule}
+websites blocked & X & X & X \\
+public relays blocked & & X & X \\
 default bridges blocked & & & X \\
-public relays blocked & & X & X \\
-websites blocked & X & X & X \\
 \end{tabular}
@@
 Different colors indicate which screen was shown at each moment.
+The narrow black lines show the times when the configuration interface
+was not running; i.e., a participant was doing something else
+such as searching the web in another browser.
 The overall length of the lines show the total time to completion,

### 2016-04-18 experiment/processing/graphs.R
Shorten the labels in all-participant-edges.
We don't need the session information here. What would be better is just
some big headings showing a block for each env-version combination. I
tried using facet_grid for that but it's not working with coord_flip.

@@ -13,7 +13,8 @@ height <- 1.5
 participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E1-NEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"))
 participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$session))
-participants$pid <- factor(participants$pid, levels=participants$pid[rev(order(participants$env, participants$version, participants$time_to_success))])
+pid_order <- rev(order(participants$env, participants$version, participants$time_to_success))
+participants$pid <- factor(participants$pid, levels=participants$pid[pid_order])
 
 edges <- read_edges()
 edges <- merge(edges, participants, by=c("seat", "runid"), all.y=T)
@@ -352,6 +353,7 @@ p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid,
 # p <- p + geom_point(color="black", size=1.5, shape="|")
 p <- p + geom_point(data=participants[is.na(participants$time_to_success), ], aes(x=pid, y=maxtime/60), shape=4)
 p <- p + coord_flip()
+p <- p + scale_x_discrete(labels=sprintf("%s-%s", participants$env[pid_order], participants$version[pid_order]))
 p <- p + scale_y_continuous(breaks=pretty_breaks(n=10))
 p <- p + scale_color_manual("Current screen", values=state.palette, labels=c(
 	"first"="first (F)",

### 2016-04-18 pets2017-paper/pets2017-paper.tex

@@
 	\noalign{\hrule}
-	E1-NEW & 19/19 & 100\% & 0:20 \\
-	E1-OLD & 19/19 & 100\% & 1:01 \\
-	E2-NEW & 18/19 & 95\% & 3:32 \\
-	E2-OLD & 16/19 & 84\% & 5:00 \\
-	E3-NEW & 13/20 & 65\% & 20:56 \\
-	E3-OLD & 10/20 & 50\% & 40:08 \\
+	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
+	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
+	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
+	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
+	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
+	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
 	\end{tabular}
@@
 Talk about the notion of ``active time,'' which is just time not spent on the progress screen. 
-The impact of the version on active time is (significant,not significant). 
-The impact of the environment on active time is (significant,not significant).
-%%% RIGHT CLAMP ACTIVE TIME 
-% TODO:  impact of env on time to success 
-% TODO: impact of version on time to success
-
-\begin{figure}
-\centering
-\includegraphics{time_to_success_clamped}
-\caption{
-{\color{red} MAKE THIS FOR ACTIVE TIME}
-}
-\label{fig:active_time_clamped}
-\end{figure}
-
-%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
+The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
+The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
+
 \begin{table}
@@
 % impacts of making bridge page collapsed 
-This is unclear. And people didn't really see our advice that we put on the page.
+This is unclear.
+
+% impacts of giving people advice on which transport to choose.
+10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
+5 people in the old interface chose meek as their second bridge (5/13, 38\%).
 

### 2016-04-18 experiment/processing/common.R
Factor edge filtering stuff into common.R.

@@ -29,9 +29,52 @@ filter_participants <- function(participants) {
 	participants[participants$good, ]
 }
 
-# Read edges.csv into one big data frame.
+# Read edges.csv into one big data frame and compute durations.
 read_edges <- function() {
-	read.csv("edges.csv")
+	edges <- read.csv("edges.csv")
+	edges <- edges[order(edges$sequence, edges$time_from_start), ]
+	edges$duration <- ave(edges$time_from_start, edges$seat, edges$runid, FUN=function(z) {
+		c(z[2:length(z)], z[length(z)]) - z
+	})
+	edges
+}
+
+# Canonicalize screen names from the OLD and NEW interfaces.
+canonicalize_screens <- function(version, x) {
+	y <- factor(x)
+	# In the NEW interface, the screen that's logged as "bridges"
+	# corresponds more closely to the "bridgeSettings" screen in the OLD
+	# interface than it does the OLD "bridges" screen. Similarly NEW
+	# "proxy" corresponds to OLD "proxyYES".
+	y[version=="NEW" & y=="bridges"] <- "bridgeSettings"
+	y[version=="NEW" & y=="proxy"] <- "proxyYES"
+	levels(y) <- list(
+		"not_running"="not_running",
+		"starting"="starting",
+		"first"="first",
+		"bridges"="bridges",
+		"bridgeSettings"="bridgeSettings",
+		"bridgeHelp"="bridgeHelp",
+		"proxy"="proxy",
+		"proxyYES"="proxyYES",
+		"summary"="summary",
+		"progress"=c("progress_bar", "inlineprogress"),
+		"error"="errorPanel"
+	)
+	droplevels(y)
+}
+
+filter_edges <- function(edges, participants) {
+	edges <- merge(edges, participants, by=c("seat", "runid"), all.y=T)
+	# Keep only the edges up to the first success.
+	edges <- edges[is.na(edges$time_to_success) | edges$time_from_start <= edges$time_to_success, ]
+	# Cut off the logs at our time limit.
+	edges <- trim_edges(edges, maxtime)
+	# Ignore "not_running" and "starting", so they just show up as blank.
+	edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
+	edges$src <- canonicalize_screens(edges$version, edges$src)
+	edges$dst <- canonicalize_screens(edges$version, edges$dst)
+	edges
 }
 
 # Assign DNFs a maximum time_to_success.
[…]

### 2016-04-18 experiment/processing/graphs.R

@@ -16,58 +16,10 @@ participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants
 pid_order <- rev(order(participants$env, participants$version, participants$time_to_success))
 participants$pid <- factor(participants$pid, levels=participants$pid[pid_order])
 
-edges <- read_edges()
-edges <- merge(edges, participants, by=c("seat", "runid"), all.y=T)
+edges <- filter_edges(read_edges(), participants)
 if (any(is.na(edges$pid))) {
   stop("found NAs in edges$pid")
 }
-
-# Remove edges that start after maxtime, and trim those that overlap it
-# so their start time plus their duration exactly reaches maxtime.
-trim_edges <- function(edges, maxtime) {
-  edges <- edges[edges$time_from_start <= maxtime, ]
-  edges$duration <- ifelse(edges$time_from_start + edges$duration > maxtime, maxtime - edges$time_from_start, edges$duration)
-  edges
-}
-
-edges <- edges[order(edges$sequence, edges$time_from_start), ]
-edges$duration <- ave(edges$time_from_start, edges$seat, edges$runid, FUN=function(z) {
-  c(z[2:length(z)], z[length(z)]) - z
-})
-# Keep only the edges up to the first success.
-edges <- edges[is.na(edges$time_to_success) | edges$time_from_start <= edges$time_to_success, ]
-# Cut off the logs at our time limit.
-edges <- trim_edges(edges, maxtime)
-# Ignore "not_running" and "starting", so they just show up as blank.
-edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
-
-# Canonicalize screen names from the OLD and NEW interfaces.
-canonicalize_screens <- function(version, x) {
-  y <- factor(x)
-  # In the NEW interface, the screen that's logged as "bridges"
-  # corresponds more closely to the "bridgeSettings" screen in the OLD
-  # interface than it does the OLD "bridges" screen. Similarly NEW
-  # "proxy" corresponds to OLD "proxyYES".
-  y[version=="NEW" & y=="bridges"] <- "bridgeSettings"
-  y[version=="NEW" & y=="proxy"] <- "proxyYES"
-  levels(y) <- list(
-    "not_running"="not_running",
-    "starting"="starting",
-    "first"="first",
-    "bridges"="bridges",
-    "bridgeSettings"="bridgeSettings",
[…]

### 2016-04-18 experiment/processing/info.R
info.R needs edges to be loaded here.

@@ -68,6 +68,8 @@ cat("****************************\n")
 # 3: create data frame "screen time per user" which has the time a user spent on each screen 
 # 4: (TODO) historgram plot function
 
+edges <- filter_edges(read_edges(), participants)
+
 # 1 
 active_edges <- edges[edges[,"src"] != "progress",] # "active time" is anytime that people are not on the progress screen.
 progress_edges <- edges[edges[,"src"]== "progress",]

### 2016-04-18 pets2017-paper/pets2017-paper.tex
discussion section and other tweaks.

@@
 \subsection{Methodology} 
-This section shows the details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.
+This section details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.
 
@@
 \subsection{Results} 
-Out of our 124 participants,  we have 116 valid data points.
-{\color {red} TODO} participants downloaded their own version of Tor, and {\color {red} TODO} participants did not sign the consent form.
-We have 58 valid participants who tested the new interface, and 58 who tested the old interface.
+Out of our 124 recruited participants, 116 provided valid data.
+We have 58 participants who tested the new interface, and 58 who tested the old interface.
 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
-Table~\ref{table:participant-summary} summarizes participants' success based on their interface version and environment combination.
-
-Talk about why we chose to assign the max time of 40 minutes to did not finish. 
-The impact of the version on time to completion is (significant,not significant). 
-The impact of the environment on time to completion is (significant,not significant).
-Figure~\ref{fig:time_to_success_clamped}
+Since our experiment ended after 40 minutes, we chose to assign the max time of 40 minutes to participants who did not succeed.
+Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
+
+\subsubsection{Rate of Success} 
+Distribution of success times. Figure~\ref{fig:time_to_success_clamped}
 
@@
 impact of version on success: not significant (W = 5.5, p-value = 0.8248)
-impact of version on time to success: not significant (W = 1399, p-value = 0.1175)
-
 impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
-impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
 
@@
 \label{table:participant-summary}
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics{time_to_success_clamped}
-\caption{
-Time to first success, by censorship environment and interface.
-The dots show the raw completion times,
-while the boxplots show the medians and interquartile ranges.
-The ``DNF'' figures at the right show the number of participants 
-who did not finish in the time allotted.
-Here, non-finishing participants are assigned the maximum time of 40:08
-for the purpose of computing the median.
-}
-\label{fig:time_to_success_clamped}
-\end{figure}
-
-Our participants had 40 minutes. In real life, people may give up a lot sooner. 
-Figure~\ref{fig:time_to_success_ecdf}. Table~\ref{table:less_time}.
-
-\begin{figure}
-\centering
-\includegraphics{time_to_success_ecdf}
-\caption{
-Cumulative success rates over time, by censorship environment and interface.
-We stopped participants after 40 minutes. Those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes. 
-}
-\label{fig:time_to_success_ecdf}
-\end{figure}
-
-\begin{table}
-\centering 
-	% Generated by info.R:
-	\begin{tabular}{l r r r r}
-	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
-	\noalign{\hrule}
-	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
-	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
-	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
-	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
-	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
-	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
-	\end{tabular}
-\caption{This Table shows what the success rate would have been
-at different cutoff times.
-For example, every E1-NEW participant finished within 90 seconds,
-but only 58\% of E1-OLD had finished by that time.
-After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
-After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
-\label{table:less_time}
 \end{table}
@@
 
+\subsubsection{Time to Success}
+
+impact of version on time to success: not significant (W = 1399, p-value = 0.1175)
+impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
+
+\begin{figure}
+\centering
+\includegraphics{time_to_success_clamped}
+\caption{
+Time to first success, by censorship environment and interface.
+The dots show the raw completion times,
+while the boxplots show the medians and interquartile ranges.
+The ``DNF'' figures at the right show the number of participants 
+who did not finish in the time allotted.
+Here, non-finishing participants are assigned the maximum time of 40:08
+for the purpose of computing the median.
+}
+\label{fig:time_to_success_clamped}
+\end{figure}
+
+Our participants had 40 minutes. In real life, people may give up a lot sooner. 
+Figure~\ref{fig:time_to_success_ecdf}. Table~\ref{table:less_time}.
+
+\begin{figure}
+\centering
+\includegraphics{time_to_success_ecdf}
+\caption{
+Cumulative success rates over time, by censorship environment and interface.
+We stopped participants after 40 minutes. Those who did not finish were assigned
+an arbitrarily high number greater than 40 minutes. 
+}
+\label{fig:time_to_success_ecdf}
+\end{figure}
+
+\begin{table}
+\centering 
+	% Generated by info.R:
+	\begin{tabular}{l r r r r}
+	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
+	\noalign{\hrule}
+	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
+	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
+	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
+	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
+	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
+	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
+	\end{tabular}
+\caption{This Table shows what the success rate would have been
+at different cutoff times.
+For example, every E1-NEW participant finished within 90 seconds,
+but only 58\% of E1-OLD had finished by that time.
+After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
+After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
+\label{table:less_time}
+\end{table}
+
+\subsubsection{Additional Information}
+
 \begin{figure*}
@@
 
-\section{Discussion}
-
 People spent a lot of time just waiting at the progress bar.
@@
 Talk about the notion of ``active time,'' which is just time not spent on the progress screen.
-The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
-The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
 
@@
 
+% statistical tests
+The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
+The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
+
+\subsection{Discussion} 
+This section talks about general trends in user behavior, common failure cases, and our recommendations for 
+improving the Tor configuration interface.
+
+\subsubsection{Observations}
+These are general observations made from our data set of participants, which may have biases.\\
+
+\begin{description}
+%connect vs configure
+\item {\bfseries Users try the easy path first.}
+81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
+
 % impacts of making the proxy page ``automated'' 
-New people still spent time configuring their proxy!
-
-% impacts of making bridge page collapsed 
-This is unclear.
+\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active time was spent configuring proxies.
+Participants with the new interface spent 31\% of their active time configuring proxies and participants in the old interface spent 63\%.
 
 % impacts of giving people advice on which transport to choose.
-10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
-5 people in the old interface chose meek as their second bridge (5/13, 38\%).
-
-% impacts of adding in a summary page 
-adding in a summary screen causes people to think about their configuration.
-summary to bridge settings: 13 \% (15/119)
-summary to progress: 86 \% (102/119)
-summary to summary: 1 \% (2/119)
-
-%FAILURES
-Elaborate on why people failed:  
-\begin{enumerate}
-\item only tried connecting directly (8/23)
-\item didn't know what to do after connecting directly and default bridge (6/23)
-\item Thought that they needed a proxy (6/23)
-\item used the bridges auto-responder incorrectly (3/23)
-\end{enumerate}
-
-These non-conservative changes may be helpful for a user, and would benefit from future research: \\
+\item {\bfseries Certain transports were chosen with high probability.}
+Of those who tried an obfs3 bridge and failed, 
+66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
+Flashproxy was also a popular choice.
+Many bridges were never chosen.
+
+%error messages
+\item {\bfseries There were (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
+Only one participant ever saw an error message.
+We are unable to state the efficacy of our attempts to make error messages more understandable and instructive for lack of data.
+
+% progress bar
+\item {\bfseries Users with the new interface waited longer.}
+Participants with the new interface the new interface spent more time waiting in the progress bar, proportionally and absolutely. 
+\end{description}
+
+It is unclear why users with the new interface chose to configure proxies after explicitly being told that they do not need one, if they chose meek bridges based on our advice, and why they chose to wait longer at the progress screen.
+
+\subsubsection{Reasons for Failure} 
+Failure is common.
+64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
+Although most participants eventually succeeded, 20\% (23 of 116) failed entirely.
+Reasons for failure were determined by a combination of log processing (i.e.
+how much time was spent on a particular screen) and video observation (i.e.
+observing what they searched for online while they were stuck).
+\\
 
 \begin{description}
-\item {\bfseries Tell people what to do.} Since a majority of the users will succeed if they click connect on the first screen, replacing the information about choices with explicit instructions to connect can lessen their cognitive load during the configuration process.
-\item{\bfseries Hide infrequently used options.} Hide the proxy screen and do not the option to configure a proxy unless it has been detected as necessary.
-\item{\bfseries Tailor for at-risk users.} Currently, the interface is for the average user.
-We guide at-risk users to the correct configuration, but suggesting that they try the default first.
-However, this isn't ideal.
+\item {\bfseries Only connected directly.
+(8/23)} These participants tried a direct connection.
+When that failed, they tried the same configuration, over and over, without trying other configurations, no matter how many times they failed.
+It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
+\item {\bfseries Didn't know what to do next.
+(6/23)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next.
+They often tried those configurations again or gave up.
+\item {\bfseries Thought that they needed a proxy (6/23)} After a couple failed attempts, these participants assumed that they needed a proxy.
+They spent the time trying to configure a proxy, usually without trying other bridges.
+\item {\bfseries Used the bridges auto-responder incorrectly (3/23)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button.
+However, they all failed to get a response.
+For details, see Appendix~\ref{failed-participants}.
 \end{description}
 
-Mention of people downloading their own Tor.
+Some participants chose to download their own version of Tor.
+We discarded these participants' data and do not count this behavior as a failures or success.
+While some downloaded their own version without trying the provided one on their desktop, others did so after feeling frustrated with the provided version.
+For unfortunate details of where participants downloaded tor when torproject.org was blocked, see Appendix~\ref{tor-downloads}.
+
+\subsubsection{Recommendations}
+Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\
+
+\begin{description}
+\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor.
+Automating the configuration process thereafter will have no increase in risk, bu can help a majority of users.
+64\% of participants who failed their first attempt.
+Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment , 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
+\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time on configuring a proxy.
+Only a small fraction of the Internet population requires a proxy to connect to the Internet.
+Hiding the proxy screen by default and only showing it after it has been detected as necessary can focus user efforts on configuring bridges.
+\item {\bfseries Be explicit about recommendations.} Being explicit about the order in which a user should choose bridges will result in higher rates of success and lessen cognitive load on the user.
+Most participants followed recommendations about which bridge to choose, and many did not know what to do after the recommended bridge failed.
+\item{\bfseries Set a timeout.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
+\item{\bfseries Have a user-tolerant auto-responder.} Having the auto-responder default respond with bridges or catching common errors (such as typing ``get bridges'' in the subject line) can help those who need custom bridges.
+\end{description}
+
+We believe that these changes have can greatly help future users connect to the Tor network.
 
@@
 Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor.
-\item {\bfseries Automate after failure.} After an unsuccessful connection attempt, the user has already indicated that they are connecting to Tor on the network.
-Assuming that the significant difference is between being logged trying to connect to Tor or not at all, we can automate the entire configuration process thereafter without increasing risk.
-This may save our users a lot of headache.
 \item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk.
@@
 
-{\bfseries Cause 1}: only tried connecting directly (8/23): 
+Only connected directly (8/23): 
 \begin{itemize}
@@
 
-{\bfseries Cause 2}: didn't know what to do after connecting directly and default bridge (6/23): 
+Didn't know what to do next (6/23): 
 \begin{itemize}
@@
 
-{\bfseries Cause 3}: Thought that they needed a proxy (6/23): 
+Thought that they needed a proxy (6/23): 
 \begin{itemize}
@@
 
-{\bfseries Cause 4}: used the bridges autoresponder incorrectly (3/23): 
+Used the bridges auto-responder incorrectly (3/23): 
 \begin{itemize}

### 2016-04-18 experiment/processing/attempts.R

@@ -17,6 +17,29 @@ attempts$bridge_default_selection[!attempts$bridge_yesno] <- NA
 # Show first successful attempts.
 # attempts[attempts$attempt_successful, c("env", "version", "runid", "attempt_successful", "time_from_start", "bridge_yesno", "bridge_radio_state", "bridge_default_selection", "bridge_custom_entry", "proxy_yesno", "proxy_type", "proxy_addr", "proxy_port")]
 
+# How many attempts were failures 
+sum(attempts$attempt_successful == "FALSE")/nrow(attempts)*100
+
+# How many FIRST attempts were direct. 
+first_attempts <- subset(attempts, subset = !duplicated(attempts[c("userid")]))
+first_attempts_new <-  first_attempts[first_attempts[,"version"]=="NEW",]
+first_attempts_old <- first_attempts[first_attempts[,"version"]=="OLD",]
+first_attempts_e1 <- first_attempts[first_attempts[,"env"]=="E1",]
+first_attempts_e2 <- first_attempts[first_attempts[,"env"]=="E2",]
+first_attempts_e3 <- first_attempts[first_attempts[,"env"]=="E3",]
+
+sum(first_attempts$bridge_radio_state == "none")#/nrow(first_attempts)*100
+sum(first_attempts_new$bridge_radio_state == "none")#/nrow(first_attempts_new)*100
+sum(first_attempts_old$bridge_radio_state == "none")#/nrow(first_attempts_old)*100
+
+# How many FIRST attempts were failures. 
+sum(first_attempts$attempt_successful == "FALSE")/nrow(first_attempts)*100
+sum(first_attempts_new$attempt_successful == "FALSE")/nrow(first_attempts_new)*100
+sum(first_attempts_old$attempt_successful == "FALSE")/nrow(first_attempts_old)*100
+sum(first_attempts_e1$attempt_successful == "FALSE")/nrow(first_attempts_e1)*100
+sum(first_attempts_e2$attempt_successful == "FALSE")/nrow(first_attempts_e2)*100
+sum(first_attempts_e3$attempt_successful == "FALSE")/nrow(first_attempts_e3)*100
+
 successful.attempts <- attempts[attempts$attempt_successful, ]
 successful.attempts$label <- sprintf("%s, %s",
 	# bridge label

### 2016-04-18 experiment/processing/info.R

@@ -202,6 +202,7 @@ sum(bridge_edges[bridge_edges[,"version"]=="OLD",]$duration)/sum(active_edges[ac
 # 1: % TOTAL time on SUMMARY screen, across users. (total, e1, e2, e3,new, old)
 # 2: % ACTIVE time on SUMMARY screen, across users. (total, e1, e2, e3,new, old)
 # 3: distribution of destinations from summary screen 
+# 4: if old interface users clicked back from proxyYES/proxy.
 
 # 1
 sum(summary_edges$duration)/sum(edges$duration)*100
@@ -220,11 +221,15 @@ sum(summary_edges[summary_edges[,"version"]=="NEW",]$duration)/sum(active_edges[
 sum(summary_edges[summary_edges[,"version"]=="OLD",]$duration)/sum(active_edges[active_edges[,"version"]=="OLD",]$duration)*100
 
 # 3
-summary_edges <- summary_edges[summary_edges$dst != "summary", ]
 sum(summary_edges$dst == "bridgeSettings")/nrow(summary_edges)*100
 sum(summary_edges$dst == "progress")/nrow(summary_edges)*100
 barplot(height=table(summary_edges$dst))
 
+#4 
+proxy_edges_transitions <- proxy_edges[!proxy_edges[,"dst"] %in% c("proxy","proxyYES"),]
+proxy_edges_transitions <- proxy_edges_transitions[proxy_edges_transitions[,"version"]=="OLD",]
+sum(proxy_edges_transitions$dst == "progress")/nrow(proxy_edges_transitions)*100
+sum(proxy_edges_transitions$dst != "progress")/nrow(proxy_edges_transitions)*100
 
 cat("\n\n\n\n\n\n")
 cat("*********************\n")

### 2016-04-18 experiment/processing/info.R
Put labels on screen stat output and format percentages.

@@ -97,41 +97,42 @@ screen_time_per_user <- merge(screen_time_per_user, bridge_time_per_user, by=c(1
 screen_time_per_user <- merge(screen_time_per_user, summary_time_per_user, by=c(1), all=T)
 screen_time_per_user[is.na(screen_time_per_user)] <- 0
 
-subreport <- function(selected_edges, denom_edges, f) {
-	print(sum(selected_edges[f(selected_edges),]$duration)/sum(denom_edges[f(denom_edges),]$duration)*100)
+subreport <- function(label, sublabel, selected_edges, denom_edges, f) {
+	cat(sprintf("%s\t%s\t%s\n", sublabel, label,
+		format_percent(sum(selected_edges[f(selected_edges),]$duration)/sum(denom_edges[f(denom_edges),]$duration))))
 }
 
-report_total <- function(selected_edges) {
-	subreport_total <- function(f) {
-		subreport(selected_edges, edges, f)
+report_total <- function(label, selected_edges) {
+	subreport_total <- function(sublabel, f) {
+		subreport(label, sublabel, selected_edges, edges, f)
 	}
 
 	# % TOTAL time on screen, across users. (total, e1, e2, e3,new, old)
-	subreport_total(function(z) { T })
-	subreport_total(function(z) { z$env=="E1" })
-	subreport_total(function(z) { z$env=="E2" })
-	subreport_total(function(z) { z$env=="E3" })
-	subreport_total(function(z) { z$version=="NEW" })
-	subreport_total(function(z) { z$version=="OLD" })
+	subreport_total("TOTAL\tAll", function(z) { T })
+	subreport_total("TOTAL\tE1", function(z) { z$env=="E1" })
+	subreport_total("TOTAL\tE2", function(z) { z$env=="E2" })
+	subreport_total("TOTAL\tE3", function(z) { z$env=="E3" })
+	subreport_total("TOTAL\tNEW", function(z) { z$version=="NEW" })
+	subreport_total("TOTAL\tOLD", function(z) { z$version=="OLD" })
 }
 
-report_active <- function(selected_edges) {
-	subreport_active <- function(f) {
-		subreport(selected_edges, active_edges, f)
+report_active <- function(label, selected_edges) {
+	subreport_active <- function(sublabel, f) {
+		subreport(label, sublabel, selected_edges, active_edges, f)
 	}
 
[…]

### 2016-04-18 pets2017-paper/pets2017-paper.tex
Remove a layer of hierarchy in sec:quantitative.

@@
 
-\subsection{Methodology} 
-This section details of our quantitative user study, such as the censorship environments we placed our users in, how we recruited our 124 participants, and the procedure for the experiment.
-
-\subsubsection{Setup}
+\subsection{Setup}
 We simulated the same three censorship environments from 
@@
 
-\subsubsection{Recruitment}
+\subsection{Recruitment}
 We recruited about 20 users for each censorship environment
@@
 
-\subsubsection{Procedure}
+\subsection{Procedure}
 The one-hour, multi-participant procedure begins when all participants are sitting at their
@@
 
-\subsubsection{Changes During the Experiment}
+\subsection{Changes During the Experiment}
 

### 2016-04-18 pets2017-paper/pets2017-paper.tex
only keep total time table, commenting out active time table.
delete changes during experiment subsection

@@
 
-\subsection{Changes During the Experiment}
-
-% $ grep 'default_bridge\.' tor-browser_en-US/Browser/TorBrowser/Data/Browser/profile.default/preferences/extension-overrides.js | awk -F. '{print $4}' | sort | uniq -c
-%       5 flashproxy
-%       6 fte
-%       2 fte-ipv6
-%       1 meek-amazon
-%       1 meek-azure
-%       1 meek-google
-%       5 obfs3
-%       3 obfs4
-%       2 scramblesuit
-% The 5 flashproxy lines are effectively 1.
-Tor Browser 5.0.3 came configured with default bridges:
-1 flashproxy;
-8 fte;
-3 meek;
-5 obfs3;
-3 obfs4;
-and 2 scramblesuit.
-In the time since 5.0.3 was released and our later experiment,
-two of the obfs4 bridges and one of the scramblesuit bridges stopped running.
-% These are the bridges that stopped running. schanenlied is known and intentional.
-% 188.226.213.208 in known and intentional: https://bugs.torproject.org/17318. Maybe
-% it was not even running at the time of 5.0.3.
-% mercurius4 is probably not running by accident.
-% schanenlied:
-% obfs4 178.209.52.110:443 67E72FF33D7D41BF11C569646A0A7B4B188340DF cert=Z+cv8z19Qb8RxWlkagp7SxiDQN++b7D2Tntowhf+j4D15/kLuj3EoSSGvuREGPc3h60Ofw iat-mode=0
-% mercurius4:
-% obfs4 104.131.108.182:56880 EF577C30B9F788B0E1801CF7E433B3B77792B77A cert=0SFhfDQrKjUJP8Qq6wrwSICEPf3Vl/nJRsYxWbg3QRoSqhl2EB78MPS2lQxbXY4EW1wwXA iat-mode=0
-% (nickname unknown):
-% scramblesuit 188.226.213.208:54278 AA5A86C1490296EF4FACA946CC5A182FCD1C5B1E password=MD2VRP7WXAMSG7MKIGMHI4CB4BMSNO7T
-This left enough bridges that participants in the later experiment would be able to connect
-under the same circumstances as those in the earlier experiment.
-We did not modify the set of bridges between the experiments,
-with one exception.
-One of the meek bridges changed its bridge identity fingerprint;
-Tor clients check the identity fingerprint and refuse to connect
-if it does not match.
-Therefore we patched the correct fingerprint in the later experiment.
-
 \subsection{Results} 
@@
 
-\begin{table}
-\centering
-	\begin{tabular}{c r r r r }
-	 & First & Proxy & Bridge & Summary \\
-	\noalign{\hrule}
-	All & 22\% & 57\% & 19\% & 2\% \\
-	NEW & 40\% & 31\% & 19\% & 9\% \\ 
-	OLD & 18\% & 63\% & 19\% & 0\% \\
-	E1 & 45\% & 22\% & 32\% & 1\% \\
-	E2 & 29\% & 48\% & 20\% & 2\% \\
-	E3 & 19\% & 61\% & 18\% & 2\% \\
-	\end{tabular}
-\caption{active time} 
-\label{table:active_time}
-\end{table}
+%\begin{table}
+%\centering
+%	\begin{tabular}{c r r r r }
+%	 & First & Proxy & Bridge & Summary \\
+%	\noalign{\hrule}
+%	All & 22\% & 57\% & 19\% & 2\% \\
+%	NEW & 40\% & 31\% & 19\% & 9\% \\ 
+%	OLD & 18\% & 63\% & 19\% & 0\% \\
+%	E1 & 45\% & 22\% & 32\% & 1\% \\
+%	E2 & 29\% & 48\% & 20\% & 2\% \\
+%	E3 & 19\% & 61\% & 18\% & 2\% \\
+%	\end{tabular}
+%\caption{active time} 
+%\label{table:active_time}
+%\end{table}
 

### 2016-04-18 pets2017-paper/pets2017-paper.tex
results:additional information subsection

@@
 
-\begin{table}
+\begin{table}[t]
 \centering
@@
 
-\subsubsection{Additional Information}
-
-\begin{figure*}
-\centering
-\includegraphics{all-participant-edges}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The narrow black lines show the times when the configuration interface
-was not running; i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes.
-}
-\label{fig:all-participant-edges}
-\end{figure*}
-
-People spent a lot of time just waiting at the progress bar.
-
-Talk about the notion of ``active time,'' which is just time not spent on the progress screen.
+\subsubsection{Additional information} 
+While we did not find a statistically significant difference between the overall time to success between the old and new versions of the interface, the time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
+Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.
 
@@
 
-%\begin{table}
-%\centering
-%	\begin{tabular}{c r r r r }
-%	 & First & Proxy & Bridge & Summary \\
-%	\noalign{\hrule}
-%	All & 22\% & 57\% & 19\% & 2\% \\
-%	NEW & 40\% & 31\% & 19\% & 9\% \\ 
-%	OLD & 18\% & 63\% & 19\% & 0\% \\
-%	E1 & 45\% & 22\% & 32\% & 1\% \\
-%	E2 & 29\% & 48\% & 20\% & 2\% \\
-%	E3 & 19\% & 61\% & 18\% & 2\% \\
-%	\end{tabular}
-%\caption{active time} 
-%\label{table:active_time}
-%\end{table}
-
-% statistical tests
-The impact of the version on active time is significant (W = 997, p-value = 0.0001571)
-The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
+We define the time participants not on the progress screen as the amount of time they actively spent configuring their connection.
+This is a simplified notion the time participants spent configuring, since some participants waited at the progress screen without doing anything while others searched for help on the web while they were waiting.
+However, participants with the new and old interface were equally likely to exhibit this behavior.
+Participants with the new interface showed a statistically significant reduction in the overall time configuring the interface (Mann-Whitney W = 997, p-value = 0.0001571).
+%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
+
+We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}.
+Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
+The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
+
+\begin{figure*}
+\centering
+\includegraphics{all-participant-edges}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The narrow black lines show the times when the configuration interface
+was not running; i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes.
+}
+\label{fig:all-participant-edges}
+\end{figure*}
 

### 2016-04-18 experiment/processing/info.R
calculate the effect size for statistical significance of interface causing a reduction in active time

@@ -1,4 +1,5 @@
-source("common.R")
+library(coin)
+csource("common.R")
 
 participants <- read_participants()
 
@@ -227,6 +228,8 @@ wilcox.test(time_to_success ~ version, data=clamp_time_to_success(participants, 
 
 cat("impact of version on active time \n")
 wilcox.test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user)
+wilcox_test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user)
+
 
 cat("\n\n\n\n")
 cat("impact of environment on success rates\n")

### 2016-04-18 pets2017-paper/pets2017-paper.tex
hastily done results section

@@
 
-\subsubsection{Rate of Success} 
-Distribution of success times. Figure~\ref{fig:time_to_success_clamped}
-
-%stats
-impact of version on success: not significant (W = 5.5, p-value = 0.8248)
-impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
-
-\begin{table}[t]
+\begin{table}
 \centering
@@
 
-\begin{table}[t]
+\subsubsection{Rate of Success} 
+5 more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network.
+Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
+However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made.
+% impact of version on success: not significant (Mann-Whitney W = 5.5, p-value = 0.8248)
+%impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
+
+Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful bootstrap in each environment and interface combination.
+Note that only four of the default bridges were used to connect successfully for the first time.
+Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options.
+Participants who were in environments in that the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
+Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek-bridge.
+
+\begin{table}
 \centering
@@
 \subsubsection{Time to Success} 
-
-impact of version on time to success: not significant (W = 1399, p-value = 0.1175)
-impact of env on time to success : significant ( Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
+Although the median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}), this difference is not statistically significant.
+The level of censorship had a significant impact on the time to success.
+The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16).
+The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
+%impact of version on time to success: not significant (W = 1569, p-value = 0.07796)
+%impact of env on time to success : significant (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
 
@@
 
-Our participants had 40 minutes. In real life, people may give up a lot sooner. 
-Figure~\ref{fig:time_to_success_ecdf}. Table~\ref{table:less_time}.
+In our experiment, participants had 40 minutes to circumvent censorship.
+Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
+Participants were less and less likely to succeed as time went on.
+Users in the wild will likely not be motivated to configure their connection for 40 minutes.
+Table~\ref{table:less_time} shows that if users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect.
+Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments will be unable to connect.
+Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment.
+We propose ideas on how to achieve this in section~\ref{recommendations}.
 
@@
 Cumulative success rates over time, by censorship environment and interface.
-We stopped participants after 40 minutes. Those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes. 
+We stopped participants after 40 minutes. Here, those who did not finish were assigned
+an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
 }
@@
 \subsubsection{Additional information} 
+We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}.
+Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
+The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
+
+\begin{figure*}
+\centering
+\includegraphics{all-participant-edges}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The narrow black lines show the times when the configuration interface
+was not running; i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes.
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
 While we did not find a statistically significant difference between the overall time to success between the old and new versions of the interface, the time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
 Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.
+Participants using the new interface and old interface waited spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively.
+We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen which keeps the users waiting indefinitely, which were present in both versions of the interface.
 
@@
 
-We define the time participants not on the progress screen as the amount of time they actively spent configuring their connection.
-This is a simplified notion the time participants spent configuring, since some participants waited at the progress screen without doing anything while others searched for help on the web while they were waiting.
-However, participants with the new and old interface were equally likely to exhibit this behavior.
-Participants with the new interface showed a statistically significant reduction in the overall time configuring the interface (Mann-Whitney W = 997, p-value = 0.0001571).
+Perhaps a more meaningful measurement of time is the amount of times participants actively spent configuring their connection.
+We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen.
+This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting.
+However, this behavior was equally likely in the new and old interface conditions.
+
+The new interface results a statistically significant reduction in the overall active configuration time (Mann-Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user.
+We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time.
 %The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
-
-We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}.
-Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
-The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
-
-\begin{figure*}
-\centering
-\includegraphics{all-participant-edges}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The narrow black lines show the times when the configuration interface
-was not running; i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes.
-}
-\label{fig:all-participant-edges}
-\end{figure*}
 
@@
 % impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active time was spent configuring proxies.
+\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active configuration time was spent on the proxy screens.
 Participants with the new interface spent 31\% of their active time configuring proxies and participants in the old interface spent 63\%.
@@
 % progress bar
-\item {\bfseries Users with the new interface waited longer.}
-Participants with the new interface the new interface spent more time waiting in the progress bar, proportionally and absolutely. 
+\item {\bfseries People waited a long, long time at the progress bar.}
+From observing videos, participants genuinely wait, dutifully following the directions.   
 \end{description}
@@
 \subsubsection{Recommendations}
+\label{recommendations}
 Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\

### 2016-04-18 pets2017-paper/pets2017-paper.tex
add conclusion sections (and mess around with formatting)

@@
 
-\begin{figure*}[t]
+Tor Browser 5.0.3.
+configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+We rate the severity of the issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
+
+\begin{itemize}
+\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
+\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
+\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
+\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
+ \end{itemize}
+
+ \begin{figure*}[h]
 	\centering
@@
 
-\begin{figure*}[t]
+\begin{figure*}[h]
 	\centering
@@
 \end{figure*}
-
-Tor Browser 5.0.3.
-configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-We rate the severity of the issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
-
-\begin{itemize}
-\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
-\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
-\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
- \end{itemize}
 
@@
 
-\section {Acknowledgments}
-{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
-{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
+%\section {Acknowledgments}
+%{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
+%{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
 
 \section{Conclusion} 
-{\color {red} I am a fan of not having long, rambling conclusions. I leave
-that for the discussion section. This section is more of a courtesy to the 
-people who read the abstract, look at the figures, and then read the 
-conclusion. Think of something to tell those people here. Something along
-the lines of a tl;dr summary of the paper.}
+We conducted a series of experiments to improve the Tor launcher configuration interface, which helps users circumvent censorship using Tor Browser.
+The qualitative user study interviews a screened 16 participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common struggles, such as difficulty in answering technical questions, feeling unqualified to make technical choices, and not receiving feedback in the event of a failed configuration.
+This feedback is used to guide the redesign of the configuration interface.
+
+We test the impact of our changes on 124 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
+We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.
 

### 2016-04-18 pets2017-paper/pets2017-paper.tex
abstract and some intro hacking

@@
 {Tor has grown beyond its original purpose as an anonymity tool and has 
-since become an important censorship circumvention tool. It is now listed
-as one of the ways that normal people use Tor.
-We specifically examine its usability as a censorship circumvention tool,
-an essential facet for adoption and use. We focus our analysis on the connection 
-configuration interface of Tor Browser. We find that the Tor Browser 5.0.3. connection
-configuration interface has a success rate of {\color {red} TODO}\% with the 
-successful users having an average completion time of {\color {red} TODO} minutes. 
-In this paper, we explore common challenges users faced during the configuration
-process and redesign the interface to improve success rate to {\color {red} TODO}\% 
-and average completion time to {\color {red} TODO} minutes.}
+since become an important censorship circumvention tool. We conducted a series of 
+experiments to improve the Tor launcher configuration interface, which configures network components
+that circumvent censorship. A 16-participant experiment and interview
+identifies common user struggles while circumventing censorship.
+We use as feedback to redesign the configuration interface.
+We test the impact of our
+changes on 124 participants to find that our changes results in a significant reduction 
+in the spent configuring a connection, while maintaining the same rate of success. We
+conclude with recommendations for changes to the current configuration interface and discuss
+alternative configuration processes with different balances of risk, automation, and user input.}
 \end{abstract}
@@
 Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
-using it as one, since Tor's role as a proxy to anonymize
-people also worked to circumvent censorship. Now, circumventing censorship is a
-common use case for Tor, and current censorship circumvention methods are
-incorporated into Tor, making it a viable censorship circumvention tool even in the face
-of adversaries. In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}. 
+using it as one, since Tor's anonymizing functionality also circumvented censorship.
+In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}.
+Today, Tor's network of unlisted relays and various methods of obfuscation making it a viable censorship circumvention tool even in the face of nation-state level adversaries.
+
 To our knowledge, this is the first user study investigating the usability of Tor as a 
 censorship circumvention tool.
-
-We believe that this is a great opportunity for user research.
-We have the opportunity to help users circumvent censorship more easily and provide them with extra security features, such as anonymity.
+We believe that this is a great opportunity for user research, both for investigating a case study of how users circumvent censorship, but also to help Tor users circumvent censorship more easily and provide them with extra security features, such as anonymity.
 Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users~\cite{dingledine2006anonymity}.
@@
 User metrics, such as success rate and time to completion, measured how well the interfaces served their purpose.
-
-Currently, {\color {red} TODO}\% of users fail and with the current interface for reasons {\color {red} TODO}, {\color {red} TODO}, and {\color {red} TODO}.
-Of those that do succeed, the average time to completion is {\color {red} TODO}.
-This can lead to a bad user experience, users quitting Tor, or causing high-risk users to make mistakes.
-With the new design, only {\color {red} TODO}\% of users fail to configure successfully and the average time to completion is {\color {red} TODO}.
-Tor has already implemented some of these changes.
 
@@
 and redesigned interface.
-
-An exploration of the problems with the existing Tor Browser 
-configuration interface through user observation and interviews can be 
-found in Section~{\color{red} TODO}. A heuristic evaluation of the existing interface and new interface is in Section~{\color{red} TODO}. We empirically show 
-that the redesigned interface improves completion rate, reduces time to completion, 
-and provides a safe path for at-risk users in Section~{\color{red} TODO}.
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
finished up introduction

@@
 censorship circumvention tool.
-We believe that this is a great opportunity for user research, both for investigating a case study of how users circumvent censorship, but also to help Tor users circumvent censorship more easily and provide them with extra security features, such as anonymity.
-Not only does improving the interface help the user trying to circumvent censorship, it helps other users who use Tor as an anonymity system by increasing the number of overall users~\cite{dingledine2006anonymity}.
-
-This study aims to understand of what is confusing about the configuration process and what find changes make the process easier.
-Our study consists of three stages.
-User interactions with the current interface in various censorship environments generated the problems we address in the study.
-User feedback and observations of users steered the design process for an improved configuration interface.
-User metrics, such as success rate and time to completion, measured how well the interfaces served their purpose.
-
-The qualitative user study gives insight into possible issues with
-the deployed interface. 
-The redesign process was guided by the participant observations, 
-heuristic evaluations and empirical goals. 
-Quantitative user studies provide empirical evaluations of the deployed
-and redesigned interface.
+We believe that this is a great opportunity for user research, both for investigating a case study of investigating the usability of a censorship circumvention tool, and also to help current Tor users censorship circumvention more easily.
+Not only will this allow for easier censorship circumvention, users who use tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity.
+Additionally, increasing the adoption of Tor as a censorship circumvention tool benefits other users who use Tor as an anonymity system by increasing the number of overall users on the Tor network~\cite{dingledine2006anonymity}.
+
+Our study consists of two user studies set in three simulated censorship environments 
+of varying levels of difficulty to circumvent. The mild, intermediate, and comprehensive 
+environments required participants to connect, configure manually with default settings
+and recommendations, and to configure manually without using defaults or recommendations. 
+In both experiments, participants are informed that they are being censored, and that their 
+goal is to reach a censored website by circumventing the censorship environment through
+configuring Tor Browser.
+
+The first user study is a small-scale, one-on-one experiment that collected 
+behavioral patterns and failure cases with the interface through user observations
+and interviews(Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
+that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{quantitative}).
+
+Our study finds that that users had difficulty in answering technical questions, feel unqualified to make technical choices, and cannot tell why their connection is failing.
+We made ten design changes that aimed to provide additional feedback, unburden the user, and build a user's understanding of the process.
+Our changes decreased the time participants spent configuring their connections, with no decrease in success rates.
+We conclude with a recommendation of changes that we believe will increase the usability of Tor Browser's configuration interface.
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
formatting and small tweaks

@@
 \section{Redesigning the Configuration Interface}
-
+\label{redesign} 
+ \begin{figure*}[t]
+	\centering
+		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
+		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
+		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
+		be configured and directs to the bridge configuration screen (B2). 
+		The ``NEW'' interface gives users advice on configuring bridges
+		while giving the option of not configuring a bridge, on one screen (B).} 
+\end{figure*}
+
+\begin{figure*}[t]
+	\centering
+		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
+		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
+		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
+		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
+		and informs the user whether a proxy is required, and if so, what those settings are (P).}
+\end{figure*}
+
+Tor Browser 5.0.3.
+configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+We rate the severity of the issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
+
+\begin{itemize}
+\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
+\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
+\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
+\item {\bfseries Cosmetic Problem}: The interface can be simplified visually. 
+ \end{itemize}
+
+ \label{redesign}
 \begin{figure*}[t]
@@
 \label{fig:flow}
-\end{figure*}
-
-Tor Browser 5.0.3.
-configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-We rate the severity of the issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
-
-\begin{itemize}
-\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
-\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
-\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
- \end{itemize}
-
- \begin{figure*}[h]
-	\centering
-		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
-		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
-		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
-		be configured and directs to the bridge configuration screen (B2). 
-		The ``NEW'' interface gives users advice on configuring bridges
-		while giving the option of not configuring a bridge, on one screen (B).} 
-\end{figure*}
-
-\begin{figure*}[h]
-	\centering
-		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
-		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
-		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
-		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
-		and informs the user whether a proxy is required, and if so, what those settings are (P).}
 \end{figure*}
@@
 Most participants followed recommendations about which bridge to choose, and many did not know what to do after the recommended bridge failed.
-\item{\bfseries Set a timeout.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration. 
+\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration.
 \item{\bfseries Have a user-tolerant auto-responder.} Having the auto-responder default respond with bridges or catching common errors (such as typing ``get bridges'' in the subject line) can help those who need custom bridges.
@@
 We believe that these changes have can greatly help future users connect to the Tor network.
+We also encourage best practices, such as providing a summary screen to let the user know the configuration settings before connecting, having a checklist progress bar to give users feedback on what network component needs configuring, and rewriting screen text and error messages to be more instructive and understandable.
 
@@
 \begin{itemize}
-\item E3-NEW-X23-20160328-155924 (Figure \ref{autoresponder1})
-\item E3-OLD-X12-20160325-140813 (Figure \ref{autoresponder2})
-\item E3-OLD-X24-20160328-133857 (Figure \ref{autoresponder3})
+\item E3-NEW-X23-20160328-155924 (Figure~\ref{autoresponder1})
+\item E3-OLD-X12-20160325-140813 (Figure~\ref{autoresponder2})
+\item E3-OLD-X24-20160328-133857 (Figure~\ref{autoresponder3})
 \end{itemize}
@@
 \begin{figure}[h]
-\label{autoresponder1}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
@@
 The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
+\label{autoresponder1}
 \end{figure}
@@
 \begin{figure}[h]
-\label{autoresponder2}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
@@
 Since the helpdesk address is not an auto-responder, there was no reply.}
+\label{autoresponder2}
 \end{figure}
@@
 \begin{figure}[h]
-\label{autoresponder3}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
@@
 Since this request was incorrectly formatted, there was no reply.}
+\label{autoresponder3}
 \end{figure}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
This macro provides its own environment now.
Screen recording.

@@
 
-% Format a participant quotation. It should be inside a quotation environment.
+% Format a participant quotation.
 \newcommand{\pquote}[2]{
@@
 The one-hour, single-participant procedure begins when a participant enters a small 
-room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, 
-and VLC (for screen recording). A participant is firstly informed of 
+room with a single computer, which is equipped with Tor, Chrome, Firefox, and Internet Explorer.
+A participant is firstly informed of 
 the risks of the study and consenting to data collection. If they consent, the 
@@
 After instructions, researchers stepped out of the room so that there was no interaction
-between the participant and researcher for the rest of the session. Participants' screens 
-were recorded and streamed to another room, where the researchers were able to 
-observe how a participant configured their browser. Participants had an 
+between the participant and researcher for the rest of the session.
+Researchers watched a live video of each participant's screen from another room
+and saved the videos for review; the resulting videos and summaries
+are available from our project page.
+Participants had an 
 average of 45 minutes to complete their worksheet.

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Use math mode for mu and sigma.
Maybe this should be \mu and \sigma.
Fix Study 1 technical expertise summary.
I got the counts from sessions/pre/participant-summaries.txt:
	has never heard of Tor or used it: P2, P3, P4, P12, P13, P14, P15, P16
	heard of tor but has not used it:  P1, P6, P7, P9, P13
	used tor before: P8, P10, P11, P5
The sentence used to say,
	5 had previously heard of Tor but not used it, while and 5 had used Tor previously.

@@
 
-Out of our 16 participants, ages ranged from 20 to 62
-(mu= 24.5, sigma = 12.6). 53.3\% were male. 
+Out of our 16 participants, ages ranged from 20 to~62
+($\mbox{mu} = 24.5$, $\mbox{sigma} = 12.6$). 53.3\% were male. 
 93.3\% of our participants had at least
-a college education. 5 had previously heard of Tor but not used it, while 
-and 5 had used Tor previously.
+a college education.
+4 participants had used Tor before,
+5 had heard of Tor but not used it,
+and the remaining 8 had never heard of Tor nor used it.
 
@@
 recruited from Craigslist. Ages ranged from 18 to 68
-(mu = 28.9, sigma = 12). 56.8\% were male and 
+($\mbox{mu} = 28.9$, $\mbox{sigma} = 12$). 56.8\% were male and 
 84.8\% of our participants had at least a college education.

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Formatting.

@@
 Other changes improve empirical goals from Section~\ref{sec:goals}: task completion, time to completion, and safe for high-risk users.
-5-6 improve task completion, 7-8 reduce time to completion, and 9-10 builds users' mental models of censorship circumvention and network components involved.
+Items 5 and~6 improve task completion; 7 and~8 reduce time to completion; and 9 and~10 build users' mental models of censorship circumvention and the network components involved.
 Users' full control of the configuration process remains preserved.\\

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Mention simulated censorship in abstract.

@@
 {Tor has grown beyond its original purpose as an anonymity tool and has 
-since become an important censorship circumvention tool. We conducted a series of 
-experiments to improve the Tor launcher configuration interface, which configures network components
-that circumvent censorship. A 16-participant experiment and interview
+since become an important censorship circumvention tool.
+We conducted a series of
+experiments to evaluate and improve the configuration interface of Tor Browser,
+placing users in a simulated censorship environment and measuring their ability to circumvent it.
+A 16-participant experiment and interview
 identifies common user struggles while circumventing censorship.

### 2016-04-19 experiment/processing/graphs.R
Don't need to label this axis.

@@ -128,7 +128,7 @@ p <- p + scale_color_manual("Current screen", values=state.palette, labels=c(
 	"progress"="progress (Pr)",
 	"error"="error"
 ))
-p <- p + labs(title=NULL, x="Participants", y="Minutes elapsed")
+p <- p + labs(title=NULL, x=NULL, y="Minutes elapsed")
 p <- common_theme(p)
 p <- p + theme(panel.grid.minor.x=element_blank())
 p <- p + theme(panel.grid.major.y=element_blank())

### 2016-04-19 pets2017-paper/pets2017-paper.tex
It was 3.5, not 4.0, when Tor Launcher was introduced.
Edits to intro and related work.

@@
 We believe that this is a great opportunity for user research, both for investigating a case study of investigating the usability of a censorship circumvention tool, and also to help current Tor users censorship circumvention more easily.
-Not only will this allow for easier censorship circumvention, users who use tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity.
+Not only will this allow for easier censorship circumvention, users who use Tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity.
 Additionally, increasing the adoption of Tor as a censorship circumvention tool benefits other users who use Tor as an anonymity system by increasing the number of overall users on the Tor network~\cite{dingledine2006anonymity}.
 
-Our study consists of two user studies set in three simulated censorship environments 
-of varying levels of difficulty to circumvent. The mild, intermediate, and comprehensive 
-environments required participants to connect, configure manually with default settings
-and recommendations, and to configure manually without using defaults or recommendations. 
-In both experiments, participants are informed that they are being censored, and that their 
-goal is to reach a censored website by circumventing the censorship environment through
-configuring Tor Browser.
+Our study consists of two user studies set in three simulated environments
+of mild to severe censorship.
+Study participants had to circumvent censorship and access a blocked website
+by configuring Tor Browser correctly.
+The various levels of censorship required various levels of manual configuration,
+ranging from almost none to detailed and specific settings.
 
@@
 behavioral patterns and failure cases with the interface through user observations
-and interviews(Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
-that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{quantitative}).
+and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
+that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).
 
@@
 \section{Related Work} 
-There have been three published user studies on Tor. Clark et. al examined various deployment
+There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
 options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
-were satisfactory from a usability perspective~\cite{clark2007usability}. Fabian et. al show that Tor's added
+were satisfactory from a usability perspective. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
 latency~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests more often, and prevents user adoption~\cite{fabian2010privately}. 
-Norcie et. al found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties~\cite{norcie2012eliminating}.
+to be frustrated, cancel requests more often, and prevents user adoption. 
+Norcie et~al.~\cite{norcie2012eliminating} found found that 
+64\% of users are unable to continue with installation or browsing at least once due to difficulties.
 
 There have been been no published usability evaluations of
-Tor Browser since the 4.0 series, which introduced radical UI changes. 
-The most recent usability effort is an unpublished pilot study  by Lee and Fifield~\cite {uxsprint} 
-that tests the download, install, and  user interface of Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets}. Changes made are reflected in series 5.1 and later.
-
-Previous user studies have not focused on specific features in isolation, while we choose to focus our study on 
-the configuration interface. The configuration interface guides users through setting up network components required to circumvent censorship. 
-This study examines that interface, and effectively, the usability of Tor as a censorship circumvention tool.
+Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
+The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
+that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
+some of which influenced changes in Tor Browser version~5.1 and later.
+
+Previous user studies have been on the whole browsing experience,
+without focusing on specific features in isolation.
+We choose to focus our study on 
+the browser's configuration interface, which guides users through setting up network components required to circumvent censorship. 
+This study examines that interface with a focus on circumvention,
+though we believe that this research and the changes we recommend
+can be beneficial for non-circumventing users as well.
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.

@@
 There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
-options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and Foxyproxy, and found that none of them 
+options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none of them 
 were satisfactory from a usability perspective. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
@@
 Participants in E3, the most advanced censorship environment, were required to select a meek bridge (not the default) or to configure a custom bridge.
-After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a mis-configured bridge, the pluggable transport names only confused participants and caused odd behaviors.
+After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a misconfigured bridge, the pluggable transport names only confused participants and caused odd behaviors.
 Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e.

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Dashes.

@@
 However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made.
-% impact of version on success: not significant (Mann-Whitney W = 5.5, p-value = 0.8248)
-%impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
+% impact of version on success: not significant (Mann--Whitney W = 5.5, p-value = 0.8248)
+%impact of env on success: not significant (Kruskal--Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
 
@@
 The level of censorship had a significant impact on the time to success.
-The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16).
+The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16).
 The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
 %impact of version on time to success: not significant (W = 1569, p-value = 0.07796)
-%impact of env on time to success : significant (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
+%impact of env on time to success : significant (Kruskal--Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
 
@@
 
-The new interface results a statistically significant reduction in the overall active configuration time (Mann-Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user.
+The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user.
 We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time.
-%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
+%The impact of the environment on active time is significant (Kruskal--Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
 

### 2016-04-19 experiment/processing/common.R
fix report to include not_running edges and use dst

@@ -71,9 +71,9 @@ filter_edges <- function(edges, participants) {
 	# Cut off the logs at our time limit.
 	edges <- trim_edges(edges, maxtime)
 	# Ignore "not_running" and "starting", so they just show up as blank.
-	edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
-	edges$src <- canonicalize_screens(edges$version, edges$src)
-	edges$dst <- canonicalize_screens(edges$version, edges$dst)
+	#edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
+	#edges$src <- canonicalize_screens(edges$version, edges$src)
+	#edges$dst <- canonicalize_screens(edges$version, edges$dst)
 	edges
 }
 

### 2016-04-19 experiment/processing/graphs.R

@@ -20,6 +20,10 @@ edges <- filter_edges(read_edges(), participants)
 if (any(is.na(edges$pid))) {
   stop("found NAs in edges$pid")
 }
+# Ignore "not_running" and "starting", so they just show up as blank.
+edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
+edges$src <- canonicalize_screens(edges$version, edges$src)
+edges$dst <- canonicalize_screens(edges$version, edges$dst)
 
 state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
 
@@ -132,4 +136,5 @@ p <- p + labs(title=NULL, x=NULL, y="Minutes elapsed")
 p <- common_theme(p)
 p <- p + theme(panel.grid.minor.x=element_blank())
 p <- p + theme(panel.grid.major.y=element_blank())
+p
 ggsave("all-participant-edges.pdf", p, width=textwidth, height=textheight-0.75, device=cairo_pdf)

### 2016-04-19 experiment/processing/info.R

@@ -72,12 +72,12 @@ cat("****************************\n")
 edges <- filter_edges(read_edges(), participants)
 
 # 1 
-active_edges <- edges[edges[,"src"] != "progress",] # "active time" is anytime that people are not on the progress screen.
-progress_edges <- edges[edges[,"src"]== "progress",]
-first_edges <- edges[edges[,"src"]== "first",]
-proxy_edges <- edges[edges[,"src"] %in% c("proxy","proxyYES"),]
-bridge_edges <-  edges[edges[,"src"] %in% c("bridges","bridgeSettings","bridgeHelp"),]
-summary_edges <- edges[edges[,"src"]== "summary",]
+active_edges <- edges[edges[,"dst"] != "progress",] # "active time" is anytime that people are not on the progress screen.
+progress_edges <- edges[edges[,"dst"]== "progress",]
+first_edges <- edges[edges[,"dst"]== "first",]
+proxy_edges <- edges[edges[,"dst"] %in% c("proxy","proxyYES"),]
+bridge_edges <-  edges[edges[,"dst"] %in% c("bridges","bridgeSettings","bridgeHelp"),]
+summary_edges <- edges[edges[,"dst"]== "summary",]
 
 # 2
 total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)

### 2016-04-19 experiment/processing/common.R
I think this is still wrong.

@@ -70,10 +70,8 @@ filter_edges <- function(edges, participants) {
 	edges <- edges[is.na(edges$time_to_success) | edges$time_from_start < edges$time_to_success, ]
 	# Cut off the logs at our time limit.
 	edges <- trim_edges(edges, maxtime)
-	# Ignore "not_running" and "starting", so they just show up as blank.
-	#edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
-	#edges$src <- canonicalize_screens(edges$version, edges$src)
-	#edges$dst <- canonicalize_screens(edges$version, edges$dst)
+	edges$src <- canonicalize_screens(edges$version, edges$src)
+	edges$dst <- canonicalize_screens(edges$version, edges$dst)
 	edges
 }
 

### 2016-04-19 experiment/processing/graphs.R

@@ -22,8 +22,6 @@ if (any(is.na(edges$pid))) {
 }
 # Ignore "not_running" and "starting", so they just show up as blank.
 edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
-edges$src <- canonicalize_screens(edges$version, edges$src)
-edges$dst <- canonicalize_screens(edges$version, edges$dst)
 
 state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
 

### 2016-04-19 experiment/processing/info.R

@@ -72,7 +72,9 @@ cat("****************************\n")
 edges <- filter_edges(read_edges(), participants)
 
 # 1 
-active_edges <- edges[edges[,"dst"] != "progress",] # "active time" is anytime that people are not on the progress screen.
+active_edges <- edges[!(edges[,"dst"] %in% c("not_running", "starting", "progress")),] # "active time" is anytime that people are not on the progress screen.
+not_running_edges <- edges[edges[,"dst"]== "not_running",]
+starting_edges <- edges[edges[,"dst"]== "starting",]
 progress_edges <- edges[edges[,"dst"]== "progress",]
 first_edges <- edges[edges[,"dst"]== "first",]
 proxy_edges <- edges[edges[,"dst"] %in% c("proxy","proxyYES"),]
@@ -82,6 +84,8 @@ summary_edges <- edges[edges[,"dst"]== "summary",]
 # 2
 total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)
 active_time_per_user <- aggregate(active_edges$duration ~ active_edges$userid, active_edges, sum)
+not_running_time_per_user <- aggregate(not_running_edges$duration ~ not_running_edges$userid, not_running_edges, sum)
+starting_time_per_user <- aggregate(starting_edges$duration ~ starting_edges$userid, starting_edges, sum)
 progress_time_per_user <- aggregate(progress_edges$duration ~ progress_edges$userid, progress_edges, sum)
 first_time_per_user <- aggregate(first_edges$duration ~ first_edges$userid, first_edges, sum)
 proxy_time_per_user <- aggregate(proxy_edges$duration ~ proxy_edges$userid, proxy_edges, sum)
@@ -92,6 +96,8 @@ summary_time_per_user <- aggregate(summary_edges$duration ~ summary_edges$userid
 screen_time_per_user <- participants[c("userid","env","version","pool")]
 screen_time_per_user <- merge(screen_time_per_user, total_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, active_time_per_user, by=c(1), all=T)
+screen_time_per_user <- merge(screen_time_per_user, not_running_time_per_user, by=c(1), all=T)
+screen_time_per_user <- merge(screen_time_per_user, starting_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, progress_time_per_user, by=c(1), all=T)
[…]

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.
Use math mode for test statistics.

--- 2016-04-19 pets2017-paper/pets2017-paper.tex
@@
 Out of our 16 participants, ages ranged from 20 to~62
-($\mbox{mu} = 24.5$, $\mbox{sigma} = 12.6$). 53.3\% were male. 
+($\mu = 24.5$, $\sigma = 12.6$). 53.3\% were male. 
 93.3\% of our participants had at least
@@
 recruited from Craigslist. Ages ranged from 18 to 68
-($\mbox{mu} = 28.9$, $\mbox{sigma} = 12$). 56.8\% were male and 
+($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
 84.8\% of our participants had at least a college education.
@@
 However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made.
-% impact of version on success: not significant (Mann-Whitney W = 5.5, p-value = 0.8248)
-%impact of env on success: not significant (Kruskal-Wallis chi-squared = 4.7059, df = 2, p-value = 0.09509)
+% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
+%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)
 
@@
 Participants who were in environments in that the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
-Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek-bridge.
+Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
 
@@
 The level of censorship had a significant impact on the time to success.
-The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16).
+The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
 The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
-%impact of version on time to success: not significant (W = 1569, p-value = 0.07796)
-%impact of env on time to success : significant (Kruskal-Wallis chi-squared = 80.926, df = 2, p-value < 2.2e-16)
+%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
+%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})
 
@@
 
-The new interface results a statistically significant reduction in the overall active configuration time (Mann-Whitney Z = -3.055, p-value = 0.00225, effect size = 0.284), while maintaining the same probability for success for the user.
+The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $\mbox{effect size} = 0.284$), while maintaining the same probability for success for the user.
 We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time.
-%The impact of the environment on active time is significant (Kruskal-Wallis chi-squared = 51.978, df = 2, p-value = 5.166e-12)
+%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
 

### 2016-04-19 experiment/processing/common.R

@@ -72,8 +72,8 @@ filter_edges <- function(edges, participants) {
 	edges <- trim_edges(edges, maxtime)
 	# Ignore "not_running" and "starting", so they just show up as blank.
 	#edges <- edges[!(edges$dst %in% c("not_running", "starting")), ]
-	#edges$src <- canonicalize_screens(edges$version, edges$src)
-	#edges$dst <- canonicalize_screens(edges$version, edges$dst)
+	edges$src <- canonicalize_screens(edges$version, edges$src)
+	edges$dst <- canonicalize_screens(edges$version, edges$dst)
 	edges
 }
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
"Figure" → "Fig.".

@@
 The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
-The distribution of participants' time to success can be seen in Figure~\ref{fig:time_to_success_clamped}.
+The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
 %impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
@@
 In our experiment, participants had 40 minutes to circumvent censorship.
-Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
+Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
 Participants were less and less likely to succeed as time went on.
@@
 \subsubsection{Additional information} 
-We summarize each participant's actions throughout the experiment in Figure~\ref{fig:all-participant-edges}.
-Each row in Figure~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
+We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
+Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
 The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
@@
 \begin{itemize}
-\item E3-NEW-X23-20160328-155924 (Figure~\ref{autoresponder1})
-\item E3-OLD-X12-20160325-140813 (Figure~\ref{autoresponder2})
-\item E3-OLD-X24-20160328-133857 (Figure~\ref{autoresponder3})
+\item E3-NEW-X23-20160328-155924 (Fig.~\ref{autoresponder1})
+\item E3-OLD-X12-20160325-140813 (Fig.~\ref{autoresponder2})
+\item E3-OLD-X24-20160328-133857 (Fig.~\ref{autoresponder3})
 \end{itemize}
@@
 \begin{itemize}
-\item E1-OLD-X32-20160328-134531(Figure \ref{mirror})
-\item E2-NEW-X21-20160323-133257 (Figure \ref{techspot})
-\item E2-OLD-X10-20160323-132505 (Figure \ref{downloadio})
-\item E2-OLD-X28-20160328-134111 (Figure \ref{driverupdate})
-\item E3-NEW-X11-20160330-161511 (Figure \ref{softsonic})
+\item E1-OLD-X32-20160328-134531(Fig.~\ref{mirror})
+\item E2-NEW-X21-20160323-133257 (Fig.~\ref{techspot})
+\item E2-OLD-X10-20160323-132505 (Fig.~\ref{downloadio})
+\item E2-OLD-X28-20160328-134111 (Fig.~\ref{driverupdate})
+\item E3-NEW-X11-20160330-161511 (Fig.~\ref{softsonic})
 \end{itemize}
@@
 \caption{E2-NEW-X21-20160323-133257 downloaded Tor Browser from TechSpot, clicking on the download link from 
-TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Figure \ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
+TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
 \end{figure}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.

@@
 the bridge outside.
-
-% Bridges and pluggable transports are not limited to Tor...
 
@@
 Under ``Enter custom bridges'', there is a space to paste in
-a bridge specification that was obtained out of band.
-The ``Help'' button displays instructions on obtaining such
-bridge specifications.
+a bridge line, obtained out of band.
+The ``Help'' button displays instructions on obtaining
+bridge lines.
 }
@@
 Some transports connect directly to a static IP address,
-transforming traffic to defeat its on-the-wire identification as Tor;
+obfuscating traffic to defeat on-the-wire identification;
 they rely on the secrecy of their IP addresses for their effectiveness.
@@
 which encrypt Tor to look like random noise.
-Other transports do not depend on connecting to a static IP address:
+Other transports work differently and do not depend on connecting to a static IP address:
 ``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
@@
 \label{sec:goals}
-We evaluate the existing and redesigned Tor Browser configuration interface 
+In the course of our experiments we evaluated two versions
+of the Tor Launcher interface.
+The first, which we have labeled ``OLD'' in figures and tables,
+is the version that is being distributed to users now.
+The second, ``NEW'', is the prototype we revised and redesigned
+in order to provide better usability.
+We evaluate the old and new interfaces
 through the empirical evaluation and heuristic evaluation criteria below.
@@
 \begin{enumerate}
-    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
-    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
-    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
-    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
+    \item  {\bfseries Visibility of system status}: Provide feedback on what the system is doing. 
+    \item  {\bfseries Error management}: Expressing errors in plain language and offering a solution. 
+    \item  {\bfseries Understandable language}: Explaining the task, rather than technical concepts. 
+    \item  {\bfseries Simple design}: Showing options on an as-needed basis. 
 \end{enumerate}
@@
 \begin{enumerate}
-    \item {\bfseries Task Completion}: Almost all can successfully connect to Tor
-    \item {\bfseries  Time to Completion}: Time to completion. 
-    \item {\bfseries Safe for High-Risk Users}: It should be possible to configure Tor with the interface that it doesn't leak that they are using Tor. 
+    \item {\bfseries Task completion rate}: Almost all can successfully connect to Tor.
+    \item {\bfseries  Time to completion}: Measured between program startup and successful connection to Tor.
+    \item {\bfseries Safety for high-risk users}: It should be possible to configure Tor without leaking the fact that the user is using Tor. 
 \end{enumerate}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Get rid of \nocite{*}.
That's where all these unused cites were coming from.
Edits thru qualitative study.

@@
 The first, which we have labeled ``OLD'' in figures and tables,
-is the version that is being distributed to users now.
+is the current version being distributed with Tor Browser.
 The second, ``NEW'', is the prototype we revised and redesigned
@@
 
+All our experiments use (modified versions of)
+Tor Browser~5.0.3, which was the most recent stable release at the time we began~\cite{torbrowser-503}.
+Though there were new releases during the course of the experiments,
+we stuck with 5.0.3 so as not to introduce potential confounding factors.
+
 \section{Qualitative Analysis of the Existing Interface (Study 1)}
@@
 
-We performed qualitative research as an exploratory effort to gain an 
+We began our research with a qualitative, exploratory effort to gain an 
 understanding of underlying problems, such as reasons for confusion 
@@
 configuration. We did this through observing each participant as they 
-interacted with Tor Browser 5.0.3 interface and interviewed them about
-their experience. This study provides insights into particular problems with 
-the current Tor Browser configuration interface, and helps us to design
-a new interface which addresses these problems and gives foundation
+interacted with Tor Browser's interface, and later interviewed them about
+their experience. This study provided insights into particular problems with 
+the interface
+and gave us a foundation
 for hypotheses to test in quantitative research. 
-
-All our experiments use (modified versions of)
-Tor Browser~5.0.3, which was the current stable release at the time we began~\cite{torbrowser-503}.
-Though there were new releases during the course of the experiments,
-we stuck with 5.0.3 so as not to introduce potential confounding factors.
+Our observations during this study guided us in designing
+a redesigned interface, which we will describe later.
 
 \subsection{Inspection}
-A combination of usability inspection methods~\cite{nielsen1994usability}
-were used to prepare for the user study. Two researchers conducted a pluralistic 
+We used a combination of usability inspection methods~\cite{nielsen1994usability}
+to prepare for the user study. Two researchers conducted a pluralistic 
 walkthrough and stepped through various censorship
@@
 through the configuration process. After compiling all the possible paths through the 
-interface, feature inspection was performed to list sequences
+interface, we did feature inspection to list sequences
 of features used to accomplish typical tasks, taking note of long sequences or cumbersome
-steps. To focus our observations, a heuristic evaluation was performed to mark design issues 
-that may cause confusion for users during our study.
+steps. To focus our observations, we performed a heuristic evaluation to mark design issues 
+likely to cause confusion for users during our study.
 
@@
 Using established practices from the field of user experience research~\cite{howmanyusers},
-we recruited 5 participants for each censorship environment.
+we recruited 5 participants for each of the three censorship environments E1, E2, and E3.
 We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
@@
 
-We chose our participants based on the pre-screening information to have 
+We selected participants to have
 at least one person who has never heard of Tor, at least one person who has 
 only heard of Tor, and exactly one person who has previously used Tor in each
-environment. We also tried to evenly distribute any participants who had technical
+censorship
+environment. We tried to evenly distribute any participants who had technical
 expertise or used particular security tools throughout the censorship environments.
 
-Out of our 16 participants, ages ranged from 20 to~62
+Out of our 16 participants, ages ranged from 20 to~62 years
 ($\mu = 24.5$, $\sigma = 12.6$). 53.3\% were male. 
@@
 a college education.
-4 participants had used Tor before,
-5 had heard of Tor but not used it,
+4 participants had used Tor before;
+5 had heard of Tor but not used it;
 and the remaining 8 had never heard of Tor nor used it.
@@
 \subsection{Procedure}
-We conducted a qualitative evaluation of the interface through real-time observations of 
-users interacting with the configuration interface in a simulated censored environment.
-There was no researcher-user interaction during the experiment. A follow-up interview 
-detailed their thoughts about the configuration process.
+We evaluated the interface through real-time observation of 
+participants interacting with the configuration interface in simulated censored environments.
+A follow-up interview 
+solicited their thoughts about the configuration process.
 
@@
 room with a single computer, which is equipped with Tor, Chrome, Firefox, and Internet Explorer.
-A participant is firstly informed of 
-the risks of the study and consenting to data collection. If they consent, the 
-experiment begins. A researcher reads a script (Appendix~\ref{qualitative-script}) that 
+Each participant is informed of 
+the risks and purpose of the study.
+A researcher reads a script (Appendix~\ref{qualitative-script}) that 
 informs the participant of the simulated censorship environment and
-instruct them to visit a sample blocked website and a sample non-blocked website on a
-non-Tor browser of their choice to illustrate the situation. Then, participants are asked to 
+instructs them to visit sample blocked and unblocked websites
+in a standard browser, to show what it looks like when a site is blocked.
+Then, the participant is asked to 
 complete a worksheet (Appendix~\ref{participant-worksheet}) that gives information
@@
 to visit one blocked website and one non-blocked website.
-
-We chose Wikipedia's featured article of the day as the blocked website and 
-the CNN homepage as our non-blocked website because the familiarity 
-that most users have with these websites makes the browsing task relatively easy, 
-which focuses participants' attention to configuring Tor Browser. 
-After instructions, researchers stepped out of the room so that there was no interaction
+The worksheet informs the participant that the network is censored,
+but does not give details of what is censored or how.
+Participants were able to visit the unblocked website using any familiar browser,
+but had to configure Tor Browser in order to visit the blocked website.
+
+For the blocked website, we used the main page of Wikipedia,
+and for the unblocked site we used the CNN homepage.
+We chose these two sites because of their likely familiarity to web users;
+our goal was to evaluate the user interface,
+not to test users with a difficult browsing task.
+After giving the instructions,
+the researchers stepped out of the room so that there was no interaction
 between the participant and researcher for the rest of the session.
@@
 
-At this point, the participants do not know the details of their censorship environment,
-only that they are actively being censored. Ultimately, participants needed to configure Tor Browser to 
-circumvent the simulated censorship.
-
-After users completed the browsing tasks or have spent the rest of the time
-trying to configure Tor Browser, we interviewed participants about their experience.
-We performed a live transcription of the interview to avoid recording voices, which is
-considered personally identifying information. 
+We refreshed a list of Tor relay IP addresses and added them
+to a firewall blacklist before each session.
+In this first study, we neglected to block the IP addresses
+of the Tor directory authorities, which are the first hosts
+a client contacts when initiating a non-bridge connection.
+This, combined with new relays appearing in the network on an hourly basis,
+enabled a small number of participants to succeed with
+a direct connection when we expected them to fail.
+We fixed this problem in our second study by blocking the directory authorities.
+
+After participants completed the browsing tasks, or ran out of time,
+we interviewed them about their experience,
+taking notes of the questions and answers.
 We asked three standard questions asking about their general experience, 
 confusing interface features, and soliciting feedback for improvements. We followed up
-with specific questions we had for a particular participant from observing their screen. 
-This was to verify any hypothesis we had about the participant (i.e. ``they didn't know what to do on window~3'').  
-After their interview, participants were informed that the experiment was over and 
-given their payment of~\$30 for their time.
+with specific per-participant questions prompted from watching their screen. 
+This was to verify any hypotheses we had (e.g. ``they did not know what to do on window~3'').
+We paid each participant~\$30 for their time.
 
 \subsection{Results} 
-In this section, we discuss problems encountered by our participants at each step of the configuration process and solutions to those problems.
-We conclude with our goals for improving the configuration interface.
-Because of the small sample size of qualitative studies, we can only state that these are problems that participants can encounter when configuring.
-All quotes are not verbatim, but from best-effort live transcriptions of participant interviews.
+Here we discuss the problems our participants encountered at each step of the configuration process, and solutions to those problems.
+We outline our goals for improving the configuration interface.
+Participant quotations come from live transcription during the post-experiment interview
+and are not necessarily verbatim.
 
 \subsubsection{User Communication} 
-Many participants, including participants who were pre-screened as having high technical ability and previous experience with using Tor, were not familiar with the vocabulary.
+Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary:
 
@@
 
-\pquote{P2}{I don't know what any of those means (list of bridges),or what that (proxy) means at all.}
+\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
 \pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
 \pquote{P4}{I didn't know why I was getting back `establishing encrypted directory'---what does that mean?}
-The text in the interface intended to guide users through the process was not understood by our participants.
-The text also gave our participants a sense that the process intimidating for people who did not have a technical background.
+Participants did not understand the text in the interface that was intended to guide them.
+The text also gave our participants a sense that the process is intimidating for people without a technical background.
 
 \subsubsection{Connect vs. Configure} 
-The first task for our participants was to decide between connecting directly to the Tor network or configuring their connection.
-Text in the interface tells people that connecting directly ``will work in most situations'' and instructs to configure a bridge or proxy if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.
-
-Participants across all censorship environments connected directly to the Tor network.
-When they did, they did so because they were taking the path of least resistance first or intimidated by the configuration process.
+The first screen in Tor Launcher offers a choice to
+``Connect'' (directly to Tor without a proxy or a bridge),
+or ``Configure'' (bridge and proxy options).
+Text in the interface tells people that connecting directly ``will work in most situations'' and instructs them to configure if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.
+
+Participants across all censorship environments tried connecting directly.
+When they did, they did so because they were taking the path of least resistance first, or were intimidated by the configuration process:
 \pquote{P9}{Configure seemed manual, so I clicked connect.}
@@
 
-Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this happens, or what the difference between a blocked website and a blocked relay.
-Participant 10 and several other participants in the mild censorship environment opted to configure a connection when a direct connection to the Tor network would have worked.
+Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this was the case---whether only websites were blocked or relays were blocked as well.
+Several participants in E1, the mildest censorship environment, chose the ``Configure'' option when ``Connect'' would have worked, using a more complicated configuration than necessary.
 
@@
 \subsubsection{Bridge Configuration} 
-When a participant chooses to configure their connection, their next step is to determine whether they need to configure a bridge, and to configure one if necessary.
-Answering yes to ``Does your Internet Service Provider (ISP) block or otherwise censor connections to the Tor Network'' directs to a bridge configuration screen, whereas answering no skips that screen.
-We observed that multiple participants struggled with the technical language on the screen, and ultimately decided to try process of elimination.
+When a participant chooses the ``Configure'' option, their next step is to determine whether they need to configure a bridge.
+Answering yes to ``Does your Internet Service Provider (ISP) block or otherwise censor connections to the Tor Network'' sends the user to a bridge configuration screen, whereas answering no skips that screen.
+We saw that multiple participants struggled with the technical language on the yes-or-no screen, and ultimately decided to try a process of elimination.
 Most participants went with the default option to not configure a bridge.
@@
 
-On the bridge configuration screen, participants need to choose between configuring a built-in bridge versus a custom bridge.
-Participants were unsure of the difference between a built-in bridge and a custom bridge and also why one would use a custom bridge.
-Most chose obfs3 as their transport, because those were the default options on the screen.
+On the bridge configuration screen, participants need to select a built-in ``provided'' bridge or enter a custom bridge line.
+Participants were unsure of the difference between provided and custom, and also why one would use a custom bridge.
+Most chose the built-in obfs3 bridge, which the interface marks as ``recommended.''
 
@@
 
-Participants in E3, the most advanced censorship environment, were required to select a meek bridge (not the default) or to configure a custom bridge.
-After the first pluggable transport failed and even if the participants deduced that the source of the failed connection was a misconfigured bridge, the pluggable transport names only confused participants and caused odd behaviors.
-Participants chose transports at random, in order of the list starting from the default, in order of the list starting from the top, choosing familiar-sounding transports first (i.e.
-meek-amazon over fte), and choosing technical-sounding transports first (i.e.
+Participants in E3, the most difficult censorship environment, had to use either a meek bridge or a custom bridge.
+After trying and failing with obfs3, and even if they deduced that the source of the failed connection was a misconfigured bridge, participants were confused by the list of pluggable transport names.
+Participants used various selection strategies, choosing transports at random, in order, by name familiarity (e.g.
+meek-amazon over fte), or by how technical the names sounded (e.g.
 fte over meek-amazon).
@@
 \subsubsection{Proxy Configuration} 
-After the bridge configuration, the participant is asked if they need a proxy and if so, to configure one. This question also was too technical for most participants.
+After the bridge configuration, the interface asks whether a local proxy is needed. This question also was too technical for most participants.
 
@@
 
-For our participants, trying to unsuccessfully configure a proxy was the only mistake that resulted in failure.
-On the first attempt at configuration, most chose to not configure a proxy.
-Since the interface passively re-displayed a proxy-related window after an attempted connection regardless of the error, participants incorrectly assumed that they needed a proxy.
+For our participants, trying unsuccessfully to configure a proxy was the only mistake that resulted in failure.
+On the first attempt at configuration, most chose not to configure a proxy.
+Since the interface passively re-displayed a proxy-related window after a failed connection attempt, regardless of whether the failure was related to a proxy, participants incorrectly assumed that their configuration error lay on that screen.
 Participants did not check their incorrect assumption~\cite{wason1960failure}.
@@
 None of our censorship environments required our participants to configure a proxy for a successful connection.
-Participants followed the directions to look at the Internet settings, but they never found the (nonexistent) information.
+Participants heeded the program's suggestion to look at the settings in another browser, but what they found (a variation on ``use system proxy settings'') was not adequate to answer Tor Browser's question.
 
 \subsubsection{Progress Bar} 
-Users were generally displeased with the lack of feedback on the progress bar.
-Users do tolerate delays if they are for security reasons, but only if they understand the reason~\cite{egelmanplease}.
+Users were generally displeased with the lack of feedback from the progress bar.
+Users do tolerate delays if they are for security reasons, but only if they understand the reason for the delay~\cite{egelmanplease}.
 Participants in our study usually did not understand the security reason, and experienced delays up to 2 minutes, even in the ideal case in which a user chose the correct configuration on the first attempt.
@@
 
-Additionally, the progress bar remains empty on subsequent attempts to connect to the Tor Network until the percent progress supersedes the last displayed progress value (i.e.
-a participant who saw 30\% progress on their first attempt would see 0\% progress in the progress bar until subsequent attempts got at least 40\% progress).
-The negative feedback of a 0\% progress bar would cause users to assume that their subsequent attempts were wrong, even if they were correct.
+Additionally, the progress bar has a bug
+that causes it to draw itself only when the level of progress increases.
+If progress bar reaches a certain level,
+then the user closes the window,
+the next time the progress bar appears it will apparenly have regressed to 0\%.
+The apparent negative progress caused users to assume that their subsequent attempts were wrong, even if they were correct.
 
@@
 \bibliographystyle{abbrv}
-\nocite{*}
 \bibliography{pets2017-paper}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Put labels after captions in appenx figures.
Use session rather than full runid in participant identification.

@@
 
-Only connected directly (8/23): 
+Only tried to connect directly (8/23): 
 \begin{itemize}
-\item E2-NEW-X21-20160323-133257 
-\item E2-OLD-X04-20160330-181928
-\item E2-OLD-X10-20160331-153028
-\item E3-NEW-X05-20160324-132535
-\item E3-NEW-X17-20160323-133002
-\item E3-OLD-X06-20160328-132053
-\item E3-OLD-X06-20160330-161525 
-\item E3-OLD-X12-20160330-182011
+\item E2-NEW-X21-20160323-1400
+\item E2-OLD-X04-20160330-1800
+\item E2-OLD-X10-20160331-1600
+\item E3-NEW-X05-20160324-1400
+\item E3-NEW-X17-20160323-1400
+\item E3-OLD-X06-20160328-1400
+\item E3-OLD-X06-20160330-1600
+\item E3-OLD-X12-20160330-1800
 \end{itemize}
@@
 \begin{itemize}
-\item E3-NEW-X11-20160330-161511
-\item E3-NEW-X11-20160331-174655
-\item E3-NEW-X23-20160323-133346
-\item E3-OLD-X06-20160331-174650
-\item E3-OLD-X12-20160331-153055
-\item E3-OLD-X30-20160328-134412
+\item E3-NEW-X11-20160330-1600
+\item E3-NEW-X11-20160331-1800
+\item E3-NEW-X23-20160323-1400
+\item E3-OLD-X06-20160331-1800
+\item E3-OLD-X12-20160331-1600
+\item E3-OLD-X30-20160328-1400
 \end{itemize}
@@
 \begin{itemize}
-\item E2-OLD-X10-20160328-132828
-\item E3-NEW-X18-20160330-170145
-\item E3-NEW-X17-20160328-160037
-\item E3-OLD-X06-20160325-175101
-\item E3-OLD-X06-20160330-181926
-\item E3-OLD-X24-20160328-155926
+\item E2-OLD-X10-20160328-1400
+\item E3-NEW-X18-20160330-1800
+\item E3-NEW-X17-20160328-1600
+\item E3-OLD-X06-20160325-1800
+\item E3-OLD-X06-20160330-1800
+\item E3-OLD-X24-20160328-1600
 \end{itemize}
@@
 \begin{itemize}
-\item E3-NEW-X23-20160328-155924 (Fig.~\ref{autoresponder1})
-\item E3-OLD-X12-20160325-140813 (Fig.~\ref{autoresponder2})
-\item E3-OLD-X24-20160328-133857 (Fig.~\ref{autoresponder3})
+\item E3-NEW-X23-20160328-1600 (Fig.~\ref{autoresponder1})
+\item E3-OLD-X12-20160325-1400 (Fig.~\ref{autoresponder2})
+\item E3-OLD-X24-20160328-1400 (Fig.~\ref{autoresponder3})
 \end{itemize}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that E3-NEW-X23-20160328-155924 attempted to send to the bridge auto-responder.
+\caption{The message that E3-NEW-X23-20160328-1600 attempted to send to the bridge auto-responder.
 The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that E3-OLD-X12-20160325-140813 accidentally sent to the helpdesk rather than the bridge auto-responder.
+\caption{The message that E3-OLD-X12-20160325-1400 accidentally sent to the helpdesk rather than the bridge auto-responder.
 The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
-\caption{The message that E3-OLD-X24-20160328-133857 sent to the bridge auto-responder.
+\caption{The message that E3-OLD-X24-20160328-1400 sent to the bridge auto-responder.
 A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
@@
 \begin{itemize}
-\item E1-OLD-X32-20160328-134531(Fig.~\ref{mirror})
-\item E2-NEW-X21-20160323-133257 (Fig.~\ref{techspot})
-\item E2-OLD-X10-20160323-132505 (Fig.~\ref{downloadio})
-\item E2-OLD-X28-20160328-134111 (Fig.~\ref{driverupdate})
-\item E3-NEW-X11-20160330-161511 (Fig.~\ref{softsonic})
+\item E1-OLD-X32-20160328-1400 (Fig.~\ref{mirror})
+\item E2-NEW-X21-20160323-1400 (Fig.~\ref{techspot})
+\item E2-OLD-X10-20160323-1400 (Fig.~\ref{downloadio})
+\item E2-OLD-X28-20160328-1400 (Fig.~\ref{driverupdate})
+\item E3-NEW-X11-20160330-1600 (Fig.~\ref{softsonic})
 \end{itemize}
@@
 \begin{itemize}
-\item {\bfseries techspot.com -> 1download.io}: the ad firefox yahoo ad result for ``tor browser downloads.'' 
-\item {\bfseries driverupdate.net}: the 5th chrome google search result for ``tor browser download.'' 
-\item {\bfseries www.torservers.net/mirrors}: the first chrome google search result for ``tor browser mirror.''
-\item {\bfseries techspot.com}: the 5th chrome google search result for ``tor browser download.''
-\item {\bfseries softsonic.com}: the 2nd firefox yahoo search result for ``tor browser.''
+\item {\bfseries techspot.com -> 1download.io:} the ad firefox yahoo ad result for ``tor browser downloads.'' 
+\item {\bfseries driverupdate.net:} the 5th chrome google search result for ``tor browser download.'' 
+\item {\bfseries www.torservers.net/mirrors:} the first chrome google search result for ``tor browser mirror.''
+\item {\bfseries techspot.com:} the 5th chrome google search result for ``tor browser download.''
+\item {\bfseries softsonic.com:} the 2nd firefox yahoo search result for ``tor browser.''
 \end{itemize}
@@
 \begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
+\caption{E2-OLD-X10-20160323-1400 attempted downloaded Tor Browser from TechSpot.com, but clicked on one 
+a download link which was not from TechSpot.com. The download was from 1download.io, a suspicious source.}
 \label{downloadio}
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
-\caption{X10-20160323-132505 attempted downloaded Tor Browser from TechSpot.com, but clicked on one 
-a download link which was not from TechSpot.com. The download was from 1download.io, a suspicious source.}
 \end{figure}
@@
 \begin{figure}[h]
-\label{driverupdate}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
-\caption{X28-20160328-134111 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
+\caption{E2-OLD-X28-20160328-1400 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
 are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
 participant dutifully does before running the Tor Browser executable.}
+\label{driverupdate}
 \end{figure}
@@
 \begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
+\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror,www.torservers.net/mirrors.}
 \label{mirror}
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
-\caption{X32-20160328-134531 downloaded Tor Browser from a legitimate Tor Browser mirror,www.torservers.net/mirrors.}
 \end{figure}
@@
 \begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
+\caption{E2-NEW-X21-20160323-1400 downloaded Tor Browser from TechSpot, clicking on the download link from 
+TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
 \label{techspot}
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
-\caption{E2-NEW-X21-20160323-133257 downloaded Tor Browser from TechSpot, clicking on the download link from 
-TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
 \end{figure}
@@
 \begin{figure}[h]
+\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
+\caption{E3-NEW-X11-20160330-1600 downloaded Tor Browser from Softsonic, a reputable-looking but
+unconfirmed site.}
 \label{softsonic}
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{E3-NEW-X11-20160330-161511 downloaded Tor Browser from Softsonic, a reputable-looking but
-unconfirmed site.}
 \end{figure}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Formatting fixes.

@@
 \begin{enumerate}
-    \item  {\bfseries Visibility of system status}: Provide feedback on what the system is doing. 
-    \item  {\bfseries Error management}: Expressing errors in plain language and offering a solution. 
-    \item  {\bfseries Understandable language}: Explaining the task, rather than technical concepts. 
-    \item  {\bfseries Simple design}: Showing options on an as-needed basis. 
+    \item  {\bfseries Visibility of system status:} Provide feedback on what the system is doing. 
+    \item  {\bfseries Error management:} Expressing errors in plain language and offering a solution. 
+    \item  {\bfseries Understandable language:} Explaining the task, rather than technical concepts. 
+    \item  {\bfseries Simple design:} Showing options on an as-needed basis. 
 \end{enumerate}
@@
 \begin{enumerate}
-    \item {\bfseries Task completion rate}: Almost all can successfully connect to Tor.
-    \item {\bfseries  Time to completion}: Measured between program startup and successful connection to Tor.
-    \item {\bfseries Safety for high-risk users}: It should be possible to configure Tor without leaking the fact that the user is using Tor. 
+    \item {\bfseries Task completion rate:} Almost all can successfully connect to Tor.
+    \item {\bfseries  Time to completion:} Measured between program startup and successful connection to Tor.
+    \item {\bfseries Safety for high-risk users:} It should be possible to configure Tor without leaking the fact that the user is using Tor. 
 \end{enumerate}
@@
 
-Tor Browser 5.0.3.
-configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
-We rate the severity of the issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
+The Tor Browser configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+We rate the severity of each issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
 
 \begin{itemize}
-\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
-\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
-\item {\bfseries Cosmetic Problem}: The interface can be simplified visually. 
+\item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
+\item {\bfseries Major Problem:} The text was too technical for an average user to understand. 
+\item {\bfseries Minor Problem:} The configuration is not visible to the users before they connect or while they are connecting.
+\item {\bfseries Cosmetic Problem:} The interface can be simplified visually. 
  \end{itemize}
@@
 \begin{itemize}
-\item {\bfseries techspot.com -> 1download.io:} the ad firefox yahoo ad result for ``tor browser downloads.'' 
-\item {\bfseries driverupdate.net:} the 5th chrome google search result for ``tor browser download.'' 
-\item {\bfseries www.torservers.net/mirrors:} the first chrome google search result for ``tor browser mirror.''
-\item {\bfseries techspot.com:} the 5th chrome google search result for ``tor browser download.''
-\item {\bfseries softsonic.com:} the 2nd firefox yahoo search result for ``tor browser.''
+\item {\bfseries techspot.com} $\rightarrow$ {\bfseries 1download.io}: an advertisement in the Yahoo search results for ``tor browser downloads''.
+\item {\bfseries driverupdate.net}: the fifth Google search result for ``tor browser download''.
+\item {\bfseries www.torservers.net/mirrors}: the first google search result for ``tor browser mirror''.
+\item {\bfseries techspot.com}: the fifth Google search result for ``tor browser download''.
+\item {\bfseries softsonic.com}: the second Yahoo search result for ``tor browser''.
 \end{itemize}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
-\caption{E2-OLD-X10-20160323-1400 attempted downloaded Tor Browser from TechSpot.com, but clicked on one 
-a download link which was not from TechSpot.com. The download was from 1download.io, a suspicious source.}
+\caption{E2-OLD-X10-20160323-1400 attempted to download Tor Browser from TechSpot.com, but clicked on
+a download link which was not from TechSpot.com. The download was from another site, 1download.io.}
 \label{downloadio}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
-\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror,www.torservers.net/mirrors.}
+\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
 \label{mirror}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits

@@
 
-To fix the aforementioned problems, we made the following changes: \\
+To fix the aforementioned problems, we made the following changes,
+in a revised interface we labeled ``NEW'': \\
 
@@
 \item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user.
-Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy.
-\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process.
-Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
-\item {\bfseries Added system status visibility.} Before any attempt to connect to the Tor network, a summary screen displays if a bridge or proxy is configured, and if so, what the configurations are.
-The progress screen also displays the configurations while the connection attempt is being made.
+The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy.
+\item {\bfseries Reduced the overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process.
+Since users generally could not understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
+\item {\bfseries Added system status visibility.} Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings.
+The same information is shown on the progress screen while the connection is in progress.
 \item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen.
-For instance, additional fields were hidden until the relevant options were chosen.
-Additional stylistic simplifications were made, such as removing grouping boxes.
+For instance, additional fields are hidden until the relevant options were chosen.
 \end{enumerate}
 
-Other changes improve empirical goals from Section~\ref{sec:goals}: task completion, time to completion, and safe for high-risk users.
+Other changes improve empirical goals from Section~\ref{sec:goals}: task completion rate, time to completion, and safety for high-risk users.
 Items 5 and~6 improve task completion; 7 and~8 reduce time to completion; and 9 and~10 build users' mental models of censorship circumvention and the network components involved.
-Users' full control of the configuration process remains preserved.\\
+Users retain full control of the configuration process.\\
 
@@
 \setcounter{enumi}{4}
-\item {\bfseries Added guidance on choosing connect vs configure.} We labeled the configure option as advanced, manual, and only for heavily censored situations. 
-\item {\bfseries Added explicit advice on choosing bridge transports.} The default bridge is still obfs3. There is added text that advises users to try a meek bridge if obfs3 does not work.
+\item {\bfseries Added guidance on choosing connect versus configure.} We labeled the configure option as being advanced, manual, and suitable only for heavily censored situations. 
+\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
Edits.

@@
 
-\item {\bfseries Eliminated technical questions.}  We removed questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
-There are two fewer screens in the interface.
-\item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files.
-This is safe even for at-risk users, and greatly simplifies the configuration process.
-
-\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are configured in a topologically sequential order.
+\item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
+There are two fewer screens in the revised interface.
+\item {\bfseries Added auto-detection of proxies.} In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration.
+This purely local detection does not carry the potential risks of network probing and should be safe even for at-risk users.
+(In our experiment, we simulated the auto-detection by hard-coding the fact that a proxy was not required.)
+
+\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen.
 Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
-With auto-detection, configuring a proxy before a bridge will not burden the users.
-\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bar that shows network components involved in connecting to the Tor network.
+With auto-detection, configuring a proxy before a bridge burden users less than before.
+\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
 This aligns with the mental model we are trying to build.
-As connections are made with components, the progress bar displays a green check, giving immediate feedback to the user.
+As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user.
 For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network.
@@
 
-The redesigned interface conservatively interacts with users by automating only safe configuration processes and still allowing users to have control over configuring all interacting network components.
-The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as the censorship environments change.
+The redesigned interface conservatively interacts with users by automating only those configuration processes that are safe to automate, while still allowing users to have control.
+The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as censorship environments change.
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
More revisions.

@@
 \label{sec:quantitative}
-We performed quantitative research to quantify the existing problems
-and the impact of our redesign. Specifically, we collected all events, transitions, 
-and state for Tor Browser 5.0.3 and the redesigned Tor Browser.
+Having identified problems with the existing interface
+and done a redesign in an attempt to ameliorate them,
+we did research to quantify the existing problems
+and the impact of our changes.
+This study involved a larger number of users,
+again in simulated censorship environments,
+split between the old and new interface.
 
@@
 
-We instrumented Tor Launcher 5.0.3 and our redesigned Tor Launcher.
-The instrumentation logs recorded every meaningful interaction with the interface---every
+We added special instrumentation logging to both interfaces.
+The instrumentation logs recorded every meaningful interaction---every
 button press, every menu selection, every screen change---along with a timestamp.
 The logs enabled us to calculate statistics such as the success rate
-for each condition. We also recorded the participants' computer screens 
+and time spent on each screen.
+We also recorded the participants' computer screens
 throughout the experiment to capture non-interface activity such as 
@@
 
-We ran our experiment at Xlab, the Experimental Social Science Laboratory at University of 
-California, Berkeley. The Xlab allows researchers to run experiments on 36 participants at a time.
-There are 36 Windows machines in rows of 4, which are separated by cubicle walls. 
-We provided the scripts to set up the simulated censorship environment, install necessary software, 
-start the video recording, and save the logs and videos. Our experiment was not limited by Xlab
-requirements. However, the configuration interface relies on OS-provided features but testing 
-was only done on Windows machines, as a byproduct of using Xlab.
+We ran our experiment at Xlab, the Experimental Social Science Laboratory at the University of 
+California, Berkeley.
+The Xlab has 36 Windows~7 laptops, separated from each other by cubicle walls. 
+We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
+start the video recording, and save the logs and videos.
+% Our experiment was not limited by Xlab requirements.
+% [What does that mean?]
+Though Tor Browser runs on other operating systems,
+testing was only done on Windows, as a byproduct of using Xlab.
 
 \subsection{Recruitment}
-We recruited about 20 users for each censorship environment
-and interface combination, resulting in a total of 124 users. 
-Data analysis considerations deem 20 participants in each 
-6 interface version and simulated censorship combination a 
-minimum to be able to assume normal distributions and 60 participants
-testing each interface is large enough to have adequate effect size.
+We recruited 124 participants, about 20 for each
+of the six combinations of censorship environment
+and interface revision.
+Data analysis considerations deem 20 participants per combination a 
+minimum to be able to assume normal distributions, and 60 participants
+per interface revision is large enough to have an adequate effect size.
 
@@
 The recruitment text can be found in Appendix~\ref{quantitative-recruitment}. 
-
 Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
-recruited from Craigslist. Ages ranged from 18 to 68
+recruited from Craigslist. Ages ranged from 18 to~68 years
 ($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
linda's edits through abstract.

@@
 {Tor has grown beyond its original purpose as an anonymity tool and has 
-since become an important censorship circumvention tool.
-We conducted a series of
-experiments to evaluate and improve the configuration interface of Tor Browser,
-placing users in a simulated censorship environment and measuring their ability to circumvent it.
-A 16-participant experiment and interview
-identifies common user struggles while circumventing censorship.
-We use as feedback to redesign the configuration interface.
-We test the impact of our
-changes on 124 participants to find that our changes results in a significant reduction 
+become a widely-used censorship circumvention tool.
+This is the first study to examine Tor's usability as a censorship circumvention tool, 
+rather than an anonymity tool. We evaluate, redesign, and test the interface by
+placing users in simulated censorship environments, instruct them to use Tor
+to circumvent censorship, and measuring their interactions with the interface.
+A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
+We use the results as feedback to redesign the configuration interface.
+A 124-participant quantitative user study tests the impact of our changes
+to find that our changes results in a significant reduction 
 in the spent configuring a connection, while maintaining the same rate of success. We

### 2016-04-19 pets2017-paper/pets2017-paper.tex
this makes the figures align better.
linda's edits through half the intro

@@
 
-Although Tor~\cite{dingledine2004tor} was not designed to be a censorship circumvention tool, users started
-using it as one, since Tor's anonymizing functionality also circumvented censorship.
-In fact, some countries unsuccessfully attempt to block Tor for this reason~\cite{winter2012great}.
-Today, Tor's network of unlisted relays and various methods of obfuscation making it a viable censorship circumvention tool even in the face of nation-state level adversaries.
-
-To our knowledge, this is the first user study investigating the usability of Tor as a 
-censorship circumvention tool.
-We believe that this is a great opportunity for user research, both for investigating a case study of investigating the usability of a censorship circumvention tool, and also to help current Tor users censorship circumvention more easily.
-Not only will this allow for easier censorship circumvention, users who use Tor will be provided with extra security features that other censorship circumvention tools do not provide, such as anonymity.
-Additionally, increasing the adoption of Tor as a censorship circumvention tool benefits other users who use Tor as an anonymity system by increasing the number of overall users on the Tor network~\cite{dingledine2006anonymity}.
+Users started using Tor~\cite{dingledine2004tor} as a censorship circumvention tool because Tor's anonymizing functionality also coincidentally circumvented censorship.
+In fact, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}.
+Today, Tor is aware of these users and explicitly provides support for circumventing censorship through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and employs advanced techniques to resist blocking.
+
+This is the first user study investigating the usability of Tor as a censorship circumvention tool.
+Our experiments are both a great a case study of observing users circumvent censorship, and a step to help current Tor users by making censorship circumvention easier.
+All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool.
+Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased the number of overall users on the Tor network~\cite{dingledine2006anonymity}.
 
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
@@
 
-\begin{figure}[h]
+\begin{figure}
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}

### 2016-04-19 pets2017-paper/pets2017-paper.tex
delete bad participant.

@@
 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
-Although most participants eventually succeeded, 20\% (23 of 116) failed entirely.
+Although most participants eventually succeeded, 20\% (22 of 116) failed entirely.
 Reasons for failure were determined by a combination of log processing (i.e.
@@
 They often tried those configurations again or gave up.
-\item {\bfseries Thought that they needed a proxy (6/23)} After a couple failed attempts, these participants assumed that they needed a proxy.
+\item {\bfseries Thought that they needed a proxy (5/23)} After a couple failed attempts, these participants assumed that they needed a proxy.
 They spent the time trying to configure a proxy, usually without trying other bridges.
@@
 
-Thought that they needed a proxy (6/23): 
+Thought that they needed a proxy (5/23): 
 \begin{itemize}
 \item E2-OLD-X10-20160328-1400
-\item E3-NEW-X18-20160330-1800
 \item E3-NEW-X17-20160328-1600

### 2016-04-19 pets2017-paper/pets2017-paper.tex
finish intro pass

@@
 
-Our study consists of two user studies set in three simulated environments
-of mild to severe censorship.
-Study participants had to circumvent censorship and access a blocked website
-by configuring Tor Browser correctly.
-The various levels of censorship required various levels of manual configuration,
-ranging from almost none to detailed and specific settings.
-
+This paper details two user studies, and a redesign of the Tor configuration interface. 
+Both user studies are set in three simulated censorship environments
+that required various levels of manual configuration to circumvent.  
+Participants were instructed to circumvent censorship and access a blocked website
+by configuring Tor Browser and using it to visit the website.
 The first user study is a small-scale, one-on-one experiment that collected 
@@
 
-Our study finds that that users had difficulty in answering technical questions, feel unqualified to make technical choices, and cannot tell why their connection is failing.
-We made ten design changes that aimed to provide additional feedback, unburden the user, and build a user's understanding of the process.
-Our changes decreased the time participants spent configuring their connections, with no decrease in success rates.
-We conclude with a recommendation of changes that we believe will increase the usability of Tor Browser's configuration interface.
+In the Tor Browser 5.0.3 configuration interface, users don't know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
+We redesign the interface to build users' mental models, provide instructive text, and assist on error.
+These changes decreased the time participants spent configuring their connections, with no decrease in success rates.
+We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.
+
+\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
+As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
+\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
+Participants knew that they were censored to some degree since we had simulated censorship of websites.
+However, bridges are only necessary when the government has taken active steps to censor Tor itself.
+\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
+The problem is not necessarily where the interface directs users, misguiding them.
+It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
+\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
+The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+\end{itemize}
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
oops, delete copied text.

@@
 We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.
-
-\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
-As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
-\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
-Participants knew that they were censored to some degree since we had simulated censorship of websites.
-However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
-The problem is not necessarily where the interface directs users, misguiding them.
-It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
-\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
-The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
-\end{itemize}
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
background section pass

@@
 become a widely-used censorship circumvention tool.
-This is the first study to examine Tor's usability as a censorship circumvention tool, 
-rather than an anonymity tool. We evaluate, redesign, and test the interface by
+This is the first study to examine Tor's usability as a censorship circumvention tool.
+We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
 placing users in simulated censorship environments, instruct them to use Tor
@@
 
-Users started using Tor~\cite{dingledine2004tor} as a censorship circumvention tool because Tor's anonymizing functionality also coincidentally circumvented censorship.
-In fact, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}.
-Today, Tor is aware of these users and explicitly provides support for circumventing censorship through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and employs advanced techniques to resist blocking.
+Tor~\cite{dingledine2004tor} is an anonymity network that routes traffic through a series of relays
+that makes it difficult to observe the source and destination.
+Tor's anonymizing functionality coincidentally also circumvented censorship.
+Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}.
+Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.
 
@@
 
-This paper details two user studies, and a redesign of the Tor configuration interface. 
-Both user studies are set in three simulated censorship environments
-that required various levels of manual configuration to circumvent.  
-Participants were instructed to circumvent censorship and access a blocked website
-by configuring Tor Browser and using it to visit the website.
+We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
+measuring participants' interactions with the interface in various censorship environments.
 The first user study is a small-scale, one-on-one experiment that collected 
@@
 
-In the Tor Browser 5.0.3 configuration interface, users don't know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
+We find that users don't know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
 We redesign the interface to build users' mental models, provide instructive text, and assist on error.
@@
 
-\section{Circumvention and Tor}
-
-Censors of the Internet typically seek to block certain network resources such as websites.
-They use various technical means, for example falsifying DNS responses,
-blocking IP addresses, filtering keywords, and detecting protocols by deep packet inspection.
-Internet users, naturally, try to evade a censor's blocks,
-also employing a variety of technical means.
-
-Tor is an anonymity network that has also grown into
-a role as a vehicle for censorship circumvention.
-Tor routes user traffic through a random series of relays
-in a way that makes it difficult for an observer to connect source and destination.
-Tor, in its native form, is easy for censors to block,
-because the list of relays and their IP addresses is public.
-However, combined with \emph{bridges} and
-\emph{pluggable transports}, it becomes challenging to block access to Tor.
-
-Bridges are unlisted Tor relays that make it possible for a user to connect
-to the Tor network even if a censor blocks all publicly listed Tor relays.
-Pluggable transports are special protocols that run on bridges and obfuscate
-Tor's network protocol to make it difficult to detect.
+\section{Background}
+This section talks about how the configuration interface relates to Tor, what the network components are involved in censorship circumvention, and which configuration settings required to bypass levels of Tor-adverse censorship environments.
+
+\subsection{Tor, Tor Browser, and Tor Launcher}
+The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
+a modified Firefox browser that includes a built-in Tor client.
+Tor Browser has a software component called Tor Launcher that
+starts, stops, and otherwise controls the underlying Tor processes.
+Tor Launcher's graphical user interface gives access to a variety of 
+sophisticated circumvention mechanisms, asking the user
+to configure two a proxy and bridge (if any) before connecting to Tor
+for the first time. This is the target of our study.
+
+In principle, the process of configuring a proxy and bridge can be automated, but
+the interface eschews automatic configuration through network probing
+in favor of guided manual configuration to give users agency in configuring their connection.
+A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
+However, this burdens on the user to grapple with technical concepts such as 
+of bridges, pluggable transports, and proxies and to configure their connection correctly.
+
+\subsection{Bridges, Pluggable Transports, and Proxies} 
+Internet censors seek to block network resources, such as websites, through 
+a variety of means, such as falsifying DNS responses, blocking IP addresses, 
+filtering keywords, and detecting protocols by deep packet inspection.
+Censors can block the Tor network by blocking the list of Tor relays, which 
+are public. However, it becomes challenging to block access to Tor when
+the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
+Fig.~\ref{fig:topology} illustrates the interacting components.
 
@@
 
-Fig.~\ref{fig:topology} illustrates the interacting components.
-In addition to those components already mentioned,
-a user may need a local proxy in order to connect outside the local network.
-The terminology can be confusing:
-technically a Tor client is also a proxy,
-and so is a pluggable transport bridge.
-By ``proxy'' we mean an ordinary unobfuscated proxy such
-as a SOCKS or HTTP proxy.
-A proxy is only needed in certain managed networks,
-such as some corporate or university networks.
-An important distinction is that the proxy usually lies within the censor's control;
-the bridge outside.
-
-\subsection{Tor Browser and Tor Launcher}
-
-For most users, the recommended way to use Tor is through Tor Browser~\cite{torbrowser},
-a modified Firefox browser that includes a built-in Tor client.
-Tor Browser has a special software component that
-Tor Launcher starts, stops, and otherwise controls
-an underlying Tor process.
-This component is called Tor Launcher
-and it is the primary target of our study.
-% Tor Launcher is also used by Tor Messenger~\cite{tormessenger},
-% an instant messaging client.
-
-Tor Launcher has a graphical user interface,
-displayed at its first startup, that asks the user
-to configure two important settings before connecting to Tor
-for the first time:
-what proxy to use (if any) and what bridge to use (if any).
-The correct configuration settings will vary depending
-on the user and their circumstances.
-A graphical wizard asks a series of questions to guide
-users in finding the correct configuration.
-Most Tor users do not require a bridge nor a proxy and
-can simply click the ``Connect'' shortcut on
-the first page to bypass all configuration.
-Others, though, need to know or find out
-all these pieces of information:
-
-\begin{itemize}
-	\item{Whether they are censored} 
-	\item{Whether the Tor network is censored by their ISP}
-	\item{Which bridges work in the current environment} 
-	\item{If no bridges work, how to get a custom bridge} 
-	\item{Whether a proxy is required to access the Internet}
-	\item{If a proxy is required, the proxy settings}
-\end{itemize}
-
-While these steps can in principle be automated to some degree,
-the interface eschews automatic configuration through network probing
-in favor of guided manual configuration,
-in order to give users their own agency in configuring their connection.
-A knowledgeable user can connect while minimizing their network trace
-and not make it obvious that they are using Tor.
-However, this design decision puts the burden of technical knowledge and correct configuration on the user.
-The technical concepts of bridges, pluggable transports, and proxies are likely unfamiliar to the average user.
-
-\subsection{Bridges and pluggable transports}
+Bridges are unlisted Tor relays that make it possible for a user to connect
+to the Tor network even if a censor blocks all publicly listed Tor relays.
+Pluggable transports are special protocols that run on bridges and obfuscate
+Tor's network protocol to make it difficult to detect. 
+Configuring a bridge requires providing one or more
+``bridge lines,'' a specification of a bridge that
+includes its IP address, transport type, and other metadata.
+For ease of use, the interface has hard-coded options for 
+the user to choose a group of bridges that use a particular
+pluggable transport. For example, choosing  the hard-coded``obfs3'' option
+configures a handful of bridges that use obfs3 pluggable transport.
+Some censors block the IP addresses of the hard-coded bridges by looking
+at the source code for those addresses (except ``flashproxy'' and ``meek,'' which work differently).
+If the built-in bridges do not work, a user can obtain bridge lines
+through out-of-band channels, for instance by email~\cite{bridgedb}.
+
+Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
+options at the time of the study and lists the available pluggable transports.
+Some transports connect directly to a static IP address,
+obfuscating traffic to defeat on-the-wire identification;
+they rely on the secrecy of their IP addresses for their effectiveness.
+These include ``fte'' and ``fte-ipv6''~\cite{fte},
+which make Tor look like another protocol such as HTTP; and
+``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
+which encrypt Tor to look like random noise.
+Other transports work differently and do not depend on connecting to a static IP address:
+``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
+and the three ``meek''~\cite{fifield2015blocking} options route traffic
+through content delivery networks.
 
@@
 
-Tor Launcher gives access to a variety of sophisticated
-circumvention mechanisms.
-Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
-interface as it existed at the time we did our study
-and lists the available pluggable transports.
-Some transports connect directly to a static IP address,
-obfuscating traffic to defeat on-the-wire identification;
-they rely on the secrecy of their IP addresses for their effectiveness.
-These include ``fte'' and ``fte-ipv6''~\cite{fte},
-which make Tor look like another protocol such as HTTP; and
-``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
-which encrypt Tor to look like random noise.
-Other transports work differently and do not depend on connecting to a static IP address:
-``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
-and the three ``meek''~\cite{fifield2015blocking} options route traffic
-through content delivery networks.
-
-Configuring a bridge requires providing one or more
-``bridge lines,'' short specifications of a bridge
-including its IP address, transport type, and other metadata.
-For ease of use, the options under ``Connect with provided bridges''
-activate ready-made, built-in bridge lines,
-hard-coded into the browser.
-Choosing ``obfs3,'' for example, activates a handful
-of bridges that use obfs3, without the user needing
-to find and paste in obfs3 bridge lines.
-A censor can of course block the IP addresses of the default bridge lines
-(except ``flashproxy'' and ``meek,'' which work differently).
-If the built-in bridges do not work, a user can obtain bridge lines
-through out-of-band channels, for instance by email~\cite{bridgedb}.
-
-The ``flashproxy'' transport, because of the way it works,
-requires users to take special technical steps before using it.
-Unlike the other options, it does not work out of the box
-in most situations, including during our experiments.
-For our participants, its presence at the top of the list
-was an inviting failure mode.
+In addition to tor-specific components, a proxy may be necessary to connect 
+outside the local network in certain managed networks, such as corporate or university networks.
+Configuring a proxy requires providing the proxy protocol, ip address, port and additional optional
+fields. There is no assistance or automation with this process. The user must locate the 
+proxy information and correctly format this information into the configuration interface.
+
+Technically the Tor client, pluggable transport bridge, and proxy are all
+proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
+as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
+censor's control.
+
+\subsection{Circumventing Censorship with Tor}
+There are many valid configuration settings to connect to the Tor network.
+For instance, a user who does not need a bridge or proxy to circumvent censorship
+can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
+The minimum amount of configuration required, and therefore, the set of valid configuration settings,
+vary depending on the censorship environment. At the maximum, users will need to know or find out:\\
+
+\begin{itemize}
+	\item{Whether they are censored} 
+	\item{Whether the Tor network is censored by their ISP}
+	\item{Which groups of hard-coded bridges work in their environment} 
+	\item{If no hard-coded bridges work, how to get and enter in a custom bridge} 
+	\item{Whether a proxy is required to access the Internet}
+	\item{If a proxy is required, and if so, the proxy settings}
+\end{itemize}
+
+Uncensored users and users in censorship environments that do not explicitly 
+block Tor do not require a bridge nor a proxy and can bypass the configuration process.
+Users in censorship environments that explicitly block Tor but has not blocked the 
+hard-coded bridges in the Tor Launcher source code are required to use a 
+a hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
+blocked Tor relays and hard-coded bridges will be required to configure a meek-bridge (which 
+routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
+configure a custom bridge to connect to Tor.
 
@@
 and are not necessarily verbatim.
+
+%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
+%\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
+As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
+%\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
+Participants knew that they were censored to some degree since we had simulated censorship of websites.
+However, bridges are only necessary when the government has taken active steps to censor Tor itself.
+%\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
+The problem is not necessarily where the interface directs users, misguiding them.
+It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
+%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
+The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
+%\end{itemize}
 

### 2016-04-19 pets2017-paper/pets2017-paper.tex
evaluation and setup sections

@@
 
-\section{Goals/Evaluation Criteria}
+\section{Evaluation Criteria and Goals}
 \label{sec:goals}
-In the course of our experiments we evaluated two versions
-of the Tor Launcher interface.
+The series of user studies evaluated two versions of the Tor Launcher interface.
 The first, which we have labeled ``OLD'' in figures and tables,
@@
 The second, ``NEW'', is the prototype we revised and redesigned
-in order to provide better usability.
-We evaluate the old and new interfaces
-through the empirical evaluation and heuristic evaluation criteria below.
+in order to provide better usability. Below are the empirical and 
+heuristic evaluation criteria we use to assess the interfaces.
+
+Our empirical evaluation criteria for the Tor Browser configuration
+interface are from common metrics that measure ease of use: \\
+
+\begin{enumerate}
+    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
+    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful connection to Tor.
+    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor. 
+\end{enumerate}
 
@@
 \begin{enumerate}
-    \item  {\bfseries Visibility of system status:} Provide feedback on what the system is doing. 
-    \item  {\bfseries Error management:} Expressing errors in plain language and offering a solution. 
-    \item  {\bfseries Understandable language:} Explaining the task, rather than technical concepts. 
-    \item  {\bfseries Simple design:} Showing options on an as-needed basis. 
+    \item  {\bfseries Visibility of system status:} There is feedback on system state is and what the system is doing. 
+    \item  {\bfseries Error management:}  Errors are in plain language and offers a solution. 
+    \item  {\bfseries Understandable language:} Users are able to understand the text and concepts mentioned in the interface. 
 \end{enumerate}
 
-Our empirical evaluation criteria for the Tor Browser configuration
-interface are from common metrics that measure ease of use with a special 
-consideration for high-risk users: \\
-
-\begin{enumerate}
-    \item {\bfseries Task completion rate:} Almost all can successfully connect to Tor.
-    \item {\bfseries  Time to completion:} Measured between program startup and successful connection to Tor.
-    \item {\bfseries Safety for high-risk users:} It should be possible to configure Tor without leaking the fact that the user is using Tor. 
-\end{enumerate}
-
-\subsection{Censorship Environments}
+An ideal interface would guide users though the configuration process while communicating system state and managing errors along the way.
+Users would be able to connect to the Tor network in a couple of minutes.
+
+\section{Experimental Setup}
 \label{sec:environments}
-In each experiment, we simulated three censorship environments,
-which we labeled ``E1,'' ``E2,'' and ``E3''
-in order of increasing severity.
+For our experiments, we use (modified versions of) Tor Browser~5.0.3, 
+the most recent stable release at the time~\cite{torbrowser-503}.
+Though there were new releases during the experiments,
+we tested the same version across all participants to not introduce
+confounding factors.
+
+For both user studies, we simulated three censorship environments,
+which we refer to as ``E1,'' ``E2,'' and ``E3,'' in order of increasing severity.
 We designed the environments to be representative
 of what, in our estimation, are important real-world
-cases of censorship, but they are not intended to imitate
-any particular country's censorship exactly.
+cases of censorship. They are not intended to imitate
+any particular country's censorship environment.
 
@@
 
-Table~\ref{tab:environments} summarizes what is blocked
-in each environment.
-We used features of the Windows operating system to implement
-the above environments.
+Table~\ref{tab:environments} summarizes our simulated censorship
+environments. We used features of the Windows operating system 
+to implement the above blocking behaviors.
 To simulate website blocking, we added entries to the hosts file,
@@
 \end{table}
-
-All our experiments use (modified versions of)
-Tor Browser~5.0.3, which was the most recent stable release at the time we began~\cite{torbrowser-503}.
-Though there were new releases during the course of the experiments,
-we stuck with 5.0.3 so as not to introduce potential confounding factors.
 

### 2016-04-20 pets2017-paper/pets2017-paper.tex
qualitative section pass

@@
 
-We began our research with a qualitative, exploratory effort to gain an 
-understanding of underlying problems, such as reasons for confusion 
-during the configuration process and motivations for particular choices in 
-configuration. We did this through observing each participant as they 
-interacted with Tor Browser's interface, and later interviewed them about
-their experience. This study provided insights into particular problems with 
-the interface
-and gave us a foundation
-for hypotheses to test in quantitative research. 
-Our observations during this study guided us in designing
-a redesigned interface, which we will describe later.
+We ran a qualitative, exploratory user study to gain an 
+understanding of how users interact with the configuration interface and
+what common problems may be. We did this by observing participants using 
+the interface to circumvent censorship, and interviewing them about
+their experience.  Our observations during this study guided us in
+redesigning interface and provided hypotheses to test in our quantitative study.
 
@@
 through the configuration process. After compiling all the possible paths through the 
-interface, we did feature inspection to list sequences
-of features used to accomplish typical tasks, taking note of long sequences or cumbersome
-steps. To focus our observations, we performed a heuristic evaluation to mark design issues 
+interface, researchers performed feature inspection, listing sequences of features used 
+to accomplish typical tasks and taking note of long sequences or cumbersome
+steps. To focus our observations, we performed a heuristic evaluation to mark tasks
 likely to cause confusion for users during our study.
@@
 
-We recruited our users from Craigslist. The recruitment text can be found in 
-Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
-SurveyGizmo online survey that collected information about our participants.
+We recruited our users from Craigslist, vaguely stating that we wanted to evaluate some piece of software. 
+The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
+SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
 The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
-
-We selected participants to have
-at least one person who has never heard of Tor, at least one person who has 
-only heard of Tor, and exactly one person who has previously used Tor in each
-censorship
-environment. We tried to evenly distribute any participants who had technical
+We selected participants to have at least one person who has never heard of Tor, 
+at least one person who has only heard of Tor, and exactly one person who has previously used Tor in each
+censorship environment. We tried to evenly distribute any participants who had technical
 expertise or used particular security tools throughout the censorship environments.
@@
 \subsection{Procedure}
-We evaluated the interface through real-time observation of 
-participants interacting with the configuration interface in simulated censored environments.
-A follow-up interview 
-solicited their thoughts about the configuration process.
-
 The one-hour, single-participant procedure begins when a participant enters a small 
-room with a single computer, which is equipped with Tor, Chrome, Firefox, and Internet Explorer.
-Each participant is informed of 
-the risks and purpose of the study.
-A researcher reads a script (Appendix~\ref{qualitative-script}) that 
-informs the participant of the simulated censorship environment and
+room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
+Each participant is informed of the risks and purpose of the study.
+A researcher reads a script that informs the participant of the simulated censorship environment and
 instructs them to visit sample blocked and unblocked websites
-in a standard browser, to show what it looks like when a site is blocked.
-Then, the participant is asked to 
-complete a worksheet (Appendix~\ref{participant-worksheet}) that gives information
+in a standard browser, to show what it looks like when a site is blocked (Appendix~\ref{qualitative-script}).
+Then, the participant is asked to  complete a worksheet that gives information
 on their censorship environment and instructs them
-to visit one blocked website and one non-blocked website.
+to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
 The worksheet informs the participant that the network is censored,
-but does not give details of what is censored or how.
+but does not give details of what services and websites are specifically blocked.
 Participants were able to visit the unblocked website using any familiar browser,
@@
 We chose these two sites because of their likely familiarity to web users;
-our goal was to evaluate the user interface,
-not to test users with a difficult browsing task.
-After giving the instructions,
-the researchers stepped out of the room so that there was no interaction
+our goal was to evaluate the user interface, not to test users with a browsing task.
+After giving the instructions, the researchers stepped out of the room so that there was no interaction
 between the participant and researcher for the rest of the session.
@@
 are available from our project page.
-Participants had an 
-average of 45 minutes to complete their worksheet.
+Participants had an average of 45 minutes to complete their worksheet.
 
@@
 
-After participants completed the browsing tasks, or ran out of time,
+After participants completed the browsing tasks or ran out of time,
 we interviewed them about their experience,
@@
 \subsection{Results} 
-Here we discuss the problems our participants encountered at each step of the configuration process, and solutions to those problems.
-We outline our goals for improving the configuration interface.
+We discuss six common challenges our participants encountered during the configuration process.
 Participant quotations come from live transcription during the post-experiment interview
-and are not necessarily verbatim.
+and are not necessarily verbatim.\\
 
@@
 
-\subsubsection{User Communication} 
-Many participants, including participants who were pre-screened for high technical ability and previous experience with using Tor, were not familiar with the vocabulary:
+\noindent {\bfseries Challenge 1: Users did not understand what proxies, bridges, and pluggable transports were.}
+Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary:
 
@@
 \pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
-\pquote{P4}{I didn't know why I was getting back `establishing encrypted directory'---what does that mean?}
-Participants did not understand the text in the interface that was intended to guide them.
-The text also gave our participants a sense that the process is intimidating for people without a technical background.
-
-\subsubsection{Connect vs. Configure} 
-The first screen in Tor Launcher offers a choice to
-``Connect'' (directly to Tor without a proxy or a bridge),
-or ``Configure'' (bridge and proxy options).
-Text in the interface tells people that connecting directly ``will work in most situations'' and instructs them to configure if the ``Internet connection is censored or proxied.'' We found that a majority of our participants did not take the time to read the text on the screen and that if they did, the text did not always soundly influence their decision.
-
-Participants across all censorship environments tried connecting directly.
-When they did, they did so because they were taking the path of least resistance first, or were intimidated by the configuration process:
-\pquote{P9}{Configure seemed manual, so I clicked connect.}
-\pquote{P14}{The words were confusing.
-I don't really understand computers.
-I don't know what configure means in this setting.
-Hmm, is it going to crash?
-When you see connect, you want to click it because you really want it to connect.}
-
-Bridges are only necessary when Tor relays are censored, but participants are not able to determine when this was the case---whether only websites were blocked or relays were blocked as well.
-Several participants in E1, the mildest censorship environment, chose the ``Configure'' option when ``Connect'' would have worked, using a more complicated configuration than necessary.
-
-\pquote{P10}{I was censored, so I picked the configure.}
-
-Users do not make the optimal choice between connect and configure.
-This leads to discouragement from attempting a failed connection and wasted time spent waiting for feedback, which lessen the chance for a successful connection.
-
-\subsubsection{Bridge Configuration} 
-When a participant chooses the ``Configure'' option, their next step is to determine whether they need to configure a bridge.
-Answering yes to ``Does your Internet Service Provider (ISP) block or otherwise censor connections to the Tor Network'' sends the user to a bridge configuration screen, whereas answering no skips that screen.
-We saw that multiple participants struggled with the technical language on the yes-or-no screen, and ultimately decided to try a process of elimination.
-Most participants went with the default option to not configure a bridge.
-
-\pquote{P7}{The bridge screen was the most challenging. It seemed very technical to me. I don't know what a bridge is.}
-\pquote{P12}{I decided which options to choose by process of elimination with trial and error.}
-
-On the bridge configuration screen, participants need to select a built-in ``provided'' bridge or enter a custom bridge line.
-Participants were unsure of the difference between provided and custom, and also why one would use a custom bridge.
-Most chose the built-in obfs3 bridge, which the interface marks as ``recommended.''
+
+\noindent {\bfseries Challenge 2: Users do not know if they should connect directly or configure a connection.} 
+Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to.
+Other participants were not able to determine that a failed direct connection to the Tor network was the result of the Tor network being censored.
+\\
+
+\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
+On the bridge configuration screen, participants were intimidated by the names of the bridge transports.
+The most common behavior was to configure with the recommended bridge option (obfs3).
+If the recommended one did not work, participants didn't know how to choose another.
 
@@
 
-Participants in E3, the most difficult censorship environment, had to use either a meek bridge or a custom bridge.
-After trying and failing with obfs3, and even if they deduced that the source of the failed connection was a misconfigured bridge, participants were confused by the list of pluggable transport names.
-Participants used various selection strategies, choosing transports at random, in order, by name familiarity (e.g.
-meek-amazon over fte), or by how technical the names sounded (e.g.
-fte over meek-amazon).
-
-\pquote{P4}{When I saw obfs3 as the recommended option, the next option logically for me was obfs4.}
-\pquote{P5}{I tried the pluggable transport that used google, because I noticed that google was working (when I was using a non-Tor browser).}
-
-Users are not qualified to choose transports in an educated order.
-When our participants chose incorrectly, they spent time testing their wrong hypothesis and got discouraged with each wrong decision.
-Our participants were resilient and tried for 40 minutes, but we believe that this is a byproduct of the experimental setting and compensation.
-
-\subsubsection{Proxy Configuration} 
-After the bridge configuration, the interface asks whether a local proxy is needed. This question also was too technical for most participants.
-
-\pquote{P11}{I think you can only answer this question (does this computer need a local proxy) if you know what a local proxy is. Otherwise, you have no chance.}
-
-For our participants, trying unsuccessfully to configure a proxy was the only mistake that resulted in failure.
-On the first attempt at configuration, most chose not to configure a proxy.
-Since the interface passively re-displayed a proxy-related window after a failed connection attempt, regardless of whether the failure was related to a proxy, participants incorrectly assumed that their configuration error lay on that screen.
-Participants did not check their incorrect assumption~\cite{wason1960failure}.
-All who chose to configure a proxy were unsuccessful.
+\noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
+Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
+When participants did encounter an error message, they did not understand what errors meant (Figure~\ref{fig:error}).\\
+
+\noindent {\bfseries Challenge 5: Users assume they are wrong when they are right.}
+If users chose particular wrong configurations (i.e. a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time. 
+\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
+
+The progress bar also has a bug that causes it to update itself only when the level of progress increases.
+If progress bar reaches a 90\% and fails, the next attempt will apparently have regressed to 0\% and remain there until the progress reaches >90\%.
+Due to this, participants assumed that their subsequent attempts were wrong, even if they were correct.
+\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
+
+\noindent {\bfseries Challenge 6: Users assume that proxy is required after a failed connection.} 
+All of our participants who failed to connect (5 of 16) failed for this reason.
+Many mistakenly assumed that they needed a proxy upon failure, because the interface passively redirects to the proxy screen (the last screen) after failure.
 
@@
 
-None of our censorship environments required our participants to configure a proxy for a successful connection.
-Participants heeded the program's suggestion to look at the settings in another browser, but what they found (a variation on ``use system proxy settings'') was not adequate to answer Tor Browser's question.
-
-\subsubsection{Progress Bar} 
-Users were generally displeased with the lack of feedback from the progress bar.
-Users do tolerate delays if they are for security reasons, but only if they understand the reason for the delay~\cite{egelmanplease}.
-Participants in our study usually did not understand the security reason, and experienced delays up to 2 minutes, even in the ideal case in which a user chose the correct configuration on the first attempt.
-If users chose particular wrong configurations (i.e.
-a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time.
-
-\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-\pquote{P6}{How long does this actually take (to connect)? This took way too long, and I didn't know how long it should take.}
-\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
-
-Additionally, the progress bar has a bug
-that causes it to draw itself only when the level of progress increases.
-If progress bar reaches a certain level,
-then the user closes the window,
-the next time the progress bar appears it will apparenly have regressed to 0\%.
-The apparent negative progress caused users to assume that their subsequent attempts were wrong, even if they were correct.
+From interviewing our participants, we found that these challenges result because users are not familiar with technical or Tor-specific terms, feedback on progress or an errors were inconsistent, and the interface did not instruct users on what to do in the event of a failure.
 

### 2016-04-20 pets2017-paper/pets2017-paper.tex
qualitative section

--- 2016-04-19 pets2017-paper/pets2017-paper.tex
@@
 then the user closes the window,
-the next time the progress bar appears it will apparenly have regressed to 0\%.
+the next time the progress bar appears it will apparently have regressed to 0\%.
 The apparent negative progress caused users to assume that their subsequent attempts were wrong, even if they were correct.

### 2016-04-20 pets2017-paper/pets2017-paper.tex
redesign pass

--- 2016-04-20 pets2017-paper/pets2017-paper.tex
@@
 
-%\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
-%\item {\bfseries Challenge 1:} People don't know how to choose between ``connect directly'' versus ``configure'' on the first screen.
-As seen in Figure \ref{fig:window1}, there is some guidance for the users, but we found this largely unhelpful since people do not understand the text on the screen.
-%\item {\bfseries Challenge 2:} People feel compelled to set up a bridge, even if they don't need one, because they do not know how censorship works.
-Participants knew that they were censored to some degree since we had simulated censorship of websites.
-However, bridges are only necessary when the government has taken active steps to censor Tor itself.
-%\item {\bfseries Challenge 3:} When their first attempt to connect fails, the interface directs people to the last window they saw before the connection failure.
-The problem is not necessarily where the interface directs users, misguiding them.
-It was common for the interface to redirect users to the proxy window in Figure \ref{fig:window5}, even when they needed to pick another bridge.
-%\item {\bfseries Challenge 4:} When the first attempt to connect fails, people did not know what to do or what to try next.
-The feedback given to users was not understood (see Figure \ref{fig:error}) and also did not guide users into specific actions (such as trying a different bridge, trying the same configuration again, try connecting directly, etc.).
-%\end{itemize}
-
 \noindent {\bfseries Challenge 1: Users did not understand what proxies, bridges, and pluggable transports were.}
@@
 \label{redesign}
+
  \begin{figure*}[t]
@@
 
-The Tor Browser configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design.
+From the result of our qualitative user study, we see that many users struggle with the configuration process. 
+The Tor Browser configuration interface does not adequately meet our criteria from Section~\ref{sec:goals} of
+managing errors gracefully, communicating in understandable language, and giving  users feedback on system state. 
 We rate the severity of each issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
@@
 \item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem:} The text was too technical for an average user to understand. 
-\item {\bfseries Minor Problem:} The configuration is not visible to the users before they connect or while they are connecting.
-\item {\bfseries Cosmetic Problem:} The interface can be simplified visually. 
+\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users were required to answer were too technical for the average user. 
+\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect to the Tor network or while they are connecting to the Tor network.
  \end{itemize}
@@
 
-To fix the aforementioned problems, we made the following changes,
-in a revised interface we labeled ``NEW'': \\
+To address these three aforementioned user interaction problems, we made the following three changes to the configuration interface:  \\
 
@@
 The same information is shown on the progress screen while the connection is in progress.
-\item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen.
-For instance, additional fields are hidden until the relevant options were chosen.
 \end{enumerate}
@@
 \begin{enumerate}
-\setcounter{enumi}{4}
-\item {\bfseries Added guidance on choosing connect versus configure.} We labeled the configure option as being advanced, manual, and suitable only for heavily censored situations. 
+\setcounter{enumi}{3}
+\item {\bfseries Added guidance on choosing connect versus configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
 \item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.
@@
 \item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
-There are two fewer screens in the revised interface.
+This are two fewer screens in the revised interface.
 \item {\bfseries Added auto-detection of proxies.} In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration.
@@
 \item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
-This aligns with the mental model we are trying to build.
+This aligns with the mental model we are trying to build in the user.
 As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user.
@@
 
-The redesigned interface conservatively interacts with users by automating only those configuration processes that are safe to automate, while still allowing users to have control.
-The design requires more maintenance because of the explicit advice given on which order to select bridges and advice on error messages, which may change as censorship environments change.
+These changes result in a redesigned interface which we refer to as ``NEW.'' Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.
 

### 2016-04-20 pets2017-paper/pets2017-paper.tex
pass through limitations, future work, and discussion.

@@
 \begin{description}
-\item{\bfseries Automate the configuration.} This sounds like a radical idea, but this wouldn't harm users today.
-Additionally, our study finds that most users would leak that they are using Tor when trying to circumvent an advanced censor.
+\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this wouldn't harm users today (as far as we know).
+Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail.
 \item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk.
@@
 \section{Conclusion} 
-We conducted a series of experiments to improve the Tor launcher configuration interface, which helps users circumvent censorship using Tor Browser.
-The qualitative user study interviews a screened 16 participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common struggles, such as difficulty in answering technical questions, feeling unqualified to make technical choices, and not receiving feedback in the event of a failed configuration.
+We conducted a series of experiments to improve the Tor 5.0.3 Tor launcher configuration interface, which helps users circumvent censorship using Tor.
+The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure.
 This feedback is used to guide the redesign of the configuration interface.

### 2016-04-20 pets2017-paper/pets2017-paper.tex
pass through quantitative section

@@
 and done a redesign in an attempt to ameliorate them,
-we did research to quantify the existing problems
-and the impact of our changes.
-This study involved a larger number of users,
-again in simulated censorship environments,
-split between the old and new interface.
+we quantify the existing problems
+and the impact of our changes with a study involving a larger number of users.
+We split participants by simulated censorship environments,
+and between old and new interfaces.
 
 \subsection{Setup}
-We simulated the same three censorship environments from 
-our qualitative user study. Details of the E1, E2, and E3
-censorship environments and what configurations are necessary for a 
-successful connection can be found in Section~\ref{sec:environments}.
-
-We added special instrumentation logging to both interfaces.
-The instrumentation logs recorded every meaningful interaction---every
-button press, every menu selection, every screen change---along with a timestamp.
-The logs enabled us to calculate statistics such as the success rate
-and time spent on each screen.
-We also recorded the participants' computer screens
+We ran our experiment at Xlab, the Experimental Social Science Laboratory at the University of 
+California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
+Though Tor Browser runs on other operating systems,
+testing was only done on Windows, as a byproduct of using Xlab.
+
+We augmented the interfaces with instrumentation 
+to log every meaningful interaction
+(button press, every menu selection, every screen change).
+We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
+start the video recording, and save the logs and videos.
+We recorded the participants' computer screens
 throughout the experiment to capture non-interface activity such as 
 web searching and inspection of system networking settings.
-
-We ran our experiment at Xlab, the Experimental Social Science Laboratory at the University of 
-California, Berkeley.
-The Xlab has 36 Windows~7 laptops, separated from each other by cubicle walls. 
-We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
-start the video recording, and save the logs and videos.
-% Our experiment was not limited by Xlab requirements.
-% [What does that mean?]
-Though Tor Browser runs on other operating systems,
-testing was only done on Windows, as a byproduct of using Xlab.
 
@@
 Data analysis considerations deem 20 participants per combination a 
-minimum to be able to assume normal distributions, and 60 participants
-per interface revision is large enough to have an adequate effect size.
+minimum to assume normal distributions, and 60 participants
+per interface revision is adequate to have a meaningful effect size.
 
@@
 half of our participants from Craigslist to ensure a diverse set of participants. 
-The recruitment text can be found in Appendix~\ref{quantitative-recruitment}. 
+The recruitment text vaguely suggests testing a piece of software, and does not require
+that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
 Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
@@
 The one-hour, multi-participant procedure begins when all participants are sitting at their
-respective computers in Xlab. Each computer is equipped with an old or modified version
+respective computers in Xlab. Each computer is equipped with an instrumented old or new version
 of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
@@
 form, the experiment formally begins. A researcher informs the participants that they are in a
-simulated censorship environment, where some websites and services are blocked. 
-For the full script of what participants have heard, see Appendix~\ref{quantitative-script}. We
-instruct them to visit a sample blocked website on a non-Tor browser of their choice to illustrate 
-the situation.
-
-After illustrating the censorship environment, participants are asked to 
-complete a worksheet that asks to visit one blocked website. 
+simulated censorship environment, instruct them to visit a sample blocked website on a 
+non-Tor browser of their choice to illustrate the situation, and ask them to 
+complete a worksheet that asks to visit one blocked website (Appendix~\ref{quantitative-script}). 
 To mirror the qualitative study, we chose Wikipedia's featured article of the day 
-as the blocked website.
+as the blocked website to visit on their worksheet.
 
@@
 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
-Since our experiment ended after 40 minutes, we chose to assign the max time of 40 minutes to participants who did not succeed.
+Since our experiment ended after 40 minutes, we chose to assign the max time of 40:08 minutes to participants who did not succeed.
 Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
@@
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
-However, this does suggest that users are not less likely to succeed with the new interface based on the changes that were made.
+However, this does suggest that users are equally likely to succeed with the new interface.
 % impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
@@
 
-\subsubsection{Additional information} 
+\subsubsection{Active Configuration Time} 
 We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
@@
 %connect vs configure
-\item {\bfseries Users try the easy path first.}
+\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.
 81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
@@
 % impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} Overall, 57\% of participants' active configuration time was spent on the proxy screens.
-Participants with the new interface spent 31\% of their active time configuring proxies and participants in the old interface spent 63\%.
+\item {\bfseries Users wasted time configuring proxies.} Users believe that they needed proxies to connect.
+This confusion prevented users from configuring their bridges correctly.
+Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies and participants in the old interface who did not receive feedback spent 63\%.
 
@@
 66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
-Flashproxy was also a popular choice.
-Many bridges were never chosen.
+We suspect that flashproxy was a popular choice, because it is listed first in the drop-down menu.
+Many bridges listed at the end of the drop-down menu were not chosen.
 
@@
 \item {\bfseries There were (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
-Only one participant ever saw an error message.
-We are unable to state the efficacy of our attempts to make error messages more understandable and instructive for lack of data.
+There were warnings, but those warnings went largely unnoticed by our participants.
+Across both versions of the interface, only one participant ever saw an error message.
 
@@
 \item {\bfseries People waited a long, long time at the progress bar.}
-From observing videos, participants genuinely wait, dutifully following the directions.   
+Participants spend so much time waiting. Some are dutifully following the directions to wait, while others are lost for what to do and choose to wait in frustration.   
 \end{description}
 
-It is unclear why users with the new interface chose to configure proxies after explicitly being told that they do not need one, if they chose meek bridges based on our advice, and why they chose to wait longer at the progress screen.
+We are unable to state the efficacy of our attempts to make instructive and understandable error messages due to lack of data.
+Users in the new interface were more likely to chose meek bridges, but we cannot say if this can be attributed to the advice we added on the bridge configuration screen to choose a meek bridge after an obfs3 bridge fails.
+It is unclear why users with the new interface chose to configure proxies after explicitly being told that they do not need one.
 
@@
 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
-Although most participants eventually succeeded, 20\% (22 of 116) failed entirely.
+20\% (22 of 116) of participants failed entirely.
 Reasons for failure were determined by a combination of log processing (i.e.
 how much time was spent on a particular screen) and video observation (i.e.
-observing what they searched for online while they were stuck).
+observing what they searched for online).
 \\
@@
 
-Some participants chose to download their own version of Tor.
-We discarded these participants' data and do not count this behavior as a failures or success.
-While some downloaded their own version without trying the provided one on their desktop, others did so after feeling frustrated with the provided version.
-For unfortunate details of where participants downloaded tor when torproject.org was blocked, see Appendix~\ref{tor-downloads}.
+We discarded data on participants who chose to download their own version of Tor Browser online.
+Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
+Appendix~\ref{tor-downloads} gives the unfortunate details the of where Tor was downlaoded when torproject.org was blocked.
 
@@
 64\% of participants who failed their first attempt.
-Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment , 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
+Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
 \item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time on configuring a proxy.
@@
 
-We believe that these changes have can greatly help future users connect to the Tor network.
 We also encourage best practices, such as providing a summary screen to let the user know the configuration settings before connecting, having a checklist progress bar to give users feedback on what network component needs configuring, and rewriting screen text and error messages to be more instructive and understandable.
@@
 In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface.
-We plan to continue our work with Tor developers to integrate changes we found to be helpful.
+We plan to work with Tor developers to integrate helpful changes.
 This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.
 
-We took an approach that optimized for the average case user yet was conservative enough in automation to allow users to connect without leaking that they use Tor.
+We took an approach that optimized for the average case user manually configuring a connection.
 Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
@@
 
-Ideally, we want users in censorship environments across the world to succeed in connecting to the Tor network in a couple of minutes.
-We believe that this is possible with continued improvements to the interface.
+We believe that automation, risk, and identifying struggling users are all integral to making significant improvements to the configuration process.
 

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Manually hack in better scales for the all-participant-edges graphic.
I did this just by editing the original graphic in Inkscape. This
version isn't automatically regenerated, so we have to remember to
re-edit the graphic if the underlying data change.
Spell check.

@@
 
-In addition to tor-specific components, a proxy may be necessary to connect 
+In addition to Tor-specific components, a proxy may be necessary to connect 
 outside the local network in certain managed networks, such as corporate or university networks.
-Configuring a proxy requires providing the proxy protocol, ip address, port and additional optional
+Configuring a proxy requires providing the proxy protocol, IP address, port and additional optional
 fields. There is no assistance or automation with this process. The user must locate the 
@@
 \centering
-\includegraphics{all-participant-edges}
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges-scales}
 \caption{
@@
 Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
-Appendix~\ref{tor-downloads} gives the unfortunate details the of where Tor was downlaoded when torproject.org was blocked.
+Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
 

### 2016-04-23 pets2017-paper/pets2017-paper.tex
More specific.
Move the first cite of "Tor" to the end of the sentence.
So the first sentence can have a little more impact.

@@
 
-Tor~\cite{dingledine2004tor} is an anonymity network that routes traffic through a series of relays
-that makes it difficult to observe the source and destination.
+Tor is an anonymity network that routes traffic through a series of relays
+that makes it difficult to observe the source and destination~\cite{dingledine2004tor}.
 Tor's anonymizing functionality coincidentally also circumvented censorship.
@@
 Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
-The obscure strings under ``Connect with provided bridges'' denote various
+The obscure strings under ``Transport type'' denote various
 built-in circumvention technologies (``pluggable transports'').

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Normalize version numbering.
Tor has its own independent version numbers, so you can't say
"Tor 5.0.3". Don't mention the Tor Browser version number until we start
getting more detailed, in the background.

@@
 This is the first study to examine Tor's usability as a censorship circumvention tool.
-We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
+We evaluate, redesign, and test the Tor configuration interface by
 placing users in simulated censorship environments, instruct them to use Tor
@@
 
-We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
+We evaluate, redesign, and test the Tor configuration interface by
 measuring participants' interactions with the interface in various censorship environments.
@@
 \section{Conclusion} 
-We conducted a series of experiments to improve the Tor 5.0.3 Tor launcher configuration interface, which helps users circumvent censorship using Tor.
+We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, which helps users circumvent censorship using Tor.
 The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure.

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Proofread.

@@
 This is the first user study investigating the usability of Tor as a censorship circumvention tool.
-Our experiments are both a great a case study of observing users circumvent censorship, and a step to help current Tor users by making censorship circumvention easier.
+Our experiments are both a case study of observing users circumvent censorship, and a step toward helping current Tor users by making censorship circumvention easier.
 All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool.
@@
 
-We find that users don't know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
+We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
 We redesign the interface to build users' mental models, provide instructive text, and assist on error.
@@
 \section{Background}
-This section talks about how the configuration interface relates to Tor, what the network components are involved in censorship circumvention, and which configuration settings required to bypass levels of Tor-adverse censorship environments.
+This section talks about how the configuration interface relates to Tor, what network components are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.
 
@@
 sophisticated circumvention mechanisms, asking the user
-to configure two a proxy and bridge (if any) before connecting to Tor
+to configure a proxy and bridge (if necessary) before connecting to Tor
 for the first time. This is the target of our study.
@@
 A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-However, this burdens on the user to grapple with technical concepts such as 
-of bridges, pluggable transports, and proxies and to configure their connection correctly.
+However, this burdens the user to grapple with technical concepts such as 
+bridges, pluggable transports, and proxies and to configure their connection correctly.
 
@@
 the user to choose a group of bridges that use a particular
-pluggable transport. For example, choosing  the hard-coded``obfs3'' option
+pluggable transport. For example, choosing  the hard-coded ``obfs3'' option
 configures a handful of bridges that use obfs3 pluggable transport.
@@
 built-in circumvention technologies (``pluggable transports'').
-Under ``Enter custom bridges'', there is a space to paste in
+Under ``Enter custom bridges,'' there is a space to paste in
 a bridge line, obtained out of band.
@@
 hard-coded bridges in the Tor Launcher source code are required to use a 
-a hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
-blocked Tor relays and hard-coded bridges will be required to configure a meek-bridge (which 
+hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
+blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
 routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
@@
 is the current version being distributed with Tor Browser.
-The second, ``NEW'', is the prototype we revised and redesigned
+The second, ``NEW,'' is the prototype we revised and redesigned
 in order to provide better usability. Below are the empirical and 
@@
 The most common behavior was to configure with the recommended bridge option (obfs3).
-If the recommended one did not work, participants didn't know how to choose another.
+If the recommended one did not work, participants did not know how to choose another.
 
@@
 Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
-When participants did encounter an error message, they did not understand what errors meant (Figure~\ref{fig:error}).\\
+When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\
 
@@
 to log every meaningful interaction
-(button press, every menu selection, every screen change).
+(button presses, menu selections, screen changes).
 We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
@@
 of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
-Each computer was assigned one of the 6 conditions in the beginning of the study. Participants
+Each computer was assigned one of the six conditions in the beginning of the study. Participants
 were assigned to the seats at random, effectively being assigned a configuration launcher and
@@
 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
-Since our experiment ended after 40 minutes, we chose to assign the max time of 40:08 minutes to participants who did not succeed.
+Since our experiment ended after 40 minutes, we chose to assign the maximum time of 40:08 minutes to participants who did not succeed.
 Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
@@
 Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options.
-Participants who were in environments in that the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
+Participants who were in environments in which the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
 Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
@@
 
-Perhaps a more meaningful measurement of time is the amount of times participants actively spent configuring their connection.
+Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection.
 We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen.
@@
 %connect vs configure
-\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.
+\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.
 81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
@@
 % impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} Users believe that they needed proxies to connect.
+\item {\bfseries Users wasted time configuring proxies.} Users believed that they needed proxies to connect.
 This confusion prevented users from configuring their bridges correctly.
@@
 20\% (22 of 116) of participants failed entirely.
-Reasons for failure were determined by a combination of log processing (i.e.
-how much time was spent on a particular screen) and video observation (i.e.
-observing what they searched for online).
+Reasons for failure were determined by a combination of log processing (i.e., how much time was spent on a particular screen) and video observation (i.e., observing what they searched for online).
 \\
@@
 It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-\item {\bfseries Didn't know what to do next.
+\item {\bfseries Did not know what to do next.
 (6/23)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next.
@@
 
-We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.
+We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and were able to speak English.
 
@@
 \begin{description}
-\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this wouldn't harm users today (as far as we know).
+\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this would not harm users today (as far as we know).
 Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail.
@@
 
-Didn't know what to do next (6/23): 
+Did not know what to do next (6/23): 
 \begin{itemize}
@@
 
-Participants that downloaded Tor (5/124): 
+Participants that downloaded Tor Browser (5/124): 
 \begin{itemize}

### 2016-04-23 pets2017-paper/pets2017-paper.tex
It was about Tor Browser 4.5 that our uxsprint2015 changes started happening.
Previously this said "Tor Browser 5.1," which is not a version number
that existed.

Here's an example of one of our tagged tickets getting closed in the Tor
Browser changelog. 4.5a4 is earlier than 4.5, but maybe we should just
mention the stable release.

https://gitweb.torproject.org/builders/tor-browser-bundle.git/tree/Bundle-Data/Docs/ChangeLog.txt
Tor Browser 4.5a4 -- Feb 24 2015
     * Bug 14630: Hide Torbutton's proxy settings tab.

@@
 that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
-some of which influenced changes in Tor Browser version~5.1 and later.
+some of which influenced changes in Tor Browser version~4.5 and later.
 
@@
 Redesigning the configuration interface was a mutual interest.
-In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface.
+In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
 We plan to work with Tor developers to integrate helpful changes.

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Give a year for the 3.5 UI overhaul.

@@
 There have been been no published usability evaluations of
-Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
+Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
 The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 

### 2016-04-23 pets2017-paper/pets2017-paper.tex
Fix the counts per environment in Study 1.
It said, "5 participants for each of the three censorship environments
E1, E2, and E3," which doesn't add up to 16. I got the counts from
sessions/pre/participant-summaries.txt:

E1: P2, P3, P4, P9, P10
E2: P7, P8, P11, P12, P13
E3: P1, P5, P6, P14, P15, P16

@@
 Using established practices from the field of user experience research~\cite{howmanyusers},
-we recruited 5 participants for each of the three censorship environments E1, E2, and E3.
+we recruited 16 participants across the three censorship environments:
+5~in E1, 5~in E2, and 6~in E3.
 We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,

### 2016-04-25 pets2017-paper/pets2017-paper.tex
Explain the × notation in all-participant-edges figure.
david's suggestions

--- 2016-04-23 pets2017-paper/pets2017-paper.tex
@@
 This is the first study to examine Tor's usability as a censorship circumvention tool.
-We evaluate, redesign, and test the Tor configuration interface by
+We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
 placing users in simulated censorship environments, instruct them to use Tor
@@
 We use the results as feedback to redesign the configuration interface.
-A 124-participant quantitative user study tests the impact of our changes
+A 116-participant quantitative user study tests the impact of our changes
 to find that our changes results in a significant reduction 
@@
 
-Tor is an anonymity network that routes traffic through a series of relays
-that makes it difficult to observe the source and destination~\cite{dingledine2004tor}.
+Tor~\cite{dingledine2004tor} is an anonymity network that routes traffic through a series of relays
+that makes it difficult to observe the source and destination.
 Tor's anonymizing functionality coincidentally also circumvented censorship.
@@
 This is the first user study investigating the usability of Tor as a censorship circumvention tool.
-Our experiments are both a case study of observing users circumvent censorship, and a step toward helping current Tor users by making censorship circumvention easier.
+Our experiments are both a great a case study of observing users circumvent censorship, and a step to help current Tor users by making censorship circumvention easier.
 All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool.
@@
 
-We evaluate, redesign, and test the Tor configuration interface by
+We evaluate, redesign, and test the Tor 5.0.3 configuration interface by
 measuring participants' interactions with the interface in various censorship environments.
@@
 
-We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
+We find that users don't know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
 We redesign the interface to build users' mental models, provide instructive text, and assist on error.
@@
 that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
-some of which influenced changes in Tor Browser version~4.5 and later.
+some of which influenced changes in Tor Browser version~5.1 and later.
 
@@
 \section{Background}
-This section talks about how the configuration interface relates to Tor, what network components are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.
+This section talks about how the configuration interface relates to Tor, what the network components are involved in censorship circumvention, and which configuration settings required to bypass levels of Tor-adverse censorship environments.
 
@@
 sophisticated circumvention mechanisms, asking the user
-to configure a proxy and bridge (if necessary) before connecting to Tor
+to configure two a proxy and bridge (if any) before connecting to Tor
 for the first time. This is the target of our study.
@@
 A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-However, this burdens the user to grapple with technical concepts such as 
-bridges, pluggable transports, and proxies and to configure their connection correctly.
+However, this burdens on the user to grapple with technical concepts such as 
+of bridges, pluggable transports, and proxies and to configure their connection correctly.
 
@@
 the user to choose a group of bridges that use a particular
-pluggable transport. For example, choosing  the hard-coded ``obfs3'' option
+pluggable transport. For example, choosing  the hard-coded``obfs3'' option
 configures a handful of bridges that use obfs3 pluggable transport.
@@
 Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
-The obscure strings under ``Transport type'' denote various
+The obscure strings under ``Connect with provided bridges'' denote various
 built-in circumvention technologies (``pluggable transports'').
-Under ``Enter custom bridges,'' there is a space to paste in
+Under ``Enter custom bridges'', there is a space to paste in
 a bridge line, obtained out of band.
@@
 
-In addition to Tor-specific components, a proxy may be necessary to connect 
+In addition to tor-specific components, a proxy may be necessary to connect 
 outside the local network in certain managed networks, such as corporate or university networks.
-Configuring a proxy requires providing the proxy protocol, IP address, port and additional optional
+Configuring a proxy requires providing the proxy protocol, ip address, port and additional optional
 fields. There is no assistance or automation with this process. The user must locate the 
@@
 hard-coded bridges in the Tor Launcher source code are required to use a 
-hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
-blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
+a hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
+blocked Tor relays and hard-coded bridges will be required to configure a meek-bridge (which 
 routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
@@
 is the current version being distributed with Tor Browser.
-The second, ``NEW,'' is the prototype we revised and redesigned
+The second, ``NEW'', is the prototype we revised and redesigned
 in order to provide better usability. Below are the empirical and 
@@
 The most common behavior was to configure with the recommended bridge option (obfs3).
-If the recommended one did not work, participants did not know how to choose another.
+If the recommended one did not work, participants didn't know how to choose another.
 
@@
 Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
-When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\
+When participants did encounter an error message, they did not understand what errors meant (Figure~\ref{fig:error}).\\
 
@@
 to log every meaningful interaction
-(button presses, menu selections, screen changes).
+(button press, every menu selection, every screen change).
 We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
@@
 of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
-Each computer was assigned one of the six conditions in the beginning of the study. Participants
+Each computer was assigned one of the 6 conditions in the beginning of the study. Participants
 were assigned to the seats at random, effectively being assigned a configuration launcher and
@@
 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
-Since our experiment ended after 40 minutes, we chose to assign the maximum time of 40:08 minutes to participants who did not succeed.
+Since our experiment ended after 40 minutes, we chose to assign the max time of 40:08 minutes to participants who did not succeed.
 Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
@@
 Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options.
-Participants who were in environments in which the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
+Participants who were in environments in that the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
 Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
@@
 Users in the wild will likely not be motivated to configure their connection for 40 minutes.
-Table~\ref{table:less_time} shows that if users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect.
+If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect.
 Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments will be unable to connect.
@@
 \includegraphics{time_to_success_ecdf}
-\caption{
-Cumulative success rates over time, by censorship environment and interface.
-We stopped participants after 40 minutes. Here, those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
-}
-\label{fig:time_to_success_ecdf}
-\end{figure}
-
-\begin{table}
-\centering 
 	% Generated by info.R:
@@
 	\end{tabular}
-\caption{This Table shows what the success rate would have been
-at different cutoff times.
+\caption{
+Cumulative success rates over time, by censorship environment and interface.
+We stopped participants after 40 minutes. Here, those who did not finish were assigned
+an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
 For example, every E1-NEW participant finished within 90 seconds,
@@
 After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
-After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.}
-\label{table:less_time}
-\end{table}
+After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
+}
+\label{fig:time_to_success_ecdf}
+\end{figure}
 
@@
 \centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges-scales}
+\includegraphics{all-participant-edges}
 \caption{
@@
 
-Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection.
+Perhaps a more meaningful measurement of time is the amount of times participants actively spent configuring their connection.
 We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen.
@@
 %connect vs configure
-\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.
+\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.
 81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
@@
 % impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} Users believed that they needed proxies to connect.
+\item {\bfseries Users wasted time configuring proxies.} Users believe that they needed proxies to connect.
 This confusion prevented users from configuring their bridges correctly.
@@
 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
-20\% (22 of 116) of participants failed entirely.
-Reasons for failure were determined by a combination of log processing (i.e., how much time was spent on a particular screen) and video observation (i.e., observing what they searched for online).
+20\% (21 of 116) of participants failed entirely.
+Reasons for failure were determined by a combination of log processing (i.e.
+how much time was spent on a particular screen) and video observation (i.e.
+observing what they searched for online).
 \\
@@
 \item {\bfseries Only connected directly.
-(8/23)} These participants tried a direct connection.
+(7/21)} These participants tried a direct connection.
 When that failed, they tried the same configuration, over and over, without trying other configurations, no matter how many times they failed.
 It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-\item {\bfseries Did not know what to do next.
-(6/23)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next.
+\item {\bfseries Didn't know what to do next.
+(6/21)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next.
 They often tried those configurations again or gave up.
-\item {\bfseries Thought that they needed a proxy (5/23)} After a couple failed attempts, these participants assumed that they needed a proxy.
+\item {\bfseries Thought that they needed a proxy (5/21)} After a couple failed attempts, these participants assumed that they needed a proxy.
 They spent the time trying to configure a proxy, usually without trying other bridges.
-\item {\bfseries Used the bridges auto-responder incorrectly (3/23)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button.
+\item {\bfseries Used the bridges auto-responder incorrectly (2/21)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button.
 However, they all failed to get a response.
@@
 Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
-Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
+Appendix~\ref{tor-downloads} gives the unfortunate details the of where Tor was downlaoded when torproject.org was blocked.
 
@@
 
-We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and were able to speak English.
+We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and are able to speak English.
 
@@
 Redesigning the configuration interface was a mutual interest.
-In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
+In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface.
 We plan to work with Tor developers to integrate helpful changes.
@@
 \begin{description}
-\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this would not harm users today (as far as we know).
+\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this wouldn't harm users today (as far as we know).
 Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail.
@@
 
-%\section {Acknowledgments}
-%{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
-%{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
+\section {Acknowledgments}
+I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruting.
+I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
+
+\section {Resources} 
+For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
+
+\noindent https://github.com/lindanlee/circumvention-ux-tor
 
 \section{Conclusion} 
-We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, which helps users circumvent censorship using Tor.
+We conducted a series of experiments to improve the Tor 5.0.3 Tor launcher configuration interface, which helps users circumvent censorship using Tor.
 The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure.
@@
 
-We test the impact of our changes on 124 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
+We test the impact of our changes on 116 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
 We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.
@@
 
-Only tried to connect directly (8/23): 
+Only tried to connect directly (7/21): 
 \begin{itemize}
@@
 \item E3-NEW-X17-20160323-1400
-\item E3-OLD-X06-20160328-1400
 \item E3-OLD-X06-20160330-1600
@@
 
-Did not know what to do next (6/23): 
+Didn't know what to do next (6/21): 
 \begin{itemize}
@@
 
-Thought that they needed a proxy (5/23): 
+Thought that they needed a proxy (5/21): 
 \begin{itemize}
@@
 
-Used the bridges auto-responder incorrectly (3/23): 
+Used the bridges auto-responder incorrectly (2/21): 
 \begin{itemize}
@@
 \item E3-OLD-X12-20160325-1400 (Fig.~\ref{autoresponder2})
-\item E3-OLD-X24-20160328-1400 (Fig.~\ref{autoresponder3})
 \end{itemize}
@@
 
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
-\caption{The message that E3-OLD-X24-20160328-1400 sent to the bridge auto-responder.
-A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
-Since this request was incorrectly formatted, there was no reply.}
-\label{autoresponder3}
-\end{figure}
-
 \section{Tor Downloads}
@@
 
-Participants that downloaded Tor Browser (5/124): 
+Participants that downloaded Tor (5/124): 
 \begin{itemize}

### 2016-04-25 pets2017-paper/pets2017-paper.tex
nathan's suggestions.

--- 2016-04-23 pets2017-paper/pets2017-paper.tex
@@
 become a widely-used censorship circumvention tool.
-This is the first study to examine Tor's usability as a censorship circumvention tool.
+This is the first study to examine Tor's usability in this role.
 We evaluate, redesign, and test the Tor configuration interface by
-placing users in simulated censorship environments, instruct them to use Tor
+placing users in simulated censorship environments, instructed them to use Tor
 to circumvent censorship, and measuring their interactions with the interface.
@@
 We use the results as feedback to redesign the configuration interface.
-A 124-participant quantitative user study tests the impact of our changes
-to find that our changes results in a significant reduction 
-in the spent configuring a connection, while maintaining the same rate of success. We
+A 116-participant quantitative user study tests the impact of our changes.
+We find that our changes results in a significant reduction 
+in the time spent configuring a connection, while maintaining the same rate of success. We
 conclude with recommendations for changes to the current configuration interface and discuss
@@
 Tor is an anonymity network that routes traffic through a series of relays
-that makes it difficult to observe the source and destination~\cite{dingledine2004tor}.
-Tor's anonymizing functionality coincidentally also circumvented censorship.
-Eventually, censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for that reason~\cite{winter2012great}.
-Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network indistinguishable, and advanced techniques to resist blocking.
+that make it difficult to observe the source and destination~\cite{dingledine2004tor}.
+Tor's anonymizing functionality also circumvented censorship.
+Censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for this reason~\cite{winter2012great}.
+Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.
 
 This is the first user study investigating the usability of Tor as a censorship circumvention tool.
-Our experiments are both a case study of observing users circumvent censorship, and a step toward helping current Tor users by making censorship circumvention easier.
-All Tor users will benefit from improving the configuration interface, and therefore increasing the adoption of Tor as a censorship circumvention tool.
-Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased the number of overall users on the Tor network~\cite{dingledine2006anonymity}.
+Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier.
+All Tor users will benefit from improving the configuration interface, therefore increasing the adoption of Tor as a censorship circumvention tool.
+Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
 
@@
 behavioral patterns and failure cases with the interface through user observations
-and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, data-centric user study
+and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, many-to-one experiment
 that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).
@@
 We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
-We redesign the interface to build users' mental models, provide instructive text, and assist on error.
-These changes decreased the time participants spent configuring their connections, with no decrease in success rates.
+We redesign the interface to build users' mental models, make the text easier to understand, and provide messages to assist users on error.
+Our changes decreased the time participants spent configuring their connections, but there was no difference in success rates.
+We expected the success rate to increase after providing suggestions on what to do next with error messages, but this had no effect since only 1 of 116 users encountered an error message.
 We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.
@@
 Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
+The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
 that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
@@
 without focusing on specific features in isolation.
-We choose to focus our study on 
+We focus our study on 
 the browser's configuration interface, which guides users through setting up network components required to circumvent censorship.
-This study examines that interface with a focus on circumvention,
-though we believe that this research and the changes we recommend
-can be beneficial for non-circumventing users as well.
 
 \section{Background}
-This section talks about how the configuration interface relates to Tor, what network components are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.
+This section discusses the configuration interface relates to Tor, what network components that are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.
 
@@
 to configure a proxy and bridge (if necessary) before connecting to Tor
-for the first time. This is the target of our study.
+for the first time. This is the object of our study.
 
@@
 A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-However, this burdens the user to grapple with technical concepts such as 
-bridges, pluggable transports, and proxies and to configure their connection correctly.
+However, this requires the user to grapple with technical concepts such as 
+bridges, pluggable transports, and proxies.
 
 \subsection{Bridges, Pluggable Transports, and Proxies} 
-Internet censors seek to block network resources, such as websites, through 
+Internet censors seek to block network resources through 
 a variety of means, such as falsifying DNS responses, blocking IP addresses, 
@@
 the user to choose a group of bridges that use a particular
-pluggable transport. For example, choosing  the hard-coded ``obfs3'' option
+pluggable transport. For example, choosing  the hard-coded obfs3 option
 configures a handful of bridges that use obfs3 pluggable transport.
 Some censors block the IP addresses of the hard-coded bridges by looking
-at the source code for those addresses (except ``flashproxy'' and ``meek,'' which work differently).
+at the source code for those addresses (except flashproxy and meek).
 If the built-in bridges do not work, a user can obtain bridge lines
 through out-of-band channels, for instance by email~\cite{bridgedb}.
-
 Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
 options at the time of the study and lists the available pluggable transports.
-Some transports connect directly to a static IP address,
-obfuscating traffic to defeat on-the-wire identification;
-they rely on the secrecy of their IP addresses for their effectiveness.
-These include ``fte'' and ``fte-ipv6''~\cite{fte},
-which make Tor look like another protocol such as HTTP; and
-``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
-which encrypt Tor to look like random noise.
-Other transports work differently and do not depend on connecting to a static IP address:
-``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
-and the three ``meek''~\cite{fifield2015blocking} options route traffic
-through content delivery networks.
+%Some transports connect directly to a static IP address,
+%obfuscating traffic to defeat on-the-wire identification;
+%they rely on the secrecy of their IP addresses for their effectiveness.
+%These include ``fte'' and ``fte-ipv6''~\cite{fte},
+%which make Tor look like another protocol such as HTTP; and
+%``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
+%which encrypt Tor to look like random noise.
+%Other transports work differently and do not depend on connecting to a static IP address:
+%``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
+%and the three ``meek''~\cite{fifield2015blocking} options route traffic
+%through content delivery networks.
 
@@
 Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
-The obscure strings under ``Transport type'' denote various
+The options under ``Transport type'' denote various
 built-in circumvention technologies (``pluggable transports'').
@@
 In addition to Tor-specific components, a proxy may be necessary to connect 
-outside the local network in certain managed networks, such as corporate or university networks.
-Configuring a proxy requires providing the proxy protocol, IP address, port and additional optional
+outside the local network in certain managed environments, such as corporate or university networks.
+Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
 fields. There is no assistance or automation with this process. The user must locate the 
-proxy information and correctly format this information into the configuration interface.
-
-Technically the Tor client, pluggable transport bridge, and proxy are all
-proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
-as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
-censor's control.
+proxy information and correctly input this information into the configuration interface.
+
+%Technically the Tor client, pluggable transport bridge, and proxy are all
+%proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
+%as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
+%censor's control.
 
@@
 can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
-The minimum amount of configuration required, and therefore, the set of valid configuration settings,
+The minimum amount of configuration required, therefore, the set of valid configuration settings,
 vary depending on the censorship environment. At the maximum, users will need to know or find out:\\
@@
 	\item{Which groups of hard-coded bridges work in their environment} 
-	\item{If no hard-coded bridges work, how to get and enter in a custom bridge} 
+	\item{If no hard-coded bridges work, how to get and enter a custom bridge} 
 	\item{Whether a proxy is required to access the Internet}
@@
 Uncensored users and users in censorship environments that do not explicitly 
-block Tor do not require a bridge nor a proxy and can bypass the configuration process.
-Users in censorship environments that explicitly block Tor but has not blocked the 
+block Tor do not require a bridge or a proxy and can bypass the configuration process.
+Users in censorship environments that explicitly block Tor but have not blocked the 
 hard-coded bridges in the Tor Launcher source code are required to use a 
@@
 blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
-routes traffic through content delivery networks and therefore resists blocking via collateral damage) or 
+routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
 configure a custom bridge to connect to Tor.
@@
 is the current version being distributed with Tor Browser.
-The second, ``NEW,'' is the prototype we revised and redesigned
+The second, ``NEW,'' is the prototype we designed
 in order to provide better usability. Below are the empirical and 
@@
 Our empirical evaluation criteria for the Tor Browser configuration
-interface are from common metrics that measure ease of use: \\
+interface are based on common metrics that measure ease of use: \\
 
@@
     \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
-    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful connection to Tor.
-    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor. 
+    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for a the connection to bootstrap.
+    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
 \end{enumerate}
 
-A heuristic evaluation is a rule-based evaluation based on time-tested standards
+A heuristic evaluation is based on standards
 in the user interface design community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
-and other industry standards to form the following heuristic evaluation criteria: \\
+to form the following heuristic evaluation criteria: \\
 
@@
 \label{sec:environments}
-For our experiments, we use (modified versions of) Tor Browser~5.0.3, 
+For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
 the most recent stable release at the time~\cite{torbrowser-503}.
@@
 The E2 environment blocks websites as in E1;
-and additionally blocks the IP addresses of public Tor relays
+it additionally blocks the IP addresses of public Tor relays
 and directory authorities, simulating a censor that knows
@@
 In this environment, simply clicking ``Connect'' will not work;
-participants had at least to select a built-in bridge
+participants had to select a built-in bridge
 (any type other than ``flashproxy'' would work).
@@
 what common problems may be. We did this by observing participants using 
-the interface to circumvent censorship, and interviewing them about
+the interface to circumvent censorship and interviewing them about
 their experience.  Our observations during this study guided us in
-redesigning interface and provided hypotheses to test in our quantitative study.
+redesigning the interface and provided hypotheses to test in our quantitative study.
 
@@
 The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
-We selected participants to have at least one person who has never heard of Tor, 
-at least one person who has only heard of Tor, and exactly one person who has previously used Tor in each
-censorship environment. We tried to evenly distribute any participants who had technical
+We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
+at least one person who has only heard of Tor, and exactly one person who has previously used Tor
+. We tried to evenly distribute any participants who had technical
 expertise or used particular security tools throughout the censorship environments.
@@
 \subsection{Procedure}
-The one-hour, single-participant procedure begins when a participant enters a small 
+The one-hour, single-participant procedure began when a participant enters a small 
 room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
 Each participant is informed of the risks and purpose of the study.
-A researcher reads a script that informs the participant of the simulated censorship environment and
-instructs them to visit sample blocked and unblocked websites
+A researcher read a script that informed the participant of the simulated censorship environment and
+instruct them to visit sample blocked and unblocked websites
 in a standard browser, to show what it looks like when a site is blocked (Appendix~\ref{qualitative-script}).
-Then, the participant is asked to  complete a worksheet that gives information
-on their censorship environment and instructs them
+Then, the participant was asked to complete a worksheet that gives information
+on their censorship environment and instructed them
 to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
-The worksheet informs the participant that the network is censored,
-but does not give details of what services and websites are specifically blocked.
+The worksheet informed the participant that the network is censored,
+but did not give details of what services and websites are specifically blocked.
 Participants were able to visit the unblocked website using any familiar browser,
@@
 our goal was to evaluate the user interface, not to test users with a browsing task.
-After giving the instructions, the researchers stepped out of the room so that there was no interaction
+After instructions, the researchers stepped out of the room so that there was no interaction
 between the participant and researcher for the rest of the session.
@@
 
-We refreshed a list of Tor relay IP addresses and added them
-to a firewall blacklist before each session.
-In this first study, we neglected to block the IP addresses
-of the Tor directory authorities, which are the first hosts
-a client contacts when initiating a non-bridge connection.
-This, combined with new relays appearing in the network on an hourly basis,
-enabled a small number of participants to succeed with
-a direct connection when we expected them to fail.
-We fixed this problem in our second study by blocking the directory authorities.
-
 After participants completed the browsing tasks or ran out of time,
@@
 We asked three standard questions asking about their general experience, 
-confusing interface features, and soliciting feedback for improvements. We followed up
-with specific per-participant questions prompted from watching their screen. 
+confusing interface features, and feedback for improvements. We followed up
+with specific questions prompted from watching their screen. 
 This was to verify any hypotheses we had (e.g. ``they did not know what to do on window~3'').
@@
 \noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
-On the bridge configuration screen, participants were intimidated by the names of the bridge transports.
+On the bridge configuration screen, participants were confused by the names of the bridge transports.
 The most common behavior was to configure with the recommended bridge option (obfs3).
@@
 \noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
-Unfortunately, many mistakes did not result in error messages, bu warnings that went unnoticed.
+Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
 When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\
@@
 \noindent {\bfseries Challenge 5: Users assume they are wrong when they are right.}
-If users chose particular wrong configurations (i.e. a syntactically valid but nonfunctional proxy), they would be waiting for an indefinite period of time. 
-\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-
-The progress bar also has a bug that causes it to update itself only when the level of progress increases.
+The progress bar has a bug that causes it to update only when the level of progress increases.
 If progress bar reaches a 90\% and fails, the next attempt will apparently have regressed to 0\% and remain there until the progress reaches >90\%.
@@
 \pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
+\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
 
@@
 All of our participants who failed to connect (5 of 16) failed for this reason.
-Many mistakenly assumed that they needed a proxy upon failure, because the interface passively redirects to the proxy screen (the last screen) after failure.
+Many mistakenly assumed that they needed a proxy upon failure, because the interface redirects to the proxy screen (the last screen) after failure.
 
@@
 
-From interviewing our participants, we found that these challenges result because users are not familiar with technical or Tor-specific terms, feedback on progress or an errors were inconsistent, and the interface did not instruct users on what to do in the event of a failure.
+From interviewing our participants, we found that these challenges result because users are not familiar with technical or Tor-specific terms, feedback on progress or errors was inconsistent, and the interface did not instruct users on what to do in the event of a failure.
 
@@
 
-From the result of our qualitative user study, we see that many users struggle with the configuration process. 
+From the results of our qualitative user study, we see that many users struggle with the configuration process. 
 The Tor Browser configuration interface does not adequately meet our criteria from Section~\ref{sec:goals} of
@@
 \item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users were required to answer were too technical for the average user. 
-\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect to the Tor network or while they are connecting to the Tor network.
+\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users are required to answer are too technical for the average user. 
+\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect or while they are connecting to the Tor network.
  \end{itemize}
@@
 
-To address these three aforementioned user interaction problems, we made the following three changes to the configuration interface:  \\
+To address these problems, we made the following three changes to the configuration interface:  \\
 
@@
 \setcounter{enumi}{3}
-\item {\bfseries Added guidance on choosing connect versus configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
+\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
 \item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.
@@
 Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
-With auto-detection, configuring a proxy before a bridge burden users less than before.
+With auto-detection, configuring a proxy before a bridge burdens users less than before.
 \item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
@@
 We recruited 124 participants, about 20 for each
-of the six combinations of censorship environment
-and interface revision.
+condition.
 Data analysis considerations deem 20 participants per combination a 
@@
 \subsection{Procedure}
-The one-hour, multi-participant procedure begins when all participants are sitting at their
-respective computers in Xlab. Each computer is equipped with an instrumented old or new version
+The one-hour, multi-participant procedure began when all participants sat at their
+respective computers in Xlab. Each computer was equipped with an instrumented old or new version
 of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
 Each computer was assigned one of the six conditions in the beginning of the study. Participants
-were assigned to the seats at random, effectively being assigned a configuration launcher and
-simulated censorship environment combination at random.
-
-Participants are firstly informed of the risks of the study and consenting to data collection.  At
-this time, participants are given the chance to leave the laboratory if they do not consent to 
-the experiment conditions. When every participant left in the room has turned in their consent
-form, the experiment formally begins. A researcher informs the participants that they are in a
-simulated censorship environment, instruct them to visit a sample blocked website on a 
-non-Tor browser of their choice to illustrate the situation, and ask them to 
+were assigned to a simulated censorship environment combination at random.
+
+A researcher informed the participants that they are in a
+simulated censorship environment, instructed them to visit a sample blocked website on a 
+non-Tor browser of their choice to illustrate the situation, and asked them to 
 complete a worksheet that asks to visit one blocked website (Appendix~\ref{quantitative-script}). 
@@
 about 40 minutes to complete their worksheet.
-(In our analysis we defined the cutoff time to be 40 minutes and 8~seconds
-in order to include a participant who finished at the wire.)
-The participants do not know the details of their censorship environment,
+The participants did not know the details of their censorship environment,
 only that they are actively being censored. Participants needed to configure Tor Browser to 
@@
 collecting their demographics. All users were instructed to sit until the end of the experiment,
-regardless of when they had completed their task. After the 40 minutes were up, 
+regardless of when they had completed their task. After the 40 minutes, 
 participants were officially informed that their time was up, and were given their payment of 
@@
 38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
-Since our experiment ended after 40 minutes, we chose to assign the maximum time of 40:08 minutes to participants who did not succeed.
 Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
@@
 \subsubsection{Rate of Success} 
-5 more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network.
+Five more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network.
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
@@
 
-Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful bootstrap in each environment and interface combination.
+Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.
 Note that only four of the default bridges were used to connect successfully for the first time.
-Users avoid making decisions when a recommendation is given and tend to avoid/fail with more advanced options.
-Participants who were in environments in which the recommended bridge (obfs3) worked did not configure another bridge, not taking advantage of the various default bridges available to them.
+Users avoid making decisions when a recommendation is given and tend to avoid or fail with more advanced options.
+Participants who were in environments where the recommended bridge (obfs3) worked did not successfully configure another bridge.
 Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
@@
 a different bridge before obfs3.
-All of the successful E3 participants, but one,
+All of the successful E3 participants but one
 used one of the meek bridges.
@@
 Users in the wild will likely not be motivated to configure their connection for 40 minutes.
-Table~\ref{table:less_time} shows that if users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments will be unable to connect.
-Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments will be unable to connect.
+If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
+Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
 Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment.
@@
 The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes.
+except for those we cut off after approximately 40 minutes
+(marked with a $\times$).
 }
@@
 Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.
-Participants using the new interface and old interface waited spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively.
+Participants using the new interface and old interface spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively.
 We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen which keeps the users waiting indefinitely, which were present in both versions of the interface.
@@
 	\end{tabular}
-\caption{overall time} 
+\caption{Fraction of time spent on each screen.
+Participants spent most of their time on the progress screen, waiting.
+Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
+although none of the censorship environments required a proxy.
+Participants spent less time on the proxy screen
+in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
 \label{table:overall_time}
@@
 \subsection{Discussion} 
-This section talks about general trends in user behavior, common failure cases, and our recommendations for 
+This section details general trends in user behavior, common failure cases, and our recommendations for 
 improving the Tor configuration interface.
@@
 %connect vs configure
-\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays, and just try the easy option to connect directly to the Tor network first, leaking that they are connecting to Tor on the network.
+\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays and try the easy option of connecting directly to the Tor network first, leaking that they are connecting to Tor on the network.
 81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
+It's critical to note that the participants did not believe the interface when it informed them that they did not need a proxy.
 
@@
 66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
-We suspect that flashproxy was a popular choice, because it is listed first in the drop-down menu.
+We suspect that flashproxy was a popular choice because it is listed first in the drop-down menu.
 Many bridges listed at the end of the drop-down menu were not chosen.
@@
 \item {\bfseries People waited a long, long time at the progress bar.}
-Participants spend so much time waiting. Some are dutifully following the directions to wait, while others are lost for what to do and choose to wait in frustration.   
+Some dutifully followed the directions to wait, while others are lost for what to do and choose to wait in frustration. Either way, we think that people spent too much time waiting. 
 \end{description}
@@
 We are unable to state the efficacy of our attempts to make instructive and understandable error messages due to lack of data.
-Users in the new interface were more likely to chose meek bridges, but we cannot say if this can be attributed to the advice we added on the bridge configuration screen to choose a meek bridge after an obfs3 bridge fails.
-It is unclear why users with the new interface chose to configure proxies after explicitly being told that they do not need one.
+We do not understand why users with the new interface choose to configure proxies after explicitly being told that they do not need one.
+We notice that users in the new interface were more likely to chose meek bridges.
+10 users in the new interface chose a meek-bridge as their second bridge, whereas only 5 users in the old interface did.
+However, we cannot say if this can be attributed to the advice we added on the bridge configuration screen, due to the small sample size.
 
@@
 Failure is common.
+20\% (21 of 116) of participants failed entirely.
 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
-20\% (22 of 116) of participants failed entirely.
-Reasons for failure were determined by a combination of log processing (i.e., how much time was spent on a particular screen) and video observation (i.e., observing what they searched for online).
+Reasons for failure were determined by a combination of log processing (i.e.
+how much time was spent on a particular screen) and video observation (i.e.
+observing what they searched for online).
 \\
@@
 \item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor.
-Automating the configuration process thereafter will have no increase in risk, bu can help a majority of users.
-64\% of participants who failed their first attempt.
+Automating the configuration process thereafter will have no increase in risk, but can help a majority of users; 64\% of participants who failed their first attempt.
 Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
-\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time on configuring a proxy.
+\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time configuring a proxy.
 Only a small fraction of the Internet population requires a proxy to connect to the Internet.
@@
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
-Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this effect should affect all of our conditions equally.
-
-Our study was conducted in an inorganic setting, which can cause our participants to be under or over-motivated.
+Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this should affect all of our conditions equally.
+
+We refreshed a list of Tor relay IP addresses and added them
+to a firewall blacklist before each session.
+In the first study, we neglected to block the IP addresses
+of the Tor directory authorities, which are the first hosts
+a client contacts when initiating a non-bridge connection.
+This, combined with new relays appearing in the network on an hourly basis,
+enabled a small number of participants to succeed with
+a direct connection when we expected them to fail.
+We believe this is acceptable, since 
+the first study was not used to quantify failures or successes, 
+but to explore possible problems.
+We fixed this problem in our second study by blocking the directory authorities.
+
+Our study was conducted in a laboratory setting, which can cause our participants to be under or over-motivated.
 Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website or service.
-The nature of the experiment places social pressure to attempt connect for the whole duration of the session, whereas participants may have given up earlier if they were not in an organic setting.
+The nature of the experiment places social pressure to attempt connect for the whole duration of the session, whereas participants may have given up earlier if they were not in a real-world setting.
 
@@
 We took an approach that optimized for the average case user manually configuring a connection.
-Additional user studies that focus specifically on users in heavily censored environments, or increasing the amount of automation in the configuration process can yield to higher rates of success and faster time to success.
+Additional user studies that focus specifically on users in heavily censored environments or increasing the amount of automation in the configuration process can yield higher rates of success and faster time to success.
 We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.\\
@@
 \begin{description}
-\item{\bfseries Automate the configuration.} Complete automation and network probing sounds like a radical idea, but this would not harm users today (as far as we know).
-Most users would leak that they are using Tor when trying to circumvent an advanced censor, since most first attempts to connect fail.
-\item{\bfseries Ask about the risk.} Ask the users if they would be at risk if the process was automated, and automate the configuration process for all who are not at risk.
-The ones at risk will configure manually.
-The complication with this approach is that users may not be qualified to answer this question or may not trust Tor to answer honestly.
+\item{\bfseries Automate the configuration.} Complete automation of the configuration process, which involves network probing, would not harm users today (as far as we know).
+Our study finds that most users fail on the first try when trying to circumvent an advanced censor, so this automation may not increase the number of users who leak that they are connecting to the Tor network.
+\item{\bfseries Ask about the risk.} Automating the configuration process for all who are not at risk and offering manual configuration to those who would like to be more cautious is an alternative to complete automation.
+The complication with this approach is that we would need to ask the users about the risk involved with connecting to the Tor network.
+Users may not be qualified to answer this question or may not trust Tor with this information.
 \item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not.
@@
 
-We believe that automation, risk, and identifying struggling users are all integral to making significant improvements to the configuration process.
-
-%\section {Acknowledgments}
-%{\color {red} Rowilma del Castillo for setting up Xlab, Nima Fatemi, Isabela Bagueros, Georg Koppen, and the UX team for giving feedback, and Cecile Basnage for reviewing the UI of circumvention tools.}
-%{\color {red} Tor Browser devs for taking our recommendations to heart and implementing changes.}
+We believe that automation, asking about risk, and identifying struggling users are all integral to making significant improvements to the configuration process.
+
+\section {Acknowledgments}
+I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruting.
+I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
+
+\section {Resources} 
+For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
+
+\noindent https://github.com/lindanlee/circumvention-ux-tor
 
@@
 We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, which helps users circumvent censorship using Tor.
-The qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection, such as confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure.
+A qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection.
+These include confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure.
 This feedback is used to guide the redesign of the configuration interface.
 
-We test the impact of our changes on 124 participants in the quantitative user study to find that that the changes made cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
+We test the impact of our changes on 116 participants in a quantitative user study to find that that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
 We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.
@@
 \label{autoresponder2}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-155924-bridgeresponder.png}
-\caption{The message that E3-OLD-X24-20160328-1400 sent to the bridge auto-responder.
-A correct message is a ``get bridges'' in the body of the message, with any non-empty subject.
-Since this request was incorrectly formatted, there was no reply.}
-\label{autoresponder3}
 \end{figure}

### 2016-04-26 pets2017-paper/pets2017-paper.tex
serge's suggestions.

@@
 measuring participants' interactions with the interface in various censorship environments.
-The first user study is a small-scale, one-on-one experiment that collected 
+The first user study is a small-scale, qualitative experiment that collected 
 behavioral patterns and failure cases with the interface through user observations
-and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, many-to-one experiment
+and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, quantitative experiment
 that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).
@@
 
-There have been been no published usability evaluations of
+We do not know of any published usability evaluations of
 Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
@@
 in favor of guided manual configuration to give users agency in configuring their connection. 
+Automatic configuration through network probing may put some users in certain regimes at risk. 
 A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
@@
 Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
-The options under ``Transport type'' denote various
+Users are not familiar with the options under ``Transport type'' denote various
 built-in circumvention technologies (``pluggable transports'').
@@
     \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
-    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for a the connection to bootstrap.
+    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
     \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
@@
 
+% E1
+% (Representative of countries such as France and Australia.)
+% E2 
+% (Representative of countries such as Tunisia.)
+% E3
+% (Representative of countries such as China and Syria.)
+
 \begin{description}
 \item[E1: Mild censorship]
+(Representative of countries such as France and Australia.)
 The E1 environment only blocks some websites,
@@
 \item[E2: Intermediate censorship]
+(Representative of countries such as Tunisia.)
 The E2 environment blocks websites as in E1;
@@
 \item[E3: Comprehensive censorship]
+(Representative of countries such as China and Syria.)
 The E3 environment blocks websites and Tor relays as in E1 and E2;
@@
 We recruited 124 participants, about 20 for each
-condition.
-Data analysis considerations deem 20 participants per combination a 
-minimum to assume normal distributions, and 60 participants
-per interface revision is adequate to have a meaningful effect size.
-
-We recruited half of our users from Craigslist, and half of our participants from 
+condition. We recruited half of our users from Craigslist, and half of our participants from 
 the Xlab participant pool. Although Xlab participants are not limited to UC Berkeley students and staff,
@@
 
-\subsubsection{Rate of Success} 
-Five more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network.
-Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
-However, this does suggest that users are equally likely to succeed with the new interface.
-% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
-%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)
-
-Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.
-Note that only four of the default bridges were used to connect successfully for the first time.
-Users avoid making decisions when a recommendation is given and tend to avoid or fail with more advanced options.
-Participants who were in environments where the recommended bridge (obfs3) worked did not successfully configure another bridge.
-Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
+\subsubsection{Active Configuration Time} 
+We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
+Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
+The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
+
+\begin{figure*}
+\centering
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges-scales}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The narrow black lines show the times when the configuration interface
+was not running; i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes
+(marked with a $\times$).
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
+The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
+Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.
+Participants using the new interface and old interface spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively.
+We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen, which were present in both versions of the interface.
 
@@
 \centering
-% Generated by attempts.R, and manually reordered:
-\begin{tabular}{r c c c c c c}
-& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
-no bridge, no proxy & 17 & 13 &  &  &  &  \\
-obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
-meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
-meek-google, no proxy &  &  &  &  & 5 & 4 \\
-meek-azure, no proxy &  &  &  &  & 1 & 1 \\
-no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
-DNF &  &  & 1 & 3 & 7 & 10 \\
+	\begin{tabular}{c r r r r r}
+	 & First & Proxy & Bridge & Summary & Progress \\
+	\noalign{\hrule}
+	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
+	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
+	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
+	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
+	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
+	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
 	\end{tabular}
-\caption{
-Bridge--proxy combinations that led to the first successful bootstrap
-in each environment and interface.
-Most E1 participants used a direct connection,
-but a few tried a built-in obfs3 bridge.
-All the E2 participants who succeeded,
-did so with obfs3 (the recommended bridge type)---none tried
-a different bridge before obfs3.
-All of the successful E3 participants but one
-used one of the meek bridges.
-The remaining E3 participant succeeded in an unexpected way:
-by searching the web for an open proxy and configuring it
-as the proxy setting.
-}
-\label{tab:attempts-bridge-proxy}
+\caption{Fraction of time spent on each screen.
+Participants spent most of their time on the progress screen, waiting.
+Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
+although none of the censorship environments required a proxy.
+Participants spent less time on the proxy screen
+in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
+\label{table:overall_time}
 \end{table}
+
+Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection.
+We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen.
+This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting.
+However, this behavior was equally likely in the new and old interface conditions.
+
+The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$), while maintaining the same probability for success for the user.
+We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time.
+%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
 
@@
 
-\subsubsection{Active Configuration Time} 
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
-Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
-The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
-
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges-scales}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The narrow black lines show the times when the configuration interface
-was not running; i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes
-(marked with a $\times$).
-}
-\label{fig:all-participant-edges}
-\end{figure*}
-
-While we did not find a statistically significant difference between the overall time to success between the old and new versions of the interface, the time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
-Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.
-Participants using the new interface and old interface spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively.
-We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen which keeps the users waiting indefinitely, which were present in both versions of the interface.
+\subsubsection{Rate of Success} 
+Five more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network.
+Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
+However, this does suggest that users are equally likely to succeed with the new interface.
+% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
+%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)
+
+Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.
+Note that only four of the default bridges were used to connect successfully for the first time.
+Users avoid making decisions when a recommendation is given and tend to avoid or fail with more advanced options.
+Participants who were in environments where the recommended bridge (obfs3) worked did not successfully configure another bridge.
+Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
 
@@
 \centering
-	\begin{tabular}{c r r r r r}
-	 & First & Proxy & Bridge & Summary & Progress \\
-	\noalign{\hrule}
-	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
-	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
-	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
-	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
-	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
-	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
+% Generated by attempts.R, and manually reordered:
+\begin{tabular}{r c c c c c c}
+& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
+no bridge, no proxy & 17 & 13 &  &  &  &  \\
+obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
+meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
+meek-google, no proxy &  &  &  &  & 5 & 4 \\
+meek-azure, no proxy &  &  &  &  & 1 & 1 \\
+no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
+DNF (did not finish) &  &  & 1 & 3 & 7 & 10 \\
 \end{tabular}
-\caption{Fraction of time spent on each screen.
-Participants spent most of their time on the progress screen, waiting.
-Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
-although none of the censorship environments required a proxy.
-Participants spent less time on the proxy screen
-in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
-\label{table:overall_time}
+\caption{
+Bridge--proxy combinations that led to the first successful bootstrap
+in each environment and interface.
+Most E1 participants used a direct connection,
+but a few tried a built-in obfs3 bridge.
+All the E2 participants who succeeded,
+did so with obfs3 (the recommended bridge type)---none tried
+a different bridge before obfs3.
+All of the successful E3 participants but one
+used one of the meek bridges.
+The remaining E3 participant succeeded in an unexpected way:
+by searching the web for an open proxy and configuring it
+as the proxy setting.
+}
+\label{tab:attempts-bridge-proxy}
 \end{table}
 
-Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection.
-We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen.
-This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting.
-However, this behavior was equally likely in the new and old interface conditions.
-
-The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $\mbox{effect size} = 0.284$), while maintaining the same probability for success for the user.
-We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time.
-%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
+We believe that our change to add advice on what to try next on error messages (such as try the connection again, reconfigure your bridge settings, or try without a proxy) would have improved the rate of success.
+However, only 1 of 116 participants saw an error during the experiment.
+That participant, who used the new interface, saw that the bridge configuration was the source of the error, and heeded the interface's advice to reconfigure the bridge options.
+But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results.
+The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back to adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
+We added pre-preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not read this advice.
 
@@
 \subsubsection{Observations}
-These are general observations made from our data set of participants, which may have biases.\\
+These are general observations made from our data set of participants, which may or may not be representative of the Tor user base.\\
 
@@
 This confusion prevented users from configuring their bridges correctly.
-Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies and participants in the old interface who did not receive feedback spent 63\%.
+Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface.
+Participants in the old interface who did not receive feedback spent 63\%.
 
@@
 \item {\bfseries There were (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
+Error messages are intended to appear after a timeout.
 There were warnings, but those warnings went largely unnoticed by our participants.
@@
 \item {\bfseries People waited a long, long time at the progress bar.}
-Some dutifully followed the directions to wait, while others are lost for what to do and choose to wait in frustration. Either way, we think that people spent too much time waiting. 
+From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are lost for what to do and choose to wait in frustration.
 \end{description}
@@
 We discarded data on participants who chose to download their own version of Tor Browser online.
-Some downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
+5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
 Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
@@
 Users may not be qualified to answer this question or may not trust Tor with this information.
-\item{\bfseries Ask if users if they know what to do.} We ask users if they know how to configure a bridge and proxy, and automate the configuration process if they do not.
-However, there are ethical implications of making mistakes on behalf of the users if there is risk involved.
+\item{\bfseries Ask if users know what to do.} Automating the process for users who do not know how to configure a bridge or proxy can be an alternative option.
+However, there are ethical implications of making mistakes on behalf of users with risk involved.
 \end{description}
@@
 
-We test the impact of our changes on 116 participants in a quantitative user study to find that that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
+We test the impact of our changes on 116 participants in a quantitative user study to find that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
 We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.

### 2016-04-26 experiment/processing/attempts.R

@@ -81,7 +81,7 @@ for (label in unique(df$label)) {
 	}
 	cat(sprintf("\\\\\n"))
 }
-cat(sprintf("DNF ", label))
+cat(sprintf("DNF (did not finish) ", label))
 for (env in c("E1", "E2", "E3")) {
 	for (version in c("NEW", "OLD")) {
 		cat(sprintf("& %s ", omitzero(dnf.tt[env, version])))

### 2016-04-26 pets2017-paper/pets2017-paper.tex
fix spelling error

@@
 \section {Acknowledgments}
-I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruting.
+I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting.
 I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.

### 2016-04-29 pets2017-paper/pets2017-paper.tex
Cite Xlab.
Make this a \url.

@@
 \subsection{Setup}
-We ran our experiment at Xlab, the Experimental Social Science Laboratory at the University of 
+We ran our experiment at Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of 
 California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
@@
 
-\noindent https://github.com/lindanlee/circumvention-ux-tor
+\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
 

### 2016-04-29 pets2017-paper/pets2017-paper.tex
Say something about simple.wikipedia.org.

@@
 
+We blocked en.wikipedia.org, the target of the experiment,
+as well as other language-specific subdomains such as
+de.wikipedia.org and fr.wikipedia.org.
+We neglected, however, to block the Simple English Wikipedia
+at simple.wikipedia.org, which one participant found,
+thinking they had completed the task.
+% E2-OLD-X04-20160330-181928
+
 Our study was conducted in a laboratory setting, which can cause our participants to be under or over-motivated.

### 2016-04-29 experiment/processing/graphs.R
Add sequential userids to all-participant-edges.

@@ -13,12 +13,13 @@ height <- 1.5
 participants <- filter_participants(read_participants())
 participants$label <- factor(sprintf("%s-%s", participants$env, participants$version), levels=c("E1-NEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"))
 participants$pid <- factor(sprintf("%s-%s-%s-%s", participants$env, participants$version, participants$seat, participants$session))
-pid_order <- rev(order(participants$env, participants$version, participants$time_to_success))
-participants$pid <- factor(participants$pid, levels=participants$pid[pid_order])
+userid_order <- rev(order(participants$env, participants$version, participants$time_to_success))
+participants$userid <- sprintf("P%d", participants$userid)
+participants$userid <- factor(participants$userid, levels=participants$userid[userid_order])
 
 edges <- filter_edges(read_edges(), participants)
-if (any(is.na(edges$pid))) {
-  stop("found NAs in edges$pid")
+if (any(is.na(edges$userid))) {
+  stop("found NAs in edges$userid")
 }
 # Ignore "not_running" and "starting", so they just show up as blank.
 edges <- droplevels(edges[!(edges$dst %in% c("not_running", "starting")), ])
@@ -112,12 +113,11 @@ ggsave("time_per_screen.pdf", p, width=textwidth, height=3, device=cairo_pdf)
 #############
 
 p <- ggplot()
-p <- p + geom_segment(data=participants, size=0.2, color="black", aes(x=pid, xend=pid, y=0, yend=ifelse(!is.na(time_to_success), time_to_success, maxtime)/60))
-p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=pid, xend=pid, y=time_from_start/60, yend=(time_from_start+duration)/60, color=dst))
+p <- p + geom_segment(data=participants, size=0.2, color="black", aes(x=userid, xend=userid, y=0, yend=ifelse(!is.na(time_to_success), time_to_success, maxtime)/60))
+p <- p + geom_segment(data=edges, size=1.5, lineend="butt", aes(x=userid, xend=userid, y=time_from_start/60, yend=(time_from_start+duration)/60, color=dst))
 # p <- p + geom_point(color="black", size=1.5, shape="|")
[…]

### 2016-04-29 experiment/processing/graphs.R
Remove "p" statement.
It was causing an Rplots.pdf file to appear in the current directory.

@@ -105,7 +105,6 @@ p <- p + scale_x_discrete("Current screen", labels=c(
 p <- p + coord_flip()
 p <- common_theme(p)
 p <- p + facet_grid(version ~ env)
-p
 ggsave("time_per_screen.pdf", p, width=textwidth, height=3, device=cairo_pdf)
 
 #############

### 2016-04-29 experiment/processing/graphs.R
No need to redefine state.palette.

@@ -85,7 +85,6 @@ ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=c
 
 # GRAPH TIME ON EACH SCREEN 
 
-state.palette <- brewer.pal(length(levels(edges$dst)), "Set1")
 data <- aggregate(edges$duration, list(env=edges$env, version=edges$version, seat=edges$seat, runid=edges$runid, dst=edges$dst), FUN=sum)
 p <- ggplot(data, aes(x=dst, y=x/60, color=dst))
 p <- p + geom_boxplot(outlier.size=0)

### 2016-04-30 pets2017-paper/pets2017-paper.tex
restructure redesign section and flip ordering in goals/evaluation section.

--- 2016-04-26 pets2017-paper/pets2017-paper.tex
@@
 \begin{enumerate}
+    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
     \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
-    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-\end{enumerate}
-
-A heuristic evaluation is based on standards
-in the user interface design community. We draw from Jacob Nielsen's ten heuristics~\cite{nielsen1994heuristic}
-to form the following heuristic evaluation criteria: \\
-
-\begin{enumerate}
-    \item  {\bfseries Visibility of system status:} There is feedback on system state is and what the system is doing. 
-    \item  {\bfseries Error management:}  Errors are in plain language and offers a solution. 
-    \item  {\bfseries Understandable language:} Users are able to understand the text and concepts mentioned in the interface. 
 \end{enumerate}
@@
 \smallskip
-
-% E1
-% (Representative of countries such as France and Australia.)
-% E2 
-% (Representative of countries such as Tunisia.)
-% E3
-% (Representative of countries such as China and Syria.)
 
@@
 
-From the results of our qualitative user study, we see that many users struggle with the configuration process. 
-The Tor Browser configuration interface does not adequately meet our criteria from Section~\ref{sec:goals} of
-managing errors gracefully, communicating in understandable language, and giving  users feedback on system state. 
-We rate the severity of each issue by its frequency, impact, and persistence~\cite{nielsen1994heuristic}:\\
-
-\begin{itemize}
-\item {\bfseries Major Problem:} Error messages do not express errors in plain language nor offer solutions. 
-\item {\bfseries Major Problem:} The concepts mentioned in the interface and the questions that users are required to answer are too technical for the average user. 
-\item {\bfseries Minor Problem:} The configuration is not visible to the users before they attempt to connect or while they are connecting to the Tor network.
- \end{itemize}
+Many users struggle with the configuration process. Our changes to the configuration interface address the causes for these issues. These underlying causes are:\\
+
+\begin{enumerate}
+\item {\bfseries Users do not know what to do.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference between bridges, pluggable transports, and proxies.
+Participants did not know how to configure these network components without any additional instructions.
+\item {\bfseries User feedback is too technical, missing, or misleading.} Participants did not understand the error messages, log lines, and other text in the interface.
+Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e.
+a syntactically correct but invalid proxy).
+Participants assumed they were not making progress, due to the progress bar not giving feedback on subsequent attempts.
+\item {\bfseries Users do not understand censorship circumvention cues.} Participants did not understand how censorship worked and what would circumvent censorship in their environment, despite adequate evidence that signals what components are necessary and unnecessary.
+A working connection to the Internet did signal to participants that they did not need a proxy; a blocked website did not translate to a blocked domain name; a failed direct connection did not equate to a blocked Tor relay.
+ \end{enumerate}
 
@@
 
-To address these problems, we made the following three changes to the configuration interface:  \\
+To help users know what to do, we made the following changes:\\
 
@@
 The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy.
-\item {\bfseries Reduced the overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process.
+\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
+\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work. 
+\end{enumerate}
+
+To address too technical, missing, or misleading feedback, we made the following changes:\\ 
+\begin{enumerate}
+\setcounter{enumi}{3}
+\item {\bfseries Progress bar feedback is accurate.}  We fixed the bug that caused the progress bar to not update on subsequent attempts.
+What users now see on the progress bar reflects the reality of the progress.
+\item {\bfseries Made the interface text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process.
 Since users generally could not understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
@@
 The same information is shown on the progress screen while the connection is in progress.
+We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
+This aligns with the mental model we are trying to build in the user.
 \end{enumerate}
 
-Other changes improve empirical goals from Section~\ref{sec:goals}: task completion rate, time to completion, and safety for high-risk users.
-Items 5 and~6 improve task completion; 7 and~8 reduce time to completion; and 9 and~10 build users' mental models of censorship circumvention and the network components involved.
-Users retain full control of the configuration process.\\
+To help clarify with interacting network components with censorship circumvention, we made the following changes:\\
 
 \begin{enumerate}
-\setcounter{enumi}{3}
-\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
-\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work.
-
+\setcounter{enumi}{6}
 \item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
@@
 (In our experiment, we simulated the auto-detection by hard-coding the fact that a proxy was not required.)
-
 \item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen.
@@
 With auto-detection, configuring a proxy before a bridge burdens users less than before.
-\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
-This aligns with the mental model we are trying to build in the user.
-As connections are made with each component, the progress bar displays a green check, giving immediate feedback to the user.
-For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network.
-Upon failure, users can see which components have succeeded and which have failed.
 \end{enumerate}

### 2016-04-30 experiment/processing/graphs.R
Make a percent_per_screen graph.

@@ -85,26 +85,38 @@ ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=c
 
 # GRAPH TIME ON EACH SCREEN 
 
+screen.short.labels = c(
+	"first"="F",
+	"bridges"="B1",
+	"bridgeSettings"="B2\nB",
+	"bridgeHelp"="BH",
+	"proxy"="P1",
+	"proxyYES"="P2\nP",
+	"summary"="S",
+	"progress"="Pr",
+	"error"="E"
+)
+
 data <- aggregate(edges$duration, list(env=edges$env, version=edges$version, seat=edges$seat, runid=edges$runid, dst=edges$dst), FUN=sum)
 p <- ggplot(data, aes(x=dst, y=x/60, color=dst))
 p <- p + geom_boxplot(outlier.size=0)
 p <- p + geom_point(size=1.0, alpha=0.6)
 p <- p + scale_color_manual(values=state.palette, guide=F)
-p <- p + scale_x_discrete("Current screen", labels=c(
-  "first"="F",
-  "bridges"="B1",
-  "bridgeSettings"="B2\nB",
-  "bridgeHelp"="BH",
-  "proxy"="P1",
-  "proxyYES"="P2\nP",
-  "summary"="S",
-  "progress"="Pr",
-  "error"="E"
-))
+p <- p + scale_x_discrete("Current screen", labels=screen.short.labels)
 p <- p + coord_flip()
 p <- common_theme(p)
 p <- p + facet_grid(version ~ env)
 ggsave("time_per_screen.pdf", p, width=textwidth, height=3, device=cairo_pdf)
+
+data <- aggregate(edges$duration, list(env=edges$env, version=edges$version, dst=edges$dst), FUN=sum)
+p <- ggplot(data, aes(x=dst, y=x/ave(x, env, version, FUN=sum), fill=dst))
+p <- p + geom_bar(stat="identity")
+p <- p + scale_fill_manual(values=state.palette, guide=F)
+p <- p + scale_x_discrete("Current screen", labels=screen.short.labels)
+p <- p + scale_y_continuous("Fraction of total time", labels=percent)
+p <- common_theme(p)
+p <- p + facet_grid(version ~ env)
+ggsave("percent_per_screen.pdf", p, width=textwidth, height=3, device=cairo_pdf)
 
 #############
 # ALL EDGES #

### 2016-04-30 experiment/processing/graphs.R
Remove another "p" statement.

@@ -145,5 +145,4 @@ p <- common_theme(p)
 p <- p + theme(panel.grid.minor.x=element_blank())
 p <- p + theme(panel.grid.major.y=element_blank())
 p <- p + theme(axis.text.y=element_text(color="gray70"))
-p
 ggsave("all-participant-edges.pdf", p, width=textwidth, height=textheight-0.75, device=cairo_pdf)

### 2016-05-04 experiment/processing/attempts.R
get percentages of time in each environment

@@ -32,7 +32,7 @@ sum(first_attempts$bridge_radio_state == "none")#/nrow(first_attempts)*100
 sum(first_attempts_new$bridge_radio_state == "none")#/nrow(first_attempts_new)*100
 sum(first_attempts_old$bridge_radio_state == "none")#/nrow(first_attempts_old)*100
 
-# How many FIRST attempts were failures. 
+# How many FIRST attempts were failures.
 sum(first_attempts$attempt_successful == "FALSE")/nrow(first_attempts)*100
 sum(first_attempts_new$attempt_successful == "FALSE")/nrow(first_attempts_new)*100
 sum(first_attempts_old$attempt_successful == "FALSE")/nrow(first_attempts_old)*100

### 2016-05-04 experiment/processing/info.R

@@ -67,9 +67,9 @@ cat("****************************\n")
 # 1: group edges by their source
 # 2: get the total time each user spent on a particular screen 
 # 3: create data frame "screen time per user" which has the time a user spent on each screen 
-# 4: (TODO) historgram plot function
 
 edges <- filter_edges(read_edges(), participants)
+edges <- trim_edges(trim_edges)
 
 # 1 
 active_edges <- edges[!(edges[,"dst"] %in% c("not_running", "starting", "progress")),] # "active time" is anytime that people are not on the progress screen.
@@ -116,11 +116,12 @@ report_total <- function(label, selected_edges) {
 
 	# % TOTAL time on screen, across users. (total, e1, e2, e3,new, old)
 	subreport_total("TOTAL\tAll", function(z) { T })
-	subreport_total("TOTAL\tE1", function(z) { z$env=="E1" })
-	subreport_total("TOTAL\tE2", function(z) { z$env=="E2" })
-	subreport_total("TOTAL\tE3", function(z) { z$env=="E3" })
-	subreport_total("TOTAL\tNEW", function(z) { z$version=="NEW" })
-	subreport_total("TOTAL\tOLD", function(z) { z$version=="OLD" })
+	subreport_total("TOTAL\tE1,NEW", function(z) { z$env=="E1" & z$version=="NEW"})
+	subreport_total("TOTAL\tE1,OLD", function(z) { z$env=="E1" & z$version=="OLD"})
+	subreport_total("TOTAL\tE2,NEW", function(z) { z$env=="E2" & z$version=="NEW"})
+	subreport_total("TOTAL\tE2,OLD", function(z) { z$env=="E2" & z$version=="OLD"})
+	subreport_total("TOTAL\tE3,NEW", function(z) { z$env=="E3" & z$version=="NEW"})
+	subreport_total("TOTAL\tE3,OLD", function(z) { z$env=="E3" & z$version=="OLD"})
 }
 
 report_active <- function(label, selected_edges) {
@@ -130,11 +131,12 @@ report_active <- function(label, selected_edges) {
 
 	# % ACTIVE time on screen, across users. (total, e1, e2, e3,new, old)
 	subreport_active("ACTIVE\tAll", function(z) { T })
-	subreport_active("ACTIVE\tE1", function(z) { z$env=="E1" })
[…]

### 2016-05-04 pets2017-paper/pets2017-paper.tex
Dave's suggestions.
-rearrange the results section: rate of success, time to success, and active time
-add detail about why people failed, showing tor log button and log lines
-added which users failed how into the failed section
-deleted claims which were subjective
-added clarifications on calculations and points being made
-additional textual changes

@@
 \begin{figure}
-\small
-\begin{itemize}
-\renewcommand{\labelitemi}{$\circ$}
-\item Connect with provided bridges\\
-Transport type:
-\begin{itemize}
-\item flashproxy
-\item fte
-\item fte-ipv6
-\item meek-amazon
-\item meek-azure
-\item meek-google
-\item obfs3 (recommended)
-\item obfs4
-\item scramblesuit
-\end{itemize}
-\item Enter custom bridges\qquad\fbox{Help}\\
-\end{itemize}
+  \centering
+    \includegraphics[width=0.5\textwidth]{bridge-options.png}
+%\small
+%\begin{itemize}
+%\renewcommand{\labelitemi}{$\circ$}
+%\item Connect with provided bridges\\
+%Transport type:
+%\begin{itemize}
+%\item flashproxy
+%\item fte
+%\item fte-ipv6
+%\item meek-amazon
+%\item meek-azure
+%\item meek-google
+%\item obfs3 (recommended)
+%\item obfs4
+%\item scramblesuit
+%\end{itemize}
+%\item Enter custom bridges\qquad\fbox{Help}\\
+%\end{itemize}
 \caption{
@@
 
-\subsubsection{Active Configuration Time} 
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
-Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
-The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
-
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges-scales}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The narrow black lines show the times when the configuration interface
-was not running; i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes
-(marked with a $\times$).
-}
-\label{fig:all-participant-edges}
-\end{figure*}
-
-The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
-Table ~\ref{table:overall_time} shows the time spent on each screen while participants used the interface, which shows that participants spent 57\% of their overall time at the progress screen.
-Participants using the new interface and old interface spent approximately the same amount of time overall on the progress screen (359 minutes versus 339 minutes), which accounts for 78\% and 45\% of their overall time, respectively.
-We attribute this to a combination of instructions that tell the user to ``wait a couple minutes'' because connections usually take a while to bootstrap and the lack of timeout on the progress screen, which were present in both versions of the interface.
-
-\begin{table}
-\centering
-	\begin{tabular}{c r r r r r}
-	 & First & Proxy & Bridge & Summary & Progress \\
-	\noalign{\hrule}
-	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
-	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
-	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
-	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
-	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
-	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
-	\end{tabular}
-\caption{Fraction of time spent on each screen.
-Participants spent most of their time on the progress screen, waiting.
-Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
-although none of the censorship environments required a proxy.
-Participants spent less time on the proxy screen
-in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
-\label{table:overall_time}
-\end{table}
-
-Perhaps a more meaningful measurement of time is the amount of time participants actively spent configuring their connection.
-We define this as the amount of time that participants spent on the interface, except for time spent on the progress screen.
-This is a simplified notion active configuration time, since some participants searched for help on the web while they were waiting.
-However, this behavior was equally likely in the new and old interface conditions.
-
-The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$), while maintaining the same probability for success for the user.
-We believe that getting rid of the technical bridge and proxy questions, instructing participants that they did not need a proxy, and simplifying the interface attributed to the reduction in time.
-%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
-
-\subsubsection{Time to Success} 
-Although the median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}), this difference is not statistically significant.
-The level of censorship had a significant impact on the time to success.
-The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
-The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
-%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
-%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})
-
-\begin{figure}
-\centering
-\includegraphics{time_to_success_clamped}
-\caption{
-Time to first success, by censorship environment and interface.
-The dots show the raw completion times,
-while the boxplots show the medians and interquartile ranges.
-The ``DNF'' figures at the right show the number of participants 
-who did not finish in the time allotted.
-Here, non-finishing participants are assigned the maximum time of 40:08
-for the purpose of computing the median.
-}
-\label{fig:time_to_success_clamped}
-\end{figure}
-
-In our experiment, participants had 40 minutes to circumvent censorship.
-Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
-Participants were less and less likely to succeed as time went on.
-Users in the wild will likely not be motivated to configure their connection for 40 minutes.
-If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
-Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
-Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment.
-We propose ideas on how to achieve this in section~\ref{recommendations}.
-
-\begin{figure}
-\centering
-\includegraphics{time_to_success_ecdf}
-	% Generated by info.R:
-	\begin{tabular}{l r r r r}
-	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
-	\noalign{\hrule}
-	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
-	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
-	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
-	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
-	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
-	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
-	\end{tabular}
-\caption{
-Cumulative success rates over time, by censorship environment and interface.
-We stopped participants after 40 minutes. Here, those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
-For example, every E1-NEW participant finished within 90 seconds,
-but only 58\% of E1-OLD had finished by that time.
-After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
-After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
-}
-\label{fig:time_to_success_ecdf}
-\end{figure}
-
 \subsubsection{Rate of Success} 
-Five more participants with the new interface were able to successfully circumvent censorship and connect to the Tor network.
+50 of 58 (86\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
-However, this does suggest that users are equally likely to succeed with the new interface.
+This suggests that users no less likely to succeed with the new interface.
 % impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
@@
 
-Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.
-Note that only four of the default bridges were used to connect successfully for the first time.
-Users avoid making decisions when a recommendation is given and tend to avoid or fail with more advanced options.
-Participants who were in environments where the recommended bridge (obfs3) worked did not successfully configure another bridge.
-Participants who were in environment that required a meek or custom bridge only were able to succeed with a meek bridge.
+\begin{figure}[t]
+\centering
+\includegraphics[width=.5\textwidth]{warning.png}
+\caption{
+A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
+which appears silently and does not interrupt the progress bar. 
+This warning was generated by entering in syntactically correct but invalid proxy settings,
+a mistake that prevents users from ever connecting to the Tor network. 
+Users are never directly notified of this error through an error message or a timeout message.
+Our participants made this error during our experiments, along with others that they were not notified about. 
+}
+\label{fig:warning}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.5\textwidth]{log-messages.png}
+\caption{
+The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
+These log lines were the result of entering in syntactically correct but invalid proxy settings,
+a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
+technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
+}
+\label{fig:warning_log}
+\end{figure}
+
+We believe that the added advice on what to try next on error messages would have improved the rate of success.
+However, only 1 of 116 participants saw an error during the experiment.
+The old interface warned users on some mistakes (i.e.
+entering in a syntactically correct but invalid proxy settings) rather than displaying an error message.
+When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}).
+To see the log messages, users must click on the button, open up a text editor, and paste the log messages.
+The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
+
+That participant was using the new interface and was told that the bridge configuration was the source of the error.
+The participant heeded the interface's advice to reconfigure the bridge options.
+But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results.
+The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
+
+We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure.
+Of the 76 participants that failed to connect on the first attempt, 15 of 36 participants with the new interface and 13 of 38 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
+10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim that this is a direct result of our advice.
+
+Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.We only consider the first successful connection since many of our curious participants tried many different settings to investigate if they will work, even after they had completed the task.
+Recall E1 does not require users to configure a bridge, E2 requires users to configure any bridge, and E3 requires users to configure a meek or custom bridge.
+Note that only four of the hard-coded bridges were used to connect successfully for the first attempt were the recommended bridge and the required bridges to succeed in E3.
+
+Our participants did not optionally configure a bridge in E1 or configure a non-recommended bridge in E2.
+This suggests that users will not configure optional components or deviate from the recommended settings unless necessary.
+If the intent of the recommendation is to get as many users as possible to use the recommended bridge, this is a positive result.
+If the intent of the recommendation is to give pointers when users are stuck but allow the users to make their own bridge choices to diversify active transports, this is a negative result.
+
+Only two participants chose to configure a custom bridge.
+Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result.
+Appendix~\ref{failed-participants} shows the malformed requests.
+These two participants failed to connect to the Tor network.
 
@@
 
-We believe that our change to add advice on what to try next on error messages (such as try the connection again, reconfigure your bridge settings, or try without a proxy) would have improved the rate of success.
-However, only 1 of 116 participants saw an error during the experiment.
-That participant, who used the new interface, saw that the bridge configuration was the source of the error, and heeded the interface's advice to reconfigure the bridge options.
-But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results.
-The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back to adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
-We added pre-preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not read this advice.
+\subsubsection{Time to Success} 
+The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}).
+However, this difference is not statistically significant.
+The level of censorship had a significant impact on the time to success.
+The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
+The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
+%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
+%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})
+
+\begin{figure}[t]
+\centering
+\includegraphics{time_to_success_clamped}
+\caption{
+Time to first success, by censorship environment and interface.
+The dots show the raw completion times,
+while the boxplots show the medians and interquartile ranges.
+The ``DNF'' figures at the right show the number of participants 
+who did not finish in the time allotted.
+Here, non-finishing participants are assigned the maximum time of 40:08
+for the purpose of computing the median.
+}
+\label{fig:time_to_success_clamped}
+\end{figure}
+
+In our experiment, participants had 40 minutes to circumvent censorship.
+Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
+In practice, faster time to completion would mean more users will succeed, since users will give up after a while.
+Users in the wild will likely not be motivated to spend 40 minutes trying to configure Tor.
+If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
+Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
+Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment.
+We propose ideas on how to achieve this in section~\ref{recommendations}.
+
+\begin{figure}[t]
+\centering
+\includegraphics{time_to_success_ecdf}
+	% Generated by info.R:
+	\begin{tabular}{l r r r r}
+	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
+	\noalign{\hrule}
+	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
+	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
+	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
+	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
+	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
+	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
+	\end{tabular}
+\caption{
+Cumulative success rates over time, by censorship environment and interface.
+We stopped participants after 40 minutes. Here, those who did not finish were assigned
+an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
+For example, every E1-NEW participant finished within 90 seconds,
+but only 58\% of E1-OLD had finished by that time.
+After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
+After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
+}
+\label{fig:time_to_success_ecdf}
+\end{figure}
+
+\subsubsection{Active Configuration Time} 
+We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
+Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
+The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
+
+\begin{figure*}
+\centering
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges-scales}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The narrow black lines show the times when the configuration interface
+was not running; i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes
+(marked with a $\times$).
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
+The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
+Logs show that participants spent 64\% of their overall time at the progress screen.
+Participants using the new interface and old interface spent approximately the same amount of absolute time on the progress screen (359 minutes versus 339 minutes, respectively). 
+Table ~\ref{table:overall_time} shows the percentage of time spent on each screen,
+computed by the total number of minutes all participants spent on each screen.
+
+We believe participants spent a long time on the progress screen for a combination of reasons.
+Even with correct configurations, the bootstrap process can take up to two minutes.
+With incorrect settings, we suspect that participants waited because the interface instructs them ``wait a couple minutes.'' A lack of error messages and timeouts on the progress screen, also caused some users to wait indefinitely.
+
+\begin{table}
+\centering
+	\begin{tabular}{c r r r r r}
+	 & First & Proxy & Bridge & Summary & Progress \\
+	\noalign{\hrule}
+	All &  5\% & 17\% & 6\% & 0\% & 64\% \\
+	E1-NEW & 34\% & 4\% & 6\% & 1\% & 50\% \\
+	E1-OLD & 23\% & 35\% & 9\% & N/A & 21\% \\
+	E2-NEW & 5\% & 4\% & 4\% & 1\% & 80\% \\
+	E2-OLD & 4\% & 22\% & 4\% & N/A & 66\% \\
+	E3-NEW & 6\% & 7\% & 4\% & 1\% & 70\% \\
+	E3-OLD & 4\% & 25\% & 9\% & N/A & 60\% \\
+	\end{tabular}
+\caption{Fraction of time spent on each screen, 
+computed by the total number of minutes all participants spent on each screen. 
+Participants spent most of their time on the progress screen.
+Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
+although none of the censorship environments required a proxy.
+Participants spent less time on the proxy screen
+in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
+\label{table:overall_time}
+\end{table}
+
+Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection.
+We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+This is a simplified notion active configuration time.
+Some participants searched for help on the web after exiting the interface or on the progress screen.
+
+The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$).
+We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time.
+%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
 
@@
 
-\subsubsection{Observations}
-These are general observations made from our data set of participants, which may or may not be representative of the Tor user base.\\
-
-\begin{description}
-%connect vs configure
-\item {\bfseries Users try the easy path first.} Users still do not seem to know how to differentiate between censored websites and censored Tor relays and try the easy option of connecting directly to the Tor network first, leaking that they are connecting to Tor on the network.
-81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
-It's critical to note that the participants did not believe the interface when it informed them that they did not need a proxy.
-
-% impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} Users believed that they needed proxies to connect.
-This confusion prevented users from configuring their bridges correctly.
-Participants with the new interface who were explicitly told that they did not need a proxy spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface.
-Participants in the old interface who did not receive feedback spent 63\%.
-
-% impacts of giving people advice on which transport to choose.
-\item {\bfseries Certain transports were chosen with high probability.}
-Of those who tried an obfs3 bridge and failed, 
-66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
-We suspect that flashproxy was a popular choice because it is listed first in the drop-down menu.
-Many bridges listed at the end of the drop-down menu were not chosen.
-
-%error messages
-\item {\bfseries There were (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
-Error messages are intended to appear after a timeout.
-There were warnings, but those warnings went largely unnoticed by our participants.
-Across both versions of the interface, only one participant ever saw an error message.
-
-% progress bar
-\item {\bfseries People waited a long, long time at the progress bar.}
-From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are lost for what to do and choose to wait in frustration.
-\end{description}
-
-We are unable to state the efficacy of our attempts to make instructive and understandable error messages due to lack of data.
-We do not understand why users with the new interface choose to configure proxies after explicitly being told that they do not need one.
-We notice that users in the new interface were more likely to chose meek bridges.
-10 users in the new interface chose a meek-bridge as their second bridge, whereas only 5 users in the old interface did.
-However, we cannot say if this can be attributed to the advice we added on the bridge configuration screen, due to the small sample size.
-
 \subsubsection{Reasons for Failure} 
 Failure is common.
-20\% (21 of 116) of participants failed entirely.
+20\% (21 of 116) of participants were not able to successfully connect to Tor.
 64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
 Reasons for failure were determined by a combination of log processing (i.e.
-how much time was spent on a particular screen) and video observation (i.e.
+configuration settings on attempts) and video observation (i.e.
 observing what they searched for online).
@@
 
+\subsubsection{Observations}
+We noticed several patterns in the behavior of our participants. These may or may not apply to the Tor user base.\\
+
+\begin{description}
+%connect vs configure
+\item {\bfseries Users try the easy path first.} Users try the easy option of connecting directly to the Tor network first.
+This leaks to network eavesdroppers leaking that they are connecting to Tor.
+81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
+
+% impacts of making the proxy page ``automated'' 
+\item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly.
+Participants with the new interface (which explicitly states that they did not need a proxy) spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface.
+Participants in the old interface spent 63\% of their time on the proxy screen.
+We do not understand why users with the new interface chose to configure proxies after explicitly being told that they do not need one.
+
+% impacts of giving people advice on which transport to choose.
+\item {\bfseries The interface has a large influence on the bridges chosen.}
+Participants in E3 were required to choose a particular subset of hard-coded bridges, none of which was the default bridge.
+After the default bridge, the most chosen bridge was the one listed first in the drop-down menu.
+Many bridges listed at the end of the drop-down menu were not chosen.
+We tried to help users by providing instructions on which bridges to choose if the default fails, but it is unclear if this advice helped.
+66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
+
+%error messages
+\item {\bfseries People saw (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
+Error messages are intended to appear after a timeout.
+There were warnings, but those warnings went largely unnoticed by our participants.
+Across both versions of the interface, only one participant ever saw an error message.
+We tried to make error messages more instructive and understandable, bu since participants in our experiment did not encounter error messages, we cannot evaluate their efficacy.
+
+% progress bar
+\item {\bfseries People waited a long, long time at the progress bar.}
+From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are lost for what to do and choose to wait in frustration.
+\end{description}
+
 \subsubsection{Recommendations}
@@
 \item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor.
-Automating the configuration process thereafter will have no increase in risk, but can help a majority of users; 64\% of participants who failed their first attempt.
+Automating the configuration process thereafter will have no increase in risk, but can help a majority of users.
+This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 64\% of participants who failed their first attempt.
 Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.

### 2016-05-04 pets2017-paper/pets2017-paper.tex
switch userids to pids in paper

@@
 \begin{description}
-\item {\bfseries Only connected directly.
-(7/21)} These participants tried a direct connection.
-When that failed, they tried the same configuration, over and over, without trying other configurations, no matter how many times they failed.
+\item {\bfseries Only connected directly (7/21): P57, P74, P76, P90, P93, P108, P112} These participants tried a direct connection.
+When that failed, they tried the same configuration, over and over, no matter how many times they failed.
 It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-\item {\bfseries Didn't know what to do next.
-(6/21)} After a failed direct connection and a failed default obfs3 bridge connection, these participants did not know what to do next.
+\item {\bfseries Didn't know what to do next (6/21): P91, P92, P95, P110, P113, P116} These participants in E3 did not know what to do next after a direct connection and a default obfs3 bridge connection.
 They often tried those configurations again or gave up.
-\item {\bfseries Thought that they needed a proxy (5/21)} After a couple failed attempts, these participants assumed that they needed a proxy.
+\item {\bfseries Thought that they needed a proxy (5/21): P75, P94, P107, P109, P115} After a couple failed attempts, these participants assumed that they needed a proxy.
 They spent the time trying to configure a proxy, usually without trying other bridges.
-\item {\bfseries Used the bridges auto-responder incorrectly (2/21)} Three participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button.
+\item {\bfseries Used the bridges auto-responder incorrectly (2/21): P96, P111} Two participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button.
 However, they all failed to get a response.
@@
 
-\section{Failed Participants} 
+\section{Custom Bridge Attempts} 
 \label{failed-participants}
-
-Only tried to connect directly (7/21): 
-\begin{itemize}
-\item E2-NEW-X21-20160323-1400
-\item E2-OLD-X04-20160330-1800
-\item E2-OLD-X10-20160331-1600
-\item E3-NEW-X05-20160324-1400
-\item E3-NEW-X17-20160323-1400
-\item E3-OLD-X06-20160330-1600
-\item E3-OLD-X12-20160330-1800
-\end{itemize}
-
-Didn't know what to do next (6/21): 
-\begin{itemize}
-\item E3-NEW-X11-20160330-1600
-\item E3-NEW-X11-20160331-1800
-\item E3-NEW-X23-20160323-1400
-\item E3-OLD-X06-20160331-1800
-\item E3-OLD-X12-20160331-1600
-\item E3-OLD-X30-20160328-1400
-\end{itemize}
-
-Thought that they needed a proxy (5/21): 
-\begin{itemize}
-\item E2-OLD-X10-20160328-1400
-\item E3-NEW-X17-20160328-1600
-\item E3-OLD-X06-20160325-1800
-\item E3-OLD-X06-20160330-1800
-\item E3-OLD-X24-20160328-1600
-\end{itemize}
-
-Used the bridges auto-responder incorrectly (2/21): 
-\begin{itemize}
-\item E3-NEW-X23-20160328-1600 (Fig.~\ref{autoresponder1})
-\item E3-OLD-X12-20160325-1400 (Fig.~\ref{autoresponder2})
-\end{itemize}
 
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that E3-NEW-X23-20160328-1600 attempted to send to the bridge auto-responder.
-The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
+\caption{The message that P96 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
 \label{autoresponder1}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that E3-OLD-X12-20160325-1400 accidentally sent to the helpdesk rather than the bridge auto-responder.
+\caption{The message that P111 accidentally sent to the helpdesk rather than the bridge auto-responder.
 The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
@@
 \begin{itemize}
-\item E1-OLD-X32-20160328-1400 (Fig.~\ref{mirror})
-\item E2-NEW-X21-20160323-1400 (Fig.~\ref{techspot})
-\item E2-OLD-X10-20160323-1400 (Fig.~\ref{downloadio})
-\item E2-OLD-X28-20160328-1400 (Fig.~\ref{driverupdate})
-\item E3-NEW-X11-20160330-1600 (Fig.~\ref{softsonic})
+\item P57 (Fig.~\ref{techspot})
+\item P91 (Fig.~\ref{softsonic})
+\item P117, data not used (Fig.~\ref{mirror})
+\item P118, data not used (Fig.~\ref{downloadio})
+\item P119, data not used (Fig.~\ref{driverupdate})
 \end{itemize}
 
-Sources of downloads: 
-\begin{itemize}
-\item {\bfseries techspot.com} $\rightarrow$ {\bfseries 1download.io}: an advertisement in the Yahoo search results for ``tor browser downloads''.
-\item {\bfseries driverupdate.net}: the fifth Google search result for ``tor browser download''.
-\item {\bfseries www.torservers.net/mirrors}: the first google search result for ``tor browser mirror''.
-\item {\bfseries techspot.com}: the fifth Google search result for ``tor browser download''.
-\item {\bfseries softsonic.com}: the second Yahoo search result for ``tor browser''.
-\end{itemize}
-
-\begin{figure}
+%Sources of downloads: 
+%\begin{itemize}
+%\item {\bfseries techspot.com} $\rightarrow$ {\bfseries 1download.io}: an advertisement in the Yahoo search results for ``tor browser downloads''.
+%\item {\bfseries driverupdate.net}: the fifth Google search result for ``tor browser download''.
+%\item {\bfseries www.torservers.net/mirrors}: the first google search result for ``tor browser mirror''.
+%\item {\bfseries techspot.com}: the fifth Google search result for ``tor browser download''.
+%\item {\bfseries softsonic.com}: the second Yahoo search result for ``tor browser''.
+%\end{itemize}
+
+\begin{figure}[h]
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
-\caption{E2-OLD-X10-20160323-1400 attempted to download Tor Browser from TechSpot.com, but clicked on
+\caption{P118 attempted to download Tor Browser from TechSpot.com, but clicked on
 a download link which was not from TechSpot.com. The download was from another site, 1download.io.}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
-\caption{E2-OLD-X28-20160328-1400 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
+\caption{P119 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
 are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
@@
 
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
-\caption{E1-OLD-X32-20160328-1400 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
+\caption{P117 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
 \label{mirror}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
-\caption{E2-NEW-X21-20160323-1400 downloaded Tor Browser from TechSpot, clicking on the download link from 
+\caption{P57 downloaded Tor Browser from TechSpot, clicking on the download link from 
 TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
@@
 
-\begin{figure}
+\begin{figure}[h]
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{E3-NEW-X11-20160330-1600 downloaded Tor Browser from Softsonic, a reputable-looking but
+\caption{P91 downloaded Tor Browser from Softsonic, a reputable-looking but
 unconfirmed site.}

### 2016-05-05 pets2017-paper/pets2017-paper.tex
explain time to success

@@
 The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}).
-However, this difference is not statistically significant.
-The level of censorship had a significant impact on the time to success.
+Non-finishing participants are assigned the maximum time of 40:08
+for the purpose of computing the median.
+However, the difference between the medians times to success between new versus old interfaces, in aggregate and in censorship environment, are not statistically significant.
+The level of censorship, rather than the interface, had a significant impact on the time to success.
 The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).

### 2016-05-05 pets2017-paper/pets2017-paper.tex
add placeholders for active time TODOS

@@
 
+\begin{table}
+\centering
+	\begin{tabular}{c r r}
+	 & Total Active Minutes & \% of Overall Time \\
+	\noalign{\hrule}
+	All & 381 & 29\% \\ 
+	E1-NEW & 4 & 45\% \\
+	E1-OLD & 19 & 67\% \\
+	E2-NEW & 15 & 15\% \\
+	E2-OLD & 68 & 31\% \\
+	E3-NEW & 74 & 18\% \\
+	E3-OLD & 200 & 38\% \\
+	\end{tabular}
+\caption{active time {\color {red} add comparable figure to the time to success figure (Fig 9)}.} 
+\label{table:active_time}
+\end{table}
+
 Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection.
@@
 
-The new interface results a statistically significant reduction in the overall active configuration time (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$).
+{\color {red} TODO: explain how this was calculated: across all participants, with DNF's getting 40:08 then subtracting the time they spent on the progress screen)} The new interface results a statistically significant reduction in the overall active configuration time.
+(Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$).
 We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time.

### 2016-05-05 experiment/processing/graphs.R

@@ -56,7 +56,6 @@ ggsave("time_to_success.pdf", p, width=columnwidth, height=height, device=cairo_
 p <- time_to_success_plot(clamp_time_to_success(participants, maxtime))
 ggsave("time_to_success_clamped.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 
-
 # Assign each environment a color (E1=blue, E2=orange, E3=green), with NEW
 # being more saturated and OLD being less saturated.
 palette <- c(

### 2016-05-05 experiment/processing/info.R

@@ -104,7 +104,7 @@ screen_time_per_user <- merge(screen_time_per_user, summary_time_per_user, by=c(
 screen_time_per_user[is.na(screen_time_per_user)] <- 0
 
 subreport <- function(label, sublabel, selected_edges, denom_edges, f) {
-	cat(sprintf("%s\t%s\t%s\n", sublabel, label,
+	cat(sprintf("%s\t%s\t%s\t%s\n", sublabel, label, round(sum(selected_edges[f(selected_edges),]$duration)/60),
 		format_percent(sum(selected_edges[f(selected_edges),]$duration)/sum(denom_edges[f(denom_edges),]$duration))))
 }
 
@@ -145,6 +145,9 @@ report <- function(label, selected_edges) {
 
 # PROGRESS SCREEN 
 report_total("PROGRESS", progress_edges)
+
+#ACTIVE TIME (all but progress)
+report_total("ACTIVE",active_edges)
 
 # FIRST SCREEN
 report("FIRST", first_edges)

### 2016-05-06 pets2017-paper/pets2017-paper.tex
Dave's suggestions pt 2:
-clarify recommendations to be more concrete.
-textual changes.
-remove paragraph in limitations about simple wikipedia since it had no huge consequence on our experiment.
-propose an automation scheme in future work.

@@
 
-{\color {red} TODO: explain how this was calculated: across all participants, with DNF's getting 40:08 then subtracting the time they spent on the progress screen)} The new interface results a statistically significant reduction in the overall active configuration time.
+{\color {red} TODO: explain how this was calculated: across all participants with all of the new and all of the old aggregated, with DNF's getting 40:08 then subtracting the time they spent on the progress screen).
+Say it is mann whitney one tailed.
+} The new interface results a statistically significant reduction in the overall active configuration time.
 (Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$).
@@
 \subsubsection{Observations}
-We noticed several patterns in the behavior of our participants. These may or may not apply to the Tor user base.\\
+We noticed several behavioral patterns in our participants. These may or may not apply to the Tor user base.\\
 
@@
 \begin{description}
-\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, the user has already indicated to their censor that they are connecting to Tor.
-Automating the configuration process thereafter will have no increase in risk, but can help a majority of users.
+\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, a user has already leaked to network eavesdroppers leaking that they are connecting to Tor.
+Automating the configuration process thereafter will have no increase in risk.
 This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 64\% of participants who failed their first attempt.
 Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
-\item{\bfseries Hide infrequently used options.} Informing users that they did not need a proxy was not enough to deter users from spending time configuring a proxy.
+\item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy.
 Only a small fraction of the Internet population requires a proxy to connect to the Internet.
-Hiding the proxy screen by default and only showing it after it has been detected as necessary can focus user efforts on configuring bridges.
-\item {\bfseries Be explicit about recommendations.} Being explicit about the order in which a user should choose bridges will result in higher rates of success and lessen cognitive load on the user.
-Most participants followed recommendations about which bridge to choose, and many did not know what to do after the recommended bridge failed.
+Hiding the proxy screen by default and only showing it after it has been detected as necessary might improve the user experience focusing user effort on configuring bridges.
+\item {\bfseries Be explicit about recommendations.} Many do not know what to do after the recommended bridge failed.
+The interface should mark which bridges have been tired before and recommend the user to try another bridge.
+(i.e.
+After a user tried an obfs3 bridge, the interface updates its recommendation to a meek bridge and mark the obfs3 bridge with an ``X''.)
 \item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration.
-\item{\bfseries Have a user-tolerant auto-responder.} Having the auto-responder default respond with bridges or catching common errors (such as typing ``get bridges'' in the subject line) can help those who need custom bridges.
+\item{\bfseries Have a user-tolerant bridge auto-responder.} The bridge auto-responder responds to user requests for custom bridges.
+Users can make this request by emailing bridges@torproject.org with a non-empty title and ``get bridges'' in the body.
+Both of our users who tried to get custom bridges this way failed to format their request correctly.
+Having the auto-responder respond with bridges as a default or recovering from common errors (such as typing ``get bridges'' in the subject line) may help users succeed.
 \end{description}
 
-We also encourage best practices, such as providing a summary screen to let the user know the configuration settings before connecting, having a checklist progress bar to give users feedback on what network component needs configuring, and rewriting screen text and error messages to be more instructive and understandable.
+We recommend best practices, such as providing a summary screen to let the user know the configuration settings before connecting, and having a progress bar that gives users feedback on what network component has failed.
 
 \section{Limitations} 
-The interface was only tested on Windows machines, which were the only types of machines in Xlab.
+The interface was only tested on Windows machines.
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
@@
 
-We blocked en.wikipedia.org, the target of the experiment,
-as well as other language-specific subdomains such as
-de.wikipedia.org and fr.wikipedia.org.
-We neglected, however, to block the Simple English Wikipedia
-at simple.wikipedia.org, which one participant found,
-thinking they had completed the task.
-% E2-OLD-X04-20160330-181928
+%We blocked en.wikipedia.org, the target of the experiment,
+%as well as other language-specific subdomains such as
+%de.wikipedia.org and fr.wikipedia.org.
+%We neglected, however, to block the Simple English Wikipedia
+%at simple.wikipedia.org, which one participant found,
+%thinking they had completed the task.
+%% E2-OLD-X04-20160330-181928
 
@@
 We took an approach that optimized for the average case user manually configuring a connection.
-Additional user studies that focus specifically on users in heavily censored environments or increasing the amount of automation in the configuration process can yield higher rates of success and faster time to success.
-We encourage future work to explore some of the non-conservative changes and alternate approaches that we were not able to test in these series of experiments.\\
+Additional user studies that focus specifically on users in heavily censored environments or increasing the amount of automation in the configuration process may yield higher rates of success and faster time to success.
+We list 3 approaches that can seem worth exploring.
+\\
 
 \begin{description}
-\item{\bfseries Automate the configuration.} Complete automation of the configuration process, which involves network probing, would not harm users today (as far as we know).
-Our study finds that most users fail on the first try when trying to circumvent an advanced censor, so this automation may not increase the number of users who leak that they are connecting to the Tor network.
+\item{\bfseries Automate the configuration.} One naive way to automate the process users should take, trying the most likely configurations to work in order.
+This process leaks to network eavesdroppers that the user is connecting to the Tor network, but this would not harm users today (as far as we know).
+Our study finds that 64\% users fail on the first try when trying to circumvent an advanced censor.
+However, further research can explore if and how much increased risk is associated with this approach.
 \item{\bfseries Ask about the risk.} Automating the configuration process for all who are not at risk and offering manual configuration to those who would like to be more cautious is an alternative to complete automation.
-The complication with this approach is that we would need to ask the users about the risk involved with connecting to the Tor network.
+The complication with this approach is that we would need to ask the users whether they would be at risk if someone learned that they are connecting to the Tor network.
 Users may not be qualified to answer this question or may not trust Tor with this information.
-\item{\bfseries Ask if users know what to do.} Automating the process for users who do not know how to configure a bridge or proxy can be an alternative option.
-However, there are ethical implications of making mistakes on behalf of users with risk involved.
+\item{\bfseries Ask if users know what to do.} Automating the process for users who do not know how to configure a bridge or proxy could be an alternative option.
+However, there are ethical implications of making mistakes on behalf of users at risk.
 \end{description}
 
-We believe that automation, asking about risk, and identifying struggling users are all integral to making significant improvements to the configuration process.
+We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process.
+
+\section{Conclusion} 
+We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
+We interviewed 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring Tor.
+We discovered multiple challenges: users are confused about who to configure bridges and proxies, a progress bar bug that causes users to falsely assume that a (valid) configuration is faulty, and users have a hard time figuring out what to do after their first attempt to connect fails.
+
+We used this feedback to guide the redesign of the configuration interface.
+We test the impact of our changes on 116 participants.
+We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
+{\color {red} TODO: add more here.} Our analysis suggests ways to improve the Tor interface as well as some potential opportunities for further research.
+
+\section {Resources} 
+For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
+
+\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
 
@@
 I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
-
-\section {Resources} 
-For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
-
-\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
-
-\section{Conclusion} 
-We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, which helps users circumvent censorship using Tor.
-A qualitative user study interviews 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring a connection.
-These include confusing the necessity of bridges and proxies, assuming that a correct configuration was wrong due to a progress bar bug, and not knowing what to do on failure.
-This feedback is used to guide the redesign of the configuration interface.
-
-We test the impact of our changes on 116 participants in a quantitative user study to find that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
-We observe and quantify common behavioral trends based on logs and video recordings of our participants, and offer recommendations that we believe will greatly increase the success rate and time to success for future users.
 

### 2016-05-06 experiment/processing/attempts.R
group first attempts by conditions.

@@ -9,6 +9,9 @@ attempts <- attempts[order(attempts$seat, attempts$runid, attempts$time_from_sta
 # Remove attempts after the first successful one.
 attempts <- attempts[is.na(attempts$time_to_success) | attempts$time_from_start <= attempts$time_to_success, ]
 
+# Hack to make DNF time to successes 40:08
+attempts$time_to_success[is.na(attempts$time_to_success)] <- 40*60 + 8
+
 attempts$bridge_default_selection[!attempts$bridge_yesno] <- NA
 
 # Show all attempts (up to first success).
@@ -22,12 +25,17 @@ sum(attempts$attempt_successful == "FALSE")/nrow(attempts)*100
 
 # How many FIRST attempts were direct. 
 first_attempts <- subset(attempts, subset = !duplicated(attempts[c("userid")]))
-first_attempts_new <-  first_attempts[first_attempts[,"version"]=="NEW",]
-first_attempts_old <- first_attempts[first_attempts[,"version"]=="OLD",]
-first_attempts_e1 <- first_attempts[first_attempts[,"env"]=="E1",]
-first_attempts_e2 <- first_attempts[first_attempts[,"env"]=="E2",]
-first_attempts_e3 <- first_attempts[first_attempts[,"env"]=="E3",]
+# Calculate time saved by automating after the first connection. 
+first_attempts$time_after_first <- first_attempts$time_to_success - first_attempts$time_from_start
 
+first_attempts_E1_NEW <-  first_attempts[first_attempts[,"env"]=="E1" & first_attempts[,"version"]=="NEW",]
+first_attempts_E1_OLD <-  first_attempts[first_attempts[,"env"]=="E1" & first_attempts[,"version"]=="OLD",]
+first_attempts_E2_NEW <-  first_attempts[first_attempts[,"env"]=="E2" & first_attempts[,"version"]=="NEW",]
+first_attempts_E2_OLD <-  first_attempts[first_attempts[,"env"]=="E2" & first_attempts[,"version"]=="OLD",]
+first_attempts_E3_NEW <-  first_attempts[first_attempts[,"env"]=="E3" & first_attempts[,"version"]=="NEW",]
+first_attempts_E3_OLD <-  first_attempts[first_attempts[,"env"]=="E3" & first_attempts[,"version"]=="OLD",]
+
+#? 
 sum(first_attempts$bridge_radio_state == "none")#/nrow(first_attempts)*100
[…]

### 2016-05-06 pets2017-paper/pets2017-paper.tex
Joel's comments. They were all textual changes.

@@
 This is the first study to examine Tor's usability in this role.
-We evaluate, redesign, and test the Tor configuration interface by
-placing users in simulated censorship environments, instructed them to use Tor
+We evaluate, design, and test the Tor configuration interface by
+placing users in simulated censorship environments, instructing them to use Tor
 to circumvent censorship, and measuring their interactions with the interface.
@@
 A 116-participant quantitative user study tests the impact of our changes.
-We find that our changes results in a significant reduction 
+We find that our changes result in a significant reduction 
 in the time spent configuring a connection, while maintaining the same rate of success. We
@@
 that make it difficult to observe the source and destination~\cite{dingledine2004tor}.
-Tor's anonymizing functionality also circumvented censorship.
-Censorship circumvention became a common enough use case for Tor that many countries attempt to block Tor for this reason~\cite{winter2012great}.
+Tor's anonymizing functionality also circumvents censorship.
+Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}.
 Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.
 
-This is the first user study investigating the usability of Tor as a censorship circumvention tool.
+This is the first user study that investigates the usability of Tor as a censorship circumvention tool.
 Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier.
-All Tor users will benefit from improving the configuration interface, therefore increasing the adoption of Tor as a censorship circumvention tool.
-Users who successfully use Tor to circumvent censorship will be provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
-
-We evaluate, redesign, and test the Tor configuration interface by
+All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool.
+Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
+
+We evaluate, redesign, and test Tor's configuration interface by
 measuring participants' interactions with the interface in various censorship environments.
@@
 We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
-We redesign the interface to build users' mental models, make the text easier to understand, and provide messages to assist users on error.
-Our changes decreased the time participants spent configuring their connections, but there was no difference in success rates.
-We expected the success rate to increase after providing suggestions on what to do next with error messages, but this had no effect since only 1 of 116 users encountered an error message.
+We redesign the interface to decrease the technical knowledge required, give explicit advice on configuring network components, and fix misleading feedback that causes users to assume they are wrong when they are right.
+Our changes decreased the time participants spent configuring their connections, with no difference in success rates.
 We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.
@@
 There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
-options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none of them 
-were satisfactory from a usability perspective. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
+options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
 latency~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests more often, and prevents user adoption. 
+to be frustrated, cancel requests, and prevents user adoption. 
 Norcie et~al.~\cite{norcie2012eliminating} found found that 
@@
 
-Previous user studies have been on the whole browsing experience,
+Previous user studies have considered the whole browsing experience,
 without focusing on specific features in isolation.
-We focus our study on 
+Our study focuses on 
 the browser's configuration interface, which guides users through setting up network components required to circumvent censorship.
@@
 \section{Background}
-This section discusses the configuration interface relates to Tor, what network components that are involved in censorship circumvention, and which configuration settings are required to bypass levels of Tor-adverse censorship environments.
+This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.
 
@@
 A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-However, this requires the user to grapple with technical concepts such as 
-bridges, pluggable transports, and proxies.
+However, this requires that the user grapple with technical concepts such as 
+bridges, pluggable transports, and proxies. Some of these concepts are specific to 
+Tor and not general concepts.
 
@@
 Censors can block the Tor network by blocking the list of Tor relays, which 
-are public. However, it becomes challenging to block access to Tor when
+are public. Blocking Tor becomes challenging when
 the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
@@
 The minimum amount of configuration required, therefore, the set of valid configuration settings,
-vary depending on the censorship environment. At the maximum, users will need to know or find out:\\
+vary depending on the censorship environment. In the worst case, users must know or find out:\\
 
@@
 Uncensored users and users in censorship environments that do not explicitly 
-block Tor do not require a bridge or a proxy and can bypass the configuration process.
+block Tor do not require a bridge or a proxy and can bypass these steps in the configuration process.
 Users in censorship environments that explicitly block Tor but have not blocked the 
@@
 hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
-blocked Tor relays and hard-coded bridges will be required to configure a meek bridge (which 
+blocked Tor relays and hard-coded bridges are required to configure a meek bridge (which 
 routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
@@
 \label{sec:goals}
-The series of user studies evaluated two versions of the Tor Launcher interface.
-The first, which we have labeled ``OLD'' in figures and tables,
+Our user studies evaluated two versions of the Tor Launcher interface.
+The first, which we have labeled OLD in our figures and tables,
 is the current version being distributed with Tor Browser.
-The second, ``NEW,'' is the prototype we designed
+The second, NEW, is the prototype that we designed
 in order to provide better usability. Below are the empirical and 
@@
 \begin{enumerate}
-    \item {\bfseries Active configuration time:} How much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-    \item {\bfseries  Time to completion:} How long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-    \item {\bfseries Task completion rate:} What percentage of users can successfully connect to Tor in a given condition.
+    \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
+    \item {\bfseries Task completion rate:} what percentage of users can successfully connect to Tor in a given condition.
 \end{enumerate}
@@
 Though there were new releases during the experiments,
-we tested the same version across all participants to not introduce
+we used the same version across all participants to not introduce
 confounding factors.
@@
 For both user studies, we simulated three censorship environments,
-which we refer to as ``E1,'' ``E2,'' and ``E3,'' in order of increasing severity.
+which we refer to as E1, E2, and E3, which are in  the order of increasing severity.
 We designed the environments to be representative
@@
 and wikipedia.org.
-(Reading a page on en.wikipedia.org was the participants' main goal.)
+(The participants' main goal in the experiment was to read a page on en.wikipedia.org.)
 To succeed in this environment,
-participants had only to click ``Connect'' on the first screen;
+participants only had to click ``Connect'' on the first screen;
 additional configuration was possible but unnecessary.
@@
 it additionally blocks the IP addresses of public Tor relays
-and directory authorities, simulating a censor that knows
+and directory authorities, simulating a censor who knows
 about circumvention and tries to stop it.
-In this environment, simply clicking ``Connect'' will not work;
+In this environment, simply clicking ``Connect'' does not work;
 participants had to select a built-in bridge
@@
 (Representative of countries such as China and Syria.)
-The E3 environment blocks websites and Tor relays as in E1 and E2;
+The E3 environment blocks websites and Tor relays like E1 and E2
 and additionally blocks the built-in default bridge IP addresses
@@
 to accomplish typical tasks and taking note of long sequences or cumbersome
-steps. To focus our observations, we performed a heuristic evaluation to mark tasks
+steps. In addition, we performed a heuristic evaluation to mark tasks
 likely to cause confusion for users during our study.
@@
 We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
-at least one person who has only heard of Tor, and exactly one person who has previously used Tor
-. We tried to evenly distribute any participants who had technical
+at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
 expertise or used particular security tools throughout the censorship environments.
@@
 4 participants had used Tor before;
-5 had heard of Tor but not used it;
-and the remaining 8 had never heard of Tor nor used it.
+5 had heard of Tor but had not used it;
+and the remaining 8 had never heard nor used it.
 
 \subsection{Procedure}
-The one-hour, single-participant procedure began when a participant enters a small 
+The one-hour, single-participant procedure begun when a participant entered a small 
 room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
 Each participant is informed of the risks and purpose of the study.
-A researcher read a script that informed the participant of the simulated censorship environment and
+A researcher informed the participant of the simulated censorship environment and
 instruct them to visit sample blocked and unblocked websites
-in a standard browser, to show what it looks like when a site is blocked (Appendix~\ref{qualitative-script}).
+in a standard browser (Appendix~\ref{qualitative-script}). 
+This shows participants what a blocked site looks like in a browser. 
 Then, the participant was asked to complete a worksheet that gives information
@@
 our goal was to evaluate the user interface, not to test users with a browsing task.
-After instructions, the researchers stepped out of the room so that there was no interaction
+After instructions, the researchers stepped out of the room.There was no interaction
 between the participant and researcher for the rest of the session.
@@
 We asked three standard questions asking about their general experience, 
-confusing interface features, and feedback for improvements. We followed up
+interface features they found confusing, and feedback for improvements. We followed up
 with specific questions prompted from watching their screen. 
@@
 
-\noindent {\bfseries Challenge 2: Users do not know if they should connect directly or configure a connection.} 
+\noindent {\bfseries Challenge 2: Users did not know if they should connect directly or configure a connection.} 
 Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to.
@@
 
-\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport.}
+\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport to use.}
 On the bridge configuration screen, participants were confused by the names of the bridge transports.
@@
 
-\noindent {\bfseries Challenge 4: Users do not know when they are wrong.} 
+\noindent {\bfseries Challenge 4: Users did not know when they are wrong.} 
 Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
@@
 
-\noindent {\bfseries Challenge 5: Users assume they are wrong when they are right.}
+\noindent {\bfseries Challenge 5: Users assumed they are wrong when they are right.}
 The progress bar has a bug that causes it to update only when the level of progress increases.
-If progress bar reaches a 90\% and fails, the next attempt will apparently have regressed to 0\% and remain there until the progress reaches >90\%.
-Due to this, participants assumed that their subsequent attempts were wrong, even if they were correct.
+If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
+Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
 \pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
@@
 \begin{enumerate}
-\item {\bfseries Users do not know what to do.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference between bridges, pluggable transports, and proxies.
-Participants did not know how to configure these network components without any additional instructions.
-\item {\bfseries User feedback is too technical, missing, or misleading.} Participants did not understand the error messages, log lines, and other text in the interface.
+\item {\bfseries Users do not know how to connect to Tor.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference among bridges, pluggable transports, and proxies.
+Participants did not know how to configure these network components without explicit additional instructions.
+\item {\bfseries Feedback is too technical, missing, or misleading.} Participants did not understand the error messages, log lines, and other text in the interface.
 Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e.
@@
 
-To address too technical, missing, or misleading feedback, we made the following changes:\\ 
+To address feedback that is too technical, missing, or misleading, we made the following changes:\\ 
 \begin{enumerate}
@@
 What users now see on the progress bar reflects the reality of the progress.
-\item {\bfseries Made the interface text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process.
-Since users generally could not understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.
+\item {\bfseries Made the interface text less technical.} We made the text more task-centric by focusing on instructing users through the configuration process.
+Since users generally did not understand the technical concepts sufficiently to influence their decisions, we thibk giving direct guidance is a better option.
 \item {\bfseries Added system status visibility.} Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings.
@@
 
-To help clarify with interacting network components with censorship circumvention, we made the following changes:\\
+To clarify with interacting network components with censorship circumvention, we made the following changes:\\
 
@@
 After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
-collecting their demographics. All users were instructed to sit until the end of the experiment,
+that collected their demographics. All users were instructed to sit until the end of the experiment,
 regardless of when they had completed their task. After the 40 minutes, 
@@
 Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
-Ideally, users should be able to connect to Tor within a couple of minutes, regardless of their censorship environment.
+Ideally, users should be able to connect to Tor within a few minutes, regardless of their censorship environment.
 We propose ideas on how to achieve this in section~\ref{recommendations}.
@@
 \item {\bfseries People waited a long, long time at the progress bar.}
-From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are lost for what to do and choose to wait in frustration.
+From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are who are uncertain wait without taking additional actions.
 \end{description}
@@
 This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 64\% of participants who failed their first attempt.
-Users in more difficult censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
+Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
 \item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy.
@@
 a direct connection when we expected them to fail.
-We believe this is acceptable, since 
+We believe this is acceptable because 
 the first study was not used to quantify failures or successes, 
@@
 
-We did not test cases in which the user is required to configure a custom bridge or proxy. Our participants were from one geographic location in the United States and were able to speak English.
+We chose to focus on more common cases, and did not simulate environments that requires users to configure a custom bridge or proxy.
+Although users in the wild can download interfaces that are not in their native language, we know how often this happens.
+We tested the English version of the Tor interface on English speaking participants.
 
 \section{Future Work} 
-Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers.
+We collaborated and communicated with Tor developers throughout the qualitative user study, redesign of the interface, and the quantitative user study.
 Redesigning the configuration interface was a mutual interest.
@@
 We test the impact of our changes on 116 participants.
-We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with no decrease in success rates.
+We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with reduction in success rates.
 {\color {red} TODO: add more here.} Our analysis suggests ways to improve the Tor interface as well as some potential opportunities for further research.

### 2016-05-07 experiment/processing/graphs.R
time_to_success.pdf no longer used.

@@ -46,9 +46,6 @@ time_to_success_plot <- function(participants) {
   p
 }
 
-p <- time_to_success_plot(participants)
-ggsave("time_to_success.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
-
 p <- time_to_success_plot(clamp_time_to_success(participants, maxtime))
 ggsave("time_to_success_clamped.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 

### 2016-05-07 experiment/processing/graphs.R
Make time_to_success_plot take edges, not participants.
Now we ignore time_to_success and instead just sum the edge durations.

@@ -26,7 +26,9 @@ if (any(is.na(edges$userid))) {
 # TIME TO SUCCESS #
 ###################
 
-time_to_success_plot <- function(participants) {
+time_to_success_plot <- function(edges) {
+  participants <- aggregate(duration ~ label + success + seat + runid, data=edges, sum)
+  colnames(participants)[colnames(participants)=="duration"] <- "time_to_success"
   minutes_to_success <- participants$time_to_success/60
   max_minutes <- max(minutes_to_success, na.rm=T)+9
   p <- ggplot(data.frame(participants, minutes_to_success), aes(x=label, y=minutes_to_success), environment=environment())
@@ -46,7 +48,7 @@ time_to_success_plot <- function(participants) {
   p
 }
 
-p <- time_to_success_plot(clamp_time_to_success(participants, maxtime))
+p <- time_to_success_plot(edges)
 ggsave("time_to_success_clamped.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 
 # Assign each environment a color (E1=blue, E2=orange, E3=green), with NEW

### 2016-05-07 experiment/processing/common.R
Factor out is_active_edge function.

@@ -117,6 +117,10 @@ pad_edges <- function(edges, maxtime) {
 	rbind(edges, new.edges)
 }
 
+is_active_edge <- function(edges) {
+	!(edges$dst %in% c("not_running", "starting", "progress"))
+}
+
 common_theme <- function(p) {
 	p <- p + theme_minimal()
 	p <- p + theme(text=element_text(size=8))

### 2016-05-07 experiment/processing/graphs.R
Make time_to_success_active_clamped.pdf.
This is the time_to_success graph, but only counting active edges.

@@ -51,6 +51,9 @@ time_to_success_plot <- function(edges) {
 p <- time_to_success_plot(edges)
 ggsave("time_to_success_clamped.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 
+p <- time_to_success_plot(edges[is_active_edge(edges), ])
+ggsave("time_to_success_active_clamped.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
+
 # Assign each environment a color (E1=blue, E2=orange, E3=green), with NEW
 # being more saturated and OLD being less saturated.
 palette <- c(

### 2016-05-07 pets2017-paper/pets2017-paper.tex
Dump time_to_success_active_clamped into the paper.
comment out error discussion from success rate

@@
 
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{warning.png}
-\caption{
-A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
-which appears silently and does not interrupt the progress bar. 
-This warning was generated by entering in syntactically correct but invalid proxy settings,
-a mistake that prevents users from ever connecting to the Tor network. 
-Users are never directly notified of this error through an error message or a timeout message.
-Our participants made this error during our experiments, along with others that they were not notified about. 
-}
-\label{fig:warning}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{log-messages.png}
-\caption{
-The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
-These log lines were the result of entering in syntactically correct but invalid proxy settings,
-a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
-technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
-}
-\label{fig:warning_log}
-\end{figure}
-
-We believe that the added advice on what to try next on error messages would have improved the rate of success.
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=.5\textwidth]{warning.png}
+%\caption{
+%A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
+%which appears silently and does not interrupt the progress bar. 
+%This warning was generated by entering in syntactically correct but invalid proxy settings,
+%a mistake that prevents users from ever connecting to the Tor network. 
+%Users are never directly notified of this error through an error message or a timeout message.
+%Our participants made this error during our experiments, along with others that they were not notified about. 
+%}
+%\label{fig:warning}
+%\end{figure}
+
+%\begin{figure}[t]
+%\centering
+%\includegraphics[width=.5\textwidth]{log-messages.png}
+%\caption{
+%The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
+%These log lines were the result of entering in syntactically correct but invalid proxy settings,
+%a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
+%technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
+%}
+%\label{fig:warning_log}
+%\end{figure}
+%
+%We believe that the added advice on what to try next on error messages would have improved the rate of success.
 However, only 1 of 116 participants saw an error during the experiment.
@@
 The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
-
-That participant was using the new interface and was told that the bridge configuration was the source of the error.
+%
+%That participant was using the new interface and was told that the bridge configuration was the source of the error.
 The participant heeded the interface's advice to reconfigure the bridge options.

### 2016-05-07 pets2017-paper/pets2017-paper.tex
switch to median times over aggregate times. This is before the bug was fixed for 3 participants; TODO: update the figures.

@@
 The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
-Logs show that participants spent 64\% of their overall time at the progress screen.
-Participants using the new interface and old interface spent approximately the same amount of absolute time on the progress screen (359 minutes versus 339 minutes, respectively). 
-Table ~\ref{table:overall_time} shows the percentage of time spent on each screen,
-computed by the total number of minutes all participants spent on each screen.
+Logs show that participants spent 58\% of their overall time at the progress screen.
+{\color {red} discuss by environment (time on first) and by version (proxy).}
+Table ~\ref{table:median_time} shows the median percentage of time spent on each screen,
+computed independently for each screen.
 
@@
 
-\begin{table}
+\begin{table}[t]
 \centering
-	\begin{tabular}{c r r r r r}
-	 & First & Proxy & Bridge & Summary & Progress \\
+	\begin{tabular}{c r r r r}
+	& First & Proxy & Bridge & Progress \\
 	\noalign{\hrule}
-	All &  5\% & 17\% & 6\% & 0\% & 64\% \\
-	E1-NEW & 34\% & 4\% & 6\% & 1\% & 50\% \\
-	E1-OLD & 23\% & 35\% & 9\% & N/A & 21\% \\
-	E2-NEW & 5\% & 4\% & 4\% & 1\% & 80\% \\
-	E2-OLD & 4\% & 22\% & 4\% & N/A & 66\% \\
-	E3-NEW & 6\% & 7\% & 4\% & 1\% & 70\% \\
-	E3-OLD & 4\% & 25\% & 9\% & N/A & 60\% \\
+	All & 7\% & 5\% & 4\% & 58\% \\
+	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
+	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
+	E2-NEW & 6\% & 5\% & 5\% & 80\% \\
+	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
+	E3-NEW & 4\% & 3\% & 5\% & 78\% \\
+	E3-OLD & 3\% & 11\% & 6\% & 60\% \\
+	% (median, total) 
+	%All & (7, 5)\% & (5, 17)\% & (4, 6)\% & (58, 64)\% \\
+	%E1-NEW & (28, 34)\% & (0, 4)\% & (0, 6)\% & (60, 50)\% \\
+	%E1-OLD & (30, 23)\% & (0, 35)\% & (0, 9)\% & (29, 21)\% \\
+	%E2-NEW & (6, 5)\% & (5, 4)\% & (5, 4)\% & (80, 80)\% \\
+	%E2-OLD & (7, 4)\% & (18, 22)\% & (8, 4)\% & (45, 66)\% \\
+	%E3-NEW & (4, 6)\% & (3, 7)\% & (5, 4)\% & (78, 70)\% \\
+	%E3-OLD & (3, 4)\% & (11, 25)\% & (6, 9)\% & (60, 60)\% \\
 	\end{tabular}
-\caption{Fraction of time spent on each screen, 
-computed by the total number of minutes all participants spent on each screen. 
-Participants spent most of their time on the progress screen.
-Additionally, participants spent proportionally more time on the proxy screen than on the bridge screen,
-although none of the censorship environments required a proxy.
-Participants spent less time on the proxy screen
-in the ``NEW'' interface (which explicitly stated that they did not need a proxy) compared to the ``OLD.''} 
-\label{table:overall_time}
+\caption{The median percent of time participants spent on each screen, which is not
+necessarily the median absolute time spent on that screen. 
+This percentage independent for each screen; that is, a participant who spent the median percent 
+of time on one screen may not be the same participant who spent the median percent
+of time on other screens.} 
+\label{table:median_time}
 \end{table}
+
+%\begin{table}[t]
+%\centering
+%	\begin{tabular}{c r r r r}
+%	& First & Proxy & Bridge & Progress \\
+%	\noalign{\hrule}
+%	All & 5\% & 17\% & 6\% & 64\% \\
+%	E1-NEW & 34\% & 4\% & 6\% & 50\% \\
+%	E1-OLD & 23\% & 35\% & 9\% & 21\% \\
+%	E2-NEW & 5\% & 4\% & 4\% & 80\% \\
+%	E2-OLD & 4\% & 22\% & 4\% & 66\% \\
+%	E3-NEW & 6\% & 7\% & 4\% & 70\% \\
+%	E3-OLD & 4\% & 25\% & 9\% & 60\% \\
+%	\end{tabular}
+%\caption{The overall percent of time all participants spent on each screen, computed by
+%dividing the aggregate number of time on a screen by the aggregate time on all screens.} 
+%\label{table:overall_time}
+%\end{table}
 
@@
 	\begin{tabular}{c r r}
-	 & Total Active Minutes & \% of Overall Time \\
+	 & Total Active Minutes & Total \% of Overall Time \\
 	\noalign{\hrule}

### 2016-05-07 experiment/processing/info.R

@@ -83,6 +83,7 @@ summary_edges <- edges[edges[,"dst"]== "summary",]
 # 2
 total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)
 active_time_per_user <- aggregate(active_edges$duration ~ active_edges$userid, active_edges, sum)
+active_time_per_user[percent_time] <- 
 not_running_time_per_user <- aggregate(not_running_edges$duration ~ not_running_edges$userid, not_running_edges, sum)
 starting_time_per_user <- aggregate(starting_edges$duration ~ starting_edges$userid, starting_edges, sum)
 progress_time_per_user <- aggregate(progress_edges$duration ~ progress_edges$userid, progress_edges, sum)
@@ -98,14 +99,16 @@ screen_time_per_user <- merge(screen_time_per_user, active_time_per_user, by=c(1
 screen_time_per_user <- merge(screen_time_per_user, not_running_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, starting_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, progress_time_per_user, by=c(1), all=T)
+screen_time_per_user <- merge(screen_time_per_user, first_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, proxy_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, bridge_time_per_user, by=c(1), all=T)
 screen_time_per_user <- merge(screen_time_per_user, summary_time_per_user, by=c(1), all=T)
 screen_time_per_user[is.na(screen_time_per_user)] <- 0
 
 subreport <- function(label, sublabel, selected_edges, denom_edges, f) {
-	cat(sprintf("%s\t%s\t%s\t%s\n", sublabel, label, round(sum(selected_edges[f(selected_edges),]$duration)/60),
-		format_percent(sum(selected_edges[f(selected_edges),]$duration)/sum(denom_edges[f(denom_edges),]$duration))))
+	cat(sprintf("%s\t%s\t%s\t%s\n", sublabel, label, 
+	            round(sum(selected_edges[f(selected_edges),]$duration)/60),
+	            format_percent(sum(selected_edges[f(selected_edges),]$duration)/sum(denom_edges[f(denom_edges),]$duration))))
 }
 
[…]

### 2016-05-08 pets2017-paper/pets2017-paper.tex
Fix percentage of time on each screen.
David found a bug that did not pad edges to maxtime.

@@
 
+\begin{figure}[t]
+\centering
+\includegraphics{time_to_success_active_clamped}
+\caption{
+Active-time configuration.
+}
+\label{fig:time_to_success_active_clamped}
+\end{figure}
+
 In our experiment, participants had 40 minutes to circumvent censorship.
@@
 	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
-	E2-NEW & 6\% & 5\% & 5\% & 80\% \\
+	E2-NEW & 5\% & 5\% & 5\% & 76\% \\
 	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
-	E3-NEW & 4\% & 3\% & 5\% & 78\% \\
-	E3-OLD & 3\% & 11\% & 6\% & 60\% \\
-	% (median, total) 
-	%All & (7, 5)\% & (5, 17)\% & (4, 6)\% & (58, 64)\% \\
-	%E1-NEW & (28, 34)\% & (0, 4)\% & (0, 6)\% & (60, 50)\% \\
-	%E1-OLD & (30, 23)\% & (0, 35)\% & (0, 9)\% & (29, 21)\% \\
-	%E2-NEW & (6, 5)\% & (5, 4)\% & (5, 4)\% & (80, 80)\% \\
-	%E2-OLD & (7, 4)\% & (18, 22)\% & (8, 4)\% & (45, 66)\% \\
-	%E3-NEW & (4, 6)\% & (3, 7)\% & (5, 4)\% & (78, 70)\% \\
-	%E3-OLD & (3, 4)\% & (11, 25)\% & (6, 9)\% & (60, 60)\% \\
+	E3-NEW & 3\% & 3\% & 5\% & 73\% \\
+	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
 	\end{tabular}
@@
 %	\noalign{\hrule}
-%	All & 5\% & 17\% & 6\% & 64\% \\
+%	All & 5\% & 16\% & 6\% & 60\% \\
 %	E1-NEW & 34\% & 4\% & 6\% & 50\% \\
 %	E1-OLD & 23\% & 35\% & 9\% & 21\% \\
-%	E2-NEW & 5\% & 4\% & 4\% & 80\% \\
-%	E2-OLD & 4\% & 22\% & 4\% & 66\% \\
-%	E3-NEW & 6\% & 7\% & 4\% & 70\% \\
-%	E3-OLD & 4\% & 25\% & 9\% & 60\% \\
+%	E2-NEW & 4\% & 3\% & 3\% & 58\% \\
+%	E2-OLD & 4\% & 22\% & 4\% & 65\% \\
+%	E3-NEW & 5\% & 6\% & 4\% & 64% \\
+%	E3-OLD & 4\% & 25\% & 8\% & 56\% \\
 %	\end{tabular}

### 2016-05-08 experiment/processing/info.R
time to success redone, still not significant (but more correct).
Time to success performs a one-tailed mann-whitney U test on
two groups of participants, participants who used NEW and OLD
interfaces. DNFs were given a time to success of 40:08.

@@ -1,7 +1,7 @@
 library(coin)
 source("common.R")
 
-participants <- read_participants()
+participants <- filter_participants(read_participants())
 
 format_percent <- function(x) {
 	sprintf("%5.1f%%", 100*x)
@@ -276,15 +276,17 @@ success_rates = with(participants, aggregate(success, list(env=env, version=vers
 
 cat("\n")
 cat("impact of version on success rates \n")
-wilcox.test(x ~ version, data=success_rates)
+wilcox.test(x ~ version, data=success_rates, paired=FALSE)
 
 cat("impact of version on times to completion \n")
-wilcox.test(time_to_success ~ version, data=clamp_time_to_success(participants, maxtime))
+clamped_time <- clamp_time_to_success(participants, maxtime)
+#one-tailed mann-whitney U for right-tailed data, with DNFs = 40:08. 
+wilcox.test(time_to_success ~ version, data=clamped_time, paired=FALSE, alternative="less")
 
 cat("impact of version on active time \n")
-wilcox.test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user)
-wilcox_test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user)
-
+#one-tailed mann-whitney U for right-tailed data, with DNFs = 40:08-time on progress screen.
+wilcox.test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user, paired=FALSE, alternative="less")
+wilcox_test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user, paired=FALSE, alternative="less")
 
 cat("\n\n\n\n")
 cat("impact of environment on success rates\n")

### 2016-05-08 pets2017-paper/pets2017-paper.tex
time to success redone, still not significant (but more correct).
Time to success performs a one-tailed mann-whitney U test on
two groups of participants, participants who used NEW and OLD
interfaces. DNFs were given a time to success of 40:08.
explain statistical test for active time

@@
 
-\begin{figure}[t]
-\centering
-\includegraphics{time_to_success_active_clamped}
-\caption{
-Active-time configuration.
-}
-\label{fig:time_to_success_active_clamped}
-\end{figure}
-
 In our experiment, participants had 40 minutes to circumvent censorship.
@@
 We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
-Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant in our experiment.
-The bar represents a participants' path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
+Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
+The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
 
@@
 
-The time to success was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
+The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
+With correct configurations, the bootstrap process can take up to two minutes.
+With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.
 Logs show that participants spent 58\% of their overall time at the progress screen.
-{\color {red} discuss by environment (time on first) and by version (proxy).}
-Table ~\ref{table:median_time} shows the median percentage of time spent on each screen,
-computed independently for each screen.
-
-We believe participants spent a long time on the progress screen for a combination of reasons.
-Even with correct configurations, the bootstrap process can take up to two minutes.
-With incorrect settings, we suspect that participants waited because the interface instructs them ``wait a couple minutes.'' A lack of error messages and timeouts on the progress screen, also caused some users to wait indefinitely.
+Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.
 
@@
 of time on one screen may not be the same participant who spent the median percent
-of time on other screens.} 
+of time on other screens. Note that the time spent on the progress bar dominates the 
+time spent in the interface.} 
 \label{table:median_time}
 \end{table}
+
+\begin{figure}[t]
+\centering
+\includegraphics{time_to_success_active_clamped}
+\caption{
+Active-time configuration.
+}
+\label{fig:time_to_success_active_clamped}
+\end{figure}
 
@@
 
-\begin{table}
-\centering
-	\begin{tabular}{c r r}
-	 & Total Active Minutes & Total \% of Overall Time \\
-	\noalign{\hrule}
-	All & 381 & 29\% \\ 
-	E1-NEW & 4 & 45\% \\
-	E1-OLD & 19 & 67\% \\
-	E2-NEW & 15 & 15\% \\
-	E2-OLD & 68 & 31\% \\
-	E3-NEW & 74 & 18\% \\
-	E3-OLD & 200 & 38\% \\
-	\end{tabular}
-\caption{active time {\color {red} add comparable figure to the time to success figure (Fig 9)}.} 
-\label{table:active_time}
-\end{table}
-
 Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection.
 We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-This is a simplified notion active configuration time.
-Some participants searched for help on the web after exiting the interface or on the progress screen.
-
-{\color {red} TODO: explain how this was calculated: across all participants with all of the new and all of the old aggregated, with DNF's getting 40:08 then subtracting the time they spent on the progress screen).
-Say it is mann whitney one tailed.
-} The new interface results a statistically significant reduction in the overall active configuration time.
-(Mann--Whitney $Z = -3.055$, $p = 0.00225$, $r= 0.284$).
+Active configuration time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
+This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.
+
+We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface.
+The new interface results a statistically significant reduction in active configuration time.
+(Mann--Whitney $Z = -2.7$, $p = 0.0032$, $r= 0.25$).
 We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time.

### 2016-05-08 pets2017-paper/pets2017-paper.tex
update time spent on proxy screen in observations

@@
 \item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly.
-Participants with the new interface (which explicitly states that they did not need a proxy) spent 31\% of their active time configuring proxies, perhaps due to not reading the text or not believing the interface.
-Participants in the old interface spent 63\% of their time on the proxy screen.
-We do not understand why users with the new interface chose to configure proxies after explicitly being told that they do not need one.
+Participants with the new interface (which explicitly states that they did not need a proxy) spent about the same time configuring proxies as bridges, whereas users with the old interface spent about twice as much time configuring proxies than bridges.
+We do not understand why users with the new interface spent time configuring proxies after explicitly being told that they do not need one.
 

### 2016-05-08 pets2017-paper/pets2017-paper.tex
talk about statistical tests

@@
 The level of censorship, rather than the interface, had a significant impact on the time to success.
-The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
+%The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). 
 The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
@@
 
+\section{Statistical Tests} 
+From our measurements, we observe that participants with the new interface 
+have a higher rate of success, succeed in less time, and configure their interface in less time. 
+We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
+We do find the the decreased active configuration time to be significant. 
+We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.
+
+%success rate and version
+Each participant had a boolean variable indicating a successful connection to Tor.
+Rates of success were calculated by dividing the number of participants who succeeded the condition over the total number of participants in the condition.
+This gave us six rates of success.
+E1-NEW, E2-NEW, and E3-NEW rates of success were compared against E1-OLD, E2-OLD, and E3-OLD.
+We used a Pearson's Chi-squared test to test the significance of success rates.
+The difference between success rates of participants with the new interface and participants with the old interface was not significant (X-squared = 0.012599, df = 2, p-value = 0.9937).
+
+%time to success and version
+Time to success was measured as the time from the participants started the Tor launcher interface to the first successful bootstrap to the Tor network.
+This measurement was 1) non-normal and heavily right-tailed since participants were less and less likely to succeed as time went on and 2) right-censored at 40 minutes, the maximum time of the experiment.
+Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
+Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
+We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant (Z = -1.5451, p-value = 0.06116).
+
+%active time and version
+Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen.
+For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes.
+This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success.
+Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
+We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant (Z = -3.4069, p-value = 0.0003286).
+
 \section{Custom Bridge Attempts} 

### 2016-05-08 experiment/processing/info.R

@@ -276,16 +276,19 @@ success_rates = with(participants, aggregate(success, list(env=env, version=vers
 
 cat("\n")
 cat("impact of version on success rates \n")
-wilcox.test(x ~ version, data=success_rates, paired=FALSE)
+success_chi <- data.frame(c("E1","E2", "E3"), c(1,0.9473684,0.6500000), c(1,0.8421053,0.5000000))
+names(success_chi)[1]<-paste("env")
+names(success_chi)[2]<-paste("success_new")
+names(success_chi)[3]<-paste("success_old")
+chisq.test(success_chi[,2:3])
 
 cat("impact of version on times to completion \n")
 clamped_time <- clamp_time_to_success(participants, maxtime)
-#one-tailed mann-whitney U for right-tailed data, with DNFs = 40:08. 
-wilcox.test(time_to_success ~ version, data=clamped_time, paired=FALSE, alternative="less")
+#one-tailed mann-whitney U for right-tailed data, with DNFs = 40:08.
+wilcox_test(time_to_success ~ version, data=clamped_time, paired=FALSE, alternative="less")
 
 cat("impact of version on active time \n")
 #one-tailed mann-whitney U for right-tailed data, with DNFs = 40:08-time on progress screen.
-wilcox.test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user, paired=FALSE, alternative="less")
 wilcox_test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user, paired=FALSE, alternative="less")
 
 cat("\n\n\n\n")

### 2016-05-08 pets2017-paper/pets2017-paper.tex
Update conclusion.

@@
 We test the impact of our changes on 116 participants.
-We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection, with reduction in success rates.
-{\color {red} TODO: add more here.} Our analysis suggests ways to improve the Tor interface as well as some potential opportunities for further research.
+We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection and spent more of that time configuring the necessary components.
+We also discuss the common reasons for failing to connect to the Tor network, general behavioral trends of participants across conditions, make suggestions to to improve the Tor interface, and discuss potential opportunities for further research.
 

### 2016-05-09 pets2017-paper/pets2017-paper.tex
future work rewording.

@@
 \section{Future Work} 
-We collaborated and communicated with Tor developers throughout the qualitative user study, redesign of the interface, and the quantitative user study.
-Redesigning the configuration interface was a mutual interest.
+Our goal was to deploy impactful, tested changes the Tor configuration interface.
 In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
-We plan to work with Tor developers to integrate helpful changes.
-This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.
-
-We took an approach that optimized for the average case user manually configuring a connection.
-Additional user studies that focus specifically on users in heavily censored environments or increasing the amount of automation in the configuration process may yield higher rates of success and faster time to success.
-We list 3 approaches that can seem worth exploring.
+Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away.
+For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed.
+However, we list some alternative approaches that seem worth exploring.
 \\
@@
 \begin{description}
-\item{\bfseries Automate the configuration.} One naive way to automate the process users should take, trying the most likely configurations to work in order.
-This process leaks to network eavesdroppers that the user is connecting to the Tor network, but this would not harm users today (as far as we know).
-Our study finds that 64\% users fail on the first try when trying to circumvent an advanced censor.
-However, further research can explore if and how much increased risk is associated with this approach.
-\item{\bfseries Ask about the risk.} Automating the configuration process for all who are not at risk and offering manual configuration to those who would like to be more cautious is an alternative to complete automation.
-The complication with this approach is that we would need to ask the users whether they would be at risk if someone learned that they are connecting to the Tor network.
-Users may not be qualified to answer this question or may not trust Tor with this information.
-\item{\bfseries Ask if users know what to do.} Automating the process for users who do not know how to configure a bridge or proxy could be an alternative option.
-However, there are ethical implications of making mistakes on behalf of users at risk.
+\item{\bfseries Automate the configuration.} The most efficient way to connect as many users to the Tor network is to automatically configure their connection on start.
+A naive automation is to try configurations that would most likely work, in order (i.e.
+a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
+This leaks to network eavesdroppers that the user is connecting to the Tor network.
+We do not know how much risk is associated with this approach.
+\item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk.
+The complication with this approach is that users may not be qualified to answer if they are at risk or may not trust Tor with this information.
+\item{\bfseries Ask if users know what to do.} Another alternative to naive automation is to offer manual configuration to those that know how to configure their connection and to automate the process for users who do not know how to configure their connection.
+This may prevent the most mistakes, but does not account for the users' risk associated with using Tor.
+\item{\bfseries Suggest configurations.} A way to help users without any automation or questions is to give users information about what would work in their country.
+The first page of the configuration interface can show a list of countries with a corresponding recommended configuration.
+This approach does not require users to answer about their risk, technical ability, or location.
+However, it does require that the user trust the given advice and to correctly configure their settings based on this advice.
+\item{\bfseries Assign configurations.} This is a smart way to automate connections to the Tor network.
+Upon start, the interface detects proxy settings and uses them, if any.
+Then, all users connect to bridges that will always work (such as meek bridges), which assign them a guard relay based on their location, effectively assigning bridges for the user.
 \end{description}

### 2016-05-09 pets2017-paper/pets2017-paper.tex
additional fixes.

@@
 We find that our changes result in a significant reduction 
-in the time spent configuring a connection, while maintaining the same rate of success. We
+in the time spent configuring a connections. We
 conclude with recommendations for changes to the current configuration interface and discuss
@@
 measuring participants' interactions with the interface in various censorship environments.
+We designed the environments to be representative important real-world
+cases of censorship, but they do not imitate any particular censorship environment.
 The first user study is a small-scale, qualitative experiment that collected 
@@
 
+{\color {red} TODO: REDO THIS PARAGRAPH COMPLETELY}
 We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
@@
 \begin{enumerate}
+    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition.
+This measures how many users are able to configure their connections with the interface.
+    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
+This measures how much time is required for a user to connect to the Tor network.
     \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-    \item {\bfseries Task completion rate:} what percentage of users can successfully connect to Tor in a given condition.
+This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
 \end{enumerate}
 
-An ideal interface would guide users though the configuration process while communicating system state and managing errors along the way.
-Users would be able to connect to the Tor network in a couple of minutes.
+An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
 
@@
 to accomplish typical tasks and taking note of long sequences or cumbersome
-steps. In addition, we performed a heuristic evaluation to mark tasks
-likely to cause confusion for users during our study.
+steps. In addition, we performed a heuristic evaluation to mark
+likely causes of confusion for users during our study.
 
@@
 Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to.
-Other participants were not able to determine that a failed direct connection to the Tor network was the result of the Tor network being censored.
+Other participants tried a direct connection because they did not know what to do, but configuring their connection seemed hard.
 \\
@@
 \pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
-\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
 I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
@@
 Participants assumed they were not making progress, due to the progress bar not giving feedback on subsequent attempts.
-\item {\bfseries Users do not understand censorship circumvention cues.} Participants did not understand how censorship worked and what would circumvent censorship in their environment, despite adequate evidence that signals what components are necessary and unnecessary.
-A working connection to the Internet did signal to participants that they did not need a proxy; a blocked website did not translate to a blocked domain name; a failed direct connection did not equate to a blocked Tor relay.
+\item {\bfseries Users do not understand censorship circumvention cues.} With enough technical background, there are  signals to what components are necessary and unnecessary.
+A connection to the Internet indicates that no proxy is required.
+A failed direct connection indicates a blocked Tor relay.
+A failed hard-coded bridge connection indicates a blocked bridge relay.
+However, the average user does not understand these signals.
  \end{enumerate}
@@
 The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy.
-\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored situations, to urge users to not assume that a website censorship necessitates configuration.
+\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored environments, to urge users in mild censorship environments to try a direct connection.
 \item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work. 
@@
 	\end{tabular}
-\caption{The median percent of time participants spent on each screen, which is not
+\caption{The median percent of time spent on each screen, which is not
 necessarily the median absolute time spent on that screen. 
-This percentage independent for each screen; that is, a participant who spent the median percent 
+This percentage is computed independently for each screen; that is, a participant who spent the median percent 
 of time on one screen may not be the same participant who spent the median percent
@@
 \caption{
-Active-time configuration.
+Active configuration time, by censorship environment and interface.
+The dots show the raw active configuration times,
+while the boxplots show the medians and interquartile ranges.
+Here, non-finishing participants' active time was computed by
+subtracting the amount of time spent on the progress screen from the 
+the maximum time of 40:08.
 }
@@
 
-Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection.
+Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}).
 We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
@@
 (Mann--Whitney $Z = -2.7$, $p = 0.0032$, $r= 0.25$).
-We believe that getting rid of the technical questions and telling participants that they did not need a proxy attributed to the reduction in time.
+The small effect size may be due to the fact that the reduction in time mostly applied to participants in E3.
 %The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
@@
 It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-\item {\bfseries Didn't know what to do next (6/21): P91, P92, P95, P110, P113, P116} These participants in E3 did not know what to do next after a direct connection and a default obfs3 bridge connection.
+\item {\bfseries Only tried recommendations (6/21): P91, P92, P95, P110, P113, P116} These participants in E3 did not know what to do next after a direct connection and a default obfs3 bridge connection.
 They often tried those configurations again or gave up.
@@
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
-Participants who are not accustomed to using Windows machines may have been slower than usual to complete the given task, but this should affect all of our conditions equally.
+Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.
 
@@
 a client contacts when initiating a non-bridge connection.
-This, combined with new relays appearing in the network on an hourly basis,
-enabled a small number of participants to succeed with
-a direct connection when we expected them to fail.
+New relays also appeared in the network on an hourly basis,
+which enabled a small number of participants to succeed with
+a direct connection when that configuration should have failed.
 We believe this is acceptable because 
-the first study was not used to quantify failures or successes, 
+the qualitative user study was not used to quantify failures or successes, 
 but to explore possible problems.
-We fixed this problem in our second study by blocking the directory authorities.
+We fixed this problem in our quantitative user study by blocking the directory authorities.
 
@@
 Our study was conducted in a laboratory setting, which can cause our participants to be under or over-motivated.
-Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website or service.
-The nature of the experiment places social pressure to attempt connect for the whole duration of the session, whereas participants may have given up earlier if they were not in a real-world setting.
+Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website.
 
 We chose to focus on more common cases, and did not simulate environments that requires users to configure a custom bridge or proxy.
-Although users in the wild can download interfaces that are not in their native language, we know how often this happens.
+Although users in the wild can download interfaces that are not in their native language, we do not know how often this happens.
 We tested the English version of the Tor interface on English speaking participants.

### 2016-05-09 pets2017-paper/pets2017-paper.tex
revised intro.

@@
 measuring participants' interactions with the interface in various censorship environments.
-We designed the environments to be representative important real-world
-cases of censorship, but they do not imitate any particular censorship environment.
 The first user study is a small-scale, qualitative experiment that collected 
@@
 
-{\color {red} TODO: REDO THIS PARAGRAPH COMPLETELY}
-We find that users do not know if they require additional configuration to circumvent censorship, make incorrect assumptions based on interface layout, and do not know what to do in the event of a failure.
-We redesign the interface to decrease the technical knowledge required, give explicit advice on configuring network components, and fix misleading feedback that causes users to assume they are wrong when they are right.
-Our changes decreased the time participants spent configuring their connections, with no difference in success rates.
-We conclude with recommendations of changes that we believe will help the most users circumvent censorship and connect to Tor.
+In this paper, we contribute the following: \\
+\begin{itemize}
+\item 6 common challenges encountered during the configuration process and their underlying causes
+\item 10 changes to the configuration interface which we hope alleviates the common challenges
+\item 116 logs of real world user attempts to connect to Tor in three different censorship environments
+\item 4 reasons why users failed to connect to Tor
+\item 5 recommendations of configuration interface changes to help more users connect and save time
+\item 5 alternative  approaches to bootstrapping a connection that leverage varying degrees of automation
+\end{itemize}
+We hope that our work helps users circumvent censorship and connect to Tor.
 

### 2016-05-09 pets2017-paper/pets2017-paper.tex
changing where redesign section starts, formatting tweaks.

@@
 
-In this paper, we contribute the following: \\
+In this paper, we contribute the following:
+\smallskip
 \begin{itemize}
@@
 cases of censorship. They are not intended to imitate
-any particular country's censorship environment.
-
-\smallskip
+any particular country's censorship environment.\\
 
 \begin{description}
-\item[E1: Mild censorship]
+\item [E1: Mild censorship.]
 (Representative of countries such as France and Australia.)
@@
 participants only had to click ``Connect'' on the first screen;
-additional configuration was possible but unnecessary.
-% (Representative of countries such as France and Australia.)
-
-\item[E2: Intermediate censorship]
+additional configuration was optional.
+
+\item [E2: Intermediate censorship.]
 (Representative of countries such as Tunisia.)
-The E2 environment blocks websites as in E1;
-it additionally blocks the IP addresses of public Tor relays
+The E2 environment blocks websites as in E1 and
+additionally blocks IP addresses of public Tor relays
 and directory authorities, simulating a censor who knows
@@
 A custom bridge would work but was not necessary.
-% (Representative of countries such as Tunisia.)
-
-\item[E3: Comprehensive censorship]
+
+\item [E3: Comprehensive censorship.]
 (Representative of countries such as China and Syria.)
 The E3 environment blocks websites and Tor relays like E1 and E2
-and additionally blocks the built-in default bridge IP addresses
-found in the Tor Browser source code.
-To succeed in this environment, participants had either to select
-one of the ``meek'' built-in bridges (no other type would work),
-or to acquire their own custom bridge and enter it manually.
-% (Representative of countries such as China and Syria.)
+and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
+To succeed in this environment, participants had to select
+one of the ``meek'' built-in bridges (no other type would work)
+or acquire their own custom bridge and enter it manually.
 \end{description}
@@
 mapping domain names to the address 127.0.0.1.
-For IP address blocking, we used Windows Firewall rules.
+We used Windows Firewall rules for IP address blocking.
 
@@
 
-\noindent {\bfseries Challenge 1: Users did not understand what proxies, bridges, and pluggable transports were.}
-Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary:
+\begin{description}
+\item {\bfseries Users did not understand what proxies, bridges, and pluggable transports were.}
+Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary.
 
@@
 
+\smallskip
 \pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
+\smallskip
 \pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
-
-\noindent {\bfseries Challenge 2: Users did not know if they should connect directly or configure a connection.} 
+\smallskip
+
+\item {\bfseries Users did not know if they should connect directly or configure a connection.}
 Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to.
 Other participants tried a direct connection because they did not know what to do, but configuring their connection seemed hard.
-\\
-
-\noindent {\bfseries Challenge 3: Users did not know how to choose which bridge and pluggable transport to use.}
+
+\item {\bfseries Users did not know how to choose which bridge and pluggable transport to use.}
 On the bridge configuration screen, participants were confused by the names of the bridge transports.
@@
 
+\smallskip
 \pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
+\smallskip
 %\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
@@
 
-\noindent {\bfseries Challenge 4: Users did not know when they are wrong.} 
+\item {\bfseries Users did not know when they are wrong.}
 Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
-When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).\\
-
-\noindent {\bfseries Challenge 5: Users assumed they are wrong when they are right.}
+When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
+
+\item {\bfseries Users assumed they are wrong when they are right.}
 The progress bar has a bug that causes it to update only when the level of progress increases.
@@
 Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
+
+\smallskip
 \pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
+\smallskip
 \pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-
-\noindent {\bfseries Challenge 6: Users assume that proxy is required after a failed connection.} 
+\smallskip
+
+\item {\bfseries Users assume that proxy is required after a failed connection.}
 All of our participants who failed to connect (5 of 16) failed for this reason.
@@
 
+\smallskip
 \pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
-
-From interviewing our participants, we found that these challenges result because users are not familiar with technical or Tor-specific terms, feedback on progress or errors was inconsistent, and the interface did not instruct users on what to do in the event of a failure.
+\end{description}
+
+From interviewing our participants, we found that these challenges are the result of these underlying causes: \\
+
+\begin{description}
+\item {\bfseries Users do not know how to connect to Tor.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference among bridges, pluggable transports, and proxies.
+Participants did not know how to configure these network components without explicit additional instructions.
+\item {\bfseries Feedback is too technical, missing, or misleading.} Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e.
+a syntactically correct but invalid proxy).
+If participants did see an error message, they did not understand it.
+The progress bar bug also caused users to wrongly assume they were not making progress since it did not give feedback on subsequent attempts.
+\item {\bfseries Users do not understand censorship circumvention cues.} With enough technical background, there are  signals to what components are necessary and unnecessary.
+A connection to the Internet indicates that no proxy is required.
+A failed direct connection indicates a blocked Tor relay.
+A failed hard-coded bridge connection indicates a blocked bridge relay.
+However, the average user does not understand these signals.
+\end{description}
+
+The challenges users faced in the qualitative experiment and the respective underlying causes are used as feedback for redesigning the configuration interface.
 
 \section{Redesigning the Configuration Interface}
+We make ten changes to the Tor launcher configuration interface to help users connect to Tor.
+Since users did not know how to connect to Tor, we added advice where our users have previously struggled.
+Specifically, the following three changes were made to give users more information in during configuration: \\
+
 \label{redesign}
@@
 
-Many users struggle with the configuration process. Our changes to the configuration interface address the causes for these issues. These underlying causes are:\\
-
-\begin{enumerate}
-\item {\bfseries Users do not know how to connect to Tor.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference among bridges, pluggable transports, and proxies.
-Participants did not know how to configure these network components without explicit additional instructions.
-\item {\bfseries Feedback is too technical, missing, or misleading.} Participants did not understand the error messages, log lines, and other text in the interface.
-Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e.
-a syntactically correct but invalid proxy).
-Participants assumed they were not making progress, due to the progress bar not giving feedback on subsequent attempts.
-\item {\bfseries Users do not understand censorship circumvention cues.} With enough technical background, there are  signals to what components are necessary and unnecessary.
-A connection to the Internet indicates that no proxy is required.
-A failed direct connection indicates a blocked Tor relay.
-A failed hard-coded bridge connection indicates a blocked bridge relay.
-However, the average user does not understand these signals.
- \end{enumerate}
-
- \label{redesign}
 \begin{figure*}[t]
@@
 
-To help users know what to do, we made the following changes:\\
-
 \begin{enumerate}
-\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user.
+\item Added instructions on what to try next on errors.
+When an error occurs, text advice on what to try next is shown to the user to help them recover from the error.
 The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy.
-\item {\bfseries Added guidance on choosing to connect or configure.} We labeled the configure option specifically for user in heavily censored environments, to urge users in mild censorship environments to try a direct connection.
-\item {\bfseries Added explicit advice on choosing bridge transports.} The recommended bridge type is still obfs3. We added text that advises users to try a meek bridge if obfs3 does not work. 
+\item Added guidance on choosing between connect and configure.
+Before, the interface only informed users that the connect option worked some of the time, but did not specify why that was so.
+We labeled the configure option as a manual option  specifically for users in heavily censored environments.
+\item Added explicit advice on choosing bridge transports.
+Users did not know which bridges to choose if they were in E3, which requires users to choose a meek or custom bridge.
+We added text that advises users to try a meek bridge if obfs3 does not work.
 \end{enumerate}
 
-To address feedback that is too technical, missing, or misleading, we made the following changes:\\ 
+Users found the feedback to be more confusing than helpful, since error messages were technical and progress bar was misleading.
+We make the following changes to make feedback insightful and reflective of system state:\\
 \begin{enumerate}
 \setcounter{enumi}{3}
-\item {\bfseries Progress bar feedback is accurate.}  We fixed the bug that caused the progress bar to not update on subsequent attempts.
+\item Progress bar feedback is accurate.
+We fixed the bug that caused the progress bar to not update on subsequent attempts.
 What users now see on the progress bar reflects the reality of the progress.
-\item {\bfseries Made the interface text less technical.} We made the text more task-centric by focusing on instructing users through the configuration process.
+\item Made the interface text less technical.
+We made the text more task-centric by focusing on instructing users through the configuration process.
 Since users generally did not understand the technical concepts sufficiently to influence their decisions, we thibk giving direct guidance is a better option.
-\item {\bfseries Added system status visibility.} Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings.
+\item Added system status visibility.
+Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings.
 The same information is shown on the progress screen while the connection is in progress.
 We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
-This aligns with the mental model we are trying to build in the user.
 \end{enumerate}
 
-To clarify with interacting network components with censorship circumvention, we made the following changes:\\
+Our users had little technical background. We made the following changes to make the interface more compatible for the average user: \\
 
@@
 \setcounter{enumi}{6}
-\item {\bfseries Eliminated technical questions.}  We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
+\item Eliminated technical questions.
+We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
 This are two fewer screens in the revised interface.
-\item {\bfseries Added auto-detection of proxies.} In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration.
-This purely local detection does not carry the potential risks of network probing and should be safe even for at-risk users.
-(In our experiment, we simulated the auto-detection by hard-coding the fact that a proxy was not required.)
-\item {\bfseries Switched ordering to configure proxies first.} To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen.
+\item Added auto-detection of proxies.
+In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration.
+This purely local detection does not carry any risks nor reveal to network eavesdroppers that the user is using Tor.
+(We simulated the auto-detection by hard-coding the fact that a proxy was not required.)
+\item Switched ordering to configure proxies first.
+To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen.
 Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
@@
 The small effect size may be due to the fact that the reduction in time mostly applied to participants in E3.
-%The impact of the environment on active time is significant (Kruskal--Wallis $\chi^2 = 51.978$, $\mbox{df} = 2$, $p = 10^{-11}$)
 
@@
 
-\subsubsection{Reasons for Failure} 
+\subsubsection{Failures} 
 Failure is common.
@@
 \begin{description}
-\item {\bfseries Only connected directly (7/21): P57, P74, P76, P90, P93, P108, P112} These participants tried a direct connection.
+\item {\bfseries Only connected directly (7/21).} P57, P74, P76, P90, P93, P108, P112 tried a direct connection.
 When that failed, they tried the same configuration, over and over, no matter how many times they failed.
 It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-\item {\bfseries Only tried recommendations (6/21): P91, P92, P95, P110, P113, P116} These participants in E3 did not know what to do next after a direct connection and a default obfs3 bridge connection.
+
+\item {\bfseries Only tried recommendations (6/21).} P91, P92, P95, P110, P113, P116, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
 They often tried those configurations again or gave up.
-\item {\bfseries Thought that they needed a proxy (5/21): P75, P94, P107, P109, P115} After a couple failed attempts, these participants assumed that they needed a proxy.
-They spent the time trying to configure a proxy, usually without trying other bridges.
-\item {\bfseries Used the bridges auto-responder incorrectly (2/21): P96, P111} Two participants in our heavy censorship environment figured that the recommended bridge and most hard-coded bridges were not working and found the auto-responder through the help button.
-However, they all failed to get a response.
+
+\item {\bfseries Thought that they needed a proxy (5/21).} P75, P94, P107, P109, P115 assumed that they needed a proxy.
+They spent their time trying to configure a proxy, usually without trying other bridges.
+
+\item {\bfseries Used the bridges auto-responder incorrectly (2/21).} P96, P111, who were in E3, emailed the bridges auto-responder to get custom bridges.
+However, they formatted the message incorrectly and thus failed to get a response.
 For details, see Appendix~\ref{failed-participants}.
-\end{description}
 
@@
 Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
+\end{description}
 
@@
 Across both versions of the interface, only one participant ever saw an error message.
-We tried to make error messages more instructive and understandable, bu since participants in our experiment did not encounter error messages, we cannot evaluate their efficacy.
+We tried to make error messages more instructive and understandable, since participants in our experiment did not encounter error messages, we cannot evaluate them.
 

### 2016-05-09 pets2017-paper/pets2017-paper.tex
conclusion rewording

@@
 \item {\bfseries Only connected directly (7/21).} P57, P74, P76, P90, P93, P108, P112 tried a direct connection.
-When that failed, they tried the same configuration, over and over, no matter how many times they failed.
+When that failed, they tried the same option, over and over, no matter how many times they failed.
 It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
@@
 We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
-We interviewed 16 pre-screened participants about their experience trying to circumvent mild, intermediate, and heavy censorship with the current interface, giving insight into common challenges in configuring Tor.
-We discovered multiple challenges: users are confused about who to configure bridges and proxies, a progress bar bug that causes users to falsely assume that a (valid) configuration is faulty, and users have a hard time figuring out what to do after their first attempt to connect fails.
-
-We used this feedback to guide the redesign of the configuration interface.
-We test the impact of our changes on 116 participants.
-We found that the changes cause a statistically significant reduction in the time participants spent configuring their connection and spent more of that time configuring the necessary components.
-We also discuss the common reasons for failing to connect to the Tor network, general behavioral trends of participants across conditions, make suggestions to to improve the Tor interface, and discuss potential opportunities for further research.
+Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity.
+Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works.
+We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.
+
+%general advice to other censorship circumvention and call for more research 
+Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
+When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g.
+pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components.
+We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
+Not only do simulated environments avoids rerouting traffic through a censoring countries' networks, its reproducibility and stability are ideal for experiments.
 

### 2016-05-09 pets2017-paper/pets2017-paper.tex
reword abstract.

@@
 in the time spent configuring a connections. We
-conclude with recommendations for changes to the current configuration interface and discuss
-alternative configuration processes with different balances of risk, automation, and user input.}
+conclude with recommendations for changes to the current interface as well as 
+alternative approaches to bootstrapping a connection to Tor.}
 \end{abstract}
@@
 We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
-Not only do simulated environments avoids rerouting traffic through a censoring countries' networks, its reproducibility and stability are ideal for experiments.
+Not only do simulated environments avoids rerouting traffic through a censoring countries' networks, its reproducibility and stability ideal for experiments.
 

### 2016-05-09 pets2017-paper/pets2017-paper.tex
killed some orphans and trailing words

@@
 Our study focuses on 
-the browser's configuration interface, which guides users through setting up network components required to circumvent censorship.
+the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
 
@@
 a modified Firefox browser that includes a built-in Tor client.
-Tor Browser has a software component called Tor Launcher that
+Tor Browser has a component called Tor Launcher that
 starts, stops, and otherwise controls the underlying Tor processes.
-Tor Launcher's graphical user interface gives access to a variety of 
-sophisticated circumvention mechanisms, asking the user
-to configure a proxy and bridge (if necessary) before connecting to Tor
+Tor Launcher's graphical user interface gives access to 
+sophisticated circumvention mechanisms, giving the user
+the option to configure a proxy and bridge before connecting to Tor
 for the first time. This is the object of our study.
@@
 fields. There is no assistance or automation with this process. The user must locate the 
-proxy information and correctly input this information into the configuration interface.
+proxy information and correctly input this information.
 
@@
 There are many valid configuration settings to connect to the Tor network.
-For instance, a user who does not need a bridge or proxy to circumvent censorship
+For instance, a user who does not need a bridge or proxy 
 can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
@@
 \begin{itemize}
-	\item{Whether they are censored} 
+	\item{Whether their Internet connection is censored} 
 	\item{Whether the Tor network is censored by their ISP}
-	\item{Which groups of hard-coded bridges work in their environment} 
-	\item{If no hard-coded bridges work, how to get and enter a custom bridge} 
+	\item{Which hard-coded bridges work in their country} 
+	\item{If no hard-coded bridges work, how to get custom bridge information and connect to it} 
 	\item{Whether a proxy is required to access the Internet}
@@
 An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
+A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface.
+For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
 
@@
 To succeed in this environment, participants had to select
-one of the ``meek'' built-in bridges (no other type would work)
+one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
 or acquire their own custom bridge and enter it manually.
@@
 
-We recruited our users from Craigslist, vaguely stating that we wanted to evaluate some piece of software. 
+We recruited our users from Craigslist, vaguely asking to evaluate a piece of software. 
 The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
@@
 
-Out of our 16 participants, ages ranged from 20 to~62 years
-($\mu = 24.5$, $\sigma = 12.6$). 53.3\% were male. 
+Of our 16 participants, 53.3\% were male. 
+Ages ranged from 20 to~62 years
+($\mu = 24.5$, $\sigma = 12.6$). 
 93.3\% of our participants had at least
 a college education.
-4 participants had used Tor before;
-5 had heard of Tor but had not used it;
+4 had used Tor before;
+5 had heard of Tor but not used it;
 and the remaining 8 had never heard nor used it.
@@
 After participants completed the browsing tasks or ran out of time,
-we interviewed them about their experience,
-taking notes of the questions and answers.
+we interviewed them about their experience and
+took notes of the questions and answers.
 We asked three standard questions asking about their general experience, 
@@
 with specific questions prompted from watching their screen. 
-This was to verify any hypotheses we had (e.g. ``they did not know what to do on window~3'').
+This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
 We paid each participant~\$30 for their time.
@@
 Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary.
-
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
-\label{fig:error}
-\end{figure}
 
@@
 The challenges users faced in the qualitative experiment and the respective underlying causes are used as feedback for redesigning the configuration interface.
+
+\begin{figure}[t]
+  \centering
+    \includegraphics[width=0.5\textwidth]{error.png}
+    \caption{An example of a technical error message which our participants did not understand.}
+\label{fig:error}
+\end{figure}
 
@@
 
-These changes result in a redesigned interface which we refer to as ``NEW.'' Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.
+These changes result in a redesigned interface which we refer to as NEW.
+Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.
 
@@
 Having identified problems with the existing interface
-and done a redesign in an attempt to ameliorate them,
+and made changes to ameliorate them,
 we quantify the existing problems
@@
 After instructions, researchers maintained minimal interactions with the participants, 
-only answering logistical questions. Participants had
-about 40 minutes to complete their worksheet.
+only answering logistical questions.
 The participants did not know the details of their censorship environment,
-only that they are actively being censored. Participants needed to configure Tor Browser to 
-circumvent the simulated censorship.
+only that they are being censored. Participants had 40 minutes to configure Tor Browser to 
+circumvent the simulated censorship and visit the blocked website.
 
@@
 \subsection{Discussion} 
-This section details general trends in user behavior, common failure cases, and our recommendations for 
-improving the Tor configuration interface.
+We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.
 
@@
 \item {\bfseries Used the bridges auto-responder incorrectly (2/21).} P96, P111, who were in E3, emailed the bridges auto-responder to get custom bridges.
-However, they formatted the message incorrectly and thus failed to get a response.
-For details, see Appendix~\ref{failed-participants}.
+However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{failed-participants}).
+\end{description}
 
@@
 Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
-\end{description}
 
@@
 
-We recommend best practices, such as providing a summary screen to let the user know the configuration settings before connecting, and having a progress bar that gives users feedback on what network component has failed.
+Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.
 
 \section{Limitations} 
-The interface was only tested on Windows machines.
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
+We only tested interface on Windows machines, which were the machines available at Xlab.
 Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.

### 2016-05-09 pets2017-paper/pets2017-paper.tex
Explain ``not running'' better.

@@
 Different colors indicate which screen was shown at each moment.
-The narrow black lines show the times when the configuration interface
-was not running; i.e., a participant was doing something else
+The ``not running'' times are those when Tor Launcher was closed;
+i.e., a participant was doing something else
 such as searching the web in another browser.

### 2016-05-09 pets2017-paper/pets2017-paper.tex
delete quotes

--- 2016-05-09 pets2017-paper/pets2017-paper.tex
@@
 		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
-		\caption{In the ``OLD'' interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
+		\caption{In the OLD interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
 		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
 		be configured and directs to the bridge configuration screen (B2). 
-		The ``NEW'' interface gives users advice on configuring bridges
+		The NEW interface gives users advice on configuring bridges
 		while giving the option of not configuring a bridge, on one screen (B).} 
@@
 		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
-		\caption{In the ``OLD'' interface, users are asked, ``Does this computer need a local proxy to connect
+		\caption{In the OLD interface, users are asked, ``Does this computer need a local proxy to connect
 		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
-		proxy configuration screen (P2). The ``NEW'' interface checks the local machine's proxy settings,
+		proxy configuration screen (P2). The NEW interface checks the local machine's proxy settings,
 		and informs the user whether a proxy is required, and if so, what those settings are (P).}
@@
 \caption{
-Comparison of user flow in the ``OLD'' and ``NEW'' interfaces.
+Comparison of user flow in the OLD and NEW interfaces.
 We collapsed the two bridge screens into one 

### 2016-05-09 pets2017-paper/pets2017-paper.tex
Spell check.

@@
 We made the text more task-centric by focusing on instructing users through the configuration process.
-Since users generally did not understand the technical concepts sufficiently to influence their decisions, we thibk giving direct guidance is a better option.
+Since users generally did not understand the technical concepts sufficiently to influence their decisions, we think giving direct guidance is a better option.
 \item Added system status visibility.

### 2016-05-10 pets2017-paper/pets2017-paper.tex
delete the participant who downloaded own tor after using ours.

@@
 We use the results as feedback to redesign the configuration interface.
-A 116-participant quantitative user study tests the impact of our changes.
+A 115-participant quantitative user study tests the impact of our changes.
 We find that our changes result in a significant reduction 
@@
 \item 10 changes to the configuration interface which we hope alleviates the common challenges
-\item 116 logs of real world user attempts to connect to Tor in three different censorship environments
+\item 115 logs of real world user attempts to connect to Tor in three different censorship environments
 \item 4 reasons why users failed to connect to Tor
@@
 \subsection{Results} 
-Out of our 124 recruited participants, 116 provided valid data.
+Out of our 124 recruited participants, 115 provided valid data.
 We have 58 participants who tested the new interface, and 58 who tested the old interface.
-38 participants were in E1, 38 participants were in E2, and 40 participants were in E3.
+38 participants were in E1, 37 participants were in E2, and 40 participants were in E3.
 Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
@@
 	\noalign{\hrule}
-	E1-NEW & 19/19 & 100\% & 0:20 \\ % medians of only finished: 0:20 
-	E1-OLD & 19/19 & 100\% & 1:01 \\ %medians of only finished: 1:01
-	E2-NEW & 18/19 & 95\% & 3:32 \\ %medians of only finished: 3:22
-	E2-OLD & 16/19 & 84\% & 5:00 \\ %medians of only finished: 3:13
-	E3-NEW & 13/20 & 65\% & 20:56 \\ %medians of only finished: 12:38
-	E3-OLD & 10/20 & 50\% & 40:08 \\ %medians of only finished: 18:16 
+	E1-NEW & 19/19 & 100\% & 0:20 \\
+	E1-OLD & 19/19 & 100\% & 1:01 \\
+	E2-NEW & 18/18 & 100\% & 3:22 \\
+	E2-OLD & 16/19 & 84\% & 5:00 \\
+	E3-NEW & 13/20 & 65\% & 20:56 \\
+	E3-OLD & 10/20 & 50\% & 40:08 \\
 	\end{tabular}
@@
 \subsubsection{Rate of Success} 
-50 of 58 (86\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
+49 of 57 (86\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
@@
 We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure.
-Of the 76 participants that failed to connect on the first attempt, 15 of 36 participants with the new interface and 13 of 38 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
+Of the 76 participants that failed to connect on the first attempt, 14 of 35 participants with the new interface and 13 of 38 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
 10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim that this is a direct result of our advice.
@@
 no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
-DNF (did not finish) &  &  & 1 & 3 & 7 & 10 \\
+DNF (did not finish) &  &  &  & 3 & 7 & 10 \\
 \end{tabular}
@@
 	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
-	E2-NEW & 11\% & 79\% & 89\% & 95\% \\
+	E2-NEW & 11\% & 83\% & 94\% & 100\% \\
 	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
@@
 % the treatments.
-\includegraphics{all-participant-edges-scales}
+\includegraphics{all-participant-edges}
 \caption{
@@
 	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
-	E2-NEW & 5\% & 5\% & 5\% & 76\% \\
+	E2-NEW & 6\% & 5\% & 6\% & 78\% \\
 	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
@@
 Failure is common.
-20\% (21 of 116) of participants were not able to successfully connect to Tor.
-64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
+17\% (20 of 115) of participants were not able to successfully connect to Tor.
+63\% (73 of 115) of first attempts to connect failed and {\color {red} 79\% (376 of 462)} of total attempts to connect failed.
 Reasons for failure were determined by a combination of log processing (i.e.
@@
 \begin{description}
-\item {\bfseries Only connected directly (7/21).} P57, P74, P76, P90, P93, P108, P112 tried a direct connection.
+\item {\bfseries Only connected directly (6/20).} P73, P75, P89, P92, P107, P111 tried a direct connection.
 When that failed, they tried the same option, over and over, no matter how many times they failed.
@@
 
-\item {\bfseries Only tried recommendations (6/21).} P91, P92, P95, P110, P113, P116, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
+\item {\bfseries Only tried recommendations (6/20).} P90, P91, P94, P109, P112, P115, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
 They often tried those configurations again or gave up.
 
-\item {\bfseries Thought that they needed a proxy (5/21).} P75, P94, P107, P109, P115 assumed that they needed a proxy.
+\item {\bfseries Thought that they needed a proxy (5/20).} P74, P93, P106, P108, P114 assumed that they needed a proxy.
 They spent their time trying to configure a proxy, usually without trying other bridges.
 
-\item {\bfseries Used the bridges auto-responder incorrectly (2/21).} P96, P111, who were in E3, emailed the bridges auto-responder to get custom bridges.
+\item {\bfseries Used the bridges auto-responder incorrectly (2/20).} P95, P110, who were in E3, emailed the bridges auto-responder to get custom bridges.
 However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{failed-participants}).
@@
 This leaks to network eavesdroppers leaking that they are connecting to Tor.
-81\% (94 of 116) of first attempts were to connect directly, 86\% (50 of 116) from the new interface and 76\% (44 of 116) from the old interface.
+81\% (93 of 115) of first attempts were to connect directly, 53\% (49 of 115) from the new interface and 47\% (44 of 115) from the old interface.
 
@@
 Automating the configuration process thereafter will have no increase in risk.
-This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 64\% of participants who failed their first attempt.
-Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
+This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the {\color {red} 64\%} of participants who failed their first attempt.
+Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, {\color {red} 84\%} participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
 \item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy.
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that P96 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
+\caption{The message that P95 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
 \label{autoresponder1}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that P111 accidentally sent to the helpdesk rather than the bridge auto-responder.
+\caption{The message that P110 accidentally sent to the helpdesk rather than the bridge auto-responder.
 The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
@@
 \begin{itemize}
-\item P57 (Fig.~\ref{techspot})
-\item P91 (Fig.~\ref{softsonic})
+\item P90 (Fig.~\ref{softsonic})
+\item P116 (Fig.~\ref{techspot})
 \item P117, data not used (Fig.~\ref{mirror})
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
-\caption{P57 downloaded Tor Browser from TechSpot, clicking on the download link from 
+\caption{P116 downloaded Tor Browser from TechSpot, clicking on the download link from 
 TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}

### 2016-05-10 experiment/processing/attempts.R

@@ -35,19 +35,6 @@ first_attempts_E2_OLD <-  first_attempts[first_attempts[,"env"]=="E2" & first_at
 first_attempts_E3_NEW <-  first_attempts[first_attempts[,"env"]=="E3" & first_attempts[,"version"]=="NEW",]
 first_attempts_E3_OLD <-  first_attempts[first_attempts[,"env"]=="E3" & first_attempts[,"version"]=="OLD",]
 
-#? 
-sum(first_attempts$bridge_radio_state == "none")#/nrow(first_attempts)*100
-sum(first_attempts_new$bridge_radio_state == "none")#/nrow(first_attempts_new)*100
-sum(first_attempts_old$bridge_radio_state == "none")#/nrow(first_attempts_old)*100
-
-# How many FIRST attempts were failures.
-sum(first_attempts$attempt_successful == "FALSE")/nrow(first_attempts)*100
-sum(first_attempts_new$attempt_successful == "FALSE")/nrow(first_attempts_new)*100
-sum(first_attempts_old$attempt_successful == "FALSE")/nrow(first_attempts_old)*100
-sum(first_attempts_e1$attempt_successful == "FALSE")/nrow(first_attempts_e1)*100
-sum(first_attempts_e2$attempt_successful == "FALSE")/nrow(first_attempts_e2)*100
-sum(first_attempts_e3$attempt_successful == "FALSE")/nrow(first_attempts_e3)*100
-
 successful.attempts <- attempts[attempts$attempt_successful, ]
 successful.attempts$label <- sprintf("%s, %s",
 	# bridge label

### 2016-05-10 experiment/processing/info.R

@@ -83,7 +83,6 @@ summary_edges <- edges[edges[,"dst"]== "summary",]
 # 2
 total_time_per_user <- aggregate(edges$duration ~ edges$userid, edges, sum)
 active_time_per_user <- aggregate(active_edges$duration ~ active_edges$userid, active_edges, sum)
-active_time_per_user[percent_time] <- 
 not_running_time_per_user <- aggregate(not_running_edges$duration ~ not_running_edges$userid, not_running_edges, sum)
 starting_time_per_user <- aggregate(starting_edges$duration ~ starting_edges$userid, starting_edges, sum)
 progress_time_per_user <- aggregate(progress_edges$duration ~ progress_edges$userid, progress_edges, sum)

### 2016-05-10 pets2017-paper/pets2017-paper.tex
fix numbers from deleting P57 and reword accordingly. Added median active times to table 2.

@@
 \subsection{Results} 
-Out of our 124 recruited participants, 115 provided valid data.
-We have 58 participants who tested the new interface, and 58 who tested the old interface.
-38 participants were in E1, 37 participants were in E2, and 40 participants were in E3.
-Table~\ref{table:participant-summary} summarizes the rate of success and time to success for our participants' based on their interface version and environment combination.
+The possible interface version and environment combinations resulted in 6 experimental conditions.
+We recruited 124 participants to aim for about 20 participants per condition.
+We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 115 participants.
+Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
 
@@
 	% Generated by info.R.
-	\begin{tabular}{l r r r r}
-	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
-	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
+	\begin{tabular}{l r r r r r}
+	& \multicolumn{2}{r}{success rate} & \multicolumn{1}{r}{median time} &\multicolumn{1}{r}{median}\\
+	& \multicolumn{2}{r}{after 40 minutes} & \multicolumn{1}{r}{to success} & \multicolumn{1}{r} {active time} \\
 	\noalign{\hrule}
-	E1-NEW & 19/19 & 100\% & 0:20 \\
-	E1-OLD & 19/19 & 100\% & 1:01 \\
-	E2-NEW & 18/18 & 100\% & 3:22 \\
-	E2-OLD & 16/19 & 84\% & 5:00 \\
-	E3-NEW & 13/20 & 65\% & 20:56 \\
-	E3-OLD & 10/20 & 50\% & 40:08 \\
+	E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
+	E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
+	E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
+	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
+	E3-NEW & 13/20 & 65\% & 20:56 & 1:53 \\
+	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
 	\end{tabular}
@@
 \subsubsection{Time to Success} 
-The median times to completion for participants of the new interface are less than those with the old interface (Table~\ref{table:participant-summary}).
-Non-finishing participants are assigned the maximum time of 40:08
-for the purpose of computing the median.
-However, the difference between the medians times to success between new versus old interfaces, in aggregate and in censorship environment, are not statistically significant.
-The level of censorship, rather than the interface, had a significant impact on the time to success.
-%The more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$). 
-The distribution of participants' time to success can be seen in Fig.~\ref{fig:time_to_success_clamped}.
-%impact of version on time to success: not significant ($W = 1569$, $p = 0.07796$)
-%impact of env on time to success : significant (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15})
+Time to success is defined as the time until the first successful connection to Tor.
+Non-finishing participants are assigned the maximum experiment time of 40:08.
+Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $ Z = -1.69$, $p < 0.05$, $r= 0.158$).
+The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
+Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
 
@@
 who did not finish in the time allotted.
-Here, non-finishing participants are assigned the maximum time of 40:08
-for the purpose of computing the median.
+Here, non-finishing participants are assigned the maximum time of 40:08.
 }
@@
 
-\subsubsection{Active Configuration Time} 
+\subsubsection{Active Time} 
 We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
@@
 \caption{
-Active configuration time, by censorship environment and interface.
+Active time, by censorship environment and interface.
 The dots show the raw active configuration times,
@@
 
-Perhaps a more meaningful measurement of time is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}).
-We define this as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-Active configuration time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
+Perhaps a more meaningful measurement is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}).
+We define active time as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+Active time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
 This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.
@@
 We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface.
-The new interface results a statistically significant reduction in active configuration time.
-(Mann--Whitney $Z = -2.7$, $p = 0.0032$, $r= 0.25$).
-The small effect size may be due to the fact that the reduction in time mostly applied to participants in E3.
+Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.29$, $p < 0.0005$, $r = 0.307$).
+Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
 
@@
 %connect vs configure
-\item {\bfseries Users try the easy path first.} Users try the easy option of connecting directly to the Tor network first.
-This leaks to network eavesdroppers leaking that they are connecting to Tor.
-81\% (93 of 115) of first attempts were to connect directly, 53\% (49 of 115) from the new interface and 47\% (44 of 115) from the old interface.
+\item {\bfseries Users try the easy path first.} Users generally try connecting directly to the Tor network first.
+81\% (93 of 115) of first attempts were to connect directly, with 53\% (49 of 93) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
+This leaks to network eavesdroppers that they are connecting to Tor.
 
@@
 Automating the configuration process thereafter will have no increase in risk.
-This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the {\color {red} 64\%} of participants who failed their first attempt.
-Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, {\color {red} 84\%} participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
+This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 63\% of participants who failed their first attempt.
+Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
 \item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy.
@@
 We used a Pearson's Chi-squared test to test the significance of success rates.
-The difference between success rates of participants with the new interface and participants with the old interface was not significant (X-squared = 0.012599, df = 2, p-value = 0.9937).
+The difference between success rates of participants with the new interface and participants with the old interface was not significant ($X^2 = 0.0126$, $df = 2$, $p = 0.994$).
 
@@
 Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
-We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant (Z = -1.5451, p-value = 0.06116).
+We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.69$, $p = 0.0454$, $r= 0.158$).
 
@@
 Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant (Z = -3.4069, p-value = 0.0003286).
+We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.29$, $p = 0.000493$, $r = 0.307$).
 

### 2016-05-10 experiment/processing/info.R
calculate median active times per condition.

@@ -166,19 +166,13 @@ median(screen_time_per_user[screen_time_per_user[,"env"]== "E3" & screen_time_pe
 #ACTIVE TIME (all but progress)
 report_total("ACTIVE",active_edges)
 
-median(screen_time_per_user$`active_edges$duration`/screen_time_per_user$`edges$duration`)
-median(screen_time_per_user[screen_time_per_user[,"env"]== "E1" & screen_time_per_user[,"version"]== "NEW",]$`active_edges$duration`/
-         screen_time_per_user[screen_time_per_user[,"env"]== "E1" & screen_time_per_user[,"version"]== "NEW",]$`edges$duration`)
-median(screen_time_per_user[screen_time_per_user[,"env"]== "E1" & screen_time_per_user[,"version"]== "OLD",]$`active_edges$duration`/
-         screen_time_per_user[screen_time_per_user[,"env"]== "E1" & screen_time_per_user[,"version"]== "OLD",]$`edges$duration`)
-median(screen_time_per_user[screen_time_per_user[,"env"]== "E2" & screen_time_per_user[,"version"]== "NEW",]$`active_edges$duration`/
-         screen_time_per_user[screen_time_per_user[,"env"]== "E2" & screen_time_per_user[,"version"]== "NEW",]$`edges$duration`)
-median(screen_time_per_user[screen_time_per_user[,"env"]== "E2" & screen_time_per_user[,"version"]== "OLD",]$`active_edges$duration`/
-         screen_time_per_user[screen_time_per_user[,"env"]== "E2" & screen_time_per_user[,"version"]== "OLD",]$`edges$duration`)
-median(screen_time_per_user[screen_time_per_user[,"env"]== "E3" & screen_time_per_user[,"version"]== "NEW",]$`active_edges$duration`/
-         screen_time_per_user[screen_time_per_user[,"env"]== "E3" & screen_time_per_user[,"version"]== "NEW",]$`edges$duration`)
-median(screen_time_per_user[screen_time_per_user[,"env"]== "E3" & screen_time_per_user[,"version"]== "OLD",]$`active_edges$duration`/
-         screen_time_per_user[screen_time_per_user[,"env"]== "E3" & screen_time_per_user[,"version"]== "OLD",]$`edges$duration`)
+format_minutes_colons(median(screen_time_per_user$`active_edges$duration`))
[…]

### 2016-05-10 pets2017-paper/pets2017-paper.tex
update another number I missed updating after deleting P57.
filter participants who downloaded own tor. (also filter P91).

@@
 We use the results as feedback to redesign the configuration interface.
-A 115-participant quantitative user study tests the impact of our changes.
+A 114-participant quantitative user study tests the impact of our changes.
 We find that our changes result in a significant reduction 
@@
 \item 10 changes to the configuration interface which we hope alleviates the common challenges
-\item 115 logs of real world user attempts to connect to Tor in three different censorship environments
+\item 114 logs of real world user attempts to connect to Tor in three different censorship environments
 \item 4 reasons why users failed to connect to Tor
@@
 We recruited 124 participants to aim for about 20 participants per condition.
-We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 115 participants.
+We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants.
 Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
@@
 	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
-	E3-NEW & 13/20 & 65\% & 20:56 & 1:53 \\
+	E3-NEW & 13/19 & 68\% & 12:38 & 1:56 \\ 
 	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
@@
 \subsubsection{Rate of Success} 
-49 of 57 (86\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
+49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did. 
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
@@
 We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure.
-Of the 76 participants that failed to connect on the first attempt, 14 of 35 participants with the new interface and 13 of 38 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
-10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim that this is a direct result of our advice.
+Of the 75 participants that failed to connect on the first attempt, 15 participants with the new interface and 13 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
+10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim choosing meek bridges is a direct result of our advice.
 
@@
 no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
-DNF (did not finish) &  &  &  & 3 & 7 & 10 \\
+DNF (did not finish) &  &  &  & 3 & 7 & 9 \\
 \end{tabular}
@@
 Non-finishing participants are assigned the maximum experiment time of 40:08.
-Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $ Z = -1.69$, $p < 0.05$, $r= 0.158$).
-The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.926$, $\mbox{df} = 2$, $p < 10^{-15}$).
+Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
 Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
@@
 For example, every E1-NEW participant finished within 90 seconds,
-but only 58\% of E1-OLD had finished by that time.
-After 10 minutes, 79\% of E2-NEW and 68\% of E2-OLD had finished.
-After 20 minutes, 45\% of E3-NEW and only 25\% of E3-OLD had finished.
+but only 58\% of E1-OLD had finished by that time. Within 10 minutes, most
+participants in E2 had finished, along with a minority of E3 participants. 
 }
@@
 	\noalign{\hrule}
-	All & 7\% & 5\% & 4\% & 58\% \\
 	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
@@
 	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
-	E3-NEW & 3\% & 3\% & 5\% & 73\% \\
+	E3-NEW & 3\% & 5\% & 5\% & 77\% \\
 	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
@@
 
-%\begin{table}[t]
-%\centering
-%	\begin{tabular}{c r r r r}
-%	& First & Proxy & Bridge & Progress \\
-%	\noalign{\hrule}
-%	All & 5\% & 16\% & 6\% & 60\% \\
-%	E1-NEW & 34\% & 4\% & 6\% & 50\% \\
-%	E1-OLD & 23\% & 35\% & 9\% & 21\% \\
-%	E2-NEW & 4\% & 3\% & 3\% & 58\% \\
-%	E2-OLD & 4\% & 22\% & 4\% & 65\% \\
-%	E3-NEW & 5\% & 6\% & 4\% & 64% \\
-%	E3-OLD & 4\% & 25\% & 8\% & 56\% \\
-%	\end{tabular}
-%\caption{The overall percent of time all participants spent on each screen, computed by
-%dividing the aggregate number of time on a screen by the aggregate time on all screens.} 
-%\label{table:overall_time}
-%\end{table}
-
 Perhaps a more meaningful measurement is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}).
@@
 We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface.
-Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.29$, $p < 0.0005$, $r = 0.307$).
+Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
 Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
@@
 Failure is common.
-17\% (20 of 115) of participants were not able to successfully connect to Tor.
-63\% (73 of 115) of first attempts to connect failed and {\color {red} 79\% (376 of 462)} of total attempts to connect failed.
+17\% (19 of 114) of participants were not able to successfully connect to Tor.
+63\% (72 of 114) of first attempts to connect failed and 79\% (36 of 458) of total attempts to connect failed.
 Reasons for failure were determined by a combination of log processing (i.e.
@@
 \begin{description}
-\item {\bfseries Only connected directly (6/20).} P73, P75, P89, P92, P107, P111 tried a direct connection.
+\item {\bfseries Only connected directly (6/19).} P73, P75, P89, P91, P106, P110 tried a direct connection.
 When that failed, they tried the same option, over and over, no matter how many times they failed.
@@
 
-\item {\bfseries Only tried recommendations (6/20).} P90, P91, P94, P109, P112, P115, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
+\item {\bfseries Only tried recommendations (5/19).} P90, P93, P108, P111, P114, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
 They often tried those configurations again or gave up.
 
-\item {\bfseries Thought that they needed a proxy (5/20).} P74, P93, P106, P108, P114 assumed that they needed a proxy.
+\item {\bfseries Thought that they needed a proxy (5/19).} P74, P92, P105, P107, P113 assumed that they needed a proxy.
 They spent their time trying to configure a proxy, usually without trying other bridges.
 
-\item {\bfseries Used the bridges auto-responder incorrectly (2/20).} P95, P110, who were in E3, emailed the bridges auto-responder to get custom bridges.
+\item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
 However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{failed-participants}).
@@
 \item {\bfseries Users try the easy path first.} Users generally try connecting directly to the Tor network first.
-81\% (93 of 115) of first attempts were to connect directly, with 53\% (49 of 93) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
+81\% (92 of 114) of first attempts were to connect directly, with 52\% (48 of 92) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
 This leaks to network eavesdroppers that they are connecting to Tor.
@@
 Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
-We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.69$, $p = 0.0454$, $r= 0.158$).
+We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
 
@@
 Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.29$, $p = 0.000493$, $r = 0.307$).
+We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
 
@@
 \begin{itemize}
-\item P90 (Fig.~\ref{softsonic})
+\item P115 (Fig.~\ref{softsonic})
 \item P116 (Fig.~\ref{techspot})
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{P91 downloaded Tor Browser from Softsonic, a reputable-looking but
+\caption{P115 downloaded Tor Browser from Softsonic, a reputable-looking but
 unconfirmed site.}

### 2016-05-10 pets2017-paper/pets2017-paper.tex
put appendixes in order.

@@
 took notes of the questions and answers.
-We asked three standard questions asking about their general experience, 
-interface features they found confusing, and feedback for improvements. We followed up
-with specific questions prompted from watching their screen. 
+We asked questions asking about their general experience, 
+interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
+We followed up with specific questions prompted from watching their screen. 
 This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
@@
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
-This suggests that users no less likely to succeed with the new interface.
-% impact of version on success: not significant (Mann--Whitney $W = 5.5$, $p = 0.8248$)
-%impact of env on success: not significant (Kruskal--Wallis $\chi^2 = 4.7059$, $\mbox{df} = 2$, $p = 0.09509$)
+Appendix~\ref{stat-tests} details the methodology for the statistical tests used in this paper.
 
@@
 Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result.
-Appendix~\ref{failed-participants} shows the malformed requests.
+Appendix~\ref{custom} shows the malformed requests.
 These two participants failed to connect to the Tor network.
@@
 \item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
-However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{failed-participants}).
+However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
 \end{description}
@@
 \appendix
-\section{Participant Worksheet Text} 
-\label{participant-worksheet}
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-For instance, www.torproject.org is blocked.
-Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
-It will fail to load, when you can visit other sites.
-
-To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
-If you can visit wikipedia, then you know that you have successfully circumvented censorship.
 
@@
 
+\section{Participant Worksheet Text} 
+\label{participant-worksheet}
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+For instance, www.torproject.org is blocked.
+Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
+It will fail to load, when you can visit other sites.
+
+To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
+If you can visit wikipedia, then you know that you have successfully circumvented censorship.
+
 \section{Post-Experiment Standard Interview Questions}
+\label{interview-questions}
 We asked our participants these questions after they were given time to configure Tor Browser. \\
@@
 \section{Statistical Tests} 
+\label{stat-tests}
 From our measurements, we observe that participants with the new interface 
@@
 \section{Custom Bridge Attempts} 
-\label{failed-participants}
+\label{custom}
 

### 2016-05-11 experiment/processing/attempts-bridge-proxy.tex
Move autogenerated tables into separate files.

--- 2016-05-10 pets2017-paper/pets2017-paper.tex
@@
-\documentclass[USenglish,oneside,twocolumn]{article}
-\usepackage{color}
-\usepackage[hyphens]{url}
-\usepackage{longtable}
-\usepackage{graphicx}
-\usepackage{enumitem}
-\usepackage{pdfpages}
-%\usepackage{hyperref}
-
-\usepackage[utf8]{inputenc}%(only for the pdftex engine)
-%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
-\usepackage[big]{dgruyter_NEW}
-
-\DOI{foobar}
-
-\cclogo{\includegraphics{by-nc-nd.pdf}}
-
-% Format a participant quotation.
-\newcommand{\pquote}[2]{
-\begin{quotation}
-\noindent #1:~\textit{``#2''}
-\end{quotation}
-}
-
-\begin{document}
-
-  \author*[1]{Linda Lee}
-
-  \author[2]{David Fifield}
-
-  \author[3]{Nathan Malkin}
-
-  \author[4]{Ganesh Iyer}
-
-  \author[5]{Serge Egelman}
-
-  \author[6]{David Wagner}
-
-  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
-
-  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
-
-  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
-
-  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
-
-  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
-
-  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
-
-  \title{\huge Tor's Usability for Censorship Circumvention}
-  %Internet Freedom Made Easy: On Improving Tor’s Usability for Censorship Circumvention
-  %Towards Usable Censorship Circumvention
-
-  \runningtitle{Tor's Usability for Censorship Circumvention}
-
-  %\subtitle{...}
-
-  \begin{abstract}
-{Tor has grown beyond its original purpose as an anonymity tool and has 
-become a widely-used censorship circumvention tool.
-This is the first study to examine Tor's usability in this role.
-We evaluate, design, and test the Tor configuration interface by
-placing users in simulated censorship environments, instructing them to use Tor
-to circumvent censorship, and measuring their interactions with the interface.
-A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
-We use the results as feedback to redesign the configuration interface.
-A 114-participant quantitative user study tests the impact of our changes.
-We find that our changes result in a significant reduction 
-in the time spent configuring a connections. We
-conclude with recommendations for changes to the current interface as well as 
-alternative approaches to bootstrapping a connection to Tor.}
-\end{abstract}
-  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
-%  \classification[PACS]{}
- % \communicated{...}
- % \dedication{...}
-
-  \journalname{Proceedings on Privacy Enhancing Technologies}
-\DOI{Editor to enter DOI}
-  \startpage{1}
-  \received{..}
-  \revised{..}
-  \accepted{..}
-
-  \journalyear{2015}
-  \journalvolume{2015}
-  \journalissue{2}
-
-\maketitle
-
-\section{Introduction}
-
-Tor is an anonymity network that routes traffic through a series of relays
-that make it difficult to observe the source and destination~\cite{dingledine2004tor}.
-Tor's anonymizing functionality also circumvents censorship.
-Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}.
-Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.
-
-This is the first user study that investigates the usability of Tor as a censorship circumvention tool.
-Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier.
-All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool.
-Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
-
-We evaluate, redesign, and test Tor's configuration interface by
-measuring participants' interactions with the interface in various censorship environments.
-The first user study is a small-scale, qualitative experiment that collected 
-behavioral patterns and failure cases with the interface through user observations
-and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, quantitative experiment
-that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).
-
-In this paper, we contribute the following:
-\smallskip
-\begin{itemize}
-\item 6 common challenges encountered during the configuration process and their underlying causes
-\item 10 changes to the configuration interface which we hope alleviates the common challenges
-\item 114 logs of real world user attempts to connect to Tor in three different censorship environments
-\item 4 reasons why users failed to connect to Tor
-\item 5 recommendations of configuration interface changes to help more users connect and save time
-\item 5 alternative  approaches to bootstrapping a connection that leverage varying degrees of automation
-\end{itemize}
-We hope that our work helps users circumvent censorship and connect to Tor.
-
-\section{Related Work} 
-There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
-options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
-latency~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests, and prevents user adoption. 
-Norcie et~al.~\cite{norcie2012eliminating} found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties.
-
-We do not know of any published usability evaluations of
-Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
-that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
-some of which influenced changes in Tor Browser version~4.5 and later.
-
-Previous user studies have considered the whole browsing experience,
-without focusing on specific features in isolation.
-Our study focuses on 
-the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
-
-\section{Background}
-This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.
-
-\subsection{Tor, Tor Browser, and Tor Launcher}
-The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
-a modified Firefox browser that includes a built-in Tor client.
-Tor Browser has a component called Tor Launcher that
-starts, stops, and otherwise controls the underlying Tor processes.
-Tor Launcher's graphical user interface gives access to 
-sophisticated circumvention mechanisms, giving the user
-the option to configure a proxy and bridge before connecting to Tor
-for the first time. This is the object of our study.
-
-In principle, the process of configuring a proxy and bridge can be automated, but
-the interface eschews automatic configuration through network probing
-in favor of guided manual configuration to give users agency in configuring their connection. 
-Automatic configuration through network probing may put some users in certain regimes at risk. 
-A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-However, this requires that the user grapple with technical concepts such as 
-bridges, pluggable transports, and proxies. Some of these concepts are specific to 
-Tor and not general concepts.
-
-\subsection{Bridges, Pluggable Transports, and Proxies} 
-Internet censors seek to block network resources through 
-a variety of means, such as falsifying DNS responses, blocking IP addresses, 
-filtering keywords, and detecting protocols by deep packet inspection.
-Censors can block the Tor network by blocking the list of Tor relays, which 
-are public. Blocking Tor becomes challenging when
-the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
-Fig.~\ref{fig:topology} illustrates the interacting components.
-
-\begin{figure}
-\centering
-\includegraphics{topology.pdf}
-\caption{
-The chain of components involved in connecting to a website over Tor.
-Most users do not need a proxy;
-similarly only those users who face a censor need a bridge.
-In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
-We have shown the bridge as a separate component
-because of the special role it plays.
-When a bridge is used, it takes the place of the first Tor hop.
-}
-\label{fig:topology}
-\end{figure}
-
-Bridges are unlisted Tor relays that make it possible for a user to connect
-to the Tor network even if a censor blocks all publicly listed Tor relays.
-Pluggable transports are special protocols that run on bridges and obfuscate
-Tor's network protocol to make it difficult to detect. 
-Configuring a bridge requires providing one or more
-``bridge lines,'' a specification of a bridge that
-includes its IP address, transport type, and other metadata.
-For ease of use, the interface has hard-coded options for 
-the user to choose a group of bridges that use a particular
-pluggable transport. For example, choosing  the hard-coded obfs3 option
-configures a handful of bridges that use obfs3 pluggable transport.
-Some censors block the IP addresses of the hard-coded bridges by looking
-at the source code for those addresses (except flashproxy and meek).
-If the built-in bridges do not work, a user can obtain bridge lines
-through out-of-band channels, for instance by email~\cite{bridgedb}.
-Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
-options at the time of the study and lists the available pluggable transports.
-%Some transports connect directly to a static IP address,
-%obfuscating traffic to defeat on-the-wire identification;
-%they rely on the secrecy of their IP addresses for their effectiveness.
-%These include ``fte'' and ``fte-ipv6''~\cite{fte},
-%which make Tor look like another protocol such as HTTP; and
-%``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
-%which encrypt Tor to look like random noise.
-%Other transports work differently and do not depend on connecting to a static IP address:
-%``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
-%and the three ``meek''~\cite{fifield2015blocking} options route traffic
-%through content delivery networks.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.5\textwidth]{bridge-options.png}
-%\small
-%\begin{itemize}
-%\renewcommand{\labelitemi}{$\circ$}
-%\item Connect with provided bridges\\
-%Transport type:
-%\begin{itemize}
-%\item flashproxy
-%\item fte
-%\item fte-ipv6
-%\item meek-amazon
-%\item meek-azure
-%\item meek-google
-%\item obfs3 (recommended)
-%\item obfs4
-%\item scramblesuit
-%\end{itemize}
-%\item Enter custom bridges\qquad\fbox{Help}\\
-%\end{itemize}
-\caption{
-Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
-Users are not familiar with the options under ``Transport type'' denote various
-built-in circumvention technologies (``pluggable transports'').
-Under ``Enter custom bridges,'' there is a space to paste in
-a bridge line, obtained out of band.
-The ``Help'' button displays instructions on obtaining
-bridge lines. 
-}
-\label{fig:bridge-options}
-\end{figure}
-
-In addition to Tor-specific components, a proxy may be necessary to connect 
-outside the local network in certain managed environments, such as corporate or university networks.
-Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
-fields. There is no assistance or automation with this process. The user must locate the 
-proxy information and correctly input this information.
-
-%Technically the Tor client, pluggable transport bridge, and proxy are all
-%proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
-%as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
-%censor's control.
-
-\subsection{Circumventing Censorship with Tor}
-There are many valid configuration settings to connect to the Tor network.
-For instance, a user who does not need a bridge or proxy 
-can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
-The minimum amount of configuration required, therefore, the set of valid configuration settings,
-vary depending on the censorship environment. In the worst case, users must know or find out:\\
-
-\begin{itemize}
-	\item{Whether their Internet connection is censored} 
-	\item{Whether the Tor network is censored by their ISP}
-	\item{Which hard-coded bridges work in their country} 
-	\item{If no hard-coded bridges work, how to get custom bridge information and connect to it} 
-	\item{Whether a proxy is required to access the Internet}
-	\item{If a proxy is required, and if so, the proxy settings}
-\end{itemize}
-
-Uncensored users and users in censorship environments that do not explicitly 
-block Tor do not require a bridge or a proxy and can bypass these steps in the configuration process.
-Users in censorship environments that explicitly block Tor but have not blocked the 
-hard-coded bridges in the Tor Launcher source code are required to use a 
-hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
-blocked Tor relays and hard-coded bridges are required to configure a meek bridge (which 
-routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
-configure a custom bridge to connect to Tor.
-
-\section{Evaluation Criteria and Goals}
-\label{sec:goals}
-Our user studies evaluated two versions of the Tor Launcher interface.
-The first, which we have labeled OLD in our figures and tables,
-is the current version being distributed with Tor Browser.
-The second, NEW, is the prototype that we designed
-in order to provide better usability. Below are the empirical and 
-heuristic evaluation criteria we use to assess the interfaces.
-
-Our empirical evaluation criteria for the Tor Browser configuration
-interface are based on common metrics that measure ease of use: \\
-
-\begin{enumerate}
-    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition.
-This measures how many users are able to configure their connections with the interface.
-    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-This measures how much time is required for a user to connect to the Tor network.
-    \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
-\end{enumerate}
-
-An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
-A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface.
-For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
-
-\section{Experimental Setup}
-\label{sec:environments}
-For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
-the most recent stable release at the time~\cite{torbrowser-503}.
-Though there were new releases during the experiments,
-we used the same version across all participants to not introduce
-confounding factors.
-
-For both user studies, we simulated three censorship environments,
-which we refer to as E1, E2, and E3, which are in  the order of increasing severity.
-We designed the environments to be representative
-of what, in our estimation, are important real-world
-cases of censorship. They are not intended to imitate
-any particular country's censorship environment.\\
-
-\begin{description}
-\item [E1: Mild censorship.]
-(Representative of countries such as France and Australia.)
-The E1 environment only blocks some websites,
-as if by DNS poisoning.
-We blocked subdomains of torproject.org
-and wikipedia.org.
-(The participants' main goal in the experiment was to read a page on en.wikipedia.org.)
-To succeed in this environment,
-participants only had to click ``Connect'' on the first screen;
-additional configuration was optional.
-
-\item [E2: Intermediate censorship.]
-(Representative of countries such as Tunisia.)
-The E2 environment blocks websites as in E1 and
-additionally blocks IP addresses of public Tor relays
-and directory authorities, simulating a censor who knows
-about circumvention and tries to stop it.
-In this environment, simply clicking ``Connect'' does not work;
-participants had to select a built-in bridge
-(any type other than ``flashproxy'' would work).
-A custom bridge would work but was not necessary.
-
-\item [E3: Comprehensive censorship.]
-(Representative of countries such as China and Syria.)
-The E3 environment blocks websites and Tor relays like E1 and E2
-and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
-To succeed in this environment, participants had to select
-one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
-or acquire their own custom bridge and enter it manually.
-\end{description}
-
-\smallskip
-
-Table~\ref{tab:environments} summarizes our simulated censorship
-environments. We used features of the Windows operating system 
-to implement the above blocking behaviors.
-To simulate website blocking, we added entries to the hosts file,
-mapping domain names to the address 127.0.0.1.
-We used Windows Firewall rules for IP address blocking.
-
-\begin{table}
-\centering
-\begin{tabular}{r c c c}
-& E1 & E2 & E3 \\
-% \noalign{\hrule}
-websites blocked & X & X & X \\
-public relays blocked & & X & X \\
-default bridges blocked & & & X \\
-\end{tabular}
-\caption{
-Summary of our simulated censorship environments.
-E1 only requires participants to click ``Connect'';
-E2 requires selection of a built-in bridge;
-and E3 requires selection of a specific type of built-in bridge,
-or manual configuration of a custom bridge.
-E2's blocking is a superset of E1's;
-similarly E3's is a superset of E2's.
-}
-\label{tab:environments}
-\end{table}
-
-\section{Qualitative Analysis of the Existing Interface (Study 1)}
-\label{sec:qualitative}
-
-We ran a qualitative, exploratory user study to gain an 
-understanding of how users interact with the configuration interface and
-what common problems may be. We did this by observing participants using 
-the interface to circumvent censorship and interviewing them about
-their experience.  Our observations during this study guided us in
-redesigning the interface and provided hypotheses to test in our quantitative study.
-
-\subsection{Inspection}
-We used a combination of usability inspection methods~\cite{nielsen1994usability}
-to prepare for the user study. Two researchers conducted a pluralistic 
-walkthrough and stepped through various censorship
-scenarios, discussing which elements would be involved for that use case, and walking 
-through the configuration process. After compiling all the possible paths through the 
-interface, researchers performed feature inspection, listing sequences of features used 
-to accomplish typical tasks and taking note of long sequences or cumbersome
-steps. In addition, we performed a heuristic evaluation to mark
-likely causes of confusion for users during our study.
-
-\subsection{Recruitment}
-Using established practices from the field of user experience research~\cite{howmanyusers},
-we recruited 16 participants across the three censorship environments:
-5~in E1, 5~in E2, and 6~in E3.
-We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
-and self-reported familiarity with Tor in each simulated censorship environment for our summative
-usability test~\cite{summative}.
-
-We recruited our users from Craigslist, vaguely asking to evaluate a piece of software. 
-The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
-SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
-The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
-We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
-at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
-expertise or used particular security tools throughout the censorship environments.
-
-Of our 16 participants, 53.3\% were male. 
-Ages ranged from 20 to~62 years
-($\mu = 24.5$, $\sigma = 12.6$). 
-93.3\% of our participants had at least
-a college education.
-4 had used Tor before;
-5 had heard of Tor but not used it;
-and the remaining 8 had never heard nor used it.
-
-\subsection{Procedure}
-The one-hour, single-participant procedure begun when a participant entered a small 
-room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
-Each participant is informed of the risks and purpose of the study.
-A researcher informed the participant of the simulated censorship environment and
-instruct them to visit sample blocked and unblocked websites
-in a standard browser (Appendix~\ref{qualitative-script}). 
-This shows participants what a blocked site looks like in a browser. 
-Then, the participant was asked to complete a worksheet that gives information
-on their censorship environment and instructed them
-to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
-The worksheet informed the participant that the network is censored,
-but did not give details of what services and websites are specifically blocked.
-Participants were able to visit the unblocked website using any familiar browser,
-but had to configure Tor Browser in order to visit the blocked website.
-
-For the blocked website, we used the main page of Wikipedia,
-and for the unblocked site we used the CNN homepage.
-We chose these two sites because of their likely familiarity to web users;
-our goal was to evaluate the user interface, not to test users with a browsing task.
-After instructions, the researchers stepped out of the room.There was no interaction
-between the participant and researcher for the rest of the session.
-Researchers watched a live video of each participant's screen from another room
-and saved the videos for review; the resulting videos and summaries
-are available from our project page.
-Participants had an average of 45 minutes to complete their worksheet.
-
-After participants completed the browsing tasks or ran out of time,
-we interviewed them about their experience and
-took notes of the questions and answers.
-We asked questions asking about their general experience, 
-interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
-We followed up with specific questions prompted from watching their screen. 
-This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
-We paid each participant~\$30 for their time.
-
-\subsection{Results} 
-We discuss six common challenges our participants encountered during the configuration process.
-Participant quotations come from live transcription during the post-experiment interview
-and are not necessarily verbatim.\\
-
-\begin{description}
-\item {\bfseries Users did not understand what proxies, bridges, and pluggable transports were.}
-Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary.
-
-\smallskip
-\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
-\smallskip
-\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
-\smallskip
-
-\item {\bfseries Users did not know if they should connect directly or configure a connection.}
-Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to.
-Other participants tried a direct connection because they did not know what to do, but configuring their connection seemed hard.
-
-\item {\bfseries Users did not know how to choose which bridge and pluggable transport to use.}
-On the bridge configuration screen, participants were confused by the names of the bridge transports.
-The most common behavior was to configure with the recommended bridge option (obfs3).
-If the recommended one did not work, participants did not know how to choose another.
-
-\smallskip
-\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
-\smallskip
-%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
-I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
-
-\item {\bfseries Users did not know when they are wrong.}
-Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
-When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
-
-\item {\bfseries Users assumed they are wrong when they are right.}
-The progress bar has a bug that causes it to update only when the level of progress increases.
-If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
-Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
-
-\smallskip
-\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
-\smallskip
-\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-\smallskip
-
-\item {\bfseries Users assume that proxy is required after a failed connection.}
-All of our participants who failed to connect (5 of 16) failed for this reason.
-Many mistakenly assumed that they needed a proxy upon failure, because the interface redirects to the proxy screen (the last screen) after failure.
-
-\smallskip
-\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
-\end{description}
-
-From interviewing our participants, we found that these challenges are the result of these underlying causes: \\
-
-\begin{description}
-\item {\bfseries Users do not know how to connect to Tor.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference among bridges, pluggable transports, and proxies.
-Participants did not know how to configure these network components without explicit additional instructions.
-\item {\bfseries Feedback is too technical, missing, or misleading.} Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e.
-a syntactically correct but invalid proxy).
-If participants did see an error message, they did not understand it.
-The progress bar bug also caused users to wrongly assume they were not making progress since it did not give feedback on subsequent attempts.
-\item {\bfseries Users do not understand censorship circumvention cues.} With enough technical background, there are  signals to what components are necessary and unnecessary.
-A connection to the Internet indicates that no proxy is required.
-A failed direct connection indicates a blocked Tor relay.
-A failed hard-coded bridge connection indicates a blocked bridge relay.
-However, the average user does not understand these signals.
-\end{description}
-
-The challenges users faced in the qualitative experiment and the respective underlying causes are used as feedback for redesigning the configuration interface.
-
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
-\label{fig:error}
-\end{figure}
-
-\section{Redesigning the Configuration Interface}
-We make ten changes to the Tor launcher configuration interface to help users connect to Tor.
-Since users did not know how to connect to Tor, we added advice where our users have previously struggled.
-Specifically, the following three changes were made to give users more information in during configuration: \\
-
-\label{redesign}
-
- \begin{figure*}[t]
-	\centering
-		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
-		\caption{In the OLD interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
-		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
-		be configured and directs to the bridge configuration screen (B2). 
-		The NEW interface gives users advice on configuring bridges
-		while giving the option of not configuring a bridge, on one screen (B).} 
-\end{figure*}
-
-\begin{figure*}[t]
-	\centering
-		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
-		\caption{In the OLD interface, users are asked, ``Does this computer need a local proxy to connect
-		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
-		proxy configuration screen (P2). The NEW interface checks the local machine's proxy settings,
-		and informs the user whether a proxy is required, and if so, what those settings are (P).}
-\end{figure*}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.85\textwidth]{old-and-new-flows.png}
-\caption{
-Comparison of user flow in the OLD and NEW interfaces.
-We collapsed the two bridge screens into one 
-and also collapsed the two proxy screens into one.
-We swapped the order of the bridge and proxy configuration
-so it matches the order of network components (compare with Fig.~\ref{fig:topology}).
-We added a summary screen as a last step before initiating a connection.\\
-\textbf{F}: first screen;
-\textbf{B/B1/B2}: bridge screens;
-\textbf{P/P1/P2}: proxy screens;
-\textbf{S}: summary screen;
-\textbf{Pr}: progress bar.
-}
-\label{fig:flow}
-\end{figure*}
-
-\begin{enumerate}
-\item Added instructions on what to try next on errors.
-When an error occurs, text advice on what to try next is shown to the user to help them recover from the error.
-The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy.
-\item Added guidance on choosing between connect and configure.
-Before, the interface only informed users that the connect option worked some of the time, but did not specify why that was so.
-We labeled the configure option as a manual option  specifically for users in heavily censored environments.
-\item Added explicit advice on choosing bridge transports.
-Users did not know which bridges to choose if they were in E3, which requires users to choose a meek or custom bridge.
-We added text that advises users to try a meek bridge if obfs3 does not work.
-\end{enumerate}
-
-Users found the feedback to be more confusing than helpful, since error messages were technical and progress bar was misleading.
-We make the following changes to make feedback insightful and reflective of system state:\\
-\begin{enumerate}
-\setcounter{enumi}{3}
-\item Progress bar feedback is accurate.
-We fixed the bug that caused the progress bar to not update on subsequent attempts.
-What users now see on the progress bar reflects the reality of the progress.
-\item Made the interface text less technical.
-We made the text more task-centric by focusing on instructing users through the configuration process.
-Since users generally did not understand the technical concepts sufficiently to influence their decisions, we think giving direct guidance is a better option.
-\item Added system status visibility.
-Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings.
-The same information is shown on the progress screen while the connection is in progress.
-We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
-\end{enumerate}
-
-Our users had little technical background. We made the following changes to make the interface more compatible for the average user: \\
-
-\begin{enumerate}
-\setcounter{enumi}{6}
-\item Eliminated technical questions.
-We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
-This are two fewer screens in the revised interface.
-\item Added auto-detection of proxies.
-In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration.
-This purely local detection does not carry any risks nor reveal to network eavesdroppers that the user is using Tor.
-(We simulated the auto-detection by hard-coding the fact that a proxy was not required.)
-\item Switched ordering to configure proxies first.
-To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen.
-Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
-With auto-detection, configuring a proxy before a bridge burdens users less than before.
-\end{enumerate}
-
-These changes result in a redesigned interface which we refer to as NEW.
-Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.
-
-\section{Quantitative Analyses of the Interfaces (Study 2)}
-\label{sec:quantitative}
-Having identified problems with the existing interface
-and made changes to ameliorate them,
-we quantify the existing problems
-and the impact of our changes with a study involving a larger number of users.
-We split participants by simulated censorship environments,
-and between old and new interfaces.
-
-\subsection{Setup}
-We ran our experiment at Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of 
-California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
-Though Tor Browser runs on other operating systems,
-testing was only done on Windows, as a byproduct of using Xlab.
-
-We augmented the interfaces with instrumentation 
-to log every meaningful interaction
-(button presses, menu selections, screen changes).
-We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
-start the video recording, and save the logs and videos.
-We recorded the participants' computer screens
-throughout the experiment to capture non-interface activity such as 
-web searching and inspection of system networking settings.
-
-\subsection{Recruitment}
-We recruited 124 participants, about 20 for each
-condition. We recruited half of our users from Craigslist, and half of our participants from 
-the Xlab participant pool. Although Xlab participants are not limited to UC Berkeley students and staff,
-a majority of the participants are from campus. For this reason, we chose to recruit 
-half of our participants from Craigslist to ensure a diverse set of participants. 
-The recruitment text vaguely suggests testing a piece of software, and does not require
-that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
-Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
-recruited from Craigslist. Ages ranged from 18 to~68 years
-($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
-84.8\% of our participants had at least a college education.
-
-\subsection{Procedure}
-The one-hour, multi-participant procedure began when all participants sat at their
-respective computers in Xlab. Each computer was equipped with an instrumented old or new version
-of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
-Each computer was assigned one of the six conditions in the beginning of the study. Participants
-were assigned to a simulated censorship environment combination at random.
-
-A researcher informed the participants that they are in a
-simulated censorship environment, instructed them to visit a sample blocked website on a 
-non-Tor browser of their choice to illustrate the situation, and asked them to 
-complete a worksheet that asks to visit one blocked website (Appendix~\ref{quantitative-script}). 
-To mirror the qualitative study, we chose Wikipedia's featured article of the day 
-as the blocked website to visit on their worksheet.
-
-After instructions, researchers maintained minimal interactions with the participants, 
-only answering logistical questions.
-The participants did not know the details of their censorship environment,
-only that they are being censored. Participants had 40 minutes to configure Tor Browser to 
-circumvent the simulated censorship and visit the blocked website.
-
-After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
-that collected their demographics. All users were instructed to sit until the end of the experiment,
-regardless of when they had completed their task. After the 40 minutes, 
-participants were officially informed that their time was up, and were given their payment of 
-\$30 for their time.
-
-\subsection{Results} 
-The possible interface version and environment combinations resulted in 6 experimental conditions.
-We recruited 124 participants to aim for about 20 participants per condition.
-We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants.
-Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
-
-\begin{table}
-\centering
-	% Generated by info.R.
-	\begin{tabular}{l r r r r r}
-	& \multicolumn{2}{r}{success rate} & \multicolumn{1}{r}{median time} &\multicolumn{1}{r}{median}\\
-	& \multicolumn{2}{r}{after 40 minutes} & \multicolumn{1}{r}{to success} & \multicolumn{1}{r} {active time} \\
-	\noalign{\hrule}
-	E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
-	E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
-	E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
-	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
-	E3-NEW & 13/19 & 68\% & 12:38 & 1:56 \\ 
-	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
-	\end{tabular}
-\caption{
-A summary of participants' success in circumventing censorship
-given their simulated censorship environment and version of Tor. Those who
-failed to connect successfully were assigned the maximum time of 40:08.
-}
-\label{table:participant-summary}
-\end{table}
-
-\subsubsection{Rate of Success} 
-49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did.
-Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
-Appendix~\ref{stat-tests} details the methodology for the statistical tests used in this paper.
-
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=.5\textwidth]{warning.png}
-%\caption{
-%A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
-%which appears silently and does not interrupt the progress bar. 
-%This warning was generated by entering in syntactically correct but invalid proxy settings,
-%a mistake that prevents users from ever connecting to the Tor network. 
-%Users are never directly notified of this error through an error message or a timeout message.
-%Our participants made this error during our experiments, along with others that they were not notified about. 
-%}
-%\label{fig:warning}
-%\end{figure}
-
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=.5\textwidth]{log-messages.png}
-%\caption{
-%The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
-%These log lines were the result of entering in syntactically correct but invalid proxy settings,
-%a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
-%technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
-%}
-%\label{fig:warning_log}
-%\end{figure}
-%
-%We believe that the added advice on what to try next on error messages would have improved the rate of success.
-However, only 1 of 116 participants saw an error during the experiment.
-The old interface warned users on some mistakes (i.e.
-entering in a syntactically correct but invalid proxy settings) rather than displaying an error message.
-When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}).
-To see the log messages, users must click on the button, open up a text editor, and paste the log messages.
-The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
-%
-%That participant was using the new interface and was told that the bridge configuration was the source of the error.
-The participant heeded the interface's advice to reconfigure the bridge options.
-But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results.
-The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
-
-We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure.
-Of the 75 participants that failed to connect on the first attempt, 15 participants with the new interface and 13 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
-10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim choosing meek bridges is a direct result of our advice.
-
-Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.We only consider the first successful connection since many of our curious participants tried many different settings to investigate if they will work, even after they had completed the task.
-Recall E1 does not require users to configure a bridge, E2 requires users to configure any bridge, and E3 requires users to configure a meek or custom bridge.
-Note that only four of the hard-coded bridges were used to connect successfully for the first attempt were the recommended bridge and the required bridges to succeed in E3.
-
-Our participants did not optionally configure a bridge in E1 or configure a non-recommended bridge in E2.
-This suggests that users will not configure optional components or deviate from the recommended settings unless necessary.
-If the intent of the recommendation is to get as many users as possible to use the recommended bridge, this is a positive result.
-If the intent of the recommendation is to give pointers when users are stuck but allow the users to make their own bridge choices to diversify active transports, this is a negative result.
-
-Only two participants chose to configure a custom bridge.
-Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result.
-Appendix~\ref{custom} shows the malformed requests.
-These two participants failed to connect to the Tor network.
-
-\begin{table}
-\centering
-% Generated by attempts.R, and manually reordered:
 \begin{tabular}{r c c c c c c}
@@
 \end{tabular}
-\caption{
-Bridge--proxy combinations that led to the first successful bootstrap
-in each environment and interface.
-Most E1 participants used a direct connection,
-but a few tried a built-in obfs3 bridge.
-All the E2 participants who succeeded,
-did so with obfs3 (the recommended bridge type)---none tried
-a different bridge before obfs3.
-All of the successful E3 participants but one
-used one of the meek bridges.
-The remaining E3 participant succeeded in an unexpected way:
-by searching the web for an open proxy and configuring it
-as the proxy setting.
-}
-\label{tab:attempts-bridge-proxy}
-\end{table}
-
-\subsubsection{Time to Success} 
-Time to success is defined as the time until the first successful connection to Tor.
-Non-finishing participants are assigned the maximum experiment time of 40:08.
-Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
-Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
-
-\begin{figure}[t]
-\centering
-\includegraphics{time_to_success_clamped}
-\caption{
-Time to first success, by censorship environment and interface.
-The dots show the raw completion times,
-while the boxplots show the medians and interquartile ranges.
-The ``DNF'' figures at the right show the number of participants 
-who did not finish in the time allotted.
-Here, non-finishing participants are assigned the maximum time of 40:08.
-}
-\label{fig:time_to_success_clamped}
-\end{figure}
-
-In our experiment, participants had 40 minutes to circumvent censorship.
-Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
-In practice, faster time to completion would mean more users will succeed, since users will give up after a while.
-Users in the wild will likely not be motivated to spend 40 minutes trying to configure Tor.
-If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
-Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
-Ideally, users should be able to connect to Tor within a few minutes, regardless of their censorship environment.
-We propose ideas on how to achieve this in section~\ref{recommendations}.
-
-\begin{figure}[t]
-\centering
-\includegraphics{time_to_success_ecdf}
-	% Generated by info.R:
-	\begin{tabular}{l r r r r}
-	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
-	\noalign{\hrule}
-	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
-	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
-	E2-NEW & 11\% & 83\% & 94\% & 100\% \\
-	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
-	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
-	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
-	\end{tabular}
-\caption{
-Cumulative success rates over time, by censorship environment and interface.
-We stopped participants after 40 minutes. Here, those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
-For example, every E1-NEW participant finished within 90 seconds,
-but only 58\% of E1-OLD had finished by that time. Within 10 minutes, most
-participants in E2 had finished, along with a minority of E3 participants. 
-}
-\label{fig:time_to_success_ecdf}
-\end{figure}
-
-\subsubsection{Active Time} 
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
-Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
-The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
-
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The ``not running'' times are those when Tor Launcher was closed;
-i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes
-(marked with a $\times$).
-}
-\label{fig:all-participant-edges}
-\end{figure*}
-
-The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
-With correct configurations, the bootstrap process can take up to two minutes.
-With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.
-Logs show that participants spent 58\% of their overall time at the progress screen.
-Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.
-
-\begin{table}[t]
-\centering
-	\begin{tabular}{c r r r r}
-	& First & Proxy & Bridge & Progress \\
-	\noalign{\hrule}
-	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
-	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
-	E2-NEW & 6\% & 5\% & 6\% & 78\% \\
-	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
-	E3-NEW & 3\% & 5\% & 5\% & 77\% \\
-	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
-	\end{tabular}
-\caption{The median percent of time spent on each screen, which is not
-necessarily the median absolute time spent on that screen. 
-This percentage is computed independently for each screen; that is, a participant who spent the median percent 
-of time on one screen may not be the same participant who spent the median percent
-of time on other screens. Note that the time spent on the progress bar dominates the 
-time spent in the interface.} 
-\label{table:median_time}
-\end{table}
-
-\begin{figure}[t]
-\centering
-\includegraphics{time_to_success_active_clamped}
-\caption{
-Active time, by censorship environment and interface.
-The dots show the raw active configuration times,
-while the boxplots show the medians and interquartile ranges.
-Here, non-finishing participants' active time was computed by
-subtracting the amount of time spent on the progress screen from the 
-the maximum time of 40:08.
-}
-\label{fig:time_to_success_active_clamped}
-\end{figure}
-
-Perhaps a more meaningful measurement is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}).
-We define active time as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-Active time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
-This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.
-
-We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface.
-Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
-
-\subsection{Discussion} 
-We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.
-
-\subsubsection{Failures}
-Failure is common.
-17\% (19 of 114) of participants were not able to successfully connect to Tor.
-63\% (72 of 114) of first attempts to connect failed and 79\% (36 of 458) of total attempts to connect failed.
-Reasons for failure were determined by a combination of log processing (i.e.
-configuration settings on attempts) and video observation (i.e.
-observing what they searched for online).
-\\
-
-\begin{description}
-\item {\bfseries Only connected directly (6/19).} P73, P75, P89, P91, P106, P110 tried a direct connection.
-When that failed, they tried the same option, over and over, no matter how many times they failed.
-It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-
-\item {\bfseries Only tried recommendations (5/19).} P90, P93, P108, P111, P114, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
-They often tried those configurations again or gave up.
-
-\item {\bfseries Thought that they needed a proxy (5/19).} P74, P92, P105, P107, P113 assumed that they needed a proxy.
-They spent their time trying to configure a proxy, usually without trying other bridges.
-
-\item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
-However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
-\end{description}
-
-We discarded data on participants who chose to download their own version of Tor Browser online.
-5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
-Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
-
-\subsubsection{Observations}
-We noticed several behavioral patterns in our participants. These may or may not apply to the Tor user base.\\
-
-\begin{description}
-%connect vs configure
-\item {\bfseries Users try the easy path first.} Users generally try connecting directly to the Tor network first.
-81\% (92 of 114) of first attempts were to connect directly, with 52\% (48 of 92) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
-This leaks to network eavesdroppers that they are connecting to Tor.
-
-% impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly.
-Participants with the new interface (which explicitly states that they did not need a proxy) spent about the same time configuring proxies as bridges, whereas users with the old interface spent about twice as much time configuring proxies than bridges.
-We do not understand why users with the new interface spent time configuring proxies after explicitly being told that they do not need one.
-
-% impacts of giving people advice on which transport to choose.
-\item {\bfseries The interface has a large influence on the bridges chosen.}
-Participants in E3 were required to choose a particular subset of hard-coded bridges, none of which was the default bridge.
-After the default bridge, the most chosen bridge was the one listed first in the drop-down menu.
-Many bridges listed at the end of the drop-down menu were not chosen.
-We tried to help users by providing instructions on which bridges to choose if the default fails, but it is unclear if this advice helped.
-66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
-
-%error messages
-\item {\bfseries People saw (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
-Error messages are intended to appear after a timeout.
-There were warnings, but those warnings went largely unnoticed by our participants.
-Across both versions of the interface, only one participant ever saw an error message.
-We tried to make error messages more instructive and understandable, since participants in our experiment did not encounter error messages, we cannot evaluate them.
-
-% progress bar
-\item {\bfseries People waited a long, long time at the progress bar.}
-From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are who are uncertain wait without taking additional actions.
-\end{description}
-
-\subsubsection{Recommendations}
-\label{recommendations}
-Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\
-
-\begin{description}
-\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, a user has already leaked to network eavesdroppers leaking that they are connecting to Tor.
-Automating the configuration process thereafter will have no increase in risk.
-This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 63\% of participants who failed their first attempt.
-Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
-\item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy.
-Only a small fraction of the Internet population requires a proxy to connect to the Internet.
-Hiding the proxy screen by default and only showing it after it has been detected as necessary might improve the user experience focusing user effort on configuring bridges.
-\item {\bfseries Be explicit about recommendations.} Many do not know what to do after the recommended bridge failed.
-The interface should mark which bridges have been tired before and recommend the user to try another bridge.
-(i.e.
-After a user tried an obfs3 bridge, the interface updates its recommendation to a meek bridge and mark the obfs3 bridge with an ``X''.)
-\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration.
-\item{\bfseries Have a user-tolerant bridge auto-responder.} The bridge auto-responder responds to user requests for custom bridges.
-Users can make this request by emailing bridges@torproject.org with a non-empty title and ``get bridges'' in the body.
-Both of our users who tried to get custom bridges this way failed to format their request correctly.
-Having the auto-responder respond with bridges as a default or recovering from common errors (such as typing ``get bridges'' in the subject line) may help users succeed.
-\end{description}
-
-Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.
-
-\section{Limitations} 
-The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
-We only tested interface on Windows machines, which were the machines available at Xlab.
-Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.
-
-We refreshed a list of Tor relay IP addresses and added them
-to a firewall blacklist before each session.
-In the first study, we neglected to block the IP addresses
-of the Tor directory authorities, which are the first hosts
-a client contacts when initiating a non-bridge connection.
-New relays also appeared in the network on an hourly basis,
-which enabled a small number of participants to succeed with
-a direct connection when that configuration should have failed.
-We believe this is acceptable because 
-the qualitative user study was not used to quantify failures or successes, 
-but to explore possible problems.
-We fixed this problem in our quantitative user study by blocking the directory authorities.
-
-%We blocked en.wikipedia.org, the target of the experiment,
-%as well as other language-specific subdomains such as
-%de.wikipedia.org and fr.wikipedia.org.
-%We neglected, however, to block the Simple English Wikipedia
-%at simple.wikipedia.org, which one participant found,
-%thinking they had completed the task.
-%% E2-OLD-X04-20160330-181928
-
-Our study was conducted in a laboratory setting, which can cause our participants to be under or over-motivated.
-Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website.
-
-We chose to focus on more common cases, and did not simulate environments that requires users to configure a custom bridge or proxy.
-Although users in the wild can download interfaces that are not in their native language, we do not know how often this happens.
-We tested the English version of the Tor interface on English speaking participants.
-
-\section{Future Work} 
-Our goal was to deploy impactful, tested changes the Tor configuration interface.
-In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
-Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away.
-For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed.
-However, we list some alternative approaches that seem worth exploring.
-\\
-
-\begin{description}
-\item{\bfseries Automate the configuration.} The most efficient way to connect as many users to the Tor network is to automatically configure their connection on start.
-A naive automation is to try configurations that would most likely work, in order (i.e.
-a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
-This leaks to network eavesdroppers that the user is connecting to the Tor network.
-We do not know how much risk is associated with this approach.
-\item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk.
-The complication with this approach is that users may not be qualified to answer if they are at risk or may not trust Tor with this information.
-\item{\bfseries Ask if users know what to do.} Another alternative to naive automation is to offer manual configuration to those that know how to configure their connection and to automate the process for users who do not know how to configure their connection.
-This may prevent the most mistakes, but does not account for the users' risk associated with using Tor.
-\item{\bfseries Suggest configurations.} A way to help users without any automation or questions is to give users information about what would work in their country.
-The first page of the configuration interface can show a list of countries with a corresponding recommended configuration.
-This approach does not require users to answer about their risk, technical ability, or location.
-However, it does require that the user trust the given advice and to correctly configure their settings based on this advice.
-\item{\bfseries Assign configurations.} This is a smart way to automate connections to the Tor network.
-Upon start, the interface detects proxy settings and uses them, if any.
-Then, all users connect to bridges that will always work (such as meek bridges), which assign them a guard relay based on their location, effectively assigning bridges for the user.
-\end{description}
-
-We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process.
-
-\section{Conclusion} 
-We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
-Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity.
-Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works.
-We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.
-
-%general advice to other censorship circumvention and call for more research 
-Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
-When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g.
-pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components.
-We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
-Not only do simulated environments avoids rerouting traffic through a censoring countries' networks, its reproducibility and stability ideal for experiments.
-
-\section {Resources} 
-For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
-
-\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
-
-\section {Acknowledgments}
-I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting.
-I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
-
-\bibliographystyle{abbrv}
-\bibliography{pets2017-paper}
-
-\appendix
-
-\section{Qualitative User Study Recruitment Posting} 
-\label{qualitative-recruitment}
-We are recruiting participants for an in-person research study at the University of California, Berkeley.
-You will need to come in to our lab and perform tasks on a computer for an hour or less.
-You will be compensated \$30 for participating.
-No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.
-
-\section{Qualitative User Study Prescreening Survey} 
-\label{qualitative-prescreening}
-We are recruiting participants for an in-person research study at the University of California, Berkeley.
-You will need to come in to our lab and perform tasks on a computer for an hour or less.
-You will be compensated \$30 for participating.
-No special knowledge and no technical experience is required.\\
-
-\begin{enumerate}
-\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
-\item{I am able to provide my own transportation to the University of California, Berkeley campus.}
-\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
-\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
-\item{What is your gender?}
-\item{What is your age?}
-\item{Please select your highest completed (or current) level of education.}
-\item{What is your occupation?} 
-\item{Do you speak any languages other than English fluently?}
-\item{If you have a personal computer, what kind do you use?}
-\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
-\item{How often do you use the following software or features?
-\textit{<answer choices: a grid of radio buttons.
-Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption.
-Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
-\end{enumerate}
-Thank you for filling out this form. You are now done!
-
-\section{Qualitative User Study Introduction Script} 
-\label{qualitative-script} 
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
-
-To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
-If you are able to reach the website, then you know that you have successfully circumvented censorship.
-Fill out the question on the worksheet.
-This isn't intended to be hard, just write what you see.
-We want to just check you saw the website.
-
-Before you start, do you have any questions about what you are asked to do?
-
-\section{Participant Worksheet Text} 
-\label{participant-worksheet}
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-For instance, www.torproject.org is blocked.
-Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
-It will fail to load, when you can visit other sites.
-
-To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
-If you can visit wikipedia, then you know that you have successfully circumvented censorship.
-
-\section{Post-Experiment Standard Interview Questions}
-\label{interview-questions}
-We asked our participants these questions after they were given time to configure Tor Browser. \\
-
-\begin{enumerate}
-\item{Can you talk us through what you did along with what you were thinking at the time?}
-\item{What was most challenging part of connecting?}
-\item{Were there any unfamiliar terms?}
-\item{How did you decide which options to choose?}
-\item{What did you think about using Tor?}
-\item{What is one change you would recommend?} 
-\item{Did you need any additional information?} 
-\end{enumerate}
-
-In addition to these questions, we asked our participants about specific questions based on their observation, usually regarding a specific choice in action, a particular screen they seemed stuck on, and any errors they encountered during the configuration process.
-
-\section{Quantitative User Recruitment Posting}
-\label{quantitative-recruitment}
-We are recruiting up to 40 participants for a user study at UC Berkeley.
-The experiment will involve basic Internet browsing tasks.
-You are not eligible if you have participated in our previous sessions.\\
-
-\indent Payment: \$30 Amazon gift card\\
-\indent Duration: 1 hour \\
-\indent Where: Xlab at Hearst Memorial Gymnasium\\
-
-\textit{<list of sessions>}\\
-
-To be eligible, you must be an adult (18 or older). This is to comply with university policies on research.
-
-If you are interested: 1.
-Email lnl@berkeley.edu with the sessions you are able to attend.
-We will confirm your participation and assign you a session.
-2.
-Come to Xlab at the appointed time for the experiment.
-
-\section{Quantitative User Study Introduction Script} 
-\label{quantitative-script} 
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
-
-To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
-Tor is already installed for you.
-On the desktop, you should see a globe icon that says ``Start Tor Browser.'' If you are able to reach the website, then you know that you have successfully circumvented censorship.
-Fill out the question on the worksheet.
-This isn't intended to be hard, just write what you see.
-We want to just check you saw the website.
-
-Afterward, we ask you to take a short survey to collect some information about you. The link is also on your worksheet.
-We will give you time to complete this task.
-If you finish early, we ask that you sit at your desk until the remainder of the hour.
-Since we are recording your screen, we ask that you don't do anything personal afterward, like checking your email.
-
-Before you start, do you have any questions about what you are asked to do?
-
-\section{Quantitative User Study Exit Survey} 
-\label{quantitative-exit-survey}
-We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.
-
-This survey is part of a research project being conducted by the University of California, Berkeley.
-If you have any questions about your rights or treatment as a research participant in this study, please contact the University of California at Berkeley's Committee for Protection of Human Subjects at 510-642-7461, or email subjects@berkeley.edu.
-If you agree to participate, please click Next below.\\
-
-\begin{enumerate}
-\item{What is your participant ID? (This can be found on the sticker on the left hand corner of the desk you are currently sitting at.)}
-\item{What is your gender?}
-\item{What is your age?}
-\item{Please select your highest completed (or current) level of education}.
-\item{What is your current occupation?}  
-\end{enumerate}
-
-Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
-
-\section{Statistical Tests} 
-\label{stat-tests}
-From our measurements, we observe that participants with the new interface 
-have a higher rate of success, succeed in less time, and configure their interface in less time. 
-We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
-We do find the the decreased active configuration time to be significant. 
-We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.
-
-%success rate and version
-Each participant had a boolean variable indicating a successful connection to Tor.
-Rates of success were calculated by dividing the number of participants who succeeded the condition over the total number of participants in the condition.
-This gave us six rates of success.
-E1-NEW, E2-NEW, and E3-NEW rates of success were compared against E1-OLD, E2-OLD, and E3-OLD.
-We used a Pearson's Chi-squared test to test the significance of success rates.
-The difference between success rates of participants with the new interface and participants with the old interface was not significant ($X^2 = 0.0126$, $df = 2$, $p = 0.994$).
-
-%time to success and version
-Time to success was measured as the time from the participants started the Tor launcher interface to the first successful bootstrap to the Tor network.
-This measurement was 1) non-normal and heavily right-tailed since participants were less and less likely to succeed as time went on and 2) right-censored at 40 minutes, the maximum time of the experiment.
-Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
-We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-
-%active time and version
-Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen.
-For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes.
-This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success.
-Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-
-\section{Custom Bridge Attempts} 
-\label{custom}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that P95 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
-\label{autoresponder1}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that P110 accidentally sent to the helpdesk rather than the bridge auto-responder.
-The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
-Since the helpdesk address is not an auto-responder, there was no reply.}
-\label{autoresponder2}
-\end{figure}
-
-\section{Tor Downloads}
-\label{tor-downloads}
-
-Participants that downloaded Tor Browser (5/124): 
-\begin{itemize}
-\item P115 (Fig.~\ref{softsonic})
-\item P116 (Fig.~\ref{techspot})
-\item P117, data not used (Fig.~\ref{mirror})
-\item P118, data not used (Fig.~\ref{downloadio})
-\item P119, data not used (Fig.~\ref{driverupdate})
-\end{itemize}
-
-%Sources of downloads: 
-%\begin{itemize}
-%\item {\bfseries techspot.com} $\rightarrow$ {\bfseries 1download.io}: an advertisement in the Yahoo search results for ``tor browser downloads''.
-%\item {\bfseries driverupdate.net}: the fifth Google search result for ``tor browser download''.
-%\item {\bfseries www.torservers.net/mirrors}: the first google search result for ``tor browser mirror''.
-%\item {\bfseries techspot.com}: the fifth Google search result for ``tor browser download''.
-%\item {\bfseries softsonic.com}: the second Yahoo search result for ``tor browser''.
-%\end{itemize}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
-\caption{P118 attempted to download Tor Browser from TechSpot.com, but clicked on
-a download link which was not from TechSpot.com. The download was from another site, 1download.io.}
-\label{downloadio}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
-\caption{P119 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
-are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
-participant dutifully does before running the Tor Browser executable.}
-\label{driverupdate}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
-\caption{P117 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
-\label{mirror}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
-\caption{P116 downloaded Tor Browser from TechSpot, clicking on the download link from 
-TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
-\label{techspot}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{P115 downloaded Tor Browser from Softsonic, a reputable-looking but
-unconfirmed site.}
-\label{softsonic}
-\end{figure}
-
-\end{document}

### 2016-05-11 pets2017-paper/pets2017-paper.tex
Move autogenerated tables into separate files.

@@
 \centering
-	% Generated by info.R.
-	\begin{tabular}{l r r r r r}
-	& \multicolumn{2}{r}{success rate} & \multicolumn{1}{r}{median time} &\multicolumn{1}{r}{median}\\
-	& \multicolumn{2}{r}{after 40 minutes} & \multicolumn{1}{r}{to success} & \multicolumn{1}{r} {active time} \\
-	\noalign{\hrule}
-	E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
-	E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
-	E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
-	E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
-	E3-NEW & 13/19 & 68\% & 12:38 & 1:56 \\ 
-	E3-OLD & 10/20 & 50\% & 40:08 & 9:06 \\
-	\end{tabular}
+\input{participant-summary.tex}
 \caption{
@@
 \centering
-% Generated by attempts.R, and manually reordered:
-\begin{tabular}{r c c c c c c}
-& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
-no bridge, no proxy & 17 & 13 &  &  &  &  \\
-obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
-meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
-meek-google, no proxy &  &  &  &  & 5 & 4 \\
-meek-azure, no proxy &  &  &  &  & 1 & 1 \\
-no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
-DNF (did not finish) &  &  &  & 3 & 7 & 9 \\
-\end{tabular}
+\input{attempts-bridge-proxy.tex}
 \caption{
@@
 \includegraphics{time_to_success_ecdf}
-	% Generated by info.R:
-	\begin{tabular}{l r r r r}
-	& \multicolumn{1}{c}{1.5~m} & \multicolumn{1}{c}{10~m} & \multicolumn{1}{c}{20~m} & \multicolumn{1}{c}{40~m} \\
-	\noalign{\hrule}
-	E1-NEW & 100\% & 100\% & 100\% & 100\% \\
-	E1-OLD & 58\% & 100\% & 100\% & 100\% \\
-	E2-NEW & 11\% & 83\% & 94\% & 100\% \\
-	E2-OLD & 16\% & 68\% & 79\% & 84\% \\
-	E3-NEW & 0\% & 25\% & 45\% & 65\% \\
-	E3-OLD & 0\% & 20\% & 25\% & 50\% \\
-	\end{tabular}
+\input{time_to_success_ecdf.tex}
 \caption{

### 2016-05-11 experiment/processing/graphs.R
Move labels in time_to_success_ecdf graph.
The data under E2-NEW and E3-NEW changed, so the lines moved.

@@ -76,7 +76,7 @@ p <- p + scale_color_manual(values=palette)
 # p <- p + guides(color=guide_legend(override.aes=list(size=2, title=NULL)))
 p <- p + guides(color=F)
 p <- p + labs(title=NULL, x="Minutes elapsed", y="Successful participants")
-p <- p + annotate(geom="text", x=c(1, 3.3, 14, 15.3, 23, 24.7), y=c(0.86, 0.87, 0.91, 0.71, 0.61, 0.32), label=c("E1-\nNEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=c(1, 0, 0, 0, 0, 0), vjust=0, size=2, lineheight=0.8)
+p <- p + annotate(geom="text", x=c(1, 3.3, 14.2, 15.3, 23.4, 24.7), y=c(0.86, 0.87, 0.87, 0.71, 0.55, 0.32), label=c("E1-\nNEW", "E1-OLD", "E2-NEW", "E2-OLD", "E3-NEW", "E3-OLD"), hjust=c(1, 0, 0, 0, 0, 0), vjust=0, size=2, lineheight=0.8)
 p <- common_theme(p)
 ggsave("time_to_success_ecdf.pdf", p, width=columnwidth, height=height, device=cairo_pdf)
 

### 2016-05-12 experiment/processing/info.R
Output a table of all participant times and percentages.
It's in two columns because that's required in order to fit on the
printed page.

@@ -382,4 +382,30 @@ for (e in names(ecdfs)) {
 cat("\\end{tabular}\n")
 sink()
 
+for (column in list(c("E1-NEW", "E1-OLD", "E2-NEW"), c("E2-OLD", "E3-NEW", "E3-OLD"))) {
+	cat("\\adjustbox{valign=t}{\n")
+	cat("\\begin{tabular}{r @{~} r r@{~}r r@{~}r r@{~}r r@{~}r}\n")
+	cat("& & \\multicolumn{2}{r}{First} & \\multicolumn{2}{r}{Proxy} & \\multicolumn{2}{r}{Bridge} & \\multicolumn{2}{r}{Progress} \\\\\n")
+	for (block in column) {
+		parts <- unlist(strsplit(block, "-"))
+		env <- parts[[1]]
+		version <- parts[[2]]
+		env.version <- screen_time_per_user[screen_time_per_user$env==env & screen_time_per_user$version==version, ]
+		cat("\\noalign{\\hrule}\n")
+		cat(sprintf("\\multirow{%d}{*}{\\rotatebox{90}{%s-%s}}\n", nrow(env.version), env, version))
+		for (userid in env.version$userid) {
+			cat(sprintf("& P%d", userid))
+			user <- screen_time_per_user[screen_time_per_user$userid==userid, ]
+			for (edges in c("first_edges$duration", "proxy_edges$duration", "bridge_edges$duration", "progress_edges$duration")) {
+				cat(sprintf(" & %s & %.f\\%%",
+					format_minutes_colons(user[[edges]]),
+					100 * user[[edges]]/user[["edges$duration"]]))
+			}
+			cat(" \\\\\n")
+		}
+	}
+	cat("\\end{tabular}\n")
+	cat("}\n")
+}
+
 cat("\n\n\n\n\n\n")

### 2016-05-12 experiment/processing/info.R
Make all-participant-times.tex be autogenerated.

@@ -382,6 +382,8 @@ for (e in names(ecdfs)) {
 cat("\\end{tabular}\n")
 sink()
 
+sink("all-participant-times.tex")
+cat("% Do not edit this file. Edit info.R instead.\n")
 for (column in list(c("E1-NEW", "E1-OLD", "E2-NEW"), c("E2-OLD", "E3-NEW", "E3-OLD"))) {
 	cat("\\adjustbox{valign=t}{\n")
 	cat("\\begin{tabular}{r @{~} r r@{~}r r@{~}r r@{~}r r@{~}r}\n")
@@ -407,5 +409,6 @@ for (column in list(c("E1-NEW", "E1-OLD", "E2-NEW"), c("E2-OLD", "E3-NEW", "E3-O
 	cat("\\end{tabular}\n")
 	cat("}\n")
 }
+sink()
 
 cat("\n\n\n\n\n\n")

### 2016-05-12 experiment/processing/info.R
Make median_time.tex be autogenerated.

@@ -382,6 +382,24 @@ for (e in names(ecdfs)) {
 cat("\\end{tabular}\n")
 sink()
 
+sink("median_time.tex")
+cat("% Do not edit this file. Edit info.R instead.\n")
+cat("\\begin{tabular}{l r r r r}\n")
+cat("& First & Proxy & Bridge & Progress \\\\\n")
+cat("\\noalign{\\hrule}\n")
+for (env in levels(screen_time_per_user$env)) {
+	for (version in levels(screen_time_per_user$version)) {
+		cat(sprintf("%s-%s", env, version))
+		env.version <- screen_time_per_user[screen_time_per_user$env==env & screen_time_per_user$version==version, ]
+		for (edges in c("first_edges$duration", "proxy_edges$duration", "bridge_edges$duration", "progress_edges$duration")) {
+			cat(sprintf(" & %.f\\%%", 100 * median(env.version[[edges]]/env.version[["edges$duration"]])))
+		}
+		cat(" \\\\\n")
+	}
+}
+cat("\\end{tabular}\n")
+sink()
+
 sink("all-participant-times.tex")
 cat("% Do not edit this file. Edit info.R instead.\n")
 for (column in list(c("E1-NEW", "E1-OLD", "E2-NEW"), c("E2-OLD", "E3-NEW", "E3-OLD"))) {

### 2016-05-12 experiment/processing/common.R
Update common_theme for ggplot2 2.1.0.
The default axis tick lengths changed, leading to lots of extra
whitespace around the graph.

"Panel Grid Aesthetics Can't be Changed for theme_classic"
https://github.com/hadley/ggplot2/issues/1555

@@ -125,5 +125,6 @@ common_theme <- function(p) {
 	p <- p + theme_minimal()
 	p <- p + theme(text=element_text(size=8))
 	p <- p + theme(plot.margin=margin(0,0,0,0,"mm"))
+	p <- p + theme(axis.ticks=element_blank(), axis.ticks.length=unit(0,"lines"))
 	p
 }

### 2016-05-12 pets2017-paper/pets2017-paper.tex
\hyphenation{Isa-bela}
It was being broken as Is-
abela.
Left-align the env–version column of table:median_time.
To match other tables.
Add all-participant-times appendix.
Move table:median_time into a file so it can be autogenerated.
Fix grammar.

@@
 \usepackage{pdfpages}
+\usepackage{adjustbox}
 %\usepackage{hyperref}
@@
 \usepackage[big]{dgruyter_NEW}
+
+\hyphenation{Isa-bela}
 
@@
 \centering
-	\begin{tabular}{c r r r r}
-	& First & Proxy & Bridge & Progress \\
-	\noalign{\hrule}
-	E1-NEW & 28\% & 0\% & 0\% & 60\% \\
-	E1-OLD & 30\% & 0\% & 0\% & 29\% \\
-	E2-NEW & 6\% & 5\% & 6\% & 78\% \\
-	E2-OLD & 7\% & 18\% & 8\% & 45\% \\
-	E3-NEW & 3\% & 5\% & 5\% & 77\% \\
-	E3-OLD & 2\% & 12\% & 6\% & 64\% \\
-	\end{tabular}
+\input{median_time.tex}
 \caption{The median percent of time spent on each screen, which is not
@@
 We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
-Not only do simulated environments avoids rerouting traffic through a censoring countries' networks, its reproducibility and stability ideal for experiments.
+Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
 
@@
 
+\section{All Participant Times}
+\label{all-participant-times}
+
+\begin{table*}
+\input{all-participant-times.tex}
+\caption{
+Times spent on each screen, per participant.
+}
+\label{table:all-participant-times}
+\end{table*}
+
 \end{document}

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
make a copy for my master's thesis.

--- 2016-05-12 pets2017-paper/pets2017-paper.tex
@@
 \caption{
-Bridge selection options in Tor Launcher, as it appeared in Tor Browser~5.0.3.
-Users are not familiar with the options under ``Transport type'' denote various
+Bridge selection options in Tor Launcher for Tor Browser~5.0.3.
+Users are not familiar with the options under ``Transport type,'' which are various
 built-in circumvention technologies (``pluggable transports'').

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
use all-participant-edges with scales, including P57 and P91.
Fix numbers to match those of commit ce7d7e4926e325576491cf3ef6358b5d66821838.

@@
 We use the results as feedback to redesign the configuration interface.
-A 114-participant quantitative user study tests the impact of our changes.
+A 116-participant quantitative user study tests the impact of our changes.
 We find that our changes result in a significant reduction 
@@
 \item 10 changes to the configuration interface which we hope alleviates the common challenges
-\item 114 logs of real world user attempts to connect to Tor in three different censorship environments
+\item 116 logs of real world user attempts to connect to Tor in three different censorship environments
 \item 4 reasons why users failed to connect to Tor
@@
 We recruited 124 participants to aim for about 20 participants per condition.
-We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants.
+We filtered participants who did not use our instrumented version of Tor Browser or did not sign the consent form, resulting in 116 participants.
 Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
@@
 \subsubsection{Rate of Success} 
-49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did.
+50 of 58 (86\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did.
 Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
@@
 We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure.
-Of the 75 participants that failed to connect on the first attempt, 15 participants with the new interface and 13 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
+Of the 76 participants that failed to connect on the first attempt, 15 participants with the new interface and 13 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
 10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim choosing meek bridges is a direct result of our advice.
@@
 Non-finishing participants are assigned the maximum experiment time of 40:08.
-Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+{\color {red} Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).} The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
 Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
@@
 % the treatments.
-\includegraphics{all-participant-edges}
+\includegraphics{all-participant-edges-scales}
 \caption{
@@
 We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface.
-Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -2.7$, $p = 0.0032$, $r= 0.25$).
 Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
@@
 Failure is common.
-17\% (19 of 114) of participants were not able to successfully connect to Tor.
-63\% (72 of 114) of first attempts to connect failed and 79\% (36 of 458) of total attempts to connect failed.
+20\% (21 of 116) of participants were not able to successfully connect to Tor.
+64\% (74 of 116) of first attempts to connect failed and 79\% (376 of 462) of total attempts to connect failed.
 Reasons for failure were determined by a combination of log processing (i.e.
@@
 \begin{description}
-\item {\bfseries Only connected directly (6/19).} P73, P75, P89, P91, P106, P110 tried a direct connection.
+\item {\bfseries Only connected directly (7/21).} P57, P74, P76, P90, P93, P108, P112 tried a direct connection.
 When that failed, they tried the same option, over and over, no matter how many times they failed.
@@
 
-\item {\bfseries Only tried recommendations (5/19).} P90, P93, P108, P111, P114, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
+\item {\bfseries Only tried recommendations (6/21).} P91, P92, P95, P110, P113, P116, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
 They often tried those configurations again or gave up.
 
-\item {\bfseries Thought that they needed a proxy (5/19).} P74, P92, P105, P107, P113 assumed that they needed a proxy.
+\item {\bfseries Thought that they needed a proxy (5/21).} P75, P94, P107, P109, P115 assumed that they needed a proxy.
 They spent their time trying to configure a proxy, usually without trying other bridges.
 
-\item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
+\item {\bfseries Used the bridges auto-responder incorrectly (2/21).} P96, P111, who were in E3, emailed the bridges auto-responder to get custom bridges.
 However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
@@
 \item {\bfseries Users try the easy path first.} Users generally try connecting directly to the Tor network first.
-81\% (92 of 114) of first attempts were to connect directly, with 52\% (48 of 92) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
+81\% (94 of 116) of first attempts were to connect directly, with 53\% (50 of 94) direct first attempts from the new interface and 47\% (44 of 94) direct first attempts from the old interface.
 This leaks to network eavesdroppers that they are connecting to Tor.
@@
 Automating the configuration process thereafter will have no increase in risk.
-This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 63\% of participants who failed their first attempt.
+This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 64\% of participants who failed their first attempt.
 Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
@@
 Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
-We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.55$, $p = 0.0612$, $r= 0.143$).
 
@@
 Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.41$, $p = 0.000329$, $r = 0.316$).
 
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that P95 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
+\caption{The message that P96 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
 \label{autoresponder1}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that P110 accidentally sent to the helpdesk rather than the bridge auto-responder.
+\caption{The message that P111 accidentally sent to the helpdesk rather than the bridge auto-responder.
 The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
@@
 \begin{itemize}
-\item P115 (Fig.~\ref{softsonic})
-\item P116 (Fig.~\ref{techspot})
+\item P57 (Fig.~\ref{techspot})
+\item P91 (Fig.~\ref{softsonic})
 \item P117, data not used (Fig.~\ref{mirror})
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
-\caption{P116 downloaded Tor Browser from TechSpot, clicking on the download link from 
+\caption{P57 downloaded Tor Browser from TechSpot, clicking on the download link from 
 TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{P115 downloaded Tor Browser from Softsonic, a reputable-looking but
+\caption{P91 downloaded Tor Browser from Softsonic, a reputable-looking but
 unconfirmed site.}

### 2016-05-12 pets2017-paper/pets2017-paper.tex
Fix numbers to match those of commit ce7d7e4926e325576491cf3ef6358b5d66821838.

@@
 17\% (19 of 114) of participants were not able to successfully connect to Tor.
-63\% (72 of 114) of first attempts to connect failed and 79\% (36 of 458) of total attempts to connect failed.
+63\% (72 of 114) of first attempts to connect failed and {\color {red} 79\% (36 of 458)} of total attempts to connect failed.
 Reasons for failure were determined by a combination of log processing (i.e.
@@
 Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
-We do not find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+We find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
 
@@
 Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-We do find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+We find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
 

### 2016-05-12 lindas-ms-paper/attempts-bridge-proxy.tex
change aliases to copies of files

% Do not edit this file. Edit attempts.R instead.
\begin{tabular}{r c c c c c c}
& \rotatebox{90}{E1-NEW} & \rotatebox{90}{E1-OLD} & \rotatebox{90}{E2-NEW} & \rotatebox{90}{E2-OLD} & \rotatebox{90}{E3-NEW} & \rotatebox{90}{E3-OLD} \\
no bridge, no proxy & 17 & 13 &  &  &  &  \\
obfs3, no proxy & 2 & 6 & 18 & 16 &  &  \\
meek-amazon, no proxy &  &  &  &  & 7 & 4 \\
meek-google, no proxy &  &  &  &  & 5 & 4 \\
meek-azure, no proxy &  &  &  &  & 1 & 1 \\
no bridge, 3rd-party proxy &  &  &  &  &  & 1 \\
DNF (did not finish) &  &  &  & 3 & 6 & 10 \\
\end{tabular}

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
fix another sentence.

@@
 Non-finishing participants are assigned the maximum experiment time of 40:08.
-{\color {red} Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).} The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+Our changes to the interface did not have a significant impact in reducing the time participants took to successfully connect to Tor.
+The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
 Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
+%(Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$)
 

### 2016-05-12 lindas-ms-paper/lindas-ms-paper.tex
cite the table of all participants and order appendixes to be in order of citation.

@@
 \subsubsection{Active Time} 
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
+We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges} and summarize where they spent their time in Appendix~\ref{all-participant-times}.
 Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
@@
 
+\section{All Participant Times}
+\label{all-participant-times}
+Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface.
+These are the raw numbers used to compute values such as the median time spend on each screen.
+Participants are grouped by condition.
+Within each condition, participants are ordered in the order of time to success.
+For example, observe that P1 and P2 were in the E1-NEW condition and that P1 finished faster than P2.
+
+\begin{table*}
+\input{all-participant-times.tex}
+\caption{
+Times spent on each screen, per participant.
+}
+\label{table:all-participant-times}
+\end{table*}
+
 \section{Tor Downloads}
@@
 
-\section{All Participant Times}
-\label{all-participant-times}
-
-\begin{table*}
-\input{all-participant-times.tex}
-\caption{
-Times spent on each screen, per participant.
-}
-\label{table:all-participant-times}
-\end{table*}
-
 \end{document}

### 2016-05-12 pets2017-paper/pets2017-paper.tex
fix typo.
cite the table of all participants and order appendixes to be in order of citation.

@@
 17\% (19 of 114) of participants were not able to successfully connect to Tor.
-63\% (72 of 114) of first attempts to connect failed and {\color {red} 79\% (36 of 458)} of total attempts to connect failed.
+63\% (72 of 114) of first attempts to connect failed and (363 of 458) of total attempts to connect failed.
 Reasons for failure were determined by a combination of log processing (i.e.

### 2016-05-12 pets2017-paper/pets2017-paper.tex
anonymize.

@@
 \begin{document}
-
-  \author*[1]{Linda Lee}
-
-  \author[2]{David Fifield}
-
-  \author[3]{Nathan Malkin}
-
-  \author[4]{Ganesh Iyer}
-
-  \author[5]{Serge Egelman}
-
-  \author[6]{David Wagner}
-
-  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
-
-  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
-
-  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
-
-  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
-
-  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
-
-  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
+   \author*[1]{Author 1}
+
+  \author[2]{Author 2}
+
+  \author[3]{Author 3}
+
+  \author[4]{Author 4}
+
+  \author[5]{Author 5}
+
+  \author[6]{Author 6}
+
+  \affil[1]{Affiliation of Author 1, E-mail: \mbox{author1@affiliation.edu}}
+  \affil[2]{Affiliation of Author 2, E-mail: \mbox{author2@affiliation.edu}}
+  \affil[3]{Affiliation of Author 3, E-mail: \mbox{author3@affiliation.edu}}
+  \affil[4]{Affiliation of Author 4, E-mail: \mbox{author4@affiliation.edu}}
+  \affil[5]{Affiliation of Author 5, E-mail: \mbox{author5@affiliation.edu}}
+  \affil[6]{Affiliation of Author 6, E-mail: \mbox{author6@affiliation.edu}}
+%  \author*[1]{Linda Lee}
+%
+%  \author[2]{David Fifield}
+%
+%  \author[3]{Nathan Malkin}
+%
+%  \author[4]{Ganesh Iyer}
+%
+%  \author[5]{Serge Egelman}
+%  
+%  \author[6]{David Wagner}
+%
+%  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
+%
+%  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
+%
+%  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
+%
+%  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
+%  
+%  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
+%   
+%  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
 
@@
 \end{abstract}
-  \keywords{User Studies, Tor, Security, Censorship, Anonymity}
+  \keywords{Usable Security, User Studies, Tor, Security, Censorship, Anonymity}
 %  \classification[PACS]{}
@@
 \subsection{Setup}
-We ran our experiment at Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of 
-California, Berkeley. Xlab has 36 Windows~7 laptops, separated by cubicle walls. 
+We ran our experiment at <redacted> 
+%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
+<redacted> %Xlab 
+has 36 Windows~7 laptops, separated by cubicle walls. 
 Though Tor Browser runs on other operating systems,
-testing was only done on Windows, as a byproduct of using Xlab.
+testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.
 
@@
 condition. We recruited half of our users from Craigslist, and half of our participants from 
-the Xlab participant pool. Although Xlab participants are not limited to UC Berkeley students and staff,
+the <redacted> %Xlab 
+participant pool. Although <redacted> %Xlab 
+participants are not limited to <redacted> %UC Berkeley 
+students and staff,
 a majority of the participants are from campus. For this reason, we chose to recruit 
@@
 that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
-Out of our 124 participants, 59 were recruited from the Xlab pool and the other 65 were
+Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
+pool and the other 65 were
 recruited from Craigslist. Ages ranged from 18 to~68 years
@@
 The one-hour, multi-participant procedure began when all participants sat at their
-respective computers in Xlab. Each computer was equipped with an instrumented old or new version
+respective computers in <redacted>. %Xlab. 
+Each computer was equipped with an instrumented old or new version
 of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
@@
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
-We only tested interface on Windows machines, which were the machines available at Xlab.
-Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.
+We only tested interface on Windows machines, which were the machines available at <redacted>.
+%Xlab.
+Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.
 
@@
 
-\section {Resources} 
-For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
-
-\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
-
-\section {Acknowledgments}
-I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting.
+%\section {Resources} 
+%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
+%
+%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
+%
+%\section {Acknowledgments}
+%I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting.
 I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
@@
 \label{qualitative-recruitment}
-We are recruiting participants for an in-person research study at the University of California, Berkeley.
-You will need to come in to our lab and perform tasks on a computer for an hour or less.
-You will be compensated \$30 for participating.
+We are recruiting participants for an in-person research study at <redacted>. %the University of California, Berkeley. 
+You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
 No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.
@@
 \label{qualitative-prescreening}
-We are recruiting participants for an in-person research study at the University of California, Berkeley.
-You will need to come in to our lab and perform tasks on a computer for an hour or less.
-You will be compensated \$30 for participating.
-No special knowledge and no technical experience is required.\\
+We are recruiting participants for an in-person research study at the <redacted>. %University of California, Berkeley. 
+You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. No special knowledge and no technical experience is required.\\
 
@@
 \item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
-\item{I am able to provide my own transportation to the University of California, Berkeley campus.}
+\item{I am able to provide my own transportation to the <redacted> %University of California, Berkeley 
+campus.}
 \item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
@@
 \label{quantitative-recruitment}
-We are recruiting up to 40 participants for a user study at UC Berkeley.
-The experiment will involve basic Internet browsing tasks.
-You are not eligible if you have participated in our previous sessions.\\
+We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
+The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
 
@@
 \indent Duration: 1 hour \\
-\indent Where: Xlab at Hearst Memorial Gymnasium\\
+\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\
 
@@
 
-If you are interested: 1.
-Email lnl@berkeley.edu with the sessions you are able to attend.
-We will confirm your participation and assign you a session.
-2.
-Come to Xlab at the appointed time for the experiment.
+If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
+with the sessions you are able to attend. We will confirm your participation and assign you a session. 
+2. Come to <redacted> %Xlab 
+at the appointed time for the experiment.
 
@@
 
-This survey is part of a research project being conducted by the University of California, Berkeley.
-If you have any questions about your rights or treatment as a research participant in this study, please contact the University of California at Berkeley's Committee for Protection of Human Subjects at 510-642-7461, or email subjects@berkeley.edu.
+This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
+If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
+Committee for Protection of Human Subjects at 510-642-7461, or email 
+<redacted>. %subjects@berkeley.edu. 
 If you agree to participate, please click Next below.\\
@@
 \section{Custom Bridge Attempts} 
+We provide screenshots of the messages sent to the bridges autoresponder. 
 \label{custom}
@@
 
-\section{All Participant Times}
-\label{all-participant-times}
-Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface.
+%\section{All Participant Times}
+%\label{all-participant-times}
+%Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface.
 These are the raw numbers used to compute values such as the median time spend on each screen.
@@
 For example, observe that P1 and P2 were in the E1-NEW condition and that P1 finished faster than P2.
-
-\begin{table*}
-\input{all-participant-times.tex}
-\caption{
-Times spent on each screen, per participant.
-}
-\label{table:all-participant-times}
-\end{table*}
+%
+%\begin{table*}
+%\input{all-participant-times.tex}
+%\caption{
+%Times spent on each screen, per participant.
+%}
+%\label{table:all-participant-times}
+%\end{table*}
 
@@
 
-Participants that downloaded Tor Browser (5/124): 
-\begin{itemize}
-\item P115 (Fig.~\ref{softsonic})
-\item P116 (Fig.~\ref{techspot})
-\item P117, data not used (Fig.~\ref{mirror})
-\item P118, data not used (Fig.~\ref{downloadio})
-\item P119, data not used (Fig.~\ref{driverupdate})
-\end{itemize}
+5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softsonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).
 

### 2016-05-19 experiment/processing/common.R
Draw boxes for facet strip labels.

@@ -126,5 +126,6 @@ common_theme <- function(p) {
 	p <- p + theme(text=element_text(size=8))
 	p <- p + theme(plot.margin=margin(0,0,0,0,"mm"))
 	p <- p + theme(axis.ticks=element_blank(), axis.ticks.length=unit(0,"lines"))
+	p <- p + theme(strip.background=element_rect(fill="gray90", color=NA))
 	p
 }

### 2016-05-19 experiment/processing/graphs.R
Add a ×=DNF mark to the all-participants-edges legend.

@@ -168,10 +168,12 @@ names(scale.sizes) <- scale.names
 p <- ggplot()
 p <- p + geom_segment(data=edges, lineend="butt", aes(y=userid, yend=userid, x=time_from_start/60, xend=(time_from_start+duration)/60, color=dst, size=dst))
 # p <- p + geom_point(color="black", size=1.5, shape="|")
-p <- p + geom_point(data=participants[is.na(participants$time_to_success), ], aes(y=userid, x=maxtime/60), shape=4)
+p <- p + geom_point(data=participants[is.na(participants$time_to_success), ], aes(y=userid, x=maxtime/60, shape=as.factor(0)))
 p <- p + scale_x_continuous(breaks=pretty_breaks(n=10), limits=c(0, maxtime/60+1), expand=c(0, 0))
-p <- p + scale_size_manual("Current screen", values=scale.sizes, labels=scale.labels)
-p <- p + scale_color_manual("Current screen", values=state.palette, labels=scale.labels)
+p <- p + scale_size_manual(NULL, values=scale.sizes, labels=scale.labels)
+p <- p + scale_color_manual(NULL, values=state.palette, labels=scale.labels)
+p <- p + scale_shape_manual(NULL, values=c(4), labels=c("DNF (did not finish)"))
+p <- p + guides(size=guide_legend(order=1), color=guide_legend(order=1), shape=guide_legend(order=2))
 p <- p + labs(title=NULL, y=NULL, x="Minutes elapsed")
 p <- common_theme(p)
 p <- p + facet_grid(label ~ ., scales="free_y", space="free_y")

### 2016-05-19 pets2017-paper/pets2017-paper.tex
Add a ×=DNF mark to the all-participants-edges legend.
Add missing period.

@@
 \subsection{Setup}
-We ran our experiment at <redacted> 
+We ran our experiment at <redacted>.
 %Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
@@
 The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes
-(marked with a $\times$).
+except for those we cut off after approximately 40 minutes.
 }

### 2016-06-01 pets2017-paper/pets2017-paper.tex
dave's comments: minor typo changes

@@
 Non-finishing participants are assigned the maximum experiment time of 40:08.
-Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$; see Appendix~\ref{stat-tests}).
 The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
@@
 \subsubsection{Active Time} 
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges} and summarize where they spent their time in Appendix~\ref{all-participant-times}.
+We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
+%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
 Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
@@
 Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-Table Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
+Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
 
@@
 
-5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softsonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).
+5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).
 
@@
 \includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{P115 downloaded Tor Browser from Softsonic, a reputable-looking but
+\caption{P115 downloaded Tor Browser from Softonic, a reputable-looking but
 unconfirmed site.}
-\label{softsonic}
+\label{softonic}
 \end{figure}

### 2016-10-14 pets2017-paper/pets2017-paper.tex
delete appendixes J and K

@@
 
-\section{Custom Bridge Attempts} 
-We provide screenshots of the messages sent to the bridges autoresponder. 
-\label{custom}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160325-140813-bridgeresponder-redacted.png}
-\caption{The message that P95 attempted to send to the bridge auto-responder. The message was sent to the wrong address: bridges@bridges.torproject.org instead of bridges@torproject.org.}
-\label{autoresponder1}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/failed-participants/20160328-133857-bridgeresponder-redacted.png}
-\caption{The message that P110 accidentally sent to the helpdesk rather than the bridge auto-responder.
-The participant should have used the address bridges@torproject.org, not help@rt.torproject.org.
-Since the helpdesk address is not an auto-responder, there was no reply.}
-\label{autoresponder2}
-\end{figure}
-
-%\section{All Participant Times}
-%\label{all-participant-times}
-%Table~\ref{table:all-participant-times} shows where each participant spent their time in the interface.
-These are the raw numbers used to compute values such as the median time spend on each screen.
-Participants are grouped by condition.
-Within each condition, participants are ordered in the order of time to success.
-For example, observe that P1 and P2 were in the E1-NEW condition and that P1 finished faster than P2.
-%
-%\begin{table*}
-%\input{all-participant-times.tex}
-%\caption{
-%Times spent on each screen, per participant.
-%}
-%\label{table:all-participant-times}
-%\end{table*}
-
-\section{Tor Downloads}
-\label{tor-downloads}
-
-5 Participants downloaded Tor Browser:  P115 (Fig.~\ref{softonic}), P116 (Fig.~\ref{techspot}), P117, data not used (Fig.~\ref{mirror}), P118, data not used (Fig.~\ref{downloadio}), and P119, data not used (Fig.~\ref{driverupdate}).
-
-%Sources of downloads: 
-%\begin{itemize}
-%\item {\bfseries techspot.com} $\rightarrow$ {\bfseries 1download.io}: an advertisement in the Yahoo search results for ``tor browser downloads''.
-%\item {\bfseries driverupdate.net}: the fifth Google search result for ``tor browser download''.
-%\item {\bfseries www.torservers.net/mirrors}: the first google search result for ``tor browser mirror''.
-%\item {\bfseries techspot.com}: the fifth Google search result for ``tor browser download''.
-%\item {\bfseries softsonic.com}: the second Yahoo search result for ``tor browser''.
-%\end{itemize}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X10-20160323-132505-1downloadio.png}
-\caption{P118 attempted to download Tor Browser from TechSpot.com, but clicked on
-a download link which was not from TechSpot.com. The download was from another site, 1download.io.}
-\label{downloadio}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X28-20160328-134111-driverupdate.png}
-\caption{P119 downloaded Tor Browser from DriverUpdate, a suspicious source. Two executables
-are downloaded, and the website instructs the user to run an executable named ``DriverUpdate-setup.exe,'' which the
-participant dutifully does before running the Tor Browser executable.}
-\label{driverupdate}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/X32-20160328-134531-mirror.png}
-\caption{P117 downloaded Tor Browser from a legitimate Tor Browser mirror, \url{www.torservers.net/mirrors}.}
-\label{mirror}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160323-133257-techspot.png}
-\caption{P116 downloaded Tor Browser from TechSpot, clicking on the download link from 
-TechSpot (the white ``Direct Download'' button). X10-20160323-132505 in Fig.~\ref{downloadio} clicked the blue ``Download Now'' button and downloaded from a different source.}
-\label{techspot}
-\end{figure}
-
-\begin{figure}[h]
-\includegraphics[width=0.5\textwidth]{../experiment/processing/bad-participants/20160330-161511-softsonic.png}
-\caption{P115 downloaded Tor Browser from Softonic, a reputable-looking but
-unconfirmed site.}
-\label{softonic}
-\end{figure}
-
 \end{document}

### 2016-10-14 pets2017-paper/pets2017-rebuttal.txt
(now) unstateful changes from a while ago.

We would like to thank the reviewers for their comments. We now will address each reviewer’s concerns:

7A:
- We will clarify that our experiments may be most applicable to novice Tor users. We expect our participants were adequately motivated to complete the task, due to the Hawthorne effect (i.e., they knew they were being observed completing the tasks). We will acknowledge that we have not studied international users. 
- The success rate improvement is indeed not statistically significant; see Section 8.4.1, sentence 2. We will revise to clarify that our primary contribution is in reducing the time it takes to configure Tor.

7B:
- The purpose of the quantitative study was to evaluate the impact of our proposed changes. A qualitative study can only identify a breadth of potential usability problems, but not their prevalence. 
- We obtained informed consent from all participants, warned them that they were being recorded (see Appendix G), and obtained IRB approval.
- We agree that we need to greatly expand Related Work. We will add discussion of how our findings relate to heuristics in the general usability literature.

7C:
-Our work is unique in that we study previously unexplored concepts (bridges and pluggable transports), and heavily favor minimizing any behaviors that reveal to a passive network eavesdropper that users are connecting to Tor. 
-We will detail what we learned from the pluralistic walkthrough and heuristic evaluation, including how participants behaved (based on the videos) and their responses to the interview questions. We omitted this because the insights largely overlap with what we learned from the other methods.
- We agree that studying real censorship environments would increase external validity; however, it makes it more difficult to eliminate potential confounds, more difficult to characterize the censorship environment, and thus more challenging to assess how results from one location might apply to another.
- Full automation introduces complex ethical and security considerations (see Section 10), not all of which are solely technical. To increase the likelihood that our proposals are adopted by the Tor project, the scope of this work is focused on UI improvements. This scope was informed by discussions with numerous Tor developers.

7D:
-Quotes are based on our notes from the interviews and are not verbatim since we did not record voices (PII). We stopped participants after 45 minutes. 
- We picked wikipedia and CNN because they are 1) websites from the Alexa 100 that 2) do not require personal information , and 3) are commonly blocked by censors. 
- We know the UI was designed with user’s agency in mind based on Tor developers who strongly oppose automating the process (personal conversations; see also https://trac.torproject.org/projects/tor/ticket/10418#comment:18, https://trac.torproject.org/projects/tor/ticket/10538#comment:3, https://lists.torproject.org/pipermail/tor-dev/2015-May/008790.html).
- We will revise the discussion of Related Work to better clarify the relationship to prior work.

We will revise to correct the issues regarding typos, organization, clarity, causal implications, and rephrasing mentioned by 7C and 7D. We believe that most of the issues raised can be fixed with a minor revision/shepherding.

### 2016-10-14 experiment/processing/attempts.R
more stateful changes in r script.

@@ -35,15 +35,6 @@ first_attempts_E2_OLD <-  first_attempts[first_attempts[,"env"]=="E2" & first_at
 first_attempts_E3_NEW <-  first_attempts[first_attempts[,"env"]=="E3" & first_attempts[,"version"]=="NEW",]
 first_attempts_E3_OLD <-  first_attempts[first_attempts[,"env"]=="E3" & first_attempts[,"version"]=="OLD",]
 
-# This is the order to arrange the rows in the output table.
-label.order <- c(
-	"no bridge, no proxy",
-	"obfs3, no proxy",
-	"meek-amazon, no proxy",
-	"meek-google, no proxy",
-	"meek-azure, no proxy",
-	"no bridge, 3rd-party proxy"
-)
 successful.attempts <- attempts[attempts$attempt_successful, ]
 successful.attempts$label <- sprintf("%s, %s",
 	# bridge label
@@ -57,10 +48,6 @@ successful.attempts$label <- sprintf("%s, %s",
 		"3rd-party proxy",
 		"no proxy")
 )
-if (length(unique(successful.attempts$label)) != length(label.order)) {
-	stop(sprintf("something's wrong: we think this table should have %d rows but there are %d", length(label.order), length(unique(successful.attempts$label))))
-}
-successful.attempts$label <- factor(successful.attempts$label, levels=label.order)
 
 # Convert a number to a decimal string, but map 0 to "".
 omitzero <- function(n) {
@@ -72,8 +59,7 @@ df <- as.data.frame(tt)
 
 dnf.tt <- table(participants[!participants$success, c("env", "version")])
 
-sink("attempts-bridge-proxy.tex")
-cat("% Do not edit this file. Edit attempts.R instead.\n")
+cat("\n")
 cat("\\begin{tabular}{r c c c c c c}\n")
 for (env in c("E1", "E2", "E3")) {
 	for (version in c("NEW", "OLD")) {
@@ -81,7 +67,7 @@ for (env in c("E1", "E2", "E3")) {
 	}
 }
 cat(sprintf("\\\\\n"))
-for (label in levels(df$label)) {
+for (label in unique(df$label)) {
 	cat(sprintf("%s ", label))
 	for (env in c("E1", "E2", "E3")) {
 		for (version in c("NEW", "OLD")) {
@@ -98,4 +84,3 @@ for (env in c("E1", "E2", "E3")) {
 }
 cat(sprintf("\\\\\n"))
 cat("\\end{tabular}\n")
-sink()

### 2016-10-14 experiment/processing/info.R

@@ -258,12 +258,6 @@ cat("*********************\n")
     # compares >2 groups of independent measures. 
     # measures must be continuous (success rates, time to success)
 
-# Logistic regression: 
-    # is a classifier (can predict success/fail based on ver, env, pool)
-
-# Linear regression: 
-    # is a model (can predict time to success based on ver, env, pool)
-
 # x is success rate
 success_rates = with(participants, aggregate(success, list(env=env, version=version), pct))
 
@@ -284,6 +278,13 @@ cat("impact of version on active time \n")
 #one-tailed mann-whitney U for right-tailed data, with DNFs = 40:08-time on progress screen.
 wilcox_test(screen_time_per_user$`active_edges$duration` ~ version, data=screen_time_per_user, paired=FALSE, alternative="less")
 
+#one-tailed mann-whiteny U per environment. 
+aaa <- screen_time_per_user[screen_time_per_user[,"env"]== "E1",]
+
+wilcox_test(screen_time_per_user[screen_time_per_user[,"env"]== "E1",]$`active_edges$duration` ~ version, data=screen_time_per_user[screen_time_per_user[,"env"]== "E1",], paired=FALSE, alternative="less")
+wilcox_test(screen_time_per_user[screen_time_per_user[,"env"]== "E2",]$`active_edges$duration` ~ version, data=screen_time_per_user[screen_time_per_user[,"env"]== "E2",], paired=FALSE, alternative="less")
+wilcox_test(screen_time_per_user[screen_time_per_user[,"env"]== "E3",]$`active_edges$duration` ~ version, data=screen_time_per_user[screen_time_per_user[,"env"]== "E3",], paired=FALSE, alternative="less")
+
 cat("\n\n\n\n")
 cat("impact of environment on success rates\n")
 kruskal.test(x ~ env, data=success_rates)
@@ -294,22 +295,6 @@ kruskal.test(time_to_success ~ env, data=clamp_time_to_success(participants, max
 cat("impact of environment on active time \n")
 kruskal.test(screen_time_per_user$`active_edges$duration` ~ env, data=screen_time_per_user)
 
-
-cat("\n\n\n\n")
-cat("logistic regression predicting success by ver, env, pool \n")
-#just env, version, pool, and success columns
-participants_glm_subset <- subset(clamp_time_to_success(participants, maxtime),select=c(5,6,9,10))
[…]

### 2016-10-14 pets2017-paper/pets2017-paper.tex
pass through introduction; de-emphasize censorship, add clairity.

@@
   \begin{abstract}
-{Tor has grown beyond its original purpose as an anonymity tool and has 
-become a widely-used censorship circumvention tool.
-This is the first study to examine Tor's usability in this role.
+{
 We evaluate, design, and test the Tor configuration interface by
 placing users in simulated censorship environments, instructing them to use Tor
-to circumvent censorship, and measuring their interactions with the interface.
-A 16-participant qualitative user study identifies common user struggles while circumventing censorship.
+to circumvent censorship, and measuring their interface interactions.
+A 16-participant qualitative study examines user assumptions and common mistakes.
 We use the results as feedback to redesign the configuration interface.
-A 114-participant quantitative user study tests the impact of our changes.
-We find that our changes result in a significant reduction 
-in the time spent configuring a connections. We
-conclude with recommendations for changes to the current interface as well as 
-alternative approaches to bootstrapping a connection to Tor.}
+A 114-participant quantitative study shows that our design changes result in
+a significant reduction in time. We conclude with recommendations for changes 
+to the current interface as well as alternative solutions.}
 \end{abstract}

### 2016-10-14 pets2017-paper/pets2017-paper.tex
editing pass through introduction.

@@
 {
-We evaluate, design, and test the Tor configuration interface by
+We evaluate, design, and test the Tor Launcher interface by
 placing users in simulated censorship environments, instructing them to use Tor
@@
 
-Tor is an anonymity network that routes traffic through a series of relays
-that make it difficult to observe the source and destination~\cite{dingledine2004tor}.
-Tor's anonymizing functionality also circumvents censorship.
-Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}.
-Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.
-
-This is the first user study that investigates the usability of Tor as a censorship circumvention tool.
-Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier.
-All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool.
-Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
-
-We evaluate, redesign, and test Tor's configuration interface by
-measuring participants' interactions with the interface in various censorship environments.
-The first user study is a small-scale, qualitative experiment that collected 
-behavioral patterns and failure cases with the interface through user observations
-and interviews (Section~\ref{sec:qualitative}). This feedback was used to make changes to the interface (Section~\ref{redesign}). The second user study is a large-scale, quantitative experiment
-that collected data on user interactions with the interface to quantify the impact of the design changes (Section~\ref{sec:quantitative}).
-
-In this paper, we contribute the following:
+Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
+that make it difficult to observe the source and destination. 
+Tor Browser~\cite{torbrowser}, a modified Firefox browser with a built-in Tor client, 
+is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
+starts, stops, and otherwise controls the underlying Tor processes.
+Tor Launcher's graphical user interface asks the user to configure
+bridges, pluggable transports, and proxies to make a connection to Tor (we refer to as the ``configuration interface'' throughout this paper). This is the object of our study.
+
+We start by introducing terms (section~\ref{sec:background}) and, 
+describing the experimental setup (section~\ref{sec:environments}). 
+Then we report of user observations and interviews (section~\ref{sec:qualitative}),
+evaluate the current interface (section~\ref{sec:eval}), 
+list design principles and interface changes (section~\ref{redesign}),
+measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
+testing measured the impact of the design changes (Section~\ref{sec:quantitative}, and
+discuss user behaviors (section~\ref{sec:discussion}).
+We end with limitations (section~\ref{sec:limitations}), 
+related work (section~\ref{sec:related}), 
+future work (section~\ref{sec:future}), and
+a conclusion (section~\ref{sec:conclusion}).
+
+We contribute:
 \smallskip
 \begin{itemize}
-\item 6 common challenges encountered during the configuration process and their underlying causes
-\item 10 changes to the configuration interface which we hope alleviates the common challenges
-\item 114 logs of real world user attempts to connect to Tor in three different censorship environments
-\item 4 reasons why users failed to connect to Tor
-\item 5 recommendations of configuration interface changes to help more users connect and save time
-\item 5 alternative  approaches to bootstrapping a connection that leverage varying degrees of automation
+\item an evaluation of the current configuration interface
+\item a redesigned configuration interface
+\item logs of 114 users' connection attempts
+\item failure modes seen during connection attempts
+\item recommended interface changes
+\item alternative bootstrapping approaches
 \end{itemize}
@@
 \section{Related Work}
+\label{sec:related} 
 There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
@@
 \section{Background}
+\label{sec:background}
 This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.
-
-\subsection{Tor, Tor Browser, and Tor Launcher}
-The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
-a modified Firefox browser that includes a built-in Tor client.
-Tor Browser has a component called Tor Launcher that
-starts, stops, and otherwise controls the underlying Tor processes.
-Tor Launcher's graphical user interface gives access to 
-sophisticated circumvention mechanisms, giving the user
-the option to configure a proxy and bridge before connecting to Tor
-for the first time. This is the object of our study.
-
-In principle, the process of configuring a proxy and bridge can be automated, but
-the interface eschews automatic configuration through network probing
-in favor of guided manual configuration to give users agency in configuring their connection. 
-Automatic configuration through network probing may put some users in certain regimes at risk. 
-A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-However, this requires that the user grapple with technical concepts such as 
-bridges, pluggable transports, and proxies. Some of these concepts are specific to 
-Tor and not general concepts.
 
@@
 
-\subsection{Circumventing Censorship with Tor}
+\subsection{Connecting to Tor}
 There are many valid configuration settings to connect to the Tor network.
@@
 
-\section{Evaluation Criteria and Goals}
-\label{sec:goals}
+\subsection{Potential for good} 
+%Tor's anonymizing functionality also circumvents censorship.
+Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}.
+Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.
+
+%This is the first user study that investigates the usability of Tor as a censorship circumvention tool.
+Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier.
+All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool.
+Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
+
+\section{Evaluation Criteria}
+\label{sec:eval}
 Our user studies evaluated two versions of the Tor Launcher interface.
@@
 \section{Future Work} 
+%In principle, the process of configuring a proxy and bridge can be automated, but
+%the interface eschews automatic configuration through network probing
+%in favor of guided manual configuration to give users agency in configuring their connection. 
+%Automatic configuration through network probing may put some users in certain regimes at risk. 
+%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
+%However, this requires that the user grapple with technical concepts such as 
+%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
+%Tor and not general concepts.
+
 Our goal was to deploy impactful, tested changes the Tor configuration interface.

### 2016-10-14 pets2017-paper/pets2017-paper.tex
reorganize paper.

@@
 Then we report of user observations and interviews (section~\ref{sec:qualitative}),
-evaluate the current interface (section~\ref{sec:eval}), 
 list design principles and interface changes (section~\ref{redesign}),
+state evaluation criteria for gauging the succcessfulness of an interface (section~\ref{sec:eval}), 
 measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
@@
 
-We contribute:
+This paper contributes:
 \smallskip
@@
 We hope that our work helps users circumvent censorship and connect to Tor.
-
-\section{Related Work}
-\label{sec:related} 
-There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
-options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
-latency~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests, and prevents user adoption. 
-Norcie et~al.~\cite{norcie2012eliminating} found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties.
-
-We do not know of any published usability evaluations of
-Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
-that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
-some of which influenced changes in Tor Browser version~4.5 and later.
-
-Previous user studies have considered the whole browsing experience,
-without focusing on specific features in isolation.
-Our study focuses on 
-the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
 
@@
 
-\section{Evaluation Criteria}
-\label{sec:eval}
-Our user studies evaluated two versions of the Tor Launcher interface.
-The first, which we have labeled OLD in our figures and tables,
-is the current version being distributed with Tor Browser.
-The second, NEW, is the prototype that we designed
-in order to provide better usability. Below are the empirical and 
-heuristic evaluation criteria we use to assess the interfaces.
-
-Our empirical evaluation criteria for the Tor Browser configuration
-interface are based on common metrics that measure ease of use: \\
-
-\begin{enumerate}
-    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition.
-This measures how many users are able to configure their connections with the interface.
-    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-This measures how much time is required for a user to connect to the Tor network.
-    \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
-\end{enumerate}
-
-An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
-A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface.
-For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
-
 \section{Experimental Setup}
@@
 
+\section{Evaluation Criteria}
+\label{sec:eval}
+Our user studies evaluated two versions of the Tor Launcher interface.
+The first, which we have labeled OLD in our figures and tables,
+is the current version being distributed with Tor Browser.
+The second, NEW, is the prototype that we designed
+in order to provide better usability. Below are the empirical and 
+heuristic evaluation criteria we use to assess the interfaces.
+
+Our empirical evaluation criteria for the Tor Browser configuration
+interface are based on common metrics that measure ease of use: \\
+
+\begin{enumerate}
+    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition.
+This measures how many users are able to configure their connections with the interface.
+    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
+This measures how much time is required for a user to connect to the Tor network.
+    \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
+\end{enumerate}
+
+An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
+A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface.
+For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
+
 \section{Quantitative Analyses of the Interfaces (Study 2)}
@@
 We tested the English version of the Tor interface on English speaking participants.
+
+\section{Related Work}
+\label{sec:related} 
+There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
+options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
+latency~\cite{dingledine2009performance} causes users
+to be frustrated, cancel requests, and prevents user adoption. 
+Norcie et~al.~\cite{norcie2012eliminating} found found that 
+64\% of users are unable to continue with installation or browsing at least once due to difficulties.
+
+We do not know of any published usability evaluations of
+Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
+The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
+that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
+some of which influenced changes in Tor Browser version~4.5 and later.
+
+Previous user studies have considered the whole browsing experience,
+without focusing on specific features in isolation.
+Our study focuses on 
+the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
 

### 2016-10-17 pets2017-paper/pets2017-paper.tex
shuffle sections and reword headings.
scrap the title.
another pass through the introduction.

--- 2016-10-14 pets2017-paper/pets2017-paper.tex
@@
 
-  \title{\huge Tor's Usability for Censorship Circumvention}
-  %Internet Freedom Made Easy: On Improving Tor’s Usability for Censorship Circumvention
-  %Towards Usable Censorship Circumvention
-
-  \runningtitle{Tor's Usability for Censorship Circumvention}
+  \title{\huge A Better (One-Line!) Title Here}
+
+  \runningtitle{Ugh!}
 
@@
 that make it difficult to observe the source and destination. 
-Tor Browser~\cite{torbrowser}, a modified Firefox browser with a built-in Tor client, 
+Tor Browser~\cite{torbrowser} is a modified Firefox browser with a built-in Tor client that
 is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
@@
 Tor Launcher's graphical user interface asks the user to configure
-bridges, pluggable transports, and proxies to make a connection to Tor (we refer to as the ``configuration interface'' throughout this paper). This is the object of our study.
-
-We start by introducing terms (section~\ref{sec:background}) and, 
-describing the experimental setup (section~\ref{sec:environments}). 
-Then we report of user observations and interviews (section~\ref{sec:qualitative}),
-evaluate the current interface (section~\ref{sec:eval}), 
-list design principles and interface changes (section~\ref{redesign}),
-measure the impact of changes in the quantitative experiment in section~\ref{sec:quantitative}, 
-testing measured the impact of the design changes (Section~\ref{sec:quantitative}, and
-discuss user behaviors (section~\ref{sec:discussion}).
-We end with limitations (section~\ref{sec:limitations}), 
-related work (section~\ref{sec:related}), 
-future work (section~\ref{sec:future}), and
-a conclusion (section~\ref{sec:conclusion}).
-
-We contribute:
+bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper).
+This is the object of our study.
+
+We hope that our work helps users more easily connect to Tor.
+The direct and obvious benefit of our work is that is that it may help users who would have previously been unable to configure Tor Browser to use it or that it may save time for users who would have been able to configure a valid connection to the Tor.
+Improving the user experience through user testing has the potential to be beneficial for both the software company (less help desk tickets) and the end users (less frustration).
+
+However, we believe that our work uniquely necesssary and beneficial to Tor Browser.
+Although originally designed for Internet anonymity, using Tor Browser to circumvent censorship has now become sufficiently common that many countries now attempt to block Tor relays for this reason~\cite{winter2012great}.
+Our experiment to design an easier bootstrapping process will especially benefit citizens who face Internet censorship.
+If successful, an increase in overall users means more than user growth, but an increased anonymity set~\cite{dingledine2006anonymity}.
+\\
+
+\noindent This paper contributes:
 \smallskip
@@
 \end{itemize}
-We hope that our work helps users circumvent censorship and connect to Tor.
-
-\section{Related Work}
-\label{sec:related} 
-There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
-options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
-latency~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests, and prevents user adoption. 
-Norcie et~al.~\cite{norcie2012eliminating} found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties.
-
-We do not know of any published usability evaluations of
-Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
-that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
-some of which influenced changes in Tor Browser version~4.5 and later.
-
-Previous user studies have considered the whole browsing experience,
-without focusing on specific features in isolation.
-Our study focuses on 
-the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
+
+We start by introducing relevant concepts (section~\ref{sec:background}) and
+defining the scope of our experiment (section~\ref{sec:scope}). 
+Then, we report user observations and interviews (section~\ref{sec:qualitative}),
+list design principles and interface changes (section~\ref{redesign}),
+state evaluation criteria for testing the interface (section~\ref{sec:eval}), 
+and measure the impact of our design changes (Section~\ref{sec:quantitative}).
+We end with a discussion on what we learned (section~\ref{sec:discussion}),
+limitations of out experiment (section~\ref{sec:limitations}), 
+a look at our work in the context of existing work (section~\ref{sec:related}), and
+a brief conclusion (section~\ref{sec:conclusion}).
+
+%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
 
@@
     \includegraphics[width=0.5\textwidth]{bridge-options.png}
-%\small
-%\begin{itemize}
-%\renewcommand{\labelitemi}{$\circ$}
-%\item Connect with provided bridges\\
-%Transport type:
-%\begin{itemize}
-%\item flashproxy
-%\item fte
-%\item fte-ipv6
-%\item meek-amazon
-%\item meek-azure
-%\item meek-google
-%\item obfs3 (recommended)
-%\item obfs4
-%\item scramblesuit
-%\end{itemize}
-%\item Enter custom bridges\qquad\fbox{Help}\\
-%\end{itemize}
 \caption{
@@
 
-\subsection{Potential for good} 
+\subsection{Motivation} 
 %Tor's anonymizing functionality also circumvents censorship.
@@
 
-\section{Evaluation Criteria}
-\label{sec:eval}
-Our user studies evaluated two versions of the Tor Launcher interface.
-The first, which we have labeled OLD in our figures and tables,
-is the current version being distributed with Tor Browser.
-The second, NEW, is the prototype that we designed
-in order to provide better usability. Below are the empirical and 
-heuristic evaluation criteria we use to assess the interfaces.
-
-Our empirical evaluation criteria for the Tor Browser configuration
-interface are based on common metrics that measure ease of use: \\
-
-\begin{enumerate}
-    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition.
-This measures how many users are able to configure their connections with the interface.
-    \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-This measures how much time is required for a user to connect to the Tor network.
-    \item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
-\end{enumerate}
-
-An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
-A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface.
-For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
-
-\section{Experimental Setup}
-\label{sec:environments}
+\section{Scope}
+\label{sec:scope}
+%insert explanation into why we did what we did here.
+
 For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
@@
 
-\subsection{Discussion} 
+\section{Discussion} 
+\label{sec:discussion}
 We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.
@@
 \section{Limitations}
+\label{sec:limitations}
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
@@
 
-\section{Future Work} 
+\section{Related Work}
+\label{sec:related} 
+There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
+options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
+latency~\cite{dingledine2009performance} causes users
+to be frustrated, cancel requests, and prevents user adoption. 
+Norcie et~al.~\cite{norcie2012eliminating} found found that 
+64\% of users are unable to continue with installation or browsing at least once due to difficulties.
+
+We do not know of any published usability evaluations of
+Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
+The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
+that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
+some of which influenced changes in Tor Browser version~4.5 and later.
+
+Previous user studies have considered the whole browsing experience,
+without focusing on specific features in isolation.
+Our study focuses on 
+the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
+
+\section{Conclusion} 
+\label{sec:conclusion}
+We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
+Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity.
+Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works.
+We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.
+
+%general advice to other censorship circumvention and call for more research 
+Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
+When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g.
+pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components.
+We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
+Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
+
+%\section {Resources} 
+%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
+%
+%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
+%
+%\section {Acknowledgments}
+% Rowilma del Castillo of Xlab supported out experiment by assisting with testing, offering recruitment services, and allowing experiments after-hours.
+Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team have provided me with valuable feedback along the way.
+
+\bibliographystyle{abbrv}
+\bibliography{pets2017-paper}
+
+\appendix
+\section{Alternative Approaches} 
 %In principle, the process of configuring a proxy and bridge can be automated, but
@@
 We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process.
-
-\section{Conclusion} 
-We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
-Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity.
-Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works.
-We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.
-
-%general advice to other censorship circumvention and call for more research 
-Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
-When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g.
-pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components.
-We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
-Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
-
-%\section {Resources} 
-%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
-%
-%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
-%
-%\section {Acknowledgments}
-%I want to especially thank Rowilma del Castillo of Xlab for supporting the experiment, assisting with testing, and being flexible with non-Xlab recruiting.
-I have received much valuable feedback from Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team.
-
-\bibliographystyle{abbrv}
-\bibliography{pets2017-paper}
-
-\appendix
 

### 2016-10-17 pets2017-paper/pets2017-paper.tex
reorganize background section.

@@
 \label{sec:background}
-This section provides the necessary background the configuration interface relates to Tor, the network components that are involved in censorship circumvention, and the configuration settings are required to bypass levels of Tor-adverse censorship environments.
+This section talks about network components involved in connecting to Tor, network conditions that require these network components, and examples of what users must currently do to connect to Tor.
 
@@
 
-\subsection{Connecting to Tor}
+\subsection{Light, Heavy, and Corporate Censorship}
+
+\subsection{Connections to Tor}
+
 There are many valid configuration settings to connect to the Tor network.
@@
 configure a custom bridge to connect to Tor.
-
-\subsection{Motivation} 
-%Tor's anonymizing functionality also circumvents censorship.
-Using Tor for censorship circumvention became sufficiently common that many countries attempt to block Tor for this reason~\cite{winter2012great}.
-Today, Tor explicitly provides support for censorship circumvention through a network of unlisted relays as entry points into the Tor network, various methods of obfuscation to make connections to the Tor network less obvious, and advanced techniques to resist blocking.
-
-%This is the first user study that investigates the usability of Tor as a censorship circumvention tool.
-Our experiments are both a case study observing users circumvent censorship and a step toward helping current Tor users by making censorship circumvention easier.
-All Tor users benefit from improving the configuration interface, and thereby increasing the adoption of Tor as a censorship circumvention tool.
-Users who successfully use Tor to circumvent censorship are provided with extra security features that other censorship circumvention tools do not provide, while users who use Tor as an anonymity system benefit from an increased number of overall users on the Tor network~\cite{dingledine2006anonymity}.
 

### 2016-10-17 pets2017-paper/pets2017-paper.tex
pass through network components background subsection.

@@
 
-%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
-
 \section{Background}
@@
 
-\subsection{Bridges, Pluggable Transports, and Proxies} 
-Internet censors seek to block network resources through 
-a variety of means, such as falsifying DNS responses, blocking IP addresses, 
-filtering keywords, and detecting protocols by deep packet inspection.
-Censors can block the Tor network by blocking the list of Tor relays, which 
-are public. Blocking Tor becomes challenging when
-the Tor network is augmented with \emph{bridges} and \emph{pluggable transports}.
+%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
+
+\subsection{Relays, Bridges, Pluggable Transports, and Proxies}
+
+Tor relays are routers in the Tor Network that receive and pass along Tor traffic. 
+There are three types of Tor relays: guard relays that serve as an entry node, middle relays that forward traffic from an entry node to an exit node, and exit relays which directs traffic to the destination.
+Censors can block access to the Tor network by blocking these relays, which are publicly listed.
+
+Bridges are unlisted Tor relays that can serve as the entry node to the Tor network.
+Bridges can be simple, unlisted relays. 
+But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand), protocols that obfuscates Tor's network protocol. 
+Most transports obfuscate traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
+These include ``fte'' and ``fte-ipv6''~\cite{fte},
+which disguise the Tor protocol as another protocol (such as HTTP), and
+``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
+which encrypt or alter the Tor protocol to appear as random noise.
+Some transports route traffic through other services to obfuscate the traffic, avoiding the need for a secret IP address. 
+``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
+and the ``meek''~\cite{fifield2015blocking} options route traffic
+through content delivery networks.
+Bridges and transports make it possible to connect to the Tor network even if a censor has blocked all publicly listed relays and are blocking any packets that look like the Tor network protocols.
+Fig.~\ref{fig:bridge-options} paraphrases the bridge and pluggable transport options at the time of the study.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.5\textwidth]{bridge-options.png}
+\caption{
+Bridge options in Tor Browser~5.0.3's Tor Launcher interface.
+Pre-configured bridges can be selected by ``Transport type,'' which refer to various
+censorship circumvention technologies (``pluggable transports'').
+%Under ``Enter custom bridges,'' there is a space to paste in
+%a bridge line, obtained out of band.
+%The ``Help'' button displays instructions on obtaining
+%bridge lines. 
+}
+\label{fig:bridge-options}
+\end{figure}
+
+In addition to Tor-specific components, a local proxy may be necessary to connect 
+outside the local network in managed environments, such as corporate or university networks.
+(Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
 Fig.~\ref{fig:topology} illustrates the interacting components.
@@
 Most users do not need a proxy;
-similarly only those users who face a censor need a bridge.
+only users who face a censor need a bridge.
 In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
@@
 because of the special role it plays.
-When a bridge is used, it takes the place of the first Tor hop.
+When a bridge is used, it becomes the first Tor relay.
 }
@@
 \end{figure}
-
-Bridges are unlisted Tor relays that make it possible for a user to connect
-to the Tor network even if a censor blocks all publicly listed Tor relays.
-Pluggable transports are special protocols that run on bridges and obfuscate
-Tor's network protocol to make it difficult to detect. 
-Configuring a bridge requires providing one or more
-``bridge lines,'' a specification of a bridge that
-includes its IP address, transport type, and other metadata.
-For ease of use, the interface has hard-coded options for 
-the user to choose a group of bridges that use a particular
-pluggable transport. For example, choosing  the hard-coded obfs3 option
-configures a handful of bridges that use obfs3 pluggable transport.
-Some censors block the IP addresses of the hard-coded bridges by looking
-at the source code for those addresses (except flashproxy and meek).
-If the built-in bridges do not work, a user can obtain bridge lines
-through out-of-band channels, for instance by email~\cite{bridgedb}.
-Fig.~\ref{fig:bridge-options} paraphrases the bridge configuration
-options at the time of the study and lists the available pluggable transports.
-%Some transports connect directly to a static IP address,
-%obfuscating traffic to defeat on-the-wire identification;
-%they rely on the secrecy of their IP addresses for their effectiveness.
-%These include ``fte'' and ``fte-ipv6''~\cite{fte},
-%which make Tor look like another protocol such as HTTP; and
-%``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
-%which encrypt Tor to look like random noise.
-%Other transports work differently and do not depend on connecting to a static IP address:
-%``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
-%and the three ``meek''~\cite{fifield2015blocking} options route traffic
-%through content delivery networks.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.5\textwidth]{bridge-options.png}
-\caption{
-Bridge selection options in Tor Launcher for Tor Browser~5.0.3.
-Users are not familiar with the options under ``Transport type,'' which are various
-built-in circumvention technologies (``pluggable transports'').
-Under ``Enter custom bridges,'' there is a space to paste in
-a bridge line, obtained out of band.
-The ``Help'' button displays instructions on obtaining
-bridge lines. 
-}
-\label{fig:bridge-options}
-\end{figure}
-
-In addition to Tor-specific components, a proxy may be necessary to connect 
-outside the local network in certain managed environments, such as corporate or university networks.
-Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
-fields. There is no assistance or automation with this process. The user must locate the 
-proxy information and correctly input this information.
-
-%Technically the Tor client, pluggable transport bridge, and proxy are all
-%proxies. In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such
-%as a SOCKS or HTTP proxy. An important distinction is that the local proxy lies within the 
-%censor's control.
 
@@
 configure a custom bridge to connect to Tor.
+
+%Configuring a bridge requires providing one or more
+%``bridge lines,'' a specification of a bridge that
+%includes its IP address, transport type, and other metadata.
+%For ease of use, the interface has hard-coded options for 
+%the user to choose a group of bridges that use a particular
+%pluggable transport. For example, choosing  the hard-coded obfs3 option
+%configures a handful of bridges that use obfs3 pluggable transport.
+%Some censors block the IP addresses of the hard-coded bridges by looking
+%at the source code for those addresses (except flashproxy and meek).
+%If the built-in bridges do not work, a user can obtain bridge lines
+%through out-of-band channels, for instance by email~\cite{bridgedb}.
+
+%Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields.
+There is no assistance or automation with this process.
+The user must locate the  proxy information and correctly input this information.
 

### 2016-10-17 pets2017-paper/pets2017-paper.tex
made running title match temp title
finshed pass through background section.

@@
 
-  \runningtitle{Ugh!}
+  \runningtitle{A Better (One-Line!) Title Here}
 
@@
 Although originally designed for Internet anonymity, using Tor Browser to circumvent censorship has now become sufficiently common that many countries now attempt to block Tor relays for this reason~\cite{winter2012great}.
-Our experiment to design an easier bootstrapping process will especially benefit citizens who face Internet censorship.
-If successful, an increase in overall users means more than user growth, but an increased anonymity set~\cite{dingledine2006anonymity}.
+Our contributions toward an easier bootstrapping process will especially benefit citizens who face Internet censorship.
+If there is an increase in overall users as a result, they add a security bonus by increasing the anonymity set~\cite{dingledine2006anonymity}.
 \\
@@
 
-%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
-
 \subsection{Relays, Bridges, Pluggable Transports, and Proxies}
@@
 
-Bridges are unlisted Tor relays that can serve as the entry node to the Tor network.
+Bridges are unlisted Tor relays that can serve as an alternative entry node.
 Bridges can be simple, unlisted relays. 
-But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand), protocols that obfuscates Tor's network protocol. 
-Most transports obfuscate traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
+But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates the traffic. 
+Most transports disguise traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
 These include ``fte'' and ``fte-ipv6''~\cite{fte},
@@
 which encrypt or alter the Tor protocol to appear as random noise.
-Some transports route traffic through other services to obfuscate the traffic, avoiding the need for a secret IP address. 
+Some transports route traffic through other services, avoiding the need for a secret IP address. 
 ``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
@@
 through content delivery networks.
-Bridges and transports make it possible to connect to the Tor network even if a censor has blocked all publicly listed relays and are blocking any packets that look like the Tor network protocols.
-Fig.~\ref{fig:bridge-options} paraphrases the bridge and pluggable transport options at the time of the study.
+Bridges and transports allow a connection to the Tor network when all publicly listed relays and any Tor-looking packets are blocked.
+Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.
 
@@
 
-In addition to Tor-specific components, a local proxy may be necessary to connect 
-outside the local network in managed environments, such as corporate or university networks.
+In addition to Tor-specific components, a local proxy is required to connect 
+in certain managed networks.
 (Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
@@
 
-\subsection{Light, Heavy, and Corporate Censorship}
-
-\subsection{Connections to Tor}
+\subsection{State and Corporate Censorship}
+State level censors can vary in their thoroughness in censorship, resulting in a variety of ever-changing network conditions.
+Some DNS-poison websites they want to block, while others that employ more sophisticated techniques, such as deep packet inspection and protocol detection.
+In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship.
+In other countries, sophisticated state-level censorship require bridges that run specific tranports that route traffic through other, non-Tor services first.
+For example, only meek-amazon and meek-azure transports work to bypass China's GFW.
+
+Some companies and educational institutions have a firewall, which can be bypassed by a proxy (with or without Tor).
+The users behind a corporate firewall represent a very small fraction of censored users.
+
+\subsection{Connecting to Tor}
+
+%\begin{itemize}
+%	\item{Whether their Internet connection is censored} 
+%	\item{Whether the Tor network is censored by their ISP}
+%	\item{Which hard-coded bridges work in their country} 
+%	\item{If no hard-coded bridges work, how to get a custom bridge and connect to it} 
+%	\item{Whether a proxy is required to access the Internet}
+%	\item{If a proxy is required, and if so, the proxy settings}
+%\end{itemize}
+
+Configuring a bridge requires providing one or more
+``bridge lines,'' a specifically formatted bridge specification that
+includes its IP address, transport type, and other metadata.
+The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
+that select a group of bridges that use a particular transport.
+For instance, choosing the hard-coded obfs3 option
+configures a handful of bridges that use obfs3 transport.
+If the built-in bridges do not work, a user can obtain bridge lines
+through out-of-band channels, for instance by email~\cite{bridgedb}.
+
+Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields. The user must locate and input this information.
 
 There are many valid configuration settings to connect to the Tor network.
-For instance, a user who does not need a bridge or proxy 
-can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
-The minimum amount of configuration required, therefore, the set of valid configuration settings,
-vary depending on the censorship environment. In the worst case, users must know or find out:\\
-
-\begin{itemize}
-	\item{Whether their Internet connection is censored} 
-	\item{Whether the Tor network is censored by their ISP}
-	\item{Which hard-coded bridges work in their country} 
-	\item{If no hard-coded bridges work, how to get custom bridge information and connect to it} 
-	\item{Whether a proxy is required to access the Internet}
-	\item{If a proxy is required, and if so, the proxy settings}
-\end{itemize}
-
-Uncensored users and users in censorship environments that do not explicitly 
-block Tor do not require a bridge or a proxy and can bypass these steps in the configuration process.
-Users in censorship environments that explicitly block Tor but have not blocked the 
-hard-coded bridges in the Tor Launcher source code are required to use a 
-hard-coded bridge or custom bridge to connect to Tor. Users in a censorship environment that has explicitly 
-blocked Tor relays and hard-coded bridges are required to configure a meek bridge (which 
-routes traffic through content delivery networks and therefore resists blocking through collateral damage) or 
-configure a custom bridge to connect to Tor.
-
-%Configuring a bridge requires providing one or more
-%``bridge lines,'' a specification of a bridge that
-%includes its IP address, transport type, and other metadata.
-%For ease of use, the interface has hard-coded options for 
-%the user to choose a group of bridges that use a particular
-%pluggable transport. For example, choosing  the hard-coded obfs3 option
-%configures a handful of bridges that use obfs3 pluggable transport.
-%Some censors block the IP addresses of the hard-coded bridges by looking
-%at the source code for those addresses (except flashproxy and meek).
-%If the built-in bridges do not work, a user can obtain bridge lines
-%through out-of-band channels, for instance by email~\cite{bridgedb}.
-
-%Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields.
-There is no assistance or automation with this process.
-The user must locate the  proxy information and correctly input this information.
+For instance, a user who needs a bridge but not need a proxy can connect to Tor with a bridge and proxy, provided that both were configured correctly.
+The set of valid configuration settings vary on the censorship environment.
+
+%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
 
@@
 confounding factors.
+
+Because proxies are not Tor-specific concept and affects a small fraction of the Internet population, we study connections to Tor that require a bridge but not a proxy.
+We focus our attention on the parts of the configuration interface that set up bridges and simulate environments that do not need a proxy.
+However, connections to Tor are still considered valid in the experiment.
 
@@
 \item [E1: Mild censorship.]
-(Representative of countries such as France and Australia.)
 The E1 environment only blocks some websites,
@@
 \item [E2: Intermediate censorship.]
-(Representative of countries such as Tunisia.)
 The E2 environment blocks websites as in E1 and
@@
 \item [E3: Comprehensive censorship.]
-(Representative of countries such as China and Syria.)
 The E3 environment blocks websites and Tor relays like E1 and E2
@@
 E1 only requires participants to click ``Connect'';
-E2 requires selection of a built-in bridge;
-and E3 requires selection of a specific type of built-in bridge,
+E2 requires a built-in bridge;
+and E3 requires a specific type of built-in bridge
 or manual configuration of a custom bridge.

### 2016-10-17 pets2017-paper/pets2017-paper.tex
nitpicking tweaks throughout background section.

@@
 in certain managed networks.
-(Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
-Fig.~\ref{fig:topology} illustrates the interacting components.
+In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
+(Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) Fig.~\ref{fig:topology} illustrates the interacting components.
 
@@
 State level censors can vary in their thoroughness in censorship, resulting in a variety of ever-changing network conditions.
-Some DNS-poison websites they want to block, while others that employ more sophisticated techniques, such as deep packet inspection and protocol detection.
+Some block websites with a combination of IP blacklisting and DNS-poisoning while others that employ more sophisticated techniques such as deep packet inspection and protocol detection.
 In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship.
@@
 
-Some companies and educational institutions have a firewall, which can be bypassed by a proxy (with or without Tor).
-The users behind a corporate firewall represent a very small fraction of censored users.
+Some companies and educational institutions have a firewall, which can be bypassed with a proxy (with or without a connection to Tor).
 
@@
 For instance, a user who needs a bridge but not need a proxy can connect to Tor with a bridge and proxy, provided that both were configured correctly.
-The set of valid configuration settings vary on the censorship environment.
+The set of valid configuration settings vary on the specific network environment.
 

### 2016-10-17 pets2017-paper/pets2017-paper.tex
pass through experimental setup

@@
 
-%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
-
-\section{Scope}
-\label{sec:scope}
-%insert explanation into why we did what we did here.
+\section{Experimental Setup}
+We simulated three environments (which we refer to as E1, E2, and E3), 
+which are in the order of increasing severity in censorship. We chose to 
+simulate environments for the stability, reproducibility, and simplicity of the 
+experiment, as real censored networks are voilatile, subject to change, and complex.
+
+The simulated environments are not intended to imitate any particular country's censorship environment. However, they were designed so that they would require similar configurations
+to make a connection to Tor.
+For instance, E3 does not block the same websites, public Tor relays, or Tor protocols that China would, but similarly requires a bridge that runs a specific type of transport to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we want to test.
+Table~\ref{tab:environments} summarizes our
+environments and what network components are required to make a 
+connection to Tor.
+
+We used features of the Windows operating system 
+to block websites and Tor relays. 
+We added entries to the hosts file to
+mapping domain names to the address 127.0.0.1, which simulated
+website by using Tor.
+We blocked torproject.org and its respective subdomains to discourage downloading Tor Browser, as we had installed an instrumented version on the test computers (E1, E2, E3).
+We blocked wikipedia.org, cnn.com, and their respective subdomains to create an artificial task to visit a
+``censored'' website as motivation to connect to Tor during the experiment (E1, E2, E3). 
+We specified Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3).
 
@@
 
-Because proxies are not Tor-specific concept and affects a small fraction of the Internet population, we study connections to Tor that require a bridge but not a proxy.
-We focus our attention on the parts of the configuration interface that set up bridges and simulate environments that do not need a proxy.
-However, connections to Tor are still considered valid in the experiment.
-
-For both user studies, we simulated three censorship environments,
-which we refer to as E1, E2, and E3, which are in  the order of increasing severity.
-We designed the environments to be representative
-of what, in our estimation, are important real-world
-cases of censorship. They are not intended to imitate
-any particular country's censorship environment.\\
-
-\begin{description}
-\item [E1: Mild censorship.]
-The E1 environment only blocks some websites,
-as if by DNS poisoning.
-We blocked subdomains of torproject.org
-and wikipedia.org.
-(The participants' main goal in the experiment was to read a page on en.wikipedia.org.)
-To succeed in this environment,
-participants only had to click ``Connect'' on the first screen;
-additional configuration was optional.
-
-\item [E2: Intermediate censorship.]
-The E2 environment blocks websites as in E1 and
-additionally blocks IP addresses of public Tor relays
-and directory authorities, simulating a censor who knows
-about circumvention and tries to stop it.
-In this environment, simply clicking ``Connect'' does not work;
-participants had to select a built-in bridge
-(any type other than ``flashproxy'' would work).
-A custom bridge would work but was not necessary.
-
-\item [E3: Comprehensive censorship.]
-The E3 environment blocks websites and Tor relays like E1 and E2
-and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
-To succeed in this environment, participants had to select
-one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
-or acquire their own custom bridge and enter it manually.
-\end{description}
-
-\smallskip
-
-Table~\ref{tab:environments} summarizes our simulated censorship
-environments. We used features of the Windows operating system 
-to implement the above blocking behaviors.
-To simulate website blocking, we added entries to the hosts file,
-mapping domain names to the address 127.0.0.1.
-We used Windows Firewall rules for IP address blocking.
-
-\begin{table}
+\begin{table}[t]
 \centering
@@
 \end{table}
+
+%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
 

### 2016-10-18 pets2017-paper/pets2017-paper.tex
add inspection section, reword titles, mark TODO red.

@@
 
+%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
+\section{Usability Inspection}
+{\color {red}
+We used a combination of usability inspection methods~\cite{nielsen1994usability}
+to prepare for the user study. Two researchers conducted a pluralistic 
+walkthrough and stepped through various censorship
+scenarios, discussing which elements would be involved for that use case, and walking 
+through the configuration process. After compiling all the possible paths through the 
+interface, researchers performed feature inspection, listing sequences of features used 
+to accomplish typical tasks and taking note of long sequences or cumbersome
+steps. In addition, we performed a heuristic evaluation to mark
+likely causes of confusion for users during our study.
+}
+
 \section{Experimental Setup}
@@
 
-\subsection{Inspection}
-We used a combination of usability inspection methods~\cite{nielsen1994usability}
-to prepare for the user study. Two researchers conducted a pluralistic 
-walkthrough and stepped through various censorship
-scenarios, discussing which elements would be involved for that use case, and walking 
-through the configuration process. After compiling all the possible paths through the 
-interface, researchers performed feature inspection, listing sequences of features used 
-to accomplish typical tasks and taking note of long sequences or cumbersome
-steps. In addition, we performed a heuristic evaluation to mark
-likely causes of confusion for users during our study.
-
 \subsection{Recruitment}
@@
 
-\section{Redesigning the Configuration Interface}
+%for color red
+}
+
+\section{Design Principles and Changes}
+\label{redesign} 
+{\color {red}
 We make ten changes to the Tor launcher configuration interface to help users connect to Tor.
@@
 Specifically, the following three changes were made to give users more information in during configuration: \\
-
-\label{redesign}
 
@@
 Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.
-
-\section{Evaluation Criteria}
+%for color red
+}
+
+\section{Evaluation Method and Criteria}
 \label{sec:eval}
+{\color {red} 
 Our user studies evaluated two versions of the Tor Launcher interface.
@@
 For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
-
-\section{Quantitative Analyses of the Interfaces (Study 2)}
+%for color red
+}
+
+\section{Quantitative User Testing}
 \label{sec:quantitative}
+
+{\color {red} 
 Having identified problems with the existing interface
@@
 Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
+%for color red
+}
 
@@
 \label{sec:discussion}
+
+{\color {red} 
 We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.
@@
 
+%for color red
+}
+
 \subsubsection{Recommendations}
 \label{recommendations}
+{\color {red} 
 Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\
@@
 Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.
+%for color red
+}
 
@@
 \label{sec:limitations}
+{\color {red} 
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
@@
 
+%for color red
+}
+
 \section{Related Work}
 \label{sec:related}
+
+{\color {red} 
 There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
@@
 the browser's configuration interface, which guides users through setting up components required to circumvent censorship. 
+%for color red
+}
 
@@
 \label{sec:conclusion}
+
+{\color {red} 
 We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
@@
 
+%for color red
+}
+
 %\section {Resources} 
@@
 \section{Alternative Approaches} 
+{\color {red} 
 %In principle, the process of configuring a proxy and bridge can be automated, but
@@
 We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process. 
+%for color red
+}
 
@@
 \label{stat-tests}
+{\color {red} 
 From our measurements, we observe that participants with the new interface 
@@
 We find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+%for color red
+}
 

### 2016-10-18 pets2017-paper/pets2017-paper.tex
reorganized sections, re-outlined what to say (blue). text in red is to be revised.

@@
 
-%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%		LINDA'S PASS UP TO HERE 		       %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \section{Usability Inspection}
@@
 
-%%%%%% LINDA'S PASS UP TO HERE %%%%%%%%%
-
-\section{Qualitative Analysis of the Existing Interface (Study 1)}
+\section{Qualitative User Testing}
+{\color {red}
 \label{sec:qualitative}
-
 We ran a qualitative, exploratory user study to gain an 
@@
 \label{redesign}
-{\color {red}
-We make ten changes to the Tor launcher configuration interface to help users connect to Tor.
-Since users did not know how to connect to Tor, we added advice where our users have previously struggled.
-Specifically, the following three changes were made to give users more information in during configuration: \\
-
- \begin{figure*}[t]
-	\centering
-		\includegraphics[width=.8\textwidth]{bridge-screens.pdf} 
-		\caption{In the OLD interface, users are asked, ``Does your Internet Service Provide (ISP) block or 
-		otherwise censor connections to the Tor Network?'' (B1). A ``Yes'' determines that a bridge should 
-		be configured and directs to the bridge configuration screen (B2). 
-		The NEW interface gives users advice on configuring bridges
-		while giving the option of not configuring a bridge, on one screen (B).} 
-\end{figure*}
-
-\begin{figure*}[t]
-	\centering
-		\includegraphics[width=.8\textwidth]{proxy-screens.pdf} 
-		\caption{In the OLD interface, users are asked, ``Does this computer need a local proxy to connect
-		to the Internet?'' (P1). A ``Yes'' determines that a proxy should be configured and directs to the 
-		proxy configuration screen (P2). The NEW interface checks the local machine's proxy settings,
-		and informs the user whether a proxy is required, and if so, what those settings are (P).}
-\end{figure*}
-
-\begin{figure*}[t]
-\centering
-\includegraphics[width=.85\textwidth]{old-and-new-flows.png}
-\caption{
-Comparison of user flow in the OLD and NEW interfaces.
-We collapsed the two bridge screens into one 
-and also collapsed the two proxy screens into one.
-We swapped the order of the bridge and proxy configuration
-so it matches the order of network components (compare with Fig.~\ref{fig:topology}).
-We added a summary screen as a last step before initiating a connection.\\
-\textbf{F}: first screen;
-\textbf{B/B1/B2}: bridge screens;
-\textbf{P/P1/P2}: proxy screens;
-\textbf{S}: summary screen;
-\textbf{Pr}: progress bar.
-}
-\label{fig:flow}
-\end{figure*}
-
+
+{\color {blue}
+Introduction to security design principles.
+
+Security design principles: 
 \begin{enumerate}
-\item Added instructions on what to try next on errors.
-When an error occurs, text advice on what to try next is shown to the user to help them recover from the error.
-The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy.
-\item Added guidance on choosing between connect and configure.
-Before, the interface only informed users that the connect option worked some of the time, but did not specify why that was so.
+\item no user-dependent inputs 
+\item no network-dependent inputs
+\item minimal information leaks
+\end{enumerate}
+
+%In principle, the process of configuring a proxy and bridge can be automated, but
+%the interface eschews automatic configuration through network probing
+%in favor of guided manual configuration to give users agency in configuring their connection. 
+%Automatic configuration through network probing may put some users in certain regimes at risk. 
+%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
+Justify why we kept the similar interface. Refer to appendix for alternative approaches.
+
+Introduction to usability design principles.
+
+Usability design principles: 
+\begin{enumerate}
+\item minimal user work
+\item full user control  
+\item targeted user feedback
+\item build a mental model
+\end{enumerate}
+
+Introduction to design changes.  \\
+
+\noindent Changes made for minimal user work: 
+\begin{itemize}
+\item eliminated technical questions. Less questions to answer, less screens. 
+\item auto-detection for proxies.
+A local scan of the operating system configuration does reveal information to network eavesdroppers and can detect if a proxy is used (if configured in other browsers).
+(We simulated the auto-detection by hard-coding the fact that a proxy was not required.)
+\end{itemize}
+
+Changes made for full user control: 
+\begin{itemize}
+\item added intructions on what to try next on errors. The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy. 
+\item added advice for choosing connect versus configure.
+Before, the interface only informed users that the connect option worked some of the time, but did not specify why.
 We labeled the configure option as a manual option  specifically for users in heavily censored environments.
-\item Added explicit advice on choosing bridge transports.
-Users did not know which bridges to choose if they were in E3, which requires users to choose a meek or custom bridge.
-We added text that advises users to try a meek bridge if obfs3 does not work.
-\end{enumerate}
-
-Users found the feedback to be more confusing than helpful, since error messages were technical and progress bar was misleading.
-We make the following changes to make feedback insightful and reflective of system state:\\
-\begin{enumerate}
-\setcounter{enumi}{3}
-\item Progress bar feedback is accurate.
+\item gave advice on choosing transports. We tell users to try a meek bridge if obfs3 does not work.
+\end{itemize}
+
+Changes made for feedback: 
+\begin{itemize}
+\item progress bar feedback fixed and network-accurate.
 We fixed the bug that caused the progress bar to not update on subsequent attempts.
-What users now see on the progress bar reflects the reality of the progress.
-\item Made the interface text less technical.
-We made the text more task-centric by focusing on instructing users through the configuration process.
-Since users generally did not understand the technical concepts sufficiently to influence their decisions, we think giving direct guidance is a better option.
-\item Added system status visibility.
-Before beginning any connection attempt, a summary screen displays the current bridge and proxy settings.
-The same information is shown on the progress screen while the connection is in progress.
 We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
-\end{enumerate}
-
-Our users had little technical background. We made the following changes to make the interface more compatible for the average user: \\
-
-\begin{enumerate}
-\setcounter{enumi}{6}
-\item Eliminated technical questions.
-We removed the gating questions that determined whether a bridge and proxy should be configured, which were highly technical and challenging for users to answer.
-This are two fewer screens in the revised interface.
-\item Added auto-detection of proxies.
-In principle, the interface can guess whether a proxy is needed by scanning the operating system configuration.
-This purely local detection does not carry any risks nor reveal to network eavesdroppers that the user is using Tor.
-(We simulated the auto-detection by hard-coding the fact that a proxy was not required.)
-\item Switched ordering to configure proxies first.
-To build users' mental models, network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology} and the new progress screen.
-Previously, proxies were put after bridge configuration because only a small fraction of users require proxies.
-With auto-detection, configuring a proxy before a bridge burdens users less than before.
-\end{enumerate}
-
-These changes result in a redesigned interface which we refer to as NEW.
-Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.
-%for color red
+\item minimized interface text. Whenever we could, we tried to shave text and keep it simple. 
+\end{itemize}
+
+Changes made to build a mental model:
+\begin{itemize}
+\item added system status visibility. We added a summary screen displays the current bridge and proxy settings
+\item switched proxy and bridge configuration order. Network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology}.
+\end{itemize}
+
+Refer to figure with all deployed interface window (in previous section), refer to figure with all new interface windows (in caption, refer to appendix with advice text given on errors).
+Intorduce new/old labels.
 }
@@
 \label{sec:eval}
-{\color {red} 
-Our user studies evaluated two versions of the Tor Launcher interface.
-The first, which we have labeled OLD in our figures and tables,
-is the current version being distributed with Tor Browser.
-The second, NEW, is the prototype that we designed
-in order to provide better usability. Below are the empirical and 
-heuristic evaluation criteria we use to assess the interfaces.
-
-Our empirical evaluation criteria for the Tor Browser configuration
-interface are based on common metrics that measure ease of use: \\
-
-\begin{enumerate}
-    \item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition.
-This measures how many users are able to configure their connections with the interface.
+
+{\color {blue}
+Justification of quantitative analysis over qualitative.
+
+Below are the empirical and criteria we use to assess the interfaces:  
+\begin{itemize}
+\item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition. This measures how many users are able to configure their connections with the interface. 
 \item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
@@
 This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
-\end{enumerate}
-
-An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.
-A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface.
-For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.
-%for color red
+\end{itemize}
+
+Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long.
+
+Measure of success is x\% succeeding and taking no longer than average of y minutes. 
 }
@@
 
+%We refreshed a list of Tor relay IP addresses and added them
+%to a firewall blacklist before each session.
+%In the first study, we neglected to block the IP addresses
+%of the Tor directory authorities, which are the first hosts
+%a client contacts when initiating a non-bridge connection.
+%New relays also appeared in the network on an hourly basis,
+%which enabled a small number of participants to succeed with
+%a direct connection when that configuration should have failed.
+%We believe this is acceptable because 
+%the qualitative user study was not used to quantify failures or successes, 
+%but to explore possible problems.
+%We fixed this problem in our quantitative user study by blocking the directory authorities.
+
+%We blocked en.wikipedia.org, the target of the experiment,
+%as well as other language-specific subdomains such as
+%de.wikipedia.org and fr.wikipedia.org.
+%We neglected, however, to block the Simple English Wikipedia
+%at simple.wikipedia.org, which one participant found,
+%thinking they had completed the task.
+%% E2-OLD-X04-20160330-181928
+
+%We discarded data on participants who chose to download their own version of Tor Browser online.
+5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
+
+%Many waited for minutes at the progress screen, but never saw an error message.
+Error messages are intended to appear after a timeout.
+There were warnings, but those warnings went largely unnoticed by our participants.
+Across both versions of the interface, only one participant ever saw an error message.
+We tried to make error messages more instructive and understandable, since participants in our experiment did not encounter error messages, we cannot evaluate them.
+
 \begin{table}
@@
 
+% Is this the right place for this? 
+% GENERAL STUFF; SHORTEN THIS A LOT
+{\color {red} 
+Additional stuff we found out through a combination of log processing (i.e. configuration settings on attempts) and video observation (i.e. watching what they searched for online).
+
+How people succeeded. Straightforward.
+
+How people failed-- 17\% (19 of 114) of participants were not able to successfully connect to Tor.
+63\% (72 of 114) of first attempts to connect failed and (363 of 458) of total attempts to connect failed.
+\\
+
+\begin{description}
+\item {\bfseries Some people won't try other options (6/19).} P73, P75, P89, P91, P106, P110 tried a direct connection.
+When that failed, they tried the same option, over and over, no matter how many times they failed.
+It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
+
+\item {\bfseries Recommendations work, but one and done (5/19).} P90, P93, P108, P111, P114, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
+They often tried those configurations again or gave up.
+
+\item {\bfseries People don't know what their problem is (5/19).} P74, P92, P105, P107, P113 assumed that they needed a proxy.
+They spent their time trying to configure a proxy, usually without trying other bridges.
+
+\item {\bfseries Bridges auto-responder is hard to use (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
+However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
+\end{description}
+}
+
 \subsubsection{Time to Success} 
@@
 
-\section{Discussion} 
-\label{sec:discussion}
-
-{\color {red} 
-We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.
-
-\subsubsection{Failures}
-Failure is common.
-17\% (19 of 114) of participants were not able to successfully connect to Tor.
-63\% (72 of 114) of first attempts to connect failed and (363 of 458) of total attempts to connect failed.
-Reasons for failure were determined by a combination of log processing (i.e.
-configuration settings on attempts) and video observation (i.e.
-observing what they searched for online).
-\\
+\section{Recommendations}
+\label{recommendations}
+{\color {blue}
+If you adopt our redesigned interface, there will be better results.
+
+We can't say how much each change helped, since we did not test them independently.
+Some changes could have even have a negative or no-effect that is masked by other changes that had positive impact.
+To know this, we would have had to do some AB testing.
+some possible things to fix:
 
 \begin{description}
-\item {\bfseries Only connected directly (6/19).} P73, P75, P89, P91, P106, P110 tried a direct connection.
-When that failed, they tried the same option, over and over, no matter how many times they failed.
-It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-
-\item {\bfseries Only tried recommendations (5/19).} P90, P93, P108, P111, P114, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
-They often tried those configurations again or gave up.
-
-\item {\bfseries Thought that they needed a proxy (5/19).} P74, P92, P105, P107, P113 assumed that they needed a proxy.
-They spent their time trying to configure a proxy, usually without trying other bridges.
-
-\item {\bfseries Used the bridges auto-responder incorrectly (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
-However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
-\end{description}
-
-We discarded data on participants who chose to download their own version of Tor Browser online.
-5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
-Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
-
-\subsubsection{Observations}
-We noticed several behavioral patterns in our participants. These may or may not apply to the Tor user base.\\
-
-\begin{description}
-%connect vs configure
-\item {\bfseries Users try the easy path first.} Users generally try connecting directly to the Tor network first.
-81\% (92 of 114) of first attempts were to connect directly, with 52\% (48 of 92) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
-This leaks to network eavesdroppers that they are connecting to Tor.
-
-% impacts of making the proxy page ``automated'' 
-\item {\bfseries Users wasted time configuring proxies.} This confusion prevented users from configuring their bridges correctly.
-Participants with the new interface (which explicitly states that they did not need a proxy) spent about the same time configuring proxies as bridges, whereas users with the old interface spent about twice as much time configuring proxies than bridges.
-We do not understand why users with the new interface spent time configuring proxies after explicitly being told that they do not need one.
-
-% impacts of giving people advice on which transport to choose.
-\item {\bfseries The interface has a large influence on the bridges chosen.}
+\item {\bfseries Getting people to click configure if they need it.}  81\% (92 of 114) of first attempts were to connect directly, with 52\% (48 of 92) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
+%giving specific countries
+\item {\bfseries Stop users from configuring proxies.} Everyone did this.
+Participants with the new interface (which explicitly states that they did not need a proxy) spent less configuring proxies comparatively, but we do not understand why users with the new interface spent time configuring proxies after explicitly being told that they do not need one.
+%redirect to bridge or proxy page depending on error
+\item {\bfseries Help people choose second bridges.}
 Participants in E3 were required to choose a particular subset of hard-coded bridges, none of which was the default bridge.
@@
 66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
-
-%error messages
-\item {\bfseries People saw (almost) no error messages.} Many waited for minutes at the progress screen, but never saw an error message.
-Error messages are intended to appear after a timeout.
-There were warnings, but those warnings went largely unnoticed by our participants.
-Across both versions of the interface, only one participant ever saw an error message.
-We tried to make error messages more instructive and understandable, since participants in our experiment did not encounter error messages, we cannot evaluate them.
-
-% progress bar
-\item {\bfseries People waited a long, long time at the progress bar.}
-From watching the screen capture videos, we see that some participants dutifully followed the directions to wait, while others are who are uncertain wait without taking additional actions.
+%automate after first failure
+\item {\bfseries fix the progress bar and add error messages.} 
+We can't say anything about our error messages, because they never happened. Our progress bar didn't help, either, since it causes to people to wait almost indefinitely anyway. 
+\item {\bfseries add system visibility.} 
 \end{description}
 
-%for color red
-}
-
-\subsubsection{Recommendations}
-\label{recommendations}
-{\color {red} 
-Based on our observations of general behavioral trends and common failure cases, we make the following recommendations to increase success rate and decrease overall time spent in the interface: \\
-
-\begin{description}
-\item {\bfseries Automate configuration after failure.} After one unsuccessful attempt, a user has already leaked to network eavesdroppers leaking that they are connecting to Tor.
-Automating the configuration process thereafter will have no increase in risk.
-This will specifically help users that will never try to configure their connection (the most common failure case) to succeed and drastically reduce the time spent for the 63\% of participants who failed their first attempt.
-Users in more comprehensive censorship environments are more likely to benefit from this, as 5\% of participants in the mild censorship environment, 84\% participants in intermediate censorship environment, and 100\% of participants in the heavy censorship environment failed the first time.
-\item{\bfseries Hide infrequently used options.} Telling users they did not need a proxy was not enough to deter users from configuring a proxy.
-Only a small fraction of the Internet population requires a proxy to connect to the Internet.
-Hiding the proxy screen by default and only showing it after it has been detected as necessary might improve the user experience focusing user effort on configuring bridges.
-\item {\bfseries Be explicit about recommendations.} Many do not know what to do after the recommended bridge failed.
-The interface should mark which bridges have been tired before and recommend the user to try another bridge.
-(i.e.
-After a user tried an obfs3 bridge, the interface updates its recommendation to a meek bridge and mark the obfs3 bridge with an ``X''.)
-\item{\bfseries Set a timeout on the progress bar.} Informing users that they have failed earlier will decrease the overall time to success, create an opportunity to give suggestions, and reduce user frustration.
-\item{\bfseries Have a user-tolerant bridge auto-responder.} The bridge auto-responder responds to user requests for custom bridges.
-Users can make this request by emailing bridges@torproject.org with a non-empty title and ``get bridges'' in the body.
-Both of our users who tried to get custom bridges this way failed to format their request correctly.
-Having the auto-responder respond with bridges as a default or recovering from common errors (such as typing ``get bridges'' in the subject line) may help users succeed.
-\end{description}
-
-Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.
-%for color red
+You don't have to really listen to these specific things though,but definitely take out user design principles to heart.
+
+Reconsider some of the securty considerations and consider an alternative approach!
+Not saying that if we can't do it, no one can, but we know it's hard.
+As of now, people are still failing, so we need to do better.
 }
@@
 \label{sec:limitations}
-{\color {red} 
+{\color {blue}
+It's not exact censorship, so we cannot make any claims about how difficult it would be for a user to connect to Tor in a certain country or much our improvements will help those people.
+
+Our study was conducted in a laboratory setting.
+We believe that our participants were suffiencitnly motivated to complete the task due to the Hawthorne effect (they knew that they were being watched) and the monetary reward.
+We don't know if this is more or less motivated than people in censorships.
+We don't have information about when users would give up.
+
 The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
@@
 
-We refreshed a list of Tor relay IP addresses and added them
-to a firewall blacklist before each session.
-In the first study, we neglected to block the IP addresses
-of the Tor directory authorities, which are the first hosts
-a client contacts when initiating a non-bridge connection.
-New relays also appeared in the network on an hourly basis,
-which enabled a small number of participants to succeed with
-a direct connection when that configuration should have failed.
-We believe this is acceptable because 
-the qualitative user study was not used to quantify failures or successes, 
-but to explore possible problems.
-We fixed this problem in our quantitative user study by blocking the directory authorities.
-
-%We blocked en.wikipedia.org, the target of the experiment,
-%as well as other language-specific subdomains such as
-%de.wikipedia.org and fr.wikipedia.org.
-%We neglected, however, to block the Simple English Wikipedia
-%at simple.wikipedia.org, which one participant found,
-%thinking they had completed the task.
-%% E2-OLD-X04-20160330-181928
-
-Our study was conducted in a laboratory setting, which can cause our participants to be under or over-motivated.
-Our participants had a monetary incentive to connect to Tor, whereas a real user in a censored environment would want to reach a particular website.
-
 We chose to focus on more common cases, and did not simulate environments that requires users to configure a custom bridge or proxy.
-Although users in the wild can download interfaces that are not in their native language, we do not know how often this happens.
-We tested the English version of the Tor interface on English speaking participants.
-
-%for color red
+But if it's this hard to connec without using the more advanced configuration methods, then out point about needing an alternative method still stands.
+
+We did not study international users.
+English on english users.
+Again, english is the best language though, so if it's this hard for native english speakers in the best tranlated language, it will be harder for others.
 }
@@
 
-{\color {red} 
-We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface, focusing on users who use Tor to circumvent censorship.
-Since connecting to the Tor network unsuccessfully indicates to network eavesdroppers that users are connecting to Tor, the configuration process is manual to allow users to have control over the network activity.
-Through interviews and lab studies, we find that users have difficulty configuring network components to circumvent censorship, because they do not know how censorship or Tor works.
-We detail the common challenges, our changes to the configuration interface address those challenges, and the recommendations we have for Tor in this paper.
-
-%general advice to other censorship circumvention and call for more research 
-Interacting with a censorship circumvention tool users can be a complex balance of leveraging user input for local information while accounting for user trust of the software and minimizing potential risks.
-When designing censorship circumvention tools, we caution against requiring first-time users to make decisions on software-specific notions (e.g.
-pluggable transports for Tor), answering questions that assume technical knowledge, or manually configuring components.
+{\color {blue}
+We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface. A couple sentences to summarize the whole thing. Echo roadmap in intro, but make it summary-like.
+
+%proof that user testing is important and general advice to for more research on Tor
+Tor doesn't collect any information or perform AB testing, so this type of user research is especially important.
+to set it up, get users, computers, consent, and instrumented versions of the software.
+Research can be exploratory (ask users what they want), observational (look at what they do), or testing a hypothesis (verify changes).
 We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
 Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
-
-%for color red
 }
@@
 \section{Alternative Approaches} 
-{\color {red} 
-%In principle, the process of configuring a proxy and bridge can be automated, but
-%the interface eschews automatic configuration through network probing
-%in favor of guided manual configuration to give users agency in configuring their connection. 
-%Automatic configuration through network probing may put some users in certain regimes at risk. 
-%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-%However, this requires that the user grapple with technical concepts such as 
-%bridges, pluggable transports, and proxies. Some of these concepts are specific to 
-%Tor and not general concepts.
-
+{\color {blue}
 Our goal was to deploy impactful, tested changes the Tor configuration interface.
@@
 
+%remember: 	no user inputs, no network inputs, minimize info leaks
+%and:		minimal user work, full user control
+
 \begin{description}
@@
 We do not know how much risk is associated with this approach.
+\item {\bfseries automate after the first failure.} The network leak happened. But then this automation would be pretty fingerprintable behavior. 
 \item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk.

### 2016-10-19 pets2017-paper/pets2017-paper.tex
limitations section pass

@@
 \label{sec:limitations}
-{\color {blue}
-It's not exact censorship, so we cannot make any claims about how difficult it would be for a user to connect to Tor in a certain country or much our improvements will help those people.
-
-Our study was conducted in a laboratory setting.
-We believe that our participants were suffiencitnly motivated to complete the task due to the Hawthorne effect (they knew that they were being watched) and the monetary reward.
-We don't know if this is more or less motivated than people in censorships.
-We don't have information about when users would give up.
-
-The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems.
-We only tested interface on Windows machines, which were the machines available at <redacted>.
-%Xlab.
-Participants who are not accustomed to Windows machines may have been slower to complete the given task, but this affected all conditions equally.
-
-We chose to focus on more common cases, and did not simulate environments that requires users to configure a custom bridge or proxy.
-But if it's this hard to connec without using the more advanced configuration methods, then out point about needing an alternative method still stands.
-
-We did not study international users.
-English on english users.
-Again, english is the best language though, so if it's this hard for native english speakers in the best tranlated language, it will be harder for others.
-}
+We did not study international users, or the configuration interface in languages other than English.
+All of our participants were from the United States and instructed to interact with the English version of Tor Browser.
+
+Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}.
+We are aware that our participants were likely motivated differently compared to real users.
+We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward.
+If true, this makes our results are a conservative estimate of the current problems.
+
+Since the configuration interfaces in simulated environments, we cannot claim how difficult it would be for a user to connect to Tor in a certain country or how much our redesigned interface would help those users.
+
+Our experiment did not directly test more advanced tasks.
+Our simulated environments did not require users to configuring a proxy or to get a custom bridge.
+From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how or why they do.
+
+We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
+The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent.
+Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all testing conditions equally.
 

### 2016-10-19 pets2017-paper/pets2017-paper.tex
re-wrote recommendations.

@@
 \section{Design Principles and Changes}
-\label{redesign}
+\label{sec:design}
 
@@
 \label{recommendations}
-{\color {blue}
-If you adopt our redesigned interface, there will be better results.
-
-We can't say how much each change helped, since we did not test them independently.
-Some changes could have even have a negative or no-effect that is masked by other changes that had positive impact.
-To know this, we would have had to do some AB testing.
-some possible things to fix:
-
-\begin{description}
-\item {\bfseries Getting people to click configure if they need it.}  81\% (92 of 114) of first attempts were to connect directly, with 52\% (48 of 92) direct first attempts from the new interface and 47\% (44 of 93) direct first attempts from the old interface.
-%giving specific countries
-\item {\bfseries Stop users from configuring proxies.} Everyone did this.
-Participants with the new interface (which explicitly states that they did not need a proxy) spent less configuring proxies comparatively, but we do not understand why users with the new interface spent time configuring proxies after explicitly being told that they do not need one.
-%redirect to bridge or proxy page depending on error
-\item {\bfseries Help people choose second bridges.}
-Participants in E3 were required to choose a particular subset of hard-coded bridges, none of which was the default bridge.
-After the default bridge, the most chosen bridge was the one listed first in the drop-down menu.
-Many bridges listed at the end of the drop-down menu were not chosen.
-We tried to help users by providing instructions on which bridges to choose if the default fails, but it is unclear if this advice helped.
-66\% (10 of 15) participants with the new interface and 38\% (5 of 13) participants with the old interface chose meek as their second bridge.
-%automate after first failure
-\item {\bfseries fix the progress bar and add error messages.} 
-We can't say anything about our error messages, because they never happened. Our progress bar didn't help, either, since it causes to people to wait almost indefinitely anyway. 
-\item {\bfseries add system visibility.} 
-\end{description}
-
-You don't have to really listen to these specific things though,but definitely take out user design principles to heart.
-
-Reconsider some of the securty considerations and consider an alternative approach!
-Not saying that if we can't do it, no one can, but we know it's hard.
-As of now, people are still failing, so we need to do better.
-}
+We believe that adopting our design will help save users time when connecting to Tor.
+But we do not claim how much and in what way each change impacted our participants, since we did not test them independently.
+Some of our changes may have little or negative effects, but may be masked by other changes with positive effects.
+We also recognize that there may be equivalent or more impactful changes that may be made in place of ours.
+
+We hope that our inspection, design, and evaluation evaluation process provided valuable insight for potential changes.
+We do not recommend our specific design changes, but offer some advice and accompanying suggestions: \\
+
+\begin{itemize}
+\item {\bfseries Use less words.} While a thorough explanation isn't always possible with brevity, users are more likely to read the text if it is short.
+\item {\bfseries Minimize work.} Ask users to perform tasks only when necessary.
+Hide less frequently used options or components.
+Redirect users to the relevant pages (i.e.
+redirect to the bridge screen the bridge fails).
+\item {\bfseries Give advice.} Guide users toward connecting directly unless they need a bridge or proxy, help them decide between transports, and discourage them from configuring optional components.
+\item {\bfseries Add system visibility.} Rather than requiring users to remember their bridge and proxy configuraitons, summarize their choices.
+The progress bar should reflect the current state of the connection.
+\item {\bfseries Provide feedback.} In addition to displaying the error message, tell users what to try next when they encounter that error. 
+\end{itemize}
+
+We should consider alternative approaches of bootstrapping a connection to Tor.
+We recommend leveraging automation, user-dependent inputs, or network-dependent inputs for a solution that will help more users succed in a shorter amount of time.
+We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.
 
@@
 \section{Alternative Approaches} 
+\label{alternatives}
 {\color {blue}

### 2016-10-19 pets2017-paper/pets2017-paper.tex
re-ordered some paragraphs in the quantitative section.

@@
 Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
-
-Measure of success is x\% succeeding and taking no longer than average of y minutes. 
 }
@@
 
+We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
+%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
+Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
+The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
+
+\begin{figure*}
+\centering
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The ``not running'' times are those when Tor Launcher was closed;
+i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes.
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
 \begin{table}
@@
 %\end{figure}
-%
+
 %We believe that the added advice on what to try next on error messages would have improved the rate of success.
@@
 The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
-%
-%That participant was using the new interface and was told that the bridge configuration was the source of the error.
-The participant heeded the interface's advice to reconfigure the bridge options.
-But since most participants did not see any error messages, any effects they may have had on success rates are not reflected in our results.
-The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
+
+%The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
 
@@
 Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result.
-Appendix~\ref{custom} shows the malformed requests.
 These two participants failed to connect to the Tor network.
@@
 
-\subsubsection{Active Time} 
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
-%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
-Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
-The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
-
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The ``not running'' times are those when Tor Launcher was closed;
-i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes.
-}
-\label{fig:all-participant-edges}
-\end{figure*}
-
+\subsubsection{Active Time to Success} 
 The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.

### 2016-10-19 pets2017-paper/pets2017-paper.tex
delete marker, since now sections todo and revise are color coded
hack at eval, and the two usability testing sections.

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%		LINDA'S PASS UP TO HERE 		       %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Usability Inspection}
@@
 
-\section{Qualitative User Testing}
+\section{Evaluation Method and Criteria}
+\label{sec:eval}
+
+{\color {blue}
+It is easy to specify usability metrics, but hard to collect them.
+Typically, usability is measured relative to users' performance on a given set of test tasks.
+The most basic measures are based on the definition of usability as a quality metric: success rate (whether users can perform the task at all), the time a task requires, the error rate, and users' subjective satisfaction.
+%https://www.nngroup.com/articles/usability-metrics/
+%http://www.measuringu.com/blog/essential-metrics.php
+
+We chose to evaluate the two interfaces by testing them on a large number of users, using the following criteria to measure usability: \\
+\begin{itemize}
+\item {\bfseries Success rate:} what percentage of users eventually connect to Tor in a given condition. 
+\item {\bfseries Error rate:} what percentage of user attempts could not connect to Tor. 
+\item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
+\item {\bfseries Configuration time:} time from Tor Browser startup to progress screen, measures includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+\end{itemize}
+
+Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long.
+
+}
+
+\section{Formative Usability Testing}
+\label{sec:qualitative}
+{\color {blue}
+Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable.
+It is typically called a Formative Usability Evaluation.
+In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores.
+Summative tells you how usable an interface is and formative tells you what isn't usable.
+
+Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
+
+With formative user testing, it is enough to test 3–5 users.
+After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again.
+Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
+%https://www.nngroup.com/articles/usability-metrics/
+%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/
+}
+
 {\color {red}
-\label{sec:qualitative}
-We ran a qualitative, exploratory user study to gain an 
-understanding of how users interact with the configuration interface and
-what common problems may be. We did this by observing participants using 
-the interface to circumvent censorship and interviewing them about
-their experience.  Our observations during this study guided us in
-redesigning the interface and provided hypotheses to test in our quantitative study.
-
 \subsection{Recruitment}
@@
 
-\section{Evaluation Method and Criteria}
-\label{sec:eval}
+\section{Summative Usability Testing}
+\label{sec:quantitative}
 
 {\color {blue} 
-Justification of quantitative analysis over qualitative.
-
-Below are the empirical and criteria we use to assess the interfaces:  
-\begin{itemize}
-\item {\bfseries Success rate:} what percentage of users can successfully connect to Tor in a given condition. This measures how many users are able to configure their connections with the interface. 
-\item {\bfseries  Time to completion:} how long it takes between program startup and a successful Tor bootstrap, which includes time spent searching online for help and waiting for the connection to bootstrap.
-This measures how much time is required for a user to connect to the Tor network.
-\item {\bfseries Active configuration time:} how much time a user spends actively configuring network components to connect to Tor, which only includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-This measures how much of the time spent connecting to the Tor network was spent configuring versus waiting.
-\end{itemize}
-
-Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
-}
-
-\section{Quantitative User Testing}
-\label{sec:quantitative}
+Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable.
+It is typically called a Formative Usability Evaluation.
+In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores.
+Summative tells you how usable an interface is and formative tells you what isn't usable.
+
+Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process.
+A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience.
+This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
+
+https://www.nngroup.com/articles/usability-metrics/
+https://www.nngroup.com/articles/quantitative-studies-how-many-users/
+}
 
 {\color {red} 
-Having identified problems with the existing interface
-and made changes to ameliorate them,
-we quantify the existing problems
-and the impact of our changes with a study involving a larger number of users.
-We split participants by simulated censorship environments,
-and between old and new interfaces.
-
 \subsection{Setup}

### 2016-10-20 pets2017-paper/pets2017-paper.tex
create a methodology section.

@@
 
-\section{Usability Inspection}
-{\color {red}
-We used a combination of usability inspection methods~\cite{nielsen1994usability}
-to prepare for the user study. Two researchers conducted a pluralistic 
-walkthrough and stepped through various censorship
-scenarios, discussing which elements would be involved for that use case, and walking 
-through the configuration process. After compiling all the possible paths through the 
-interface, researchers performed feature inspection, listing sequences of features used 
-to accomplish typical tasks and taking note of long sequences or cumbersome
-steps. In addition, we performed a heuristic evaluation to mark
-likely causes of confusion for users during our study.
-}
-
-\section{Experimental Setup}
+\section{Methodology}
+
+\subsection{Testing Procedure} 
+{\color {blue}
+
+Procedure: inspection, formative, design, summative.
+
+We wanted to inspect the thing ourselves before doing formative testing so we know what to look for. 
+http://www.usabilitybok.org/heuristic-walkthrough, not a pluralistic walkthrough (http://www.usabilitybok.org/pluralistic-walkthrough) or cognitive walkthrough (http://www.usabilitybok.org/cognitive-walkthrough).
+
+Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable.
+It is typically called a Formative Usability Evaluation.
+In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores.
+Summative tells you how usable an interface is and formative tells you what isn't usable.
+
+Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
+%http://www.usabilitybok.org/Formative-evaluation
+%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/
+
+With formative user testing, it is enough to test 3–5 users.
+After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again.
+Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
+
+We wanted to try an anternative interface to see if we can make any improvements.
+We wanted to, since we had all this testing!
+But we can also test the original design in a formative and summative way.
+
+Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process.
+A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience.
+This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
+%http://www.usabilitybok.org/Summative-evaluation
+%https://www.nngroup.com/articles/quantitative-studies-how-many-users/
+}
+
+\subsection{Evaluation Criteria}
+\label{sec:eval}
+
+{\color {blue}
+It is easy to specify usability metrics, but hard to collect them.
+Typically, usability is measured relative to users' performance on a given set of test tasks.
+The most basic measures are based on the definition of usability as a quality metric: success rate (whether users can perform the task at all), the time a task requires, the error rate, and users' subjective satisfaction.
+%https://www.nngroup.com/articles/usability-metrics/
+%http://www.measuringu.com/blog/essential-metrics.php
+
+We chose to evaluate the two interfaces by testing them on a large number of users, using the following criteria to measure usability: \\
+\begin{itemize}
+\item {\bfseries Success rate:} what percentage of users eventually connect to Tor in a given condition. 
+\item {\bfseries Error rate:} what percentage of user attempts could not connect to Tor. 
+\item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
+\item {\bfseries Configuration time:} time from Tor Browser startup to progress screen, measures includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+\end{itemize}
+
+Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
+}
+
+\subsection{Experimental Setup}
 We simulated three environments (which we refer to as E1, E2, and E3), 
@@
 
-\section{Evaluation Method and Criteria}
-\label{sec:eval}
-
-{\color {blue}
-It is easy to specify usability metrics, but hard to collect them.
-Typically, usability is measured relative to users' performance on a given set of test tasks.
-The most basic measures are based on the definition of usability as a quality metric: success rate (whether users can perform the task at all), the time a task requires, the error rate, and users' subjective satisfaction.
-%https://www.nngroup.com/articles/usability-metrics/
-%http://www.measuringu.com/blog/essential-metrics.php
-
-We chose to evaluate the two interfaces by testing them on a large number of users, using the following criteria to measure usability: \\
-\begin{itemize}
-\item {\bfseries Success rate:} what percentage of users eventually connect to Tor in a given condition. 
-\item {\bfseries Error rate:} what percentage of user attempts could not connect to Tor. 
-\item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
-\item {\bfseries Configuration time:} time from Tor Browser startup to progress screen, measures includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-\end{itemize}
-
-Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long.
-
+\section{Usability Inspection}
+{\color {red}
+We used a combination of usability inspection methods~\cite{nielsen1994usability}
+to prepare for the user study. Two researchers conducted a pluralistic 
+walkthrough and stepped through various censorship
+scenarios, discussing which elements would be involved for that use case, and walking 
+through the configuration process. After compiling all the possible paths through the 
+interface, researchers performed feature inspection, listing sequences of features used 
+to accomplish typical tasks and taking note of long sequences or cumbersome
+steps. In addition, we performed a heuristic evaluation to mark
+likely causes of confusion for users during our study.
 }
@@
 \label{sec:qualitative}
+
 {\color {blue}
-Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable.
-It is typically called a Formative Usability Evaluation.
-In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores.
-Summative tells you how usable an interface is and formative tells you what isn't usable.
-
-Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
-
-With formative user testing, it is enough to test 3–5 users.
-After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again.
-Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
-%https://www.nngroup.com/articles/usability-metrics/
-%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/
-}
-
+short intro sentence
+}
+
+\subsection{Recruitment}
 {\color {red}
-\subsection{Recruitment}
 Using established practices from the field of user experience research~\cite{howmanyusers},
@@
 {\color {blue} 
-Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable.
-It is typically called a Formative Usability Evaluation.
-In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores.
-Summative tells you how usable an interface is and formative tells you what isn't usable.
-
-Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process.
-A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience.
-This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
-
-https://www.nngroup.com/articles/usability-metrics/
-https://www.nngroup.com/articles/quantitative-studies-how-many-users/
+short intro sentence.
 }

### 2016-10-20 pets2017-paper/pets2017-paper.tex
add setup section for first user test too (the second had it..)
minor tweaks at first user test's recruitment wording.

@@
 
-We recruited our users from Craigslist, vaguely asking to evaluate a piece of software. 
-The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
-SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
-The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
-We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
-at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
-expertise or used particular security tools throughout the censorship environments.
+We recruited users from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}. 
+The recruitment posting linked an online survey that collected their demographics, technical expertise, and familiarity with Tor.
 
@@
 and the remaining 8 had never heard nor used it. 
+We distributed participants so that each experimental condition had at least one person who has never heard of Tor, at least one person who has only heard of Tor, and one person who has previously used Tor.
+The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.
+}
+
+\subsection{Setup} 
+{\color {blue}
+Setup details here.
+}
 

### 2016-10-20 pets2017-paper/pets2017-paper.tex
switch order of setup and recruitment section in second user study section.

@@
 
-{\color {red} 
-\subsection{Setup}
-We ran our experiment at <redacted>.
-%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
-<redacted> %Xlab 
-has 36 Windows~7 laptops, separated by cubicle walls. 
-Though Tor Browser runs on other operating systems,
-testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.
-
-We augmented the interfaces with instrumentation 
-to log every meaningful interaction
-(button presses, menu selections, screen changes).
-We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
-start the video recording, and save the logs and videos.
-We recorded the participants' computer screens
-throughout the experiment to capture non-interface activity such as 
-web searching and inspection of system networking settings.
-
 \subsection{Recruitment}
@@
 84.8\% of our participants had at least a college education.
-
+}
+
+\subsection{Setup}
+{\color {red} 
+We ran our experiment at <redacted>.
+%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
+<redacted> %Xlab 
+has 36 Windows~7 laptops, separated by cubicle walls. 
+Though Tor Browser runs on other operating systems,
+testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.
+
+We augmented the interfaces with instrumentation 
+to log every meaningful interaction
+(button presses, menu selections, screen changes).
+We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
+start the video recording, and save the logs and videos.
+We recorded the participants' computer screens
+throughout the experiment to capture non-interface activity such as 
+web searching and inspection of system networking settings.
+}
 \subsection{Procedure}
+{\color {red} 
 The one-hour, multi-participant procedure began when all participants sat at their

### 2016-10-20 pets2017-paper/pets2017-paper.tex
more coloring for TODOS.

@@
 \subsection{Procedure}
+{\color {red}
 The one-hour, single-participant procedure begun when a participant entered a small 
@@
 We paid each participant~\$30 for their time. 
+}
 
 \subsection{Results} 
+{\color {red}
 We discuss six common challenges our participants encountered during the configuration process.
@@
 \end{figure}
-
-%for color red
 }
@@
 \subsection{Recruitment}
+{\color {red} 
 We recruited 124 participants, about 20 for each
@@
 \$30 for their time. 
+}
 
 \subsection{Results} 
+{\color {red} 
 The possible interface version and environment combinations resulted in 6 experimental conditions.

### 2016-10-20 pets2017-paper/pets2017-paper.tex
redo first recruitment subsection

@@
 \subsection{Recruitment}
-{\color {red}
-Using established practices from the field of user experience research~\cite{howmanyusers},
-we recruited 16 participants across the three censorship environments:
-5~in E1, 5~in E2, and 6~in E3.
-We pre-screened~\cite{screening} our participants for diversity of gender, age, technical expertise,
-and self-reported familiarity with Tor in each simulated censorship environment for our summative
-usability test~\cite{summative}.
-
-We recruited users from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}. 
-The recruitment posting linked an online survey that collected their demographics, technical expertise, and familiarity with Tor.
-
+We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an online survey that collected demographics.
+We pre-screened~\cite{screening} to have diversity of gender, age, technical expertise, and self-reported familiarity with Tor.
+The complete pre-screening survey can be found in Appendix~\ref{qualitative-prescreening}.
+
+We recruited 16 participants for the test and distributed them evenly across environments:  5~in E1, 5~in E2, and 6~in E3.
 Of our 16 participants, 53.3\% were male.
-Ages ranged from 20 to~62 years
-($\mu = 24.5$, $\sigma = 12.6$). 
-93.3\% of our participants had at least
-a college education.
-4 had used Tor before;
-5 had heard of Tor but not used it;
+Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$).
+93.3\% of our participants had at least a college education.
+4 had used Tor before; 5 had heard of Tor but not used it;
 and the remaining 8 had never heard nor used it.
-We distributed participants so that each experimental condition had at least one person who has never heard of Tor, at least one person who has only heard of Tor, and one person who has previously used Tor.
-The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.
-}
+Although there is variation in gender, age, technical expertise in each experimental condition, we ensured each condition had a participant who has not heard of Tor, a participant who has heard of Tor, and a participant who has previously used Tor.
 

### 2016-10-20 pets2017-paper/pets2017-paper.tex
move citations deleted from recuitment section into the metholodgy section.
clarified that we prescreened due to small participant size in recuirments subsection.

@@
 %http://www.usabilitybok.org/Formative-evaluation
-%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/
+%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/ ~\cite{howmanyusers}
 
@@
 %https://www.nngroup.com/articles/quantitative-studies-how-many-users/
+%~\cite{summative}
 }
@@
 We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an online survey that collected demographics.
-We pre-screened~\cite{screening} to have diversity of gender, age, technical expertise, and self-reported familiarity with Tor.
-The complete pre-screening survey can be found in Appendix~\ref{qualitative-prescreening}.
+We pre-screened~\cite{screening} to ensure diversity of gender, age, technical expertise, and (self-reported) familiarity with Tor in a small participant pool.
+The pre-screening survey is in Appendix~\ref{qualitative-prescreening}.
 

### 2016-10-20 pets2017-paper/pets2017-paper.tex
finish up both recruitment sections, add appendix for prescreen survey results.

@@
 }
-
 \subsection{Recruitment}
-We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an online survey that collected demographics.
-We pre-screened~\cite{screening} to ensure diversity of gender, age, technical expertise, and (self-reported) familiarity with Tor in a small participant pool.
-The pre-screening survey is in Appendix~\ref{qualitative-prescreening}.
-
-We recruited 16 participants for the test and distributed them evenly across environments:  5~in E1, 5~in E2, and 6~in E3.
-Of our 16 participants, 53.3\% were male.
+We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
+We pre-screened~\cite{screening} to ensure diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
+
+Of our 16 recruited participants, 53.3\% were male.
 Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$).
-93.3\% of our participants had at least a college education.
-4 had used Tor before; 5 had heard of Tor but not used it;
-and the remaining 8 had never heard nor used it.
-Although there is variation in gender, age, technical expertise in each experimental condition, we ensured each condition had a participant who has not heard of Tor, a participant who has heard of Tor, and a participant who has previously used Tor.
+93.3\% of our participants had college education.
+We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
+We verified their self-reported familiarity with Tor in-person, and found that 4 had used Tor before, 5 had heard of Tor but not used it, and the remaining 8 had never heard nor used it.
+We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
+Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who has used tor, a participant who has heard of Tor, and multiple participants who had never heard nor used it.
 
@@
 \subsection{Recruitment}
-{\color {red} 
-We recruited 124 participants, about 20 for each
-condition. We recruited half of our users from Craigslist, and half of our participants from 
-the <redacted> %Xlab 
-participant pool. Although <redacted> %Xlab 
-participants are not limited to <redacted> %UC Berkeley 
-students and staff,
-a majority of the participants are from campus. For this reason, we chose to recruit 
-half of our participants from Craigslist to ensure a diverse set of participants. 
-The recruitment text vaguely suggests testing a piece of software, and does not require
-that users provide information in advance (Appendix~\ref{quantitative-recruitment}). 
-Out of our 124 participants, 59 were recruited from the <redacted> %Xlab 
-pool and the other 65 were
-recruited from Craigslist. Ages ranged from 18 to~68 years
-($\mu = 28.9$, $\sigma = 12$). 56.8\% were male and 
-84.8\% of our participants had at least a college education.
-}
+We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}.
+We recruited 65 participants from Craiglist and 59 participants from the <redacted lab> participant pool.
+<Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants.
+Although the <redacted lab>'s participant pool is not limited to students and staff from <redacted institution>, it was estimated that a large majority were.
+
+Of our recruited 124 participants, 56.8\% were male.
+Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$).
+56.8\% were male.
+84.8\% of our participants had a college education.
+We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
+Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.
 
@@
 
+\section{Prescreening Survey Responses}
+\label{prescreening-responses}
+{\color{blue} 
+short intro and conclusion. Take self-reported with a grain of salt, but here they are anyways.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.5\textwidth]{self-reported-tech-familiarity.png}
+\caption{most participants reported familiarity with terms, even made up ones.}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.5\textwidth]{self-reported-security-use.png}
+\caption{most people didn't use many security tools.}
+\end{figure}
+}
+
 \section{Qualitative User Study Introduction Script} 

### 2016-10-20 pets2017-paper/pets2017-paper.tex
write setup sections, show artifacts and acks sections

@@
 website by using Tor.
-We blocked torproject.org and its respective subdomains to discourage downloading Tor Browser, as we had installed an instrumented version on the test computers (E1, E2, E3).
+We blocked torproject.org and its respective subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers (E1, E2, E3).
 We blocked wikipedia.org, cnn.com, and their respective subdomains to create an artificial task to visit a
@@
 We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
-We pre-screened~\cite{screening} to ensure diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
-
+We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
 Of our 16 recruited participants, 53.3\% were male.
@@
 We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
-We verified their self-reported familiarity with Tor in-person, and found that 4 had used Tor before, 5 had heard of Tor but not used it, and the remaining 8 had never heard nor used it.
+We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.
+
 We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
-Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who has used tor, a participant who has heard of Tor, and multiple participants who had never heard nor used it.
+Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser, a participant who heard of it, and multiple participants who never heard of or used it.
 
 \subsection{Setup} 
+We ran the experiment in a meeting room in <redacted building> at <redacted university>.
+The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up.
+On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment.
+Before each participant entered the room, we ran a script on the computer that simulated E1, E2, or E3 and started the video recording.
+
+\subsection{Procedure}
 {\color {blue}
-Setup details here.
-}
-
-\subsection{Procedure}
-{\color {red}
-The one-hour, single-participant procedure begun when a participant entered a small 
-room with a single computer, which is equipped with Tor, Chrome, Firefox, Internet Explorer, and VLC.
-Each participant is informed of the risks and purpose of the study.
+When a participant entered the room, researchers informed them of purpose of the study, data collected, and associated risks. 
 A researcher informed the participant of the simulated censorship environment and
@@
 Researchers watched a live video of each participant's screen from another room
-and saved the videos for review; the resulting videos and summaries
-are available from our project page.
+and saved the videos for review.
+
 Participants had an average of 45 minutes to complete their worksheet. 
-
 After participants completed the browsing tasks or ran out of time,
@@
 \subsection{Setup}
-{\color {red} 
-We ran our experiment at <redacted>.
+We ran our experiment at <Redacted lab>, an experimental social science laboratory for behavioral experiments.
+The testing room had 36 workstations with identical Windows~7 laptops.
+Side panels at each workstation to discouraged participants from looking at other participants' screens.
 %Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
-<redacted> %Xlab 
-has 36 Windows~7 laptops, separated by cubicle walls. 
-Though Tor Browser runs on other operating systems,
-testing was only done on Windows, as a byproduct of using <redacted>. %Xlab.
-
-We augmented the interfaces with instrumentation 
-to log every meaningful interaction
-(button presses, menu selections, screen changes).
-We wrote scripts to automatically set up the simulated censorship environment, install necessary software, 
-start the video recording, and save the logs and videos.
-We recorded the participants' computer screens
-throughout the experiment to capture non-interface activity such as 
-web searching and inspection of system networking settings.
-}
+The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.
+
+Before each session, we ran a script that downloaded the necessary software, set up one of the six experimental conditions, and start the video recording.
+Each computer was manually assigned an interface-environment combination in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
+In contrast to the previous usability test, we installed an instrumented version of Tor Browser 5.0.3 or an instrumented version of Tor Browser 5.0.3.
+with a redesigned configuration interface.
+The instrumentation in the interface logged user interactions such as window transitions, mouse clicks, and menu selections.
+Similarly to the previous usability test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment.
+
 \subsection{Procedure}
-{\color {red} 
-The one-hour, multi-participant procedure began when all participants sat at their
-respective computers in <redacted>. %Xlab. 
-Each computer was equipped with an instrumented old or new version
-of Tor Browser, Chrome, Firefox, Internet Explorer,  Chrome, and VLC (for screen recording).
-Each computer was assigned one of the six conditions in the beginning of the study. Participants
-were assigned to a simulated censorship environment combination at random.
-
-A researcher informed the participants that they are in a
-simulated censorship environment, instructed them to visit a sample blocked website on a 
-non-Tor browser of their choice to illustrate the situation, and asked them to 
-complete a worksheet that asks to visit one blocked website (Appendix~\ref{quantitative-script}). 
-To mirror the qualitative study, we chose Wikipedia's featured article of the day 
-as the blocked website to visit on their worksheet.
-
-After instructions, researchers maintained minimal interactions with the participants, 
-only answering logistical questions.
-The participants did not know the details of their censorship environment,
-only that they are being censored. Participants had 40 minutes to configure Tor Browser to 
-circumvent the simulated censorship and visit the blocked website.
-
-After users completed the browsing tasks, they took a short exit survey (Appendix~\ref{quantitative-exit-survey})
-that collected their demographics. All users were instructed to sit until the end of the experiment,
-regardless of when they had completed their task. After the 40 minutes, 
-participants were officially informed that their time was up, and were given their payment of 
-\$30 for their time. 
+{\color {blue} 
+Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random.
+When all participants sat at their respective computers,
+
+With only the consenting participants remaining, one of the researchers then read from a script that details the experiment, task, and data collected (Appendix~\ref{quantitative-script}).
+We told users of the simulated censorship environment, that Tor Browser can be used to circumvent censorship, and that we ask them to use Tor Browser to circumvent our simulated censorship.
+We ask users to complete a worksheet, which asks questions that can only be answered by going to the censored websites.
+To mirror the qualitative study, we chose Wikipedia's featured article of the day as the blocked website to visit on their worksheet.
+All users were instructed to sit until the end of the experiment, regardless of when they had completed their task.
+We remind them again that their screens are being recorded and to not show any personal information, such checking email.
+We give users a chance to ask any questions about the experiment or task.
+
+After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions.
+Participants had 40 minutes to complete the task.
+After the 40 minutes, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}) and were paid \$30 for their time.
 }
@@
 
-%\section {Resources} 
-%For additional details, such as the censorship simulation code, interview transcriptions, and logs of participant interactions, we refer you to the project repository: \\
-%
+\section {Experiment Artifacts} 
+Due to space constraints, we could not include many of our experiment artifacts.
+This includes the experiment setup and teardown code, firewall rules that simulated censorship environments, interview transcriptions from the formative user study, logs from our instrumented configuration interfaces, and videos of users attempting to connect to Tor through the configuration interface.
+We urge you to check out the project repository: \\
+
+\noindent <redacted url>
 %\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
-%
-%\section {Acknowledgments}
-% Rowilma del Castillo of Xlab supported out experiment by assisting with testing, offering recruitment services, and allowing experiments after-hours.
-Nima Fatemi, Isabela Bagueros, Georg Koppen, and the Tor UX team have provided me with valuable feedback along the way.
+
+\section {Acknowledgments}
+Many generous people helped us along the way.
+<Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours.
+<Redacted> and <redacted> were instrumental during the design process, as they helped me interate through many not-so-great ideas.
+<Redacted>,and <redacted> provided me with insider insight into the design decisions made at Tor.
+% Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.
 

### 2016-10-21 pets2017-paper/pets2017-paper.tex
add subsections to design section.
move all-participant-edges to appendix.

@@
 {\color {blue}
-Introduction to security design principles.
+Introductory sentence.
+}
+
+\subsection{Procedure} 
+{\color {blue}
+Talk about iteration and how we designed it here.
+}
+
+\subsection{Design Princples} 
+{\color {blue}
+Introduce design principles.
 
@@
 \end{enumerate} 
-
+}
+
+\subsection{Design Changes} 
+{\color {blue}
 Introduction to design changes.  \\
@@
 Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
+Appendix~\ref{all-participant-edges}'s Fig.~\ref{fig:all-participant-edges} summarizes invididual participants' actions throughout the experiment.
 
@@
 We tried to make error messages more instructive and understandable, since participants in our experiment did not encounter error messages, we cannot evaluate them.
-
-We summarize each participant's actions throughout the experiment in Fig.~\ref{fig:all-participant-edges}.
-%and summarize where they spent their time in Appendix~\ref{all-participant-times}. 
-Each row in Fig.~\ref{fig:all-participant-edges} corresponds to a participant.
-The bar represents a path through the interface, illustrating time spent on each screen, transitions between screens, how many attempts were made, and if they were eventually successful.
-
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The ``not running'' times are those when Tor Launcher was closed;
-i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes.
-}
-\label{fig:all-participant-edges}
-\end{figure*}
 
@@
 
+\section{Quantitative Summary}
+\label{all-participant-edges} 
+\begin{figure*}
+\centering
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The ``not running'' times are those when Tor Launcher was closed;
+i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes.
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
 \section{Statistical Tests} 

### 2016-10-21 pets2017-paper/pets2017-paper.tex
new title.
create procedure subsections, mark things to do.

@@
 
-  \title{\huge A Better (One-Line!) Title Here}
-
-  \runningtitle{A Better (One-Line!) Title Here}
+  \title{\huge A Usability Evaluation of Tor Launcher}
+
+  \runningtitle{A Usability Evaluation of Tor Launcher}
 
@@
 {
+{\color {blue}
 We evaluate, design, and test the Tor Launcher interface by
@@
 a significant reduction in time. We conclude with recommendations for changes 
-to the current interface as well as alternative solutions.}
+to the current interface as well as alternative solutions.
+}
+}
 \end{abstract}
@@
 http://www.usabilitybok.org/heuristic-walkthrough, not a pluralistic walkthrough (http://www.usabilitybok.org/pluralistic-walkthrough) or cognitive walkthrough (http://www.usabilitybok.org/cognitive-walkthrough).
+
+%We used a combination of usability inspection methods~\cite{nielsen1994usability}
+%to prepare for the user study. Two researchers conducted a pluralistic 
+%walkthrough and stepped through various censorship
+%scenarios, discussing which elements would be involved for that use case, and walking 
+%through the configuration process. After compiling all the possible paths through the 
+%interface, researchers performed feature inspection, listing sequences of features used 
+%to accomplish typical tasks and taking note of long sequences or cumbersome
+%steps. In addition, we performed a heuristic evaluation to mark
+%likely causes of confusion for users during our study.
 
@@
 \section{Usability Inspection}
-{\color {red}
-We used a combination of usability inspection methods~\cite{nielsen1994usability}
-to prepare for the user study. Two researchers conducted a pluralistic 
-walkthrough and stepped through various censorship
-scenarios, discussing which elements would be involved for that use case, and walking 
-through the configuration process. After compiling all the possible paths through the 
-interface, researchers performed feature inspection, listing sequences of features used 
-to accomplish typical tasks and taking note of long sequences or cumbersome
-steps. In addition, we performed a heuristic evaluation to mark
-likely causes of confusion for users during our study.
+{\color {blue}
+Short intro sentence. 
+}
+
+\subsection{Procedure} 
+{\color {blue}
+David and I sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom.
+}
+
+\subsection{Observations}
+{\color {blue}
+Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.
+
+A short paragraph with 1-3 observations--using a non-leading tone! 
 }

### 2016-10-21 pets2017-paper/pets2017-paper.tex
delete weird thing I added.
re-outlined first results section

@@
 \item {\bfseries Success rate:} what percentage of users eventually connect to Tor in a given condition. 
-\item {\bfseries Error rate:} what percentage of user attempts could not connect to Tor. 
 \item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
@@
 \subsection{Results} 
-{\color {red}
-We discuss six common challenges our participants encountered during the configuration process.
-Participant quotations come from live transcription during the post-experiment interview
-and are not necessarily verbatim.\\
-
-\begin{description}
-\item {\bfseries Users did not understand what proxies, bridges, and pluggable transports were.}
-Most participants, including those pre-screened for high technical ability and previous experience with Tor, were not familiar with the vocabulary.
-
-\smallskip
+{\color {blue}
+We give a summary of all participants here!  Quotations come from live transcription and are not necessarily verbatim.
+
+Observations in E1:
+
+Observations in E2:
+
+Observations in E3:
+
 \pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
-\smallskip
 \pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
-\smallskip
-
-\item {\bfseries Users did not know if they should connect directly or configure a connection.}
-Participants incorrectly determined that a blocked torproject.org website meant that Tor relays were censored, configuring bridges and proxies when they did not need to.
-Other participants tried a direct connection because they did not know what to do, but configuring their connection seemed hard.
-
-\item {\bfseries Users did not know how to choose which bridge and pluggable transport to use.}
-On the bridge configuration screen, participants were confused by the names of the bridge transports.
-The most common behavior was to configure with the recommended bridge option (obfs3).
-If the recommended one did not work, participants did not know how to choose another.
-
-\smallskip
+\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
 \pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
-\smallskip
-%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
 I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
-
-\item {\bfseries Users did not know when they are wrong.}
-Unfortunately, many mistakes did not result in error messages, but warnings that went unnoticed.
 When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
-
-\item {\bfseries Users assumed they are wrong when they are right.}
-The progress bar has a bug that causes it to update only when the level of progress increases.
-If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
+%The progress bar has a bug that causes it to update only when the level of progress increases.
+%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
 Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
-
-\smallskip
 \pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
-\smallskip
 \pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-\smallskip
-
-\item {\bfseries Users assume that proxy is required after a failed connection.}
-All of our participants who failed to connect (5 of 16) failed for this reason.
-Many mistakenly assumed that they needed a proxy upon failure, because the interface redirects to the proxy screen (the last screen) after failure.
-
-\smallskip
 \pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
-\end{description}
-
-From interviewing our participants, we found that these challenges are the result of these underlying causes: \\
-
-\begin{description}
-\item {\bfseries Users do not know how to connect to Tor.} Participants did not know the difference between a direct connection and an indirect connection to the Tor network or the difference among bridges, pluggable transports, and proxies.
-Participants did not know how to configure these network components without explicit additional instructions.
-\item {\bfseries Feedback is too technical, missing, or misleading.} Participants did not know when they failed, since certain mistakes do not trigger error warnings or timeouts (i.e.
-a syntactically correct but invalid proxy).
-If participants did see an error message, they did not understand it.
-The progress bar bug also caused users to wrongly assume they were not making progress since it did not give feedback on subsequent attempts.
-\item {\bfseries Users do not understand censorship circumvention cues.} With enough technical background, there are  signals to what components are necessary and unnecessary.
-A connection to the Internet indicates that no proxy is required.
-A failed direct connection indicates a blocked Tor relay.
-A failed hard-coded bridge connection indicates a blocked bridge relay.
-However, the average user does not understand these signals.
-\end{description}
 

### 2016-10-21 pets2017-paper/pets2017-paper.tex
finish evaluation metrics section

@@
 We wanted to inspect the thing ourselves before doing formative testing so we know what to look for. 
-http://www.usabilitybok.org/heuristic-walkthrough, not a pluralistic walkthrough (http://www.usabilitybok.org/pluralistic-walkthrough) or cognitive walkthrough (http://www.usabilitybok.org/cognitive-walkthrough).
-
-%We used a combination of usability inspection methods~\cite{nielsen1994usability}
-%to prepare for the user study. Two researchers conducted a pluralistic 
-%walkthrough and stepped through various censorship
-%scenarios, discussing which elements would be involved for that use case, and walking 
-%through the configuration process. After compiling all the possible paths through the 
-%interface, researchers performed feature inspection, listing sequences of features used 
-%to accomplish typical tasks and taking note of long sequences or cumbersome
-%steps. In addition, we performed a heuristic evaluation to mark
-%likely causes of confusion for users during our study.
-
-Most usability testing involves finding and fixing problems as part of an iterative design process to make an interface more usable.
-It is typically called a Formative Usability Evaluation.
-In contrast, a Summative Usability Evaluation describes the current usability of an interface—as measured by things like task times, completion rates and satisfaction scores.
-Summative tells you how usable an interface is and formative tells you what isn't usable.
-
-Formative usability testing takes the role of a support tool for decision making during the beginning stages of the design process and - if applied early in the development process - provides valuable insights of where users have difficulty reaching their user goals with the technology (website, desktop GUI design, hardware product) or service.
+We did a heuristic walkthrough, not a pluralistic walkthrough or cognitive walkthrough. 
+%~\cite{nielsen1994usability} %inspection methods book
+%http://www.usabilitybok.org/heuristic-walkthrough
+%http://www.usabilitybok.org/pluralistic-walkthrough
+%http://www.usabilitybok.org/cognitive-walkthrough
+
+Formative usability testing is a support tool used during the beginning stages of the design process to provide insights of where users have difficulty.
+With formative user testing, it is enough to test 3–5 users.
+After the fifth user, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again.
+Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
+
 %http://www.usabilitybok.org/Formative-evaluation
 %https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/ ~\cite{howmanyusers}
-
-With formative user testing, it is enough to test 3–5 users.
-After the fifth user tests, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again.
-Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
 
@@
 
-Summative usability testing is a Quality Assurance (QA) type of test usually performed later in the development process.
-A similar usability test protocol is used as in formative usability testing but now this setup is used to do formal user acceptance testing before the product is released to the target audience.
+Summative usability testing is a quality assurance test usually performed later in the development process.
+While formative tells you what isn't usable, while summative tells you if it is usable.
 This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
@@
 
-\subsection{Evaluation Criteria}
+\subsection{Evaluation Metrics}
 \label{sec:eval}
-
-{\color {blue}
-It is easy to specify usability metrics, but hard to collect them.
-Typically, usability is measured relative to users' performance on a given set of test tasks.
-The most basic measures are based on the definition of usability as a quality metric: success rate (whether users can perform the task at all), the time a task requires, the error rate, and users' subjective satisfaction.
-%https://www.nngroup.com/articles/usability-metrics/
-%http://www.measuringu.com/blog/essential-metrics.php
-
-We chose to evaluate the two interfaces by testing them on a large number of users, using the following criteria to measure usability: \\
+Usability measures users' abilities to complete tasks. We use the following industry-standard~\cite{albert2013measuring} metrics: \\
+
 \begin{itemize}
-\item {\bfseries Success rate:} what percentage of users eventually connect to Tor in a given condition. 
+\item {\bfseries Completion rate:}  percentage of users that eventually connect to Tor in an experimental condition. 
 \item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
-\item {\bfseries Configuration time:} time from Tor Browser startup to progress screen, measures includes time spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+\item {\bfseries Configuration time:} time from Tor Browser startup to intializing a successful Tor bootstrap.
 \end{itemize}
 
-Explain reason for choosing success and time, citing sources. Explain that we made up active configuration time to measure time to completion more accurately since bootstrapping takes so long. 
-}
+Completion rate is the fundamental usability metric that measures if users can accomplish the task.
+We define success as a binary metric that is true if a user connects to Tor and false if a user does not.
+
+Task time is a supplemental usability metric that measures user productivity during the task.
+We measure task time two different ways.
+Connection time captures the amount of time users take to use the configuration interface to connect to Tor.
+This includes time users spend waiting while a Tor Browser establishes a connection to Tor, which can take minutes and potentially dominate the measurement.
+Configuration time captures the amount of time users spend configuring network components necessary to connect to Tor.
 

### 2016-10-21 pets2017-paper/pets2017-paper.tex
sketch out format of formative results, and add takeaway sections to formative and summative sections

@@
 
-\subsection{Results} 
+\subsection{Observations and Interviews} 
 {\color {blue}
@@
 Observations in E1: 
+\pquote{P1, NF}{summary of what they did. ``and a quote too.''}
+\pquote{P2, NF}{summary of what they did. ``and a quote too.''}
+\pquote{P3, NF}{summary of what they did. ``and a quote too.''}
+\pquote{P4, HT}{summary of what they did. ``and a quote too.''}
+\pquote{P5, UT}{summary of what they did. ``and a quote too.''}
 
@@
 
-The challenges users faced in the qualitative experiment and the respective underlying causes are used as feedback for redesigning the configuration interface.
+\subsection{Where Users Struggled} 
+{\color {blue}
+LIST `EM! 
+}
 
@@
 %for color red
+}
+
+\subsection{Usability of Tor Launcher} 
+{\color {blue}
+Tell people HOW usable it seemed, based on the data.  
 }

### 2016-10-21 pets2017-paper/pets2017-paper.tex
write the testing pipeline subsection

@@
 \section{Methodology} 
-
-\subsection{Testing Procedure} 
-{\color {blue}
-
-Procedure: inspection, formative, design, summative.
-
-We wanted to inspect the thing ourselves before doing formative testing so we know what to look for. 
-We did a heuristic walkthrough, not a pluralistic walkthrough or cognitive walkthrough. 
-%~\cite{nielsen1994usability} %inspection methods book
-%http://www.usabilitybok.org/heuristic-walkthrough
-%http://www.usabilitybok.org/pluralistic-walkthrough
-%http://www.usabilitybok.org/cognitive-walkthrough
-
-Formative usability testing is a support tool used during the beginning stages of the design process to provide insights of where users have difficulty.
-With formative user testing, it is enough to test 3–5 users.
-After the fifth user, you have all the insight you are likely to get and your best bet is to go back to the drawing board and improve the design so that you can test it again.
-Testing more than five users wastes resources, reducing the number of design iterations and compromising the final design quality.
-
-%http://www.usabilitybok.org/Formative-evaluation
-%https://www.nngroup.com/articles/why-you-only-need-to-test-with-5-users/ ~\cite{howmanyusers}
-
-We wanted to try an anternative interface to see if we can make any improvements.
-We wanted to, since we had all this testing!
-But we can also test the original design in a formative and summative way.
-
-Summative usability testing is a quality assurance test usually performed later in the development process.
-While formative tells you what isn't usable, while summative tells you if it is usable.
-This works on the assumption that the design direction is the right one and that there is potential for a usable solution, and thus the summative usability testing determines whether the execution actually delivers on that promise.
-%http://www.usabilitybok.org/Summative-evaluation
-%https://www.nngroup.com/articles/quantitative-studies-how-many-users/
-%~\cite{summative}
-}
+This section talks about our process, principles, and preparations for evaluating the configuration interface.
+
+\subsection{Testing Pipeline} 
+Two researchers first performed a cognitive walkthough~\cite{cognitive-walkthrough} to prepare for user testing.
+A cognitive walkthough is evaluation method in which usability evaluators and product experts work through a series of tasks from the perspective of the user to understand a system's learnability for new or infrequent users.
+
+We then conducted a formative usability test~\cite{formative} that found where and why users have difficulty.
+Formative usability testing is a support tool designed to gain insight into how the design can be improved.
+5 users is considered to be user testing's maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited for 5 participants in each experimental condition.
+
+Formative testing is usually used as feedback for design iterations.
+We opportunistically used our observations to make design changes to the configuration interface.
+We believed that the process of a identifying design principles, proposing design changes, and showing an alternative interface was insightful in itself---and had the potential to discover impactful changes.
+
+We concluded with a summative usability test~\cite{summative} that determined the usability of an interface.
+We test the current interface to evaluate it and test the redesigned interface to see if our design changes had impact.
+Summative usability testing is a qualtiy assurance tool designed to test features in a design.
+In short, formative usability tells you what isn't usable, while summative usability testing tells you if it is usable.
+20 users is considered to be the minimum number to statistically significant measurments~\cite{howmanyusers}, so we recruited for 20 participants in each experimental condition.
 

### 2016-10-21 pets2017-paper/pets2017-paper.tex
minor wording tweaks

@@
 \label{sec:background}
-This section talks about network components involved in connecting to Tor, network conditions that require these network components, and examples of what users must currently do to connect to Tor.
+This section discusses network components involved in connecting to Tor, network conditions that require these network components, and the set of valid ways to connect to Tor.
 
@@
 
-For our experiments, we use instrumented versions of Tor Browser~5.0.3, 
+For our experiments, we use versions of Tor Browser~5.0.3, 
 the most recent stable release at the time~\cite{torbrowser-503}.

### 2016-10-24 pets2017-paper/pets2017-paper.tex
word tweaks and tense corrections throughout methodology section.

@@
 We concluded with a summative usability test~\cite{summative} that determined the usability of an interface.
-We test the current interface to evaluate it and test the redesigned interface to see if our design changes had impact.
-Summative usability testing is a qualtiy assurance tool designed to test features in a design.
-In short, formative usability tells you what isn't usable, while summative usability testing tells you if it is usable.
+We test the current interface to evaluate it.
+Opportunistically, we also test the redesigned interface as well.
+Summative usability testing is a quality assurance tool designed to test features in a design.
+In short, formative testing tells you {\it what} is or is not usable, while summative testing testing tells you {\it if} it is or is not usable.
 20 users is considered to be the minimum number to statistically significant measurments~\cite{howmanyusers}, so we recruited for 20 participants in each experimental condition.
@@
 Completion rate is the fundamental usability metric that measures if users can accomplish the task.
-We define success as a binary metric that is true if a user connects to Tor and false if a user does not.
+We defined success as a binary metric that is true if a user connected to Tor and false if a user did not.
 
 Task time is a supplemental usability metric that measures user productivity during the task.
-We measure task time two different ways.
-Connection time captures the amount of time users take to use the configuration interface to connect to Tor.
-This includes time users spend waiting while a Tor Browser establishes a connection to Tor, which can take minutes and potentially dominate the measurement.
-Configuration time captures the amount of time users spend configuring network components necessary to connect to Tor.
+We measured task time two different ways.
+Connection time captured the amount of time users take to use the configuration interface to connect to Tor.
+This included time users spent waiting while a Tor Browser establishes a connection to Tor, which can potentially dominate the measurement.
+Configuration time captured the amount of time users spent configuring network components necessary to connect to Tor.
 
@@
 
-The simulated environments are not intended to imitate any particular country's censorship environment. However, they were designed so that they would require similar configurations
-to make a connection to Tor.
-For instance, E3 does not block the same websites, public Tor relays, or Tor protocols that China would, but similarly requires a bridge that runs a specific type of transport to connect to Tor.
-We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we want to test.
-Table~\ref{tab:environments} summarizes our
-environments and what network components are required to make a 
-connection to Tor.
+The simulated environments are not intended to imitate any particular country's censorship environment. Rather, they were designed to require particular network configurations
+to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we wanted to test.
+Table~\ref{tab:environments} summarizes our environments and what network components are required to make a  connection to Tor.
 
@@
 Though there were new releases during the experiments,
-we used the same version across all participants to not introduce
+we used the same version throughout to not introduce
 confounding factors.

### 2016-10-24 pets2017-paper/pets2017-paper.tex
hash out inspection section

@@
 {\color {blue}
-David and I sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom.
+David and I (1 security/tor person and 1 usable security researcher) sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom.
+Along the way, we discussed when a certain option would need to be used, if the option seemed visible or helpful, and other things like that.
 }
@@
 {\color {blue}
-Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.
+Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.  Appendix ~\ref{states}, Figure~\ref{fig:digraph}.
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{tor-digraph.png}
+\caption{
+caption here. give example of e12,s2,e12',s2' refer to appendix for the list of all errors. 
+% e12; selected proxy type, good address syntax, good ip address, blank port (bridge) 
+% s2; selected proxy type, good address syntax, good ip address, blank port (bridge)
+% e12'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
+% s2'; selected proxy type, good address syntax, good ip address, blank port (no bridge) 
+}
+\label{fig:digraph}
+\end{figure*}
 
 A short paragraph with 1-3 observations--using a non-leading tone!
+1) most of this is only for the censorship use case 2) this assumed a level of technical familiarity in the user 3) lots of places where users can mess up--just look at the number of end states.
 }
@@
 \appendix
+
+\section{Success and Error States in Tor Launcher 5.0.3} 
+\label{states} 
+{\color {blue} 
+success states: 
+\begin{itemize}
+\item s0: no bridge no proxy connection.
+\item s1: bridge, no proxy connection.
+\item s2: bridge and proxy connection (correct proxy syntax and with default port)
+\item s3: bridge and proxy connection (correct proxy syntax and with specified port)
+\end{itemize}
+
+error states:
+\begin{itemize} 
+\item e0: custom bridge: field left blank
+\item e1: custom bridge: syntax error
+\item e2: custom bridge: good syntax, bad ip address
+\item e3: hardcoded bridge: bridge blocked in country
+\item e4: bridge blocked in country
+\item e5: blank proxy input
+\item e6: no proxy type
+\item e7: selected proxy type, bad address syntax
+\item e8: selected proxy type, good address syntax, bad ip address, blank port
+\item e9: selected proxy type, good address syntax, bad ip address, good port
+\item e10: selected proxy type, good address syntax, bad ip address, bad port
+\item e11: selected proxy type, good address syntax, good ip address, bad port
+\item e12: selected proxy type, good address syntax, good ip address, blank port
+\end{itemize} 
+}
+
 \section{Alternative Approaches} 

### 2016-10-24 pets2017-paper/pets2017-paper.tex
delete unused old text

@@
 \subsection{Connecting to Tor} 
-
-%\begin{itemize}
-%	\item{Whether their Internet connection is censored} 
-%	\item{Whether the Tor network is censored by their ISP}
-%	\item{Which hard-coded bridges work in their country} 
-%	\item{If no hard-coded bridges work, how to get a custom bridge and connect to it} 
-%	\item{Whether a proxy is required to access the Internet}
-%	\item{If a proxy is required, and if so, the proxy settings}
-%\end{itemize}
-
 Configuring a bridge requires providing one or more

### 2016-10-24 pets2017-paper/pets2017-paper.tex
hash out design procedure

@@
 {\color {blue}
-Talk about iteration and how we designed it here.
+We had 1 security researcher, 2 usable security researchers, and 1 UI designer.
+All the researchers watched the videos, that they have not seen.
+The researchers talked about the observations from the formative study, then discussed the design principles that we wanted to follow, what the goals of this re-design was, and then and brainstormed ideas on how to make things better.
+We caught up the designer and summarized what had happened, giving him access to the videos, interviews, and resources.
+We went back and forth on iteratively mocking up wireframes and clickable prototypes until we found one that we thought might be a good shot.
+A goal of this was to discover some changes to push to the current interface.
 }

### 2016-10-24 pets2017-paper/pets2017-paper.tex
finish writing inspection section

@@
 \section{Methodology} 
-This section talks about our process, principles, and preparations for evaluating the configuration interface.
+This section discusses our process, principles, and preparations for evaluating the configuration interface.
 
@@
 \subsection{Experimental Setup}
+\label{sec:environments}
 We simulated three environments (which we refer to as E1, E2, and E3), 
-which are in the order of increasing severity in censorship. We chose to 
+which are in the order of increasing severity in censorship.
+Table~\ref{tab:environments} summarizes our environments and what network components are required to make a  connection to Tor.
+We chose to
 simulate environments for the stability, reproducibility, and simplicity of the 
 experiment, as real censored networks are voilatile, subject to change, and complex.
-
-The simulated environments are not intended to imitate any particular country's censorship environment. Rather, they were designed to require particular network configurations
-to connect to Tor.
-We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we wanted to test.
-Table~\ref{tab:environments} summarizes our environments and what network components are required to make a  connection to Tor.
-
-We used features of the Windows operating system 
-to block websites and Tor relays. 
-We added entries to the hosts file to
-mapping domain names to the address 127.0.0.1, which simulated
-website by using Tor.
-We blocked torproject.org and its respective subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers (E1, E2, E3).
-We blocked wikipedia.org, cnn.com, and their respective subdomains to create an artificial task to visit a
-``censored'' website as motivation to connect to Tor during the experiment (E1, E2, E3). 
-We specified Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3).
-
-For our experiments, we use versions of Tor Browser~5.0.3, 
-the most recent stable release at the time~\cite{torbrowser-503}.
-Though there were new releases during the experiments,
-we used the same version throughout to not introduce
-confounding factors.
 
@@
 
+The simulated environments are not intended to imitate any particular country's censorship environment. Rather, they were designed to require particular network configurations
+to connect to Tor. We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we wanted to test.
+
+We used features of the Windows operating system 
+to block websites and Tor relays. 
+We added entries to the hosts file to
+mapping domain names to the address 127.0.0.1, which simulated
+website by using Tor.
+We blocked torproject.org and its respective subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers (E1, E2, E3).
+We blocked wikipedia.org, cnn.com, and their respective subdomains to create an artificial task to visit a
+``censored'' website as motivation to connect to Tor during the experiment (E1, E2, E3). 
+We specified Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3).
+
+For our experiments, we use versions of Tor Browser~5.0.3, 
+the most recent stable release at the time~\cite{torbrowser-503}.
+Though there were new releases during the experiments,
+we used the same version throughout to not introduce
+confounding factors.
+
 \section{Usability Inspection}
-{\color {blue}
-Short intro sentence. 
-}
+This section discusses our inspection of the configuration interface and the resulting observations.
 
 \subsection{Procedure} 
-{\color {blue}
-David and I (1 security/tor person and 1 usable security researcher) sat down in the same room, started from the first screen, and tried to toggle every single path in a systematic way, usually going with the default option first if any, then working from top to bottom.
-Along the way, we discussed when a certain option would need to be used, if the option seemed visible or helpful, and other things like that.
-}
+Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time.
+We then systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
+
+We first examined tasks required, inputs taken, and consequences of possible actions on each screeen to map all potential paths through the interface (Figure~\ref{fig:digraph}).
+We then stepped through each user path, systematically toggling all actions and inputs.
 
 \subsection{Observations}
-{\color {blue}
-Quick refer to the digraph, and explain everything in the caption. Put end states in the appendix (if it doesn't fit in the caption.  Appendix ~\ref{states}, Figure~\ref{fig:digraph}.
+Through this process, we observed that:  \\
+\begin{itemize} 
+\item The interface does not presuppose that a user has previous exposure to Tor. 
+\item The interface provides recommendations in text and populates options with recommended settings. 
+\item The user has the burden of determining if Tor relays are blocked or if a proxy is required. 
+\item A user can optionally configure a bridge and proxy even if they are not necessary to connect to Tor. 
+\item Free-form inputs lead to many potential error states. 
+\end{itemize}
+
+We used the map of potential user paths (Figure~\ref{fig:digraph}) to design our simulated environments (section~\ref{sec:environments}).
+We used our walkthrough observations as inspiration for drafting our post-experiment interview questions (Appendix~\ref{interview-questions}) for formative usability testing.
 
@@
 \caption{
-caption here. give example of e12,s2,e12',s2' refer to appendix for the list of all errors. 
-% e12; selected proxy type, good address syntax, good ip address, blank port (bridge) 
-% s2; selected proxy type, good address syntax, good ip address, blank port (bridge)
-% e12'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
-% s2'; selected proxy type, good address syntax, good ip address, blank port (no bridge) 
+A digraph illustrating the potential user paths through the interface.
+Non-leaf nodes are screens in the user interface (start, bridge 1, bridge 2, proxy 1, proxy 2, and progress).
+Leaf nodes are various end states (quit, success, or error).
+Tansitions between these nodes denote user actions.
+For details of each end state, see Appendix ~\ref{states}.
 }
@@
 \end{figure*}
-
-A short paragraph with 1-3 observations--using a non-leading tone!
-1) most of this is only for the censorship use case 2) this assumed a level of technical familiarity in the user 3) lots of places where users can mess up--just look at the number of end states.
-}
 
@@
 {\color {blue} 
+A reminder of the digraph, and a reference (Figure~\ref{digraph}). Give an example of one input leading to many end states.
+
+% e12; selected proxy type, good address syntax, good ip address, blank port (bridge) 
+% s2; selected proxy type, good address syntax, good ip address, blank port (bridge)
+% e12'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
+% s2'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
+
 success states: 

### 2016-10-24 pets2017-paper/pets2017-paper.tex
introductory sentences for sections.

@@
 \label{sec:background}
-This section discusses network components involved in connecting to Tor, network conditions that require these network components, and the set of valid ways to connect to Tor.
+This section discusses network components involved in connecting to Tor, network conditions that require specific network components, and how to configure the involved network components.
 
@@
 \label{sec:qualitative}
-
-{\color {blue}
-short intro sentence
-}
+This section discusses our small-scale, qualitative usability evaluation and resulting user insights.
+
 \subsection{Recruitment}
@@
 \label{sec:design} 
-
-{\color {blue}
-Introductory sentence.
-}
+This section discusses how we converted our formative usability testing observations into design changes.
 
@@
 \label{sec:quantitative}
-
-{\color {blue} 
-short intro sentence.
-}
+This section discusses our large-scale quantitative usability evaluation and resulting user measurements.
 

### 2016-10-24 pets2017-paper/pets2017-paper.tex
word fixes.

@@
 We test the current interface to evaluate it.
-Opportunistically, we also test the redesigned interface as well.
+We also opportunistically test the redesigned interface.
 Summative usability testing is a quality assurance tool designed to test features in a design.
@@
 
-We first examined tasks required, inputs taken, and consequences of possible actions on each screeen to map all potential paths through the interface (Figure~\ref{fig:digraph}).
-We then stepped through each user path, systematically toggling all actions and inputs.
+We first examined each screen in the interface for tasks required, inputs taken, and consequences of possible actions.
+This was done to map all potential paths through the interface (Figure~\ref{fig:digraph}).
+We then stepped through each user path and recorded our observations.
 

### 2016-10-24 pets2017-paper/pets2017-paper.tex
small word optimizations.

@@
 \label{sec:qualitative}
-This section discusses our small-scale, qualitative usability evaluation and resulting user insights.
+This section discusses our small-scale, qualitative usability experiment and resulting user insights.
 
@@
 On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment.
-Before each participant entered the room, we ran a script on the computer that simulated E1, E2, or E3 and started the video recording.
+Before each participant entered the room, we ran a script on the computer that
+set up one of the three simulated environments (E1, E2, or E3) and started the screen recording.
 
@@
 \label{sec:quantitative}
-This section discusses our large-scale quantitative usability evaluation and resulting user measurements.
+This section discusses our large-scale quantitative usability experiment and resulting user measurements.
 
@@
 \subsection{Setup}
-We ran our experiment at <Redacted lab>, an experimental social science laboratory for behavioral experiments.
+We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments.
 The testing room had 36 workstations with identical Windows~7 laptops.
@@
 
-Before each session, we ran a script that downloaded the necessary software, set up one of the six experimental conditions, and start the video recording.
-Each computer was manually assigned an interface-environment combination in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
-In contrast to the previous usability test, we installed an instrumented version of Tor Browser 5.0.3 or an instrumented version of Tor Browser 5.0.3.
-with a redesigned configuration interface.
-The instrumentation in the interface logged user interactions such as window transitions, mouse clicks, and menu selections.
-Similarly to the previous usability test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment.
+Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and start the video recording.
+In contrast to the previous test, we installed an instrumented versions of Tor Browser 5.0.3.
+The instrumentation logged user interactions, such as window transitions, mouse clicks, and menu selections.
+Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment.
+Each computer was manually assigned one of the six interface-environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
 

### 2016-10-24 pets2017-paper/pets2017-paper.tex
formative procedure rewriting

@@
 \subsection{Procedure}
-{\color {blue}
-When a participant entered the room, researchers informed them of purpose of the study, data collected, and associated risks. 
-A researcher informed the participant of the simulated censorship environment and
-instruct them to visit sample blocked and unblocked websites
-in a standard browser (Appendix~\ref{qualitative-script}). 
-This shows participants what a blocked site looks like in a browser. 
-Then, the participant was asked to complete a worksheet that gives information
-on their censorship environment and instructed them
-to visit one blocked website and one non-blocked website (Appendix~\ref{participant-worksheet}).
-The worksheet informed the participant that the network is censored,
-but did not give details of what services and websites are specifically blocked.
-Participants were able to visit the unblocked website using any familiar browser,
-but had to configure Tor Browser in order to visit the blocked website.
-
-For the blocked website, we used the main page of Wikipedia,
-and for the unblocked site we used the CNN homepage.
-We chose these two sites because of their likely familiarity to web users;
-our goal was to evaluate the user interface, not to test users with a browsing task.
-After instructions, the researchers stepped out of the room.There was no interaction
-between the participant and researcher for the rest of the session.
-Researchers watched a live video of each participant's screen from another room
-and saved the videos for review.
-
-Participants had an average of 45 minutes to complete their worksheet. 
-After participants completed the browsing tasks or ran out of time,
-we interviewed them about their experience and
-took notes of the questions and answers.
-We asked questions asking about their general experience, 
-interface features they found confusing, and feedback for improvements (Appendix~\ref{interview-questions}). 
-We followed up with specific questions prompted from watching their screen. 
-This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
+Before the experiment began, each participant was verbally informed of the purpose of the 
+study, what data was collected, and any associated risks. If they wished to participate,
+they were informed again in writing and consented by signing the document. To be thorough, 
+we clarified verbally that they could stop at any time during the experiment with no negative consequences.
+
+The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}).
+This purpose of this introduction was to ensure that the main task
+was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
+We instructed them to visit a blocked and unblocked website
+in a non-Tor browser to clarify that the Internet was functioning as expected. 
+We then told them to use Tor Browser to visit a censored site and pointed out 
+the respective shortcut on their desktop.
+
+We then asked them to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
+required answers from one blocked website (Wikipedia) and one non-blocked website (CNN).
+The worksheet did not specify which website was censored. 
+We chose these websites because they are popular websites and that their likely familiarity 
+would make the task seem less intimidating.
+
+Participants were given 45 minutes to complete their worksheet. 
+After instructions, the researchers left and watched a live feed of the participants' screen in another room to minimize interactions.
+
+After participants completed the browsing tasks (or ran out of time),
+we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses.
+We then followed up with participant-specific questions to verify any hypotheses we had from observation (e.g.
+``the participant was selecting bridges at random'').
 We paid each participant~\$30 for their time.
-}
 

### 2016-10-24 pets2017-paper/pets2017-paper.tex
summative procedure rewrite

@@
 \subsection{Procedure}
-{\color {blue} 
 Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random.
-When all participants sat at their respective computers,
-
-With only the consenting participants remaining, one of the researchers then read from a script that details the experiment, task, and data collected (Appendix~\ref{quantitative-script}).
-We told users of the simulated censorship environment, that Tor Browser can be used to circumvent censorship, and that we ask them to use Tor Browser to circumvent our simulated censorship.
-We ask users to complete a worksheet, which asks questions that can only be answered by going to the censored websites.
-To mirror the qualitative study, we chose Wikipedia's featured article of the day as the blocked website to visit on their worksheet.
-All users were instructed to sit until the end of the experiment, regardless of when they had completed their task.
-We remind them again that their screens are being recorded and to not show any personal information, such checking email.
-We give users a chance to ask any questions about the experiment or task.
-
+Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks.
+If they wished to participate, they were ifnormed again in writing and consented by signing the document.
+To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.
+
+The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvnt censorship (Appendix~\ref{quantitative-script}).
+This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so.
+Before participants started their tasks, we reminded them that their screens are being recorded so they should not log into anything that shows personal information.
+We gave users a chance to ask any questions about the experiment or task.
+
+Participants were given 40 minutes to complete the task.
 After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions.
-Participants had 40 minutes to complete the task.
-After the 40 minutes, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}) and were paid \$30 for their time.
-}
+Afterward, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}).
+We paid each participant \$30 for their time.
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
add a placeholder image to show old interface screens, and refer to it in text.

@@
 \subsection{Procedure} 
-Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time.
-We then systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
+Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
+We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
 
@@
 We then stepped through each user path and recorded our observations.
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
+\caption{
+A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
+}
+\label{fig:old-interface}
+\end{figure*}
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
add number of researchers involved in formative testing

@@
 \subsection{Procedure}
+Three researchers ran the formative usability testing, with each session having at least two researchers.  
 Before the experiment began, each participant was verbally informed of the purpose of the 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
write the design procedure subsection, refer to placeholder image of redesigned interface screens

@@
 \subsection{Procedure} 
-{\color {blue}
-We had 1 security researcher, 2 usable security researchers, and 1 UI designer.
-All the researchers watched the videos, that they have not seen.
-The researchers talked about the observations from the formative study, then discussed the design principles that we wanted to follow, what the goals of this re-design was, and then and brainstormed ideas on how to make things better.
-We caught up the designer and summarized what had happened, giving him access to the videos, interviews, and resources.
-We went back and forth on iteratively mocking up wireframes and clickable prototypes until we found one that we thought might be a good shot.
-A goal of this was to discover some changes to push to the current interface.
-}
+Three researchers agreed on security and usability design principles. 
+We then rewatched screen capture videos and read interview transcirptions to brainstorm design changes.
+We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind.
+Figure~\ref{fig:new-interface} shows our redesign of the interface.
+
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
+\caption{
+A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
+}
+\label{fig:new-interface}
+\end{figure*}
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
rough pass through summative section

@@
 \subsection{Results} 
-{\color {red} 
-The possible interface version and environment combinations resulted in 6 experimental conditions.
-We recruited 124 participants to aim for about 20 participants per condition.
-We filtered participants who downloaded their own version of Tor Browser or did not sign the consent form, resulting in 114 participants.
+{\color {blue} 
+124 people participated in our experiment , but use data from 114 of them.
+We filtered participants who made errors in completing the consent form, downloaded their own version of Tor Browser, or did not interact with the interface.
 Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
 Appendix~\ref{all-participant-edges}'s Fig.~\ref{fig:all-participant-edges} summarizes invididual participants' actions throughout the experiment.
-
-%We refreshed a list of Tor relay IP addresses and added them
-%to a firewall blacklist before each session.
-%In the first study, we neglected to block the IP addresses
-%of the Tor directory authorities, which are the first hosts
-%a client contacts when initiating a non-bridge connection.
-%New relays also appeared in the network on an hourly basis,
-%which enabled a small number of participants to succeed with
-%a direct connection when that configuration should have failed.
-%We believe this is acceptable because 
-%the qualitative user study was not used to quantify failures or successes, 
-%but to explore possible problems.
-%We fixed this problem in our quantitative user study by blocking the directory authorities.
-
-%We blocked en.wikipedia.org, the target of the experiment,
-%as well as other language-specific subdomains such as
-%de.wikipedia.org and fr.wikipedia.org.
-%We neglected, however, to block the Simple English Wikipedia
-%at simple.wikipedia.org, which one participant found,
-%thinking they had completed the task.
-%% E2-OLD-X04-20160330-181928
-
-%We discarded data on participants who chose to download their own version of Tor Browser online.
-5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version.
-
-%Many waited for minutes at the progress screen, but never saw an error message.
-Error messages are intended to appear after a timeout.
-There were warnings, but those warnings went largely unnoticed by our participants.
-Across both versions of the interface, only one participant ever saw an error message.
-We tried to make error messages more instructive and understandable, since participants in our experiment did not encounter error messages, we cannot evaluate them.
+}
 
@@
 \centering
-\input{participant-summary.tex}
+\begin{tabular}{l r r r r r}
+& \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
+& \multicolumn{2}{r}{(at 40 minutes)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
+\noalign{\hrule}
+E1-NEW & 19/19 & 100\% & 0:20 & 0:06 \\
+E1-OLD & 19/19 & 100\% & 1:01 & 0:24 \\
+E2-NEW & 18/18 & 100\% & 3:22 & 0:40 \\
+E2-OLD & 16/19 & 84\% & 5:00 & 2:04 \\
+E3-NEW & 13/19 & 68\% & 20:25 & 1:56 \\
+E3-OLD & 10/20 & 50\% & 40:08 & 9:09 \\
+\end{tabular}
 \caption{
@@
 
-\subsubsection{Rate of Success} 
-49 of 56 (88\%) participants with the new interface successfully connected to Tor, while 45 of 58 (78\%) participants with the old interface did.
-Due to the limited number of participants, this difference is not large enough to rule out the possibility of random chance being the cause for the difference.
-Appendix~\ref{stat-tests} details the methodology for the statistical tests used in this paper.
-
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=.5\textwidth]{warning.png}
-%\caption{
-%A screenshot of the interface with the ``Copy Tor Log to Clipboard'' button, 
-%which appears silently and does not interrupt the progress bar. 
-%This warning was generated by entering in syntactically correct but invalid proxy settings,
-%a mistake that prevents users from ever connecting to the Tor network. 
-%Users are never directly notified of this error through an error message or a timeout message.
-%Our participants made this error during our experiments, along with others that they were not notified about. 
-%}
-%\label{fig:warning}
-%\end{figure}
-
-%\begin{figure}[t]
-%\centering
-%\includegraphics[width=.5\textwidth]{log-messages.png}
-%\caption{
-%The last 24 of 45 log lines that users receive after clicking clicking the ``Copy Tor Log to Clipboard'' button. 
-%These log lines were the result of entering in syntactically correct but invalid proxy settings,
-%a mistake that prevents users from ever connecting to the Tor network. Understanding the Tor logs require
-%technical expertise from the user to understand the logs, diagnose the problem, and formulate next steps.
-%}
-%\label{fig:warning_log}
-%\end{figure}
-
-%We believe that the added advice on what to try next on error messages would have improved the rate of success.
-However, only 1 of 116 participants saw an error during the experiment.
-The old interface warned users on some mistakes (i.e.
-entering in a syntactically correct but invalid proxy settings) rather than displaying an error message.
-When a user receives a warning, a button that says ``Copy Tor Log to Clipboard'' silently appears at the bottom of the interface (Figure~\ref{fig:warning}).
-To see the log messages, users must click on the button, open up a text editor, and paste the log messages.
-The log messages require the user to understand the log, diagnose the problem, and formulate next steps (Figure~\ref{fig:warning_log}).
-
-%The addition of a summary screen did cause behavioral changes (13\% of participants saw their current settings, then went back and adjusted them), but this behavioral change did not have a statistically significant impact on success rates.
-
-We added preemptive advice to the bridge configuration screen to first try an obfs3 bridge and then a meek bridge, but we suspect that most participants did not benefit from this advice since participants did not think to adjust their bridge settings upon failure.
-Of the 75 participants that failed to connect on the first attempt, 15 participants with the new interface and 13 participants with the old interface went back to the bridge screen and chose another hard-coded bridge.
-10 of 15 in the new interface chose a meek bridge as their next bridge whereas 5 of 13 in the old interface chose meek as their next bridge, but we cannot claim choosing meek bridges is a direct result of our advice.
-
-Table~\ref{tab:attempts-bridge-proxy} shows the configuration settings of the first successful connection in each environment and interface combination.We only consider the first successful connection since many of our curious participants tried many different settings to investigate if they will work, even after they had completed the task.
-Recall E1 does not require users to configure a bridge, E2 requires users to configure any bridge, and E3 requires users to configure a meek or custom bridge.
-Note that only four of the hard-coded bridges were used to connect successfully for the first attempt were the recommended bridge and the required bridges to succeed in E3.
-
-Our participants did not optionally configure a bridge in E1 or configure a non-recommended bridge in E2.
-This suggests that users will not configure optional components or deviate from the recommended settings unless necessary.
-If the intent of the recommendation is to get as many users as possible to use the recommended bridge, this is a positive result.
-If the intent of the recommendation is to give pointers when users are stuck but allow the users to make their own bridge choices to diversify active transports, this is a negative result.
-
-Only two participants chose to configure a custom bridge.
-Both of these participants sent an incorrectly formatted request to the automatic bridge responder, which did not reply with custom bridges as a result.
-These two participants failed to connect to the Tor network.
-
-\begin{table}
+\label{all-participant-edges} 
+\begin{figure*}
+\centering
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges}
+\caption{
+Summary of participants' actions throughout the entire experiment.
+Different colors indicate which screen was shown at each moment.
+The ``not running'' times are those when Tor Launcher was closed;
+i.e., a participant was doing something else
+such as searching the web in another browser.
+The overall length of the lines show the total time to completion,
+except for those we cut off after approximately 40 minutes.
+}
+\label{fig:all-participant-edges}
+\end{figure*}
+
+\subsubsection{Completion Rate} 
+{\color {blue} 
+Completion rate was defined as the percentage of users that eventually connect to Tor in an experimental condition.
+Table~\ref{table:participant-summary} summarizes the completion rates and Table~\ref{tab:attempts-bridge-proxy} shows the configuration for users' first successful connection.
+We only conside the first successful configuration, as some curious participants investigated other solutions even after completing their task.
+
+% failure observations
+63\% (72 of 114) of first attempts to connect failed and (363 of 458) of total attempts to connect failed.
+17\% (19 of 114) of participants were not able to successfully connect to Tor.
+Specifically, Five (P73, P75, P89, P91, P106, P110) tried a direct connection; when it failed, they assumed there was something wrong with their computer, network settings, or the Tor network.
+Five (P90, P93, P108, P111, P114) tried a direct connection, a default obfs3 bridge connection, then failed.
+Five (P74, P92, P105, P107, P113) assumed that they needed a proxy when they needed another bridge.
+Two (P94, P109) tried to get custom bridges but failed to format the message correctly to get a response.
+%We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment.
+
+%success rate and version
+Our interface changes did not have a significant impact on completion rates (Pearson's Chi-squared; $X^2 = 0.0126$, $df = 2$, $p = 0.994$).
+That is, the differences in completion rates of E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+}
+
+\begin{table}[t]
 \centering
@@
 as the proxy setting.
+%Our participants did not optionally configure a bridge in E1 or configure a non-recommended bridge in E2. 
+%we cannot claim choosing meek bridges is a direct result of our advice.
+%Recall E1 does not require users to configure a bridge, E2 requires users to configure any bridge, and E3 requires users to configure a meek or custom bridge.
+Note that only four of the hard-coded bridges were used to connect successfully for the first attempt were the recommended bridge and the required bridges to succeed in E3.
 }
@@
 
-% Is this the right place for this? 
-% GENERAL STUFF; SHORTEN THIS A LOT
-{\color {red} 
-Additional stuff we found out through a combination of log processing (i.e. configuration settings on attempts) and video observation (i.e. watching what they searched for online).
-
-How people succeeded. Straightforward.
-
-How people failed-- 17\% (19 of 114) of participants were not able to successfully connect to Tor.
-63\% (72 of 114) of first attempts to connect failed and (363 of 458) of total attempts to connect failed.
-\\
-
-\begin{description}
-\item {\bfseries Some people won't try other options (6/19).} P73, P75, P89, P91, P106, P110 tried a direct connection.
-When that failed, they tried the same option, over and over, no matter how many times they failed.
-It was common to restart the interface, check Internet settings, and wait between subsequent attempts.
-
-\item {\bfseries Recommendations work, but one and done (5/19).} P90, P93, P108, P111, P114, who were in E3, did not know what to do next after a direct connection and a default obfs3 bridge connection.
-They often tried those configurations again or gave up.
-
-\item {\bfseries People don't know what their problem is (5/19).} P74, P92, P105, P107, P113 assumed that they needed a proxy.
-They spent their time trying to configure a proxy, usually without trying other bridges.
-
-\item {\bfseries Bridges auto-responder is hard to use (2/19).} P94, P109, who were in E3, emailed the bridges auto-responder to get custom bridges.
-However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{custom}).
-\end{description}
-}
-
-\subsubsection{Time to Success} 
-Time to success is defined as the time until the first successful connection to Tor.
+\subsubsection{Connection time} 
+{\color {blue} 
+Connection time is the time from Tor Browser starup to the first successful Tor bootstrap.
 Non-finishing participants are assigned the maximum experiment time of 40:08.
-Our changes to the interface had a significant impact in reducing the time participants took to successfully connect to Tor (Mann--Whitney $Z = -1.84$, $p = 0.0328$, $r= 0.172$; see Appendix~\ref{stat-tests}).
+Table~\ref{table:participant-summary} summarizes the median connection times while Figure~\ref{fig:time_to_success_clamped} shows their distribution.
+Figure ~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
+
+%time observations (how long people took)
 The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
-Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_clamped} shows their distribution.
+The longer the time went on, the less likely that the participants were going to figure it out.
+
+%time to success and version
+Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+That is, the differences in mean connection times in E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).
+}
 
@@
 \end{figure}
-
-In our experiment, participants had 40 minutes to circumvent censorship.
-Fig.~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
-In practice, faster time to completion would mean more users will succeed, since users will give up after a while.
-Users in the wild will likely not be motivated to spend 40 minutes trying to configure Tor.
-If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
-Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
-Ideally, users should be able to connect to Tor within a few minutes, regardless of their censorship environment.
-We propose ideas on how to achieve this in section~\ref{recommendations}.
 
@@
 
-\subsubsection{Active Time to Success} 
-The overall time was largely dominated by the time spent waiting to connect to Tor, rather than actively configuring the interface.
-With correct configurations, the bootstrap process can take up to two minutes.
+\subsubsection{Configuration Time} 
+{\color {blue} 
+Configuration time is the time from Tor Browser startup to initializing a successful Tor bootstrap.
+This is the connection time minus the bootstrap time, which can take up to two minutes.
+Table~\ref{table:participant-summary} shows the median configuration times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
+
+%how its calcuated 
+We believe that a more meaningful measurement of task time is the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
+Failures were 40:08 - time on progress screen.
 With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.
@@
 Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.
+
+%things to keep in mind 
+This is just a helpful metric to supplement the connection time.
+Look at E1, for instance.
+People who failed, waited, tried, and succeeded lost the progress thing when they shouldn't have.
+BUT since our error thing broke, this might be a useful metric.
+Active time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
+This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.
+
+%active time and version
+Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+That is, the differences in mean configuration times in E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed.
+}
 
@@
 
-Perhaps a more meaningful measurement is the amount of time participants actively configured their connection (Figure~\ref{fig:time_to_success_active_clamped}).
-We define active time as the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-Active time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
-This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.
-
-We performed a one-tailed Mann--Whitney test to compare the amount of active configuration time between participants who used the new interface and the participants who used the old interface.
-Our changes to the interface reduced the time participants spent configuring the interface (Mann--Whitney $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-Table~\ref{table:participant-summary} shows the median active times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
-%for color red
-}
-
 \subsection{Usability of Tor Launcher} 
 {\color {blue}
-Tell people HOW usable it seemed, based on the data.  
+%success rate 
+Not enough people got through!
+There's a steep decline between downloads and users in real life too, if you look at Tor metrics.
+Something is definitely stopping people.
+We're not saying that this is the main reason, but it certainly isn't helping.
+
+% connection and configuration time 
+Ideally, users should be able to connect to Tor within a few minutes, regardless of their censorship environment.
+Users in the wild will likely not be motivated to spend 40 minutes trying to configure Tor, and likely give up before then.
+If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
+Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
 }
@@
 
-\section{Quantitative Summary}
-\label{all-participant-edges} 
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges}
-\caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The ``not running'' times are those when Tor Launcher was closed;
-i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
-except for those we cut off after approximately 40 minutes.
-}
-\label{fig:all-participant-edges}
-\end{figure*}
-
-\section{Statistical Tests} 
-\label{stat-tests}
-{\color {red} 
-From our measurements, we observe that participants with the new interface 
-have a higher rate of success, succeed in less time, and configure their interface in less time. 
-We do not find that the increased rate of success with the new interface or the decreased time to success with the new interface significant. That is, random chance can account for the difference. 
-We do find the the decreased active configuration time to be significant. 
-We describe the methodology for the statistical tests used in this paper to determine the impact of the interface on success rate, time to success, and active time.
-
-%success rate and version
-Each participant had a boolean variable indicating a successful connection to Tor.
-Rates of success were calculated by dividing the number of participants who succeeded the condition over the total number of participants in the condition.
-This gave us six rates of success.
-E1-NEW, E2-NEW, and E3-NEW rates of success were compared against E1-OLD, E2-OLD, and E3-OLD.
-We used a Pearson's Chi-squared test to test the significance of success rates.
-The difference between success rates of participants with the new interface and participants with the old interface was not significant ($X^2 = 0.0126$, $df = 2$, $p = 0.994$).
-
-%time to success and version
-Time to success was measured as the time from the participants started the Tor launcher interface to the first successful bootstrap to the Tor network.
-This measurement was 1) non-normal and heavily right-tailed since participants were less and less likely to succeed as time went on and 2) right-censored at 40 minutes, the maximum time of the experiment.
-Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-Because the Mann--Whitney test does not account for right-censored data, we assigned the participants who did not succeed the maximum time of 40 minutes for the purpose of this test.
-We find the difference of times to success between participants with the new interface and participants with the old interface to be significant ($ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-
-%active time and version
-Active configuration time was measured as the time the participants spent in the Tor launcher interface, except for the time spent the progress screen.
-For our participants who did not succeed to connect to Tor, subtracted the time spent on the progress screen from the maximum experiment time of 40 minutes.
-This measurement was also 1) non-normal and heavily right tailed and 2) impacted by right-censored measurement of time to success.
-Because of the right-tailed nature of the data, we used a one-tailed Mann--Whitney test.
-We find the difference of active configuration times between participants with the new interface and participants with the old interface to be significant ($Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-%for color red
+\section{Alternative Approaches} 
+\label{alternatives}
+{\color {blue}
+Our goal was to deploy impactful, tested changes the Tor configuration interface.
+In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
+Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away.
+For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed.
+However, we list some alternative approaches that seem worth exploring.
+\\
+
+%remember: 	no user inputs, no network inputs, minimize info leaks
+%and:		minimal user work, full user control
+
+\begin{description}
+\item{\bfseries Automate the configuration.} The most efficient way to connect as many users to the Tor network is to automatically configure their connection on start.
+A naive automation is to try configurations that would most likely work, in order (i.e.
+a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
+This leaks to network eavesdroppers that the user is connecting to the Tor network.
+We do not know how much risk is associated with this approach.
+\item {\bfseries automate after the first failure.} The network leak happened. But then this automation would be pretty fingerprintable behavior. 
+\item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk.
+The complication with this approach is that users may not be qualified to answer if they are at risk or may not trust Tor with this information.
+\item{\bfseries Ask if users know what to do.} Another alternative to naive automation is to offer manual configuration to those that know how to configure their connection and to automate the process for users who do not know how to configure their connection.
+This may prevent the most mistakes, but does not account for the users' risk associated with using Tor.
+\item{\bfseries Suggest configurations.} A way to help users without any automation or questions is to give users information about what would work in their country.
+The first page of the configuration interface can show a list of countries with a corresponding recommended configuration.
+This approach does not require users to answer about their risk, technical ability, or location.
+However, it does require that the user trust the given advice and to correctly configure their settings based on this advice.
+\item{\bfseries Assign configurations.} This is a smart way to automate connections to the Tor network.
+Upon start, the interface detects proxy settings and uses them, if any.
+Then, all users connect to bridges that will always work (such as meek bridges), which assign them a guard relay based on their location, effectively assigning bridges for the user.
+\end{description}
+
+We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process. 
 }

### 2016-10-28 pets2017-paper/pets2017-paper.tex
refer to alternative approaches later
reword summative results intro and captions

@@
 %A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-Justify why we kept the similar interface. Refer to appendix for alternative approaches.
+Justify why we kept the similar interface.
 
@@
 \subsection{Results} 
-{\color {blue} 
-124 people participated in our experiment , but use data from 114 of them.
-We filtered participants who made errors in completing the consent form, downloaded their own version of Tor Browser, or did not interact with the interface.
-Table~\ref{table:participant-summary} summarizes the rate of success, time to success, and active time for our participants' by condition.
-Appendix~\ref{all-participant-edges}'s Fig.~\ref{fig:all-participant-edges} summarizes invididual participants' actions throughout the experiment.
-}
-
-\begin{table}
+124 people participated in our experiment, but we used data from 114.
+We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface.
+Table~\ref{table:participant-summary} gives an overview of the results, summarizing completion rate, connection time, and configuration time by condition.
+Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
+
+\begin{table}[t]
 \centering
@@
 \caption{
-A summary of participants' success in circumventing censorship
-given their simulated censorship environment and version of Tor. Those who
-failed to connect successfully were assigned the maximum time of 40:08.
+An overview of the results of the experiment. Those who
+failed to connect were assigned the maximum time of 40:08.
 }
@@
 \caption{
-Summary of participants' actions throughout the entire experiment.
-Different colors indicate which screen was shown at each moment.
-The ``not running'' times are those when Tor Launcher was closed;
-i.e., a participant was doing something else
-such as searching the web in another browser.
-The overall length of the lines show the total time to completion,
+A summary of our valid participants' paths through the interface.
+The length of the bars show the total time taken to complete the task,
 except for those we cut off after approximately 40 minutes.
+Different colors indicate which screen they were on during the experiment.
+The ``not running'' times are those when Tor Launcher was closed (
+i.e. searching for help in another browser, restarting the application, etc.).
 }
@@
 \caption{
-Bridge--proxy combinations that led to the first successful bootstrap
-in each environment and interface.
+Network components that led to the first successful bootstrap
+in each condition.
 Most E1 participants used a direct connection,
@@
 a different bridge before obfs3.
+% flashproxy, fte, fte-ipv6, obf4, and scramblesuit were not used! 
 All of the successful E3 participants but one
@@
 as the proxy setting.
-%Our participants did not optionally configure a bridge in E1 or configure a non-recommended bridge in E2. 
-%we cannot claim choosing meek bridges is a direct result of our advice.
-%Recall E1 does not require users to configure a bridge, E2 requires users to configure any bridge, and E3 requires users to configure a meek or custom bridge.
-Note that only four of the hard-coded bridges were used to connect successfully for the first attempt were the recommended bridge and the required bridges to succeed in E3.
 }
@@
 }
+
+\section{Qualitative User Study Recruitment Posting} 
+\label{qualitative-recruitment}
+We are recruiting participants for an in-person research study at <redacted>. %the University of California, Berkeley. 
+You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
+No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.
+
+\section{Qualitative User Study Prescreening Survey} 
+\label{qualitative-prescreening}
+We are recruiting participants for an in-person research study at the <redacted>. %University of California, Berkeley. 
+You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. No special knowledge and no technical experience is required.\\
+
+\begin{enumerate}
+\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
+\item{I am able to provide my own transportation to the <redacted> %University of California, Berkeley 
+campus.}
+\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
+\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
+\item{What is your gender?}
+\item{What is your age?}
+\item{Please select your highest completed (or current) level of education.}
+\item{What is your occupation?} 
+\item{Do you speak any languages other than English fluently?}
+\item{If you have a personal computer, what kind do you use?}
+\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
+\item{How often do you use the following software or features?
+\textit{<answer choices: a grid of radio buttons.
+Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption.
+Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
+\end{enumerate}
+Thank you for filling out this form. You are now done!
+
+\section{Prescreening Survey Responses}
+\label{prescreening-responses}
+{\color{blue} 
+short intro and conclusion. Take self-reported with a grain of salt, but here they are anyways.
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.5\textwidth]{self-reported-tech-familiarity.png}
+\caption{most participants reported familiarity with terms, even made up ones.}
+\end{figure}
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=.5\textwidth]{self-reported-security-use.png}
+\caption{most people didn't use many security tools.}
+\end{figure}
+}
+
+\section{Qualitative User Study Introduction Script} 
+\label{qualitative-script} 
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
+
+To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
+If you are able to reach the website, then you know that you have successfully circumvented censorship.
+Fill out the question on the worksheet.
+This isn't intended to be hard, just write what you see.
+We want to just check you saw the website.
+
+Before you start, do you have any questions about what you are asked to do?
+
+\section{Participant Worksheet Text} 
+\label{participant-worksheet}
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+For instance, www.torproject.org is blocked.
+Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
+It will fail to load, when you can visit other sites.
+
+To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
+If you can visit wikipedia, then you know that you have successfully circumvented censorship.
+
+\section{Post-Experiment Standard Interview Questions}
+\label{interview-questions}
+We asked our participants these questions after they were given time to configure Tor Browser. \\
+
+\begin{enumerate}
+\item{Can you talk us through what you did along with what you were thinking at the time?}
+\item{What was most challenging part of connecting?}
+\item{Were there any unfamiliar terms?}
+\item{How did you decide which options to choose?}
+\item{What did you think about using Tor?}
+\item{What is one change you would recommend?} 
+\item{Did you need any additional information?} 
+\end{enumerate}
+
+In addition to these questions, we asked our participants about specific questions based on their observation, usually regarding a specific choice in action, a particular screen they seemed stuck on, and any errors they encountered during the configuration process.
+
+\section{Quantitative User Recruitment Posting}
+\label{quantitative-recruitment}
+We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
+The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
+
+\indent Payment: \$30 Amazon gift card\\
+\indent Duration: 1 hour \\
+\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\
+
+\textit{<list of sessions>}\\
+
+To be eligible, you must be an adult (18 or older). This is to comply with university policies on research.
+
+If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
+with the sessions you are able to attend. We will confirm your participation and assign you a session. 
+2. Come to <redacted> %Xlab 
+at the appointed time for the experiment.
+
+\section{Quantitative User Study Introduction Script} 
+\label{quantitative-script} 
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
+
+To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
+Tor is already installed for you.
+On the desktop, you should see a globe icon that says ``Start Tor Browser.'' If you are able to reach the website, then you know that you have successfully circumvented censorship.
+Fill out the question on the worksheet.
+This isn't intended to be hard, just write what you see.
+We want to just check you saw the website.
+
+Afterward, we ask you to take a short survey to collect some information about you. The link is also on your worksheet.
+We will give you time to complete this task.
+If you finish early, we ask that you sit at your desk until the remainder of the hour.
+Since we are recording your screen, we ask that you don't do anything personal afterward, like checking your email.
+
+Before you start, do you have any questions about what you are asked to do?
+
+\section{Quantitative User Study Exit Survey} 
+\label{quantitative-exit-survey}
+We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.
+
+This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
+If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
+Committee for Protection of Human Subjects at 510-642-7461, or email 
+<redacted>. %subjects@berkeley.edu. 
+If you agree to participate, please click Next below.\\
+
+\begin{enumerate}
+\item{What is your participant ID? (This can be found on the sticker on the left hand corner of the desk you are currently sitting at.)}
+\item{What is your gender?}
+\item{What is your age?}
+\item{Please select your highest completed (or current) level of education}.
+\item{What is your current occupation?}  
+\end{enumerate}
+
+Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
 
@@
 We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process. 
-%for color red
-}
-
-\section{Qualitative User Study Recruitment Posting} 
-\label{qualitative-recruitment}
-We are recruiting participants for an in-person research study at <redacted>. %the University of California, Berkeley. 
-You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
-No special knowledge and no technical experience is required. If you are interested, fill out the survey at \textit{<survey link>}.
-
-\section{Qualitative User Study Prescreening Survey} 
-\label{qualitative-prescreening}
-We are recruiting participants for an in-person research study at the <redacted>. %University of California, Berkeley. 
-You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. No special knowledge and no technical experience is required.\\
-
-\begin{enumerate}
-\item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
-\item{I am able to provide my own transportation to the <redacted> %University of California, Berkeley 
-campus.}
-\item{Thank you for your interest! Please provide an email address where we can contact you to share more logistical details.}
-\item{we are looking for a very small number of participants, so unfortunately, we may not be able to accommodate everyone who applies. Would you like us to let you know about future opportunities?}
-\item{What is your gender?}
-\item{What is your age?}
-\item{Please select your highest completed (or current) level of education.}
-\item{What is your occupation?} 
-\item{Do you speak any languages other than English fluently?}
-\item{If you have a personal computer, what kind do you use?}
-\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
-\item{How often do you use the following software or features?
-\textit{<answer choices: a grid of radio buttons.
-Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption.
-Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
-\end{enumerate}
-Thank you for filling out this form. You are now done!
-
-\section{Prescreening Survey Responses}
-\label{prescreening-responses}
-{\color{blue} 
-short intro and conclusion. Take self-reported with a grain of salt, but here they are anyways.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{self-reported-tech-familiarity.png}
-\caption{most participants reported familiarity with terms, even made up ones.}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{self-reported-security-use.png}
-\caption{most people didn't use many security tools.}
-\end{figure}
-}
-
-\section{Qualitative User Study Introduction Script} 
-\label{qualitative-script} 
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
-
-To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
-If you are able to reach the website, then you know that you have successfully circumvented censorship.
-Fill out the question on the worksheet.
-This isn't intended to be hard, just write what you see.
-We want to just check you saw the website.
-
-Before you start, do you have any questions about what you are asked to do?
-
-\section{Participant Worksheet Text} 
-\label{participant-worksheet}
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-For instance, www.torproject.org is blocked.
-Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
-It will fail to load, when you can visit other sites.
-
-To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
-If you can visit wikipedia, then you know that you have successfully circumvented censorship.
-
-\section{Post-Experiment Standard Interview Questions}
-\label{interview-questions}
-We asked our participants these questions after they were given time to configure Tor Browser. \\
-
-\begin{enumerate}
-\item{Can you talk us through what you did along with what you were thinking at the time?}
-\item{What was most challenging part of connecting?}
-\item{Were there any unfamiliar terms?}
-\item{How did you decide which options to choose?}
-\item{What did you think about using Tor?}
-\item{What is one change you would recommend?} 
-\item{Did you need any additional information?} 
-\end{enumerate}
-
-In addition to these questions, we asked our participants about specific questions based on their observation, usually regarding a specific choice in action, a particular screen they seemed stuck on, and any errors they encountered during the configuration process.
-
-\section{Quantitative User Recruitment Posting}
-\label{quantitative-recruitment}
-We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
-The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
-
-\indent Payment: \$30 Amazon gift card\\
-\indent Duration: 1 hour \\
-\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\
-
-\textit{<list of sessions>}\\
-
-To be eligible, you must be an adult (18 or older). This is to comply with university policies on research.
-
-If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
-with the sessions you are able to attend. We will confirm your participation and assign you a session. 
-2. Come to <redacted> %Xlab 
-at the appointed time for the experiment.
-
-\section{Quantitative User Study Introduction Script} 
-\label{quantitative-script} 
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
-
-To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
-Tor is already installed for you.
-On the desktop, you should see a globe icon that says ``Start Tor Browser.'' If you are able to reach the website, then you know that you have successfully circumvented censorship.
-Fill out the question on the worksheet.
-This isn't intended to be hard, just write what you see.
-We want to just check you saw the website.
-
-Afterward, we ask you to take a short survey to collect some information about you. The link is also on your worksheet.
-We will give you time to complete this task.
-If you finish early, we ask that you sit at your desk until the remainder of the hour.
-Since we are recording your screen, we ask that you don't do anything personal afterward, like checking your email.
-
-Before you start, do you have any questions about what you are asked to do?
-
-\section{Quantitative User Study Exit Survey} 
-\label{quantitative-exit-survey}
-We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.
-
-This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
-If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
-Committee for Protection of Human Subjects at 510-642-7461, or email 
-<redacted>. %subjects@berkeley.edu. 
-If you agree to participate, please click Next below.\\
-
-\begin{enumerate}
-\item{What is your participant ID? (This can be found on the sticker on the left hand corner of the desk you are currently sitting at.)}
-\item{What is your gender?}
-\item{What is your age?}
-\item{Please select your highest completed (or current) level of education}.
-\item{What is your current occupation?}  
-\end{enumerate}
-
-Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
-
-\section{Alternative Approaches} 
-\label{alternatives}
-{\color {blue}
-Our goal was to deploy impactful, tested changes the Tor configuration interface.
-In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
-Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away.
-For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed.
-However, we list some alternative approaches that seem worth exploring.
-\\
-
-%remember: 	no user inputs, no network inputs, minimize info leaks
-%and:		minimal user work, full user control
-
-\begin{description}
-\item{\bfseries Automate the configuration.} The most efficient way to connect as many users to the Tor network is to automatically configure their connection on start.
-A naive automation is to try configurations that would most likely work, in order (i.e.
-a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
-This leaks to network eavesdroppers that the user is connecting to the Tor network.
-We do not know how much risk is associated with this approach.
-\item {\bfseries automate after the first failure.} The network leak happened. But then this automation would be pretty fingerprintable behavior. 
-\item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk.
-The complication with this approach is that users may not be qualified to answer if they are at risk or may not trust Tor with this information.
-\item{\bfseries Ask if users know what to do.} Another alternative to naive automation is to offer manual configuration to those that know how to configure their connection and to automate the process for users who do not know how to configure their connection.
-This may prevent the most mistakes, but does not account for the users' risk associated with using Tor.
-\item{\bfseries Suggest configurations.} A way to help users without any automation or questions is to give users information about what would work in their country.
-The first page of the configuration interface can show a list of countries with a corresponding recommended configuration.
-This approach does not require users to answer about their risk, technical ability, or location.
-However, it does require that the user trust the given advice and to correctly configure their settings based on this advice.
-\item{\bfseries Assign configurations.} This is a smart way to automate connections to the Tor network.
-Upon start, the interface detects proxy settings and uses them, if any.
-Then, all users connect to bridges that will always work (such as meek bridges), which assign them a guard relay based on their location, effectively assigning bridges for the user.
-\end{description}
-
-We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process. 
 }

### 2016-10-28 pets2017-paper/pets2017-paper.tex
refine recommendations section

@@
 \label{recommendations}
-We believe that adopting our design will help save users time when connecting to Tor.
-But we do not claim how much and in what way each change impacted our participants, since we did not test them independently.
-Some of our changes may have little or negative effects, but may be masked by other changes with positive effects.
-We also recognize that there may be equivalent or more impactful changes that may be made in place of ours.
-
-We hope that our inspection, design, and evaluation evaluation process provided valuable insight for potential changes.
-We do not recommend our specific design changes, but offer some advice and accompanying suggestions: \\
+We do believe that adopting our design will help save users time when connecting to Tor.
+But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made.
+Some of our changes may have little or negative effect.
+Additionally, we recognize equivalent (or more impactful!) changes could be made in place of ours.
+Therefore, we do not recommend specific changes, but offer some suggestions based on what we learned: \\
 
 \begin{itemize}
-\item {\bfseries Use less words.} While a thorough explanation isn't always possible with brevity, users are more likely to read the text if it is short.
-\item {\bfseries Minimize work.} Ask users to perform tasks only when necessary.
-Hide less frequently used options or components.
-Redirect users to the relevant pages (i.e.
-redirect to the bridge screen the bridge fails).
-\item {\bfseries Give advice.} Guide users toward connecting directly unless they need a bridge or proxy, help them decide between transports, and discourage them from configuring optional components.
-\item {\bfseries Add system visibility.} Rather than requiring users to remember their bridge and proxy configuraitons, summarize their choices.
-The progress bar should reflect the current state of the connection.
-\item {\bfseries Provide feedback.} In addition to displaying the error message, tell users what to try next when they encounter that error. 
+\item {\bfseries Use less words.} Shorten text so users read it.
+\item {\bfseries Give advice.} Discourage users from configuring optional components. Add a secondary recommendation (try meek if obfs3 doesn't work). 
+\item {\bfseries Hide infrequent options.} Hide the proxy configuration screen and less-used transports. 
+\item {\bfseries Minimize work.} Detect if users need a proxy or not. Redirect users to the relevant pages on error (i.e. redirect to the bridge screen the bridge fails).  
+\item {\bfseries Add system visibility.}  Show users their bridge and proxy settings before and during connection. Fix the progress bar updating weirdness.
+\item {\bfseries Provide feedback.} Tell users what to do when a specific error occurs (i.e. try agin, fix bridges, etc.). 
 \end{itemize}
 
-We should consider alternative approaches of bootstrapping a connection to Tor.
-We recommend leveraging automation, user-dependent inputs, or network-dependent inputs for a solution that will help more users succed in a shorter amount of time.
+Although the abovementioned suggestions will improve the deployed interface, we recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs.
 We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.

### 2016-10-28 pets2017-paper/pets2017-paper.tex
minor word tweaks in recommendation and limitations

@@
 Additionally, we recognize equivalent (or more impactful!) changes could be made in place of ours.
-Therefore, we do not recommend specific changes, but offer some suggestions based on what we learned: \\
+Therefore, we do not recommend specific changes, but offer some suggestions for Tor Launcher's GUI based on what we learned: \\
 
@@
 We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward.
-If true, this makes our results are a conservative estimate of the current problems.
+If true, this makes our results are a conservative estimate of the current usability problems.
 
@@
 Our simulated environments did not require users to configuring a proxy or to get a custom bridge.
-From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how or why they do.
+From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how much they do.
 
@@
 The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent.
-Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all testing conditions equally.
+Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
introduce NEW and OLD

@@
 We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface.
-Table~\ref{table:participant-summary} gives an overview of the results, summarizing completion rate, connection time, and configuration time by condition.
-Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
+In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}).
+Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
write summative conclusion section.

@@
 Table~\ref{table:participant-summary} summarizes the completion rates and Table~\ref{tab:attempts-bridge-proxy} shows the configuration for users' first successful connection.
-We only conside the first successful configuration, as some curious participants investigated other solutions even after completing their task.
+We only considered the first successful configuration, as some curious participants investigated others after completing their task.
 
 % failure observations
-63\% (72 of 114) of first attempts to connect failed and (363 of 458) of total attempts to connect failed.
 17\% (19 of 114) of participants were not able to successfully connect to Tor.
@@
 \subsection{Usability of Tor Launcher} 
-{\color {blue}
-%success rate 
-Not enough people got through!
-There's a steep decline between downloads and users in real life too, if you look at Tor metrics.
-Something is definitely stopping people.
-We're not saying that this is the main reason, but it certainly isn't helping.
-
-% connection and configuration time 
-Ideally, users should be able to connect to Tor within a few minutes, regardless of their censorship environment.
-Users in the wild will likely not be motivated to spend 40 minutes trying to configure Tor, and likely give up before then.
-If users were only willing to put in a minute or so of their time, users in intermediate and heavily censored environments would be unable to connect.
-Even if users were willing to dedicate 10 minutes to configuring their connection, most users in heavily censored environments would be unable to connect.
-}
+In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. 
+On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or cutsom bridge took over 20 minutes.
+
+Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes.
+Neither the Tor Browser's 5.0.3.
+Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
finished completion rate subsection

@@
 \subsubsection{Completion Rate}
-{\color {blue} 
-Completion rate was defined as the percentage of users that eventually connect to Tor in an experimental condition.
-Table~\ref{table:participant-summary} summarizes the completion rates and Table~\ref{tab:attempts-bridge-proxy} shows the configuration for users' first successful connection.
-We only considered the first successful configuration, as some curious participants investigated others after completing their task.
-
-% failure observations
-17\% (19 of 114) of participants were not able to successfully connect to Tor.
-Specifically, Five (P73, P75, P89, P91, P106, P110) tried a direct connection; when it failed, they assumed there was something wrong with their computer, network settings, or the Tor network.
-Five (P90, P93, P108, P111, P114) tried a direct connection, a default obfs3 bridge connection, then failed.
-Five (P74, P92, P105, P107, P113) assumed that they needed a proxy when they needed another bridge.
-Two (P94, P109) tried to get custom bridges but failed to format the message correctly to get a response.
-%We believe that the added advice on what to try next on error messages would have improved the rate of success. However, only 1 of 116 participants saw an error during the experiment.
-
-%success rate and version
-Our interface changes did not have a significant impact on completion rates (Pearson's Chi-squared; $X^2 = 0.0126$, $df = 2$, $p = 0.994$).
-That is, the differences in completion rates of E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-}
-
+
+%table
 \begin{table}[t]
@@
 in each condition.
-Most E1 participants used a direct connection,
-but a few tried a built-in obfs3 bridge.
-All the E2 participants who succeeded,
-did so with obfs3 (the recommended bridge type)---none tried
-a different bridge before obfs3.
-% flashproxy, fte, fte-ipv6, obf4, and scramblesuit were not used! 
-All of the successful E3 participants but one
-used one of the meek bridges.
-The remaining E3 participant succeeded in an unexpected way:
-by searching the web for an open proxy and configuring it
-as the proxy setting.
+Most successful E1 participants used a direct connection,
+but a few optionally used an obfs3 bridge.
+All successful E2 participants used 
+an obfs3 bridge (the recommended option)---none used 
+flashproxy, fte, fte-ipv6, obf4, or scramblesuit bridges to connect. 
+Most successful E3 participants
+used a meek bridges, disfavoring meek-azure.
+One E3 participant succeeded in an unexpected way
+by using an open proxy and configuring it to bypass our 
+simulated environment.
 }
@@
 \end{table}
+
+%overview
+Completion rate was defined as the percentage of users that eventually connected to Tor.
+Table~\ref{table:participant-summary} summarizes the completion rates and Table~\ref{tab:attempts-bridge-proxy} shows the configuration for users' first successful connection.
+We only considered the first successful configuration, as some curious participants tried others after completing their task.
+
+% failure observations
+17\% (19 of 114) of participants were not able to successfully connect to Tor.
+Five (P73, P75, P89, P91, P106, P110) tried a direct connection.
+When that failed, they assumed there was something wrong with their computer, network settings, or the Tor network and never tried to configure bridges or proxies.
+Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor.
+We belive this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails.
+Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed.
+Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder.
+We suspect that they would have succeeded if they had gotten a response.
+
+%success rate and version
+Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $X^2 = 0.0126$, $df = 2$, $p = 0.994$).
+That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
 

### 2016-10-28 pets2017-paper/pets2017-paper.tex
finish connection time section

@@
 \subsubsection{Connection time} 
-{\color {blue} 
 Connection time is the time from Tor Browser starup to the first successful Tor bootstrap.
@@
 Table~\ref{table:participant-summary} summarizes the median connection times while Figure~\ref{fig:time_to_success_clamped} shows their distribution.
-Figure ~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
+Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
 
 %time observations (how long people took)
-The simulated censorship environment also had an impact; the more difficult the censorship environment, the longer participants took to configure their connection (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
-The longer the time went on, the less likely that the participants were going to figure it out.
+The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
 
@@
 Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-That is, the differences in mean connection times in E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
 We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).
-}
 
@@
 \caption{
-Time to first success, by censorship environment and interface.
-The dots show the raw completion times,
+The dots show the raw connection times,
 while the boxplots show the medians and interquartile ranges.
-The ``DNF'' figures at the right show the number of participants 
-who did not finish in the time allotted.
-Here, non-finishing participants are assigned the maximum time of 40:08.
+The ``DNF'' (did not finish) numbers at the right show how many of participants 
+did not finish, who were assigned the maximum time of 40:08.
 }
@@
 \caption{
-Cumulative success rates over time, by censorship environment and interface.
-We stopped participants after 40 minutes. Here, those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes for the purposes of plotting. 
-For example, every E1-NEW participant finished within 90 seconds,
-but only 58\% of E1-OLD had finished by that time. Within 10 minutes, most
-participants in E2 had finished, along with a minority of E3 participants. 
+Cumulative success rates over time, shown continuously and at discrete times we found interesting.
+For the purposes of plotting the cumulative distribution, those who did not finish were assigned
+an arbitrarily high number greater than 40 minutes. 
+Notice that the longer the time went on, participants were less likely to succeed. 
+At 1.5 minutes, every E1-NEW participant finished,
+but only 58\% of E1-OLD had finished by that time.  
+At 10 minutes, most participants in E2 had finished. 
 }

### 2016-10-28 pets2017-paper/pets2017-paper.tex
finish configuration time

@@
 \item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
-\item {\bfseries Configuration time:} time from Tor Browser startup to intializing a successful Tor bootstrap.
+\item {\bfseries Configuration time:} time spent in the Tor Launcher GUI configuring network components.
 \end{itemize}
@@
 Connection time captured the amount of time users take to use the configuration interface to connect to Tor.
-This included time users spent waiting while a Tor Browser establishes a connection to Tor, which can potentially dominate the measurement.
-Configuration time captured the amount of time users spent configuring network components necessary to connect to Tor.
+This included time users spent waiting while a Tor Browser establishes a connection to Tor, which can dominate the measurement.
+Configuration time captured the amount of time users spent configuring bridges and proxies.
 
@@
 Non-finishing participants are assigned the maximum experiment time of 40:08.
-Table~\ref{table:participant-summary} summarizes the median connection times while Figure~\ref{fig:time_to_success_clamped} shows their distribution.
+Table~\ref{table:participant-summary} summarizes the median times while Figure~\ref{fig:time_to_success_clamped} shows their distribution.
 Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
@@
 That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).
+We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).
 
@@
 \subsubsection{Configuration Time} 
-{\color {blue} 
-Configuration time is the time from Tor Browser startup to initializing a successful Tor bootstrap.
-This is the connection time minus the bootstrap time, which can take up to two minutes.
-Table~\ref{table:participant-summary} shows the median configuration times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
-
-%how its calcuated 
-We believe that a more meaningful measurement of task time is the time that participants spent interacting with the interface, excluding the time waiting for the connection to bootstrap.
-Failures were 40:08 - time on progress screen.
-With incorrect configurations, a lack of error messages on the progress screen caused some users to wait indefinitely.
-Logs show that participants spent 58\% of their overall time at the progress screen.
-Table ~\ref{table:median_time} shows the median percentage of time spent on each screen.
+Configuration time is the time spent configuring network components, which we define as the completion time minus any time spent on the progress screen.
+Table~\ref{table:participant-summary} shows the median times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
+Table~\ref{table:median_time} shows the percentage of time spent on each screen.
+Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valild configuration).
 
 %things to keep in mind
-This is just a helpful metric to supplement the connection time.
-Look at E1, for instance.
-People who failed, waited, tried, and succeeded lost the progress thing when they shouldn't have.
-BUT since our error thing broke, this might be a useful metric.
-Active time for unsuccessful participants were calculated by subtracting the amount of time spent on the progress screen from the maximum experiment time, 40 minutes.
-This is an approximation, since some participants searched for help on the web after exiting the interface or on the progress screen.
+We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1.
+and 2) some mistakes, such as using a syntactically valid but unsuable proxy, generate non-interruping warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
+But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.
 
@@
 Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-That is, the differences in mean configuration times in E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-We used a one-tailed Mann--Whitney test because configuration time was 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed.
-}
+That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+We used a one-tailed Mann--Whitney test because the distribution of configuration times were also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.
 
@@
 of time on one screen may not be the same participant who spent the median percent
-of time on other screens. Note that the time spent on the progress bar dominates the 
-time spent in the interface.} 
+of time on other screens.} 
 \label{table:median_time}
@@
 \caption{
-Active time, by censorship environment and interface.
 The dots show the raw active configuration times,
@@
 subtracting the amount of time spent on the progress screen from the 
-the maximum time of 40:08.
+their assigned completion time of 40:08.
 }

### 2016-10-31 pets2017-paper/pets2017-paper.tex
small wording tweaks throughout

@@
 
-Bridges are unlisted Tor relays that can serve as an alternative entry node.
+Bridges are unlisted Tor relays that serve as an alternative entry node.
 Bridges can be simple, unlisted relays. 
@@
 
-In addition to Tor-specific components, a local proxy is required to connect 
+A local proxy is required to connect 
 in certain managed networks.
@@
 \subsection{State and Corporate Censorship}
-State level censors can vary in their thoroughness in censorship, resulting in a variety of ever-changing network conditions.
+State level censors can vary in their thoroughness in censorship.
 Some block websites with a combination of IP blacklisting and DNS-poisoning while others that employ more sophisticated techniques such as deep packet inspection and protocol detection.
 In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship.
-In other countries, sophisticated state-level censorship require bridges that run specific tranports that route traffic through other, non-Tor services first.
-For example, only meek-amazon and meek-azure transports work to bypass China's GFW.
+In other countries, sophisticated state-level censorship require custom bridges or bridges that run specific tranports that route traffic through non-Tor services first.
 
@@
 \pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
-
-\subsection{Where Users Struggled} 
-{\color {blue}
-LIST `EM! 
 }
@@
 \end{figure}
-}
-
-\section{Design Principles and Changes}
+
+\subsection{Pain Points in Tor Launcher} 
+{\color {blue}
+LIST `EM! 
+}
+
+\section{A Design Iteration}
 \label{sec:design} 
@@
 That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned the maximum time of 40 minutes).
+We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).
 
@@
 
-%active time and version
+%configuration time and version
 Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
@@
 But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made.
-Some of our changes may have little or negative effect.
-Additionally, we recognize equivalent (or more impactful!) changes could be made in place of ours.
 Therefore, we do not recommend specific changes, but offer some suggestions for Tor Launcher's GUI based on what we learned: \\
@@
 
-Although the abovementioned suggestions will improve the deployed interface, we recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs.
+We also recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs.
 We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.

### 2016-10-31 pets2017-paper/pets2017-paper.tex
almost done with design section

@@
 \subsection{Design Princples} 
-{\color {blue}
-Introduce design principles.
-
-Security design principles: 
-\begin{enumerate}
-\item no user-dependent inputs 
-\item no network-dependent inputs
-\item minimal information leaks
-\end{enumerate}
-
-%In principle, the process of configuring a proxy and bridge can be automated, but
-%the interface eschews automatic configuration through network probing
-%in favor of guided manual configuration to give users agency in configuring their connection. 
-%Automatic configuration through network probing may put some users in certain regimes at risk. 
-%A knowledgeable user can minimize their network trace and hide that they are connecting to Tor.
-Justify why we kept the similar interface.
-
-Introduction to usability design principles.
-
-Usability design principles: 
-\begin{enumerate}
-\item minimal user work
-\item full user control  
-\item targeted user feedback
-\item build a mental model
-\end{enumerate} 
-}
-
-\subsection{Design Changes} 
-{\color {blue}
-Introduction to design changes.  \\
-
-\noindent Changes made for minimal user work: 
+The interface currently favors a guided manual configuration over an automated configuration with network probing.
+Our redesign preserves this approach and has no user-dependent inputs, no network-dependent inputs, and minimal information leaks.
+
+{\color {blue} WRITE ABOUT PAIN POINTS HERE} We aimed to minimize work, give targeted feedback, and to build a mental model.
+
+\subsection{Changes Made} 
+We made these changes for a more usable interface. \\
+
+\noindent To minimize work: 
 \begin{itemize}
-\item eliminated technical questions. Less questions to answer, less screens. 
-\item auto-detection for proxies.
-A local scan of the operating system configuration does reveal information to network eavesdroppers and can detect if a proxy is used (if configured in other browsers).
-(We simulated the auto-detection by hard-coding the fact that a proxy was not required.)
+\item We eliminated technical questions, resulting in less tasks and interface screens. 
+\item We simulated auto-detection for proxies, telling users that they did not need a proxy. This is feasible to do with a local scan (no information leaked). 
+\item We labeled the configure button as an option for users in heavily censored environments.
+\item We gave advice on choosing transports, telling users to try a meek bridge if obfs3 does not work.
 \end{itemize}
 
-Changes made for full user control: 
+To give targeted feedback: 
 \begin{itemize}
-\item added intructions on what to try next on errors. The advice may be to try the connection again, to choose a different bridge, or to try a connection without a proxy. 
-\item added advice for choosing connect versus configure.
-Before, the interface only informed users that the connect option worked some of the time, but did not specify why.
-We labeled the configure option as a manual option  specifically for users in heavily censored environments.
-\item gave advice on choosing transports. We tell users to try a meek bridge if obfs3 does not work.
+\item We switched added indicators to the progress bar to show the progress of bridges and proxies. 
+\item We told users what to try next on errors (i.e. choose a different bridge, try a without a proxy). 
 \end{itemize}
 
-Changes made for feedback: 
+To build a mental model:
 \begin{itemize}
-\item progress bar feedback fixed and network-accurate.
-We fixed the bug that caused the progress bar to not update on subsequent attempts.
-We switched the continuous progress bar to a discrete checkpoint-based progress indicator that shows the network components involved in connecting to the Tor network.
-\item minimized interface text. Whenever we could, we tried to shave text and keep it simple. 
+\item We added a summary screen displays the current bridge and proxy settings for system visibility. 
+\item We switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}).
 \end{itemize}
 
-Changes made to build a mental model:
-\begin{itemize}
-\item added system status visibility. We added a summary screen displays the current bridge and proxy settings
-\item switched proxy and bridge configuration order. Network components are now configured in a topologically sequential order, resembling Fig.~\ref{fig:topology}.
-\end{itemize}
-
-Refer to figure with all deployed interface window (in previous section), refer to figure with all new interface windows (in caption, refer to appendix with advice text given on errors).
-Intorduce new/old labels.
-}
+Figure~\ref{fig:new-interface} shows the resulting interface.  Figure~\ref{fig:old-interface} shows the unchanged version.
 

### 2016-10-31 pets2017-paper/pets2017-paper.tex
hash out formative results

@@
 \begin{quotation}
-\noindent #1:~\textit{``#2''}
+\noindent #1:~\textit{#2}
 \end{quotation}
@@
 
-Observations in E1: 
-\pquote{P1, NF}{summary of what they did. ``and a quote too.''}
-\pquote{P2, NF}{summary of what they did. ``and a quote too.''}
-\pquote{P3, NF}{summary of what they did. ``and a quote too.''}
-\pquote{P4, HT}{summary of what they did. ``and a quote too.''}
-\pquote{P5, UT}{summary of what they did. ``and a quote too.''}
-
-Observations in E2:
-
-Observations in E3:
-
-\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
-\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
-\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
-\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
-\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
+%E1: P2, P3, P4, P9, P10
+%E2: P7, P8, P11, P12, P13
+%E3: P1, P5, P6, P14, P15, P16
+
+%TODO: re-watch the videos and get the exact times.
+
+A summary about what we have seen in E1. Just put the high level takeaways so 
+that people don't really need to read the summaries. Observations in E1:
+
+%P2(regular): E1 (~1:52) 
+\pquote{P1 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P3(regular): E1 (N/A; lost chunk of video… but ~1 minute) 
+\pquote{P2 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P4(regular): E1 (~4:30)
+\pquote{P3 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P9 (regular): E1 (~0:45)
+\pquote{P4 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P10 (has used Tor before): E1 (GET TIME)
+\pquote{P5 (success, connection time, configuration time)}{summary of what they did here.}
+
+A summary about what we have seen in E2. Just put the high level takeaways so 
+that people don't really need to read the summaries. Observations in E2:
+
+%P7 (heard of Tor): E2 (~4:30) 
+\pquote{P6 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P8 (used Tor): E2 (clock drift mission impossible, never succeeds) 
+\pquote{P7 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P11 (used Tor before): E2 (~3:00)
+\pquote{P8 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P12 (regular): E2 (GET TIME)
+\pquote{P9 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P13 (regular): E2 (GET TIME) 
+\pquote{P10 (success, connection time, configuration time)}{summary of what they did here.}
+
+A summary about what we have seen in E3. Just put the high level takeaways so 
+that people don't really need to read the summaries. Observations in E3:
+
+%P1 (heard of tor before): E3 (~8:30) 
+\pquote{P11 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P5 (has used tor before): E3 (~22:30)
+\pquote{P12 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P6 (heard of Tor): E3 (~26:50) 
+\pquote{P13 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P14 (regular): E3 FAIL
+\pquote{P14 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P15 (regular): E3 FAIL
+\pquote{P15 (success, connection time, configuration time)}{summary of what they did here.}
+
+%P16: E3 FAIL (why did obfs3 work the first time? It shouldn't have!) 
+\pquote{P16 (success, connection time, configuration time)}{summary of what they did here.}
+
+%\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
+%\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
+%\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
+%\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
+%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
 I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
-When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
-%The progress bar has a bug that causes it to update only when the level of progress increases.
-%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
+%When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
+%%The progress bar has a bug that causes it to update only when the level of progress increases.
+%%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
 Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
-\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
-\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
+%\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
+%\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
+%\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
+
+Some qualifiers about how these are supposed to be insights, but we don't know how representative these problems are.
+That's for the summative user testing!
+But these are definitely problems that exist.
 }

### 2016-11-03 pets2017-paper/pets2017-paper.tex
write some of formative results.

@@
 We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
-Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser, a participant who heard of it, and multiple participants who never heard of or used it.
+Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser before.
 
@@
 we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses.
-We then followed up with participant-specific questions to verify any hypotheses we had from observation (e.g.
+We then followed up with participant-specific questions to verify any hypotgit heses we had from observation (e.g.
 ``the participant was selecting bridges at random'').
@@
 
-\subsection{Observations and Interviews} 
-{\color {blue}
-We give a summary of all participants here!  Quotations come from live transcription and are not necessarily verbatim.
+\subsection{Results} 
+We give a summary of what our participants did below. We watched the screen recording to summerize their actions and referred to their interviews for insight into why they took specific actions.
 
@@
 %TODO: re-watch the videos and get the exact times. 
-
-A summary about what we have seen in E1. Just put the high level takeaways so 
-that people don't really need to read the summaries. Observations in E1:
-
-%P2(regular): E1 (~1:52) 
-\pquote{P1 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P3(regular): E1 (N/A; lost chunk of video… but ~1 minute) 
-\pquote{P2 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P4(regular): E1 (~4:30)
-\pquote{P3 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P9 (regular): E1 (~0:45)
-\pquote{P4 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P10 (has used Tor before): E1 (GET TIME)
-\pquote{P5 (success, connection time, configuration time)}{summary of what they did here.}
-
-A summary about what we have seen in E2. Just put the high level takeaways so 
-that people don't really need to read the summaries. Observations in E2:
-
-%P7 (heard of Tor): E2 (~4:30) 
-\pquote{P6 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P8 (used Tor): E2 (clock drift mission impossible, never succeeds) 
-\pquote{P7 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P11 (used Tor before): E2 (~3:00)
-\pquote{P8 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P12 (regular): E2 (GET TIME)
-\pquote{P9 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P13 (regular): E2 (GET TIME) 
-\pquote{P10 (success, connection time, configuration time)}{summary of what they did here.}
-
-A summary about what we have seen in E3. Just put the high level takeaways so 
-that people don't really need to read the summaries. Observations in E3:
-
-%P1 (heard of tor before): E3 (~8:30) 
-\pquote{P11 (success, connection time, configuration time)}{summary of what they did here.}
+%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos
+
+In E1, any connection to Tor will work. Bridges and proxies are optional.  
+Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants configured bridges that they did not need. 
+Observations in E1:
+
+%P9 (regular): E1 (0:39; 4:49 to 5:28)
+\pquote{P1 (new user, direct, 0:39)}{They clicked connect on the first screen almost immediately.}
+
+%P2(regular): E1 (1:20, 0:22 to 1:42) 
+\pquote{P2 (new user, direct, 1:20)}{They spent time reading all the text on the start screen, and clicked connect. They chose to connect directly because they were intimidated by the other option.}
+
+%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
+\pquote{P3 (previous Tor user, obfs3, 1:02)}{They clicked configure and connected with the recommended bridge.}
+
+%P3(regular): E1 (N/A; 5:47 to 6:26) 
+\pquote{P4 (new user, obfs3, ~1:39)}{They clicked configure and connected with the recommended bridge. They were going to use a proxy, but decided not to when they saw the proxy input fields.}
+
+%P4(regular): E1 (8:56, 7:22 to 16:18)
+\pquote{P5 (new user, obfs4, 8:56)}{They clicked configure, chose the recommended bridge, and then tried to configure a proxy.
+After not being able to fill out the proxy input fields, they go back to the bridge screen, select the obfs4 bridge, and make a connection without a proxy.}
+
+In E2, a bridge is required to connect, but any bridge will work. Proxies are optional. 
+Participants in E2 usually tried a direct connection before {\it eventually} trying the recommended bridge.
+Participants spent a fair bit of time trying to answer bridge and proxy questions and trying to configure proxies.
+Observations in E2:
+
+%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
+\pquote{P6 (new user, obfs3, 4:04)}{They click connect and wait three minutes before giving up on the direct connection.
+They then clicked configure and connected with the recommended bridge, because it was the next easiest thing to do.}
+
+%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
+\pquote{P7 (previous Tor user, obfs3, 4:08)}{They clicked connect and made a direct connection.
+Then, they clicked configure, answered no to both bridge and proxy questions, and effectively made another direct connection.
+After that, they go back to the bridge screen and finally connect with the recommended bridge.}
+
+%P13 (regular): E2 (7:48; 0:34 to 9:22) 
+\pquote{P8 (new user, obfs3, 9:22)}{They clicked connect to make a direct connection.
+When that did not work, they restarted Tor Launcher and made another direct connection--and repeated this three times.
+On the fourth restart, they decided to configure a proxy, but gave up.
+On the fifth restart, they connect with the recommended bridge.}
+
+%P12 (regular): E2 (10:40; 0:46 to 11:26)
+\pquote{P9 (new user, direct, 10:40)}{They clicked configure, but answer no to both bridge and proxy questions and made a direct connection, which fails.
+They then look at proxy settings, get intimidated, and try the direct connection again, which fails.
+They look for proxy settings and tried configuring a proxy for 4 minutes, but give up and try a diret connection again, which worked.
+This was not supposed to work, but new public relays came online after we ran our firewall rules and they connected using those relays.}
+
+%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
+\pquote{P10 (previous Tor user, failed to connect)}{They clicked connect to make a direct connection, then they made a connection with the recommended bridge (~5:42), which should have worked.
+However, our setup experienced a clock drift.
+Tor does not allow connections with bad clocks, so they could not connect to Tor unless they fixed the clock.
+The interface did not display an error for the clock drift, and they spent the rest of their time trying different bridges and proxies in vain.}
+
+{\color {blue}
+In E3, a bridge is required to connect, but only meek bridges work. Proxies are optional. 
+Summary of E3 connections. 
+Observations in E3:
+
+%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
+\pquote{P11 (success, 7:31)}{The participant tries connecting directy to the Tor network and connecting to the Tor network with an obfs3 bridge, both of which do not connect to Tor E3.
+Eventually, the participant selects a bridge that will connect to Tor (meek-azure), but was convinced that it would not work because it was taking too slow.
+They go back to the first page and click connect, which uses the configured meek-azure bridge.
+The participant thought that they had connected to Tor directly, and did not realize that the connect button uses whatever settings are toggled in the interface.}
 
@@
 \pquote{P16 (success, connection time, configuration time)}{summary of what they did here.}
+
+Some qualifiers about how these are supposed to be insights, but we don't know how representative these problems are.
+That's for the summative user testing!
+But these are definitely problems that exist.
+}
+
+\subsection{Pain Points in Tor Launcher} 
+{\color {blue}
+A summary about what we have seen in E1, E2, E3. How to fix it. 
+Use some quotes here, and say insights from the interview. 
+Quotations come from live transcription and are not necessarily verbatim.
 
@@
 %\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
-
-Some qualifiers about how these are supposed to be insights, but we don't know how representative these problems are.
-That's for the summative user testing!
-But these are definitely problems that exist.
-}
-
-\begin{figure}[t]
-  \centering
-    \includegraphics[width=0.5\textwidth]{error.png}
-    \caption{An example of a technical error message which our participants did not understand.}
-\label{fig:error}
-\end{figure}
-
-\subsection{Pain Points in Tor Launcher} 
-{\color {blue}
-LIST `EM! 
 }

### 2016-11-04 pets2017-paper/pets2017-paper.tex
reword summaries, shuffle participant order

@@
 %P9 (regular): E1 (0:39; 4:49 to 5:28)
-\pquote{P1 (new user, direct, 0:39)}{They clicked connect on the first screen almost immediately.}
+\pquote{P1 (new user, direct, 0:39)}{They made a direct connection immediately.}
 
 %P2(regular): E1 (1:20, 0:22 to 1:42) 
-\pquote{P2 (new user, direct, 1:20)}{They spent time reading all the text on the start screen, and clicked connect. They chose to connect directly because they were intimidated by the other option.}
+\pquote{P2 (new user, direct, 1:20)}{They spent time reading the text on the start screen, and chose to connect directly because they were intimidated by the other option.}
+
+%P3(regular): E1 (N/A; 5:47 to 6:26) 
+\pquote{P3 (new user, obfs3, ~1:39)}{They connected with the recommended bridge. They were also going to use a proxy, but decided not to when they saw the proxy input fields.}
+
+%P4(regular): E1 (8:56, 7:22 to 16:18)
+\pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy.
+After not being able to fill out the proxy input fields, make a connection with an obfs4 bridge and no proxy.
+Note that they didn't try connecting with the obfs3 bridge, which would have worked.}
 
 %P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
-\pquote{P3 (previous Tor user, obfs3, 1:02)}{They clicked configure and connected with the recommended bridge.}
-
-%P3(regular): E1 (N/A; 5:47 to 6:26) 
-\pquote{P4 (new user, obfs3, ~1:39)}{They clicked configure and connected with the recommended bridge. They were going to use a proxy, but decided not to when they saw the proxy input fields.}
-
-%P4(regular): E1 (8:56, 7:22 to 16:18)
-\pquote{P5 (new user, obfs4, 8:56)}{They clicked configure, chose the recommended bridge, and then tried to configure a proxy.
-After not being able to fill out the proxy input fields, they go back to the bridge screen, select the obfs4 bridge, and make a connection without a proxy.}
+\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}
 
@@
 %P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
-\pquote{P6 (new user, obfs3, 4:04)}{They click connect and wait three minutes before giving up on the direct connection.
-They then clicked configure and connected with the recommended bridge, because it was the next easiest thing to do.}
+\pquote{P6 (new user, obfs3, 4:04)}{They made a direct connection and giving up after three minutes of waiting. Then, they connected with the recommended bridge.}
+
+%P13 (regular): E2 (7:48; 0:34 to 9:22) 
+\pquote{P7 (new user, obfs3, 9:22)}{They made a direct connection.
+When that did not work, they restarted Tor Launcher and made another direct connection--and repeated this two more times.
+On the fourth restart, they decided to not use a bridge but tried to configure a proxy, but gave up.
+On the fifth restart, they connect with the recommended bridge.}
+
+%P12 (regular): E2 (10:40; 0:46 to 11:26)
+\pquote{P8 (new user, direct, 10:40)}{They made a direct connection, which fails.
+They then look at proxy settings, get intimidated, and tried the direct connection again, which fails.
+They tried configuring a proxy for 4 minutes, but gave up.
+They tried a direct connection again, which worked.
+E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those relays.}
 
 %P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
-\pquote{P7 (previous Tor user, obfs3, 4:08)}{They clicked connect and made a direct connection.
-Then, they clicked configure, answered no to both bridge and proxy questions, and effectively made another direct connection.
-After that, they go back to the bridge screen and finally connect with the recommended bridge.}
-
-%P13 (regular): E2 (7:48; 0:34 to 9:22) 
-\pquote{P8 (new user, obfs3, 9:22)}{They clicked connect to make a direct connection.
-When that did not work, they restarted Tor Launcher and made another direct connection--and repeated this three times.
-On the fourth restart, they decided to configure a proxy, but gave up.
-On the fifth restart, they connect with the recommended bridge.}
-
-%P12 (regular): E2 (10:40; 0:46 to 11:26)
-\pquote{P9 (new user, direct, 10:40)}{They clicked configure, but answer no to both bridge and proxy questions and made a direct connection, which fails.
-They then look at proxy settings, get intimidated, and try the direct connection again, which fails.
-They look for proxy settings and tried configuring a proxy for 4 minutes, but give up and try a diret connection again, which worked.
-This was not supposed to work, but new public relays came online after we ran our firewall rules and they connected using those relays.}
+\pquote{P9 (previous Tor user, obfs3, 4:08)}{They made a direct connection.
+Then, they answered no to both bridge and proxy questions, and effectively made another direct connection.
+After that, they connect with the recommended bridge.}
 
 %P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
-\pquote{P10 (previous Tor user, failed to connect)}{They clicked connect to make a direct connection, then they made a connection with the recommended bridge (~5:42), which should have worked.
-However, our setup experienced a clock drift.
-Tor does not allow connections with bad clocks, so they could not connect to Tor unless they fixed the clock.
-The interface did not display an error for the clock drift, and they spent the rest of their time trying different bridges and proxies in vain.}
+\pquote{P10 (previous Tor user, failed to connect)}{They made a direct connection.
+Then they made a connection with the recommended bridge (~5:42), which should have worked.
+However, our setup experienced a clock drift and Tor does not allow connections with bad clocks.
+The interface did not tell the user about the clock, and they spent the rest of their time trying different bridges and proxies in vain.}
 
@@
 
+%P6 (heard of Tor): E3 (~26:50) 
+\pquote{P13 (new user, failed to connect)}{summary of what they did here.}
+
+%P14 (regular): E3 FAIL
+\pquote{P14 (new user, failed to connect)}{summary of what they did here.}
+
+%P15 (regular): E3 FAIL
+\pquote{P15 (new user, failed to connect)}{summary of what they did here.}
+
+%P16: E3 (regular) FAIL (why did obfs3 work the first time? It shouldn't have!) 
+\pquote{P16 (new user, failed to connect)}{summary of what they did here.}
+
 %P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
-\pquote{P11 (success, 7:31)}{The participant tries connecting directy to the Tor network and connecting to the Tor network with an obfs3 bridge, both of which do not connect to Tor E3.
+\pquote{P11 (new user, meek-azure, 7:31)}{The participant tries connecting directy to the Tor network and connecting to the Tor network with an obfs3 bridge, both of which do not connect to Tor E3.
 Eventually, the participant selects a bridge that will connect to Tor (meek-azure), but was convinced that it would not work because it was taking too slow.
@@
 %P5 (has used tor before): E3 (~22:30)
-\pquote{P12 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P6 (heard of Tor): E3 (~26:50) 
-\pquote{P13 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P14 (regular): E3 FAIL
-\pquote{P14 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P15 (regular): E3 FAIL
-\pquote{P15 (success, connection time, configuration time)}{summary of what they did here.}
-
-%P16: E3 FAIL (why did obfs3 work the first time? It shouldn't have!) 
-\pquote{P16 (success, connection time, configuration time)}{summary of what they did here.}
+\pquote{P12 (previous Tor user, )}{summary of what they did here.}
 
@@
 {\color {blue}
-A summary about what we have seen in E1, E2, E3. How to fix it. 
+not trying direct or trying direct, bad progress bar, trying to configure a proxy. How to fix it. 
 Use some quotes here, and say insights from the interview. 

### 2016-11-04 pets2017-paper/pets2017-paper.tex
finish formative section

@@
 
-In E1, any connection to Tor will work. Bridges and proxies are optional.  
-Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants configured bridges that they did not need. 
+In E1, any connection to Tor worked. Configuring bridges and proxies were optional.  
+Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges. 
 Observations in E1:
@@
 %P9 (regular): E1 (0:39; 4:49 to 5:28)
-\pquote{P1 (new user, direct, 0:39)}{They made a direct connection immediately.}
+\pquote{P1 (new user, direct, 0:39)}{They connected directly.}
 
 %P2(regular): E1 (1:20, 0:22 to 1:42) 
-\pquote{P2 (new user, direct, 1:20)}{They spent time reading the text on the start screen, and chose to connect directly because they were intimidated by the other option.}
+\pquote{P2 (new user, direct, 1:20)}{They spent time reading the text on the start screen, and connected directly because they were intimidated by the other option.}
 
@@
 \pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy.
-After not being able to fill out the proxy input fields, make a connection with an obfs4 bridge and no proxy.
+After not being able to fill out the proxy input fields, they start over and connected using an obfs4 bridge.
 Note that they didn't try connecting with the obfs3 bridge, which would have worked.}
@@
 %P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
-\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}
-
-In E2, a bridge is required to connect, but any bridge will work. Proxies are optional. 
-Participants in E2 usually tried a direct connection before {\it eventually} trying the recommended bridge.
-Participants spent a fair bit of time trying to answer bridge and proxy questions and trying to configure proxies.
+\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected using the recommended bridge.}
+
+In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
+Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsucccessfully configuring proxies. 
 Observations in E2:
@@
 %P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
-\pquote{P6 (new user, obfs3, 4:04)}{They made a direct connection and giving up after three minutes of waiting. Then, they connected with the recommended bridge.}
+\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly and gave up after minutes of waiting. Then, they connected using the recommended bridge.}
 
 %P13 (regular): E2 (7:48; 0:34 to 9:22) 
-\pquote{P7 (new user, obfs3, 9:22)}{They made a direct connection.
-When that did not work, they restarted Tor Launcher and made another direct connection--and repeated this two more times.
-On the fourth restart, they decided to not use a bridge but tried to configure a proxy, but gave up.
-On the fifth restart, they connect with the recommended bridge.}
+\pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly.
+They restarted Tor Launcher and tried another direct connection--and repeated this two more times.
+On the fourth restart, they tried to configure a proxy, but gave up.
+On the fifth restart, they connected using the recommended bridge.}
 
 %P12 (regular): E2 (10:40; 0:46 to 11:26)
-\pquote{P8 (new user, direct, 10:40)}{They made a direct connection, which fails.
-They then look at proxy settings, get intimidated, and tried the direct connection again, which fails.
-They tried configuring a proxy for 4 minutes, but gave up.
+\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly.
+They then looked at proxy settings, gave up, and tried connecting directly again.
+Then, they tried to configure a proxy, and gave up.
 They tried a direct connection again, which worked.
-E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those relays.}
+E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.}
 
 %P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
-\pquote{P9 (previous Tor user, obfs3, 4:08)}{They made a direct connection.
-Then, they answered no to both bridge and proxy questions, and effectively made another direct connection.
-After that, they connect with the recommended bridge.}
+\pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly.
+Then, they answered no to both bridge and proxy questions, and effectively tried another direct connection.
+After that, they connect using the recommended bridge.}
 
 %P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
-\pquote{P10 (previous Tor user, failed to connect)}{They made a direct connection.
-Then they made a connection with the recommended bridge (~5:42), which should have worked.
-However, our setup experienced a clock drift and Tor does not allow connections with bad clocks.
-The interface did not tell the user about the clock, and they spent the rest of their time trying different bridges and proxies in vain.}
-
-{\color {blue}
-In E3, a bridge is required to connect, but only meek bridges work. Proxies are optional. 
-Summary of E3 connections. 
+\pquote{P10 (previous Tor user, failed to connect)}{They tried a direct connection.
+Then, they tried a connection with the recommended bridge, which should have worked.
+However, our setup experienced a clock drift.
+Tor does not allow connections with bad clocks.
+They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.5\textwidth]{P8-proxy-attempt.png}
+\caption{
+Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
+}
+\label{fig:proxy-attempt}
+\end{figure}
+
+In E3, a bridge was required to connect, but only meek and custom bridges worked. Configuring a proxy was optional.
+Participants in E3 struggled.
+Three failed to connect.
+Of the three that connected, one brute forced options until something worked (P14), another did not understand what they did (P15), and the third used a custom bridge after being convinced meek bridges were not working (P16).
 Observations in E3:
 
-%P6 (heard of Tor): E3 (~26:50) 
-\pquote{P13 (new user, failed to connect)}{summary of what they did here.}
-
 %P14 (regular): E3 FAIL
-\pquote{P14 (new user, failed to connect)}{summary of what they did here.}
+\pquote{P11 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
+Then, they retried connecting directly and retried connecting using the recommended bridge.
+After that, the participant spent the rest of their time trying to configure a proxy and retrying connections with the recommended bridge.}
 
 %P15 (regular): E3 FAIL
-\pquote{P15 (new user, failed to connect)}{summary of what they did here.}
+\pquote{P12 (new user, failed to connect)}{They tried connecting with the recommended bridge.
+They decided that they need a proxy along with the recommended bridge, and spent the rest of their time trying to configure a proxy.}
 
 %P16: E3 (regular) FAIL (why did obfs3 work the first time? It shouldn't have!) 
-\pquote{P16 (new user, failed to connect)}{summary of what they did here.}
+\pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
+They retried connecting with the recommended bridge.
+When that didn't work, they tried to configure a proxy.
+Then, they gave up and tried using other browsers to complete the task.}
+
+%P6 (heard of Tor): E3 (26:48; 0:18 to 27:06) 
+\pquote{P14 (new user, meek-google, 26:48)}{They tried a direct connection by answering no to bridge and proxy questions.
+After waiting a while, they canceled the connection and tried connecting with the recommended bridge.
+They retried connecting with the recommended bridge two more times, then tried to connect with a flashproxy bridge, an obfs4 bridge, a scramblesuit bridge.
+After retrying the recommended bridge again, they made a connection using a meek-google bridge.}
 
 %P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
-\pquote{P11 (new user, meek-azure, 7:31)}{The participant tries connecting directy to the Tor network and connecting to the Tor network with an obfs3 bridge, both of which do not connect to Tor E3.
-Eventually, the participant selects a bridge that will connect to Tor (meek-azure), but was convinced that it would not work because it was taking too slow.
-They go back to the first page and click connect, which uses the configured meek-azure bridge.
-The participant thought that they had connected to Tor directly, and did not realize that the connect button uses whatever settings are toggled in the interface.}
-
-%P5 (has used tor before): E3 (~22:30)
-\pquote{P12 (previous Tor user, )}{summary of what they did here.}
-
-Some qualifiers about how these are supposed to be insights, but we don't know how representative these problems are.
-That's for the summative user testing!
-But these are definitely problems that exist.
-}
+\pquote{P15 (new user, meek-azure, 7:31)}{They tried connecting directly, and then with the recommended bridge.
+After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect.
+They went back to the start screen and clicked connect, which made a connection using meek-azure bridge.
+The participant thought they made a direct connection, but the connect button used settings toggled in the bridge and proxy screens in the interface.}
+
+%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
+\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge.
+After briefly looking at error messages the system log, they retried connecting directly two more times.
+After looking up proxy settings, they tried connecting with a meek-google bridge, but gave up before it could connect.
+They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}
+
+We hope that these participant summaries give some insight into how users may currently struggle with the Tor Launcher interface.
 
 \subsection{Pain Points in Tor Launcher} 
-{\color {blue}
-not trying direct or trying direct, bad progress bar, trying to configure a proxy. How to fix it. 
-Use some quotes here, and say insights from the interview. 
-Quotations come from live transcription and are not necessarily verbatim.
-
-%\pquote{P2}{I don't know what any of those [list of bridges] means, or what that [proxy] means at all.}
-%\pquote{P3}{The vocabulary is really challenging, for someone not doing IT work.}
-%\pquote{P\#}{find when Michael said he didn't know if he was E2 or E3!} 
-%\pquote{P8}{I have no clue what's the difference between flashproxy, fte, etc. I need to know why the built-in ones aren't working. And why do I need a custom bridge if there are options built in?}
-%\pquote{P7}{Since it (obfs3) said recommended, it helped actually, and I selected it because it was chosen.
-I saw the custom bridges option, but I didn't know what to enter there so I went with this (obfs3).}
-%When participants did encounter an error message, they did not understand what errors meant (Fig.~\ref{fig:error}).
-%%The progress bar has a bug that causes it to update only when the level of progress increases.
-%%If progress bar reaches a 90\% and fails, the next attempt have regressed to 0\% and remain there until the progress surpasses 90\%.
-Due to this, participants assumed that their subsequent attempts were wrong, even if they were right.
-%\pquote{P1}{It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.}
-%\pquote{P16}{There doesn't seem to be a timeout on any of this stuff. Am I waiting long enough? It should work immediately.}
-%\pquote{P15}{I didn't know if this computer had any proxy information. I wasn't able to find it if it did.}
-}
+\label{sec:pain-points}
+We talk about the main challenges our participants faced during the experiment. 
+Quotations were transcribed live during the follow-up interview.
+
+Participants found the interface confusing, and were often intimidated by the tasks they were asked to do.
+
+%P8 in the repo, P10 in the paper
+\pquote{P10}{``I have no clue what's the difference between flashproxy, fte, etc. And why do I need a custom bridge if there are options built in?''}
+
+%P3 in the repo, P3 in the paper
+\pquote{P3}{``The vocabulary is really challenging, for someone not doing IT work.''}
+
+Participants were unsure of what to do, and often configured bridges and proxies when they did not need to.
+
+%P15 in the repo, but P12 in the paper
+\pquote{P15}{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
+
+The progress bar had system dependencies that made it update oddly.
+If progress bar reached a 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%.
+Many assumed that their subsequent attempts were wrong because of this.
+
+%P1 in the repo, P15 in the paper
+\pquote{P15}{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
+
+We think users in the wild may also face these challenges, and that changes should be made to mitigate them. We show our attempt in the next section.
 
@@
 
-{\color {blue} WRITE ABOUT PAIN POINTS HERE} We aimed to minimize work, give targeted feedback, and to build a mental model.
+In addition to addressing the pain points we discovered through our formative usability testing (Section~\ref{sec:pain-points}), we aimed to follow usability best practices by minimizing work, giving targeted feedback, and helping users build an understanding of the system.
 
@@
 \begin{itemize}
+\item We fixed the progress bar so that it reflects the current progress on subsequent attempts. 
 \item We switched added indicators to the progress bar to show the progress of bridges and proxies. 
@@
 
-To build a mental model:
+To build an understanding of the system:
 \begin{itemize}

### 2016-11-04 pets2017-paper/pets2017-paper.tex
clean up introduction.

@@
 Our contributions toward an easier bootstrapping process will especially benefit citizens who face Internet censorship.
-If there is an increase in overall users as a result, they add a security bonus by increasing the anonymity set~\cite{dingledine2006anonymity}.
-\\
+If there is an increase in overall users as a result, the additional users increase the anonymity set and benefit all Tor users~\cite{dingledine2006anonymity}.
+
+We started our usability evaluation by inspecting the interface (section~\ref{sec:inspection}) and
+running observing participants interact with it (section~\ref{sec:qualitative}). 
+We opportunistically used the insights from our observations to make some changes (section~\ref{sec:design}).
+Then we quantified how usable the interface was, and 
+how much our changes helped save users time (section~\ref{sec:quantitative}).
+Afterward, we gave some recommendations (section~\ref{sec:recommendations}), addressed
+limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}). \\
 
@@
 \begin{itemize}
-\item an evaluation of the current configuration interface
-\item a redesigned configuration interface
-\item logs of 114 users' connection attempts
-\item failure modes seen during connection attempts
-\item recommended interface changes
-\item alternative bootstrapping approaches
+\item an inspection of the Tor Launcher 5.0.3. interface
+\item user connection attempts in various environments
+\item what users found challenging about the interface
+\item measurements of how many users could connect
+\item measurements of how long users took to connect
+\item patterns seen in the users that failed to connect
+\item some recommendations to improve the interface
 \end{itemize}
-
-We start by introducing relevant concepts (section~\ref{sec:background}) and
-defining the scope of our experiment (section~\ref{sec:scope}). 
-Then, we report user observations and interviews (section~\ref{sec:qualitative}),
-list design principles and interface changes (section~\ref{redesign}),
-state evaluation criteria for testing the interface (section~\ref{sec:eval}), 
-and measure the impact of our design changes (Section~\ref{sec:quantitative}).
-We end with a discussion on what we learned (section~\ref{sec:discussion}),
-limitations of out experiment (section~\ref{sec:limitations}), 
-a look at our work in the context of existing work (section~\ref{sec:related}), and
-a brief conclusion (section~\ref{sec:conclusion}).
 
@@
 \section{Usability Inspection}
+\label{sec:inspection}
 This section discusses our inspection of the configuration interface and the resulting observations.
@@
 \section{Recommendations}
-\label{recommendations}
+\label{sec:recommendations}
 We do believe that adopting our design will help save users time when connecting to Tor.

### 2016-11-04 pets2017-paper/pets2017-paper.tex
clean up appendix.

@@
 Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
+
+%Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
 }
@@
 \label{states} 
-{\color {blue} 
-A reminder of the digraph, and a reference (Figure~\ref{digraph}). Give an example of one input leading to many end states.
-
-% e12; selected proxy type, good address syntax, good ip address, blank port (bridge) 
-% s2; selected proxy type, good address syntax, good ip address, blank port (bridge)
-% e12'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
-% s2'; selected proxy type, good address syntax, good ip address, blank port (no bridge)
-
-success states: 
+An exhaustive list of Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}.
+End states such as e\# and e\#' are equivalent, but e\#' uses a bridge while e\# does not.
+This was generated during the inspection process.\\
+
+\noindent success states: 
 \begin{itemize}
-\item s0: no bridge no proxy connection.
-\item s1: bridge, no proxy connection.
-\item s2: bridge and proxy connection (correct proxy syntax and with default port)
-\item s3: bridge and proxy connection (correct proxy syntax and with specified port)
+\item s0: no bridge no proxy
+\item s1: valid bridge, no proxy
+\item s2: valid bridge and valid proxy (blank port)
+\item s3: valid bridge and valid proxy (specified port)
 \end{itemize}
@@
 \item e1: custom bridge: syntax error
-\item e2: custom bridge: good syntax, bad ip address
-\item e3: hardcoded bridge: bridge blocked in country
-\item e4: bridge blocked in country
-\item e5: blank proxy input
-\item e6: no proxy type
-\item e7: selected proxy type, bad address syntax
-\item e8: selected proxy type, good address syntax, bad ip address, blank port
-\item e9: selected proxy type, good address syntax, bad ip address, good port
-\item e10: selected proxy type, good address syntax, bad ip address, bad port
-\item e11: selected proxy type, good address syntax, good ip address, bad port
-\item e12: selected proxy type, good address syntax, good ip address, blank port
+\item e2: custom bridge: invalid address
+\item e3: hardcoded bridge blocked
+\item e4: custom bridge blocked
+\item e5: proxy type is not selected
+\item e6: proxy: ip address left blank
+\item e7: proxy: syntax error
+\item e8: proxy: invalid ip address, blank port
+\item e9: proxy: invalid ip address, good port
+\item e10: proxy: invalid ip address, bad port
+\item e11: proxy: valid ip address, bad port
+\item e12: proxy: valid ip address, blank port
 \end{itemize}
-}
+
+The same input can lead to different end states.
+Tor Launcher will connect to a proxy successfully with the port left blank if the proxy uses port 80 (s2) but will not if the proxy uses another port (e12).
 
@@
 \label{prescreening-responses}
-{\color{blue} 
-short intro and conclusion. Take self-reported with a grain of salt, but here they are anyways.
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{self-reported-tech-familiarity.png}
-\caption{most participants reported familiarity with terms, even made up ones.}
-\end{figure}
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=.5\textwidth]{self-reported-security-use.png}
-\caption{most people didn't use many security tools.}
-\end{figure}
-}
+We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing.
+We did not use these self-reported answers to influence any process of our testing.
+We show the responses from the particpants that we chose.
+
+We suspect that participants answered dishonestly in hopes of appearing more technically fluent.
+We know this because some reported that they were familiar a term that did not exist (x.511 certificates).
+We inserted this fictional term specifically to detect this.
+Here are our participants' self-reported familiarity with technical terms: \\
+
+{\color {red} MAKE A TABLE HERE} \\
+
+Participants' self-reported use of security tools.
+We assume that self-reported use is the upper bound of how many participants have used these security tools.
+Here are our participants' self-reported use of security tools:\\
+
+{\color {red} MAKE A TABLE HERE}
 
@@
 \label{alternatives}
-{\color {blue}
-Our goal was to deploy impactful, tested changes the Tor configuration interface.
-In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
-Throughout our experiments, we collaborated with Tor developers and focused on discovering changes that could be deployed right away.
-For this reason, we assumed that the configuration process will remain a manual process that requires user inputs, as it is currently deployed.
-However, we list some alternative approaches that seem worth exploring.
-\\
-
-%remember: 	no user inputs, no network inputs, minimize info leaks
-%and:		minimal user work, full user control
-
+We list some of our ideas:\\
 \begin{description}
-\item{\bfseries Automate the configuration.} The most efficient way to connect as many users to the Tor network is to automatically configure their connection on start.
-A naive automation is to try configurations that would most likely work, in order (i.e.
+\item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country.
+one way to do this is to show a list of countries with a corresponding recommended configuration.
+This requires developers to maintain a list of suggestions and that the users trust the suggestions.
+\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publically associated with Tor, using transport that obfuscates their connection.
+If users are not sensitive, let them configure their own bridges and proxies.
+\item{\bfseries Ask users if they know what to do.} If they know, offer the option to manually configure bridges and proxies.
+If they do not know, give suggestions on what to do next or automate the process for them somehow.
+This requires users to answer honestly to the question and to trust the suggestions given.
+\item{\bfseries Automate naively.} Have the interface automatically try configurations that would most likely work, in order (i.e.
 a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
-This leaks to network eavesdroppers that the user is connecting to the Tor network.
-We do not know how much risk is associated with this approach.
-\item {\bfseries automate after the first failure.} The network leak happened. But then this automation would be pretty fingerprintable behavior. 
-\item{\bfseries Ask about the risk.} An alternative to naive automation is to offer manual configuration to those that want to be more cautious and automatically configuring a connection for who are not at risk.
-The complication with this approach is that users may not be qualified to answer if they are at risk or may not trust Tor with this information.
-\item{\bfseries Ask if users know what to do.} Another alternative to naive automation is to offer manual configuration to those that know how to configure their connection and to automate the process for users who do not know how to configure their connection.
-This may prevent the most mistakes, but does not account for the users' risk associated with using Tor.
-\item{\bfseries Suggest configurations.} A way to help users without any automation or questions is to give users information about what would work in their country.
-The first page of the configuration interface can show a list of countries with a corresponding recommended configuration.
-This approach does not require users to answer about their risk, technical ability, or location.
-However, it does require that the user trust the given advice and to correctly configure their settings based on this advice.
-\item{\bfseries Assign configurations.} This is a smart way to automate connections to the Tor network.
-Upon start, the interface detects proxy settings and uses them, if any.
-Then, all users connect to bridges that will always work (such as meek bridges), which assign them a guard relay based on their location, effectively assigning bridges for the user.
+This is what most users would ideally do anyway.
+However, this method leaks to network eavesdroppers that the user is using Tor without the user's awareness.
+\item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies.
+If they fail, then a network adversary already knows that the user is trying to connect to Tor.
+At this point, we believe that it is low risk to naively automate configuring bridges and proxies.
+\item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any.
+Then it automatically connects to some secret bridges that will always work, which assign the user an entry relay that works based on their location.
+This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.
 \end{description}
 
-We believe that automation, asking about risk, and identifying struggling users could enable significant improvements to the configuration process. 
-}
+We believe that these ideas can significantly help users connect to Tor.
 

### 2016-11-04 pets2017-paper/pets2017-paper.tex
reword abstract.

@@
 {
-{\color {blue}
-We evaluate, design, and test the Tor Launcher interface by
-placing users in simulated censorship environments, instructing them to use Tor
-to circumvent censorship, and measuring their interface interactions.
-A 16-participant qualitative study examines user assumptions and common mistakes.
-We use the results as feedback to redesign the configuration interface.
-A 114-participant quantitative study shows that our design changes result in
-a significant reduction in time. We conclude with recommendations for changes 
-to the current interface as well as alternative solutions.
-}
+We perform the first usability test on Tor Launcher, a graphical user interface (GUI) 
+that all Tor Browser users must use to configure their initial connection to the Tor network. 
+We believe that the interface is usable if a new user can to identify what to do,
+knows if and when they do the right thing in the process, 
+and configures the necessary network components to connect to Tor. 
+We use a combination of user observations and user interaction logs to determine
+where the interface is not usable, and quantify how unusable the interface is. We 
+offer some suggestions for the interface based on what 
+we have learned and also suggest alternative approaches 
+to bootstrap a connection to Tor that do not require new users to configure the network components. 
 }

### 2016-11-04 pets2017-paper/pets2017-paper.tex
reword background

@@
 
-We hope that our work helps users more easily connect to Tor.
-The direct and obvious benefit of our work is that is that it may help users who would have previously been unable to configure Tor Browser to use it or that it may save time for users who would have been able to configure a valid connection to the Tor.
-Improving the user experience through user testing has the potential to be beneficial for both the software company (less help desk tickets) and the end users (less frustration).
-
-However, we believe that our work uniquely necesssary and beneficial to Tor Browser.
-Although originally designed for Internet anonymity, using Tor Browser to circumvent censorship has now become sufficiently common that many countries now attempt to block Tor relays for this reason~\cite{winter2012great}.
-Our contributions toward an easier bootstrapping process will especially benefit citizens who face Internet censorship.
-If there is an increase in overall users as a result, the additional users increase the anonymity set and benefit all Tor users~\cite{dingledine2006anonymity}.
+Although Tor Browser was originally designed for Internet anonymity, many now use Tor Browser to circumvent Internet censorship.
+In fact, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
+The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor, but all Tor Browser users must interact with it regardless of why they use Tor Browser.
+
+Tor minimizes collecting user data.
+Therefore, Tor does not have data on how users interact with the configuration interface.
+While we agree that this is respectful to the users, we also believe that this data will be helpful to improve the usability of the configuration interface.
+Improving the usability of the configuration interface has the obvious benefit of helping more users connect to Tor.
+But this is also benefits the Tor company (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
 
@@
 \item patterns seen in the users that failed to connect
-\item some recommendations to improve the interface
+\item recommendations to improve the interface
+\item alternatives to burdening users with configuration 
 \end{itemize}
@@
 \label{sec:background}
-This section discusses network components involved in connecting to Tor, network conditions that require specific network components, and how to configure the involved network components.
+This section covers technical background necessary to understand the study.
 
@@
 
-Tor relays are routers in the Tor Network that receive and pass along Tor traffic. 
-There are three types of Tor relays: guard relays that serve as an entry node, middle relays that forward traffic from an entry node to an exit node, and exit relays which directs traffic to the destination.
-Censors can block access to the Tor network by blocking these relays, which are publicly listed.
+Tor relays are routers in the Tor Network that receive and route Tor traffic. 
+The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays which directs traffic to the destination.
 
 Bridges are unlisted Tor relays that serve as an alternative entry node.
-Bridges can be simple, unlisted relays. 
-But most bridges run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates the traffic. 
-Most transports disguise traffic to defeat on-the-wire identification, relying on the secrecy of their static IP addresses for their effectiveness.
+Bridges can be unlisted relays that behave similarly to a reular Tor relay,  
+but most run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
+Most transports rely on the secrecy of their static IP addresses for their effectiveness.
 These include ``fte'' and ``fte-ipv6''~\cite{fte},
@@
 which encrypt or alter the Tor protocol to appear as random noise.
-Some transports route traffic through other services, avoiding the need for a secret IP address. 
-``flashproxy''~\cite{flashproxy} connects through third parties' web browsers,
+Other transports route traffic through other services and do not need secret IP address. 
+``flashproxy''~\cite{flashproxy} connects through third party web browsers,
 and the ``meek''~\cite{fifield2015blocking} options route traffic
-through content delivery networks.
-Bridges and transports allow a connection to the Tor network when all publicly listed relays and any Tor-looking packets are blocked.
-Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.
+through content delivery networks. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.
 
@@
 
-A local proxy is required to connect 
-in certain managed networks.
 In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
@@
 \subsection{State and Corporate Censorship}
-State level censors can vary in their thoroughness in censorship.
-Some block websites with a combination of IP blacklisting and DNS-poisoning while others that employ more sophisticated techniques such as deep packet inspection and protocol detection.
-In countries that censor services but do not block censorship circumvention tools, any connection to Tor will byass the censorship.
-In other countries, sophisticated state-level censorship require custom bridges or bridges that run specific tranports that route traffic through non-Tor services first.
-
-Some companies and educational institutions have a firewall, which can be bypassed with a proxy (with or without a connection to Tor).
+State level censors block access to the Tor network by blocking Tor relays, which are publicly listed.
+Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
+Any connection to Tor will allow access to censored websites and services.
+Bridges and transports allow a connection to the Tor network when public relays are blocked and Tor-looking packets are censored.
+
+A local proxy is required to connect 
+in certain managed networks (i.e. company and university firewalls).
 
@@
 There are many valid configuration settings to connect to the Tor network.
-For instance, a user who needs a bridge but not need a proxy can connect to Tor with a bridge and proxy, provided that both were configured correctly.
-The set of valid configuration settings vary on the specific network environment.
+A user who needs a bridge can connect to Tor with a bridge and proxy, provided that both were configured correctly.
 

### 2016-11-04 pets2017-paper/pets2017-paper.tex
rewrote conclusion section

@@
 
-{\color {blue}
-We conducted a series of experiments to improve the Tor Browser 5.0.3 configuration interface. A couple sentences to summarize the whole thing. Echo roadmap in intro, but make it summary-like.
-
 %proof that user testing is important and general advice to for more research on Tor
-Tor doesn't collect any information or perform AB testing, so this type of user research is especially important.
-to set it up, get users, computers, consent, and instrumented versions of the software.
-Research can be exploratory (ask users what they want), observational (look at what they do), or testing a hypothesis (verify changes).
+Tor Browser version~4.5 incorporated textual and navigational changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.
+The authors have discussed  alternative ways to bootstrap a connection to Tor without requiring users to configure network components with Tor developers, and they were open to considering some of our ideas for future improvements.
+
+We encourage more researchers to perform this type of usability testing for other parts of Tor Browser and other Tor applications, especially because it provides user insight to company that does not collect user data.
+You can help by performing usability research that uncovers unknown problems, tests out new ideas, or verifies the impact of recently made changes.
 We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
 Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
-
-%Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface.
-}
 

### 2016-11-07 pets2017-paper/pets2017-paper.tex
mark demographics red to remember to redo

@@
 We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
-Of our 16 recruited participants, 53.3\% were male.
+{\color {red} Of our 16 recruited participants, 53.3\% were male.
 Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$).
-93.3\% of our participants had college education.
-We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
+93.3\% of our participants had college education.} We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
 We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.
@@
 
-Of our recruited 124 participants, 56.8\% were male.
+{\color {red} Of our recruited 124 participants, 56.8\% were male.
 Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$).
 56.8\% were male.
-84.8\% of our participants had a college education.
-We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
+84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
 Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.

### 2016-11-07 pets2017-paper/pets2017-paper.tex
redo recommendations and conclusions

@@
 \begin{itemize}
-\item {\bfseries Use less words.} Shorten text so users read it.
-\item {\bfseries Give advice.} Discourage users from configuring optional components. Add a secondary recommendation (try meek if obfs3 doesn't work). 
 \item {\bfseries Hide infrequent options.} Hide the proxy configuration screen and less-used transports.
+None of our participants connected using flashproxy, fte, fte-ipv6, or scramblesuit transport bridges.
+\item {\bfseries Give advice.} Discourage users from configuring optional components.
+Add a secondary recommendation for bridges (try meek if obfs3 doesn't work, use meek if you are in Syria) to help users in need.
 \item {\bfseries Minimize work.} Detect if users need a proxy or not. Redirect users to the relevant pages on error (i.e. redirect to the bridge screen the bridge fails).  
-\item {\bfseries Add system visibility.}  Show users their bridge and proxy settings before and during connection. Fix the progress bar updating weirdness.
-\item {\bfseries Provide feedback.} Tell users what to do when a specific error occurs (i.e. try agin, fix bridges, etc.). 
+\item {\bfseries Provide feedback.} Tell users what to do when a specific error occurs (i.e.
+try the same connection again, pick another bridge, try without a proxy, etc.).
+Show users their bridge and proxy settings before and during connection.
+Fix the progress bar so that it updates on subsequent connections.
 \end{itemize}
@@
 \label{sec:conclusion}
+The Tor Launcher GUI allows most users to connect to the Tor network, provided that the user's connection does not require a proxy or a non-default bridge.
+User observation showed that participants were intimidated of the tasks, unsure of what to do, and likely to get stuck configuring proxies that they did not need.
+User testing showed that most people take more than 10 minutes to connect to Tor if they need to use bridges.
 
 %proof that user testing is important and general advice to for more research on Tor
-Tor Browser version~4.5 incorporated textual and navigational changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.
-The authors have discussed  alternative ways to bootstrap a connection to Tor without requiring users to configure network components with Tor developers, and they were open to considering some of our ideas for future improvements.
-
-We encourage more researchers to perform this type of usability testing for other parts of Tor Browser and other Tor applications, especially because it provides user insight to company that does not collect user data.
-You can help by performing usability research that uncovers unknown problems, tests out new ideas, or verifies the impact of recently made changes.
-We encourage the use of simulated censorship environments as a tool for user testing censorship circumvention software.
-Not only do simulated environments avoid rerouting traffic through a censoring country's networks, their reproducibility and stability are ideal for experiments.
+We encourage usability testing for Tor Browser and other Tor applications because it provides user insight tfor products without user interaction data.
+Tor Browser version~4.5 incorporated changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.
+We also talked to Tor developers about ways to automate the bootstrapping process to Tor.
 

### 2016-11-07 pets2017-paper/pets2017-paper.tex
eek, stopped wordsmithing halfway. Should probably get feedback on rough draft first

@@
 Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
-Any connection to Tor will allow access to censored websites and services.
-Bridges and transports allow a connection to the Tor network when public relays are blocked and Tor-looking packets are censored.
-
-A local proxy is required to connect 
-in certain managed networks (i.e. company and university firewalls).
+This means that users can connect to the Internet, but not through Tor.
+The thoroughness of cenrsorship is what requries different bridges and transports.
+
+A local proxy is required to connect in certain managed networks (i.e.
+company and university firewalls).
+This usually means that users cannot connect to the Internet at all without a proxy, including conencting to the Internet through Tor.
+The user must be able to connect to the Internet through thier proxy before trying to connect to the Internet with Tor.
 
@@
 
-Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields. The user must locate and input this information.
+Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields.
+The user must locate and input this information.
+If the computer is already configured to use a proxy, the information can be found in other browsers.
+The interface tells users to ``check Internet settings in another browser'' if they are unsure of the proxy information.
 
@@
 Two researchers first performed a cognitive walkthough~\cite{cognitive-walkthrough} to prepare for user testing.
-A cognitive walkthough is evaluation method in which usability evaluators and product experts work through a series of tasks from the perspective of the user to understand a system's learnability for new or infrequent users.
-
-We then conducted a formative usability test~\cite{formative} that found where and why users have difficulty.
-Formative usability testing is a support tool designed to gain insight into how the design can be improved.
-5 users is considered to be user testing's maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited for 5 participants in each experimental condition.
-
-Formative testing is usually used as feedback for design iterations.
-We opportunistically used our observations to make design changes to the configuration interface.
-We believed that the process of a identifying design principles, proposing design changes, and showing an alternative interface was insightful in itself---and had the potential to discover impactful changes.
-
-We concluded with a summative usability test~\cite{summative} that determined the usability of an interface.
-We test the current interface to evaluate it.
-We also opportunistically test the redesigned interface.
-Summative usability testing is a quality assurance tool designed to test features in a design.
-In short, formative testing tells you {\it what} is or is not usable, while summative testing testing tells you {\it if} it is or is not usable.
-20 users is considered to be the minimum number to statistically significant measurments~\cite{howmanyusers}, so we recruited for 20 participants in each experimental condition.
+A cognitive walkthough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.
+
+We then conducted a formative usability test~\cite{formative} that found where and why users struggle.
+This testing is usually used as a support tool to find improvements.
+Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each experimental condition.
+
+We opportunistically used our observations to make changes to the interface.
+We believed that the process of identifying design principles, drafting design changes, and testing an alternative interface would be insightful and have the potential to discover impactful changes.
+
+We concluded with a summative usability test~\cite{summative} that measured the usability of the current and redesigned interface.
+This testing is a usually used as quality assurance tool to test features.
+In short, formative testing tells you {\it what} is is not usable, while summative testing testing tells you {\it if} it is or is not usable.
+Twenty users is considered to be a minimum for statistically significant measurments~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.
 
@@
 \begin{itemize}
-\item {\bfseries Completion rate:}  percentage of users that eventually connect to Tor in an experimental condition. 
-\item {\bfseries Connection time:} time from Tor Browser startup to the first successful Tor bootstrap. 
-\item {\bfseries Configuration time:} time spent in the Tor Launcher GUI configuring network components.
+\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
+\item {\bfseries Connection time:} time from Tor Browser startup to a succcessful connection to Tor. 
+\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
 \end{itemize}
@@
 We measured task time two different ways.
-Connection time captured the amount of time users take to use the configuration interface to connect to Tor.
-This included time users spent waiting while a Tor Browser establishes a connection to Tor, which can dominate the measurement.
-Configuration time captured the amount of time users spent configuring bridges and proxies.
+Connection time measures how long users use the configuration interface, which includes time  spent waiting while a Tor Browser establishes a connection to Tor, which can dominate the measurement.
+Configuration time measures the time users spent actively configuring bridges and proxies.
 
@@
 \label{sec:environments}
-We simulated three environments (which we refer to as E1, E2, and E3), 
-which are in the order of increasing severity in censorship.
-Table~\ref{tab:environments} summarizes our environments and what network components are required to make a  connection to Tor.
-We chose to
-simulate environments for the stability, reproducibility, and simplicity of the 
-experiment, as real censored networks are voilatile, subject to change, and complex.
+We use versions of Tor Browser~5.0.3, 
+the most recent stable release at the time~\cite{torbrowser-503}.
+There were new releases during the experiments, but
+we used the same version throughout to not introduce
+confounding factors.
+
+We simulated three environments of increasing severity in censorship (E1, E2, E3).
+Table~\ref{tab:environments} summarizes them and explains what is required to connect to Tor. We chose to 
+simulate environments for the stability and reproducibility of the 
+experiment, as real censored networks are voilatile and complex.
 
@@
 Summary of our simulated censorship environments.
-E1 only requires participants to click ``Connect'';
-E2 requires a built-in bridge;
-and E3 requires a specific type of built-in bridge
-or manual configuration of a custom bridge.
+E1 only requires users to connect directly;
+E2 requires users to connect with a built-in bridge;
+and E3 requires users to connect with a specific type of built-in bridge
+or a custom bridge.
 E2's blocking is a superset of E1's;
@@
 
-We used features of the Windows operating system 
-to block websites and Tor relays. 
-We added entries to the hosts file to
-mapping domain names to the address 127.0.0.1, which simulated
-website by using Tor.
-We blocked torproject.org and its respective subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers (E1, E2, E3).
-We blocked wikipedia.org, cnn.com, and their respective subdomains to create an artificial task to visit a
-``censored'' website as motivation to connect to Tor during the experiment (E1, E2, E3). 
-We specified Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3).
-
-For our experiments, we use versions of Tor Browser~5.0.3, 
-the most recent stable release at the time~\cite{torbrowser-503}.
-Though there were new releases during the experiments,
-we used the same version throughout to not introduce
-confounding factors.
+We used Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3). 
+We used the Windows operating system hosts file to to block websites by
+mapping domain names to localhost (127.0.0.1) (E1, E2, E3).
+We blocked torproject.org and its subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers.
+We blocked wikipedia.org, cnn.com, and their subdomains to create``censored'' sites for the experiment.
 
@@
 \subsection{Observations}
-Through this process, we observed that:  \\
-\begin{itemize} 
-\item The interface does not presuppose that a user has previous exposure to Tor. 
-\item The interface provides recommendations in text and populates options with recommended settings. 
-\item The user has the burden of determining if Tor relays are blocked or if a proxy is required. 
-\item A user can optionally configure a bridge and proxy even if they are not necessary to connect to Tor. 
-\item Free-form inputs lead to many potential error states. 
-\end{itemize}
+The interface did not suppose that a user has previous exposure to Tor.
+To help new users, it provided recommendations in the text and populated some options (such as bridges) with recommended options.
+However, the interface did require the user to figure out if Tor relays are blocked or if a proxy is required.
+And the interface did not discourage users from configuring components that are not necessary to connect to Tor.
+The proxy configuration has the potential for a lot of error, as there are a many free-form input fields.
+
+More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies.
+We doubted that users would have an understanding of how the Internet well enough to even explain how Tor relays, bridges, and proxies worked.
+Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing.
+The notion of bridges and transports are also specific to Tor, and not other censorship circumvention software.
 
@@
 We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.
+The main objective of this question was to identify new users versus infrequent users.
+We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.
 
@@
 Before each participant entered the room, we ran a script on the computer that
-set up one of the three simulated environments (E1, E2, or E3) and started the screen recording.
+set up one of the three simulated environments (E1, E2, or E3) and started the recording the computer screen.
 
@@
 
-\begin{figure}
-\centering
-\includegraphics[width=0.5\textwidth]{P8-proxy-attempt.png}
-\caption{
-Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
-}
-\label{fig:proxy-attempt}
-\end{figure}
-
 In E3, a bridge was required to connect, but only meek and custom bridges worked. Configuring a proxy was optional.
@@
 Observations in E3:
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.5\textwidth]{P8-proxy-attempt.png}
+\caption{
+Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
+}
+\label{fig:proxy-attempt}
+\end{figure}
 
@@
 %proof that user testing is important and general advice to for more research on Tor
-We encourage usability testing for Tor Browser and other Tor applications because it provides user insight tfor products without user interaction data.
+We encourage usability testing for Tor Browser and other Tor applications because it provides user insight for products without user interaction data.
 Tor Browser version~4.5 incorporated changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.

### 2016-11-10 pets2017-paper/pets2017-paper.tex
add in the interface screenshots

@@
 \usepackage{adjustbox}
+\usepackage{subcaption}
 %\usepackage{hyperref}
@@
 \centering
-\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
+	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
+	\label{fig:old-first}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
+	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
+	\label{fig:old-bridge}
+\end{subfigure}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
+	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
+	\label{fig:old-bridge-settings}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
+	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
+	\label{fig:old-bridge-combobox}
+\end{subfigure}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
+	\caption{Instructions on getting a custom bridge.Clicking the ``Help'' button in Figures~\ref{fig:old-bridge settings} and \ref {fig:old-bridge-combobox} leads to this page.}
+	\label{fig:old-bridge-help}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
+	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
+	\label{fig:old-proxy}
+\end{subfigure}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
+	\caption{Where users fill in proxy information.}
+	\label{fig:old-proxy-yes}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
+	\caption{The progress bar.}
+	\label{fig:old-progress}
+\end{subfigure}
 \caption{
-A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
+The Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
 }
@@
 \centering
-\includegraphics[width=\textwidth]{placeholder-fullpage.pdf}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
+	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored enviroinments.}
+	\label{fig:new-first}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
+	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
+	\label{fig:new-proxy}
+\end{subfigure}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
+	\caption{There is only one bridge screen now. The default is to connect without one.}
+	\label{fig:new-nobridge}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
+	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
+	\label{fig:new-bridge}
+\end{subfigure}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
+	\caption{The transports selections are the same.}
+	\label{fig:new-bridge-combobox}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
+	\caption{These instuctions are also the same.}
+	\label{fig:new-bridge-help}
+\end{subfigure}
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
+	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
+	\label{fig:new-summary}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.35\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
+	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
+	\label{fig:new-progress}
+\end{subfigure}
 \caption{
-A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. 
+A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
 }

### 2016-11-10 pets2017-paper/pets2017-paper.tex
initialize tables for demographics data in appendix

@@
 
+{\color {red}
 \section{Prescreening Survey Responses}
@@
 We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing.
-We did not use these self-reported answers to influence any process of our testing.
 We show the responses from the particpants that we chose.
+
+\begin{table}[h]
+\centering
+\begin{tabular}{l r r}
+& Familiarity\\
+\noalign{\hrule}
+Malware & 00/00\\
+Proxy services & 00/00\\
+Phishing & 00/00\\
+SSL & 00/00\\
+X.511 certificates & 00/00\\
+Tor & 00/00\\
+\end{tabular}
+\caption{
+An overview of the results of the experiment. Those who
+failed to connect were assigned the maximum time of 40:08.
+}
+\label{table:selfreported-tech}
+\end{table}
 
@@
 We inserted this fictional term specifically to detect this.
-Here are our participants' self-reported familiarity with technical terms: \\
-
-{\color {red} MAKE A TABLE HERE} \\
-
-Participants' self-reported use of security tools.
+
+\begin{table*}[h]
+\centering
+\begin{tabular}{l r r r r r}
+& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{}\\
+& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily}\\
+\noalign{\hrule}
+HTTPS on web pages& 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+Proxies or censorship circumvention tools & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+Virtual private networks (VPNs) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+File or disk encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+Anonymity systems (e.g. Tor) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+Email encryption (e.g. PGP) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+Instant messaging encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+Voice communication encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+\end{tabular}
+\caption{
+An overview of the results of the experiment. Those who
+failed to connect were assigned the maximum time of 40:08.
+}
+\label{table:selfreported-software}
+\end{table*}
+
 We assume that self-reported use is the upper bound of how many participants have used these security tools.
-Here are our participants' self-reported use of security tools:\\
-
-{\color {red} MAKE A TABLE HERE}
+}
 

### 2016-11-10 pets2017-paper/pets2017-paper.tex
fix broken reference

@@
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
-	\caption{Instructions on getting a custom bridge.Clicking the ``Help'' button in Figures~\ref{fig:old-bridge settings} and \ref {fig:old-bridge-combobox} leads to this page.}
+	\caption{Instructions on getting a custom bridge.Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
 	\label{fig:old-bridge-help}

### 2016-11-11 pets2017-paper/pets2017-paper.tex
Spell check.

@@
 Bridges are unlisted Tor relays that serve as an alternative entry node.
-Bridges can be unlisted relays that behave similarly to a reular Tor relay,  
-but most run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
+Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
+but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
 Most transports rely on the secrecy of their static IP addresses for their effectiveness.
@@
 This means that users can connect to the Internet, but not through Tor.
-The thoroughness of cenrsorship is what requries different bridges and transports.
+The thoroughness of censorship is what requires different bridges and transports.
 
@@
 company and university firewalls).
-This usually means that users cannot connect to the Internet at all without a proxy, including conencting to the Internet through Tor.
-The user must be able to connect to the Internet through thier proxy before trying to connect to the Internet with Tor.
+This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
+The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.
 
@@
 \subsection{Testing Pipeline} 
-Two researchers first performed a cognitive walkthough~\cite{cognitive-walkthrough} to prepare for user testing.
-A cognitive walkthough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.
+Two researchers first performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing.
+A cognitive walkthrough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.
 
@@
 In short, formative testing tells you {\it what} is is not usable, while summative testing testing tells you {\it if} it is or is not usable.
-Twenty users is considered to be a minimum for statistically significant measurments~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.
+Twenty users is considered to be a minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.
 
@@
 \item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
-\item {\bfseries Connection time:} time from Tor Browser startup to a succcessful connection to Tor. 
+\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
 \item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
@@
 simulate environments for the stability and reproducibility of the 
-experiment, as real censored networks are voilatile and complex.
+experiment, as real censored networks are volatile and complex.
 
@@
 \subsection{Procedure} 
-Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
+Two researchers performed the cognitive walkthrough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
 We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
@@
 Leaf nodes are various end states (quit, success, or error).
-Tansitions between these nodes denote user actions.
+Transitions between these nodes denote user actions.
 For details of each end state, see Appendix ~\ref{states}.
@@
 \subsection{Recruitment}
-We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
+We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
 We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
@@
 we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses.
-We then followed up with participant-specific questions to verify any hypotgit heses we had from observation (e.g.
+We then followed up with participant-specific questions to verify any hypotheses   we had from observation (e.g.
 ``the participant was selecting bridges at random'').
@@
 \subsection{Results} 
-We give a summary of what our participants did below. We watched the screen recording to summerize their actions and referred to their interviews for insight into why they took specific actions.
+We give a summary of what our participants did below. We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions.
 
@@
 In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
-Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsucccessfully configuring proxies. 
+Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies. 
 Observations in E2:
@@
 Three researchers agreed on security and usability design principles. 
-We then rewatched screen capture videos and read interview transcirptions to brainstorm design changes.
+We then rewatched screen capture videos and read interview transcriptions to brainstorm design changes.
 We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind.
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
-	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored enviroinments.}
+	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
 	\label{fig:new-first}
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
-	\caption{These instuctions are also the same.}
+	\caption{These instructions are also the same.}
 	\label{fig:new-bridge-help}
@@
 
-\subsection{Design Princples} 
+\subsection{Design Principles} 
 The interface currently favors a guided manual configuration over an automated configuration with network probing.
@@
 We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}.
-We recruited 65 participants from Craiglist and 59 participants from the <redacted lab> participant pool.
+We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool.
 <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants.
@@
 84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
-Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.
+Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
 
@@
 Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks.
-If they wished to participate, they were ifnormed again in writing and consented by signing the document.
+If they wished to participate, they were informed again in writing and consented by signing the document.
 To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.
 
-The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvnt censorship (Appendix~\ref{quantitative-script}).
+The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvent censorship (Appendix~\ref{quantitative-script}).
 This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so.
@@
 an obfs3 bridge (the recommended option)---none used 
-flashproxy, fte, fte-ipv6, obf4, or scramblesuit bridges to connect. 
+flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
 Most successful E3 participants
@@
 Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor.
-We belive this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails.
+We believe this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails.
 Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed.
@@
 \subsubsection{Connection time} 
-Connection time is the time from Tor Browser starup to the first successful Tor bootstrap.
+Connection time is the time from Tor Browser startup to the first successful Tor bootstrap.
 Non-finishing participants are assigned the maximum experiment time of 40:08.
@@
 Table~\ref{table:median_time} shows the percentage of time spent on each screen.
-Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valild configuration).
+Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valid configuration).
 
@@
 We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1.
-and 2) some mistakes, such as using a syntactically valid but unsuable proxy, generate non-interruping warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
+and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
 But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.
@@
 In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. 
-On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or cutsom bridge took over 20 minutes.
+On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.
 
@@
 We are aware that our participants were likely motivated differently compared to real users.
-We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward.
+We believe that participants were likely overmotivated to connect to Tor because they were being observed and receiving a monetary reward.
 If true, this makes our results are a conservative estimate of the current usability problems.
@@
 We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
-The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent.
-Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
+The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent.
+Additionally, we acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
 
@@
 <Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours.
-<Redacted> and <redacted> were instrumental during the design process, as they helped me interate through many not-so-great ideas.
+<Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.
 <Redacted>,and <redacted> provided me with insider insight into the design decisions made at Tor.
@@
 We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing.
-We show the responses from the particpants that we chose.
+We show the responses from the participants that we chose.
 
@@
 This requires developers to maintain a list of suggestions and that the users trust the suggestions.
-\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publically associated with Tor, using transport that obfuscates their connection.
+\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection.
 If users are not sensitive, let them configure their own bridges and proxies.

### 2016-11-11 pets2017-paper/pets2017-paper.tex
Tiny typo fixes.

@@
 \begin{itemize}
-\item an inspection of the Tor Launcher 5.0.3. interface
+\item an inspection of the Tor Launcher 5.0.3 interface
 \item user connection attempts in various environments
@@
 Tor relays are routers in the Tor Network that receive and route Tor traffic. 
-The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays which directs traffic to the destination.
+The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays which direct traffic to the destination.
 
@@
 We blocked torproject.org and its subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers.
-We blocked wikipedia.org, cnn.com, and their subdomains to create``censored'' sites for the experiment.
+We blocked wikipedia.org, cnn.com, and their subdomains to create ``censored'' sites for the experiment.
 
@@
 \caption{
-The Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
+The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
 }
@@
 Transitions between these nodes denote user actions.
-For details of each end state, see Appendix ~\ref{states}.
+For details of each end state, see Appendix~\ref{states}.
 }
@@
 %P3(regular): E1 (N/A; 5:47 to 6:26) 
-\pquote{P3 (new user, obfs3, ~1:39)}{They connected with the recommended bridge. They were also going to use a proxy, but decided not to when they saw the proxy input fields.}
+\pquote{P3 (new user, obfs3, 1:39)}{They connected with the recommended bridge. They were also going to use a proxy, but decided not to when they saw the proxy input fields.}
 
@@
 \pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly.
-They restarted Tor Launcher and tried another direct connection--and repeated this two more times.
+They restarted Tor Launcher and tried another direct connection---and repeated this two more times.
 On the fourth restart, they tried to configure a proxy, but gave up.
@@
 \caption{
-A redesigned version of the Tor Browser 5.0.3. Tor Launcher GUI. Screens are in the order that they appear. 
+A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
 }
@@
 Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment.
-Each computer was manually assigned one of the six interface-environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
+Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
 
@@
 %things to keep in mind
-We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1.
-and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
+We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1, and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
 But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.
@@
 <Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.
-<Redacted>,and <redacted> provided me with insider insight into the design decisions made at Tor.
+<Redacted>, and <redacted> provided me with insider insight into the design decisions made at Tor.
 % Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.

### 2016-11-11 pets2017-paper/pets2017-paper.tex
Proper prime notation.

@@
 Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes.
-Neither the Tor Browser's 5.0.3.
-Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.
+Neither the Tor Browser's 5.0.3 Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.
 
@@
 An exhaustive list of Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}.
-End states such as e\# and e\#' are equivalent, but e\#' uses a bridge while e\# does not.
+End states such as e\# and $\mbox{e\#}^\prime$ are equivalent, but $\mbox{e\#}^\prime$ uses a bridge while e\# does not.
 This was generated during the inspection process.\\

### 2016-11-11 pets2017-paper/pets2017-paper.tex
\chi^2 rather than X^2.
add formative demographics

--- 2016-11-11 pets2017-paper/pets2017-paper.tex
@@
 Bridges are unlisted Tor relays that serve as an alternative entry node.
-Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
-but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
+Bridges can be unlisted relays that behave similarly to a reular Tor relay,  
+but most run a pluggable tranport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
 Most transports rely on the secrecy of their static IP addresses for their effectiveness.
@@
 This means that users can connect to the Internet, but not through Tor.
-The thoroughness of censorship is what requires different bridges and transports.
+The thoroughness of cenrsorship is what requries different bridges and transports.
 
@@
 company and university firewalls).
-This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
-The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.
+This usually means that users cannot connect to the Internet at all without a proxy, including conencting to the Internet through Tor.
+The user must be able to connect to the Internet through thier proxy before trying to connect to the Internet with Tor.
 
@@
 \subsection{Testing Pipeline} 
-Two researchers first performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing.
-A cognitive walkthrough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.
+Two researchers first performed a cognitive walkthough~\cite{cognitive-walkthrough} to prepare for user testing.
+A cognitive walkthough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.
 
@@
 In short, formative testing tells you {\it what} is is not usable, while summative testing testing tells you {\it if} it is or is not usable.
-Twenty users is considered to be a minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.
+Twenty users is considered to be a minimum for statistically significant measurments~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.
 
@@
 \item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
-\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
+\item {\bfseries Connection time:} time from Tor Browser startup to a succcessful connection to Tor. 
 \item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
@@
 simulate environments for the stability and reproducibility of the 
-experiment, as real censored networks are volatile and complex.
+experiment, as real censored networks are voilatile and complex.
 
@@
 \subsection{Procedure} 
-Two researchers performed the cognitive walkthrough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
+Two researchers performed the cognitive walkthough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
 We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
@@
 Leaf nodes are various end states (quit, success, or error).
-Transitions between these nodes denote user actions.
+Tansitions between these nodes denote user actions.
 For details of each end state, see Appendix ~\ref{states}.
@@
 \subsection{Recruitment}
-We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
+We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an presecreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
 We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
-{\color {red} Of our 16 recruited participants, 53.3\% were male.
-Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$).
-93.3\% of our participants had college education.} We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
+Of our 16 recruited participants, 50\% were male.
+Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
+One participant declined to submit their age, so the previous calcuations were done without thier information.
+100\% had at least some college education.
+We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
 We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.
@@
 We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.
+
+% gender: Male: 8/Female: 8
+% education: At least some college 16
+% ages: 22, 23, 34, 52, 25, 22, 29, 21, 25, didn't answer, 20, 20, 26, 24, 62, 52
 
@@
 we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses.
-We then followed up with participant-specific questions to verify any hypotheses   we had from observation (e.g.
+We then followed up with participant-specific questions to verify any hypotgit heses we had from observation (e.g.
 ``the participant was selecting bridges at random'').
@@
 \subsection{Results} 
-We give a summary of what our participants did below. We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions.
+We give a summary of what our participants did below. We watched the screen recording to summerize their actions and referred to their interviews for insight into why they took specific actions.
 
@@
 In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
-Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies. 
+Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsucccessfully configuring proxies. 
 Observations in E2:
@@
 Three researchers agreed on security and usability design principles. 
-We then rewatched screen capture videos and read interview transcriptions to brainstorm design changes.
+We then rewatched screen capture videos and read interview transcirptions to brainstorm design changes.
 We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind.
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
-	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
+	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored enviroinments.}
 	\label{fig:new-first}
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
-	\caption{These instructions are also the same.}
+	\caption{These instuctions are also the same.}
 	\label{fig:new-bridge-help}
@@
 
-\subsection{Design Principles} 
+\subsection{Design Princples} 
 The interface currently favors a guided manual configuration over an automated configuration with network probing.
@@
 We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}.
-We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool.
+We recruited 65 participants from Craiglist and 59 participants from the <redacted lab> participant pool.
 <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants.
@@
 84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
-Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
+Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craiglist recruited participants and half <redacted lab>  pool participants.
 
@@
 Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks.
-If they wished to participate, they were informed again in writing and consented by signing the document.
+If they wished to participate, they were ifnormed again in writing and consented by signing the document.
 To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.
 
-The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvent censorship (Appendix~\ref{quantitative-script}).
+The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvnt censorship (Appendix~\ref{quantitative-script}).
 This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so.
@@
 an obfs3 bridge (the recommended option)---none used 
-flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
+flashproxy, fte, fte-ipv6, obf4, or scramblesuit bridges to connect. 
 Most successful E3 participants
@@
 Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor.
-We believe this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails.
+We belive this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails.
 Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed.
@@
 \subsubsection{Connection time} 
-Connection time is the time from Tor Browser startup to the first successful Tor bootstrap.
+Connection time is the time from Tor Browser starup to the first successful Tor bootstrap.
 Non-finishing participants are assigned the maximum experiment time of 40:08.
@@
 Table~\ref{table:median_time} shows the percentage of time spent on each screen.
-Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valid configuration).
+Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valild configuration).
 
@@
 We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1.
-and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
+and 2) some mistakes, such as using a syntactically valid but unsuable proxy, generate non-interruping warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
 But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.
@@
 In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. 
-On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.
+On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or cutsom bridge took over 20 minutes.
 
@@
 We are aware that our participants were likely motivated differently compared to real users.
-We believe that participants were likely overmotivated to connect to Tor because they were being observed and receiving a monetary reward.
+We believe that participants were likely overmotivated to connect to Tor because they were being observed and recieving a monetary reward.
 If true, this makes our results are a conservative estimate of the current usability problems.
@@
 We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
-The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent.
-Additionally, we acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
+The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OSx or Linux equivalent.
+Additionally, we acknowledge that participants' unfamilarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
 
@@
 <Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours.
-<Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.
+<Redacted> and <redacted> were instrumental during the design process, as they helped me interate through many not-so-great ideas.
 <Redacted>,and <redacted> provided me with insider insight into the design decisions made at Tor.
@@
 We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing.
-We show the responses from the participants that we chose.
+We show the responses from the particpants that we chose.
 
@@
 \noalign{\hrule}
-Malware & 00/00\\
-Proxy services & 00/00\\
-Phishing & 00/00\\
-SSL & 00/00\\
-X.511 certificates & 00/00\\
-Tor & 00/00\\
+Malware & 81\% (13/16) \\ %13/16
+Proxy services & 69\% (11/16)\\ %11/16
+Phishing & 63\% (10/16)\\ %10/16
+SSL & 63\% (10/16)\\%10/16
+X.511 certificates & 25\% (4/16)\\ %4/16
+Tor & 50\% (8/16)\\ %8/16
 \end{tabular}
@@
 \centering
-\begin{tabular}{l r r r r r}
-& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{}\\
-& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily}\\
+\begin{tabular}{l r r r r r r}
+& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Missing}\\
+& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily} & \multicolumn{1}{r}{answer}\\
 \noalign{\hrule}
-HTTPS on web pages& 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-Proxies or censorship circumvention tools & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-Virtual private networks (VPNs) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-File or disk encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-Anonymity systems (e.g. Tor) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-Email encryption (e.g. PGP) & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-Instant messaging encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
-Voice communication encryption & 00/00 & 00/00 & 00/00 & 00/00 & 00/00 \\
+HTTPS on web pages				& 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 25\% (4/16) & 56\% (9/16) & 0\% (0/16) \\
+Proxies or censorship circumvention tools & 50\% (8/16) & 13\% (2/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 13\% (2/16) \\
+Virtual private networks (VPNs) 		& 44\% (7/16) & 31\% (5/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
+File or disk encryption 				& 50\% (8/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 25\% (4/16) & 1\% (1/16) \\
+Anonymity systems (e.g. Tor) 			& 63\% (10/16) & 13\% (2/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) \\
+Email encryption (e.g. PGP) 			& 50\% (8/16) & 19\% (3/16) & 19\% (3/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
+Instant messaging encryption 			& 44\% (7/16) & 25\% (4/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 1\% (1/16) \\
+Voice communication encryption 		& 81\% (13/16) & 1\% (1/16) & 1\% (1/16) & 0\% (0/16) & 0\% (0/16) &1\% (1/16)\\
 \end{tabular}
@@
 This requires developers to maintain a list of suggestions and that the users trust the suggestions.
-\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection.
+\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publically associated with Tor, using transport that obfuscates their connection.
 If users are not sensitive, let them configure their own bridges and proxies.

### 2016-11-11 pets2017-paper/pets2017-paper.tex

--- 2016-11-11 pets2017-paper/pets2017-paper.tex
@@
 We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
-{\color {red} Of our 16 recruited participants, 53.3\% were male.
-Ages ranged from 20 to~62 years ($\mu = 24.5$, $\sigma = 12.6$).
-93.3\% of our participants had college education.} We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
+Of our 16 recruited participants, 50\% were male.
+Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
+One participant declined to submit their age, so the previous calcuations were done without thier information.
+100\% had at least some college education.
+We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
 We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.
@@
 %success rate and version
-Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $X^2 = 0.0126$, $df = 2$, $p = 0.994$).
+Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$).
 That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

### 2016-11-11 pets2017-paper/pets2017-paper.tex
clean up prescreening appendix

@@
 
-{\color {red}
 \section{Prescreening Survey Responses}
@@
 We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing.
-We show the responses from the participants that we chose.
+We did {\it not} use this information to influence the experimental procedure (i.e.
+use this to pick their environment).
+We show their responses:
 
@@
 \caption{
-An overview of the results of the experiment. Those who
-failed to connect were assigned the maximum time of 40:08.
+Formative users' self-reported familiarity with various security terms. 
 }
@@
 
+Table~\ref{table:selfreported-software} lists their self-reported familiarity with various security concepts.
+Some reported that they were familiar a term that did not exist (x.511 certificates).
+We inserted this fictional term specifically to detect this.
 We suspect that participants answered dishonestly in hopes of appearing more technically fluent.
-We know this because some reported that they were familiar a term that did not exist (x.511 certificates).
-We inserted this fictional term specifically to detect this.
 
@@
 \caption{
-An overview of the results of the experiment. Those who
-failed to connect were assigned the maximum time of 40:08.
+Formative users' self-reported use of various security software. 
 }
@@
 
-We assume that self-reported use is the upper bound of how many participants have used these security tools.
-}
+Table~\ref{table:selfreported-software} lists their self-reported use of security software.
+Similarly to self-reported familiarity, we assume that participants answered to appear more technically fluent.
+We assumed that this self-reported use of security tools is an approximate upper bound of how many have actually used these security tools.
 

### 2016-11-11 pets2017-paper/pets2017-paper.tex
changes from David's feedback

@@
 Improving the usability of the configuration interface has the obvious benefit of helping more users connect to Tor.
-But this is also benefits the Tor company (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
+But this is also benefits the Tor Project (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
 
@@
 Tor relays are routers in the Tor Network that receive and route Tor traffic. 
-The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays which direct traffic to the destination.
+The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays that direct traffic to the destination.
 
@@
 but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
+Pre-configured bridges can be selected by ``Transport type,'' which refer to various
+censorship circumvention technologies (``pluggable transports'').
 Most transports rely on the secrecy of their static IP addresses for their effectiveness.
@@
 and the ``meek''~\cite{fifield2015blocking} options route traffic
-through content delivery networks. Fig.~\ref{fig:bridge-options} shows the bridge and transport options at the time of the study.
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.5\textwidth]{bridge-options.png}
-\caption{
-Bridge options in Tor Browser~5.0.3's Tor Launcher interface.
-Pre-configured bridges can be selected by ``Transport type,'' which refer to various
-censorship circumvention technologies (``pluggable transports'').
-%Under ``Enter custom bridges,'' there is a space to paste in
-%a bridge line, obtained out of band.
-%The ``Help'' button displays instructions on obtaining
-%bridge lines. 
-}
-\label{fig:bridge-options}
-\end{figure}
+through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.
 
@@
 (Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) Fig.~\ref{fig:topology} illustrates the interacting components.
+
+\subsection{State and Corporate Censorship}
+State level censors block access to the Tor network by blocking Tor relays, which are publicly listed.
+Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
+This means that users can connect directly to websites, but some may be blocked as is Tor.
+The thoroughness of censorship is what requires different bridges and transports.
+
+A local proxy is required to connect in certain managed networks (i.e.
+company and university firewalls).
+This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
+The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.
 
@@
 
-\subsection{State and Corporate Censorship}
-State level censors block access to the Tor network by blocking Tor relays, which are publicly listed.
-Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
-This means that users can connect to the Internet, but not through Tor.
-The thoroughness of censorship is what requires different bridges and transports.
-
-A local proxy is required to connect in certain managed networks (i.e.
-company and university firewalls).
-This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
-The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.
-
 \subsection{Connecting to Tor} 
-Configuring a bridge requires providing one or more
-``bridge lines,'' a specifically formatted bridge specification that
+Configuring a bridge requires providing a
+``bridge line,'' a specifically formatted bridge specification that
 includes its IP address, transport type, and other metadata.
@@
 For instance, choosing the hard-coded obfs3 option
-configures a handful of bridges that use obfs3 transport.
+configures a handful of bridges that use the obfs3 transport.
 If the built-in bridges do not work, a user can obtain bridge lines
@@
 \item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
-\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies.
+\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, not counting time spent passively waiting.
 \end{itemize}
@@
 
-We used Windows Firewall rules to block IP address of public Tor relays (E2, E3) and default bridges (E3). 
+We used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
 We used the Windows operating system hosts file to to block websites by
@@
 \centering
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.35\textwidth}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.35\textwidth}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
-	\caption{Instructions on getting a custom bridge.Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
+	\caption{Instructions on getting a custom bridge. Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
 	\label{fig:old-bridge-help}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.35\textwidth}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
@@
 Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing.
-The notion of bridges and transports are also specific to Tor, and not other censorship circumvention software.
+The terminology of bridges and transports are also specific to Tor, and not other censorship circumvention software.
 
@@
 Before each participant entered the room, we ran a script on the computer that
-set up one of the three simulated environments (E1, E2, or E3) and started the recording the computer screen.
+set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
 
@@
 The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}).
-This purpose of this introduction was to ensure that the main task
+This purpose of this introduction was to clarify that the main task
 was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
@@
 
-In E1, any connection to Tor worked. Configuring bridges and proxies were optional.  
+In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
 Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges. 
@@
 Then, they tried to configure a proxy, and gave up.
-They tried a direct connection again, which worked.
-E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.}
+They tried a direct connection again, which worked unexpectedly.
+They found a bug in our setup that we fixed for the later experiment.
+E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.
+}
 
@@
 \centering
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.35\textwidth}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.35\textwidth}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
@@
 \end{subfigure}
-\begin{subfigure}[b]{0.35\textwidth}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
@@
 \begin{itemize}
-\item We eliminated technical questions, resulting in less tasks and interface screens. 
+\item We eliminated technical questions, resulting in fewer tasks and interface screens. 
 \item We simulated auto-detection for proxies, telling users that they did not need a proxy. This is feasible to do with a local scan (no information leaked). 
@@
 
-Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and start the video recording.
-In contrast to the previous test, we installed an instrumented versions of Tor Browser 5.0.3.
+Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and started the video recording.
+In contrast to the previous test, we installed an instrumented version of Tor Browser 5.0.3.
 The instrumentation logged user interactions, such as window transitions, mouse clicks, and menu selections.
-Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browser the Internet on a browser of their choice and VLC to record the screen during the experiment.
+Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a browser of their choice and VLC to record the screen during the experiment.
 Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
@@
 & \multicolumn{2}{r}{completion rate} & \multicolumn{1}{r}{connection} & \multicolumn{1}{r}{configuration} \\
-& \multicolumn{2}{r}{(at 40 minutes)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
+& \multicolumn{2}{r}{(at 40min 8s)} & \multicolumn{1}{r}{time (med)} & \multicolumn{1}{r}{time (med)} \\
 \noalign{\hrule}
@@
 Most successful E3 participants
-used a meek bridges, disfavoring meek-azure.
+used meek bridges, disfavoring meek-azure.
 One E3 participant succeeded in an unexpected way
@@
 Cumulative success rates over time, shown continuously and at discrete times we found interesting.
-For the purposes of plotting the cumulative distribution, those who did not finish were assigned
-an arbitrarily high number greater than 40 minutes. 
 Notice that the longer the time went on, participants were less likely to succeed. 
-At 1.5 minutes, every E1-NEW participant finished,
+At 1.5 minutes, every E1-NEW participant had finished,
 but only 58\% of E1-OLD had finished by that time.  
@@
 %things to keep in mind
-We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1, and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely at until they manually cancel the connection to try again.
+We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1, and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely until they manually cancel the connection to try again.
 But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.
@@
 That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-We used a one-tailed Mann--Whitney test because the distribution of configuration times were also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.
+We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.
 
@@
 \input{median_time.tex}
-\caption{The median percent of time spent on each screen, which is not
-necessarily the median absolute time spent on that screen. 
+\caption{The median percent of time spent on each screen. 
 This percentage is computed independently for each screen; that is, a participant who spent the median percent 
@@
 \item {\bfseries Give advice.} Discourage users from configuring optional components.
-Add a secondary recommendation for bridges (try meek if obfs3 doesn't work, use meek if you are in Syria) to help users in need.
+Add a secondary recommendation for bridges (try meek if obfs3 doesn't work, use meek if you are in China) to help users in need.
 \item {\bfseries Minimize work.} Detect if users need a proxy or not. Redirect users to the relevant pages on error (i.e. redirect to the bridge screen the bridge fails).  
@@
 We did not study international users, or the configuration interface in languages other than English.
-All of our participants were from the United States and instructed to interact with the English version of Tor Browser.
-
-Participants in a laboratory setting may alter their due to their awareness of being observed~\cite{mccarney2007hawthorne}.
+All of our participants were from the United States and were instructed to interact with the English version of Tor Browser.
+
+Participants in a laboratory setting may alter their behavior due to their awareness of being observed~\cite{mccarney2007hawthorne}.
 We are aware that our participants were likely motivated differently compared to real users.
@@
 Our experiment did not directly test more advanced tasks.
-Our simulated environments did not require users to configuring a proxy or to get a custom bridge.
+Our simulated environments did not require users to configure a proxy or to get a custom bridge.
 From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how much they do.
 
-We only tested interface on Windows machines, which were the machines available at <redacted>. %Xlab.
+We only tested the interface on Windows machines, which were the machines available at <redacted>. %Xlab.
 The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent.
@@
 The Tor Launcher GUI allows most users to connect to the Tor network, provided that the user's connection does not require a proxy or a non-default bridge.
-User observation showed that participants were intimidated of the tasks, unsure of what to do, and likely to get stuck configuring proxies that they did not need.
+User observation showed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring proxies that they did not need.
 User testing showed that most people take more than 10 minutes to connect to Tor if they need to use bridges.
@@
 \item e7: proxy: syntax error
-\item e8: proxy: invalid ip address, blank port
-\item e9: proxy: invalid ip address, good port
-\item e10: proxy: invalid ip address, bad port
-\item e11: proxy: valid ip address, bad port
-\item e12: proxy: valid ip address, blank port
+\item e8: proxy: invalid IP address, blank port
+\item e9: proxy: invalid IP address, good port
+\item e10: proxy: invalid IP address, bad port
+\item e11: proxy: valid IP address, bad port
+\item e12: proxy: valid IP address, blank port
 \end{itemize}

### 2016-11-11 pets2017-paper/pets2017-paper.tex
mark success p value to redo

@@
 %success rate and version
-Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$).
-That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
+{\color {red} Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$).} That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
 

### 2016-11-15 pets2017-paper/pets2017-paper.tex
fix chi squared numbers
add chi squared calculation into comments
Karsten's comments

--- 2016-11-11 pets2017-paper/pets2017-paper.tex
@@
 starts, stops, and otherwise controls the underlying Tor processes.
-Tor Launcher's graphical user interface asks the user to configure
+Tor Launcher's graphical user interface (Figure~\ref{fig:old-interface}) asks the user to configure
 bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper).
@@
 
+We hope that our work contributes to Tor Browser and provides an interesting case study.
+We also encourage the use our evaluation pipeline and methods for evaluating other user-facing interfaces and features.
+
+\begin{figure*}
+\centering
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
+	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
+	\label{fig:old-first}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
+	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
+	\label{fig:old-bridge}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
+	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
+	\label{fig:old-bridge-settings}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
+	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
+	\label{fig:old-bridge-combobox}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
+	\caption{Instructions on getting a custom bridge. Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
+	\label{fig:old-bridge-help}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
+	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
+	\label{fig:old-proxy}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
+	\caption{Where users fill in proxy information.}
+	\label{fig:old-proxy-yes}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
+	\caption{The progress bar.}
+	\label{fig:old-progress}
+\end{subfigure}
+\caption{
+The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
+}
+\label{fig:old-interface}
+\end{figure*}
+
 \section{Background}
@@
 
-Tor relays are routers in the Tor Network that receive and route Tor traffic. 
-The three types of relays are: guard relays that serve as an entry node, middle relays that forward traffic from an entry relay to an exit relay, and exit relays that direct traffic to the destination.
+ A user uses the Tor network to indirectly connect to websites using Tor Browser.
+The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.
+Tor relays are the routers in the Tor Network.
+Guard relays that serve as an entry node into the Tor network and receive packets from the user.
+Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network.
+Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination.
 
@@
 
-In this paper, ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
-(Technically, Tor relays, bridges, and local proxies all allow indirect network connections to other network services and can be considered a proxy.) Fig.~\ref{fig:topology} illustrates the interacting components.
+In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
+This is to maintain consistency with the wording in the configuration interface.
+Fig.~\ref{fig:topology} illustrates the interacting components.
+We recognize that, a proxy is technically anything that acts as an intermediary between clients and servers.
+By this definition, a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy.
 
@@
 includes its IP address, transport type, and other metadata.
-The interface has hard-coded options (see Figure~\ref{fig:bridge-options}) 
+The interface has hard-coded options (see Figure~\ref{fig:old-bridge-combobox}) 
 that select a group of bridges that use a particular transport.
@@
 We then stepped through each user path and recorded our observations.
-
-\begin{figure*}
-\centering
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
-	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
-	\label{fig:old-first}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
-	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
-	\label{fig:old-bridge}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
-	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
-	\label{fig:old-bridge-settings}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
-	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
-	\label{fig:old-bridge-combobox}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
-	\caption{Instructions on getting a custom bridge. Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
-	\label{fig:old-bridge-help}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
-	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
-	\label{fig:old-proxy}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
-	\caption{Where users fill in proxy information.}
-	\label{fig:old-proxy-yes}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
-	\caption{The progress bar.}
-	\label{fig:old-progress}
-\end{subfigure}
-\caption{
-The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
-}
-\label{fig:old-interface}
-\end{figure*}
 
@@
 We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
-We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 5 heard of it but not used it, and the remaining 8 never heard of or used it.
+We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 3 heard of it but not used it, and the remaining 9 never heard of or used it.
 The main objective of this question was to identify new users versus infrequent users.
@@
 ~~~~~~~~~~
-\begin{subfigure}[b]{0.35\textwidth}
+\begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
@@
 Different colors indicate which screen they were on during the experiment.
-The ``not running'' times are those when Tor Launcher was closed (
-i.e. searching for help in another browser, restarting the application, etc.).
+If participants were doing other things (i.e. searching for help in another browser)
+while off-focus, this time still counts as spending time in that off-focus window. 
+``Not running'' are times when Tor Launcher was closed (
+i.e. restarting the application).
 }
@@
 %success rate and version
-Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 0.0126$, $df = 2$, $p = 0.994$).
+Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).
 That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
+
+%using http://www.socscistatistics.com/tests/chisquare/Default2.aspx
+% OLD VS NEW: The chi-square statistic is 2.8079. The p-value is .093802.
+% E1-old vs E1-new: no valid calculation  since it's the exact same ratio (19 succeeded, 0 failed) 
+% E2-old vs E2-new: The chi-square statistic is 3.0929. The p-value is .078636.
+% E3-old vs e3-new: The chi-square statistic is 1.3666. The p-value is .242403.
 
@@
 <Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.
-<Redacted>, and <redacted> provided me with insider insight into the design decisions made at Tor.
+<Redacted> and <redacted> provided me with insider insight into the design decisions made at Tor.
 % Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.

### 2016-11-15 pets2017-paper/pets2017-paper.tex
fix summative demographics

@@
 We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
-Of our 16 recruited participants, 50\% were male.
+Of our 16 recruited participants, 50\% identified as male and 50\% identified as female.
 Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
@@
 
-{\color {red} Of our recruited 124 participants, 56.8\% were male.
-Ages ranged from 18 to~68 years ($\mu = 28.9$, $\sigma = 12$).
-56.8\% were male.
-84.8\% of our participants had a college education.} We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
+Of our recruited 124 participants, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
+Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$).
+84.1\% of our participants had at least a college education.
+We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
 Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
@@
 \subsection{Results} 
-124 people participated in our experiment, but we used data from 114.
-We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface.
+124 people participated in our experiment, but we used data from 113.
+We filtered participants who made errors in completing the consent form, did not complete the exit survey, did not understand the task, or did not interact with the instrumented interface.
 In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}).
@@
 An overview of the results of the experiment. Those who
-failed to connect were assigned the maximum time of 40:08.
+failed to connect were assigned the maximum time of 40:08, 
+the maximum time a participant took to finish the task.
 }

### 2016-11-15 pets2017-paper/pets2017-paper.tex
mark things to change for taking out p93 in red

@@
 \caption{
+{\color {red}
 An overview of the results of the experiment. Those who
@@
 the maximum time a participant took to finish the task.
+}
 }
@@
 \caption{
+{\color {red}
 A summary of our valid participants' paths through the interface.
@@
 ``Not running'' are times when Tor Launcher was closed (
-i.e. restarting the application).
+i.e. restarting the application).}
 }
@@
 \caption{
+{\color {red}
 Network components that led to the first successful bootstrap
@@
 }
+}
 \label{tab:attempts-bridge-proxy}
@@
 % failure observations
-17\% (19 of 114) of participants were not able to successfully connect to Tor.
+{\color {red} 17\% (19 of 114) of participants were not able to successfully connect to Tor.
 Five (P73, P75, P89, P91, P106, P110) tried a direct connection.
@@
 Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder.
-We suspect that they would have succeeded if they had gotten a response.
+We suspect that they would have succeeded if they had gotten a response.}
 
 %success rate and version
-Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).
-That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
+{\color {red} Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).} That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
 
@@
 %time observations (how long people took)
-The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
-Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
+The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time {\color {red} (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).} Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
 
 %time to success and version
-Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+{\color {red} Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).} That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
 We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).
@@
 \caption{
+{\color {red}
 The dots show the raw connection times,
@@
 The ``DNF'' (did not finish) numbers at the right show how many of participants 
-did not finish, who were assigned the maximum time of 40:08.
+did not finish, who were assigned the maximum time of 40:08.}
 }
@@
 \caption{
+{\color {red}
 Cumulative success rates over time, shown continuously and at discrete times we found interesting.
@@
 but only 58\% of E1-OLD had finished by that time.  
-At 10 minutes, most participants in E2 had finished. 
+At 10 minutes, most participants in E2 had finished. }
 }
@@
 %configuration time and version
-Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+{Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).} That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
 We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.
@@
 \input{median_time.tex}
-\caption{The median percent of time spent on each screen. 
+\caption{
+{\color {red}
+The median percent of time spent on each screen. 
 This percentage is computed independently for each screen; that is, a participant who spent the median percent 
@@
 of time on other screens.}
+} 
 \label{table:median_time}
@@
 \caption{
+{\color {red}
 The dots show the raw active configuration times,
@@
 }
+}
 \label{fig:time_to_success_active_clamped}
@@
 \subsection{Usability of Tor Launcher} 
-In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed. 
+{\color {red} In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.}
 On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.

### 2016-11-15 pets2017-paper/pets2017-paper.tex
rough hashout of more related work

@@
 {\color {red} 
+% Previous Tor studies 
 There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
@@
 the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
-%for color red
+
+% Scoping our work wrt usable security, usability, and interaction design  
+Our work combines the three.
+We try to make it as usable as possible by following usability practices (reducing load, not having people remember, easy learning curve, etc.) But at the same time, we also tried to make some things hard and kept things hard (not automating things that would be dangerous) like confirm if you want to delete everything is a useful feature, and it's more usable security than usability.
+Our thing was more interaction design--we changed from letting the users guide to telling them, to making it as easy as possible to having a consistent model.
+We didn't really do any real design except to prove the concept (cite Adrienne's warning study with icons and colors), and while we tried to make it good, we didn't reaaaaallly thorougly test out the icons and wording and whatnot.
 }

### 2016-11-15 pets2017-paper/pets2017-paper.tex
fix digraph to match all-participant edges

@@
 \centering
-\includegraphics[width=\textwidth]{tor-digraph.png}
+\includegraphics[width=\textwidth]{torconfig.pdf}
 \caption{
@@
 \begin{itemize} 
-\item e0: custom bridge: field left blank
-\item e1: custom bridge: syntax error
-\item e2: custom bridge: invalid address
-\item e3: hardcoded bridge blocked
-\item e4: custom bridge blocked
-\item e5: proxy type is not selected
-\item e6: proxy: ip address left blank
-\item e7: proxy: syntax error
-\item e8: proxy: invalid IP address, blank port
-\item e9: proxy: invalid IP address, good port
-\item e10: proxy: invalid IP address, bad port
-\item e11: proxy: valid IP address, bad port
-\item e12: proxy: valid IP address, blank port
+\item e0: need a bridge or proxy
+\item e1: hardcoded bridge blocked
+\item e2: custom bridge: field left blank
+\item e3: custom bridge: syntax error
+\item e4: custom bridge: invalid address
+\item e5: custom bridge blocked
+\item e6: proxy type is not selected
+\item e7: proxy: ip address left blank
+\item e8: proxy: syntax error
+\item e9: proxy: invalid IP address, blank port
+\item e10: proxy: invalid IP address, good port
+\item e11: proxy: invalid IP address, bad port
+\item e12: proxy: valid IP address, bad port
+\item e13: proxy: valid IP address, blank port
 \end{itemize}

### 2016-11-15 pets2017-paper/pets2017-paper.tex
make caption widths longer for subfigures
add subsections to formative testing

@@
 	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
@@
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
@@
 	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{Instructions on getting a custom bridge. Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
@@
 	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{Where users fill in proxy information.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{The progress bar.}
@@
 \subsection{Results} 
-We give a summary of what our participants did below. We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions.
+We give a summary of what our participants did below.
+We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions.
+We hope that these participant summaries give some insight into how users may currently struggle with the Tor Launcher interface.
 
@@
 
+\subsubsection{E1} 
 In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
-Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges. 
 Observations in E1:
@@
 
+Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges.
+
+\subsubsection{E2} 
 In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
-Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies. 
 Observations in E2:
@@
 
+Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies.
+
+\subsubsection{E3}
 In E3, a bridge was required to connect, but only meek and custom bridges worked. Configuring a proxy was optional.
-Participants in E3 struggled.
-Three failed to connect.
-Of the three that connected, one brute forced options until something worked (P14), another did not understand what they did (P15), and the third used a custom bridge after being convinced meek bridges were not working (P16).
 Observations in E3:
@@
 
-We hope that these participant summaries give some insight into how users may currently struggle with the Tor Launcher interface.
+Participants in E3 struggled.
+Three failed to connect.
+Of the three that connected, one brute forced options until something worked (P14), another did not understand what they did (P15), and the third used a custom bridge after being convinced meek bridges were not working (P16).
 
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{There is only one bridge screen now. The default is to connect without one.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{The transports selections are the same.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{These instructions are also the same.}
@@
 	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
@@
 \end{subfigure}
-~~~~~~~~~~
+~~~~~~~~~~~~~~~~~~~~~~~~~
 \begin{subfigure}[b]{0.30\textwidth}
 	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
+	\centering\captionsetup{width=1.5\linewidth}%
 	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}

### 2016-11-15 pets2017-paper/pets2017-paper.tex
unmark things to filter out P93 until I'm sure I should do it

@@
 
-Of our recruited 124 participants, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
+124 people participated in our experiment, but we used data from 114.
+We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface.
+Of the 114, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
 Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$).
@@
 \subsection{Results} 
-124 people participated in our experiment, but we used data from 113.
-We filtered participants who made errors in completing the consent form, did not complete the exit survey, did not understand the task, or did not interact with the instrumented interface.
+We summarize what our participants did below.
+Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
 In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}).
-Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
 
@@
 \caption{
-{\color {red}
 An overview of the results of the experiment. Those who
@@
 the maximum time a participant took to finish the task.
-}
 }
@@
 \caption{
-{\color {red}
 A summary of our valid participants' paths through the interface.
@@
 i.e. restarting the application).}
-}
 \label{fig:all-participant-edges}
@@
 \caption{
-{\color {red}
 Network components that led to the first successful bootstrap
@@
 }
-}
 \label{tab:attempts-bridge-proxy}
@@
 % failure observations
-{\color {red} 17\% (19 of 114) of participants were not able to successfully connect to Tor.
+17\% (19 of 114) of participants were not able to successfully connect to Tor.
 Five (P73, P75, P89, P91, P106, P110) tried a direct connection.
@@
 Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder.
-We suspect that they would have succeeded if they had gotten a response.}
+We suspect that they would have succeeded if they had gotten a response.
 
 %success rate and version
-{\color {red} Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).} That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
+Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).
+That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
 
@@
 %time observations (how long people took)
-The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time {\color {red} (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).} Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
+The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
 
 %time to success and version
-{\color {red} Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).} That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
 We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).
@@
 \caption{
-{\color {red}
 The dots show the raw connection times,
@@
 did not finish, who were assigned the maximum time of 40:08.}
-}
 \label{fig:time_to_success_clamped}
@@
 \caption{
-{\color {red}
 Cumulative success rates over time, shown continuously and at discrete times we found interesting.
@@
 but only 58\% of E1-OLD had finished by that time.  
-At 10 minutes, most participants in E2 had finished. }
+At 10 minutes, most participants in E2 had finished. 
 }
@@
 %configuration time and version
-{Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).} That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
+Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
 We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.
@@
 \caption{
-{\color {red}
 The median percent of time spent on each screen. 
@@
 of time on other screens.}
-} 
 \label{table:median_time}

### 2016-11-15 pets2017-paper/pets2017-paper.tex
i missed some things to remove

@@
 \caption{
-{\color {red}
 The dots show the raw active configuration times,
@@
 }
-}
 \label{fig:time_to_success_active_clamped}
@@
 \subsection{Usability of Tor Launcher} 
-{\color {red} In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.}
+In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
 On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.

### 2016-11-17 pets2017-paper/pets2017-paper.tex
wordsmithing
better captions for interface screenshots; kinda still overflowing but whatever?

@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen. The connect button does not connect directly, but uses settings configured in the interface (initialized to be direct).}
+	\caption{The first screen (F).
+``Connect'' connects directly to a public Tor relay unless bridges or proxies are configured.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}).
+}
 	\label{fig:old-first}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{Answering yes to this question leads to a screen to configure bridges. Answering no leads to the proxy question screen (Figure~\ref{fig:old-proxy}).}
+	\caption{The first bridge screen (B1).
+Answering yes directs users to a screen to configure bridges (Figure~\ref{fig:old-bridge-settings}).
+Answering no directs users to the proxy question screen (Figure~\ref{fig:old-proxy}).}
 	\label{fig:old-bridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{Where users choose a bridge. The recommended bridge is a hard-coded obfs3.}
+	\caption{The second bridge screen (B2).
+Users select a provided bridge or a custom one (bridges not hard coded into the interface).
+``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}).
+}
 	\label{fig:old-bridge-settings}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The available transport selections, listed in alphabetical order. They all work differently.}
+	\caption{The hardcoded bridges are listed alphabetically by the transport that they support. Each transport works differently, but their functions are not explained in the interface.}
 	\label{fig:old-bridge-combobox}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{Instructions on getting a custom bridge. Clicking the ``Help'' button in Figures~\ref{fig:old-bridge-settings} and \ref {fig:old-bridge-combobox} leads to this page.}
+	\caption{The bridge help screen (BH) gives instructions for a custom bridge three different ways. ``Done'' redirects users back to the second bridge screen (Figure~\ref{fig:old-bridge-settings}).}
 	\label{fig:old-bridge-help}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{Answering yes to this question leads to a screen to configure proxies. Answering no initiates a connection to Tor.}
+	\caption{The first proxy screen (P1). Answering yes to this question directs to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). Answering no starts a connection to Tor.}
 	\label{fig:old-proxy}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{Where users fill in proxy information.}
+	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, ip address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
 	\label{fig:old-proxy-yes}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The progress bar.}
+	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interruput this bar but an error replaces this window with an alert. }
 	\label{fig:old-progress}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen. We reduced the text on the screen and clarified that configuration is for heavily censored environments.}
+	\caption{The first screen (F).
+We reduced the text on the screen and clarified that configuration is for heavily censored environments.
+``Configure'' leads to the proxy screen  (Figure~\ref{fig:new-proxy}.)}
 	\label{fig:new-first}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The interface detects the need for a proxy. Proxy fields (same as ones in Figure \ref{fig:old-proxy-yes} are hidden until you click``configure.''}
+	\caption{The proxy screen (P). The interface locally detects if users need a proxy. If they need to configure one, proxy fields (same as Figure \ref{fig:old-proxy-yes}) are automatically populated.}
 	\label{fig:new-proxy}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{There is only one bridge screen now. The default is to connect without one.}
+	\caption{The bridge screen (B). We give users the options to connect  without a bridge (the default choice) alongside the other options. We tell users to when to choose a bridge. }
 	\label{fig:new-nobridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{We give short instructions on when to use a bridge. Users can configure one here.}
+	\caption{We give a second bridge recommedation for the provided bridges. We hide the text field to input custom bridge information until they click the radio button to configure one.}
 	\label{fig:new-bridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The transports selections are the same.}
+	\caption{The provided bridges and their supporting transports remains unchanged. This dropdown menu is the same as the bridge settings in the old interface (Figure~\ref{fig:old-bridge-combobox}).}
 	\label{fig:new-bridge-combobox}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{These instructions are also the same.}
+	\caption{The bridge help screen (BH). We did not make any changes to this page. This screen is idential to that in the old interface (Figure~\ref{fig:old-bridge-help}).}
 	\label{fig:new-bridge-help}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{This screen summarized how they would connect to Tor. There is more information if bridges and proxies are configured.}
+	\caption{The summary screen (S). This screen shows users what they had configured in the interface. If they  configurued proxies or bridges, this summarizes their choices.}
 	\label{fig:new-summary}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{A checkpoint progress bar with connection information. There are more checkpoints if bridges and proxies are configured.}
+	\caption{The progress bar (Pr). A checkpoint progress bar shows the status of each component in the connection (there are more checkpoints if bridges and proxies are configured).}
 	\label{fig:new-progress}
@@
 124 people participated in our experiment, but we used data from 114.
-We filtered participants who made errors in completing the consent form, did not understand the task, or did not interact with the instrumented interface.
+We filtered participants who made errors in completing the consent form or did not interact with the instrumented interface.
 Of the 114, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.

### 2016-11-17 pets2017-paper/pets2017-paper.tex
update with accurate demographics

@@
 Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
-One participant declined to submit their age, so the previous calcuations were done without thier information.
+One participant declined to report their age, so age calculations omit one participant's information.
 100\% had at least some college education.
 We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
-We verified their self-reported familiarity with Tor Browser in-person, and found that 4 used it, 3 heard of it but not used it, and the remaining 9 never heard of or used it.
-The main objective of this question was to identify new users versus infrequent users.
-We considered participants who had never heard of Tor or have only heard of Tor to be new users and those who have used Tor to be previous users.
+We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.
 
@@
 We filtered participants who made errors in completing the consent form or did not interact with the instrumented interface.
-Of the 114, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
+Of the 114, one participant did not report their demographics.
+We still use their experiment data.
+Of the 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
 Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$).

### 2016-11-18 pets2017-paper/pets2017-paper.tex
pass through paper. definitely procrastinating on related work.

@@
 
-We hope that our work contributes to Tor Browser and provides an interesting case study.
-We also encourage the use our evaluation pipeline and methods for evaluating other user-facing interfaces and features.
-
-\begin{figure*}
-\centering
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen (F).
-``Connect'' connects directly to a public Tor relay unless bridges or proxies are configured.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}).
-}
-	\label{fig:old-first}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first bridge screen (B1).
-Answering yes directs users to a screen to configure bridges (Figure~\ref{fig:old-bridge-settings}).
-Answering no directs users to the proxy question screen (Figure~\ref{fig:old-proxy}).}
-	\label{fig:old-bridge}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The second bridge screen (B2).
-Users select a provided bridge or a custom one (bridges not hard coded into the interface).
-``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}).
-}
-	\label{fig:old-bridge-settings}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The hardcoded bridges are listed alphabetically by the transport that they support. Each transport works differently, but their functions are not explained in the interface.}
-	\label{fig:old-bridge-combobox}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH) gives instructions for a custom bridge three different ways. ``Done'' redirects users back to the second bridge screen (Figure~\ref{fig:old-bridge-settings}).}
-	\label{fig:old-bridge-help}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first proxy screen (P1). Answering yes to this question directs to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). Answering no starts a connection to Tor.}
-	\label{fig:old-proxy}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, ip address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
-	\label{fig:old-proxy-yes}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interruput this bar but an error replaces this window with an alert. }
-	\label{fig:old-progress}
-\end{subfigure}
-\caption{
-The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
-}
-\label{fig:old-interface}
-\end{figure*}
+We hope that our work contributes to Tor Browser and is an informative case study of users interacting with anonymity and censorship circumvention tools.
 
@@
 \label{sec:background}
-This section covers technical background necessary to understand the study.
-
-\subsection{Relays, Bridges, Pluggable Transports, and Proxies}
-
- A user uses the Tor network to indirectly connect to websites using Tor Browser.
-The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.
-Tor relays are the routers in the Tor Network.
+This section discusses network components, when to configure them, and how they connect to Tor.
+
+\subsection{Proxies, Relays, Bridges, and Pluggable Transports}
+
+In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
+This is to maintain consistency with the wording in the configuration interface.
+Fig.~\ref{fig:topology} illustrates the interacting components.
+A proxy is technically an intermediary between clients and servers, so a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy.
+A user uses a proxy to bypass local firewalls.
+
+Tor relays are the routers in the Tor network. The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.  
 Guard relays that serve as an entry node into the Tor network and receive packets from the user.
@@
 Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination.
+A user uses Tor Browser to connect to the Tor network, which indirectly connects to websites.
 
@@
 and the ``meek''~\cite{fifield2015blocking} options route traffic
-through content delivery networks. Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.
-
-In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
-This is to maintain consistency with the wording in the configuration interface.
-Fig.~\ref{fig:topology} illustrates the interacting components.
-We recognize that, a proxy is technically anything that acts as an intermediary between clients and servers.
-By this definition, a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy.
+through content delivery networks.
+Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.
+A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is is being censored.
 
 \subsection{State and Corporate Censorship}
-State level censors block access to the Tor network by blocking Tor relays, which are publicly listed.
+A local proxy is required to connect in certain managed networks (i.e.
+universities and corporations).
+This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
+The user must first successfully connect to the Internet through their proxy before trying to connect to a Tor relay or bridge.
+
+State level censors block access to the Tor network by blocking pubicly listed Tor relays.
 Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
@@
 The thoroughness of censorship is what requires different bridges and transports.
-
-A local proxy is required to connect in certain managed networks (i.e.
-company and university firewalls).
-This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
-The user must be able to connect to the Internet through their proxy before trying to connect to the Internet with Tor.
 
@@
 \subsection{Connecting to Tor} 
-Configuring a bridge requires providing a
-``bridge line,'' a specifically formatted bridge specification that
-includes its IP address, transport type, and other metadata.
-The interface has hard-coded options (see Figure~\ref{fig:old-bridge-combobox}) 
+A ``bridge line,'' a specifically formatted bridge specification that
+includes its IP address, transport type, and other metadata 
+officially configures Tor Browser to use bridges.
+Users can do this more easily by choosing a 
+a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
 that select a group of bridges that use a particular transport.
@@
 configures a handful of bridges that use the obfs3 transport.
-If the built-in bridges do not work, a user can obtain bridge lines
-through out-of-band channels, for instance by email~\cite{bridgedb}.
+If the built-in bridges do not work, users can obtain bridge lines
+through out-of-band channels~\cite{bridgedb}.
 
@@
 There are many valid configuration settings to connect to the Tor network.
-A user who needs a bridge can connect to Tor with a bridge and proxy, provided that both were configured correctly.
+A user who does not need a bridge or proxy can connect with a bridge, proxy, or both, provided that they are configured correctly.
+
+\begin{figure*}
+\centering
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-first.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The first screen (F).
+``Connect'' connects directly to a public Tor relay unless bridges or proxies are configured.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}).
+}
+	\label{fig:old-first}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridges.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The first bridge screen (B1).
+Answering yes directs users to a screen to configure bridges (Figure~\ref{fig:old-bridge-settings}).
+Answering no directs users to the proxy question screen (Figure~\ref{fig:old-proxy}).}
+	\label{fig:old-bridge}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The second bridge screen (B2).
+Users select a provided bridge or a custom one (bridges not hard coded into the interface).
+``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}).
+}
+	\label{fig:old-bridge-settings}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeSettings-combobox.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The hardcoded bridges are listed alphabetically by the transport that they support. Each transport works differently, but their functions are not explained in the interface.}
+	\label{fig:old-bridge-combobox}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-bridgeHelp.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The bridge help screen (BH) gives instructions for a custom bridge three different ways. ``Done'' redirects users back to the second bridge screen (Figure~\ref{fig:old-bridge-settings}).}
+	\label{fig:old-bridge-help}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-proxy.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The first proxy screen (P1). Answering yes to this question directs to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). Answering no starts a connection to Tor.}
+	\label{fig:old-proxy}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-proxyYES.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, ip address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
+	\label{fig:old-proxy-yes}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/OLD-progress.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interruput this bar but an error replaces this window with an alert. }
+	\label{fig:old-progress}
+\end{subfigure}
+\caption{
+The Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
+}
+\label{fig:old-interface}
+\end{figure*}
 
@@
 \subsection{Testing Pipeline} 
-Two researchers first performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing.
-A cognitive walkthrough is evaluation method that requires usability evaluators to work through a series of tasks from the perspective of the user, usually to understand a system's learnability for new or infrequent users.
+We performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing.
+This evaluation method involved usability evaluators to working through a series of tasks from the perspective of the user, trying to understand a system's learnability for new or infrequent users.
 
@@
 We opportunistically used our observations to make changes to the interface.
-We believed that the process of identifying design principles, drafting design changes, and testing an alternative interface would be insightful and have the potential to discover impactful changes.
+We believed that the process of identifying design principles, drafting design changes, and testing an alternative interface would be insightful.
 
@@
 Task time is a supplemental usability metric that measures user productivity during the task.
-We measured task time two different ways.
-Connection time measures how long users use the configuration interface, which includes time  spent waiting while a Tor Browser establishes a connection to Tor, which can dominate the measurement.
-Configuration time measures the time users spent actively configuring bridges and proxies.
+We measured this in two ways.
+Connection time measures how long users took to connect to Tor, which includes time spent waiting for Tor to configure relays for the user.
+This can take up to a couple minutes and dominate the measurement.
+Configuration time measures the time users spent configuring bridges and proxies.
 
@@
 
-We used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
-We used the Windows operating system hosts file to to block websites by
+We conducted our studies at <redacted>, which only had Windows machines. 
+So we used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
+and the Windows operating system hosts file to to block websites by
 mapping domain names to localhost (127.0.0.1) (E1, E2, E3).
-We blocked torproject.org and its subdomains to discourage downloading Tor Browser, as we had installed a specific version on the test computers.
-We blocked wikipedia.org, cnn.com, and their subdomains to create ``censored'' sites for the experiment.
+For all experiments, we blocked torproject.org and its subdomains to discourage downloading Tor Browser (as we had installed a specific version on the test computers) and wikipedia.org, cnn.com, and their subdomains (these were our simulated ``censored'' websites).
 
@@
 \subsection{Recruitment}
-We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked an prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
-We pre-screened~\cite{screening} for diversity in gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
+We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked a prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
+We pre-screened~\cite{screening} so that we could have a diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
 Of our 16 recruited participants, 50\% identified as male and 50\% identified as female.
 Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
-One participant declined to report their age, so age calculations omit one participant's information.
-100\% had at least some college education.
-We took participants' self-reported familiarity with technical terms use of security tools with skepticism (Appendix~\ref{prescreening-responses}).
+One participant declined to report their age, so age calculations omit this participant's information.
+All of our users were highly educated, having at least some college education.
+We show their self-reported familiarity with technical terms use of security tools in  Appendix~\ref{prescreening-responses}.
 We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.
@@
 
-We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
-Although there is variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition, we ensured each condition had a participant who used Tor Browser before.
+We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
+We ensured that each condition had a participant who had used Tor Browse before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.
 
@@
 We ran the experiment in a meeting room in <redacted building> at <redacted university>.
-The room had a desk and chair, where a monitor, keyboard, and a Windows 8 computer were set up.
-On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a another browser of their choice, and VLC to record the screen during the experiment.
+The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
+On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in a another browser of their choice, and VLC to record the screen during the experiment.
 Before each participant entered the room, we ran a script on the computer that
@@
 \subsection{Procedure}
-Three researchers ran the formative usability testing, with each session having at least two researchers.  
-Before the experiment began, each participant was verbally informed of the purpose of the 
-study, what data was collected, and any associated risks. If they wished to participate,
-they were informed again in writing and consented by signing the document. To be thorough, 
-we clarified verbally that they could stop at any time during the experiment with no negative consequences.
-
-The experiment formally began by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}).
-This purpose of this introduction was to clarify that the main task
-was to connect to Tor, rather than figuring out if they needed to connect to Tor. 
-We instructed them to visit a blocked and unblocked website
-in a non-Tor browser to clarify that the Internet was functioning as expected. 
-We then told them to use Tor Browser to visit a censored site and pointed out 
-the respective shortcut on their desktop.
-
-We then asked them to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
-required answers from one blocked website (Wikipedia) and one non-blocked website (CNN).
-The worksheet did not specify which website was censored. 
-We chose these websites because they are popular websites and that their likely familiarity 
-would make the task seem less intimidating.
-
-Participants were given 45 minutes to complete their worksheet. 
-After instructions, the researchers left and watched a live feed of the participants' screen in another room to minimize interactions.
-
-After participants completed the browsing tasks (or ran out of time),
-we asked them standard interview questions about their experience (Appendix~\ref{interview-questions}) and took notes of their responses.
-We then followed up with participant-specific questions to verify any hypotheses   we had from observation (e.g.
+Three researchers ran the formative usability tests, with each session having at least two researchers.  
+We told the participant the purpose of the 
+study, what data was collected, and any associated risks. 
+Then they signed a consent form with this information in writing. 
+Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.
+
+We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task.
+We explicitly stated that the they should use Tor to circumvent censorship.
+We instructed them to visit sample censored and uncensored websites
+in a non-Tor browser to clarify that the Internet was functioning and
+pointed out the Tor Browser shortcut on their desktop.
+
+They were asked to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
+required answers from Wikipedia (censored) and CNN (uncensored).
+We chose these websites because their likely familiarity~\ref{alexa}
+would make the task seem less intimidating. They were given 45 minutes to complete the task. 
+After instructions, researchers left to minimize interactions and watched a live feed of the participants' screen from another room.
+
+After they completed the worksheet (or ran out of time),
+we asked them general questions about their experience (Appendix~\ref{interview-questions}) and participant-specific questions to verify any hypotheses we had (e.g.
 ``the participant was selecting bridges at random'').
@@
 \subsection{Results} 
-We give a summary of what our participants did below.
-We watched the screen recording to summarize their actions and referred to their interviews for insight into why they took specific actions.
-We hope that these participant summaries give some insight into how users may currently struggle with the Tor Launcher interface.
+We use out screen recording and interview data to give a summary of each participant.
 
@@
 \pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy.
-After not being able to fill out the proxy input fields, they start over and connected using an obfs4 bridge.
-Note that they didn't try connecting with the obfs3 bridge, which would have worked.}
+After not being able to fill out the proxy input fields, they started over and connected with an obfs4 bridge.
+Note that they did not try connecting with the obfs3 bridge, which would have worked.}
 
 %P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
-\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected using the recommended bridge.}
-
-Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily used bridges.
+\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}
+
+Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily configured bridges.
 
 \subsubsection{E2} 
-In E2, a bridge was required to connect, but any bridge worked. Configuring a proxy was optional.
+In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges aquired out of band would work. Configuring a proxy was optional.
 Observations in E2:
@@
 %P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
-\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly and gave up after minutes of waiting. Then, they connected using the recommended bridge.}
+\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly.
+After watching the progress bar not make any progress for a couple minutes, and gave up on the direct connection.
+Then they connected with the recommended bridge.}
 
@@
 \pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly.
-They restarted Tor Launcher and tried another direct connection---and repeated this two more times.
+They restarted Tor Launcher and tried to connect directly again---and repeated this two more times.
 On the fourth restart, they tried to configure a proxy, but gave up.
@@
 \pquote{P8 (new user, direct, 10:40)}{They tried connecting directly.
-They then looked at proxy settings, gave up, and tried connecting directly again.
+After waiting a couple minutes, they figured that did not work and looked at proxy settings.
+But after looking at the settings and being intimidated, they tried connecting directly again.
 Then, they tried to configure a proxy, and gave up.
-They tried a direct connection again, which worked unexpectedly.
+They tried connecting directly again, which worked unexpectedly.
 They found a bug in our setup that we fixed for the later experiment.
@@
 \pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly.
-Then, they answered no to both bridge and proxy questions, and effectively tried another direct connection.
-After that, they connect using the recommended bridge.}
+And they tried connecting directly through a different user path by answering no to bridge and proxy questions in the interface, connecting from the proxy screen.
+Then, they connected using the recommended bridge.}
 
@@
 Tor does not allow connections with bad clocks.
-They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).}
-
-Participants in E2 {\it eventually} connected using the recommended bridge, but spent a fair bit of time waiting for direct connections to fail and unsuccessfully configuring proxies.
+They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).
+This participant tried the most attempts to connect to Tor, using a variety of bridges and proxies.}
+
+Participants in E2 tried a direct connection to Tor before {\it eventually} connecting with the recommended bridge.
+They spent a fair amount of time waiting before determining that connections failed.
+Some stated that they connected directly because the interface says that it would work in ``most situations'' (Figure~\ref{fig:old-first}).
+Our participants did not know if they needed bridges or proxies, so they only tried to configure one when the direct connection failed.
+Since they did not know whether they needed a bridge or proxy, they often tried to configure proxies when they did not need one and should have configured bridges instead.
 
 \subsubsection{E3}
-In E3, a bridge was required to connect, but only meek and custom bridges worked. Configuring a proxy was optional.
+In E3, a bridge was required to connect.
+Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google.
+Custom bridges can also work.
+Configuring a proxy was optional.
 Observations in E3:
@@
 
-%P16: E3 (regular) FAIL (why did obfs3 work the first time? It shouldn't have!) 
+%P16: E3 (regular) FAIL
 \pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
@@
 When that didn't work, they tried to configure a proxy.
-Then, they gave up and tried using other browsers to complete the task.}
+Then, they gave up on the task entirely.}
 
@@
 After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect.
-They went back to the start screen and clicked connect, which made a connection using meek-azure bridge.
-The participant thought they made a direct connection, but the connect button used settings toggled in the bridge and proxy screens in the interface.}
+They went back to the first screen~\ref{fig:old-first} and clicked connect, which made a connection using meek-azure bridge.
+The connect button makes a connection to Tor with the toggled settings in the interface.
+When the interface is initialized to not use a bridge or proxy, clicking connect on the first page starts a direct connection.
+But since the participant had chosen a meek-azure bridge, the connect button made a connection to a meek-azure bridge, even though the text in the first screen says that they will ``connect directly.'' Because of this, the participant thought they made a direct connection.
+Although they succeeded in connecting to Tor, they did not realize what they had done or why connecting to a meek-azure bridge worked.
+They chose that bridge at random.}
 
@@
 After briefly looking at error messages the system log, they retried connecting directly two more times.
-After looking up proxy settings, they tried connecting with a meek-google bridge, but gave up before it could connect.
+After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked.
+But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect.
 They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}
 
-Participants in E3 struggled.
-Three failed to connect.
-Of the three that connected, one brute forced options until something worked (P14), another did not understand what they did (P15), and the third used a custom bridge after being convinced meek bridges were not working (P16).
+Participants in E3 also generally tried a direct connection to Tor.
+They did not know if they needed a bridge or proxy, and like the participnts in E2, only configured them when the direct connection failed.
+But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work.
+Of the participants that failed, they all tried the recommended bridge but not any others.
+The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed.
+P14 brute forced options until something worked, P15 did not think that thye used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
 
@@
 
-Participants found the interface confusing, and were often intimidated by the tasks they were asked to do.
+The interface uses a technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
+Participants found the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) and did not know what to do to configure bridges and proxies (Figures~\ref{fig:old-bridge-combobox} and~\ref{fig:old-proxy-yes}).
+
+%P3 in the repo, P3 in the paper
+\pquote{P3}{``The vocabulary is really challenging, for someone not doing IT work.''}
+
+%P13 in the repo, P7 in the paper 
+\pquote{P7}{``I didn't know where to start. I didn't know what to do. [I] was just fiddling, to be honest with you... it was kind of confusing.''}
+
+In addition to not knowing what to do, they did not understand the choices that they had to make.
+
+%P2 in the repo, P2 in the paper 
+\pquote{P2}{``I don't know what any of those (points to list of transports) means. I don't know what that (points to proxy settings) means at all."}
 
@@
 
-%P3 in the repo, P3 in the paper
-\pquote{P3}{``The vocabulary is really challenging, for someone not doing IT work.''}
-
-Participants were unsure of what to do, and often configured bridges and proxies when they did not need to.
-
 %P15 in the repo, but P12 in the paper
-\pquote{P15}{``I didn't know if this computer had any proxy information. I wasn't able to find it if it did.''}
-
-The progress bar had system dependencies that made it update oddly.
+\pquote{P15}{``I didn't know if this computer had any proxy information.
+I wasn't able to find it if it did.
+I went to every browser and could not find what they were talking about.
+I googled how I would find that and couldn't seem to get good information.
+[I] couldn't find anything that said tools.''}
+
+%P11 in the repo, P9 in the paper
+\pquote{P9}{``I think you can only answer this question correctly if you know what a local proxy is.
+Otherwise you have no chance... because looking at the internet setting in another browser could be anything.''}
+
+The progress bar had dependencies that made it update oddly.
 If progress bar reached a 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%.
-Many assumed that their subsequent attempts were wrong because of this.
+This made many assume that their subsequent attempts were wrong.
+
+%P13 in the repo, P7 in the paper 
+\pquote{P7}{``I was kind of doubting myself because everything was really slow.''}
+
+%P16 in the repo, P13 in the paper
+\pquote{P13}{``Put in a 30 second timeout! I don't know, maybe it takes longer than that...''}
 
 %P1 in the repo, P15 in the paper
-\pquote{P15}{``It was hard to figure out if the progress bar wasn't moving because the connection was censored, or if it was just slow.''}
-
-We think users in the wild may also face these challenges, and that changes should be made to mitigate them. We show our attempt in the next section.
+\pquote{P15}{``there doesn't seem to be any timeout on any of this stuff. Am I waiting long enough? Should I wait 5 minutes?''}
+
+We have additional concerns on system visibility, error recovery, and user workload.
+Users cannot see their settings before or while they are connecting.
+This is only visible on the bridge and proxy screens.
+Participants did not know what to do after a connection failed.
+Users should be made aware of what to fix.
+Users do too much work (reading text, click throughs, choices) in this interface.
+We show an attempt to fix these issues in Section~\ref{sec:design}.
 
@@
 \subsection{Procedure} 
-Three researchers agreed on security and usability design principles. 
-We then rewatched screen capture videos and read interview transcriptions to brainstorm design changes.
-We provided the security and usability design principles, screen capture videos, interview transcriptions, and our suggested changes to a user interface designer, who iteratively redesigned the interface with our feedback and user interface best practices in mind.
-Figure~\ref{fig:new-interface} shows our redesign of the interface.
+We agreed on security and usability design principles, before reviewing our formative usability study observations and brainstorming changes to the interface.
+We worked with a user interface designer to iteratively design the interface.
+Figure~\ref{fig:new-interface} is the result.
 
@@
 
-In addition to addressing the pain points we discovered through our formative usability testing (Section~\ref{sec:pain-points}), we aimed to follow usability best practices by minimizing work, giving targeted feedback, and helping users build an understanding of the system.
+In order of priority, our design objectives were to minimize the user workload, to assist in user decision making, and to help users understand the system.
+We preferred to eliminate tasks if we could, help users through necessary tasks, and educate them only if this information would be useful for future decisions.
+These objectives were inspired by our previous usability study.
 
 \subsection{Changes Made} 
-We made these changes for a more usable interface. \\
-
-\noindent To minimize work: 
-\begin{itemize}
-\item We eliminated technical questions, resulting in fewer tasks and interface screens. 
-\item We simulated auto-detection for proxies, telling users that they did not need a proxy. This is feasible to do with a local scan (no information leaked). 
-\item We labeled the configure button as an option for users in heavily censored environments.
-\item We gave advice on choosing transports, telling users to try a meek bridge if obfs3 does not work.
-\end{itemize}
-
-To give targeted feedback: 
-\begin{itemize}
-\item We fixed the progress bar so that it reflects the current progress on subsequent attempts. 
-\item We switched added indicators to the progress bar to show the progress of bridges and proxies. 
-\item We told users what to try next on errors (i.e. choose a different bridge, try a without a proxy). 
-\end{itemize}
-
-To build an understanding of the system:
-\begin{itemize}
-\item We added a summary screen displays the current bridge and proxy settings for system visibility. 
-\item We switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}).
-\end{itemize}
-
-Figure~\ref{fig:new-interface} shows the resulting interface.  Figure~\ref{fig:old-interface} shows the unchanged version.
+To require our users to do less work, we eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and simulated auto-detection for proxies by telling users that they did not need a proxy (this is feasible to implement with a local scan that does not leak information.
+
+To help users decide what to do, we labeled the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and gave additional advice on choosing transports if the recommended one did not work.
+
+To help users understand what is going on, we added a summary screen displays the current bridge and proxy settings for system visibility, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators of components topological order into the progress bar to that show if various components reached successfully.
 
@@
 \subsection{Recruitment}
-We recruited  people using the recruitment text in Appendix~\ref{quantitative-recruitment}.
-We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool.
+We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool using text in Appendix~\ref{quantitative-recruitment}.
 <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants.
-Although the <redacted lab>'s participant pool is not limited to students and staff from <redacted institution>, it was estimated that a large majority were.
-
-124 people participated in our experiment, but we used data from 114.
-We filtered participants who made errors in completing the consent form or did not interact with the instrumented interface.
+<Redacted lab>'s participant pool is mainlystudents and staff from <redacted institution>, even though anyone could join.
+
+We had 124 participants, but we filtered out 10 participants who did not complet the consent form correctly or did not interact with the instrumented interface.
 Of the 114, one participant did not report their demographics.
@@
 84.1\% of our participants had at least a college education.
-We distributed participants evenly across experimental condition, about 20 in each interface and environment combination.
-Although there is variation in gender and age in each experimental condition, we ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
+We had about 20 in each interface and environment combination and ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
 
@@
 The testing room had 36 workstations with identical Windows~7 laptops.
-Side panels at each workstation to discouraged participants from looking at other participants' screens.
+Side panels at each workstation to discouraged participants from looking at other screens.
 %Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
@@
 
-Before each session, we ran a script that downloaded the necessary software, set up one of the three simulated environments (E1, E2, or E3), and downloaded the original Tor Browser 5.0.3 or a modified version of Tor Browser 5.0.3 that contained our design changes (OLD or NEW), and started the video recording.
-In contrast to the previous test, we installed an instrumented version of Tor Browser 5.0.3.
-The instrumentation logged user interactions, such as window transitions, mouse clicks, and menu selections.
-Similarly to the previous test, we installed Chrome, Firefox, and Internet Explorer to allow users to browse the Internet on a browser of their choice and VLC to record the screen during the experiment.
-Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room and assigned an equal number of participants to each experimental condition.
+Before each session, we ran a script that downloaded Firefox, Chrome, IE, and VLC, set up one of the three simulated environments (E1, E2, or E3), and downloaded a version of Tor Browser 5.0.3 (original or our design), and started the computer screen recording.
+In contrast to the previous test, the Tor Browser 5.0.3 was instrumented to log user interactions with it (clicks, selects, transitions, etc.).
+Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
 
 \subsection{Procedure}
-Participants were assigned to a computer at random, which effectively assigned them to a simulated censorship environment combination at random.
-Before the experiment began, participants were verbally informed of the purpose of the study, what data was collected, and any associated risks.
-If they wished to participate, they were informed again in writing and consented by signing the document.
-To be thorough, we clarified that they could stop at any time during the experiment with no negative consequences.
-
-The experiment formally began by informing participants of the simulated censorship environment, giving them their worksheet, and informing them that Tor browser is necessary to circumvent censorship (Appendix~\ref{quantitative-script}).
-This time, the worksheet only asks users to visit one blocked website (Wikipedia) and explicitly reminds users to use Tor to do so.
-Before participants started their tasks, we reminded them that their screens are being recorded so they should not log into anything that shows personal information.
-We gave users a chance to ask any questions about the experiment or task.
-
-Participants were given 40 minutes to complete the task.
+We assigned participants  to a simulated censorship environment combination at random by being assigning them to a computer at random.
+We told the participants the purpose of the study, what data was collected, and any associated risks.
+Then they signed a consent form with this information in writing.
+Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.
+
+We started by informing participants of the simulated censorship environment, giving them their worksheet,  informing them that Tor browser is necessary to circumvent censorship, and pointing out that Tor is installed for them on the computer (Appendix~\ref{quantitative-script}).
+They were asked to complete a worksheet that requires an answer from a censored site (Wikipedia) and explicitly reminds users to use Tor to do so (Appendix~\ref{summative-worksheet}).
+We reminded them to not show personal information since we are recording their screens, answered any questions, then gave them 40 minutes to complete the task.
+
 After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions.
@@
 In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}).
+
+\label{all-participant-edges} 
+\begin{figure*}
+\centering
+% This is a manually edited version of the automatically generated
+% all-participant-edges graphic. It is edited to have better scale labels for
+% the treatments.
+\includegraphics{all-participant-edges}
+\caption{
+A summary of our valid participants' paths through the interface.
+The length of the bars show the total time taken to complete the task,
+except for those we cut off after approximately 40 minutes.
+Different colors indicate which screen they were on during the experiment.
+If participants were doing other things (i.e. searching for help in another browser)
+while off-focus, this time still counts as spending time in that off-focus window. 
+``Not running'' are times when Tor Launcher was closed (
+i.e. restarting the application).}
+\label{fig:all-participant-edges}
+\end{figure*}
+
+\subsubsection{Completion Rate}
 
@@
 \end{table}
-
-\label{all-participant-edges} 
-\begin{figure*}
-\centering
-% This is a manually edited version of the automatically generated
-% all-participant-edges graphic. It is edited to have better scale labels for
-% the treatments.
-\includegraphics{all-participant-edges}
-\caption{
-A summary of our valid participants' paths through the interface.
-The length of the bars show the total time taken to complete the task,
-except for those we cut off after approximately 40 minutes.
-Different colors indicate which screen they were on during the experiment.
-If participants were doing other things (i.e. searching for help in another browser)
-while off-focus, this time still counts as spending time in that off-focus window. 
-``Not running'' are times when Tor Launcher was closed (
-i.e. restarting the application).}
-\label{fig:all-participant-edges}
-\end{figure*}
-
-\subsubsection{Completion Rate}
 
@@
 \caption{
-The dots show the raw connection times,
-while the boxplots show the medians and interquartile ranges.
-The ``DNF'' (did not finish) numbers at the right show how many of participants 
-did not finish, who were assigned the maximum time of 40:08.}
+Participants in E2 and E3 took a long time to connect.
+The ``DNF'' (did not finish) shows how many of participants 
+did not finish; they were assigned the maximum time of 40:08.}
 \label{fig:time_to_success_clamped}
@@
 \includegraphics{time_to_success_ecdf}
-\input{time_to_success_ecdf.tex}
-\caption{
-Cumulative success rates over time, shown continuously and at discrete times we found interesting.
-Notice that the longer the time went on, participants were less likely to succeed. 
-At 1.5 minutes, every E1-NEW participant had finished,
-but only 58\% of E1-OLD had finished by that time.  
-At 10 minutes, most participants in E2 had finished. 
+%\input{time_to_success_ecdf.tex}
+\caption{
+Cumulative success rates over time. The longer the time went on, participants were less likely to succeed. 
 }
@@
 \subsubsection{Configuration Time} 
-Configuration time is the time spent configuring network components, which we define as the completion time minus any time spent on the progress screen.
-Table~\ref{table:participant-summary} shows the median times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
-Table~\ref{table:median_time} shows the percentage of time spent on each screen.
-Note that the time spent configuring bridges and proxies is {\it not} equivalent to the amount of time participants spent trying to connect, which would be the connection time minus the time spent on the progress screen for the last time (time Tor takes to bootstrap after a valid configuration).
+Configuration is defined as the completion time minus {\it any} time spent on the progress screen.Table~\ref{table:participant-summary} shows the median times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
+Table~\ref{table:median_time} shows where participants spent their time.
+
+\begin{table}[t]
+\centering
+\input{median_time.tex}
+\caption{
+The median percent of time spent on each screen, aggregated over participants in each experimental condition. }
+\label{table:median_time}
+\end{table}
+
+\begin{figure}[t]
+\centering
+\includegraphics{time_to_success_active_clamped}
+\caption{
+Only a small fraction of the time was used to configure bridges and proxies.
+Non-finishing participants' active time was computed by
+subtracting the amount of time spent on the progress screen from the 
+their assigned completion time of 40:08.
+}
+\label{fig:time_to_success_active_clamped}
+\end{figure}
 
 %things to keep in mind
-We believe that configuration time is a meaningful metric because 1) bootstrapping can take a couple minutes, which dominates measurements for users do not need much time to configure their connection, such as participants in E1, and 2) some mistakes, such as using a syntactically valid but unusable proxy, generate non-interrupting warnings and let the users wait indefinitely until they manually cancel the connection to try again.
-But this is not the most accurate measurement of time spent configuring, since it does not reflect how some participants searched for help in another browser while waiting on the progress screen.
+We believe that configuration time is a meaningful metric because 1) bootstrapping can dominate measurements for users do not need much time to configure their connection (E1 participants), and 2) many errors do not interrupt the connection attempt and cause many users to wait a long time before they manually cancel the connection to try again.
+This is metric is not perfect though, since it does not reflect how some participants actively searched for help in another browser rather than passively waiting for their connections to work.
 
@@
 
-\begin{table}[t]
-\centering
-\input{median_time.tex}
-\caption{
-The median percent of time spent on each screen. 
-This percentage is computed independently for each screen; that is, a participant who spent the median percent 
-of time on one screen may not be the same participant who spent the median percent
-of time on other screens.}
-\label{table:median_time}
-\end{table}
-
-\begin{figure}[t]
-\centering
-\includegraphics{time_to_success_active_clamped}
-\caption{
-The dots show the raw active configuration times,
-while the boxplots show the medians and interquartile ranges.
-Here, non-finishing participants' active time was computed by
-subtracting the amount of time spent on the progress screen from the 
-their assigned completion time of 40:08.
-}
-\label{fig:time_to_success_active_clamped}
-\end{figure}
-
 \subsection{Usability of Tor Launcher} 
-In total, 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-On average, users who required a bridge took over 3 minutes to connect to Tor, and users who required a meek or custom bridge took over 20 minutes.
+We confirmed our observations from our formative usability test and find that participants wait the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.
+
+From our measurements, we find that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
+Users average over 3 minutes if they needed a bridge and averaging over 20 minutes if they needed a meek or custom bridge.
 
@@
 \label{sec:recommendations}
-We do believe that adopting our design will help save users time when connecting to Tor.
-But since we did not test our design changes independently, we cannot (and do not) claim the effects each change we made.
-Therefore, we do not recommend specific changes, but offer some suggestions for Tor Launcher's GUI based on what we learned: \\
+We believe that adopting our design will save users time.
+But since we did not test our design changes independently, we cannot (and do not) claim the effects each change.
+We do not recommend specific changes, but offer some suggestions based on what we learned: \\
 
@@
 \label{sec:limitations}
-We did not study international users, or the configuration interface in languages other than English.
+We did not study international users, or the interface in languages other than English.
 All of our participants were from the United States and were instructed to interact with the English version of Tor Browser.
@@
 Participants in a laboratory setting may alter their behavior due to their awareness of being observed~\cite{mccarney2007hawthorne}.
-We are aware that our participants were likely motivated differently compared to real users.
-We believe that participants were likely overmotivated to connect to Tor because they were being observed and receiving a monetary reward.
-If true, this makes our results are a conservative estimate of the current usability problems.
+Our participants were likely motivated differently compared to real users, but we believe that they were likely overmotivated because they were being observed and receiving a monetary reward.
+If true, this makes our results a conservative estimate of the usability problems.
 
@@
 
-Our experiment did not directly test more advanced tasks.
-Our simulated environments did not require users to configure a proxy or to get a custom bridge.
-From observing of user attempts to configure proxies and get custom bridges, we suspect users generally struggle with these tasks but cannot quantify how much they do.
-
-We only tested the interface on Windows machines, which were the machines available at <redacted>. %Xlab.
-The configuration interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalent.
-Additionally, we acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
+Our experiment did not directly test advanced tasks such as configuring a proxy or a custom bridge. From observing  users, we suspect they struggle with these tasks.
+
+We only tested the interface with Windows machines.
+The interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalents.
+We acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
 
@@
 \label{sec:related} 
-
 {\color {red} 
+% intro to usable security 
+Researchers have been studying usable computer security for decades. 
+%the paper that started it all: ~\ref{whitten1999johnny}
+
+% methods
+qualitative analysis, quantitative analysis, cognitive walkthroughs
+%usability inspection: ~\ref{nielsen1994usability}
+%heuristic evaluation: ~\ref{nielsen1994heuristic}
+%improving dialogue: ~\ref{molich1990improving}
+
+% focuses
+graphical redesign, redesigning interactions, user education
+
+% user help 
+% explicit goals and subgoals ~\ref{reeder2005user}
+% hypothesis elimination ~\ref{wason1960failure}
+% user tolerance on security delays ~\ref{egelmanplease}
+
+% subjects 
+Two consistent areas of research are user authentication and email encryption ~\ref{payne2008brief}.
+%%% driveby citations of user authentication papers here
+%%% driveby citations of email authentication papers here. 
+There has not been much usable security work on cencorship circumvention or anonymity.
+
 % Previous Tor studies 
@@
 some of which influenced changes in Tor Browser version~4.5 and later.
-
-Previous user studies have considered the whole browsing experience,
-without focusing on specific features in isolation.
-Our study focuses on 
-the browser's configuration interface, which guides users through setting up components required to circumvent censorship.
-
-% Scoping our work wrt usable security, usability, and interaction design  
-Our work combines the three.
-We try to make it as usable as possible by following usability practices (reducing load, not having people remember, easy learning curve, etc.) But at the same time, we also tried to make some things hard and kept things hard (not automating things that would be dangerous) like confirm if you want to delete everything is a useful feature, and it's more usable security than usability.
-Our thing was more interaction design--we changed from letting the users guide to telling them, to making it as easy as possible to having a consistent model.
-We didn't really do any real design except to prove the concept (cite Adrienne's warning study with icons and colors), and while we tried to make it good, we didn't reaaaaallly thorougly test out the icons and wording and whatnot.
 }
@@
 
-\section{Qualitative User Study Recruitment Posting} 
+\section{Formative User Study Recruitment Posting} 
 \label{qualitative-recruitment}
@@
 
-\section{Qualitative User Study Prescreening Survey} 
+\section{Formative User Study Prescreening Survey} 
 \label{qualitative-prescreening}
@@
 
-\section{Qualitative User Study Introduction Script} 
+\section{Formative User Study Introduction Script} 
 \label{qualitative-script} 
@@
 
-\section{Participant Worksheet Text} 
+\section{Formative Study Worksheet Text} 
 \label{participant-worksheet}
@@
 
-\section{Quantitative User Recruitment Posting}
+\section{Summative User Study Recruitment Posting}
 \label{quantitative-recruitment}
@@
 
-\section{Quantitative User Study Introduction Script} 
+\section{Summative User Study Introduction Script} 
 \label{quantitative-script} 
@@
 
-\section{Quantitative User Study Exit Survey} 
+\section{Summative User Study Worksheet Text} 
+\label{summative-worksheet}
+Imagine you live in an oppressive country that censors part of the Internet. We have simulated this in the laboratory by blocking certain websites and services.
+
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+For instance, www.torproject.org is blocked.
+Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
+It will fail to load, when you can visit other sites.
+
+To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
+If you can visit wikipedia, then you know that you have successfully circumvented censorship.
+
+1. Visit Wikipedia’s main page (\url{https://en.wikipedia.org/wiki/Main\_Page}). What is the topic of today’s selected article?
+
+2. After you have completed the tasks, fill out this survey: http://bit.ly/tor-survey
+
+\section{Summative User Study Exit Survey} 
 \label{quantitative-exit-survey}

### 2016-11-21 pets2017-paper/pets2017-paper.tex
finishing touches, change words back to qualitative and quantitative, and finish related work.

@@
 \section{Methodology} 
-This section discusses our process, principles, and preparations for evaluating the configuration interface.
+This section discusses how we performed our summative evaluation to determine the interface's effectiveness.
 
 \subsection{Testing Pipeline} 
-We performed a cognitive walkthrough~\cite{cognitive-walkthrough} to prepare for user testing.
-This evaluation method involved usability evaluators to working through a series of tasks from the perspective of the user, trying to understand a system's learnability for new or infrequent users.
-
-We then conducted a formative usability test~\cite{formative} that found where and why users struggle.
-This testing is usually used as a support tool to find improvements.
-Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each experimental condition.
-
-We opportunistically used our observations to make changes to the interface.
-We believed that the process of identifying design principles, drafting design changes, and testing an alternative interface would be insightful.
-
-We concluded with a summative usability test~\cite{summative} that measured the usability of the current and redesigned interface.
-This testing is a usually used as quality assurance tool to test features.
-In short, formative testing tells you {\it what} is is not usable, while summative testing testing tells you {\it if} it is or is not usable.
-Twenty users is considered to be a minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each experimental condition.
+We performed a cognitive walkthrough~\cite{cognitive-walkthrough} of the interface by working tasks from the perspective of the user and assessing its learnability for new or infrequent users.
+
+We then conducted qualitative and quantiative usability tests of the interface.
+We believed that both were necessary for a complete evaluation.
+Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing testing tells you {\it how much} it is or is not usable.
+Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each condition in our qualitative experiment.
+Twenty users is considered to be a minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.
+
+We opportunistically used our observations from the qualitative study to design interface changes that would address common issues that our participants encountered.
+We also opportunistically used our quantitive testing setup to measure its usability with respect to the the original interface.
+We found the process of identifying design principles, drafting design changes, and testing an alternative interface to be insightful and hope that this may be insightful to others as well.
 
@@
 Two researchers performed the cognitive walkthrough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
-We systematically tried action sequences from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
+We systematically tried actions from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
 
@@
 We used the map of potential user paths (Figure~\ref{fig:digraph}) to design our simulated environments (section~\ref{sec:environments}).
-We used our walkthrough observations as inspiration for drafting our post-experiment interview questions (Appendix~\ref{interview-questions}) for formative usability testing.
+We used our walkthrough observations as inspiration for drafting our post-experiment interview questions (Appendix~\ref{interview-questions}) for qualitative usability testing.
 
@@
 
-\section{Formative Usability Testing}
+\section{Qualitative User Testing}
 \label{sec:qualitative}
@@
 \subsection{Procedure}
-Three researchers ran the formative usability tests, with each session having at least two researchers.  
+Three researchers ran the qualitative user tests. Each session had at least two researchers.  
 We told the participant the purpose of the 
@@
 \label{sec:design} 
-This section discusses how we converted our formative usability testing observations into design changes.
+This section discusses how we converted our qualitative user testing observations into design changes.
 
 \subsection{Procedure} 
-We agreed on security and usability design principles, before reviewing our formative usability study observations and brainstorming changes to the interface.
+We agreed on security and usability design principles, before reviewing our qualitative usability study observations and brainstorming changes to the interface.
 We worked with a user interface designer to iteratively design the interface.
@@
 
-\section{Summative Usability Testing}
+\section{Quantitative User Testing}
 \label{sec:quantitative}
@@
 \subsection{Usability of Tor Launcher} 
-We confirmed our observations from our formative usability test and find that participants wait the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.
+We confirmed our observations from our qualitative user test and find that participants wait the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.
 
@@
 \begin{itemize}
-\item {\bfseries Hide infrequent options.} Hide the proxy configuration screen and less-used transports.
-None of our participants connected using flashproxy, fte, fte-ipv6, or scramblesuit transport bridges.
-\item {\bfseries Give advice.} Discourage users from configuring optional components.
-Add a secondary recommendation for bridges (try meek if obfs3 doesn't work, use meek if you are in China) to help users in need.
-\item {\bfseries Minimize work.} Detect if users need a proxy or not. Redirect users to the relevant pages on error (i.e. redirect to the bridge screen the bridge fails).  
-\item {\bfseries Provide feedback.} Tell users what to do when a specific error occurs (i.e.
-try the same connection again, pick another bridge, try without a proxy, etc.).
-Show users their bridge and proxy settings before and during connection.
-Fix the progress bar so that it updates on subsequent connections.
+\item {\bfseries Hide the proxy configuration screen and less-used transports.} None of our participants connected using flashproxy, fte, fte-ipv6, or scramblesuit transport bridges.
+Hiding infrequently used options will help users make better choices.
+\item {\bfseries Discourage users from configuring optional components.} Many participants configured proxies and bridges that they did not need. Add more explicit guidance on when to use them.
+\item {\bfseries Redirect to relevant screens on error.} For instance, redirect users to the bridge screen if the bridge failed instead of requiring users to do so.
+\item {\bfseries Take advantage of the progress screen.} Participants spent a majority of their time here.
+This time could be used to inform them of their bridge and proxy settings, educate users about what Tor does, or introduce Tor Browser.
 \end{itemize}
@@
 \label{sec:related} 
-{\color {red} 
 % intro to usable security 
-Researchers have been studying usable computer security for decades. 
-%the paper that started it all: ~\ref{whitten1999johnny}
-
-% methods
-qualitative analysis, quantitative analysis, cognitive walkthroughs
-%usability inspection: ~\ref{nielsen1994usability}
-%heuristic evaluation: ~\ref{nielsen1994heuristic}
-%improving dialogue: ~\ref{molich1990improving}
-
-% focuses
-graphical redesign, redesigning interactions, user education
-
-% user help 
-% explicit goals and subgoals ~\ref{reeder2005user}
-% hypothesis elimination ~\ref{wason1960failure}
-% user tolerance on security delays ~\ref{egelmanplease}
-
-% subjects 
-Two consistent areas of research are user authentication and email encryption ~\ref{payne2008brief}.
-%%% driveby citations of user authentication papers here
-%%% driveby citations of email authentication papers here. 
-There has not been much usable security work on cencorship circumvention or anonymity.
+The difference between a poor interface and a good interface can influence users’ ability to perform tasks securely~\cite{payne2008brief}.
+Usable security aims to improve the security of a system by designing with the user in mind.
+This involves informing users about the system, communicating risks in a way that is understandable, clarifying what the security requirements are, and providing guidance with technical tasks~\cite{adams1999users}.
+Our work contributes to the body of usable security by evaluating Tor Browser, which is an anonymity and censorship circumvention software that requires user interaction.
+Other usable security research explores on a variety of security software or features, such as email encryption sofware ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
+
+Usability inspection methods~\cite{nielsen1994usability} are used to define usability problems in an interface. We
+used a cognitive walkthrough~\cite{wharton1994cognitive}\cite{cognitive-walkthrough} to evaluate our interface.
+Other inspection methods include heuristic evaluation, pluralistic walkthrough and feature inspection~\cite{inspection}.
+
+We used usability lab studies (one-on-one experiments witha  given a set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}.
+There are other ways to collect behavioral data as well, such as eyetracking, clickstream analysis and AB testing.
+These are in contrast with a variety of user experience research methods that collect qualitative or quantitative attitudnal data, such as focus group, camera studies, and product surveys~\cite{ux-methods}.
+We performed interviews after our lab study, but we mostly used these interviews to verify our behavioral observations rather than to draw conclusions about what people thought about their experience.
+
+User-centered design improves the usability of software by accounting for user factors. 
+Some work we found especially relevant to improving the usability of Tor Browser were
+Yee et~al.'s starting points for reasoning about security from
+a user-centred perspective and principles for secure interaction design ~\cite{yee2002user},  
+Molich et~al.'s examination of  common problems in human-computer dialogue deisgn ~\cite{molich1990improving}, and Egelman et~al's examination of user tolerance of security delays~\cite{egelmanplease}.
 
 % Previous Tor studies 
-There have been three published user studies on Tor. Clark et~al.~\cite{clark2007usability} examined various deployment
-options for Tor Browser, such as Vidalia, Privoxy, Torbutton, and FoxyProxy, and found that none had satisfactory from a usability. Fabian et~al.~\cite{fabian2010privately} show that Tor's added
-latency~\cite{dingledine2009performance} causes users
-to be frustrated, cancel requests, and prevents user adoption. 
-Norcie et~al.~\cite{norcie2012eliminating} found found that 
-64\% of users are unable to continue with installation or browsing at least once due to difficulties.
-
+Our work uniquely contributes to Tor by examining the usability of the configuration interface.  
+Previous usability studies on Tor have focused on installation and use.
+Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable complete installation or browsing tasks.
+Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonmity~\cite{dingledine2009performance} but reduces usability.
+They quantified how the difference in latency causes frustration and decreases adoption.
+Clark et~al.~\cite{clark2007usability} performed a cognitive walkthrough of Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy) and found that none were satisfactory from a usability perspective.
+They highlight the best aspects of each tool and offer usability improvements.
 We do not know of any published usability evaluations of
-Tor Browser since the release of the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-The most recent effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
-that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
-some of which influenced changes in Tor Browser version~4.5 and later.
-}
+Tor Browser the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
+Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser tp observe their behavior.
+This unconvered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.
 
@@
 %proof that user testing is important and general advice to for more research on Tor
-We encourage usability testing for Tor Browser and other Tor applications because it provides user insight for products without user interaction data.
+We encourage user testing for Tor Browser and other Tor applications because it provides user insight for products without user interaction data.
 Tor Browser version~4.5 incorporated changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.
@@
 Due to space constraints, we could not include many of our experiment artifacts.
-This includes the experiment setup and teardown code, firewall rules that simulated censorship environments, interview transcriptions from the formative user study, logs from our instrumented configuration interfaces, and videos of users attempting to connect to Tor through the configuration interface.
+This includes the experiment setup and teardown code, firewall rules that simulated censorship environments, interview transcriptions from the qualitative user study, logs from our instrumented configuration interfaces, and videos of users attempting to connect to Tor through the configuration interface.
 We urge you to check out the project repository: \\
@@
 \bibliographystyle{abbrv}
-\bibliography{pets2017-paper}
+\bibliography{pets2017-paper.bib}
 
@@
 \label{states} 
-An exhaustive list of Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}.
-End states such as e\# and $\mbox{e\#}^\prime$ are equivalent, but $\mbox{e\#}^\prime$ uses a bridge while e\# does not.
-This was generated during the inspection process.\\
+Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}. E\# and $\mbox{e\#}^\prime$ are equivalent, but $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\
 
@@
 
-The same input can lead to different end states.
+Same inputs can lead to different end states.
 Tor Launcher will connect to a proxy successfully with the port left blank if the proxy uses port 80 (s2) but will not if the proxy uses another port (e12).
 
-\section{Formative User Study Recruitment Posting} 
+\section{Qualitative User Study Recruitment Posting} 
 \label{qualitative-recruitment}
@@
 
-\section{Formative User Study Prescreening Survey} 
+\section{Qualitative User Study Prescreening Survey} 
 \label{qualitative-prescreening}
@@
 \label{prescreening-responses}
-We asked people how familiar they were with some technical terms and security tools during our prescreening survey for formative usability testing.
+We asked people how familiar they were with some technical terms and security tools during our prescreening survey for qualitative usability testing.
 We did {\it not} use this information to influence the experimental procedure (i.e.
@@
 \caption{
-Formative users' self-reported familiarity with various security terms. 
+Qualitative users' self-reported familiarity with various security terms. 
 }
@@
 \caption{
-Formative users' self-reported use of various security software. 
+Qualitative users' self-reported use of various security software. 
 }
@@
 
-\section{Formative User Study Introduction Script} 
+\section{Qualitative User Study Introduction Script} 
 \label{qualitative-script} 
@@
 
-\section{Formative Study Worksheet Text} 
+\section{Qualitative Study Worksheet Text} 
 \label{participant-worksheet}
@@
 
-\section{Summative User Study Recruitment Posting}
+\section{Quantitative User Study Recruitment Posting}
 \label{quantitative-recruitment}
@@
 
-\section{Summative User Study Introduction Script} 
+\section{Quantitative User Study Introduction Script} 
 \label{quantitative-script} 
@@
 
-\section{Summative User Study Worksheet Text} 
+\section{Quantitative User Study Worksheet Text} 
 \label{summative-worksheet}
@@
 
-\section{Summative User Study Exit Survey} 
+\section{Quantitative User Study Exit Survey} 
 \label{quantitative-exit-survey}
@@
 \item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies.
-If they fail, then a network adversary already knows that the user is trying to connect to Tor.
-At this point, we believe that it is low risk to naively automate configuring bridges and proxies.
+If they fail, then a network eavesdropper already knows that the user is trying to connect to Tor.
+We believe there is negligible added risk to naively automate the connection.
 \item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any.
@@
 \end{description}
-
 We believe that these ideas can significantly help users connect to Tor.

### 2016-11-21 pets2017-paper/pets2017-paper.tex
reword abstract and conclusion, check spelling

@@
 and configures the necessary network components to connect to Tor. 
-We use a combination of user observations and user interaction logs to determine
-where the interface is not usable, and quantify how unusable the interface is. We 
-offer some suggestions for the interface based on what 
-we have learned and also suggest alternative approaches 
-to bootstrap a connection to Tor that do not require new users to configure the network components. 
+We qualify where the interface is not usable with user observations 
+and quantify how unusable the interface is with user interaction logs. 
+Based on what we learned, we recommend some changes that 
+we believe will help users connect to Tor in censored environments. 
+We conclude by starting a discussion on alternative 
+approaches to bootstrap a connection to Tor. 
 }
@@
 
-In this paper, the word``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
+In this paper, the word ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
 This is to maintain consistency with the wording in the configuration interface.
@@
 
-Tor relays are the routers in the Tor network. The Tor network is a group of routers that peform onion routing, a technique for anonymous communication over a computer network.  
+Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  
 Guard relays that serve as an entry node into the Tor network and receive packets from the user.
@@
 Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.
-A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is is being censored.
+A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is being censored.
 
@@
 
-State level censors block access to the Tor network by blocking pubicly listed Tor relays.
+State level censors block access to the Tor network by blocking publicly listed Tor relays.
 Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
-This means that users can connect directly to websites, but some may be blocked as is Tor.
+This means that users can connect directly to (uncensored) websites, but Tor is blocked.
 The thoroughness of censorship is what requires different bridges and transports.
@@
 We believed that both were necessary for a complete evaluation.
-Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing testing tells you {\it how much} it is or is not usable.
+Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable.
 Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each condition in our qualitative experiment.
-Twenty users is considered to be a minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.
+Twenty users is considered to be the minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.
 
 We opportunistically used our observations from the qualitative study to design interface changes that would address common issues that our participants encountered.
-We also opportunistically used our quantitive testing setup to measure its usability with respect to the the original interface.
+We also opportunistically used our quantitative testing setup to measure its usability with respect to the original interface.
 We found the process of identifying design principles, drafting design changes, and testing an alternative interface to be insightful and hope that this may be insightful to others as well.
@@
 So we used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
-and the Windows operating system hosts file to to block websites by
+and the Windows operating system hosts file to block websites by
 mapping domain names to localhost (127.0.0.1) (E1, E2, E3).
@@
 \subsubsection{E2} 
-In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges aquired out of band would work. Configuring a proxy was optional.
+In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
 Observations in E2:
@@
 Participants in E3 also generally tried a direct connection to Tor.
-They did not know if they needed a bridge or proxy, and like the participnts in E2, only configured them when the direct connection failed.
+They did not know if they needed a bridge or proxy, and like the participants in E2, only configured them when the direct connection failed.
 But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work.
@@
 The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed.
-P14 brute forced options until something worked, P15 did not think that thye used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
+P14 brute forced options until something worked, P15 did not think that they used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
 
@@
 \pquote{P9}{``I think you can only answer this question correctly if you know what a local proxy is.
-Otherwise you have no chance... because looking at the internet setting in another browser could be anything.''}
+Otherwise you have no chance... because looking at the Internet setting in another browser could be anything.''}
 
@@
 <Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants.
-<Redacted lab>'s participant pool is mainlystudents and staff from <redacted institution>, even though anyone could join.
-
-We had 124 participants, but we filtered out 10 participants who did not complet the consent form correctly or did not interact with the instrumented interface.
+<Redacted lab>'s participant pool is mainly students and staff from <redacted institution>, even though anyone could join.
+
+We had 124 participants, but we filtered out 10 participants who did not complete the consent form correctly or did not interact with the instrumented interface.
 Of the 114, one participant did not report their demographics.
@@
 
-We used usability lab studies (one-on-one experiments witha  given a set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}.
-There are other ways to collect behavioral data as well, such as eyetracking, clickstream analysis and AB testing.
-These are in contrast with a variety of user experience research methods that collect qualitative or quantitative attitudnal data, such as focus group, camera studies, and product surveys~\cite{ux-methods}.
+We used usability lab studies (one-on-one experiments with a given a set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}.
+There are other ways to collect behavioral data as well, such as eye tracking, clickstream analysis and AB testing.
+These are in contrast with a variety of user experience research methods that collect qualitative or quantitative attitudinal data, such as focus group, camera studies, and product surveys~\cite{ux-methods}.
 We performed interviews after our lab study, but we mostly used these interviews to verify our behavioral observations rather than to draw conclusions about what people thought about their experience.
@@
 Yee et~al.'s starting points for reasoning about security from
-a user-centred perspective and principles for secure interaction design ~\cite{yee2002user},  
-Molich et~al.'s examination of  common problems in human-computer dialogue deisgn ~\cite{molich1990improving}, and Egelman et~al's examination of user tolerance of security delays~\cite{egelmanplease}.
+a user-centered perspective and principles for secure interaction design~\cite{yee2002user},  
+Molich et~al.'s examination of  common problems in human-computer dialogue design~\cite{molich1990improving}, and Egelman et~al's examination of user tolerance of security delays~\cite{egelmanplease}.
 
@@
 Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable complete installation or browsing tasks.
-Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonmity~\cite{dingledine2009performance} but reduces usability.
+Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonymity~\cite{dingledine2009performance} but reduces usability.
 They quantified how the difference in latency causes frustration and decreases adoption.
@@
 Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser tp observe their behavior.
-This unconvered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.
+This uncovered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.
 
@@
 \label{sec:conclusion}
-The Tor Launcher GUI allows most users to connect to the Tor network, provided that the user's connection does not require a proxy or a non-default bridge.
-User observation showed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring proxies that they did not need.
-User testing showed that most people take more than 10 minutes to connect to Tor if they need to use bridges.
+Users who do not require a proxy or a non-default bridge can usually connect to connect to the Tor network with the Tor Launcher GUI.
+However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need.
+User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored.
 
 %proof that user testing is important and general advice to for more research on Tor
-We encourage user testing for Tor Browser and other Tor applications because it provides user insight for products without user interaction data.
 Tor Browser version~4.5 incorporated changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.
 We also talked to Tor developers about ways to automate the bootstrapping process to Tor.
+We encourage user testing for Tor applications to provide user insight into products that do not collect user data.
+We found the use of simulated censorship environments were especially helpful in running our experiments, due to their reproducibility, stability, and simplicity.
 

### 2016-11-21 pets2017-paper/pets2017-paper.tex
fixing steve's initial comments

@@
 {
-We perform the first usability test on Tor Launcher, a graphical user interface (GUI) 
-that all Tor Browser users must use to configure their initial connection to the Tor network. 
-We believe that the interface is usable if a new user can to identify what to do,
-knows if and when they do the right thing in the process, 
-and configures the necessary network components to connect to Tor. 
-We qualify where the interface is not usable with user observations 
-and quantify how unusable the interface is with user interaction logs. 
-Based on what we learned, we recommend some changes that 
-we believe will help users connect to Tor in censored environments. 
-We conclude by starting a discussion on alternative 
+We perform the first usability test on Tor Launcher, a graphical user interface (GUI) that all Tor Browser users must use to configure their initial connection to the Tor network.
+Users who do not require a proxy or a non-default bridge can usually connect to connect to the Tor network with the Tor Launcher GUI.
+However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need.
+User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored.
+We conclude with recommendations based on what we learned and by start a discussion on alternative
 approaches to bootstrap a connection to Tor. 
@@
 \item an inspection of the Tor Launcher 5.0.3 interface
-\item user connection attempts in various environments
 \item what users found challenging about the interface
@@
 \item recommendations to improve the interface
-\item alternatives to burdening users with configuration 
 \end{itemize}
@@
 \label{sec:conclusion}
-Users who do not require a proxy or a non-default bridge can usually connect to connect to the Tor network with the Tor Launcher GUI.
-However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need.
-User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored.
+We believe that an interface is usable if a new user can to identify what to do, knows if and when they do the right thing in the process, and can accomplish the required tasks.
+Tor Browser 5.0.3's configuration interface does not meet these requirements.
+We qualified where the interface is not usable with user observations and quantified how unusable the interface is with user interaction logs.
+We believe that our recommended hanges will will help users connect to Tor in censored environments, but encourage discussion about alternative ways to configure a connection that would be easier for users.
 

### 2016-11-24 experiment/processing/info.R
Show total participant count at the beginning of info.R.
The first summary of participants counts was meant to include "bad"
participants:
	number of participants: 124 (114 good, 10 bad)
The list was being filtered too early, resulting in:
	number of participants: 114 (114 good, 0 bad)
The list is re-read after this first line is printed, omitting all "bad"
participants, so this doesn't affect any other lines.

This commit undoes one line of a396064a.

@@ -1,7 +1,7 @@
 library(coin)
 source("common.R")
 
-participants <- filter_participants(read_participants())
+participants <- read_participants()
 
 format_percent <- function(x) {
 	sprintf("%5.1f%%", 100*x)

### 2016-11-24 experiment/processing/info.R
Output demographics information in info.R.

@@ -59,6 +59,24 @@ max.e1.new <- max(participants$time_to_success[participants$env=="E1" & particip
 cat(sprintf("maximum time for E1-NEW: %s\n", format_minutes(max.e1.new)))
 
 cat("\n\n\n\n\n\n")
+cat("****************\n")
+cat("* DEMOGRAPHICS *\n")
+cat("****************\n")
+
+demographics <- read.csv("summative-demographics.csv")
+demographics <- merge(demographics, participants, by=c("session", "seat"), all=F) # omits participants that did not do the demographic survey
+
+n <- nrow(demographics)
+cat(sprintf("of %d demographic surveys,\n", n))
+cat(sprintf("male:    %s\n", pctsummary(demographics$"What.is.your.gender." == "Male")))
+cat(sprintf("female:  %s\n", pctsummary(demographics$"What.is.your.gender." == "Female")))
+cat(sprintf("neither: %s\n", pctsummary(!(demographics$"What.is.your.gender." %in% c("Male", "Female")))))
+cat("age distribution:\n")
+summary(demographics[, "What.is.your.age."])
+sd(demographics[, "What.is.your.age."])
+table(demographics$"Please.select.your.highest.completed..or.current..level.or.education.")
+
+cat("\n\n\n\n\n\n")
 cat("****************************\n")
 cat("* SCREEN SPECIFIC ANALYSES *\n")
 cat("****************************\n")

### 2016-11-24 pets2017-paper/pets2017-paper.tex
Make degrees-of-freedom "df" presentation uniform.
I actually don't know if this should be roman or italic. It was roman in
one place and italic in the other. I made it roman in both places.

@@
 %success rate and version
-Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $df = 2$, $p = 0.094$).
+Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $\mbox{df} = 2$, $p = 0.094$).
 That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.

### 2017-02-15 pets2017-paper/pets2017-paper.tex
clean up repo

--- 2016-11-21 pets2017-paper/pets2017-paper.tex
@@
 
-\section{Prescreening Survey Responses}
-\label{prescreening-responses}
-We asked people how familiar they were with some technical terms and security tools during our prescreening survey for qualitative usability testing.
-We did {\it not} use this information to influence the experimental procedure (i.e.
-use this to pick their environment).
-We show their responses:
-
-\begin{table}[h]
-\centering
-\begin{tabular}{l r r}
-& Familiarity\\
-\noalign{\hrule}
-Malware & 81\% (13/16) \\ %13/16
-Proxy services & 69\% (11/16)\\ %11/16
-Phishing & 63\% (10/16)\\ %10/16
-SSL & 63\% (10/16)\\%10/16
-X.511 certificates & 25\% (4/16)\\ %4/16
-Tor & 50\% (8/16)\\ %8/16
-\end{tabular}
-\caption{
-Qualitative users' self-reported familiarity with various security terms. 
-}
-\label{table:selfreported-tech}
-\end{table}
-
-Table~\ref{table:selfreported-software} lists their self-reported familiarity with various security concepts.
-Some reported that they were familiar a term that did not exist (x.511 certificates).
-We inserted this fictional term specifically to detect this.
-We suspect that participants answered dishonestly in hopes of appearing more technically fluent.
-
-\begin{table*}[h]
-\centering
-\begin{tabular}{l r r r r r r}
-& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Less than once} & \multicolumn{1}{r}{A few times}& \multicolumn{1}{r}{Several times}& \multicolumn{1}{r}{} & \multicolumn{1}{r}{Missing}\\
-& \multicolumn{1}{r}{Never} & \multicolumn{1}{r}{a month} & \multicolumn{1}{r}{a month}& \multicolumn{1}{r}{a week}& \multicolumn{1}{r}{Daily} & \multicolumn{1}{r}{answer}\\
-\noalign{\hrule}
-HTTPS on web pages				& 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 25\% (4/16) & 56\% (9/16) & 0\% (0/16) \\
-Proxies or censorship circumvention tools & 50\% (8/16) & 13\% (2/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 13\% (2/16) \\
-Virtual private networks (VPNs) 		& 44\% (7/16) & 31\% (5/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
-File or disk encryption 				& 50\% (8/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 25\% (4/16) & 1\% (1/16) \\
-Anonymity systems (e.g. Tor) 			& 63\% (10/16) & 13\% (2/16) & 1\% (1/16) & 13\% (2/16) & 0\% (0/16) & 1\% (1/16) \\
-Email encryption (e.g. PGP) 			& 50\% (8/16) & 19\% (3/16) & 19\% (3/16) & 0\% (0/16) & 1\% (1/16) & 1\% (1/16) \\
-Instant messaging encryption 			& 44\% (7/16) & 25\% (4/16) & 13\% (2/16) & 1\% (1/16) & 1\% (1/16) & 1\% (1/16) \\
-Voice communication encryption 		& 81\% (13/16) & 1\% (1/16) & 1\% (1/16) & 0\% (0/16) & 0\% (0/16) &1\% (1/16)\\
-\end{tabular}
-\caption{
-Qualitative users' self-reported use of various security software. 
-}
-\label{table:selfreported-software}
-\end{table*}
-
-Table~\ref{table:selfreported-software} lists their self-reported use of security software.
-Similarly to self-reported familiarity, we assume that participants answered to appear more technically fluent.
-We assumed that this self-reported use of security tools is an approximate upper bound of how many have actually used these security tools.
-
 \section{Qualitative User Study Introduction Script} 

### 2017-02-15 pets2017-paper/pets2017-paper.tex
delete reference to extraneous information
shuffle some things around.

@@
 All of our users were highly educated, having at least some college education.
-We show their self-reported familiarity with technical terms use of security tools in  Appendix~\ref{prescreening-responses}.
 We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.
@@
 \subsection{Results}
-We use out screen recording and interview data to give a summary of each participant.
-
-%E1: P2, P3, P4, P9, P10
-%E2: P7, P8, P11, P12, P13
-%E3: P1, P5, P6, P14, P15, P16
-
-%TODO: re-watch the videos and get the exact times. 
-%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos
-
-\subsubsection{E1} 
-In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
-Observations in E1:
-
-%P9 (regular): E1 (0:39; 4:49 to 5:28)
-\pquote{P1 (new user, direct, 0:39)}{They connected directly.}
-
-%P2(regular): E1 (1:20, 0:22 to 1:42) 
-\pquote{P2 (new user, direct, 1:20)}{They spent time reading the text on the start screen, and connected directly because they were intimidated by the other option.}
-
-%P3(regular): E1 (N/A; 5:47 to 6:26) 
-\pquote{P3 (new user, obfs3, 1:39)}{They connected with the recommended bridge. They were also going to use a proxy, but decided not to when they saw the proxy input fields.}
-
-%P4(regular): E1 (8:56, 7:22 to 16:18)
-\pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy.
-After not being able to fill out the proxy input fields, they started over and connected with an obfs4 bridge.
-Note that they did not try connecting with the obfs3 bridge, which would have worked.}
-
-%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
-\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}
-
-Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily configured bridges.
-
-\subsubsection{E2} 
-In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
-Observations in E2:
-
-%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
-\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly.
-After watching the progress bar not make any progress for a couple minutes, and gave up on the direct connection.
-Then they connected with the recommended bridge.}
-
-%P13 (regular): E2 (7:48; 0:34 to 9:22) 
-\pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly.
-They restarted Tor Launcher and tried to connect directly again---and repeated this two more times.
-On the fourth restart, they tried to configure a proxy, but gave up.
-On the fifth restart, they connected using the recommended bridge.}
-
-%P12 (regular): E2 (10:40; 0:46 to 11:26)
-\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly.
-After waiting a couple minutes, they figured that did not work and looked at proxy settings.
-But after looking at the settings and being intimidated, they tried connecting directly again.
-Then, they tried to configure a proxy, and gave up.
-They tried connecting directly again, which worked unexpectedly.
-They found a bug in our setup that we fixed for the later experiment.
-E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.
-}
-
-%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
-\pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly.
-And they tried connecting directly through a different user path by answering no to bridge and proxy questions in the interface, connecting from the proxy screen.
-Then, they connected using the recommended bridge.}
-
-%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
-\pquote{P10 (previous Tor user, failed to connect)}{They tried a direct connection.
-Then, they tried a connection with the recommended bridge, which should have worked.
-However, our setup experienced a clock drift.
-Tor does not allow connections with bad clocks.
-They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).
-This participant tried the most attempts to connect to Tor, using a variety of bridges and proxies.}
-
-Participants in E2 tried a direct connection to Tor before {\it eventually} connecting with the recommended bridge.
-They spent a fair amount of time waiting before determining that connections failed.
-Some stated that they connected directly because the interface says that it would work in ``most situations'' (Figure~\ref{fig:old-first}).
-Our participants did not know if they needed bridges or proxies, so they only tried to configure one when the direct connection failed.
-Since they did not know whether they needed a bridge or proxy, they often tried to configure proxies when they did not need one and should have configured bridges instead.
-
-\subsubsection{E3}
-In E3, a bridge was required to connect.
-Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google.
-Custom bridges can also work.
-Configuring a proxy was optional.
-Observations in E3:
-
-\begin{figure}[t]
-\centering
-\includegraphics[width=0.5\textwidth]{P8-proxy-attempt.png}
-\caption{
-Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
-}
-\label{fig:proxy-attempt}
-\end{figure}
-
-%P14 (regular): E3 FAIL
-\pquote{P11 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
-Then, they retried connecting directly and retried connecting using the recommended bridge.
-After that, the participant spent the rest of their time trying to configure a proxy and retrying connections with the recommended bridge.}
-
-%P15 (regular): E3 FAIL
-\pquote{P12 (new user, failed to connect)}{They tried connecting with the recommended bridge.
-They decided that they need a proxy along with the recommended bridge, and spent the rest of their time trying to configure a proxy.}
-
-%P16: E3 (regular) FAIL
-\pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
-They retried connecting with the recommended bridge.
-When that didn't work, they tried to configure a proxy.
-Then, they gave up on the task entirely.}
-
-%P6 (heard of Tor): E3 (26:48; 0:18 to 27:06) 
-\pquote{P14 (new user, meek-google, 26:48)}{They tried a direct connection by answering no to bridge and proxy questions.
-After waiting a while, they canceled the connection and tried connecting with the recommended bridge.
-They retried connecting with the recommended bridge two more times, then tried to connect with a flashproxy bridge, an obfs4 bridge, a scramblesuit bridge.
-After retrying the recommended bridge again, they made a connection using a meek-google bridge.}
-
-%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
-\pquote{P15 (new user, meek-azure, 7:31)}{They tried connecting directly, and then with the recommended bridge.
-After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect.
-They went back to the first screen~\ref{fig:old-first} and clicked connect, which made a connection using meek-azure bridge.
-The connect button makes a connection to Tor with the toggled settings in the interface.
-When the interface is initialized to not use a bridge or proxy, clicking connect on the first page starts a direct connection.
-But since the participant had chosen a meek-azure bridge, the connect button made a connection to a meek-azure bridge, even though the text in the first screen says that they will ``connect directly.'' Because of this, the participant thought they made a direct connection.
-Although they succeeded in connecting to Tor, they did not realize what they had done or why connecting to a meek-azure bridge worked.
-They chose that bridge at random.}
-
-%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
-\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge.
-After briefly looking at error messages the system log, they retried connecting directly two more times.
-After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked.
-But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect.
-They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}
-
-Participants in E3 also generally tried a direct connection to Tor.
-They did not know if they needed a bridge or proxy, and like the participants in E2, only configured them when the direct connection failed.
-But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work.
-Of the participants that failed, they all tried the recommended bridge but not any others.
-The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed.
-P14 brute forced options until something worked, P15 did not think that they used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
+
+To see a summary of what each of our 16 participants did, see Appendix~\ref{summaries}.
 
@@
 We show an attempt to fix these issues in Section~\ref{sec:design}.
+
+%\section{Alternative Approaches} 
+%\item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country.
+one way to do this is to show a list of countries with a corresponding recommended configuration.
+This requires developers to maintain a list of suggestions and that the users trust the suggestions.
+%\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection.
+If users are not sensitive, let them configure their own bridges and proxies.
+%\item{\bfseries Ask users if they know what to do.} If they know, offer the option to manually configure bridges and proxies.
+If they do not know, give suggestions on what to do next or automate the process for them somehow.
+This requires users to answer honestly to the question and to trust the suggestions given.
+%\item{\bfseries Automate naively.} Have the interface automatically try configurations that would most likely work, in order (i.e.
+a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
+This is what most users would ideally do anyway.
+However, this method leaks to network eavesdroppers that the user is using Tor without the user's awareness.
+%\item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies.
+If they fail, then a network eavesdropper already knows that the user is trying to connect to Tor.
+We believe there is negligible added risk to naively automate the connection.
+%\item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any.
+Then it automatically connects to some secret bridges that will always work, which assign the user an entry relay that works based on their location.
+This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.
+%\end{description}
+%We believe that these ideas can significantly help users connect to Tor.
 
@@
 \label{sec:recommendations}
-We believe that adopting our design will save users time.
-But since we did not test our design changes independently, we cannot (and do not) claim the effects each change.
-We do not recommend specific changes, but offer some suggestions based on what we learned: \\
+We offer some suggestions based on what we learned: \\
 
@@
 
-We also recommend exploring solutions that leverage automation, user-dependent inputs, or network-dependent inputs.
-We start this discussion by sharing some of our own ideas in appendix~\ref{alternatives}.
+While we believe that adopting our design faithfully will save users time.
+But since we did not test our design changes independently, we cannot (and do not) claim the effects each change.
+Alternative designs may be better solutions.
 
@@
 
+\section{Qualitative Testing Observations}
+\label{summary}
+We summarize of each participant's session.
+
+%E1: P2, P3, P4, P9, P10
+%E2: P7, P8, P11, P12, P13
+%E3: P1, P5, P6, P14, P15, P16
+
+% re-watched the videos and get the exact times. 
+%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos
+
+\subsubsection{E1} 
+In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
+Observations in E1:
+
+%P9 (regular): E1 (0:39; 4:49 to 5:28)
+\pquote{P1 (new user, direct, 0:39)}{They connected directly.}
+
+%P2(regular): E1 (1:20, 0:22 to 1:42) 
+\pquote{P2 (new user, direct, 1:20)}{They spent time reading the text on the start screen, and connected directly because they were intimidated by the other option.}
+
+%P3(regular): E1 (N/A; 5:47 to 6:26) 
+\pquote{P3 (new user, obfs3, 1:39)}{They connected with the recommended bridge. They were also going to use a proxy, but decided not to when they saw the proxy input fields.}
+
+%P4(regular): E1 (8:56, 7:22 to 16:18)
+\pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy.
+After not being able to fill out the proxy input fields, they started over and connected with an obfs4 bridge.
+Note that they did not try connecting with the obfs3 bridge, which would have worked.}
+
+%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
+\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}
+
+Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily configured bridges.
+
+\subsubsection{E2} 
+In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
+Observations in E2:
+
+%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
+\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly.
+After watching the progress bar not make any progress for a couple minutes, and gave up on the direct connection.
+Then they connected with the recommended bridge.}
+
+%P13 (regular): E2 (7:48; 0:34 to 9:22) 
+\pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly.
+They restarted Tor Launcher and tried to connect directly again---and repeated this two more times.
+On the fourth restart, they tried to configure a proxy, but gave up.
+On the fifth restart, they connected using the recommended bridge.}
+
+%P12 (regular): E2 (10:40; 0:46 to 11:26)
+\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly.
+After waiting a couple minutes, they figured that did not work and looked at proxy settings.
+But after looking at the settings and being intimidated, they tried connecting directly again.
+Then, they tried to configure a proxy, and gave up.
+They tried connecting directly again, which worked unexpectedly.
+They found a bug in our setup that we fixed for the later experiment.
+E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.
+}
+
+%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
+\pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly.
+And they tried connecting directly through a different user path by answering no to bridge and proxy questions in the interface, connecting from the proxy screen.
+Then, they connected using the recommended bridge.}
+
+%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
+\pquote{P10 (previous Tor user, failed to connect)}{They tried a direct connection.
+Then, they tried a connection with the recommended bridge, which should have worked.
+However, our setup experienced a clock drift.
+Tor does not allow connections with bad clocks.
+They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).
+This participant tried the most attempts to connect to Tor, using a variety of bridges and proxies.}
+
+Participants in E2 tried a direct connection to Tor before {\it eventually} connecting with the recommended bridge.
+They spent a fair amount of time waiting before determining that connections failed.
+Some stated that they connected directly because the interface says that it would work in ``most situations'' (Figure~\ref{fig:old-first}).
+Our participants did not know if they needed bridges or proxies, so they only tried to configure one when the direct connection failed.
+Since they did not know whether they needed a bridge or proxy, they often tried to configure proxies when they did not need one and should have configured bridges instead.
+
+\subsubsection{E3}
+In E3, a bridge was required to connect.
+Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google.
+Custom bridges can also work.
+Configuring a proxy was optional.
+Observations in E3:
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.5\textwidth]{P8-proxy-attempt.png}
+\caption{
+Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
+}
+\label{fig:proxy-attempt}
+\end{figure}
+
+%P14 (regular): E3 FAIL
+\pquote{P11 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
+Then, they retried connecting directly and retried connecting using the recommended bridge.
+After that, the participant spent the rest of their time trying to configure a proxy and retrying connections with the recommended bridge.}
+
+%P15 (regular): E3 FAIL
+\pquote{P12 (new user, failed to connect)}{They tried connecting with the recommended bridge.
+They decided that they need a proxy along with the recommended bridge, and spent the rest of their time trying to configure a proxy.}
+
+%P16: E3 (regular) FAIL
+\pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
+They retried connecting with the recommended bridge.
+When that didn't work, they tried to configure a proxy.
+Then, they gave up on the task entirely.}
+
+%P6 (heard of Tor): E3 (26:48; 0:18 to 27:06) 
+\pquote{P14 (new user, meek-google, 26:48)}{They tried a direct connection by answering no to bridge and proxy questions.
+After waiting a while, they canceled the connection and tried connecting with the recommended bridge.
+They retried connecting with the recommended bridge two more times, then tried to connect with a flashproxy bridge, an obfs4 bridge, a scramblesuit bridge.
+After retrying the recommended bridge again, they made a connection using a meek-google bridge.}
+
+%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
+\pquote{P15 (new user, meek-azure, 7:31)}{They tried connecting directly, and then with the recommended bridge.
+After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect.
+They went back to the first screen~\ref{fig:old-first} and clicked connect, which made a connection using meek-azure bridge.
+The connect button makes a connection to Tor with the toggled settings in the interface.
+When the interface is initialized to not use a bridge or proxy, clicking connect on the first page starts a direct connection.
+But since the participant had chosen a meek-azure bridge, the connect button made a connection to a meek-azure bridge, even though the text in the first screen says that they will ``connect directly.'' Because of this, the participant thought they made a direct connection.
+Although they succeeded in connecting to Tor, they did not realize what they had done or why connecting to a meek-azure bridge worked.
+They chose that bridge at random.}
+
+%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
+\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge.
+After briefly looking at error messages the system log, they retried connecting directly two more times.
+After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked.
+But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect.
+They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}
+
+Participants in E3 also generally tried a direct connection to Tor.
+They did not know if they needed a bridge or proxy, and like the participants in E2, only configured them when the direct connection failed.
+But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work.
+Of the participants that failed, they all tried the recommended bridge but not any others.
+The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed.
+P14 brute forced options until something worked, P15 did not think that they used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
+
 \section{Quantitative User Study Recruitment Posting}
@@
 
-\section{Alternative Approaches} 
-\label{alternatives}
-We list some of our ideas:\\
-\begin{description}
-\item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country.
-one way to do this is to show a list of countries with a corresponding recommended configuration.
-This requires developers to maintain a list of suggestions and that the users trust the suggestions.
-\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection.
-If users are not sensitive, let them configure their own bridges and proxies.
-\item{\bfseries Ask users if they know what to do.} If they know, offer the option to manually configure bridges and proxies.
-If they do not know, give suggestions on what to do next or automate the process for them somehow.
-This requires users to answer honestly to the question and to trust the suggestions given.
-\item{\bfseries Automate naively.} Have the interface automatically try configurations that would most likely work, in order (i.e.
-a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
-This is what most users would ideally do anyway.
-However, this method leaks to network eavesdroppers that the user is using Tor without the user's awareness.
-\item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies.
-If they fail, then a network eavesdropper already knows that the user is trying to connect to Tor.
-We believe there is negligible added risk to naively automate the connection.
-\item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any.
-Then it automatically connects to some secret bridges that will always work, which assign the user an entry relay that works based on their location.
-This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.
-\end{description}
-We believe that these ideas can significantly help users connect to Tor.
-
 \end{document}

### 2017-02-16 pets2017-paper/pets2017-paper.tex
change some section names
redo the design section

--- 2017-02-15 pets2017-paper/pets2017-paper.tex
@@
 
-\section{Background}
+\section{Technical Background}
 \label{sec:background}
@@
 
-\section{Qualitative User Testing}
+\section{Qualitative Testing}
 \label{sec:qualitative}
@@
 
-\section{A Design Iteration}
+\section{Design Changes}
 \label{sec:design}
-This section discusses how we converted our qualitative user testing observations into design changes.
-
-\subsection{Procedure} 
-We agreed on security and usability design principles, before reviewing our qualitative usability study observations and brainstorming changes to the interface.
-We worked with a user interface designer to iteratively design the interface.
-Figure~\ref{fig:new-interface} is the result.
+
+We limited ourselves to design changes that do not require infrastructural changes. Figure~\ref{fig:new-interface} shows the results.
 
@@
 
-\subsection{Design Principles} 
-The interface currently favors a guided manual configuration over an automated configuration with network probing.
-Our redesign preserves this approach and has no user-dependent inputs, no network-dependent inputs, and minimal information leaks.
-
-In order of priority, our design objectives were to minimize the user workload, to assist in user decision making, and to help users understand the system.
-We preferred to eliminate tasks if we could, help users through necessary tasks, and educate them only if this information would be useful for future decisions.
-These objectives were inspired by our previous usability study.
+\subsection {Design Considerations}
+
+Changes were inspired by user observations and constrained by the following design considerations:
+
+\begin{itemize}
+\item {\bfseries User consent}: Connecting to Tor requires consent since being revealed as using Tor can be dangerous.
+While we could help users by automating the configuration and connection process, taking on risk for the user without proper consent is not ethical.
+
+\item{\bfseries Active adversaries}: We could ask the user, "what country are you in?", "are you at risk?" or "do you know what you are doing?" to make decisions.
+While leveraging user input works well, third-party versions of Tor Browser will replicate the official version, but might steal the inputs to profile users.
+
+\item {\bfseries  Passive adversaries}: Assuming a sufficiently powerful network adversary (like governments), a failed, non-obfuscated attempt to connect to Tor will tell a passive eavesdropper that the user is connecting to Tor.
+We should allow users to leverage local information to reduce their risk.
+
+\item{\bfseries  Maintenance constraints}: Network environments change all the time--what bridge was reachable in a country an hour ago might not be tomorrow.
+Keeping up with how and when each country censors Tor would require a lot of time.
+Even if we keep up with how and when each country censors Tor, we would need to push changes before any of the affected users connect to Tor, which is an unreasonable turnaround time.
+
+\item{\bfseries  Financial constraints}: We could leverage harder-to-block meek relays connect people to Tor, then assign them something that would work afterward.
+But these relays cost thousands of dollars to run a month at their current capacity, and using them more would cost even more money.
+\end{itemize}
+
+It's possible that alternative changes could have been made, if we didn't treat these considerations as constraints.
+We start the discussion on methods that leverage user input and automation in Appendix~\ref{alternatives}.
 
 \subsection{Changes Made} 
-To require our users to do less work, we eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and simulated auto-detection for proxies by telling users that they did not need a proxy (this is feasible to implement with a local scan that does not leak information.
-
-To help users decide what to do, we labeled the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and gave additional advice on choosing transports if the recommended one did not work.
-
-To help users understand what is going on, we added a summary screen displays the current bridge and proxy settings for system visibility, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators of components topological order into the progress bar to that show if various components reached successfully.
-
-\section{Quantitative User Testing}
+To require less work, we eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and simulated auto-detection for proxies by telling users that they did not need a proxy (this is feasible to implement with a local scan that does not leak information).
+
+To help users decide what to do, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
+
+To help users understand, we added a summary screen displays the current bridge and proxy settings, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators into the progress bar to that show if various components were reached.
+
+\section{Quantitative Testing}
 \label{sec:quantitative}
@@
 
-\section{Quantitative User Study Recruitment Posting}
-\label{quantitative-recruitment}
-We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
-The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
-
-\indent Payment: \$30 Amazon gift card\\
-\indent Duration: 1 hour \\
-\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\
-
-\textit{<list of sessions>}\\
-
-To be eligible, you must be an adult (18 or older). This is to comply with university policies on research.
-
-If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
-with the sessions you are able to attend. We will confirm your participation and assign you a session. 
-2. Come to <redacted> %Xlab 
-at the appointed time for the experiment.
-
-\section{Quantitative User Study Introduction Script} 
-\label{quantitative-script} 
-Imagine you live in an oppressive country that censors part of the Internet.
-We have simulated this in the laboratory by blocking certain websites and services.
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
-
-To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
-Tor is already installed for you.
-On the desktop, you should see a globe icon that says ``Start Tor Browser.'' If you are able to reach the website, then you know that you have successfully circumvented censorship.
-Fill out the question on the worksheet.
-This isn't intended to be hard, just write what you see.
-We want to just check you saw the website.
-
-Afterward, we ask you to take a short survey to collect some information about you. The link is also on your worksheet.
-We will give you time to complete this task.
-If you finish early, we ask that you sit at your desk until the remainder of the hour.
-Since we are recording your screen, we ask that you don't do anything personal afterward, like checking your email.
-
-Before you start, do you have any questions about what you are asked to do?
-
-\section{Quantitative User Study Worksheet Text} 
-\label{summative-worksheet}
-Imagine you live in an oppressive country that censors part of the Internet. We have simulated this in the laboratory by blocking certain websites and services.
-
-The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-For instance, www.torproject.org is blocked.
-Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
-It will fail to load, when you can visit other sites.
-
-To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
-If you can visit wikipedia, then you know that you have successfully circumvented censorship.
-
-1. Visit Wikipedia’s main page (\url{https://en.wikipedia.org/wiki/Main\_Page}). What is the topic of today’s selected article?
-
-2. After you have completed the tasks, fill out this survey: http://bit.ly/tor-survey
-
-\section{Quantitative User Study Exit Survey} 
-\label{quantitative-exit-survey}
-We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.
-
-This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
-If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
-Committee for Protection of Human Subjects at 510-642-7461, or email 
-<redacted>. %subjects@berkeley.edu. 
-If you agree to participate, please click Next below.\\
-
-\begin{enumerate}
-\item{What is your participant ID? (This can be found on the sticker on the left hand corner of the desk you are currently sitting at.)}
-\item{What is your gender?}
-\item{What is your age?}
-\item{Please select your highest completed (or current) level of education}.
-\item{What is your current occupation?}  
-\end{enumerate}
-
-Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
+\section{Qualitative Testing Observations}
+\label{summary}
+We summarize of each participant's session.
+
+%E1: P2, P3, P4, P9, P10
+%E2: P7, P8, P11, P12, P13
+%E3: P1, P5, P6, P14, P15, P16
+
+% re-watched the videos and get the exact times. 
+%https://github.com/lindanlee/PETS2017-paper/tree/master/sessions/pre/videos
+
+\subsubsection{E1} 
+In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
+Observations in E1:
+
+%P9 (regular): E1 (0:39; 4:49 to 5:28)
+\pquote{P1 (new user, direct, 0:39)}{They connected directly.}
+
+%P2(regular): E1 (1:20, 0:22 to 1:42) 
+\pquote{P2 (new user, direct, 1:20)}{They spent time reading the text on the start screen, and connected directly because they were intimidated by the other option.}
+
+%P3(regular): E1 (N/A; 5:47 to 6:26) 
+\pquote{P3 (new user, obfs3, 1:39)}{They connected with the recommended bridge. They were also going to use a proxy, but decided not to when they saw the proxy input fields.}
+
+%P4(regular): E1 (8:56, 7:22 to 16:18)
+\pquote{P4 (new user, obfs4, 8:56)}{They chose the recommended bridge and then tried to configure a proxy.
+After not being able to fill out the proxy input fields, they started over and connected with an obfs4 bridge.
+Note that they did not try connecting with the obfs3 bridge, which would have worked.}
+
+%P10 (has used Tor before): E1 (1:02; 0:13 to 1:15)
+\pquote{P5 (previous Tor user, obfs3, 1:02)}{They connected with the recommended bridge.}
+
+Participants in E1 were able to connect to Tor, but most were unsure if their actions were correct. Three of the five participants unnecessarily configured bridges.
+
+\subsubsection{E2} 
+In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
+Observations in E2:
+
+%P7 (heard of Tor): E2 (4:04; 0:29 to 4:33) 
+\pquote{P6 (new user, obfs3, 4:04)}{They tried connecting directly.
+After watching the progress bar not make any progress for a couple minutes, and gave up on the direct connection.
+Then they connected with the recommended bridge.}
+
+%P13 (regular): E2 (7:48; 0:34 to 9:22) 
+\pquote{P7 (new user, obfs3, 9:22)}{They tried connecting directly.
+They restarted Tor Launcher and tried to connect directly again---and repeated this two more times.
+On the fourth restart, they tried to configure a proxy, but gave up.
+On the fifth restart, they connected using the recommended bridge.}
+
+%P12 (regular): E2 (10:40; 0:46 to 11:26)
+\pquote{P8 (new user, direct, 10:40)}{They tried connecting directly.
+After waiting a couple minutes, they figured that did not work and looked at proxy settings.
+But after looking at the settings and being intimidated, they tried connecting directly again.
+Then, they tried to configure a proxy, and gave up.
+They tried connecting directly again, which worked unexpectedly.
+They found a bug in our setup that we fixed for the later experiment.
+E2 required a bridge to connect, but new public relays came online after we ran our firewall rules and they were able to connect using those new relays.
+}
+
+%P11 (used Tor before): E2 (~3:00; 1:05 to 5:13)
+\pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly.
+And they tried connecting directly through a different user path by answering no to bridge and proxy questions in the interface, connecting from the proxy screen.
+Then, they connected using the recommended bridge.}
+
+%P8 (used Tor): E2 (clock drift mission impossible, 1:38 to 7:20) 
+\pquote{P10 (previous Tor user, failed to connect)}{They tried a direct connection.
+Then, they tried a connection with the recommended bridge, which should have worked.
+However, our setup experienced a clock drift.
+Tor does not allow connections with bad clocks.
+They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).
+This participant tried the most attempts to connect to Tor, using a variety of bridges and proxies.}
+
+Participants in E2 tried a direct connection to Tor before {\it eventually} connecting with the recommended bridge.
+They spent a fair amount of time waiting before determining that connections failed.
+Some stated that they connected directly because the interface says that it would work in ``most situations'' (Figure~\ref{fig:old-first}).
+Our participants did not know if they needed bridges or proxies, so they only tried to configure one when the direct connection failed.
+Since they did not know whether they needed a bridge or proxy, they often tried to configure proxies when they did not need one and should have configured bridges instead.
+
+\subsubsection{E3}
+In E3, a bridge was required to connect.
+Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google.
+Custom bridges can also work.
+Configuring a proxy was optional.
+Observations in E3:
+
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.5\textwidth]{P8-proxy-attempt.png}
+\caption{
+Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
+}
+\label{fig:proxy-attempt}
+\end{figure}
+
+%P14 (regular): E3 FAIL
+\pquote{P11 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
+Then, they retried connecting directly and retried connecting using the recommended bridge.
+After that, the participant spent the rest of their time trying to configure a proxy and retrying connections with the recommended bridge.}
+
+%P15 (regular): E3 FAIL
+\pquote{P12 (new user, failed to connect)}{They tried connecting with the recommended bridge.
+They decided that they need a proxy along with the recommended bridge, and spent the rest of their time trying to configure a proxy.}
+
+%P16: E3 (regular) FAIL
+\pquote{P13 (new user, failed to connect)}{They tried connecting directly, and then with the recommended bridge.
+They retried connecting with the recommended bridge.
+When that didn't work, they tried to configure a proxy.
+Then, they gave up on the task entirely.}
+
+%P6 (heard of Tor): E3 (26:48; 0:18 to 27:06) 
+\pquote{P14 (new user, meek-google, 26:48)}{They tried a direct connection by answering no to bridge and proxy questions.
+After waiting a while, they canceled the connection and tried connecting with the recommended bridge.
+They retried connecting with the recommended bridge two more times, then tried to connect with a flashproxy bridge, an obfs4 bridge, a scramblesuit bridge.
+After retrying the recommended bridge again, they made a connection using a meek-google bridge.}
+
+%P1 (heard of tor before): E3 (~7:31, 0:51 to 8:22) 
+\pquote{P15 (new user, meek-azure, 7:31)}{They tried connecting directly, and then with the recommended bridge.
+After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect.
+They went back to the first screen~\ref{fig:old-first} and clicked connect, which made a connection using meek-azure bridge.
+The connect button makes a connection to Tor with the toggled settings in the interface.
+When the interface is initialized to not use a bridge or proxy, clicking connect on the first page starts a direct connection.
+But since the participant had chosen a meek-azure bridge, the connect button made a connection to a meek-azure bridge, even though the text in the first screen says that they will ``connect directly.'' Because of this, the participant thought they made a direct connection.
+Although they succeeded in connecting to Tor, they did not realize what they had done or why connecting to a meek-azure bridge worked.
+They chose that bridge at random.}
+
+%P5 (has used tor before): E3 (22:06; 0:00 to 22:06)
+\pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge.
+After briefly looking at error messages the system log, they retried connecting directly two more times.
+After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked.
+But  due to a bug in the progress bar that prevents it from updating correctly on subsequent attempts, they gave up before it could connect.
+They made a connection with the custom bridge by following the instructions from the bridge help button (they created a throwaway email account, emailed the bridge responder with poor syntax and did not get a response, emailed the bridge responder again with correct syntax and got a response, and then typed in the bridge information into the custom bridge field).}
+
+Participants in E3 also generally tried a direct connection to Tor.
+They did not know if they needed a bridge or proxy, and like the participants in E2, only configured them when the direct connection failed.
+But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work.
+Of the participants that failed, they all tried the recommended bridge but not any others.
+The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed.
+P14 brute forced options until something worked, P15 did not think that they used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
 
@@
 \label{alternatives}
-We list some of our ideas:\\
-\begin{description}
+{\color {red}
+\begin{itemize} 
 \item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country.
@@
 This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.
-\end{description}
+\end{itemize}
 We believe that these ideas can significantly help users connect to Tor.
+}
+
+\section{Quantitative User Study Recruitment Posting}
+\label{quantitative-recruitment}
+We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
+The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
+
+\indent Payment: \$30 Amazon gift card\\
+\indent Duration: 1 hour \\
+\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\
+
+\textit{<list of sessions>}\\
+
+To be eligible, you must be an adult (18 or older). This is to comply with university policies on research.
+
+If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
+with the sessions you are able to attend. We will confirm your participation and assign you a session. 
+2. Come to <redacted> %Xlab 
+at the appointed time for the experiment.
+
+\section{Quantitative User Study Introduction Script} 
+\label{quantitative-script} 
+Imagine you live in an oppressive country that censors part of the Internet.
+We have simulated this in the laboratory by blocking certain websites and services.
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
+
+To circumvent censorship successfully, you will need to set up Tor browser correctly and use it to get to Wikipedia.
+Tor is already installed for you.
+On the desktop, you should see a globe icon that says ``Start Tor Browser.'' If you are able to reach the website, then you know that you have successfully circumvented censorship.
+Fill out the question on the worksheet.
+This isn't intended to be hard, just write what you see.
+We want to just check you saw the website.
+
+Afterward, we ask you to take a short survey to collect some information about you. The link is also on your worksheet.
+We will give you time to complete this task.
+If you finish early, we ask that you sit at your desk until the remainder of the hour.
+Since we are recording your screen, we ask that you don't do anything personal afterward, like checking your email.
+
+Before you start, do you have any questions about what you are asked to do?
+
+\section{Quantitative User Study Worksheet Text} 
+\label{summative-worksheet}
+Imagine you live in an oppressive country that censors part of the Internet. We have simulated this in the laboratory by blocking certain websites and services.
+
+The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
+For instance, www.torproject.org is blocked.
+Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
+It will fail to load, when you can visit other sites.
+
+To complete this worksheet, you will need to set up Tor browser (on your desktop) correctly and use it to get to blocked site.
+If you can visit wikipedia, then you know that you have successfully circumvented censorship.
+
+1. Visit Wikipedia’s main page (\url{https://en.wikipedia.org/wiki/Main\_Page}). What is the topic of today’s selected article?
+
+2. After you have completed the tasks, fill out this survey: http://bit.ly/tor-survey
+
+\section{Quantitative User Study Exit Survey} 
+\label{quantitative-exit-survey}
+We'd like to know more about you.  All of your answers will be stored separately from any identifying information in order to protect your confidentiality.
+
+This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
+If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
+Committee for Protection of Human Subjects at 510-642-7461, or email 
+<redacted>. %subjects@berkeley.edu. 
+If you agree to participate, please click Next below.\\
+
+\begin{enumerate}
+\item{What is your participant ID? (This can be found on the sticker on the left hand corner of the desk you are currently sitting at.)}
+\item{What is your gender?}
+\item{What is your age?}
+\item{Please select your highest completed (or current) level of education}.
+\item{What is your current occupation?}  
+\end{enumerate}
+
+Thank you for participating in our experiment. You are now done! Please sit at your desk for the remainder of the experiment. Our researchers will formally announce the end of the experiment.
 

### 2017-02-23 pets2017-paper/pets2017-paper.tex
Spell check.

@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, ip address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
+	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, IP address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
 	\label{fig:old-proxy-yes}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interruput this bar but an error replaces this window with an alert. }
+	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interrupt this bar but an error replaces this window with an alert. }
 	\label{fig:old-progress}
@@
 
-We then conducted qualitative and quantiative usability tests of the interface.
+We then conducted qualitative and quantitative usability tests of the interface.
 We believed that both were necessary for a complete evaluation.
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{We give a second bridge recommedation for the provided bridges. We hide the text field to input custom bridge information until they click the radio button to configure one.}
+	\caption{We give a second bridge recommendation for the provided bridges. We hide the text field to input custom bridge information until they click the radio button to configure one.}
 	\label{fig:new-bridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH). We did not make any changes to this page. This screen is idential to that in the old interface (Figure~\ref{fig:old-bridge-help}).}
+	\caption{The bridge help screen (BH). We did not make any changes to this page. This screen is identical to that in the old interface (Figure~\ref{fig:old-bridge-help}).}
 	\label{fig:new-bridge-help}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The summary screen (S). This screen shows users what they had configured in the interface. If they  configurued proxies or bridges, this summarizes their choices.}
+	\caption{The summary screen (S). This screen shows users what they had configured in the interface. If they  configured proxies or bridges, this summarizes their choices.}
 	\label{fig:new-summary}
@@
 Participants in a laboratory setting may alter their behavior due to their awareness of being observed~\cite{mccarney2007hawthorne}.
-Our participants were likely motivated differently compared to real users, but we believe that they were likely overmotivated because they were being observed and receiving a monetary reward.
+Our participants were likely motivated differently compared to real users, but we believe that they were likely over-motivated because they were being observed and receiving a monetary reward.
 If true, this makes our results a conservative estimate of the usability problems.
@@
 Our work contributes to the body of usable security by evaluating Tor Browser, which is an anonymity and censorship circumvention software that requires user interaction.
-Other usable security research explores on a variety of security software or features, such as email encryption sofware ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
+Other usable security research explores on a variety of security software or features, such as email encryption software ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
 
@@
 a user-centered perspective and principles for secure interaction design~\cite{yee2002user},  
-Molich et~al.'s examination of  common problems in human-computer dialogue design~\cite{molich1990improving}, and Egelman et~al's examination of user tolerance of security delays~\cite{egelmanplease}.
+Molich et~al.'s examination of  common problems in human-computer dialogue design~\cite{molich1990improving}, and Egelman et~al.'s examination of user tolerance of security delays~\cite{egelmanplease}.
 
@@
 Tor Browser the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser tp observe their behavior.
+Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser to observe their behavior.
 This uncovered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.
@@
 We qualified where the interface is not usable with user observations and quantified how unusable the interface is with user interaction logs.
-We believe that our recommended hanges will will help users connect to Tor in censored environments, but encourage discussion about alternative ways to configure a connection that would be easier for users.
+We believe that our recommended changes will will help users connect to Tor in censored environments, but encourage discussion about alternative ways to configure a connection that would be easier for users.
 
@@
 
-\noindent <redacted url>
+\noindent <redacted URL>
 %\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
@@
 \item e6: proxy type is not selected
-\item e7: proxy: ip address left blank
+\item e7: proxy: IP address left blank
 \item e8: proxy: syntax error

### 2017-02-23 pets2017-paper/pets2017-paper.tex
Grammar fixes noticed by pets 2017.3 reviewers.

@@
 We perform the first usability test on Tor Launcher, a graphical user interface (GUI) that all Tor Browser users must use to configure their initial connection to the Tor network.
-Users who do not require a proxy or a non-default bridge can usually connect to connect to the Tor network with the Tor Launcher GUI.
+Users who do not require a proxy or a non-default bridge can usually connect to the Tor network with the Tor Launcher GUI.
 However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need.
 User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored.
-We conclude with recommendations based on what we learned and by start a discussion on alternative
+We conclude with recommendations based on what we learned and start a discussion on alternative
 approaches to bootstrap a connection to Tor. 
@@
 Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  
-Guard relays that serve as an entry node into the Tor network and receive packets from the user.
+Guard relays serve as an entry node into the Tor network and receive packets from the user.
 Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network.
@@
 which encrypt or alter the Tor protocol to appear as random noise.
-Other transports route traffic through other services and do not need secret IP address. 
+Other transports route traffic through other services and do not need a secret IP address. 
 ``flashproxy''~\cite{flashproxy} connects through third party web browsers,
@@
 officially configures Tor Browser to use bridges.
-Users can do this more easily by choosing a 
+Users can do this more easily by choosing
 a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
@@
 We conducted our studies at <redacted>, which only had Windows machines. 
-So we used Windows Firewall rules to block IP addresses of public Tor relays (E2, E3) and default bridges (E3). 
+So we used Windows Firewall rules to block the IP addresses of public Tor relays (E2, E3) and default bridges (E3),
 and the Windows operating system hosts file to block websites by
@@
 And the interface did not discourage users from configuring components that are not necessary to connect to Tor.
-The proxy configuration has the potential for a lot of error, as there are a many free-form input fields.
+The proxy configuration has the potential for a lot of error, as there are many free-form input fields.
 
 More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies.
-We doubted that users would have an understanding of how the Internet well enough to even explain how Tor relays, bridges, and proxies worked.
+We doubted that users would understand the Internet well enough to even explain how Tor relays, bridges, and proxies worked.
 Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing.
@@
 We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
-We ensured that each condition had a participant who had used Tor Browse before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.
+We ensured that each condition had a participant who had used Tor Browser before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.
 
@@
 The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in a another browser of their choice, and VLC to record the screen during the experiment.
+On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment.
 Before each participant entered the room, we ran a script on the computer that
@@
 
-We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task.
-We explicitly stated that the they should use Tor to circumvent censorship.
+We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task. We explicitly stated that they should use Tor to circumvent censorship. 
 We instructed them to visit sample censored and uncensored websites
@@
 required answers from Wikipedia (censored) and CNN (uncensored).
-We chose these websites because their likely familiarity~\ref{alexa}
+We chose these websites because their likely familiarity~\cite{alexa}
 would make the task seem less intimidating. They were given 45 minutes to complete the task. 
@@
 
-The interface uses a technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
+The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
 Participants found the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) and did not know what to do to configure bridges and proxies (Figures~\ref{fig:old-bridge-combobox} and~\ref{fig:old-proxy-yes}).
@@
 The progress bar had dependencies that made it update oddly.
-If progress bar reached a 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%.
+If progress bar reached 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%.
 This made many assume that their subsequent attempts were wrong.
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge screen (B). We give users the options to connect  without a bridge (the default choice) alongside the other options. We tell users to when to choose a bridge. }
+	\caption{The bridge screen (B). We give users the options to connect  without a bridge (the default choice) alongside the other options. We tell users when to choose a bridge. }
 	\label{fig:new-nobridge}
@@
 
-To help users decide what to do, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
-
-To help users understand, we added a summary screen displays the current bridge and proxy settings, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators into the progress bar to that show if various components were reached.
+To help users decide what to do, we label the configure button as an option for heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
+
+To help users understand, we added a summary screen displaying the current bridge and proxy settings, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators into the progress bar that show if various components were reached.
 
@@
 The testing room had 36 workstations with identical Windows~7 laptops.
-Side panels at each workstation to discouraged participants from looking at other screens.
+Side panels at each workstation discouraged participants from looking at other screens.
 %Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
@@
 \subsection{Procedure}
-We assigned participants  to a simulated censorship environment combination at random by being assigning them to a computer at random.
+We assigned participants  to a simulated censorship environment combination at random by assigning them to a computer at random.
 We told the participants the purpose of the study, what data was collected, and any associated risks.
@@
 Non-finishing participants' active time was computed by
-subtracting the amount of time spent on the progress screen from the 
+subtracting the amount of time spent on the progress screen from
 their assigned completion time of 40:08.
@@
 %things to keep in mind
-We believe that configuration time is a meaningful metric because 1) bootstrapping can dominate measurements for users do not need much time to configure their connection (E1 participants), and 2) many errors do not interrupt the connection attempt and cause many users to wait a long time before they manually cancel the connection to try again.
-This is metric is not perfect though, since it does not reflect how some participants actively searched for help in another browser rather than passively waiting for their connections to work.
+We believe that configuration time is a meaningful metric because 1) bootstrapping can dominate measurements for users who do not need much time to configure their connection (E1 participants), and 2) many errors do not interrupt the connection attempt and cause many users to wait a long time before they manually cancel the connection to try again.
+This metric is not perfect though, since it does not reflect how some participants actively searched for help in another browser rather than passively waiting for their connections to work.
 
@@
 \subsection{Usability of Tor Launcher} 
-We confirmed our observations from our qualitative user test and find that participants wait the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.
+We confirmed our observations from our qualitative user test and find that participants wait on the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.
 
 From our measurements, we find that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-Users average over 3 minutes if they needed a bridge and averaging over 20 minutes if they needed a meek or custom bridge.
+Users average over 3 minutes if they needed a bridge and are averaging over 20 minutes if they needed a meek or custom bridge.
 
 Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes.
-Neither the Tor Browser's 5.0.3 Tor Launcher GUI or our redesigned Tor Launcher GUI meets this goal.
+Neither the Tor Browser's 5.0.3 Tor Launcher GUI nor our redesigned Tor Launcher GUI meets this goal.
 
@@
 While we believe that adopting our design faithfully will save users time.
-But since we did not test our design changes independently, we cannot (and do not) claim the effects each change.
+But since we did not test our design changes independently, we cannot (and do not) claim specific effects for each change.
 Alternative designs may be better solutions.
@@
 Our work contributes to the body of usable security by evaluating Tor Browser, which is an anonymity and censorship circumvention software that requires user interaction.
-Other usable security research explores on a variety of security software or features, such as email encryption software ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
+Other usable security research explores a variety of security software or features, such as email encryption software ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
 
@@
 
-We used usability lab studies (one-on-one experiments with a given a set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}.
+We used usability lab studies (one-on-one experiments with a given set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}.
 There are other ways to collect behavioral data as well, such as eye tracking, clickstream analysis and AB testing.
@@
 Previous usability studies on Tor have focused on installation and use.
-Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable complete installation or browsing tasks.
+Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable to complete installation or browsing tasks.
 Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonymity~\cite{dingledine2009performance} but reduces usability.
@@
 We do not know of any published usability evaluations of
-Tor Browser the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
+Tor Browser since the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
 Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser to observe their behavior.
@@
 \label{sec:conclusion}
-We believe that an interface is usable if a new user can to identify what to do, knows if and when they do the right thing in the process, and can accomplish the required tasks.
+We believe that an interface is usable if a new user can identify what to do, knows if and when they do the right thing in the process, and can accomplish the required tasks.
 Tor Browser 5.0.3's configuration interface does not meet these requirements.
@@
 \pquote{P16 (previous Tor user, custom bridge, 22:06)}{They tried and retried connecting directly, then they tried connecting with the recommended bridge.
-After briefly looking at error messages the system log, they retried connecting directly two more times.
+After briefly looking at error messages in the system log, they retried connecting directly two more times.
 After trying to configure a proxy for a while, they instead decided not to use one and tried connecting with a meek-google bridge, which would have worked.

### 2017-02-28 pets2017-paper/pets2017-paper.tex
change word

--- 2017-02-16 pets2017-paper/pets2017-paper.tex
@@
 
-To help users decide what to do, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
+To guide users, we label the configure button as an option heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
 

### 2017-02-28 pets2017-paper/pets2017-paper.tex

--- 2017-02-23 pets2017-paper/pets2017-paper.tex
@@
 
-To help users decide what to do, we label the configure button as an option for heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation.
+To help users decide what to do, we label the configure button as an option for heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex
revision for shepherd

@@
 \begin{document}
-   \author*[1]{Author 1}
-
-  \author[2]{Author 2}
-
-  \author[3]{Author 3}
-
-  \author[4]{Author 4}
-
-  \author[5]{Author 5}
-
-  \author[6]{Author 6}
-
-  \affil[1]{Affiliation of Author 1, E-mail: \mbox{author1@affiliation.edu}}
-  \affil[2]{Affiliation of Author 2, E-mail: \mbox{author2@affiliation.edu}}
-  \affil[3]{Affiliation of Author 3, E-mail: \mbox{author3@affiliation.edu}}
-  \affil[4]{Affiliation of Author 4, E-mail: \mbox{author4@affiliation.edu}}
-  \affil[5]{Affiliation of Author 5, E-mail: \mbox{author5@affiliation.edu}}
-  \affil[6]{Affiliation of Author 6, E-mail: \mbox{author6@affiliation.edu}}
-%  \author*[1]{Linda Lee}
-%
-%  \author[2]{David Fifield}
-%
-%  \author[3]{Nathan Malkin}
-%
-%  \author[4]{Ganesh Iyer}
-%
-%  \author[5]{Serge Egelman}
-%  
-%  \author[6]{David Wagner}
-%
-%  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
-%
-%  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
-%
-%  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
-%
-%  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
-%  
-%  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
-%   
-%  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
+  \author*[1]{Linda Lee}
+
+  \author[2]{David Fifield}
+
+  \author[3]{Nathan Malkin}
+
+  \author[4]{Ganesh Iyer}
+
+  \author[5]{Serge Egelman}
+
+  \author[6]{David Wagner}
+
+  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
+
+  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
+
+  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
+
+  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
+
+  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
+
+  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
 
@@
 {
-We perform the first usability test on Tor Launcher, a graphical user interface (GUI) that all Tor Browser users must use to configure their initial connection to the Tor network.
-Users who do not require a proxy or a non-default bridge can usually connect to the Tor network with the Tor Launcher GUI.
-However, user observations revealed that participants were intimidated by the tasks, unsure of what to do, and likely to get stuck configuring network components that they did not need.
-User testing showed that most users take more than 10 minutes to connect to Tor if the public relays are censored and half of the users cannot connect to Tor if the interface's hardcoded bridges are censored.
-We conclude with recommendations based on what we learned and start a discussion on alternative
-approaches to bootstrap a connection to Tor. 
+Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot make the correct decisions during the configuration process.
+We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure their connections to Tor.
+Our study shows that 79\% (363 of 458) of user attempts to connect to Tor failed, and found that users were often frustrated during the process and try options at random.
+In this paper, we describe how we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
+Tor Browser ~4.5 incorporated  changes based on our work.
 }
@@
 \section{Introduction}
-
 Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
 that make it difficult to observe the source and destination.
-Tor Browser~\cite{torbrowser} is a modified Firefox browser with a built-in Tor client that
-is the recommended way to use Tor. Tor Launcher is a Tor Browser component that
-starts, stops, and otherwise controls the underlying Tor processes.
-Tor Launcher's graphical user interface (Figure~\ref{fig:old-interface}) asks the user to configure
-bridges, pluggable transports, and proxies to make a connection to Tor (we refer to this graphical user interface as the ``configuration interface'' throughout this paper).
+Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor.
+Tor Launcher is a Tor Browser graphical user interface (Figure~\ref{fig:old-interface}) that asks the user to configure their connection to Tor.
 This is the object of our study.
@@
 Although Tor Browser was originally designed for Internet anonymity, many now use Tor Browser to circumvent Internet censorship.
-In fact, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
-The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor, but all Tor Browser users must interact with it regardless of why they use Tor Browser.
-
-Tor minimizes collecting user data.
-Therefore, Tor does not have data on how users interact with the configuration interface.
-While we agree that this is respectful to the users, we also believe that this data will be helpful to improve the usability of the configuration interface.
-Improving the usability of the configuration interface has the obvious benefit of helping more users connect to Tor.
-But this is also benefits the Tor Project (less help desk tickets) and other Tor users (an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
+Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
+The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor.
+Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this is also benefits other Tor users by increasing in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
 
@@
 running observing participants interact with it (section~\ref{sec:qualitative}). 
-We opportunistically used the insights from our observations to make some changes (section~\ref{sec:design}).
-Then we quantified how usable the interface was, and 
-how much our changes helped save users time (section~\ref{sec:quantitative}).
-Afterward, we gave some recommendations (section~\ref{sec:recommendations}), addressed
-limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}). \\
-
-\noindent This paper contributes:
-\smallskip
-\begin{itemize}
-\item an inspection of the Tor Launcher 5.0.3 interface
-\item what users found challenging about the interface
-\item measurements of how many users could connect
-\item measurements of how long users took to connect
-\item patterns seen in the users that failed to connect
-\item recommendations to improve the interface
-\end{itemize}
-
-We hope that our work contributes to Tor Browser and is an informative case study of users interacting with anonymity and censorship circumvention tools.
+We used the insights from our observations to make some changes to the interface (section~\ref{sec:design}) and
+quantified how usable the interface was before and after changes (section~\ref{sec:quantitative}).
+Afterward, we gave recommendations based on what we learned (section~\ref{sec:recommendations}), addressed
+limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}).
+We hope that our usability evaluation serves as an informative case study and provides guidance on improving Tor launcher.
 
@@
 \label{sec:background}
-This section discusses network components, when to configure them, and how they connect to Tor.
+This section discusses how to connect to Tor and what network components are involved.
 
@@
 
-In this paper, the word ``proxy'' refers to a local, ordinary unobfuscated proxy such as a SOCKS or HTTP proxy.
-This is to maintain consistency with the wording in the configuration interface.
-Fig.~\ref{fig:topology} illustrates the interacting components.
-A proxy is technically an intermediary between clients and servers, so a single Tor relay, a bridge, the circuit of entry, middle, and guard relays, and local proxies can all can be considered a proxy.
-A user uses a proxy to bypass local firewalls.
-
-Tor relays are the routers in the Tor network. The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.  
-Guard relays serve as an entry node into the Tor network and receive packets from the user.
-Middle relays forward traffic from an entry relay to an exit relay, and provide an extra layer of encryption in the Tor network.
-Exit relays receive traffic from a middle relay, and direct the traffic to its intended destination.
-A user uses Tor Browser to connect to the Tor network, which indirectly connects to websites.
-
-Bridges are unlisted Tor relays that serve as an alternative entry node.
-Bridges can be unlisted relays that behave similarly to a regular Tor relay,  
-but most run a pluggable transport (referred to as ``transport'' for shorthand) that obfuscates traffic. 
-Pre-configured bridges can be selected by ``Transport type,'' which refer to various
-censorship circumvention technologies (``pluggable transports'').
-Most transports rely on the secrecy of their static IP addresses for their effectiveness.
-These include ``fte'' and ``fte-ipv6''~\cite{fte},
-which disguise the Tor protocol as another protocol (such as HTTP), and
-``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit},
-which encrypt or alter the Tor protocol to appear as random noise.
-Other transports route traffic through other services and do not need a secret IP address. 
-``flashproxy''~\cite{flashproxy} connects through third party web browsers,
-and the ``meek''~\cite{fifield2015blocking} options route traffic
-through content delivery networks.
+Technically, proxies are any computer or service that allow its users to make indirect network connections to other services.
+In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy.
+However, in this paper and verbally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
+Fig.~\ref{fig:topology} illustrates the network components involved.
+
+Tor relays are the routers in the Tor network.
+The Tor network is a group of routers that perform onion routing, a technique for anonymous communication over a computer network.
+Guard relays receive packets from the user and forward traffic to middle relays.
+Middle relays forward traffic from an entry relay to an exit relay.
+Exit relays receive traffic from a middle relay and direct the traffic to its intended destination.
+A user uses Tor Browser to connect to the Tor network, which connects to websites on behalf of the user.
+
+Bridges are unlisted alternative entry nodes used to connect to Tor when Tor relays are censored.
+Bridges also recieve packets from the user and forward traffic to middle relays, but also run a pluggable transport (referred to as ``transport'' for shorthand).
+Bridges are grouped by which transport they run for convenience.
+
+Most bridges can be blocked by blocking their static IP addresses.
+These include bridges that run``fte'' and ``fte-ipv6''~\cite{fte} transports, which disguise the Tor protocol as another protocol (such as HTTP), and ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
+Other bridges are less blockable because of how they work.
+Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks.
+What bridges are accesssible in each country varies.
 Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.
-A user uses a bridge to connect to the Tor network while Tor relays or the Tor network protocol is being censored.
-
-\subsection{State and Corporate Censorship}
-A local proxy is required to connect in certain managed networks (i.e.
-universities and corporations).
-This usually means that users cannot connect to the Internet at all without a proxy, including connecting to the Internet through Tor.
-The user must first successfully connect to the Internet through their proxy before trying to connect to a Tor relay or bridge.
-
-State level censors block access to the Tor network by blocking publicly listed Tor relays.
-Some also employ more sophisticated techniques such as deep packet inspection and protocol detection.
-This means that users can connect directly to (uncensored) websites, but Tor is blocked.
-The thoroughness of censorship is what requires different bridges and transports.
 
@@
 \subsection{Connecting to Tor} 
-A ``bridge line,'' a specifically formatted bridge specification that
-includes its IP address, transport type, and other metadata 
-officially configures Tor Browser to use bridges.
-Users can do this more easily by choosing
-a hard-coded option in the interface (see Figure~\ref{fig:old-bridge-combobox}) 
-that select a group of bridges that use a particular transport.
-For instance, choosing the hard-coded obfs3 option
-configures a handful of bridges that use the obfs3 transport.
-If the built-in bridges do not work, users can obtain bridge lines
-through out-of-band channels~\cite{bridgedb}.
-
-Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional fields.
-The user must locate and input this information.
-If the computer is already configured to use a proxy, the information can be found in other browsers.
-The interface tells users to ``check Internet settings in another browser'' if they are unsure of the proxy information.
-
 There are many valid configuration settings to connect to the Tor network.
@@
 
+Users can configure a bridge by choosing a transport (Figure~\ref{fig:old-bridge-combobox}), which selects the group of bridges that use that transport.
+If the built-in bridges do not work, users can obtain bridge lines through out-of-band channels~\cite{bridgedb} that provides the necessary bridge specifications.
+Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}).
+The user must locate this information.
+
 \begin{figure*}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen (F).
-``Connect'' connects directly to a public Tor relay unless bridges or proxies are configured.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}).
-}
+	\caption{The first screen (F). ``Connect'' starts a connection.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
 	\label{fig:old-first}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first bridge screen (B1).
-Answering yes directs users to a screen to configure bridges (Figure~\ref{fig:old-bridge-settings}).
-Answering no directs users to the proxy question screen (Figure~\ref{fig:old-proxy}).}
+	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips it.}
 	\label{fig:old-bridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The second bridge screen (B2).
-Users select a provided bridge or a custom one (bridges not hard coded into the interface).
-``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}).
-}
+	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}). }
 	\label{fig:old-bridge-settings}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The hardcoded bridges are listed alphabetically by the transport that they support. Each transport works differently, but their functions are not explained in the interface.}
+	\caption{Some hardcoded bridges are listed alphabetically by their transport. The recommended one is obfs3.}
 	\label{fig:old-bridge-combobox}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH) gives instructions for a custom bridge three different ways. ``Done'' redirects users back to the second bridge screen (Figure~\ref{fig:old-bridge-settings}).}
+	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
 	\label{fig:old-bridge-help}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first proxy screen (P1). Answering yes to this question directs to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). Answering no starts a connection to Tor.}
+	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
 	\label{fig:old-proxy}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy settings screen (P2). Users configure a proxy by filling in the proxy's protocol, IP address, and port. ``Connect'' starts a connection to Tor with the interface settings.}
+	\caption{The proxy settings screen (P2). ``Connect'' starts a connection to Tor with the interface settings.}
 	\label{fig:old-proxy-yes}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. Warnings do not interrupt this bar but an error replaces this window with an alert. }
+	\caption{The progress bar (Pr). The bar fills up as log messages update the connection status. }
 	\label{fig:old-progress}
@@
 \section{Methodology} 
-This section discusses how we performed our summative evaluation to determine the interface's effectiveness.
+This section discusses the process we used to determine the usability of Tor launcher interface.
 
 \subsection{Testing Pipeline} 
-We performed a cognitive walkthrough~\cite{cognitive-walkthrough} of the interface by working tasks from the perspective of the user and assessing its learnability for new or infrequent users.
-
-We then conducted qualitative and quantitative usability tests of the interface.
-We believed that both were necessary for a complete evaluation.
+We inspected the interface to anticipate potential problems and formally assess its pros and cons.
+We then conducted qualitative and quantitative usability tests.
+We believed both were necessary for a complete evaluation.
 Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable.
@@
 We also opportunistically used our quantitative testing setup to measure its usability with respect to the original interface.
-We found the process of identifying design principles, drafting design changes, and testing an alternative interface to be insightful and hope that this may be insightful to others as well.
+We discuss how our changes saved users time and recommend some changes.
 
@@
 \label{sec:eval}
-Usability measures users' abilities to complete tasks. We use the following industry-standard~\cite{albert2013measuring} metrics: \\
+We use the following industry-standard~\cite{albert2013measuring} metrics to determine if the launcher is usable: \\
 
 \begin{itemize}
-\item {\bfseries Completion rate:}  percentage of users that connect to Tor in an experimental condition. 
-\item {\bfseries Connection time:} time from Tor Browser startup to a successful connection to Tor. 
-\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, not counting time spent passively waiting.
+\item {\bfseries Completion rate:}  percentage of users that connect to Tor. A high completion rate is ideal. 
+\item {\bfseries Connection time:} time until a successful connection to Tor. This should be a couple minutes. 
+\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, which excludes time waiting for connections to establish or timeout.
+This should be as short as possible.
 \end{itemize}
@@
 We defined success as a binary metric that is true if a user connected to Tor and false if a user did not.
-
 Task time is a supplemental usability metric that measures user productivity during the task.
 We measured this in two ways.
-Connection time measures how long users took to connect to Tor, which includes time spent waiting for Tor to configure relays for the user.
-This can take up to a couple minutes and dominate the measurement.
-Configuration time measures the time users spent configuring bridges and proxies.
+Connection time measures how long users took to connect to Tor, which includes the time Tor takes to establish a series of relays.
+Since that time can dominate the measurement, we use configuration time to measure the time users spent configuring bridges and proxies.
 
@@
 \label{sec:environments}
-We use versions of Tor Browser~5.0.3, 
-the most recent stable release at the time~\cite{torbrowser-503}.
-There were new releases during the experiments, but
-we used the same version throughout to not introduce
-confounding factors.
-
-We simulated three environments of increasing severity in censorship (E1, E2, E3).
-Table~\ref{tab:environments} summarizes them and explains what is required to connect to Tor. We chose to 
-simulate environments for the stability and reproducibility of the 
-experiment, as real censored networks are volatile and complex.
+We simulated three environments of various censorship severity (Table~\ref{tab:environments}). We chose to 
+simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
 
@@
 
-The simulated environments are not intended to imitate any particular country's censorship environment. Rather, they were designed to require particular network configurations
-to connect to Tor. We believe this to be sufficient for the purpose of testing the configuration interface, since these environments require the user to take the interface paths we wanted to test.
-
-We conducted our studies at <redacted>, which only had Windows machines. 
-So we used Windows Firewall rules to block the IP addresses of public Tor relays (E2, E3) and default bridges (E3),
-and the Windows operating system hosts file to block websites by
-mapping domain names to localhost (127.0.0.1) (E1, E2, E3).
-For all experiments, we blocked torproject.org and its subdomains to discourage downloading Tor Browser (as we had installed a specific version on the test computers) and wikipedia.org, cnn.com, and their subdomains (these were our simulated ``censored'' websites).
+The simulated environments are not intended to imitate any particular country's network.
+Rather, they were designed to require different bridges to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the interface paths we wanted to test.
+
+We used Tor Browser~5.0.3, the most recent stable release at the time~\cite{torbrowser-503}.
+There were new releases during the experiments, but we used the same version throughout to not introduce confounding factors.
+
+We conducted our experiments on Windows machines.
+To create the environments, we used Windows Firewall rules to block the IP addresses of public Tor relays and default bridges, and the Windows hosts file to block websites by mapping domain names to localhost.
 
@@
 \label{sec:inspection}
-This section discusses our inspection of the configuration interface and the resulting observations.
+We inspected of the interface to anticipate potential problems before testing it on users.
 
 \subsection{Procedure} 
-Two researchers performed the cognitive walkthrough on the Tor Browser 5.0.3 Tor Launcher GUI, the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
-We systematically tried actions from the perspective of a typical user, which we defined as a first time or infrequent user with almost no previous knowledge about network components involved in connecting to Tor.
-
+Two researchers performed the cognitive walkthrough~\cite{cognitive-walkthrough} on the Tor Browser 5.0.3 Tor Launcher GUI, which was the most recent version deployed at the time (Figure~\ref{fig:old-interface}).
 We first examined each screen in the interface for tasks required, inputs taken, and consequences of possible actions.
 This was done to map all potential paths through the interface (Figure~\ref{fig:digraph}).
-We then stepped through each user path and recorded our observations.
+We then stepped through each user path, systematically tried all possible actions, and recorded our observations.
 
 \subsection{Observations}
-The interface did not suppose that a user has previous exposure to Tor.
-To help new users, it provided recommendations in the text and populated some options (such as bridges) with recommended options.
-However, the interface did require the user to figure out if Tor relays are blocked or if a proxy is required.
-And the interface did not discourage users from configuring components that are not necessary to connect to Tor.
-The proxy configuration has the potential for a lot of error, as there are many free-form input fields.
-
-More generally, we suspected that new users or infrequent users would struggle to configure bridges and proxies.
-We doubted that users would understand the Internet well enough to even explain how Tor relays, bridges, and proxies worked.
-Additionally, as mentioned previously, Tor relays, bridges, and proxies all allow indirect connections, and the difference in terminology can be confusing.
-The terminology of bridges and transports are also specific to Tor, and not other censorship circumvention software.
-
-We used the map of potential user paths (Figure~\ref{fig:digraph}) to design our simulated environments (section~\ref{sec:environments}).
-We used our walkthrough observations as inspiration for drafting our post-experiment interview questions (Appendix~\ref{interview-questions}) for qualitative usability testing.
+We noticed that the interface leaves a lot of freedom for error but does not give good instructions on when there is an error and how to fix it: \\
+
+\begin{itemize}
+\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
+\item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them.
+There are nine choices for bridges by transport and more options to input a custom bridge.
+Almost any HTTP or SOCKS proxy can be used as the proxy.
+Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface.
+Proxy fields also do not provide syntactic guidlines.
+See the whole list of possible errors in Appendix~\ref{states}.
+\item {\bfseries Poor feedback:} Even if there was a syntactic error in your bridge or proxy fields, it does not notifiy until a connection is made and fails.
+If a censored bridge was chosen, the connection timeout takes a over a couple minutes.
+Errors messages were often technical and did not give suggestions.
+\end{itemize}
+
+These are some of the factors that contributed to why users struggled with the interface and therefore were unable to connect to Tor quickly.
 
@@
 \label{sec:qualitative}
-This section discusses our small-scale, qualitative usability experiment and resulting user insights.
+We observed user behaviors to see why Tor is hard to use and interviewed users afterward to see how they felt.
 
 \subsection{Recruitment}
-We recruited people from Craigslist using the recruitment text in Appendix~\ref{qualitative-recruitment}, which linked a prescreening survey that collected demographics (Appendix~\ref{qualitative-prescreening}).
-We pre-screened~\cite{screening} so that we could have a diversity of gender, age, technical expertise, use of security tools, and familiarity with Tor in a small participant pool.
+We recruited people from Craigslist using an ad (Appendix~\ref{qualitative-recruitment}) and prescreening survey (Appendix~\ref{qualitative-prescreening}).
+We pre-screened~\cite{screening} so that we could have a diversity of gender, age, and familiarity with Tor in a small participant pool.
 Of our 16 recruited participants, 50\% identified as male and 50\% identified as female.
@@
 One participant declined to report their age, so age calculations omit this participant's information.
-All of our users were highly educated, having at least some college education.
-We verified their self-reported familiarity with Tor Browser in-person to identify new users, and found that 12 were new users and 4 had previously used Tor Browser in some capacity.
+All of our users had at least some college education.
+12 were new users and 4 had previously used Tor Browser in some capacity.
 
@@
 
-We distributed participants evenly in number across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
-We ensured that each condition had a participant who had used Tor Browser before, and tried for some variation in gender, age, ``technical expertise,'' and ``use of security tools'' in each experimental condition as well.
-
-\subsection{Setup} 
-We ran the experiment in a meeting room in <redacted building> at <redacted university>.
+We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
+We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.
+
+\subsection{Procedure} 
+We ran the experiment in a meeting room at UC Berkeley.
 The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we manually downloaded and installed the necessary software for the experiment: Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment.
-Before each participant entered the room, we ran a script on the computer that
-set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
-
-\subsection{Procedure}
-Three researchers ran the qualitative user tests. Each session had at least two researchers.  
-We told the participant the purpose of the 
-study, what data was collected, and any associated risks. 
-Then they signed a consent form with this information in writing. 
-Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.
-
-We started by informing the participant of the simulated censorship environment (Appendix~\ref{qualitative-script}) and task. We explicitly stated that they should use Tor to circumvent censorship. 
-We instructed them to visit sample censored and uncensored websites
-in a non-Tor browser to clarify that the Internet was functioning and
-pointed out the Tor Browser shortcut on their desktop.
-
-They were asked to complete a worksheet (Appendix~\ref{participant-worksheet}) that 
-required answers from Wikipedia (censored) and CNN (uncensored).
-We chose these websites because their likely familiarity~\cite{alexa}
-would make the task seem less intimidating. They were given 45 minutes to complete the task. 
-After instructions, researchers left to minimize interactions and watched a live feed of the participants' screen from another room.
-
-After they completed the worksheet (or ran out of time),
-we asked them general questions about their experience (Appendix~\ref{interview-questions}) and participant-specific questions to verify any hypotheses we had (e.g.
+On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment.
+Before each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
+
+Each one-hour session was run by at least two researchers.
+We started by informing the participant of the study, task, and risks (Appendix~\ref{qualitative-script}).
+After they consent to the experiment, we instructed them to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites are blocked.
+We explicitly tell them to use Tor to circumvent censorship.
+The worksheet (Appendix~\ref{participant-worksheet}) required answers from a censored website (Wikipedia) and an uncensored website (CNN).
+We chose Wikipedia and CNN because they were popular websites~\cite{alexa} and their likely familiarity would make the task seem less intimidating.
+After instructions, researchers gave left the room to minimize interactions and watched a live feed of the participants' screen.
+
+After 45 minutes (or when they finished the worksheet), we interviewed them.
+We asked both general questions (Appendix~\ref{interview-questions}) and additional participant-specific questions that verified our observations (e.g.
 ``the participant was selecting bridges at random'').
-We paid each participant~\$30 for their time.
+We gave them~\$30 for their time.
 
@@
 
-To see a summary of what each of our 16 participants did, see Appendix~\ref{summaries}.
+We talk about the main reasons why users struggled to use Tor launcher, summarizing general behavioral trends and attitudes. We detail what each participant did in Appendix~\ref{summaries}.
 
@@
 \label{sec:pain-points}
-We talk about the main challenges our participants faced during the experiment. 
-Quotations were transcribed live during the follow-up interview.
-
-The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
-Participants found the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) and did not know what to do to configure bridges and proxies (Figures~\ref{fig:old-bridge-combobox} and~\ref{fig:old-proxy-yes}).
-
-%P3 in the repo, P3 in the paper
-\pquote{P3}{``The vocabulary is really challenging, for someone not doing IT work.''}
+Participants spent a lot of time going back and forth on screens, looking for proxy information, and waiting for the connection to work or timeout.
+We believe that the reasons for these behaviors are:\\
+
+\begin{itemize}
+\item {\bfseries A non-existent mental model:} Participants found terms in the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}).
+\end{itemize}
+
+%P11 in the repo, P9 in the paper
+\pquote{P9}{``You can only answer this question correctly if you know what a local proxy is.
+Otherwise you have no chance...''}
 
 %P13 in the repo, P7 in the paper 
-\pquote{P7}{``I didn't know where to start. I didn't know what to do. [I] was just fiddling, to be honest with you... it was kind of confusing.''}
-
-In addition to not knowing what to do, they did not understand the choices that they had to make.
-
-%P2 in the repo, P2 in the paper 
-\pquote{P2}{``I don't know what any of those (points to list of transports) means. I don't know what that (points to proxy settings) means at all."}
+\pquote{P7}{``[I] was just fiddling, to be honest with you... it was kind of confusing.''}
+
+\begin{itemize}
+\item {\bfseries Missing information:} They did not know how to choose a bridge by transport and which bridges worked in their environment (Figures~\ref{fig:old-bridge-combobox}).
+\end{itemize}
 
@@
 
-%P15 in the repo, but P12 in the paper
-\pquote{P15}{``I didn't know if this computer had any proxy information.
-I wasn't able to find it if it did.
-I went to every browser and could not find what they were talking about.
-I googled how I would find that and couldn't seem to get good information.
-[I] couldn't find anything that said tools.''}
-
-%P11 in the repo, P9 in the paper
-\pquote{P9}{``I think you can only answer this question correctly if you know what a local proxy is.
-Otherwise you have no chance... because looking at the Internet setting in another browser could be anything.''}
-
-The progress bar had dependencies that made it update oddly.
-If progress bar reached 90\% and failed, the progress bar will remain at 0\% on the next attempt until the progress surpassed 90\%.
-This made many assume that their subsequent attempts were wrong.
-
-%P13 in the repo, P7 in the paper 
-\pquote{P7}{``I was kind of doubting myself because everything was really slow.''}
+\begin{itemize}
+\item {\bfseries Bad recovery:} Participants had to wait a couple minutes to know if their connection failed, and also were quote upset that they had to wait that long to find out that their connection failed.
+\end{itemize}
 
@@
 
-We have additional concerns on system visibility, error recovery, and user workload.
-Users cannot see their settings before or while they are connecting.
-This is only visible on the bridge and proxy screens.
-Participants did not know what to do after a connection failed.
-Users should be made aware of what to fix.
-Users do too much work (reading text, click throughs, choices) in this interface.
-We show an attempt to fix these issues in Section~\ref{sec:design}.
-
-\section{Design Changes}
+These were our general observations.
+Participants who could connect directly or use the recommended bridge had an easy time connecting, but the participants who could not use many of the hardcoded bridges did not know what to do.
+For a summary of how each participant connected to Tor and what behaviroal trends dominated in each environment, see Appendix ~\ref{summary}.
+
+\section{Design}
 \label{sec:design}
 
-We limited ourselves to design changes that do not require infrastructural changes. Figure~\ref{fig:new-interface} shows the results.
+We limited design changes to ones that do not require infrastructural changes, addressed observed pain points, and adhered to our design considerations (Figure~\ref{fig:new-interface}).
 
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen (F).
-We reduced the text on the screen and clarified that configuration is for heavily censored environments.
-``Configure'' leads to the proxy screen  (Figure~\ref{fig:new-proxy}.)}
+	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavily censorship.}
 	\label{fig:new-first}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy screen (P). The interface locally detects if users need a proxy. If they need to configure one, proxy fields (same as Figure \ref{fig:old-proxy-yes}) are automatically populated.}
+	\caption{The proxy screen (P). The interface locally detects for a proxy and automatically populates the fields if necessary.}
 	\label{fig:new-proxy}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge screen (B). We give users the options to connect  without a bridge (the default choice) alongside the other options. We tell users when to choose a bridge. }
+	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and got rid of the bridge question screen.}
 	\label{fig:new-nobridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{We give a second bridge recommendation for the provided bridges. We hide the text field to input custom bridge information until they click the radio button to configure one.}
+	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields until the custom option is chosen.}
 	\label{fig:new-bridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The provided bridges and their supporting transports remains unchanged. This dropdown menu is the same as the bridge settings in the old interface (Figure~\ref{fig:old-bridge-combobox}).}
+	\caption{This dropdown menu remains the same (see Figure~\ref{fig:old-bridge-combobox}).}
 	\label{fig:new-bridge-combobox}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH). We did not make any changes to this page. This screen is identical to that in the old interface (Figure~\ref{fig:old-bridge-help}).}
+	\caption{The bridge help screen (BH) remains the same as well.}
 	\label{fig:new-bridge-help}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The summary screen (S). This screen shows users what they had configured in the interface. If they  configured proxies or bridges, this summarizes their choices.}
+	\caption{The summary screen (S) summarizes the configuration. This example configuration is connecting directly to Tor.}
 	\label{fig:new-summary}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The progress bar (Pr). A checkpoint progress bar shows the status of each component in the connection (there are more checkpoints if bridges and proxies are configured).}
+	\caption{The progress bar (Pr) shows the status of each component in the connection as the connection is made.}
 	\label{fig:new-progress}
@@
 
+\subsection{Changes Made} 
+We eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and eliminated the proxy screen by simulating auto-detection for proxies.
+We added a screen to summarize the settings before connecting and added indicators to progress bar that showed what component was unreachable.
+We switched the proxy and bridge screens so that they are in a topologically sequential order.
+We clarified that the configure option was for heavily censored environments and gave a secondary bridge recommendation for heavily censored users.
+
 \subsection {Design Considerations}
 
-Changes were inspired by user observations and constrained by the following design considerations:
+Here are some of the justifications for why we made conservative, front-end only design changes: \\
 
 \begin{itemize}
-\item {\bfseries User consent}: Connecting to Tor requires consent since being revealed as using Tor can be dangerous.
-While we could help users by automating the configuration and connection process, taking on risk for the user without proper consent is not ethical.
-
-\item{\bfseries Active adversaries}: We could ask the user, "what country are you in?", "are you at risk?" or "do you know what you are doing?" to make decisions.
-While leveraging user input works well, third-party versions of Tor Browser will replicate the official version, but might steal the inputs to profile users.
-
-\item {\bfseries  Passive adversaries}: Assuming a sufficiently powerful network adversary (like governments), a failed, non-obfuscated attempt to connect to Tor will tell a passive eavesdropper that the user is connecting to Tor.
+\item {\bfseries User consent}: Using Tor can involve some risk dangerous. While we could help users by automating connection, taking on risk for the user without proper consent is not ethical.
+
+\item{\bfseries Active adversaries}: We could ask the user for their location, risk, or preferences to make decisions.
+Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version can steal the inputs to profile users.
+
+\item {\bfseries  Passive adversaries}: A sufficiently powerful network adversary can detect that the user is connecting to Tor.
 We should allow users to leverage local information to reduce their risk.
 
-\item{\bfseries  Maintenance constraints}: Network environments change all the time--what bridge was reachable in a country an hour ago might not be tomorrow.
-Keeping up with how and when each country censors Tor would require a lot of time.
-Even if we keep up with how and when each country censors Tor, we would need to push changes before any of the affected users connect to Tor, which is an unreasonable turnaround time.
-
-\item{\bfseries  Financial constraints}: We could leverage harder-to-block meek relays connect people to Tor, then assign them something that would work afterward.
-But these relays cost thousands of dollars to run a month at their current capacity, and using them more would cost even more money.
+\item{\bfseries  Maintenance constraints}: Network environments change all the time. Keeping up with how each country censors and pushing changes before the affected users connect to Tor is difficult.
+
+\item{\bfseries  Financial constraints}: Leveraging harder-to-block meek bridges can help, but these relays cost magnitudes more than other relays and using them more would cost even more money.
 \end{itemize}
 
-It's possible that alternative changes could have been made, if we didn't treat these considerations as constraints.
-We start the discussion on methods that leverage user input and automation in Appendix~\ref{alternatives}.
-
-\subsection{Changes Made} 
-To require less work, we eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and simulated auto-detection for proxies by telling users that they did not need a proxy (this is feasible to implement with a local scan that does not leak information).
-
-To help users decide what to do, we label the configure button as an option for heavily censored environments, tell users to configure a bridge if Tor is censored, and give a secondary bridge recommendation
-
-To help users understand, we added a summary screen displaying the current bridge and proxy settings, switched proxy and bridge screens to put them in a topologically sequential order (Figure~\ref{fig:topology}), and added checklist indicators into the progress bar that show if various components were reached.
+Other beneficial changes could have been made, if we didn't treat these considerations as constraints.
 
@@
 \label{sec:quantitative}
-This section discusses our large-scale quantitative usability experiment and resulting user measurements.
+To confirm pain points and user behaviors, we logged and quantified user interactions with the interface.
 
 \subsection{Recruitment}
-We recruited 65 participants from Craigslist and 59 participants from the <redacted lab> participant pool using text in Appendix~\ref{quantitative-recruitment}.
-<Redacted lab> encouraged the use of their participant pool, but we bargained to recruit participants from Craigslist to ensure a diverse set of participants.
-<Redacted lab>'s participant pool is mainly students and staff from <redacted institution>, even though anyone could join.
-
-We had 124 participants, but we filtered out 10 participants who did not complete the consent form correctly or did not interact with the instrumented interface.
-Of the 114, one participant did not report their demographics.
-We still use their experiment data.
-Of the 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
-Ages ranged from 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$).
-84.1\% of our participants had at least a college education.
-We had about 20 in each interface and environment combination and ensured each condition had about half Craigslist recruited participants and half <redacted lab>  pool participants.
-
-\subsection{Setup}
-We ran our experiment at <redacted lab>, an experimental social science laboratory for behavioral experiments.
+We recruited 65 participants from Craigslist and 59 participants from Xlab participant pool with an ad (Appendix~\ref{quantitative-recruitment}).
+Xlab encouraged the use of their participant pool, we recruited from Craigslist as well to ensure diversity of participants since its participants were primarily students and staff from UC Berkeley.
+
+Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or did not interact with the interface.
+One participant did not report their demographics, but we still used their data.
+Of the remaining 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
+They were between 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).
+
+\subsection{Procedure}
+We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory.
 The testing room had 36 workstations with identical Windows~7 laptops.
 Side panels at each workstation discouraged participants from looking at other screens.
-%Xlab~\cite{xlab}, the Experimental Social Science Laboratory at the University of California, Berkeley. 
-The computers at <Redacted lab> use a system restore software to revert computers to a clean version at the beginning of each session.
-
-Before each session, we ran a script that downloaded Firefox, Chrome, IE, and VLC, set up one of the three simulated environments (E1, E2, or E3), and downloaded a version of Tor Browser 5.0.3 (original or our design), and started the computer screen recording.
-In contrast to the previous test, the Tor Browser 5.0.3 was instrumented to log user interactions with it (clicks, selects, transitions, etc.).
+These computers at used a system restore software to revert computers to a clean version at the beginning of each session.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+We instrumented Tor Browser to log user interactions.
 Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
 
-\subsection{Procedure}
 We assigned participants  to a simulated censorship environment combination at random by assigning them to a computer at random.
-We told the participants the purpose of the study, what data was collected, and any associated risks.
-Then they signed a consent form with this information in writing.
-Before the experiment, we clarified that they could stop at any time during the experiment with no negative consequences.
-
-We started by informing participants of the simulated censorship environment, giving them their worksheet,  informing them that Tor browser is necessary to circumvent censorship, and pointing out that Tor is installed for them on the computer (Appendix~\ref{quantitative-script}).
-They were asked to complete a worksheet that requires an answer from a censored site (Wikipedia) and explicitly reminds users to use Tor to do so (Appendix~\ref{summative-worksheet}).
-We reminded them to not show personal information since we are recording their screens, answered any questions, then gave them 40 minutes to complete the task.
-
-After instructions, researchers maintained minimal interactions with the participants, only answering logistical questions.
-Afterward, we administered an exit survey to collect demographics (Appendix~\ref{quantitative-exit-survey}).
-We paid each participant \$30 for their time.
+We informed participants of the simulated censorship environment, giving them their worksheet,  informing them that Tor browser is necessary to circumvent censorship, and pointing out that Tor is installed for them on the computer (Appendix~\ref{quantitative-script}).
+They were asked to complete a worksheet that requires visiting a censored site (Wikipedia) and explicitly reminds users to use Tor to do so (Appendix~\ref{summative-worksheet}).
+Before the experiment began, we reminded them that we are recording their screens, answered any questions, then gave them 40 minutes to complete the task.
+
+Researchers maintained minimal interactions with the participants after instructions, only answering logistical questions.
+After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we answered any additional questions and gave them \$30.
 
 \subsection{Results} 
-We summarize what our participants did below.
-Table~\ref{table:participant-summary} gives an overview of the results and Figure~\ref{fig:all-participant-edges} summarizes all participants' paths during the experiment.
-In this section, we use OLD to refer to the deployed Tor Browser 5.0.3 Tor Launcher GUI (Figure~\ref{fig:old-interface}) and NEW to refer to our redesigned version (Figure~\ref{fig:new-interface}).
+Users should be able to connect to Tor in a few minutes.
+The interface does not meet this goal (Table~\ref{table:participant-summary}).
+The design changes save users some time, but more changes are required get more people to connect and to connect even faster.
+In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
+
+We found that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
+Users average over 3 minutes in censored environments and are averaging over 20 minutes in heavily censored environments (Figure~\ref{fig:all-participant-edges}).
+We recommend a thorough redesign of the interface.
 
@@
 \caption{
-A summary of our valid participants' paths through the interface.
+A visualization of our participants' paths through the interface.
 The length of the bars show the total time taken to complete the task,
@@
 while off-focus, this time still counts as spending time in that off-focus window. 
-``Not running'' are times when Tor Launcher was closed (
-i.e. restarting the application).}
+``Not running'' are times when Tor Launcher was closed (i.e. restarting the application).}
 \label{fig:all-participant-edges}
@@
 \caption{
-An overview of the results of the experiment. Those who
-failed to connect were assigned the maximum time of 40:08, 
-the maximum time a participant took to finish the task.
+An overview of the experiment. 
+Those who didn't connect were assigned a time of 40:08, 
+(the maximum time).
 }
@@
 \caption{
-Network components that led to the first successful bootstrap
-in each condition.
-Most successful E1 participants used a direct connection,
-but a few optionally used an obfs3 bridge.
-All successful E2 participants used 
-an obfs3 bridge (the recommended option)---none used 
-flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
-Most successful E3 participants
-used meek bridges, disfavoring meek-azure.
-One E3 participant succeeded in an unexpected way
-by using an open proxy and configuring it to bypass our 
-simulated environment.
+A table showing how people connected to Tor.
+Note that none used flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
+One participant configured a proxy to bypass our simulated censorship environment.
 }
@@
 
-%overview
-Completion rate was defined as the percentage of users that eventually connected to Tor.
-Table~\ref{table:participant-summary} summarizes the completion rates and Table~\ref{tab:attempts-bridge-proxy} shows the configuration for users' first successful connection.
-We only considered the first successful configuration, as some curious participants tried others after completing their task.
-
-% failure observations
-17\% (19 of 114) of participants were not able to successfully connect to Tor.
-Five (P73, P75, P89, P91, P106, P110) tried a direct connection.
-When that failed, they assumed there was something wrong with their computer, network settings, or the Tor network and never tried to configure bridges or proxies.
-Five (P74, P92, P105, P107, P113) users who need a bridge assumed that they needed a proxy to connect to Tor.
-We believe this may be due to the fact that the OLD interface defaults to showing users the proxy page (because it is the one before the progress screen) when a connection fails.
-Five (P90, P93, P108, P111, P114) users who needed a meek or custom bridge tried the suggested bridge (obfs3), but didn't know what to do when that failed.
-Two (P94, P109) users who needed a meek or custom bridge tried to get custom bridges but failed to format their email content correctly to get a response from the bridges autoresponder.
-We suspect that they would have succeeded if they had gotten a response.
-
-%success rate and version
-Our interface changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $\mbox{df} = 2$, $p = 0.094$).
-That is, the slight differences in completion rates between E1-NEW vs E1-OLD, E2-NEW vs E2-OLD and E3-NEW vs E3-OLD are likely due to random chance.
+Most users could connect if they didn't need to configure anything (E1) or go with the recommendations in the interface (E2).
+If some bridges were blocked (E3), people couldn't figure it out, or took a long time to do so (Table~\ref{table:participant-summary}).
+Some optionally used a bridge (E1), although those who could use any bridge to connect didn't deviate from the recommendation (E2) and those who needed a meek bridge chose one at random (Table~\ref{tab:attempts-bridge-proxy}).
+17\% (19 of 114) were not able to connect to Tor.
+We confirm what we have suspected as pain points in our qualitative experiment.
+The  reasons for failing to connect were that: users did not know whether to connect directly or configure a bridge or proxy  (P73, P75, P89, P91, P106, P110), users did not know what they needed and tried to configure proxies (P74, P92, P105, P107, P113), users did not know what to do if recommended bridge didn't work (P90, P93, P108, P111, P114), and could get custom bridges (P94, P109).
+
+Our changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $\mbox{df} = 2$, $p = 0.094$).
+The differences in completion rates are likely due to random chance.
 
@@
 \subsubsection{Connection time} 
-Connection time is the time from Tor Browser startup to the first successful Tor bootstrap.
-Non-finishing participants are assigned the maximum experiment time of 40:08.
-Table~\ref{table:participant-summary} summarizes the median times while Figure~\ref{fig:time_to_success_clamped} shows their distribution.
-Figure~\ref{fig:time_to_success_ecdf} shows the cumulative success rates over time.
-
-%time observations (how long people took)
 The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
-Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
-
-%time to success and version
-Our interface changes had a significant impact in reducing connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-That is, the differences in mean connection times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-We used a one-tailed Mann--Whitney test because the distribution of completion times were 1) right-censored at 40 minutes (experiment duration) and 2) non-normal and heavily right tailed (failures were assigned a time of 40 minutes).
+Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect (Figure~\ref{fig:time_to_success_clamped}).
+The longer the time went on,the less likely that participants were to succeed (Figure~\ref{fig:time_to_success_ecdf}).
+Participants generally kept trying the same options over and over, or gave up and waited for the experiment to be over.
+
+Our changes significantly reduced connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
+We used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right tailed, and right-censored at the experiment duration.
+With the advice to only configure for heavily censored settings, users  tried a connection more quickly without trying to configure anything.
+This worked for users who did not need one (E1), but did not save users who needed any bridge (E2) much time.
+People still tried to connect with the recommended bridge before trying another one, but we suspect that the advice to ``try a meek-bridge if the recommended one did not work'' saved users who could not use certain bridges (E3) a significant amount of time.
 
@@
 Participants in E2 and E3 took a long time to connect.
-The ``DNF'' (did not finish) shows how many of participants 
-did not finish; they were assigned the maximum time of 40:08.}
+The ``DNF'' (did not finish) shows how many did not connect.}
 \label{fig:time_to_success_clamped}
@@
 \caption{
-Cumulative success rates over time. The longer the time went on, participants were less likely to succeed. 
+Cumulative success rates over time.
 }
@@
 \subsubsection{Configuration Time} 
-Configuration is defined as the completion time minus {\it any} time spent on the progress screen.Table~\ref{table:participant-summary} shows the median times and Figure~\ref{fig:time_to_success_active_clamped} shows their distribution.
-Table~\ref{table:median_time} shows where participants spent their time.
+Most users spent a majority of their time in the interface on the progress screen (Table~\ref{table:median_time}).
+Thir configuration time is a small fraction of their connection time (Figure~\ref{fig:time_to_success_active_clamped}).
+We see that the time spent bootstrapping the connection to Tor dominated measurements users who connect without configuring anything (E1), and waiting for the timeout error when Tor is blocked dominates measurements for users who do not try the correct configuration on the first try (E2, E3).
+We noticed that users who configured components incorrectly searched for help in another browser while waiting for their connection to time out.
+Users should not need to search for help outside the interface during configuration.
+
+Our changes significantly reducinged configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
+Again, we used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right tailed, and right-censored at the experiment duration.
+Users were less likely to spend time unnecessarily configuring proxies (Table~\ref{table:median_time}) and try different bridges.
+We believe that this is reflective of how most users would not require a proxy to connect to Tor, and suspsect that most real-life users spend time configuring proxies when they need a bridge instead.
 
@@
 \caption{
-The median percent of time spent on each screen, aggregated over participants in each experimental condition. }
+The median percent of time spent on each screen, aggregated over participants in each experimental condition.}
 \label{table:median_time}
@@
 \caption{
-Only a small fraction of the time was used to configure bridges and proxies.
-Non-finishing participants' active time was computed by
-subtracting the amount of time spent on the progress screen from
-their assigned completion time of 40:08.
+Configuration times are much shorter than their connection time, which means that most of the time was spent waiting for the connection to work or time out.
+Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
 }
@@
 
-%things to keep in mind
-We believe that configuration time is a meaningful metric because 1) bootstrapping can dominate measurements for users who do not need much time to configure their connection (E1 participants), and 2) many errors do not interrupt the connection attempt and cause many users to wait a long time before they manually cancel the connection to try again.
-This metric is not perfect though, since it does not reflect how some participants actively searched for help in another browser rather than passively waiting for their connections to work.
-
-%configuration time and version
-Our interface changes had a significant impact in reducing configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-That is, the differences in mean configuration times in E1-NEW vs E1-OLD and E2-NEW vs E2-OLD and E3-NEW vs E3-OLD is likely not due to random chance.
-We used a one-tailed Mann--Whitney test because the distribution of configuration times was also 1) right-censored and 2) non-normal and heavily right tailed, due to being an artifact of completion time.
-
-\subsection{Usability of Tor Launcher} 
-We confirmed our observations from our qualitative user test and find that participants wait on the progress screen for a long time, spend time configuring proxies when they did not need to, and do not know what to do if the recommended bridge doesn't work.
-
-From our measurements, we find that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-Users average over 3 minutes if they needed a bridge and are averaging over 20 minutes if they needed a meek or custom bridge.
-
-Ideally, almost all users should be able to configure the necessary or optional network components and connect to Tor within a few minutes.
-Neither the Tor Browser's 5.0.3 Tor Launcher GUI nor our redesigned Tor Launcher GUI meets this goal.
-
 \section{Recommendations}
 \label{sec:recommendations}
-We offer some suggestions based on what we learned: \\
+We do not recommend our design exactly. Instead, we offer some suggestions based on what we learned: \\
 
 \begin{itemize}
-\item {\bfseries Hide the proxy configuration screen and less-used transports.} None of our participants connected using flashproxy, fte, fte-ipv6, or scramblesuit transport bridges.
-Hiding infrequently used options will help users make better choices.
-\item {\bfseries Discourage users from configuring optional components.} Many participants configured proxies and bridges that they did not need. Add more explicit guidance on when to use them.
-\item {\bfseries Redirect to relevant screens on error.} For instance, redirect users to the bridge screen if the bridge failed instead of requiring users to do so.
-\item {\bfseries Take advantage of the progress screen.} Participants spent a majority of their time here.
-This time could be used to inform them of their bridge and proxy settings, educate users about what Tor does, or introduce Tor Browser.
+\item {\bfseries Assume users don't know technical concepts.} Users should not need to know what a relay, bridge, proxy, or transport is to connect to Tor. 
+\item {\bfseries Explain why users need to make decisions.} Knowing why they are required to perform a task will make them more cooperative.
+For instance, users currently choose transports because different subsets of transports work for different countries, and Tor does not track their location.
+\item {\bfseries Leverage user knowledge.} Users know what country they are connecting from, their level of risk involved using Tor, and what they are using Tor for.
+Guiding users to make decisions based on this information will work better than asking about their ISP or explaining what obfuscation protocols are.
 \end{itemize}
 
-While we believe that adopting our design faithfully will save users time.
-But since we did not test our design changes independently, we cannot (and do not) claim specific effects for each change.
-Alternative designs may be better solutions.
+We recommend implementing some design changes right away to resolve some problems, and consider additional ways to make connecting to Tor easier. \\
+
+\begin{itemize}
+\item{\bfseries Design changes:} as demonstrated by our design interation, tweaks in the interface can result in significant usability improvements. We don't necessarily suggest our design exactly. 
+\item{\bfseries Naive automation:} a scheme that choose bridges, wait for timeouts, and tries another one so users do not need to do this themselves. 
+\item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwith constraints. 
+\end{itemize}
+
+User consent should precede any automated connections to Tor. Alternative methods, such as on giving location-specfic advice, should be explored as well.
 
@@
 Participants in a laboratory setting may alter their behavior due to their awareness of being observed~\cite{mccarney2007hawthorne}.
-Our participants were likely motivated differently compared to real users, but we believe that they were likely over-motivated because they were being observed and receiving a monetary reward.
+Ours were likely motivated differently compared to real users.
+We believe that they were likely over-motivated because they were being observed and receiving a monetary reward.
 If true, this makes our results a conservative estimate of the usability problems.
 
-Since the configuration interfaces in simulated environments, we cannot claim how difficult it would be for a user to connect to Tor in a certain country or how much our redesigned interface would help those users.
-
 Our experiment did not directly test advanced tasks such as configuring a proxy or a custom bridge. From observing  users, we suspect they struggle with these tasks.
 
-We only tested the interface with Windows machines.
+We only tested the interface on the Windows operating system.
 The interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalents.
@@
 \label{sec:related} 
-% intro to usable security 
-The difference between a poor interface and a good interface can influence users’ ability to perform tasks securely~\cite{payne2008brief}.
-Usable security aims to improve the security of a system by designing with the user in mind.
+Previous usability studies on Tor have focused on installation and use, but not on setting up Tor Browser.
+Norcie et~al.~\cite{norcie2012eliminating} observed 25 users and found that 64\% were had issues that prevented them from installing or using Tor Browser.
+Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency that benefits their anonymity~\cite{dingledine2009performance}.
+Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.
+We do not know of any published usability evaluations of Tor Browser since the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
+Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.
+
+Usable security aims to improve the security of a system by helping the user to make good decisions~\cite{payne2008brief}.
 This involves informing users about the system, communicating risks in a way that is understandable, clarifying what the security requirements are, and providing guidance with technical tasks~\cite{adams1999users}.
-Our work contributes to the body of usable security by evaluating Tor Browser, which is an anonymity and censorship circumvention software that requires user interaction.
-Other usable security research explores a variety of security software or features, such as email encryption software ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication methods~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, web indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and security warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
-
-Usability inspection methods~\cite{nielsen1994usability} are used to define usability problems in an interface. We
-used a cognitive walkthrough~\cite{wharton1994cognitive}\cite{cognitive-walkthrough} to evaluate our interface.
-Other inspection methods include heuristic evaluation, pluralistic walkthrough and feature inspection~\cite{inspection}.
-
-We used usability lab studies (one-on-one experiments with a given set of scenarios and tasks for a specific use of  a product or service) and usability benchmarking (tightly scripted usability studies are performed with many participants used to collect measures of performance) to get qualitative and quantitative behavioral data about Tor Launcher's GUI~\cite{krol2016towards}.
-There are other ways to collect behavioral data as well, such as eye tracking, clickstream analysis and AB testing.
-These are in contrast with a variety of user experience research methods that collect qualitative or quantitative attitudinal data, such as focus group, camera studies, and product surveys~\cite{ux-methods}.
-We performed interviews after our lab study, but we mostly used these interviews to verify our behavioral observations rather than to draw conclusions about what people thought about their experience.
-
-User-centered design improves the usability of software by accounting for user factors. 
-Some work we found especially relevant to improving the usability of Tor Browser were
-Yee et~al.'s starting points for reasoning about security from
-a user-centered perspective and principles for secure interaction design~\cite{yee2002user},  
-Molich et~al.'s examination of  common problems in human-computer dialogue design~\cite{molich1990improving}, and Egelman et~al.'s examination of user tolerance of security delays~\cite{egelmanplease}.
-
-% Previous Tor studies 
-Our work uniquely contributes to Tor by examining the usability of the configuration interface.  
-Previous usability studies on Tor have focused on installation and use.
-Norcie et~al.~\cite{norcie2012eliminating} performed a 25-user test of Tor Browser and found that 64\% of users were unable to complete installation or browsing tasks.
-Fabian et~al.~\cite{fabian2010privately} discussed how added latency benefits anonymity~\cite{dingledine2009performance} but reduces usability.
-They quantified how the difference in latency causes frustration and decreases adoption.
-Clark et~al.~\cite{clark2007usability} performed a cognitive walkthrough of Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy) and found that none were satisfactory from a usability perspective.
-They highlight the best aspects of each tool and offer usability improvements.
-We do not know of any published usability evaluations of
-Tor Browser since the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
-Lee and Fifield~\cite{uxsprint} ran an informal UX sprint that recruited 5 users to install and use Tor Browser to observe their behavior.
-This uncovered some usability issues~\cite{uxsprint2015-tickets} and caused UI changes in Tor Browser version~4.5.
+Usable security research explores a variety of security concepts, such as email encryption ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, security indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
+Our work contributes to this body of knowledge by exploring the concept of censorship circumvention.
+
+We used a cognitive walkthrough~\cite{wharton1994cognitive}\cite{cognitive-walkthrough} to inspect our interface~\cite{nielsen1994usability} .
+Other usability inspection methods include heuristic evaluation, pluralistic walkthrough and feature inspection~\cite{inspection}.
+We used interviews and task benchmarking to get qualitative and quantitative data~\cite{krol2016towards}.
+Qualitative data can also be collected through focus groups, camera studies, and product surveys.
+Quantitative data can also be collected through seye tracking, clickstream analysis and AB testing~\cite{ux-methods}.
+
+For our work, we draw on the large body of previous work in secure interaction design, computer-human interaction, and user studies.
+Work we found useful to our experiment includes research on principles for secure interaction design~\cite{yee2002user}, common problems in human-computer dialogue design~\cite{molich1990improving}, user tolerance of security delays~\cite{egelmanplease}, treating human attention as a scarce resource when to delegating tasks to users ~\cite{bohme2011security}, stopping users from doing bad things ~\cite{good2007noticing}, and getting proper user consent ~\cite{bohme2010trained}.
 
@@
 \label{sec:conclusion}
-We believe that an interface is usable if a new user can identify what to do, knows if and when they do the right thing in the process, and can accomplish the required tasks.
-Tor Browser 5.0.3's configuration interface does not meet these requirements.
-We qualified where the interface is not usable with user observations and quantified how unusable the interface is with user interaction logs.
-We believe that our recommended changes will will help users connect to Tor in censored environments, but encourage discussion about alternative ways to configure a connection that would be easier for users.
-
-%proof that user testing is important and general advice to for more research on Tor
-Tor Browser version~4.5 incorporated changes to Tor Launcher based on our work <redacted Tor blog post here; it was authored by one of the authors of this paper>.
-We also talked to Tor developers about ways to automate the bootstrapping process to Tor.
-We encourage user testing for Tor applications to provide user insight into products that do not collect user data.
-We found the use of simulated censorship environments were especially helpful in running our experiments, due to their reproducibility, stability, and simplicity.
-
-\section {Experiment Artifacts} 
-Due to space constraints, we could not include many of our experiment artifacts.
-This includes the experiment setup and teardown code, firewall rules that simulated censorship environments, interview transcriptions from the qualitative user study, logs from our instrumented configuration interfaces, and videos of users attempting to connect to Tor through the configuration interface.
-We urge you to check out the project repository: \\
-
-\noindent <redacted URL>
-%\noindent \url{https://github.com/lindanlee/circumvention-ux-tor}
+We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor launcher.
+We believe that this because the interface requires users know technical terms, provides a lot of freedom for error, and does not give proper feedback.
+Users in heavily censored environments will likely not succeed in connecting to Tor without outside help.
+We encourage more usability studies on security tools in general as well as other Tor applications, as they have the potential to create user growth, help user retention, and prevent user frustration.
+Tor Browser version~4.5 incorporated  changes based on our work.
+We also talked with Tor developers about automating connections to Tor, and they are now considering this as future work.
 
 \section {Acknowledgments}
-Many generous people helped us along the way.
-<Redacted> assisted with testing our setup and teardown scripts, offered recruitment services, and allowed us to run experiments after <redacted lab>'s hours.
-<Redacted> and <redacted> were instrumental during the design process, as they helped me iterate through many not-so-great ideas.
-<Redacted> and <redacted> provided me with insider insight into the design decisions made at Tor.
-% Rowilma del Castillo. Nima Fatemi and Isabela Bagueros.  Georg Koppen and the Tor UX team.
+Georg Koppen, Mike Perry, and Isabela Bagueros from Tor Project, Inc. provided valuable insights about the history of Tor launcher and internal constraints.
 
@@
 
-\section{Alternative Approaches} 
-\label{alternatives}
-{\color {red}
-\begin{itemize} 
-\item{\bfseries Suggest bridges based on country.} Give users information about which bridges would work in their country.
-one way to do this is to show a list of countries with a corresponding recommended configuration.
-This requires developers to maintain a list of suggestions and that the users trust the suggestions.
-\item{\bfseries Ask users about their risk.} If they answer that they are sensitive about having a network adversary possibly know that they are using Tor, direct users to connect to a secret relay that is not publicly associated with Tor, using transport that obfuscates their connection.
-If users are not sensitive, let them configure their own bridges and proxies.
-\item{\bfseries Ask users if they know what to do.} If they know, offer the option to manually configure bridges and proxies.
-If they do not know, give suggestions on what to do next or automate the process for them somehow.
-This requires users to answer honestly to the question and to trust the suggestions given.
-\item{\bfseries Automate naively.} Have the interface automatically try configurations that would most likely work, in order (i.e.
-a direct connection, then an obfs3 connection without a proxy, then an meek bridge connection with out a proxy).
-This is what most users would ideally do anyway.
-However, this method leaks to network eavesdroppers that the user is using Tor without the user's awareness.
-\item {\bfseries Automate naively after users fail.} Let users try to configure bridges and proxies.
-If they fail, then a network eavesdropper already knows that the user is trying to connect to Tor.
-We believe there is negligible added risk to naively automate the connection.
-\item{\bfseries Automate in a smart way.} The interface first detects proxy settings and uses them, if any.
-Then it automatically connects to some secret bridges that will always work, which assign the user an entry relay that works based on their location.
-This requires having an invincible set of high-bandwidth bridges that work for every single user around the world.
-\end{itemize}
-We believe that these ideas can significantly help users connect to Tor.
-}
-
 \section{Quantitative User Study Recruitment Posting}

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Changes to Intro

@@
 Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot make the correct decisions during the configuration process.
-We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure their connections to Tor.
-Our study shows that 79\% (363 of 458) of user attempts to connect to Tor failed, and found that users were often frustrated during the process and try options at random.
+We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure connections to Tor.
+Our study shows that 79\% (363 of 458) of user attempts to connect to Tor in censored environments failed.
+We found that users were often frustrated during the process and try options at random.
 In this paper, we describe how we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
-Tor Browser ~4.5 incorporated  changes based on our work.
+Tor Browser ~4.5 incorporated the changes proposed by this study.
 }
@@
 
-  \journalyear{2015}
-  \journalvolume{2015}
-  \journalissue{2}
+  \journalyear{2017}
+  \journalvolume{2017}
+  \journalissue{3}
 
@@
 Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
-that make it difficult to observe the source and destination.
-Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor.
-Tor Launcher is a Tor Browser graphical user interface (Figure~\ref{fig:old-interface}) that asks the user to configure their connection to Tor.
-This is the object of our study.
-
-Although Tor Browser was originally designed for Internet anonymity, many now use Tor Browser to circumvent Internet censorship.
+that make it difficult to observe sources and destinations.
+Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers.
+Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship.
 Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
-The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor.
-Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this is also benefits other Tor users by increasing in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
-
-We started our usability evaluation by inspecting the interface (section~\ref{sec:inspection}) and
-running observing participants interact with it (section~\ref{sec:qualitative}). 
-We used the insights from our observations to make some changes to the interface (section~\ref{sec:design}) and
-quantified how usable the interface was before and after changes (section~\ref{sec:quantitative}).
-Afterward, we gave recommendations based on what we learned (section~\ref{sec:recommendations}), addressed
-limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}).
-We hope that our usability evaluation serves as an informative case study and provides guidance on improving Tor launcher.
+Tor Browser is bundled with a graphical configuration interface, Tor Launcher (Figure~\ref{fig:old-interface}), which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor.
+Of course, these configuration options are only effective if users understand how to correctly use them.
+Thus, we performed a usability study wherein we simulated various censorship environments in order to examine the effectiveness of Tor Launcher and how it could be improved.
+
+Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users: an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
+In this paper, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
+Based on the insights from our observations, we proposed some changes to the interface (Section~\ref{sec:design}) and
+quantified how usable the interface was before and after changes (Section~\ref{sec:quantitative}).
+Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address
+limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
+We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex

@@
 
-Technically, proxies are any computer or service that allow its users to make indirect network connections to other services.
+Technically, a proxy is any computer or service that allows its users to make indirect network connections to other services.
 In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy.
-However, in this paper and verbally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
-Fig.~\ref{fig:topology} illustrates the network components involved.
+However, in this paper and more generally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
+Figure~\ref{fig:topology} illustrates the potential network components involved in connecting to the Tor network.
 
@@
 Middle relays forward traffic from an entry relay to an exit relay.
-Exit relays receive traffic from a middle relay and direct the traffic to its intended destination.
+Exit relays receive traffic from a middle relay and direct the traffic to its intended destination (e.g., a website).
 A user uses Tor Browser to connect to the Tor network, which connects to websites on behalf of the user.
@@
 Bridges are unlisted alternative entry nodes used to connect to Tor when Tor relays are censored.
-Bridges also recieve packets from the user and forward traffic to middle relays, but also run a pluggable transport (referred to as ``transport'' for shorthand).
-Bridges are grouped by which transport they run for convenience.
+Bridges also receive packets from the user and forward traffic to middle relays, but also may run a pluggable transport (referred to as ``transport'' for shorthand).
+Pluggable transports specify alternative protocols by which Tor Browser may connect to the Tor network, thereby disguising Tor traffic to make it harder to detect and block bridges.
+For convenience, bridges are grouped by which transport they run.
 
 Most bridges can be blocked by blocking their static IP addresses.
-These include bridges that run``fte'' and ``fte-ipv6''~\cite{fte} transports, which disguise the Tor protocol as another protocol (such as HTTP), and ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
-Other bridges are less blockable because of how they work.
+These include bridges that run``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
+Other bridges are less susceptible to blocking because of how they work.
 Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks.
-What bridges are accesssible in each country varies.
-Fig.~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of the study.
+The bridges that are accessible in each country vary.
+Figure~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of our study.
 
@@
 only users who face a censor need a bridge.
-In the diagram, ``Tor'' represents all three anonymizing hops through the Tor network.
+In the diagram, ``Tor'' represents a circuit of hops through the Tor network.
 We have shown the bridge as a separate component
@@
 \subsection{Connecting to Tor} 
-There are many valid configuration settings to connect to the Tor network.
-A user who does not need a bridge or proxy can connect with a bridge, proxy, or both, provided that they are configured correctly.
+There are many valid configuration settings that can be used to connect to the Tor network.
+A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that they are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).
 
 Users can configure a bridge by choosing a transport (Figure~\ref{fig:old-bridge-combobox}), which selects the group of bridges that use that transport.
-If the built-in bridges do not work, users can obtain bridge lines through out-of-band channels~\cite{bridgedb} that provides the necessary bridge specifications.
+If the built-in bridges do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb} that provide the necessary information.
 Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}).
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen (F). ``Connect'' starts a connection.``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
+	\caption{The first screen (F). ``Connect'' starts a connection. ``Configure'' leads to the first bridge screen (Figure~\ref{fig:old-bridge}). }
 	\label{fig:old-first}
@@
 \section{Methodology} 
-This section discusses the process we used to determine the usability of Tor launcher interface.
+This section discusses the process we used to evaluate the usability of Tor Launcher.
 
 \subsection{Testing Pipeline} 
-We inspected the interface to anticipate potential problems and formally assess its pros and cons.
+We performed a cognitive walkthrough to inspect the interface to anticipate potential problems and formally assess its pros and cons.
 We then conducted qualitative and quantitative usability tests.
-We believed both were necessary for a complete evaluation.
+We believe both methods were necessary for a complete evaluation.
 Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable.
-Five users is considered to be the maximum benefit-cost ratio for gaining insights~\cite{howmanyusers}, so we recruited five participants for each condition in our qualitative experiment.
-Twenty users is considered to be the minimum for statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.
-
-We opportunistically used our observations from the qualitative study to design interface changes that would address common issues that our participants encountered.
-We also opportunistically used our quantitative testing setup to measure its usability with respect to the original interface.
-We discuss how our changes saved users time and recommend some changes.
+For gathering qualitative data, five users is considered to maximize the cost-benefit ratio~\cite{howmanyusers}, so we recruited five participants for each condition---multiple simulated censorship environments---in our qualitative experiment.
+Twenty users is considered to be the minimum for yielding statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.
+
+We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered.
+We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original Tor Launcher interface.
 
@@
 \item {\bfseries Completion rate:}  percentage of users that connect to Tor. A high completion rate is ideal. 
-\item {\bfseries Connection time:} time until a successful connection to Tor. This should be a couple minutes. 
+\item {\bfseries Connection time:} time until a successful connection to Tor. A low connection time is ideal, though is expected to be a couple of minutes.
 \item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, which excludes time waiting for connections to establish or timeout.
@@
 We measured this in two ways.
-Connection time measures how long users took to connect to Tor, which includes the time Tor takes to establish a series of relays.
-Since that time can dominate the measurement, we use configuration time to measure the time users spent configuring bridges and proxies.
+Connection time measures how long users took to connect to Tor, which includes the time Tor takes to establish a series of relays, while the user is forced to wait.
+Since time spent waiting can dominate the measurement, we use configuration time to measure the time users spent actively configuring bridges and proxies.
 
@@
 E2's blocking is a superset of E1's;
-similarly E3's is a superset of E2's.
+similarly, E3's is a superset of E2's.
 }
@@
 
-The simulated environments are not intended to imitate any particular country's network.
-Rather, they were designed to require different bridges to connect to Tor.
-We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the interface paths we wanted to test.
+The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
+Rather, we designed simulated environments to require different bridges to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
 
@@
 There were new releases during the experiments, but we used the same version throughout to not introduce confounding factors.
-
 We conducted our experiments on Windows machines.
@@
 
-\section{Usability Inspection}
+\section{Cognitive Walkthrough}
 \label{sec:inspection}
-We inspected of the interface to anticipate potential problems before testing it on users.
+We inspected the interface to anticipate potential problems before testing it on real users.
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Edited the Cognitive Walkthrough section

@@
 \label{sec:inspection}
-We inspected the interface to anticipate potential problems before testing it on real users.
+We inspected the interface to anticipate potential problems before testing it on study participants.
 
@@
 \begin{itemize}
-\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
+\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are likely to be unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
 \item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them.
@@
 Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface.
-Proxy fields also do not provide syntactic guidlines.
+Proxy fields also do not provide syntactic guidelines.
 See the whole list of possible errors in Appendix~\ref{states}.
-\item {\bfseries Poor feedback:} Even if there was a syntactic error in your bridge or proxy fields, it does not notifiy until a connection is made and fails.
-If a censored bridge was chosen, the connection timeout takes a over a couple minutes.
-Errors messages were often technical and did not give suggestions.
+\item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails.
+If a censored bridge was chosen, the connection timeout takes several minutes.
+Error messages were often technical and did not give suggestions.
 \end{itemize}
 
-These are some of the factors that contributed to why users struggled with the interface and therefore were unable to connect to Tor quickly.
+These are some of the factors that we believed contribute to users struggling with the interface and therefore may prevent them from connecting to Tor quickly.
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex
remove 4.5 from abstract

--- 2017-03-03 pets2017-paper/pets2017-paper.tex
@@
 Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot make the correct decisions during the configuration process.
-We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure connections to Tor.
-Our study shows that 79\% (363 of 458) of user attempts to connect to Tor in censored environments failed.
-We found that users were often frustrated during the process and try options at random.
+We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure their connections to Tor.
+Our study shows that 79\% (363 of 458) of user attempts to connect to Tor failed, and found that users were often frustrated during the process and try options at random.
 In this paper, we describe how we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
-Tor Browser ~4.5 incorporated the changes proposed by this study.
+Tor Browser incorporated  changes based on our work.
 }
@@
 
-  \journalyear{2017}
-  \journalvolume{2017}
-  \journalissue{3}
+  \journalyear{2015}
+  \journalvolume{2015}
+  \journalissue{2}
 
@@
 Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
-that make it difficult to observe sources and destinations.
-Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers.
-Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship.
+that make it difficult to observe the source and destination.
+Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor.
+Tor Launcher is a Tor Browser graphical user interface (Figure~\ref{fig:old-interface}) that asks the user to configure their connection to Tor.
+This is the object of our study.
+
+Although Tor Browser was originally designed for Internet anonymity, many now use Tor Browser to circumvent Internet censorship.
 Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
-Tor Browser is bundled with a graphical configuration interface, Tor Launcher (Figure~\ref{fig:old-interface}), which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor.
-Of course, these configuration options are only effective if users understand how to correctly use them.
-Thus, we performed a usability study wherein we simulated various censorship environments in order to examine the effectiveness of Tor Launcher and how it could be improved.
-
-Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users: an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
-In this paper, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
-Based on the insights from our observations, we proposed some changes to the interface (Section~\ref{sec:design}) and
-quantified how usable the interface was before and after changes (Section~\ref{sec:quantitative}).
-Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address
-limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
-We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.
+The configuration interface mainly exists so that people who face Internet censorship can configure bridges, transports, and proxies to connect to Tor.
+Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this is also benefits other Tor users by increasing in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
+
+We started our usability evaluation by inspecting the interface (section~\ref{sec:inspection}) and
+running observing participants interact with it (section~\ref{sec:qualitative}). 
+We used the insights from our observations to make some changes to the interface (section~\ref{sec:design}) and
+quantified how usable the interface was before and after changes (section~\ref{sec:quantitative}).
+Afterward, we gave recommendations based on what we learned (section~\ref{sec:recommendations}), addressed
+limitations of our evaluation (section~\ref{sec:limitations}), and framed our work in the context of existing work (section~\ref{sec:related}).
+We hope that our usability evaluation serves as an informative case study and provides guidance on improving Tor launcher.
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Described conditions in S. 3.3.

--- 2017-03-03 pets2017-paper/pets2017-paper.tex
@@
 \end{table}
+
+In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed).
+In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
+Finally, the third environment, E3, additionally blocked several of the included bridges, which meant experimenting with several different bridges---beyond the recommended ones---in order to successfully connect.
 
@@
 \label{sec:qualitative}
-We observed user behaviors to see why Tor is hard to use and interviewed users afterward to see how they felt.
+We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.
 
@@
 Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
-One participant declined to report their age, so age calculations omit this participant's information.
+Our age calculations omit one participant who declined to report it.
 All of our users had at least some college education.
-12 were new users and 4 had previously used Tor Browser in some capacity.
+Twelve were new users and 4 had previously used Tor Browser in some capacity.
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Added a better description of conditions

@@
 \subsection{Observations}
-We noticed that the interface leaves a lot of freedom for error but does not give good instructions on when there is an error and how to fix it: \\
+We noticed that the interface leaves a lot of freedom for error while not giving good instructions on how to recover from errors: \\
 
 \begin{itemize}
-\item {\bfseries Difficult tasks:} The interface uses technical and Tor-specific terms that are likely to be unfamiliar to an average user, such as the Tor network, internet service provider (ISP), local proxy, bridges, and transports.
+\item {\bfseries Technical terms:} The interface uses technical and Tor-specific terms that are likely unfamiliar to an average user (e.g., ``Tor network,'' ``local proxy,'' ``bridges,'' and ``transports'').
 \item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them.
@@
 Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
-Our age calculations omit one participant who declined to report it.
-All of our users had at least some college education.
+Our age statistics omit one participant who declined to disclose.
+All of our participants had at least some college education.
 Twelve were new users and 4 had previously used Tor Browser in some capacity.

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Edited up to Section 6.

@@
 On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment.
-Before each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
+Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
 
@@
 We started by informing the participant of the study, task, and risks (Appendix~\ref{qualitative-script}).
-After they consent to the experiment, we instructed them to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites are blocked.
-We explicitly tell them to use Tor to circumvent censorship.
+After they consented to the experiment, we instructed them to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites were blocked.
+We explicitly told them to use Tor to circumvent censorship.
 The worksheet (Appendix~\ref{participant-worksheet}) required answers from a censored website (Wikipedia) and an uncensored website (CNN).
 We chose Wikipedia and CNN because they were popular websites~\cite{alexa} and their likely familiarity would make the task seem less intimidating.
-After instructions, researchers gave left the room to minimize interactions and watched a live feed of the participants' screen.
-
-After 45 minutes (or when they finished the worksheet), we interviewed them.
-We asked both general questions (Appendix~\ref{interview-questions}) and additional participant-specific questions that verified our observations (e.g.
-``the participant was selecting bridges at random'').
+After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.
+
+After 45 minutes (or when participants finished the worksheet), we interviewed them.
+We asked both general questions (Appendix~\ref{interview-questions}) and additional participant-specific questions that verified our observations (e.g., ``the participant was selecting bridges at random'').
 We gave them~\$30 for their time.
@@
 
-We talk about the main reasons why users struggled to use Tor launcher, summarizing general behavioral trends and attitudes. We detail what each participant did in Appendix~\ref{summaries}.
+We talk about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes. We detail what each participant did in Appendix~\ref{summary}.
 
@@
 Participants spent a lot of time going back and forth on screens, looking for proxy information, and waiting for the connection to work or timeout.
-We believe that the reasons for these behaviors are:\\
+We believe that the reasons for these behaviors were:\\
 
@@
 \begin{itemize}
-\item {\bfseries Missing information:} They did not know how to choose a bridge by transport and which bridges worked in their environment (Figures~\ref{fig:old-bridge-combobox}).
+\item {\bfseries Missing information:} They did not know how to choose a bridge by transport or which bridges worked in their environment (Figures~\ref{fig:old-bridge-combobox}).
 \end{itemize}
@@
 \begin{itemize}
-\item {\bfseries Bad recovery:} Participants had to wait a couple minutes to know if their connection failed, and also were quote upset that they had to wait that long to find out that their connection failed.
+\item {\bfseries Bad recovery:} Participants had to wait a couple minutes to know if their connection failed, and also were quite upset that they had to wait that long to find out that their connection failed.
 \end{itemize}
@@
 Participants who could connect directly or use the recommended bridge had an easy time connecting, but the participants who could not use many of the hardcoded bridges did not know what to do.
-For a summary of how each participant connected to Tor and what behaviroal trends dominated in each environment, see Appendix ~\ref{summary}.
+For a summary of how each participant connected to Tor and what behavioral trends dominated in each environment, see Appendix~\ref{summary}.
 

### 2017-03-03 pets2017-paper/pets2017-paper.tex
Edited up to 7

@@
 These were our general observations.
-Participants who could connect directly or use the recommended bridge had an easy time connecting, but the participants who could not use many of the hardcoded bridges did not know what to do.
+Participants who could connect directly (E1) or use the recommended bridge had an easy time connecting (E2), but the participants who could not use many of the hardcoded bridges (E3) did not know what to do.
 For a summary of how each participant connected to Tor and what behavioral trends dominated in each environment, see Appendix~\ref{summary}.
 
-\section{Design}
+\section{Interface Redesign}
 \label{sec:design}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavily censorship.}
+	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavy censorship.}
 	\label{fig:new-first}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy screen (P). The interface locally detects for a proxy and automatically populates the fields if necessary.}
+	\caption{The proxy screen (P). The interface locally detects a proxy and automatically populates the fields as necessary.}
 	\label{fig:new-proxy}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and got rid of the bridge question screen.}
+	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and eliminated the bridge question screen.}
 	\label{fig:new-nobridge}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields until the custom option is chosen.}
+	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields are hidden until the custom option is chosen.}
 	\label{fig:new-bridge}
@@
 We eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and eliminated the proxy screen by simulating auto-detection for proxies.
-We added a screen to summarize the settings before connecting and added indicators to progress bar that showed what component was unreachable.
+We added a screen to summarize the settings before connecting and added indicators to the progress bar that showed what component was unreachable.
 We switched the proxy and bridge screens so that they are in a topologically sequential order.
-We clarified that the configure option was for heavily censored environments and gave a secondary bridge recommendation for heavily censored users.
+We clarified that configuration options were for heavily censored environments and gave a secondary bridge recommendation for heavily censored users.
 
@@
 \begin{itemize}
-\item {\bfseries User consent}: Using Tor can involve some risk dangerous. While we could help users by automating connection, taking on risk for the user without proper consent is not ethical.
-
-\item{\bfseries Active adversaries}: We could ask the user for their location, risk, or preferences to make decisions.
-Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version can steal the inputs to profile users.
-
-\item {\bfseries  Passive adversaries}: A sufficiently powerful network adversary can detect that the user is connecting to Tor.
-We should allow users to leverage local information to reduce their risk.
+\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks.
+While we could help users by automating configuration settings, this would involve probing network configurations, which may alert authorities to Tor usage.
+Taking this risk without proper consent is not ethical.
+
+\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions.
+Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.
+
+\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor. We should allow users to leverage local information to reduce their risk.
 
@@
 
-\item{\bfseries  Financial constraints}: Leveraging harder-to-block meek bridges can help, but these relays cost magnitudes more than other relays and using them more would cost even more money.
+\item{\bfseries Financial constraints}: Leveraging harder-to-block ``meek'' bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
 \end{itemize}
 
-Other beneficial changes could have been made, if we didn't treat these considerations as constraints.
+Other beneficial changes could have been made, if we did not consider these constraints.
 
@@
 \label{sec:quantitative}
-To confirm pain points and user behaviors, we logged and quantified user interactions with the interface.
+To confirm prior pain points and user behaviors, as well as to validate our proposed design improvements, we logged and quantified user interactions as part of a followup experiment.
 
 \subsection{Recruitment}
-We recruited 65 participants from Craigslist and 59 participants from Xlab participant pool with an ad (Appendix~\ref{quantitative-recruitment}).
-Xlab encouraged the use of their participant pool, we recruited from Craigslist as well to ensure diversity of participants since its participants were primarily students and staff from UC Berkeley.
+We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for the recruitment materials).
+We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.
 

### 2017-03-04 pets2017-paper/pets2017-paper.tex
Edited up to 9

@@
 Of the remaining 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
-They were between 18 to~68 years ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).
+They were between 18 and~68 years old ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).
 
 \subsection{Procedure}
-We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory.
-The testing room had 36 workstations with identical Windows~7 laptops.
-Side panels at each workstation discouraged participants from looking at other screens.
-These computers at used a system restore software to revert computers to a clean version at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory.
+The room had 36 workstations with identical Windows~7 laptops.
+Workstation partitions discouraged participants from looking at other screens.
+We automatically reverted the computers to the same image at the beginning of each session.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
 We instrumented Tor Browser to log user interactions.
-Each computer was manually assigned one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
+We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
 
 We assigned participants to a simulated censorship environment combination at random by assigning them to a computer at random.
-We informed participants of the simulated censorship environment, giving them their worksheet,  informing them that Tor browser is necessary to circumvent censorship, and pointing out that Tor is installed for them on the computer (Appendix~\ref{quantitative-script}).
-They were asked to complete a worksheet that requires visiting a censored site (Wikipedia) and explicitly reminds users to use Tor to do so (Appendix~\ref{summative-worksheet}).
-Before the experiment began, we reminded them that we are recording their screens, answered any questions, then gave them 40 minutes to complete the task.
+We informed participants that they were in a simulated censorship environment, informed them that Tor browser was necessary to circumvent censorship, and pointed out that Tor was installed for them on the computer (Appendix~\ref{quantitative-script}).
+We asked them to complete a worksheet that required visiting a censored site (Wikipedia) and explicitly reminded them to use Tor to do so (Appendix~\ref{summative-worksheet}).
+Before the experiment began, we reminded them that we were recording their screens, answered any questions, then gave them 40 minutes to complete the task.
 
@@
 \subsection{Results} 
-Users should be able to connect to Tor in a few minutes.
+Users should be able to connect to Tor within a few minutes.
 The interface does not meet this goal (Table~\ref{table:participant-summary}).
-The design changes save users some time, but more changes are required get more people to connect and to connect even faster.
+Our proposed design changes save users some time, but more changes are required to get more people to connect and to connect even faster.
 In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
@@
 We found that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-Users average over 3 minutes in censored environments and are averaging over 20 minutes in heavily censored environments (Figure~\ref{fig:all-participant-edges}).
-We recommend a thorough redesign of the interface.
+Participants averaged over 3 minutes in censored environments and over 20 minutes in heavily censored environments (Figure~\ref{fig:all-participant-edges}).
+Based on this, we recommend a thorough redesign of the interface.
 
@@
 Different colors indicate which screen they were on during the experiment.
-If participants were doing other things (i.e. searching for help in another browser)
+If participants were doing other things (i.e., searching for help in another browser)
 while off-focus, this time still counts as spending time in that off-focus window. 
-``Not running'' are times when Tor Launcher was closed (i.e. restarting the application).}
+``Not running'' are times when Tor Launcher was closed (i.e., restarting the application).}
 \label{fig:all-participant-edges}
@@
 An overview of the experiment. 
-Those who didn't connect were assigned a time of 40:08, 
+Those who did not connect were assigned a time of 40:08, 
 (the maximum time).
@@
 A table showing how people connected to Tor.
-Note that none used flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
+Note that none used the flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
 One participant configured a proxy to bypass our simulated censorship environment.
@@
 
-Most users could connect if they didn't need to configure anything (E1) or go with the recommendations in the interface (E2).
-If some bridges were blocked (E3), people couldn't figure it out, or took a long time to do so (Table~\ref{table:participant-summary}).
-Some optionally used a bridge (E1), although those who could use any bridge to connect didn't deviate from the recommendation (E2) and those who needed a meek bridge chose one at random (Table~\ref{tab:attempts-bridge-proxy}).
-17\% (19 of 114) were not able to connect to Tor.
-We confirm what we have suspected as pain points in our qualitative experiment.
-The  reasons for failing to connect were that: users did not know whether to connect directly or configure a bridge or proxy  (P73, P75, P89, P91, P106, P110), users did not know what they needed and tried to configure proxies (P74, P92, P105, P107, P113), users did not know what to do if recommended bridge didn't work (P90, P93, P108, P111, P114), and could get custom bridges (P94, P109).
-
-Our changes did {\it not} have a significant impact on completion rates (Pearson's Chi-squared; $\chi^2 = 2.808$, $\mbox{df} = 2$, $p = 0.094$).
-The differences in completion rates are likely due to random chance.
+Most participants could connect if they did not need to configure anything (E1) or used the recommended settings (E2).
+If some bridges were blocked (E3), people could not figure it out, or took a long time to do so (Table~\ref{table:participant-summary}).
+Some optionally used a bridge (E1), although those who could use any bridge to connect did not deviate from the recommendation (E2) and those who needed a meek bridge chose one at random (Table~\ref{tab:attempts-bridge-proxy}).
+Seventeen percent (19 of 114) were not able to connect to Tor at all.
+The most common reasons for failing to connect were not knowing whether to connect directly or configure a bridge or proxy (P73, P75, P89, P91, P106, P110), not knowing what they needed and trying to configure proxies (P74, P92, P105, P107, P113), and not knowing what to do when a recommended bridge did not work (P90, P93, P108, P111, P114).
+
+Because we hypothesized that the NEW interface would result in greater completion rates, we performed a one-tailed Pearson's chi-square test and found the results to be statistically significant ($\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$), albeit with small effect size ($\phi=0.157$).
 
@@
 \subsubsection{Connection time} 
-The simulated censorship environment, and therefore, the difficulty of the configuration, was the most determining factor for connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+The simulated censorship environment, and therefore, the difficulty of the configuration, was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
 Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect (Figure~\ref{fig:time_to_success_clamped}).
-The longer the time went on,the less likely that participants were to succeed (Figure~\ref{fig:time_to_success_ecdf}).
+The more time spent, the less likely that participants were to succeed (Figure~\ref{fig:time_to_success_ecdf}).
 Participants generally kept trying the same options over and over, or gave up and waited for the experiment to be over.
 
-Our changes significantly reduced connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p = 0.0328$, $r= 0.172$).
-We used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right tailed, and right-censored at the experiment duration.
-With the advice to only configure for heavily censored settings, users  tried a connection more quickly without trying to configure anything.
-This worked for users who did not need one (E1), but did not save users who needed any bridge (E2) much time.
+Our changes significantly reduced connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p < 0.0328$, $r= 0.172$).
+We used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right-tailed, and right-censored.
+With the advice to only configure for heavily censored settings, participants tried a connection more quickly without trying to configure anything.
+This worked for users who did not need one (E1), but did not save users who needed a bridge (E2) much time.
 People still tried to connect with the recommended bridge before trying another one, but we suspect that the advice to ``try a meek-bridge if the recommended one did not work'' saved users who could not use certain bridges (E3) a significant amount of time.
@@
 \subsubsection{Configuration Time} 
-Most users spent a majority of their time in the interface on the progress screen (Table~\ref{table:median_time}).
-Thir configuration time is a small fraction of their connection time (Figure~\ref{fig:time_to_success_active_clamped}).
-We see that the time spent bootstrapping the connection to Tor dominated measurements users who connect without configuring anything (E1), and waiting for the timeout error when Tor is blocked dominates measurements for users who do not try the correct configuration on the first try (E2, E3).
-We noticed that users who configured components incorrectly searched for help in another browser while waiting for their connection to time out.
-Users should not need to search for help outside the interface during configuration.
-
-Our changes significantly reducinged configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p = 0.000516$, $r = 0.307$).
-Again, we used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right tailed, and right-censored at the experiment duration.
-Users were less likely to spend time unnecessarily configuring proxies (Table~\ref{table:median_time}) and try different bridges.
-We believe that this is reflective of how most users would not require a proxy to connect to Tor, and suspsect that most real-life users spend time configuring proxies when they need a bridge instead.
+Most participants spent a majority of their time on the progress screen (Table~\ref{table:median_time}).
+Their active configuration time was a small fraction of their connection time (Figure~\ref{fig:time_to_success_active_clamped}).
+We see that the time spent bootstrapping the connection to Tor dominated the measurements of participants who connected without configuring anything (E1), and waiting for the timeout error when Tor was blocked dominated the measurements for participants who did not try the correct configuration on the first try (E2, E3).
+We noticed that participants who configured components incorrectly searched for help in another browser while waiting for their connection to time out.
+Participants should not need to search for help outside the interface during configuration.
+
+Our changes significantly reduced configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p < 0.0005$, $r = 0.307$).
+Again, we used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right-tailed, and right-censored.
+Participants were less likely to spend time unnecessarily configuring proxies (Table~\ref{table:median_time}) and trying different bridges.
+We believe that this is reflective of how most users would not require a proxy to connect to Tor, and suspect that most real users spend time configuring proxies when they need a bridge instead.
 
@@
 \caption{
-Configuration times are much shorter than their connection time, which means that most of the time was spent waiting for the connection to work or time out.
+Configuration times are much shorter than connection times, which means that most of the time was spent waiting for the connection to establish or time out.
 Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
@@
 \label{sec:recommendations}
-We do not recommend our design exactly. Instead, we offer some suggestions based on what we learned: \\
+While our design resulted in shorter connection times and greater success, it could still be improved.
+Thus, we do not recommend our exact design.
+Instead, we offer some suggestions based on what we learned: \\
 
 \begin{itemize}
-\item {\bfseries Assume users don't know technical concepts.} Users should not need to know what a relay, bridge, proxy, or transport is to connect to Tor. 
+\item {\bfseries Assume users do not know technical concepts.} Users should not need to know what a relay, bridge, proxy, or transport is to connect to Tor. 
 \item {\bfseries Explain why users need to make decisions.} Knowing why they are required to perform a task will make them more cooperative.
-For instance, users currently choose transports because different subsets of transports work for different countries, and Tor does not track their location.
-\item {\bfseries Leverage user knowledge.} Users know what country they are connecting from, their level of risk involved using Tor, and what they are using Tor for.
+For instance, users currently choose transports because different subsets of transports work for different countries, and Tor does not track users' locations.
+\item {\bfseries Leverage user knowledge.} Users know what country they are connecting from, their level of acceptable risk, and what they are using Tor for.
 Guiding users to make decisions based on this information will work better than asking about their ISP or explaining what obfuscation protocols are.
@@
 \begin{itemize}
-\item{\bfseries Design changes:} as demonstrated by our design interation, tweaks in the interface can result in significant usability improvements. We don't necessarily suggest our design exactly. 
-\item{\bfseries Naive automation:} a scheme that choose bridges, wait for timeouts, and tries another one so users do not need to do this themselves. 
-\item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwith constraints. 
+\item{\bfseries Design changes:} as demonstrated by our design iteration, tweaks in the interface can result in significant usability improvements.
+\item{\bfseries Naive automation:} a scheme that chooses bridges, waits for timeouts, and tries another bridge so users do not need to do this themselves. 
+\item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwidth constraints.
 \end{itemize}
 
-User consent should precede any automated connections to Tor. Alternative methods, such as on giving location-specfic advice, should be explored as well.
+User consent should precede any automated connections to Tor. Alternative methods, such as giving location-specific advice, should be explored as well.
 

### 2017-03-06 pets2017-paper/pets2017-paper.tex

@@
 
-Our experiment did not directly test advanced tasks such as configuring a proxy or a custom bridge. From observing  users, we suspect they struggle with these tasks.
+Our experiment did not directly test advanced tasks such as configuring a proxy or a custom bridge. From observing participants, we suspect they struggle with these tasks.
 
@@
 The interface leverages the native operating system's styling and elements, making the configuration interface on Windows look slightly different from the OS~X or Linux equivalents.
-We acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions minorly and equally.
+We acknowledge that participants' unfamiliarity with Windows may have affected our experiment, but we believe that this affected all experimental conditions equally.
 
@@
 Previous usability studies on Tor have focused on installation and use, but not on setting up Tor Browser.
-Norcie et~al.~\cite{norcie2012eliminating} observed 25 users and found that 64\% were had issues that prevented them from installing or using Tor Browser.
-Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency that benefits their anonymity~\cite{dingledine2009performance}.
+Norcie et~al.~\cite{norcie2012eliminating} observed 25 users and found that 64\% had issues that prevented them from installing or using Tor Browser.
+Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency benefits their anonymity~\cite{dingledine2009performance}.
 Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.
@@
 
-Usable security aims to improve the security of a system by helping the user to make good decisions~\cite{payne2008brief}.
+Usable security aims to improve the security of a system by helping the user make good decisions~\cite{payne2008brief}.
 This involves informing users about the system, communicating risks in a way that is understandable, clarifying what the security requirements are, and providing guidance with technical tasks~\cite{adams1999users}.
-Usable security research explores a variety of security concepts, such as email encryption ~\cite{whitten1999johnny}\cite{garfinkel2005johnny}, authentication~\cite{morris1979password}\cite{dhamija2000deja}\cite{suo2005graphical}, security indicators~\cite{dhamija2006phishing}\cite{akhawe2013alice}, and warnings ~\cite{schechter2007emperor}\cite{egelman2008you}.
-Our work contributes to this body of knowledge by exploring the concept of censorship circumvention.
-
-We used a cognitive walkthrough~\cite{wharton1994cognitive}\cite{cognitive-walkthrough} to inspect our interface~\cite{nielsen1994usability} .
+Usable security research explores a variety of security concepts, such as email encryption~\cite{whitten1999johnny,garfinkel2005johnny}, authentication~\cite{morris1979password,dhamija2000deja,suo2005graphical}, security indicators~\cite{dhamija2006phishing,akhawe2013alice}, and warnings~\cite{schechter2007emperor,egelman2008you}.
+Our work contributes to this body of knowledge by exploring tools for censorship circumvention.
+
+We used a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect our interface~\cite{nielsen1994usability}.
 Other usability inspection methods include heuristic evaluation, pluralistic walkthrough and feature inspection~\cite{inspection}.
@@
 Qualitative data can also be collected through focus groups, camera studies, and product surveys.
-Quantitative data can also be collected through seye tracking, clickstream analysis and AB testing~\cite{ux-methods}.
+Quantitative data can also be collected through eye tracking, clickstream analysis and A/B testing~\cite{ux-methods}.
 
 For our work, we draw on the large body of previous work in secure interaction design, computer-human interaction, and user studies.
-Work we found useful to our experiment includes research on principles for secure interaction design~\cite{yee2002user}, common problems in human-computer dialogue design~\cite{molich1990improving}, user tolerance of security delays~\cite{egelmanplease}, treating human attention as a scarce resource when to delegating tasks to users ~\cite{bohme2011security}, stopping users from doing bad things ~\cite{good2007noticing}, and getting proper user consent ~\cite{bohme2010trained}.
+Work we found useful to our experiment includes research on principles for secure interaction design~\cite{yee2002user}, common problems in human-computer dialogue design~\cite{molich1990improving}, user tolerance of security delays~\cite{egelmanplease}, treating human attention as a scarce resource when to delegating tasks to users~\cite{bohme2011security}, stopping users from doing bad things~\cite{good2007noticing}, and getting proper user consent~\cite{bohme2010trained}.
 
@@
 We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor launcher.
-We believe that this because the interface requires users know technical terms, provides a lot of freedom for error, and does not give proper feedback.
+We believe that this is because the interface requires users to know technical terms, provides a lot of freedom for error, and does not give proper feedback.
 Users in heavily censored environments will likely not succeed in connecting to Tor without outside help.

### 2017-03-06 pets2017-paper/pets2017-paper.tex
minor changes to kill orphans

@@
 {
-Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot make the correct decisions during the configuration process.
+Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot configure their connections.
+Our study shows that 79\% (363 of 458) of user attempts to connect to Tor in censored environments failed.
+We found that users were often frustrated during the process and tried options at random.
 We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure connections to Tor.
-Our study shows that 79\% (363 of 458) of user attempts to connect to Tor in censored environments failed.
-We found that users were often frustrated during the process and try options at random.
-In this paper, we describe how we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
-Tor Browser ~4.5 incorporated the changes proposed by this study.
+In this paper, we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
+Tor Browser incorporated the changes proposed by this study.
 }
@@
 The interface does not meet this goal (Table~\ref{table:participant-summary}).
-Our proposed design changes save users some time, but more changes are required to get more people to connect and to connect even faster.
+Our design changes helped more users connect to Tor in less time, but we still encourage further improvements.
 In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
@@
 We found that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-Participants averaged over 3 minutes in censored environments and over 20 minutes in heavily censored environments (Figure~\ref{fig:all-participant-edges}).
+Participants averaged over 3 minutes in censored environments (E2) and over 20 minutes in heavily censored environments (E3, Figure~\ref{fig:all-participant-edges}).
 Based on this, we recommend a thorough redesign of the interface.
@@
 Some optionally used a bridge (E1), although those who could use any bridge to connect did not deviate from the recommendation (E2) and those who needed a meek bridge chose one at random (Table~\ref{tab:attempts-bridge-proxy}).
-Seventeen percent (19 of 114) were not able to connect to Tor at all.
+Seventeen percent (19 of 114) were not able to connect to Tor.
 The most common reasons for failing to connect were not knowing whether to connect directly or configure a bridge or proxy (P73, P75, P89, P91, P106, P110), not knowing what they needed and trying to configure proxies (P74, P92, P105, P107, P113), and not knowing what to do when a recommended bridge did not work (P90, P93, P108, P111, P114).
 
-Because we hypothesized that the NEW interface would result in greater completion rates, we performed a one-tailed Pearson's chi-square test and found the results to be statistically significant ($\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$), albeit with small effect size ($\phi=0.157$).
+Our changes significantly increased success rates (one-tailed Pearson's chi-square test ; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$), helping users connect to Tor.
 
@@
 \subsubsection{Configuration Time} 
-Most participants spent a majority of their time on the progress screen (Table~\ref{table:median_time}).
+Participants spent a majority of their time on the progress screen (Table~\ref{table:median_time}).
 Their active configuration time was a small fraction of their connection time (Figure~\ref{fig:time_to_success_active_clamped}).
@@
 
-Our experiment did not directly test advanced tasks such as configuring a proxy or a custom bridge. From observing participants, we suspect they struggle with these tasks.
+Our experiment did not directly test configuring a proxy or a custom bridge. From observing participants, we suspect they struggle with these tasks.
 
@@
 \caption{
-Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. None succeeded. Here, we show P10's unsuccessful attempt. 
+Proxies were not necessary to connect to Tor, but many spent time trying to configure one when they couldn't connect. Here, we show P10's unsuccessful attempt. 
 }
@@
 They did not know if they needed a bridge or proxy, and like the participants in E2, only configured them when the direct connection failed.
-But even if the participants were able to figure out that they needed a bridge and not a proxy, the recommended bridge will not work.
 Of the participants that failed, they all tried the recommended bridge but not any others.

### 2017-03-13 pets2017-paper/pets2017-paper.tex
fixed easy rewording suggestions from shepherd

@@
 Tor~\cite{dingledine2004tor} is an anonymity network that routes Internet traffic through a series of relays 
-that make it difficult to observe sources and destinations.
+to make it difficult to observe sources and destinations.
 Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers.
@@
 
-Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users: an increase in overall users increases the anonymity set~\cite{dingledine2006anonymity}).
+Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}).
 In this paper, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
-Based on the insights from our observations, we proposed some changes to the interface (Section~\ref{sec:design}) and
-quantified how usable the interface was before and after changes (Section~\ref{sec:quantitative}).
-Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address
-limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
+Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and quantified how usable the interface was before and after changes (Section~\ref{sec:quantitative}).
+Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
 We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.
@@
 Bridges are unlisted alternative entry nodes used to connect to Tor when Tor relays are censored.
-Bridges also receive packets from the user and forward traffic to middle relays, but also may run a pluggable transport (referred to as ``transport'' for shorthand).
+Bridges also receive packets from the user and forward traffic to middle relays, but may also run a pluggable transport (referred to as ``transport'' for shorthand).
 Pluggable transports specify alternative protocols by which Tor Browser may connect to the Tor network, thereby disguising Tor traffic to make it harder to detect and block bridges.
@@
 Most bridges can be blocked by blocking their static IP addresses.
-These include bridges that run``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
+These include bridges that run ``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
 Other bridges are less susceptible to blocking because of how they work.
@@
 \subsection{Connecting to Tor} 
-There are many valid configuration settings that can be used to connect to the Tor network.
+It is important to note that there are many valid configuration settings that can be used to connect to the Tor network.
 A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that they are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).
@@
 \subsection{Testing Pipeline} 
-We performed a cognitive walkthrough to inspect the interface to anticipate potential problems and formally assess its pros and cons.
+We performed a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
 We then conducted qualitative and quantitative usability tests.
@@
 Since time spent waiting can dominate the measurement, we use configuration time to measure the time users spent actively configuring bridges and proxies.
+Connection time is always greater than the configuration time, since it includes the configuration time.
 
@@
 \label{sec:environments}
-We simulated three environments of various censorship severity (Table~\ref{tab:environments}). We chose to 
+We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
 simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
@@
 In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
-Finally, the third environment, E3, additionally blocked several of the included bridges, which meant experimenting with several different bridges---beyond the recommended ones---in order to successfully connect.
+Finally, the third environment, E3, additionally blocked several of the included bridges, which required experimenting with several different bridges---beyond the recommended option---in order to successfully connect.
 
 The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
-Rather, we designed simulated environments to require different bridges to connect to Tor.
-We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
+Rather, we designed simulated environments to have different requirements to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the different interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
 
@@
 Proxy fields also do not provide syntactic guidelines.
-See the whole list of possible errors in Appendix~\ref{states}.
+See the whole list of possible errors we identified in Appendix~\ref{states}.
 \item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails.
@@
 Transitions between these nodes denote user actions.
-For details of each end state, see Appendix~\ref{states}.
 }
@@
 
-We talk about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes. We detail what each participant did in Appendix~\ref{summary}.
+Here we report about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes.
+We detail what each participant did in Appendix~\ref{summary}.
 
@@
 \label{sec:pain-points}
-Participants spent a lot of time going back and forth on screens, looking for proxy information, and waiting for the connection to work or timeout.
+Participants spent a lot of time going back and forth on screens, looking for proxy information, and waiting for the connection to work or time out.
 We believe that the reasons for these behaviors were:\\
@@
 \subsection{Results} 
+In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
 Users should be able to connect to Tor within a few minutes.
@@
 Our design changes helped more users connect to Tor in less time, but we still encourage further improvements.
-In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
 
 We found that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-Participants averaged over 3 minutes in censored environments (E2) and over 20 minutes in heavily censored environments (E3, Figure~\ref{fig:all-participant-edges}).
+Even with the redesigned interface, participants averaged over 3 minutes in censored environments (E2) and over 20 minutes in heavily censored environments (E3, Figure~\ref{fig:all-participant-edges}).
 Based on this, we recommend a thorough redesign of the interface.
@@
 For our work, we draw on the large body of previous work in secure interaction design, computer-human interaction, and user studies.
-Work we found useful to our experiment includes research on principles for secure interaction design~\cite{yee2002user}, common problems in human-computer dialogue design~\cite{molich1990improving}, user tolerance of security delays~\cite{egelmanplease}, treating human attention as a scarce resource when to delegating tasks to users~\cite{bohme2011security}, stopping users from doing bad things~\cite{good2007noticing}, and getting proper user consent~\cite{bohme2010trained}.
+Work we found useful to our experiment includes research on principles for secure interaction design~\cite{yee2002user}, common problems in human-computer dialogue design~\cite{molich1990improving}, user tolerance of security delays~\cite{egelmanplease}, treating human attention as a scarce resource when to delegate tasks to users~\cite{bohme2011security}, stopping users from installing potentially harmful programs~\cite{good2007noticing}, and getting proper user consent~\cite{bohme2010trained}.
 
@@
 \section {Acknowledgments}
-Georg Koppen, Mike Perry, and Isabela Bagueros from Tor Project, Inc. provided valuable insights about the history of Tor launcher and internal constraints.
+We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper.
+Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
+This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{Xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
 

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Fix BibTeX capitalization issue.
This is BibTeX, Version 0.99d (TeX Live 2016/Debian)
The top-level auxiliary file: pets2017-paper.aux
Case mismatch error between cite keys Xlab and xlab
---line 190 of file pets2017-paper.aux
 : \citation{Xlab
 :               }
I'm skipping whatever remains of this command

@@
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
-This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{Xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
+This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
 

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Add my funding sources.

@@
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
-This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
+This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with support from
+Intel, the National Science Foundation,
+the Open Technology Fund through the Freedom2Connect Foundation, and from
+the US Department of State, Bureau of Democracy, Human Rights and Labor.
 

### 2017-03-14 pets2017-paper/pets2017-paper.tex
IE -> Internet Explorer.

@@
 We automatically reverted the computers to the same image at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
 We instrumented Tor Browser to log user interactions.

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Remove double "and" in a sentence.

--- 2017-03-14 pets2017-paper/pets2017-paper.tex
@@
 We automatically reverted the computers to the same image at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
 We instrumented Tor Browser to log user interactions.

### 2017-03-14 pets2017-paper/pets2017-paper.tex
Add link for VLC.

@@
 The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment.
+On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC media player~\cite{vlc} to record the screen during the experiment.
 Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
@@
 We automatically reverted the computers to the same image at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
 We instrumented Tor Browser to log user interactions.

### 2017-03-14 pets2017-paper/pets2017-paper.tex
more shepherd revisions

--- 2017-03-14 pets2017-paper/pets2017-paper.tex
@@
 In this paper, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
-Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and quantified how usable the interface was before and after changes (Section~\ref{sec:quantitative}).
+Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}).
 Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
@@
 We performed a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
+A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.
 We then conducted qualitative and quantitative usability tests.
-We believe both methods were necessary for a complete evaluation.
+We believe both methods were necessary for a complete usability evaluation.
 Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable.
-For gathering qualitative data, five users is considered to maximize the cost-benefit ratio~\cite{howmanyusers}, so we recruited five participants for each condition---multiple simulated censorship environments---in our qualitative experiment.
-Twenty users is considered to be the minimum for yielding statistically significant measurements~\cite{howmanyusers}, so we recruited twenty participants for each condition in our quantitative experiment.
-
 We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered.
 We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original Tor Launcher interface.
+
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
+We recruited five participants per experimental condition to gather qualitative data; this is considered the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
+We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
+We recruited twenty users per experimental condition to gather quantitative data; this is considered to be the minimum for yielding statistically significant measurements~\cite{howmanyusers}.
 
@@
 \begin{itemize}
-\item {\bfseries Completion rate:}  percentage of users that connect to Tor. A high completion rate is ideal. 
-\item {\bfseries Connection time:} time until a successful connection to Tor. A low connection time is ideal, though is expected to be a couple of minutes.
-\item {\bfseries Configuration time:} time users spent in Tor Launcher configuring bridges and proxies, which excludes time waiting for connections to establish or timeout.
+\item {\bfseries Completion rate:}  the percentage of users that want to connect to Tor and successfully do so.
+The higher the completion rate, the better.
+The ideal case would be that everyone is able to connect to Tor if they want to.
+Even if users do not successfully connect to Tor on previous attempts but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
+\item {\bfseries Connection time:} the amount of  time it takes a user to connect to Tor.
+The less time it takes for userss to connect, the better.
+The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to a couple minutes.
+Connection time includes this bootstrapping time and any additional time that people spend in the interface.
+\item {\bfseries Configuration time:} the amount of time users spend in the interface.
+The less time it takes for users to configure their preferences, the better.
+Configuration time is included in connection time, so it will always be less than connection time.
+We defined configuration time as any time spent on the bridge and proxy screens, since users were most likely configuring bridges and proxies.
+We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or timeout and not necessarily interacting with the interface.
 This should be as short as possible.
@@
 We measured this in two ways.
-Connection time measures how long users took to connect to Tor, which includes the time Tor takes to establish a series of relays, while the user is forced to wait.
-Since time spent waiting can dominate the measurement, we use configuration time to measure the time users spent actively configuring bridges and proxies.
+Connection time measures how long users took to connect to Tor, while configuration time to measures how long users spent actively configuring bridges and proxies.
+We use both metrics to quantify productivity since the bootstrapping time, and hence, time spent waiting for the connection to succeed or fail, can dominate the measurement.
 Connection time is always greater than the configuration time, since it includes the configuration time.
@@
 \label{sec:qualitative}
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
 We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.
@@
 The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC to record the screen during the experiment.
-Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
+On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that a participant could browse the Internet in another browser of their choice, and VLC~\cite{vlc} to record the screen during the experiment.
+Before each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
 
@@
 We started by informing the participant of the study, task, and risks (Appendix~\ref{qualitative-script}).
-After they consented to the experiment, we instructed them to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites were blocked.
-We explicitly told them to use Tor to circumvent censorship.
+After consenting to the experiment, we instructed the participant to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites were blocked.
+We explicitly tell the participant to use Tor to circumvent censorship.
 The worksheet (Appendix~\ref{participant-worksheet}) required answers from a censored website (Wikipedia) and an uncensored website (CNN).
@@
 
-After 45 minutes (or when participants finished the worksheet), we interviewed them.
-We asked both general questions (Appendix~\ref{interview-questions}) and additional participant-specific questions that verified our observations (e.g., ``the participant was selecting bridges at random'').
-We gave them~\$30 for their time.
+After 45 minutes (or when participants finished the worksheet), we interviewed the participant about their experience.
+We asked general questions (Appendix~\ref{interview-questions}) and participant-specific questions to verify any observations (e.g., ``the participant was selecting bridges at random'').
+After the interview, we allowed the participant to ask any questions about the experiment, then gave them~\$30 for their time.
 
@@
 \begin{itemize}
-\item {\bfseries A non-existent mental model:} Participants found terms in the interface confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}).
+\item {\bfseries Unfamiliar concepts:} Participants found technical terms (i.e.
+relay, bridge, proxy, censor, ISP) confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}).
 \end{itemize}
@@
 \label{sec:design} 
-
-We limited design changes to ones that do not require infrastructural changes, addressed observed pain points, and adhered to our design considerations (Figure~\ref{fig:new-interface}).
+We redesigned the interface according to usability best practices while addressing the pain points found in our qualitative usability study.
+We drafted a list of design considerations, prioritized the pain points to address, and iteratively made changes to the interface to get to our final design (Figure~\ref{fig:new-interface}).
+
+\subsection {Design Considerations}
+
+Here are some of the design considerations we considered as constraints while designing our interface. Designing an interface for Tor had unique challenges: \\
+
+\begin{itemize}
+\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks.
+While we could help users by automating configuration settings, this would involve probing network configurations, which may alert authorities to Tor usage.
+Taking this risk without proper consent is not ethical.
+
+\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions.
+Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.
+
+\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor. We should allow users to leverage local information to reduce their risk.
+
+\item{\bfseries Maintenance constraints}: Network environments change all the time. Keeping up with how each country censors and pushing changes before the affected users connect to Tor is difficult.
+
+\item{\bfseries Financial constraints}: Leveraging harder-to-block ``meek'' bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
+\end{itemize}
+
+\subsection{Changes Made} 
+We limited design changes to ones that do not require infrastructural changes, addressed observed pain points, and adhered to our design considerations.
 
@@
 
-\subsection{Changes Made} 
 We eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and eliminated the proxy screen by simulating auto-detection for proxies.
@@
 
-\subsection {Design Considerations}
-
-Here are some of the justifications for why we made conservative, front-end only design changes: \\
-
-\begin{itemize}
-\item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks.
-While we could help users by automating configuration settings, this would involve probing network configurations, which may alert authorities to Tor usage.
-Taking this risk without proper consent is not ethical.
-
-\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions.
-Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.
-
-\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor. We should allow users to leverage local information to reduce their risk.
-
-\item{\bfseries Maintenance constraints}: Network environments change all the time. Keeping up with how each country censors and pushing changes before the affected users connect to Tor is difficult.
-
-\item{\bfseries Financial constraints}: Leveraging harder-to-block ``meek'' bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
-\end{itemize}
-
 Other beneficial changes could have been made, if we did not consider these constraints.
@@
 \label{sec:quantitative}
-To confirm prior pain points and user behaviors, as well as to validate our proposed design improvements, we logged and quantified user interactions as part of a followup experiment.
+We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
+We confirm prior stumbling points and user behaviors and validate our proposed design improvements.
 
@@
 We automatically reverted the computers to the same image at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
 We instrumented Tor Browser to log user interactions.
@@
 \item {\bfseries Assume users do not know technical concepts.} Users should not need to know what a relay, bridge, proxy, or transport is to connect to Tor. 
-\item {\bfseries Explain why users need to make decisions.} Knowing why they are required to perform a task will make them more cooperative.
-For instance, users currently choose transports because different subsets of transports work for different countries, and Tor does not track users' locations.
+\item {\bfseries Explain why users need to make decisions.} Letting users know why they are required to perform a task may make them more sympathetic to  performing that task.
+For instance, users who need a bridge must choose one manually because different ones work in different countries and Tor does not track users' locations.
 \item {\bfseries Leverage user knowledge.} Users know what country they are connecting from, their level of acceptable risk, and what they are using Tor for.
@@
 
-We recommend implementing some design changes right away to resolve some problems, and consider additional ways to make connecting to Tor easier. \\
+We ourselves did not follow the above advice, due to design constraints.
+But seeing as how our redesigned interface still did not have an ideal success rate, connection time, or configuration time, we think that alternative designs that leverage user input and automation should be considered.
+We recommend implementing some design changes right away initially to improve on the current design, then consider implementing our advice above.
+\\
 
@@
 \item{\bfseries Naive automation:} a scheme that chooses bridges, waits for timeouts, and tries another bridge so users do not need to do this themselves.
+We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would have had to take.
 \item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwidth constraints.
+We call this ``smart'' automation because this scheme involves communication with Tor servers, which choose a bridge that will work for the user on the first try.
 \end{itemize}
@@
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
-This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with support from
-Intel, the National Science Foundation,
-the Open Technology Fund through the Freedom2Connect Foundation, and from
-the US Department of State, Bureau of Democracy, Human Rights and Labor.
+This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{Xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
 

### 2017-03-14 pets2017-paper/pets2017-paper.tex

@@
 The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that a participant could browse the Internet in another browser of their choice, and VLC~\cite{vlc} to record the screen during the experiment.
-Before each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
+On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC media player~\cite{vlc} to record the screen during the experiment.
+Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
 
@@
 We automatically reverted the computers to the same image at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, IE, and VLC, and Tor Browser 5.0.3 or a modified version of Tor 5.0.3 with our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
+Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
 We instrumented Tor Browser to log user interactions.
@@
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
-This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{Xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with funding from Intel and the National Science Foundation.
+This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with support from
+Intel, the National Science Foundation,
+the Open Technology Fund through the Freedom2Connect Foundation, and from
+the US Department of State, Bureau of Democracy, Human Rights and Labor.
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Reorder abstract per shepherd request.

@@
 {
-Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will likely not be able to connect to Tor because they cannot configure their connections.
-Our study shows that 79\% (363 of 458) of user attempts to connect to Tor in censored environments failed.
+Although Tor has state-of-the art anti-censorship measures, users in heavily censored environments will not be able to connect to Tor if they cannot configure their connections.
+We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure connections to Tor.
+Our study shows that 79\% (363 of 458) of user attempts to connect to Tor in simulated censored environments failed.
 We found that users were often frustrated during the process and tried options at random.
-We perform the first usability evaluation of Tor Launcher, the graphical user interface (GUI) that Tor Browser uses to configure connections to Tor.
-In this paper, we measured potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
+In this paper, we measure potential usability issues, discuss design constraints unique to Tor, and provide recommendations based on what we learned to help more users connect to Tor while reducing the time they take to do so.
 Tor Browser incorporated the changes proposed by this study.

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Unredact "<redacted>".

@@
 \label{qualitative-recruitment}
-We are recruiting participants for an in-person research study at <redacted>. %the University of California, Berkeley. 
+We are recruiting participants for an in-person research study at the University of California, Berkeley. 
 You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. 
@@
 \label{qualitative-prescreening}
-We are recruiting participants for an in-person research study at the <redacted>. %University of California, Berkeley. 
+We are recruiting participants for an in-person research study at the University of California, Berkeley. 
 You will need to come in to our lab and perform tasks on a computer for an hour or less. You will be compensated \$30 for participating. No special knowledge and no technical experience is required.\\
@@
 \item{Please select when you are available. We will assign you an hour experiment time slot during one of those times.}
-\item{I am able to provide my own transportation to the <redacted> %University of California, Berkeley 
+\item{I am able to provide my own transportation to the University of California, Berkeley 
 campus.}
@@
 \label{quantitative-recruitment}
-We are recruiting up to 40 participants for a user study at <redacted>. %UC Berkeley. 
+We are recruiting up to 40 participants for a user study at UC Berkeley. 
 The experiment will involve basic Internet browsing tasks. You are not eligible if you have participated in our previous sessions.\\
@@
 \indent Duration: 1 hour \\
-\indent Where: <redacted> \\ %Xlab at Hearst Memorial Gymnasium\\
+\indent Where: Xlab at Hearst Memorial Gymnasium\\
 
@@
 
-If you are interested: 1. Email <redacted> %lnl@berkeley.edu 
+If you are interested: 1. Email lnl@berkeley.edu 
 with the sessions you are able to attend. We will confirm your participation and assign you a session. 
-2. Come to <redacted> %Xlab 
+2. Come to Xlab 
 at the appointed time for the experiment.
@@
 
-This survey is part of a research project being conducted by the <redacted>. %University of California, Berkeley. 
-If you have any questions about your rights or treatment as a research participant in this study, please contact the <redacted>'s %University of California at Berkeley's 
+This survey is part of a research project being conducted by the University of California, Berkeley. 
+If you have any questions about your rights or treatment as a research participant in this study, please contact the University of California at Berkeley's 
 Committee for Protection of Human Subjects at 510-642-7461, or email 
-<redacted>. %subjects@berkeley.edu. 
+subjects@berkeley.edu. 
 If you agree to participate, please click Next below.\\

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Fix occurences of "Fig ~\ref".

@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure ~\ref{fig:old-bridge-help}). }
+	\caption{The second bridge screen (B2). Users select a bridge here. ``Help'' directs to bridge help screen (Figure~\ref{fig:old-bridge-help}). }
 	\label{fig:old-bridge-settings}
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure ~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
+	\caption{The proxy question screen (P1). ``Yes'' goes to the proxy settings screen (Figure~\ref{fig:old-proxy-yes}). and ``no'' starts a connection.}
 	\label{fig:old-proxy}

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Put references in Figure 1 and Figure 2 in order.

@@
 Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
-Tor Browser is bundled with a graphical configuration interface, Tor Launcher (Figure~\ref{fig:old-interface}), which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor.
+Tor Browser is bundled with a graphical configuration interface, Tor Launcher, which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor.
 Of course, these configuration options are only effective if users understand how to correctly use them.
@@
 
+A connection to Tor involves many interacting components,
+illustrated in Figure~\ref{fig:topology}.
+It may involve a proxy and a bridge,
+possibly in the presence of a censor.
+
 Technically, a proxy is any computer or service that allows its users to make indirect network connections to other services.
@@
 However, in this paper and more generally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
-Figure~\ref{fig:topology} illustrates the potential network components involved in connecting to the Tor network.
 
@@
 For convenience, bridges are grouped by which transport they run.
+
+Tor Launcher is the graphical user interface for configuring
+an optional proxy, bridge, and transport
+prior to initiating a connection to the Tor network.
+Figure~\ref{fig:old-interface} shows the various screens
+of Tor Launcher at the time we began our research.
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Improve the specific meaning of "proxy".

@@
 
-Technically, a proxy is any computer or service that allows its users to make indirect network connections to other services.
+The word ``proxy'' has a specific meaning in the context of a Tor connection.
+Generally, a proxy is any computer or service that allows its users to make indirect network connections to other services.
 In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy.
-However, in this paper and more generally, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
+However, in this paper, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
De-ligature my email address.
I learned the hard way on another paper that for some people,
copy-pasting from the PDF causes them to send mail to the nonexistent
address "ﬁﬁeld@cs.berkeley.edu" (where the "fi" are replaced with a
Unicode "ﬁ" ligature).
Add comma in "University of California Berkeley".

@@
 
-  \affil[1]{University of California Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
-
-  \affil[2]{University of California Berkeley, E-mail: \mbox{fifield@cs.berkeley.edu}}
-
-  \affil[3]{University of California Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
-
-  \affil[4]{University of California Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
-
-  \affil[5]{University of California Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
-
-  \affil[6]{University of California Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
+  \affil[1]{University of California, Berkeley, E-mail: \mbox{lnl@cs.berkeley.edu}}
+
+  \affil[2]{University of California, Berkeley, E-mail: \mbox{f{}if{}ield@cs.berkeley.edu}}
+
+  \affil[3]{University of California, Berkeley, E-mail: \mbox{nmalkin@cs.berkeley.edu}}
+
+  \affil[4]{University of California, Berkeley, E-mail: \mbox{ganesh.v@berkeley.edu}}
+
+  \affil[5]{University of California, Berkeley and International Computer Science Institute, E-mail: \mbox{egelman@cs.berkeley.edu}}
+
+  \affil[6]{University of California, Berkeley, E-mail: \mbox{daw@cs.berkeley.edu}}
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Say where B1 skips ahead to (P1).
Minor edits through background and methodology.

@@
 Pluggable transports specify alternative protocols by which Tor Browser may connect to the Tor network, thereby disguising Tor traffic to make it harder to detect and block bridges.
+When a bridge is used, it takes the place of the guard relay.
 For convenience, bridges are grouped by which transport they run.
@@
 Most bridges can be blocked by blocking their static IP addresses.
-These include bridges that run ``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
+These include bridges that run the ``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
 Other bridges are less susceptible to blocking because of how they work.
 Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks.
-The bridges that are accessible in each country vary.
+The bridges and transports that are accessible in each country vary.
 Figure~\ref{fig:old-bridge-combobox} shows the bridge and transport options at the time of our study.
@@
 \subsection{Connecting to Tor} 
-It is important to note that there are many valid configuration settings that can be used to connect to the Tor network.
+It is important to note that there are many valid configuration settings that can be used to connect to the Tor network. A user may or may not need a combination of proxy and bridge.
 A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that they are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).
@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips it.}
+	\caption{The first bridge screen (B1). ``Yes'' leads to a bridge configuration screen (Figure~\ref{fig:old-bridge-settings}) and ``no'' skips to P1.}
 	\label{fig:old-bridge}
@@
 \subsection{Testing Pipeline} 
-We performed a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
+We began by performing a cognitive walkthrough~\cite{wharton1994cognitive,cognitive-walkthrough} to inspect the interface to anticipate potential problems and formally assess its pros and cons.
 A cognitive walkthrough is a formal method of inspection performed by researchers without any user involvement.

### 2017-03-15 pets2017-paper/pets2017-paper.tex
Unsplit sentence per shepherd's comment.

@@
 
-Our changes significantly increased success rates (one-tailed Pearson's chi-square test ; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$), helping users connect to Tor.
+Our changes significantly increased success rates (one-tailed Pearson's chi-square test; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$).
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
expanded introduction; finished addressing intro comments

@@
 Tor Browser is bundled with a graphical configuration interface, Tor Launcher, which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor.
-Of course, these configuration options are only effective if users understand how to correctly use them.
-Thus, we performed a usability study wherein we simulated various censorship environments in order to examine the effectiveness of Tor Launcher and how it could be improved.
+Of course, these options are only effective if users understand how to use them.
+Thus, we performed a usability study to examine the effectiveness of Tor Launcher and how it could be improved.
 
 Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}).
-In this paper, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
+Tor does not collect user interaction data from its real users, so we believe that usability testing research is critical to help users in heavily censored regimes and increase user adoption.
+In this paper, we: \\
+
+\begin{itemize}
+\item{Perform a qualitative and quantitative usability evaluation of Tor Launcher 5.0.3  under simulated censorship environments to determine why and how much it is or is not usable.}
+\item{Contribute design changes that statistically significantly improve users' likelihood of connecting to Tor and also statistically significantly reduces the amount of time users take to connect.} 
+\item{Provide recommendations beyond design changes to improve Tor Launcher, such as leveraging user input (requires research) and building an automated connection scheme (requires Tor-infrastructure work).}
+\end{itemize}
+
+Specifically, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
 Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}).

### 2017-03-15 pets2017-paper/pets2017-paper.tex
wordsmith background (section 2) for formatting; time for really pretty pages

@@
 \label{sec:background}
-This section discusses how to connect to Tor and what network components are involved.
+This section discusses the network components are involved in connecting to Tor and how users can connect to Tor in various ways.
+An understanding of the network components or the various connection options are not required to understand our work, but we refer to these terms and methods throughout the paper.
 
@@
 illustrated in Figure~\ref{fig:topology}.
-It may involve a proxy and a bridge,
-possibly in the presence of a censor.
+In the presence of a local firewall and censor, it may involve a proxy and a bridge.
 
 The word ``proxy'' has a specific meaning in the context of a Tor connection.
-Generally, a proxy is any computer or service that allows its users to make indirect network connections to other services.
+Generally, a proxy is any computer or service that allows users to make indirect connections to other services.
 In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy.
@@
 
-Users can configure a bridge by choosing a transport (Figure~\ref{fig:old-bridge-combobox}), which selects the group of bridges that use that transport.
-If the built-in bridges do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb} that provide the necessary information.
+Users can configure a bridge by choosing a transport, which selects the group of bridges that use that transport.
+For instance, choosing the ``obfs3'' option in Figure~\ref{fig:old-bridge-combobox} will select a group of bridges that peform the obfs3 transport protocol as okay to use, and the user will be assigned one of these bridges as their guard relay.
+If these built-in options do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb}.
 Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}).

### 2017-03-15 pets2017-paper/pets2017-paper.tex
expand on methodology, switch setup and metrics sections, wordsmith to look pretty

@@
 \section{Methodology} 
-This section discusses the process we used to evaluate the usability of Tor Launcher.
+This section discusses the usability testing process used to evaluate Tor Launcher, the simulated censorship environments we used to require users to configure different network components to connect to Tor, and what our evaluation metrics  we collected to deem the interface usable or not usable.
 
@@
 We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered.
-We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original Tor Launcher interface.
+We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.
 
@@
 
+\subsection{Experimental Setup}
+\label{sec:environments}
+We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
+simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
+Re-routing participant traffic through other countries' networks also may introduce unforseen risks to the participants out of our control and performing hundreds of connections in short intervals during expeirments may draw unnecessary attention to Tor use in that country.
+
+\begin{table}[t]
+\centering
+\begin{tabular}{r c c c}
+& E1 & E2 & E3 \\
+% \noalign{\hrule}
+websites blocked & X & X & X \\
+public relays blocked & & X & X \\
+default bridges blocked & & & X \\
+\end{tabular}
+\caption{
+Summary of our simulated censorship environments.
+E1 only requires users to connect directly;
+E2 requires users to connect with a built-in bridge;
+and E3 requires users to connect with a specific type of built-in bridge
+or a custom bridge.
+E2's blocking is a superset of E1's;
+similarly, E3's is a superset of E2's.
+}
+\label{tab:environments}
+\end{table}
+
+The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
+Rather, we designed simulated environments to have different requirements to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the different interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
+
+In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed).
+In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
+Finally, the third environment, E3, additionally blocked several of the included bridges, which required experimenting with several different bridges---beyond the recommended option---in order to successfully connect.
+
+We used Tor Browser~5.0.3, the most recent stable release at the time~\cite{torbrowser-503}.
+There were new releases during the experiments, but we used the same version throughout to not introduce confounding factors.
+We conducted our experiments on Windows machines.
+To create the environments, we used Windows Firewall rules to block the IP addresses of public Tor relays and default bridges, and the Windows hosts file to block websites by mapping domain names to localhost.
+
 \subsection{Evaluation Metrics}
 \label{sec:eval}
-We use the following industry-standard~\cite{albert2013measuring} metrics to determine if the launcher is usable: \\
+We use the following three industry-standard~\cite{albert2013measuring} usability metrics to quantify how easily users completed their task and if they were productive with their time: \\
 
@@
 We defined success as a binary metric that is true if a user connected to Tor and false if a user did not.
+We consider this to be the most important usability metric, as this directly measures if users could connect to Tor.
+
 Task time is a supplemental usability metric that measures user productivity during the task.
@@
 Connection time is always greater than the configuration time, since it includes the configuration time.
-
-\subsection{Experimental Setup}
-\label{sec:environments}
-We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
-simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{r c c c}
-& E1 & E2 & E3 \\
-% \noalign{\hrule}
-websites blocked & X & X & X \\
-public relays blocked & & X & X \\
-default bridges blocked & & & X \\
-\end{tabular}
-\caption{
-Summary of our simulated censorship environments.
-E1 only requires users to connect directly;
-E2 requires users to connect with a built-in bridge;
-and E3 requires users to connect with a specific type of built-in bridge
-or a custom bridge.
-E2's blocking is a superset of E1's;
-similarly, E3's is a superset of E2's.
-}
-\label{tab:environments}
-\end{table}
-
-In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed).
-In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
-Finally, the third environment, E3, additionally blocked several of the included bridges, which required experimenting with several different bridges---beyond the recommended option---in order to successfully connect.
-
-The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
-Rather, we designed simulated environments to have different requirements to connect to Tor.
-We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the different interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
-
-We used Tor Browser~5.0.3, the most recent stable release at the time~\cite{torbrowser-503}.
-There were new releases during the experiments, but we used the same version throughout to not introduce confounding factors.
-We conducted our experiments on Windows machines.
-To create the environments, we used Windows Firewall rules to block the IP addresses of public Tor relays and default bridges, and the Windows hosts file to block websites by mapping domain names to localhost.
+We consider connection time and configuration time to be equally important in measuring user productivity.
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
wordsmith qualitative section to be pretty; shortened/reworded the procedure

@@
 Ages ranged from 20 to~62 years ($\mu = 30.5$, $\sigma = 13.5$).
-Our age statistics omit one participant who declined to disclose.
+Our age statistics omit one participant who declined to disclose their age.
 All of our participants had at least some college education.
-Twelve were new users and 4 had previously used Tor Browser in some capacity.
+Twelve were new users and four had previously used Tor Browser in some capacity.
 
@@
 
-We distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
+As we performed the experiments, we distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
 We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.
@@
 \subsection{Procedure} 
-We ran the experiment in a meeting room at UC Berkeley.
-The room had a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we downloaded and installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer so that participants could browse the Internet in another browser of their choice, and VLC media player~\cite{vlc} to record the screen during the experiment.
-Prior to each participant, we ran a script on the computer that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
-
-Each one-hour session was run by at least two researchers.
-We started by informing the participant of the study, task, and risks (Appendix~\ref{qualitative-script}).
-After consenting to the experiment, we instructed the participant to visit sample censored and uncensored websites in a non-Tor browser to illustrate that some sites were blocked.
-We explicitly tell the participant to use Tor to circumvent censorship.
-The worksheet (Appendix~\ref{participant-worksheet}) required answers from a censored website (Wikipedia) and an uncensored website (CNN).
-We chose Wikipedia and CNN because they were popular websites~\cite{alexa} and their likely familiarity would make the task seem less intimidating.
+We ran the experiments in a small room with a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
+On a clean computer, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment.
+We ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen before each participant.
+
+We get informed consent by talking about the study, task, and risks (Appendix~\ref{qualitative-script}).
+Then the participant visited sample websites in a non-Tor browser to illustrate that some sites were blocked and instruct them to use Tor to circumvent censorship.
+Their task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visitng a censored website (Wikipedia) and an uncensored website (CNN).
+We chose Wikipedia and CNN because their likely familiarity~\cite{alexa}.
 After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.

### 2017-03-15 pets2017-paper/pets2017-paper.tex
redesign section expanded and formatted

@@
 
-Here are some of the design considerations we considered as constraints while designing our interface. Designing an interface for Tor had unique challenges: \\
+Designing an interface for Tor had unique challenges: \\
 
@@
 
+We kept the user involved so that they explicitly start a connection to Tor.
+We chose not to leverage user inputs such as their location, risk, or other preferences due to active and passive adversaries.
+We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to increase the chances of Tor adoption our design changes.
+
 \subsection{Changes Made} 
-We limited design changes to ones that do not require infrastructural changes, addressed observed pain points, and adhered to our design considerations.
+In this section, we highlight and explain the speific design changes we made to address the observed pain points while adhering to the design considerations. We: \\
 
@@
 
-We eliminated the bridge and proxy questions from Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy} and eliminated the proxy screen by simulating auto-detection for proxies.
-We added a screen to summarize the settings before connecting and added indicators to the progress bar that showed what component was unreachable.
-We switched the proxy and bridge screens so that they are in a topologically sequential order.
-We clarified that configuration options were for heavily censored environments and gave a secondary bridge recommendation for heavily censored users.
-
-Other beneficial changes could have been made, if we did not consider these constraints.
+\begin{itemize}
+\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and ~\ref{fig:new-progress})  to encourage users to read instructions.}
+\item{centered the text to make the design compatible for left to right and right to left languages.}
+\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies to not optionally configure them.}
+\item{added a status bar on the proxy and bridge screens (Figure~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge}, and~\ref{fig:new-bridge-combobox}) to hint at future tasks.}
+\item{reordered proxy and bridge screens (Figures ~\ref{fig:new-proxy} and ~\ref{fig:new-nobridge}) in a topologically sequential order.
+This hints that proper proxy settings (if required, to set one up properly, and if not required, to be set up properly or not selected) are necessary to reach bridges.}
+\item{eliminated the bridge and proxy questions (Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) to reduce the number of screens.}
+\item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question.
+In theory, this can be done locally without leacking information onto the network or for infrastructural changes.}
+\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the of the bridge question screen (Figure~\ref{fig:old-bridge}).}
+\item{gave a recommendation to use one of the three meek-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended obfs3-transport bridges were unreachable, which happens in heavily censored real environments and our simulated enviornment E3.}
+\item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
+\item{added indicators on the progress screen (Figure~\ref{fig:new-progress}) that visualized what components are trying to be reached, and in the case of failure, showed which component was unreachable.
+This was to help users understand what was going on during  connection and to help troubleshoot their configuration.}
+\end{itemize}
+
+Our interface was made to test changes in a laboratory testing.
+We acknowledge that our version would need refining (aligning text properly, using higher quality visual assets, etc.) before deployment.
 
@@
 We encourage more usability studies on security tools in general as well as other Tor applications, as they have the potential to create user growth, help user retention, and prevent user frustration.
-Tor Browser version~4.5 incorporated  changes based on our work.
+Tor Browser version~5.4.5 incorporated  changes based on our work.
 We also talked with Tor developers about automating connections to Tor, and they are now considering this as future work.

### 2017-03-15 pets2017-paper/pets2017-paper.tex
wordsmith procedure and recruitment for formatting

@@
 \subsection{Recruitment}
-We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for the recruitment materials).
+We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for recruitment materials).
 We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.
 
-Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or did not interact with the interface.
+Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or downloaded another version of Tor Browser to use during the experiment.
 One participant did not report their demographics, but we still used their data.
-Of the remaining 113, 44.2\% identified as male, 54.0\% identified as female, and 1.8\% identified as neither.
+Of the remaining 113, 44.2\% identified as male, 54.0\% as female, and 1.8\% as neither.
 They were between 18 and~68 years old ($\mu = 28.2$, $\sigma = 12.3$) and highly educated (84.1\% had at least a college education).
@@
 \subsection{Procedure}
-We ran our experiment at the Xlab~\cite{xlab}, an experimental social science laboratory.
-The room had 36 workstations with identical Windows~7 laptops.
-Workstation partitions discouraged participants from looking at other screens.
-We automatically reverted the computers to the same image at the beginning of each session.
-Before each session, we ran a script that downloaded the necessary software (Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 with or without our proposed UI changes), set up one of the three simulated environments (E1, E2, or E3), and started the computer screen recording.
-We instrumented Tor Browser to log user interactions.
-We manually assigned each computer to one of the six interface--environment combinations in a way that evenly distributed experimental conditions throughout the room.
-
-We assigned participants to a simulated censorship environment combination at random by assigning them to a computer at random.
-We informed participants that they were in a simulated censorship environment, informed them that Tor browser was necessary to circumvent censorship, and pointed out that Tor was installed for them on the computer (Appendix~\ref{quantitative-script}).
-We asked them to complete a worksheet that required visiting a censored site (Wikipedia) and explicitly reminded them to use Tor to do so (Appendix~\ref{summative-worksheet}).
-Before the experiment began, we reminded them that we were recording their screens, answered any questions, then gave them 40 minutes to complete the task.
-
-Researchers maintained minimal interactions with the participants after instructions, only answering logistical questions.
-After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we answered any additional questions and gave them \$30.
+We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory.
+Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens.
+At the beginning of each session, we used a script to revert the computers to a clean image, download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes ), set up one of the three simulated environments (E1, E2, or E3), and started recording the computer screen.
+We manually assigned interface--environment combinations to each computer.
+
+We receive informed consent after talking about the study (Appendix~\ref{quantitative-script}) and instruct participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}), and gave them 40 minutes to complete the task.
+Researchers maintained minimal interactions with the participants.
+After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), gave them \$30 for their time.
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
move the redesigned interface figure up a page.
Uniform capitalization in lab acronyms.

@@
 
+\begin{figure*}
+\centering
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavy censorship.}
+	\label{fig:new-first}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The proxy screen (P). The interface locally detects a proxy and automatically populates the fields as necessary.}
+	\label{fig:new-proxy}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and eliminated the bridge question screen.}
+	\label{fig:new-nobridge}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields are hidden until the custom option is chosen.}
+	\label{fig:new-bridge}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{This dropdown menu remains the same (see Figure~\ref{fig:old-bridge-combobox}).}
+	\label{fig:new-bridge-combobox}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The bridge help screen (BH) remains the same as well.}
+	\label{fig:new-bridge-help}
+\end{subfigure}
+~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The summary screen (S) summarizes the configuration. This example configuration is connecting directly to Tor.}
+	\label{fig:new-summary}
+\end{subfigure}
+~~~~~~~~~~~~~~~~~~~~~~~~~
+\begin{subfigure}[b]{0.30\textwidth}
+	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
+	\centering\captionsetup{width=1.5\linewidth}%
+	\caption{The progress bar (Pr) shows the status of each component in the connection as the connection is made.}
+	\label{fig:new-progress}
+\end{subfigure}
+\caption{
+A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
+}
+\label{fig:new-interface}
+\end{figure*}
+
 \subsection {Design Considerations}
@@
 In this section, we highlight and explain the speific design changes we made to address the observed pain points while adhering to the design considerations. We: \\
-
-\begin{figure*}
-\centering
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-first.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The first screen (F) with reduced, alternative text. We said configuration was required for heavy censorship.}
-	\label{fig:new-first}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-proxyYES.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The proxy screen (P). The interface locally detects a proxy and automatically populates the fields as necessary.}
-	\label{fig:new-proxy}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge screen (B). We give users the options to connect with or without a bridge all on one screen, and eliminated the bridge question screen.}
-	\label{fig:new-nobridge}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-default.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge menu and additional advice shows up when the corresponding option is chosen. The custom bridge input fields are hidden until the custom option is chosen.}
-	\label{fig:new-bridge}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeSettings-combobox.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{This dropdown menu remains the same (see Figure~\ref{fig:old-bridge-combobox}).}
-	\label{fig:new-bridge-combobox}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-bridgeHelp.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH) remains the same as well.}
-	\label{fig:new-bridge-help}
-\end{subfigure}
-~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-summary.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The summary screen (S) summarizes the configuration. This example configuration is connecting directly to Tor.}
-	\label{fig:new-summary}
-\end{subfigure}
-~~~~~~~~~~~~~~~~~~~~~~~~~
-\begin{subfigure}[b]{0.30\textwidth}
-	\includegraphics[width=\textwidth]{screenshots/NEW-progress.png}
-	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The progress bar (Pr) shows the status of each component in the connection as the connection is made.}
-	\label{fig:new-progress}
-\end{subfigure}
-\caption{
-A redesigned version of the Tor Browser 5.0.3 Tor Launcher GUI. Screens are in the order that they appear. 
-}
-\label{fig:new-interface}
-\end{figure*}
 
@@
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
-This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (secure computing research for users' benefit)~\cite{scrub}, and BLUES (Berkeley laboratory for usable and experimental security)~\cite{blues} laboratories, with support from
+This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (Secure Computing Research for Users' Benefit)~\cite{scrub}, and BLUES (Berkeley Laboratory for Usable and Experimental Security)~\cite{blues} laboratories, with support from
 Intel, the National Science Foundation,

### 2017-03-15 pets2017-paper/pets2017-paper.tex
finished up quantitative section todos

--- 2017-03-15 pets2017-paper/pets2017-paper.tex
@@
 In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
-Users should be able to connect to Tor within a few minutes.
-The interface does not meet this goal (Table~\ref{table:participant-summary}).
-Our design changes helped more users connect to Tor in less time, but we still encourage further improvements.
-
-We found that 63\% (72 of 114) of first attempts to connect failed and 79\% (363 of 458) of total attempts to connect failed.
-Even with the redesigned interface, participants averaged over 3 minutes in censored environments (E2) and over 20 minutes in heavily censored environments (E3, Figure~\ref{fig:all-participant-edges}).
-Based on this, we recommend a thorough redesign of the interface.
+As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time.
+However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3).
+Figure~\ref{fig:all-participant-edges}) summarizes each partipant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time.
+Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.
 
@@
 
+Our changes significantly increased success rates (one-tailed Pearson's chi-square test; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$).
+
+Table~\ref{tab:attempts-bridge-proxy} shows participants' connections to Tor.
+As reported in the first two columns, most participants who did not need to configure anything (E1) didn't, although some optionally used a bridge.
+Participants who needed any bridge (E2) all used the recommended bridge.
+Participants who needed a meek-bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and did not connect to Tor.
+
 %table
@@
 \caption{
-A table showing how people connected to Tor.
+A table showing participants' connections to Tor.
 Note that none used the flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
@@
 
-Most participants could connect if they did not need to configure anything (E1) or used the recommended settings (E2).
-If some bridges were blocked (E3), people could not figure it out, or took a long time to do so (Table~\ref{table:participant-summary}).
-Some optionally used a bridge (E1), although those who could use any bridge to connect did not deviate from the recommendation (E2) and those who needed a meek bridge chose one at random (Table~\ref{tab:attempts-bridge-proxy}).
 Seventeen percent (19 of 114) were not able to connect to Tor.
 The most common reasons for failing to connect were not knowing whether to connect directly or configure a bridge or proxy (P73, P75, P89, P91, P106, P110), not knowing what they needed and trying to configure proxies (P74, P92, P105, P107, P113), and not knowing what to do when a recommended bridge did not work (P90, P93, P108, P111, P114).
-
-Our changes significantly increased success rates (one-tailed Pearson's chi-square test; $\chi^2 = 2.808$, $\mbox{df} = 1$, $p < 0.047$, albeit with small effect size $\phi=0.157$).
 
@@
 \subsubsection{Connection time} 
-The simulated censorship environment, and therefore, the difficulty of the configuration, was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
-Participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect (Figure~\ref{fig:time_to_success_clamped}).
-The more time spent, the less likely that participants were to succeed (Figure~\ref{fig:time_to_success_ecdf}).
-Participants generally kept trying the same options over and over, or gave up and waited for the experiment to be over.
-
 Our changes significantly reduced connection time (one-tailed Mann--Whitney; $ Z = -1.84$, $p < 0.0328$, $r= 0.172$).
 We used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right-tailed, and right-censored.
-With the advice to only configure for heavily censored settings, participants tried a connection more quickly without trying to configure anything.
-This worked for users who did not need one (E1), but did not save users who needed a bridge (E2) much time.
-People still tried to connect with the recommended bridge before trying another one, but we suspect that the advice to ``try a meek-bridge if the recommended one did not work'' saved users who could not use certain bridges (E3) a significant amount of time.
+
+However, the simulated censorship environment (and therefore, the difficulty of the configuration), was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+Figure~\ref{fig:time_to_success_clamped} shows that participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
+It would be ideal to have an interface that allows users to connect in the similar amounts of time, no matter what their configuration requirements; neither the OLD or NEW interface achieves this.
+
+Figure~\ref{fig:time_to_success_ecdf} shows a cumulative distribution of connection times.
+Everyone in E1 was able to connect right away; particpants with the NEW interface doing so faster than participiants with the OLD interface.
+Most participants in E2 were able to connect right away; participants with the NEW interface and OLD interface connecting in a similar distribution of time.
+Participants in E3 took various amount of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.
 
@@
 \caption{
-Cumulative success rates over time.
+Cumulative success rates over time. Those who did not connect were assigned an arbitratily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution. 
 }
@@
 \subsubsection{Configuration Time} 
-Participants spent a majority of their time on the progress screen (Table~\ref{table:median_time}).
-Their active configuration time was a small fraction of their connection time (Figure~\ref{fig:time_to_success_active_clamped}).
-We see that the time spent bootstrapping the connection to Tor dominated the measurements of participants who connected without configuring anything (E1), and waiting for the timeout error when Tor was blocked dominated the measurements for participants who did not try the correct configuration on the first try (E2, E3).
-We noticed that participants who configured components incorrectly searched for help in another browser while waiting for their connection to time out.
-Participants should not need to search for help outside the interface during configuration.
-
 Our changes significantly reduced configuration time (one-tailed Mann--Whitney; $Z = -3.28$, $p < 0.0005$, $r = 0.307$).
 Again, we used a one-tailed Mann--Whitney test because the distributions were non-normal, heavily right-tailed, and right-censored.
-Participants were less likely to spend time unnecessarily configuring proxies (Table~\ref{table:median_time}) and trying different bridges.
-We believe that this is reflective of how most users would not require a proxy to connect to Tor, and suspect that most real users spend time configuring proxies when they need a bridge instead.
+
+Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time were generally a small fraction of their connection time.
+E1 participants' configuration time was a small fraction of connection time because because they generally chose a configuration that successfully connected to Tor right away, and the time spent bootstrapping the connection to Tor dominated the connection time.
+E3 participants' configuration time was significantly less than their connection time they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts.
+E2, participants' configuration time was a a modest amount of their connection time, due to the combination of reasons that affected participants in E1 and E3.
+
+Due to the mentions above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}).
+We defined configuration time as a partcipant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen.
+However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.
+
+\begin{figure}[t]
+\centering
+\includegraphics{time_to_success_active_clamped}
+\caption{
+Configuration times are much shorter than connection times, which means that most of the time was spent waiting for the connection to establish or time out.
+Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
+}
+\label{fig:time_to_success_active_clamped}
+\end{figure}
 
@@
 \end{table}
-
-\begin{figure}[t]
-\centering
-\includegraphics{time_to_success_active_clamped}
-\caption{
-Configuration times are much shorter than connection times, which means that most of the time was spent waiting for the connection to establish or time out.
-Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
-}
-\label{fig:time_to_success_active_clamped}
-\end{figure}
 

### 2017-03-15 pets2017-paper/pets2017-paper.tex
More about norcie2012eliminating.

@@
 \label{sec:related}
-Previous usability studies on Tor have focused on installation and use, but not on setting up Tor Browser.
-Norcie et~al.~\cite{norcie2012eliminating} observed 25 users and found that 64\% had issues that prevented them from installing or using Tor Browser.
+
+We do not know of any published usability studies of Tor Browser
+since the introduction of Tor Launcher,
+which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
+There are some earlier usability studies that focused on installation and use,
+but not on setting up Tor Browser.
+Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
+investigated ``stop-points''
+in the installation and use of Tor Browser,
+places where users' uncertainty about what to do
+put them at risk of not completing a task.
+Of their 25 participants, 64\% encountered at least one stop-point,
+such as a long startup time, misidentified icons, or confusion with other web browsers.
 Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency benefits their anonymity~\cite{dingledine2009performance}.
 Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.
-We do not know of any published usability evaluations of Tor Browser since the 3.5 series in 2013, which introduced radical UI changes~\cite{torbrowser-35}.
 Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.

### 2017-03-16 pets2017-paper/pets2017-paper.tex
More on fabian2010privately.

@@
 such as a long startup time, misidentified icons, or confusion with other web browsers.
-Fabian et~al.~\cite{fabian2010privately} revealed how users are frustrated by latency in Tor Browser enough not to use it, even if that latency benefits their anonymity~\cite{dingledine2009performance}.
+Fabian et~al.~\cite{fabian2010privately}, in 2010,
+estimated how much Tor's added latency harms usability.
+They measured the latency of requests to common websites with and without Tor,
+and mapped the latencies to compute an expected ``cancelation rate,''
+the fraction of users who would have given up waiting for a request to complete.
+They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
+% \cite{dingledine2009performance}
 Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.

### 2017-03-16 pets2017-paper/pets2017-paper.tex
More on clark2007usability.

@@
 which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
-There are some earlier usability studies that focused on installation and use,
-but not on setting up Tor Browser.
+There are some studies that evaluated earlier forms of the browser,
+without a particular focus on configuration.
 Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
@@
 Fabian et~al.~\cite{fabian2010privately}, in 2010,
-estimated how much Tor's added latency harms usability.
+estimated how much Tor's added latency harms usability
+(considered separately from user interface concerns).
 They measured the latency of requests to common websites with and without Tor,
@@
 % \cite{dingledine2009performance}
-Clark et~al.~\cite{clark2007usability} evaluated various Tor Browser deployment options (Vidalia, Privoxy, Torbutton, and FoxyProxy--none of which are around today) to find that none were satisfactory from a usability perspective and offered advice on how to improve them.
+In 2007, Clark et~al.~\cite{clark2007usability}
+used cognitive walkthroughs to evaluate four
+methods of web browsing over Tor
+(all of which have since been superseded by Tor Browser and Tor Launcher).
+Evaluating each method against a set of guidelines,
+they found that none were fully satisfactory,
+though the ones that used automatic configuration did better.
 Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.

### 2017-03-16 pets2017-paper/pets2017-paper.tex
More on uxsprint.

@@
 which happened in the 3.5 release in December 2013~\cite{torbrowser-35}.
-There are some studies that evaluated earlier forms of the browser,
+Lee and Fifield ran an informal ``UX sprint''
+for Tor Browser in 2015~\cite{uxsprint}, bringing together developers and users
+to discover common usability problems.
+They conducted detailed walkthroughs with five participants,
+in a precursor to the present work.
+There are some studies that evaluated earlier forms of web browsing over Tor,
 without a particular focus on configuration.
@@
 though the ones that used automatic configuration did better.
-Lee and Fifield~\cite{uxsprint} ran an informal UX sprint~\cite{uxsprint2015-tickets}.
 

### 2017-03-16 pets2017-paper/pets2017-paper.tex
dingledine2006anonymity as related work.

@@
 They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
-% \cite{dingledine2009performance}
 In 2007, Clark et~al.~\cite{clark2007usability}
@@
 though the ones that used automatic configuration did better.
+In 2006, Dingledine and Mathewson~\cite{dingledine2006anonymity}
+emphasized that anonymizing networks, by their nature,
+require lots of users, so usability is an even greater concern
+than with other security systems.
+They considered a case study of the ease of installing Tor,
+at a time when technically inexperienced users were just beginning to use it.
 

### 2017-03-16 pets2017-paper/pets2017-paper.tex
Spell check.

@@
 Users can configure a bridge by choosing a transport, which selects the group of bridges that use that transport.
-For instance, choosing the ``obfs3'' option in Figure~\ref{fig:old-bridge-combobox} will select a group of bridges that peform the obfs3 transport protocol as okay to use, and the user will be assigned one of these bridges as their guard relay.
+For instance, choosing the ``obfs3'' option in Figure~\ref{fig:old-bridge-combobox} will select a group of bridges that perform the obfs3 transport protocol as okay to use, and the user will be assigned one of these bridges as their guard relay.
 If these built-in options do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb}.
@@
 simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
-Re-routing participant traffic through other countries' networks also may introduce unforseen risks to the participants out of our control and performing hundreds of connections in short intervals during expeirments may draw unnecessary attention to Tor use in that country.
+Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country.
 
@@
 \item {\bfseries Connection time:} the amount of  time it takes a user to connect to Tor.
-The less time it takes for userss to connect, the better.
+The less time it takes for users to connect, the better.
 The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to a couple minutes.
@@
 Then the participant visited sample websites in a non-Tor browser to illustrate that some sites were blocked and instruct them to use Tor to circumvent censorship.
-Their task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visitng a censored website (Wikipedia) and an uncensored website (CNN).
+Their task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visiting a censored website (Wikipedia) and an uncensored website (CNN).
 We chose Wikipedia and CNN because their likely familiarity~\cite{alexa}.
@@
 \subsection{Changes Made} 
-In this section, we highlight and explain the speific design changes we made to address the observed pain points while adhering to the design considerations. We: \\
+In this section, we highlight and explain the specific design changes we made to address the observed pain points while adhering to the design considerations. We: \\
 
@@
 \item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question.
-In theory, this can be done locally without leacking information onto the network or for infrastructural changes.}
+In theory, this can be done locally without leaking information onto the network or for infrastructural changes.}
 \item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the of the bridge question screen (Figure~\ref{fig:old-bridge}).}
-\item{gave a recommendation to use one of the three meek-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended obfs3-transport bridges were unreachable, which happens in heavily censored real environments and our simulated enviornment E3.}
+\item{gave a recommendation to use one of the three meek-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended obfs3-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
 \item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
@@
 However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3).
-Figure~\ref{fig:all-participant-edges}) summarizes each partipant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time.
+Figure~\ref{fig:all-participant-edges}) summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time.
 Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.
@@
 Figure~\ref{fig:time_to_success_ecdf} shows a cumulative distribution of connection times.
-Everyone in E1 was able to connect right away; particpants with the NEW interface doing so faster than participiants with the OLD interface.
+Everyone in E1 was able to connect right away; participants with the NEW interface doing so faster than participants with the OLD interface.
 Most participants in E2 were able to connect right away; participants with the NEW interface and OLD interface connecting in a similar distribution of time.
@@
 \caption{
-Cumulative success rates over time. Those who did not connect were assigned an arbitratily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution. 
+Cumulative success rates over time. Those who did not connect were assigned an arbitrarily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution. 
 }
@@
 Due to the mentions above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}).
-We defined configuration time as a partcipant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen.
+We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen.
 However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.
@@
 They measured the latency of requests to common websites with and without Tor,
-and mapped the latencies to compute an expected ``cancelation rate,''
+and mapped the latencies to compute an expected ``cancellation rate,''
 the fraction of users who would have given up waiting for a request to complete.
-They estimated a median cancelation rate of 88\% for Tor, compared to 14\% for direct requests.
+They estimated a median cancellation rate of 88\% for Tor, compared to 14\% for direct requests.
 In 2007, Clark et~al.~\cite{clark2007usability}

### 2017-03-16 pets2017-paper/pets2017-paper.tex
State some outcomes of the UX sprint.

@@
 to discover common usability problems.
-They conducted detailed walkthroughs with five participants,
-in a precursor to the present work.
+In what was a precursor to the present work,
+they conducted detailed walkthroughs with five participants
+and identified common obstacles to using Tor Browser successfully,
+including hard-to-find downloads,
+bad interactions with other end-user security software,
+and misleading error messages.
 There are some studies that evaluated earlier forms of web browsing over Tor,

### 2017-03-16 pets2017-paper/pets2017-paper.tex
Fix spelling Grossklas → Grossklags.

@@
 \section {Acknowledgments}
-We would like to thank the peer reviewers, especially our shepherd Jens Grossklas, for giving us valuable feedback on this paper.
+We would like to thank the peer reviewers, especially our shepherd Jens Grossklags, for giving us valuable feedback on this paper.
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.

### 2017-03-16 pets2017-paper/pets2017-paper.tex
break up long related work paragraph and wordsmith for alignment

@@
 they conducted detailed walkthroughs with five participants
-and identified common obstacles to using Tor Browser successfully,
-including hard-to-find downloads,
+to identify common obstacles to using Tor Browser such as hard-to-find downloads,
 bad interactions with other end-user security software,
 and misleading error messages.
-There are some studies that evaluated earlier forms of web browsing over Tor,
+
+There are studies that evaluated earlier forms of web browsing over Tor,
 without a particular focus on configuration.
-Norcie et~al.~\cite{norcie2012eliminating}, in 2012,
-investigated ``stop-points''
-in the installation and use of Tor Browser,
-places where users' uncertainty about what to do
+In 2012, Norcie et~al.~\cite{norcie2012eliminating}
+investigated Tor Browser's``stop-points'' during installation and use,
+which they define as places where users' uncertainty about what to do
 put them at risk of not completing a task.
@@
 such as a long startup time, misidentified icons, or confusion with other web browsers.
-Fabian et~al.~\cite{fabian2010privately}, in 2010,
+
+In 2010, Fabian et~al.~\cite{fabian2010privately}
 estimated how much Tor's added latency harms usability
@@
 and mapped the latencies to compute an expected ``cancellation rate,''
-the fraction of users who would have given up waiting for a request to complete.
+which they define as the fraction of users who would have given up waiting for a request to complete.
 They estimated a median cancellation rate of 88\% for Tor, compared to 14\% for direct requests.
+
 In 2007, Clark et~al.~\cite{clark2007usability}
@@
 than with other security systems.
-They considered a case study of the ease of installing Tor,
-at a time when technically inexperienced users were just beginning to use it.
 

### 2017-03-16 pets2017-paper/pets2017-paper.tex
Missing space.

@@
 In 2012, Norcie et~al.~\cite{norcie2012eliminating}
-investigated Tor Browser's``stop-points'' during installation and use,
+investigated Tor Browser's ``stop-points'' during installation and use,
 which they define as places where users' uncertainty about what to do

### 2017-03-20 pets2017-paper/pets2017-paper.tex
correct wrong word: user >use

@@
 
-We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use.
 We recruited five participants per experimental condition to gather qualitative data; this is considered the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
switch first sentence to last

@@
 \label{sec:environments}
-We simulated three environments of varying censorship severity (Table~\ref{tab:environments}). We chose to 
-simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
+We chose to simulate environments for the stability and reproducibility of the experiment, as real censored networks are volatile and complex.
 Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country.
+The three environments are described in Table~\ref{tab:environments}.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
swtich order of paragraphs in methodology section
minor wordsmithing to make it sound less awkward

@@
 
+In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed).
+In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
+Finally, the third environment, E3, additionally blocked several of the included bridges, which required experimenting with several different bridges---beyond the recommended option---in order to successfully connect.
+
 The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
@@
 We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the different interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
-
-In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed).
-In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
-Finally, the third environment, E3, additionally blocked several of the included bridges, which required experimenting with several different bridges---beyond the recommended option---in order to successfully connect.
 
@@
 The ideal case would be that everyone is able to connect to Tor if they want to.
-Even if users do not successfully connect to Tor on previous attempts but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
-\item {\bfseries Connection time:} the amount of  time it takes a user to connect to Tor.
+Even if users do not successfully connect to Tor at first but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
+\item {\bfseries Connection time:} the amount of time a user takes to connect to Tor.
 The less time it takes for users to connect, the better.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
refer to users in plural for all three metrics
fix wrong word

@@
 Even if users do not successfully connect to Tor at first but eventually do so during the experiment, they are considered to have successfully connected to Tor for this metric.
-\item {\bfseries Connection time:} the amount of time a user takes to connect to Tor.
+\item {\bfseries Connection time:} the amount of time users take to connect to Tor.
 The less time it takes for users to connect, the better.
@@
 \label{sec:qualitative}
-We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use.
 We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
delete repetitive reference to appendix
delete stray parenthesis

@@
 Here we report about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes.
-We detail what each participant did in Appendix~\ref{summary}.
 
@@
 However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3).
-Figure~\ref{fig:all-participant-edges}) summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time.
+Figure~\ref{fig:all-participant-edges} summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time.
 Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
rewording configuration time sentences

@@
 Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time were generally a small fraction of their connection time.
-E1 participants' configuration time was a small fraction of connection time because because they generally chose a configuration that successfully connected to Tor right away, and the time spent bootstrapping the connection to Tor dominated the connection time.
-E3 participants' configuration time was significantly less than their connection time they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts.
-E2, participants' configuration time was a a modest amount of their connection time, due to the combination of reasons that affected participants in E1 and E3.
-
-Due to the mentions above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}).
+E1 participants' configuration time was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away.
+E3 participants' configuration time was also dominated by the time waiting for a connection to be established to Tor because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts.
+E2 participants' configuration time was a a fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.
+
+Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}).
 We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
tweak the recommendations section

@@
 \label{sec:recommendations}
-While our design resulted in shorter connection times and greater success, it could still be improved.
-Thus, we do not recommend our exact design.
+While our design resulted in shorter connection times and greater success,  but it could still be improved.
+We do not recommend our exact design as the optimal design, although we believe it is an improvement.
 Instead, we offer some suggestions based on what we learned: \\
@@
 
-We ourselves did not follow the above advice, due to design constraints.
-But seeing as how our redesigned interface still did not have an ideal success rate, connection time, or configuration time, we think that alternative designs that leverage user input and automation should be considered.
-We recommend implementing some design changes right away initially to improve on the current design, then consider implementing our advice above.
-\\
+We did not try any designs that asked for user inputs, due to design constraints.
+But we see further room for improvement in success rate, connection time, and configuration time that could be made by leverage user input and automation.
+Here, we talk about the potential approaches to redesigning the interface:  \\
 
@@
 
-User consent should precede any automated connections to Tor. Alternative methods, such as giving location-specific advice, should be explored as well.
+We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation into the interface only if the impact of those changes are still unsatisfactory.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Use \subsection, not \subsubsection here.
\subsubsection within Appendix G was creating labels "G.0.1 E1",
"G.0.2 E2", "G.0.3 E3".

@@
 
-\subsubsection{E1} 
+\subsection{E1} 
 In E1, any connection to Tor worked. Configuring bridges and proxies was optional.  
@@
 
-\subsubsection{E2} 
+\subsection{E2} 
 In E2, a bridge was required to connect. Any of the hardcoded bridges from the dropdown menu, as well as any custom bridges acquired out of band would work. Configuring a proxy was optional.
@@
 
-\subsubsection{E3}
+\subsection{E3}
 In E3, a bridge was required to connect.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Typo fix.
Proofread \label{states}.

@@
 \label{states} 
-Tor Launcher 5.0.3's end states corresponding to Figure~\ref{fig:digraph}. E\# and $\mbox{e\#}^\prime$ are equivalent, but $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\
+Here we define the end state codes that appear in Figure~\ref{fig:digraph}.
+e\# and $\mbox{e\#}^\prime$ are equivalent, except that $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\
 
@@
 \begin{itemize}
-\item s0: no bridge no proxy
+\item s0: no bridge, no proxy
 \item s1: valid bridge, no proxy
@@
 
-Same inputs can lead to different end states.
-Tor Launcher will connect to a proxy successfully with the port left blank if the proxy uses port 80 (s2) but will not if the proxy uses another port (e12).
+The same inputs can lead to different end states,
+depending on the network environment.
+For example, Tor Launcher will connect to a proxy successfully with the port left blank if the proxy uses port 80 (s2) but will not if the proxy uses another port (e12).
 
@@
 \item{If you have a personal computer, what kind do you use?}
-\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
+\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
 \item{How often do you use the following software or features?
@@
 \label{summary}
-We summarize of each participant's session.
+We summarize each participant's session.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Proofread appendices B through F.

@@
 \item{If you have a personal computer, what kind do you use?}
-\item{Which of the following terms have you heard of? \textit{<answer choices: a checkboxlist of the following terms: malware, proxy services, phishing, SSL, X.511 certificates, Tor>}}
+\item{Which of the following terms have you heard of? \textit{<Answer choices: a checklist of the following terms: malware; proxy services; phishing; SSL; X.511 certificates; Tor.>}}
 \item{How often do you use the following software or features?
-\textit{<answer choices: a grid of radio buttons.
-Software/features (rows): HTTPS on web pages, proxies or other censorship circumvention tools, virtual private networks (VPN), file or whole-disk encryption, anonymity systems (e.g., Tor), email encryption (e.g., PGP), chat or instant messaging encryption, voice communication encryption.
-Frequency (columns): never, less than once a month, a few times a month, several times a week, daily.>}}
+\textit{<Answer choices: a grid of radio buttons.
+Software/features (rows): HTTPS on web pages; proxies or other censorship circumvention tools; virtual private networks (VPN); file or whole-disk encryption; anonymity systems (e.g., Tor); email encryption (e.g., PGP); chat or instant messaging encryption; voice communication encryption.
+Frequency (columns): never; less than once a month; a few times a month; several times a week; daily.>}}
 \end{enumerate}
@@
 The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-Currently, torproject is blocked (you can check this by going to torproject.org on a standard browser, like Firefox, Chrome, or Internet Explorer).
+Currently, torproject is blocked (you can check this by going to \begin{NoHyper}\url{torproject.org}\end{NoHyper} on a standard browser, like Firefox, Chrome, or Internet Explorer).
 
@@
 The purpose of this experiment is to evaluate the use of Tor browser, which is a browser that can circumvent censorship and let you visit blocked websites.
-For instance, www.torproject.org is blocked.
+For instance, \begin{NoHyper}\url{www.torproject.org}\end{NoHyper} is blocked.
 Check this by going to the site on a standard browser, like Firefox, Chrome, or Internet Explorer.
@@
 If you can visit wikipedia, then you know that you have successfully circumvented censorship.
+
+\begin{enumerate}
+\item Visit Wikipedia’s main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today’s selected article?
+\item After you have completed the tasks, fill out this survey: \textit{<survey link>} 
+\end{enumerate}
+
+Now you are done! Please stay stay at your desk until the experiment is formally over.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
My mistake, this text was already present under quantitative.

@@
 
-\begin{enumerate}
-\item Visit Wikipedia’s main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today’s selected article?
-\item After you have completed the tasks, fill out this survey: \textit{<survey link>} 
-\end{enumerate}
-
-Now you are done! Please stay stay at your desk until the experiment is formally over.
-
 \section{Post-Experiment Standard Interview Questions}
@@
 
-1. Visit Wikipedia’s main page (\url{https://en.wikipedia.org/wiki/Main\_Page}). What is the topic of today’s selected article?
-
-2. After you have completed the tasks, fill out this survey: http://bit.ly/tor-survey
+\begin{enumerate}
+\item Visit Wikipedia’s main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today’s selected article?
+\item After you have completed the tasks, fill out this survey: \begin{NoHyper}\url{http://bit.ly/tor-survey}\end{NoHyper}
+\end{enumerate}
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Proofread Appendices G through K.

@@
 \pquote{P9 (previous Tor user, obfs3, 4:08)}{They tried connecting directly.
-And they tried connecting directly through a different user path by answering no to bridge and proxy questions in the interface, connecting from the proxy screen.
+And they tried connecting directly through a different user path by answering `no' to the bridge and proxy questions in the interface, connecting from the proxy screen.
 Then, they connected using the recommended bridge.}
@@
 They spent the rest of their time trying different bridges and proxies in vain (Figure~\ref{fig:proxy-attempt}).
-This participant tried the most attempts to connect to Tor, using a variety of bridges and proxies.}
-
-Participants in E2 tried a direct connection to Tor before {\it eventually} connecting with the recommended bridge.
+This participant made the most connection attempts, using a variety of bridges and proxies.}
+
+Participants in E2 tried a direct connection to Tor before \emph{eventually} connecting with the recommended bridge.
 They spent a fair amount of time waiting before determining that connections failed.
@@
 In E3, a bridge was required to connect.
-Most of the hardcoded bridges in the dropdown menu do not work, with the exception of meek-amazon, meek-azure, and meek-google.
+Most of the hardcoded bridges in the dropdown menu would not work, with the exception of meek-amazon, meek-azure, and meek-google.
 Custom bridges can also work.
@@
 %P6 (heard of Tor): E3 (26:48; 0:18 to 27:06) 
-\pquote{P14 (new user, meek-google, 26:48)}{They tried a direct connection by answering no to bridge and proxy questions.
+\pquote{P14 (new user, meek-google, 26:48)}{They tried a direct connection by answering `no' to the bridge and proxy questions.
 After waiting a while, they canceled the connection and tried connecting with the recommended bridge.
@@
 After that, they tried a connection using a meek-azure bridge, but gave up after before it could connect.
-They went back to the first screen~\ref{fig:old-first} and clicked connect, which made a connection using meek-azure bridge.
+They went back to the first screen (Figure~\ref{fig:old-first}) and clicked connect, which made a connection using a meek-azure bridge.
 The connect button makes a connection to Tor with the toggled settings in the interface.
@@
 The participants that did manage to connect to Tor did not know which bridges worked and which ones did not, or which ones to try next in case the recommended one failed.
-P14 brute forced options until something worked, P15 did not think that they used a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
+P14 brute-forced options until something worked, P15 did not think that they were using a bridge, and P16 gave up on a hardcoded bridge that would have worked and used a custom bridge instead.
 
@@
 
-If you are interested: 1. Email lnl@berkeley.edu 
+If you are interested: 1.~Email lnl@berkeley.edu 
 with the sessions you are able to attend. We will confirm your participation and assign you a session. 
-2. Come to Xlab 
+2.~Come to Xlab 
 at the appointed time for the experiment.
@@
 \begin{enumerate}
-\item Visit Wikipedia’s main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today’s selected article?
+\item Visit Wikipedia's main page (\begin{NoHyper}\url{https://en.wikipedia.org/wiki/Main_Page}\end{NoHyper}). What is the topic of today's selected article?
 \item After you have completed the tasks, fill out this survey: \begin{NoHyper}\url{http://bit.ly/tor-survey}\end{NoHyper}

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Missing space.

@@
 
-Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else(Table~\ref{table:median_time}).
+Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else (Table~\ref{table:median_time}).
 We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Proofread sec:recommendations.

@@
 \label{sec:recommendations}
-While our design resulted in shorter connection times and greater success,  but it could still be improved.
+Our design resulted in shorter connection times and greater success,  but it could still be improved.
 We do not recommend our exact design as the optimal design, although we believe it is an improvement.
@@
 We did not try any designs that asked for user inputs, due to design constraints.
-But we see further room for improvement in success rate, connection time, and configuration time that could be made by leverage user input and automation.
+But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation.
 Here, we talk about the potential approaches to redesigning the interface:  \\
@@
 \item{\bfseries Naive automation:} a scheme that chooses bridges, waits for timeouts, and tries another bridge so users do not need to do this themselves.
-We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would have had to take.
+We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually.
 \item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwidth constraints.
@@
 
-We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation into the interface only if the impact of those changes are still unsatisfactory.
+We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation into the interface only if the impact of those changes is still unsatisfactory.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Edit up to section 5
P.S. This is the 1000th commit!

@@
 to make it difficult to observe sources and destinations.
-Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, thereby simplifying the process of configuring Tor to use existing browsers.
-Although Tor Browser was originally designed for anonymity, many now use Tor Browser to circumvent Internet censorship.
-Many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
+Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, designed to minimize the configuration required before connecting.
+Although Tor was originally designed for anonymity, many now use it to circumvent Internet censorship.
+Because of this, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
+
 Tor Browser is bundled with a graphical configuration interface, Tor Launcher, which allows users to bypass censorship by configuring various bridges, proxies, and transport protocols prior to connecting to Tor.
 Of course, these options are only effective if users understand how to use them.
-Thus, we performed a usability study to examine the effectiveness of Tor Launcher and how it could be improved.
-
-Improving Tor launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}).
+To understand to what extent this is the case, we researched the effectiveness of Tor Launcher as well as how it could be improved.
+
+Improving Tor Launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}).
 Tor does not collect user interaction data from its real users, so we believe that usability testing research is critical to help users in heavily censored regimes and increase user adoption.
@@
 \begin{itemize}
-\item{Perform a qualitative and quantitative usability evaluation of Tor Launcher 5.0.3  under simulated censorship environments to determine why and how much it is or is not usable.}
-\item{Contribute design changes that statistically significantly improve users' likelihood of connecting to Tor and also statistically significantly reduces the amount of time users take to connect.} 
-\item{Provide recommendations beyond design changes to improve Tor Launcher, such as leveraging user input (requires research) and building an automated connection scheme (requires Tor-infrastructure work).}
+\item{Perform a qualitative and quantitative usability evaluation of Tor Launcher 5.0.3  under simulated censorship environments}
+\item{Contribute design changes that improve users' likelihood of connecting to Tor and also reduce the amount of time users take to connect}
+\item{Provide recommendations beyond design changes to improve Tor Launcher, such as leveraging user input (requires research) and building an automated connection scheme (requires Tor infrastructure work).}
 \end{itemize}
 
-Specifically, we describe how we started our usability evaluation by inspecting the interface (Section~\ref{sec:inspection}) and observing participants interact with it (Section~\ref{sec:qualitative}).
+Specifically, we describe how the initial evaluation of the interface (Section~\ref{sec:inspection}) and our observations of participants' interactions with it (Section~\ref{sec:qualitative}).
 Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}).
@@
 \label{sec:background}
-This section discusses the network components are involved in connecting to Tor and how users can connect to Tor in various ways.
-An understanding of the network components or the various connection options are not required to understand our work, but we refer to these terms and methods throughout the paper.
+This section discusses the network components involved in connecting to Tor.
+An understanding of the various connection options are not required to understand our work, but we refer to these terms and methods throughout the paper.
 
@@
 Generally, a proxy is any computer or service that allows users to make indirect connections to other services.
-In this sense, any Tor relay and the Tor circuit can also be considered to be a proxy.
+In this sense, any Tor relay and the Tor circuit can also be considered a proxy.
 However, in this paper, the word ``proxy'' refers to a SOCKS or HTTP proxy that bypasses local firewalls.
@@
 When a bridge is used, it takes the place of the guard relay.
-For convenience, bridges are grouped by which transport they run.
+For convenience, bridges are grouped in the interface by which transport they run.
 
@@
 Most bridges can be blocked by blocking their static IP addresses.
-These include bridges that run the ``fte'' and ``fte-ipv6''~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the ``obfs3''~\cite{obfs3}, ``obfs4''~\cite{obfs4}, and ``scramblesuit''~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
+These include bridges that run the \texttt{fte} and \texttt{fte-ipv6}~\cite{fte} pluggable transports, which disguise the Tor protocol as another protocol (such as HTTP); these also include the \texttt{obfs3}~\cite{obfs3}, \texttt{obfs4}~\cite{obfs4}, and \texttt{scramblesuit}~\cite{scramblesuit} transports, which encrypt or alter the Tor protocol to appear as random noise.
+
 Other bridges are less susceptible to blocking because of how they work.
-Bridges that run the ``flashproxy''~\cite{flashproxy} and ``meek''~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks.
+Bridges that run the \texttt{flashproxy}~\cite{flashproxy} and \texttt{meek}~\cite{fifield2015blocking} transports route traffic through third party web browsers and content delivery networks.
 The bridges and transports that are accessible in each country vary.
@@
 \subsection{Connecting to Tor} 
-It is important to note that there are many valid configuration settings that can be used to connect to the Tor network. A user may or may not need a combination of proxy and bridge.
-A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that they are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).
+It is important to note that there are many valid configuration settings that can be used to connect to the Tor network. A user may or may not need a proxy and/or a bridge.
+A user who does not need a bridge or proxy can still connect with a bridge, proxy, or both, provided that these are configured correctly (though adding unnecessary network hops or obfuscation protocols may slow the connection down).
 
 Users can configure a bridge by choosing a transport, which selects the group of bridges that use that transport.
-For instance, choosing the ``obfs3'' option in Figure~\ref{fig:old-bridge-combobox} will select a group of bridges that perform the obfs3 transport protocol as okay to use, and the user will be assigned one of these bridges as their guard relay.
+For instance, a user choosing the \texttt{obfs3} option in Figure~\ref{fig:old-bridge-combobox} will be assigned one of these bridges as their guard relay.
 If these built-in options do not work, users can obtain bridge configurations through out-of-band channels~\cite{bridgedb}.
 Configuring a proxy requires entering in the proxy protocol, IP address, port, and additional optional fields (Figure~\ref{fig:old-proxy}).
-The user must locate this information.
+The user must obtain this information themselves.
 
@@
 \section{Methodology} 
-This section discusses the usability testing process used to evaluate Tor Launcher, the simulated censorship environments we used to require users to configure different network components to connect to Tor, and what our evaluation metrics  we collected to deem the interface usable or not usable.
+This section discusses our usability testing process, including the simulated censorship environments we used to require users to configure different network components to connect to Tor and the evaluation metrics  we collected.
 
@@
 We believe both methods were necessary for a complete usability evaluation.
-Qualitative testing tells you {\it why or how} it is or is not usable, while quantitative testing tells you {\it how much} it is or is not usable.
-We used our observations from the qualitative study to design interface changes that would address common issues that these participants encountered.
+Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
+We used our observations from the qualitative study to design interface changes that would address common issues that participants encountered.
 We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.
 
-We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use.
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
 We recruited five participants per experimental condition to gather qualitative data; this is considered the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
@@
 
-In the first environment, E1, particular websites were blocked, which meant that they could be accessed via a default Tor configuration (i.e., bridges or proxies were not needed).
+The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
+Rather, we designed simulated environments to have different requirements to connect to Tor.
+We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the different interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
+
+In the first environment, E1, particular websites were blocked, which meant that they could be accessed using a default Tor configuration (i.e., bridges or proxies were not needed).
 In the second environment, E2, we additionally blocked the IP addresses of public Tor relays, which meant that Tor could still be accessed by enabling any of the included bridges.
@@
 The less time it takes for users to connect, the better.
-The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to a couple minutes.
+The ideal case would be that the connection time is very close to the time it takes for the application to communicate with the servers and establish a circuit of relays for the connection, which can take up to several minutes.
 Connection time includes this bootstrapping time and any additional time that people spend in the interface.
@@
 
-Completion rate is the fundamental usability metric that measures if users can accomplish the task.
+Completion rate is the most important usability metric, measuring if users can accomplish the task.
 We defined success as a binary metric that is true if a user connected to Tor and false if a user did not.
-We consider this to be the most important usability metric, as this directly measures if users could connect to Tor.
-
 Task time is a supplemental usability metric that measures user productivity during the task.
-We measured this in two ways.
-Connection time measures how long users took to connect to Tor, while configuration time to measures how long users spent actively configuring bridges and proxies.
-We use both metrics to quantify productivity since the bootstrapping time, and hence, time spent waiting for the connection to succeed or fail, can dominate the measurement.
-Connection time is always greater than the configuration time, since it includes the configuration time.
-We consider connection time and configuration time to be equally important in measuring user productivity.
+We use both connection and configuration time to quantify productivity since the bootstrapping time, and hence, time spent waiting for the connection to succeed or fail, can dominate the measurement.
 
@@
 \item {\bfseries Too many choices:}  Users who do not need a bridge or proxy are able to configure them.
-There are nine choices for bridges by transport and more options to input a custom bridge.
+There are nine choices for bridges and more options to input a custom bridge.
 Almost any HTTP or SOCKS proxy can be used as the proxy.
-Custom bridge lines require the bridge information with specific syntax, but this syntax is not specified in the interface.
+Custom bridge lines require the bridge information in a specific syntax, but this syntax is not specified in the interface.
 Proxy fields also do not provide syntactic guidelines.
-See the whole list of possible errors we identified in Appendix~\ref{states}.
+The full list of possible errors we identified can be found in Appendix~\ref{states}.
 \item {\bfseries Poor feedback:} Even if there was a syntactic error in the bridge or proxy fields, the user is not notified until after a connection is attempted and fails.
 If a censored bridge was chosen, the connection timeout takes several minutes.
-Error messages were often technical and did not give suggestions.
+Error messages were often technical and did not give suggestions for next steps.
 \end{itemize}
@@
 \label{sec:qualitative}
-We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use.
-We observed user behaviors to identify Tor stumbling points and then interviewed them afterwards to gather explanatory data and their opinions.
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time identify stumbling points in the interface.
+At the completion of the task, we interviewed our participants to gather explanatory data and their opinions.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Fix newly introduced typo

@@
 \label{sec:qualitative}
-We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time identify stumbling points in the interface.
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and identify stumbling points in the interface.
 At the completion of the task, we interviewed our participants to gather explanatory data and their opinions.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Proofread sec:quantitative.

@@
 \label{sec:quantitative}
-We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
-We confirm prior stumbling points and user behaviors and validate our proposed design improvements.
+We performed our quantitative experiments at a behavioral laboratory on many participants at a time, using instrumentation to capture evaluation metrics.
+We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.
 
 \subsection{Recruitment}
-We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted-in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for recruitment materials).
+We recruited 59 participants from the Xlab mailing list, which is a university-wide pool of participants who have opted in to participating in social science experiments (see Appendix~\ref{quantitative-recruitment} for recruitment materials).
 We recruited an additional 65 participants from Craigslist to ensure diversity, since Xlab participants are primarily students and staff from UC Berkeley.
 
-Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or downloaded another version of Tor Browser to use during the experiment.
+Of our 124 participants, we filtered out 10 participants who did not complete the consent form correctly or who downloaded another version of Tor Browser to use during the experiment.
 One participant did not report their demographics, but we still used their data.
@@
 Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens.
-At the beginning of each session, we used a script to revert the computers to a clean image, download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes ), set up one of the three simulated environments (E1, E2, or E3), and started recording the computer screen.
+At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
 We manually assigned interface--environment combinations to each computer.
 
-We receive informed consent after talking about the study (Appendix~\ref{quantitative-script}) and instruct participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}), and gave them 40 minutes to complete the task.
+We received informed consent after talking about the study (Appendix~\ref{quantitative-script}).
+We instructed participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}) and gave them 40 minutes to complete the task.
 Researchers maintained minimal interactions with the participants.
-After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), gave them \$30 for their time.
+After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we gave each participant \$30 for their time.
 
@@
 As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time.
-However, many, including users who used the redesigned version, still could not connect to Tor (63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed) and those that did took long to do so (>3 minutes in E2 and >20 minutes in E3).
-Figure~\ref{fig:all-participant-edges} summarizes each participant--showing if they connect to Tor, how long each participant took to do so, and where they spent their time.
+However, many, including users who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed.
+Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3).
+Figure~\ref{fig:all-participant-edges} summarizes each participant---showing if they connected to Tor, how long they took to do so, and where they spent their time.
 Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.
@@
 As reported in the first two columns, most participants who did not need to configure anything (E1) didn't, although some optionally used a bridge.
-Participants who needed any bridge (E2) all used the recommended bridge.
-Participants who needed a meek-bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and did not connect to Tor.
+Participants who could have used any bridge (E2) all used the recommended bridge.
+Participants who needed a meek bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.
 
@@
 Everyone in E1 was able to connect right away; participants with the NEW interface doing so faster than participants with the OLD interface.
-Most participants in E2 were able to connect right away; participants with the NEW interface and OLD interface connecting in a similar distribution of time.
+Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time.
 Participants in E3 took various amount of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.
@@
 
-Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time were generally a small fraction of their connection time.
-E1 participants' configuration time was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away.
-E3 participants' configuration time was also dominated by the time waiting for a connection to be established to Tor because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts.
-E2 participants' configuration time was a a fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.
-
-Due to the reasons above, participants spent a majority of their time on the progress screen compared to the time spent anywhere else (Table~\ref{table:median_time}).
+Figure~\ref{fig:time_to_success_active_clamped} shows that participants' active configuration time was generally a small fraction of their connection time.
+The configuration time of participants in E1 was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away.
+The configuration time of participants in E3 was also dominated by the time waiting for a connection to be established to Tor, because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts.
+The configuration time of participants in E2 was a modest fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.
+
+Due to the reasons above, participants spent more time on the progress screen than on any other screen (Table~\ref{table:median_time}).
 We defined configuration time as a participant's connection time spent on all screens but the progress screen, because participants mostly waited on the progress screen.
-However, we noticed that some participants did utilize this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a prefect metric to measure participant engagement.
+However, we noticed that some participants utilized this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a perfect metric to measure participant engagement.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Edit section 5 (qualitative study)

@@
 We ran the experiments in a small room with a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
-On a clean computer, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment.
+Using a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment.
 We ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen before each participant.
 
-We get informed consent by talking about the study, task, and risks (Appendix~\ref{qualitative-script}).
-Then the participant visited sample websites in a non-Tor browser to illustrate that some sites were blocked and instruct them to use Tor to circumvent censorship.
-Their task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visiting a censored website (Wikipedia) and an uncensored website (CNN).
-We chose Wikipedia and CNN because their likely familiarity~\cite{alexa}.
+Before beginning our procedure, we obtained informed consent from all our participants (Appendix~\ref{qualitative-script}).
+The session began with the participant visiting sample websites in a non-Tor browser to ascertain that some sites were blocked.
+The participants' task was to complete a worksheet (Appendix~\ref{participant-worksheet}) that required visiting a censored website (Wikipedia) and an uncensored website (CNN).
+We chose Wikipedia and CNN because of their likely familiarity~\cite{alexa}.
 After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.
 
-After 45 minutes (or when participants finished the worksheet), we interviewed the participant about their experience.
+After 45 minutes (or when participants finished the worksheet), the experimenters interviewed them about their experience.
 We asked general questions (Appendix~\ref{interview-questions}) and participant-specific questions to verify any observations (e.g., ``the participant was selecting bridges at random'').
-After the interview, we allowed the participant to ask any questions about the experiment, then gave them~\$30 for their time.
+After the interview, we allowed the participant to ask any questions about the experiment and provided their compensation~(\$30).
 
@@
 
-Here we report about the main reasons why participants struggled to use Tor launcher, summarizing general behavioral trends and attitudes.
-
-\subsection{Pain Points in Tor Launcher} 
 \label{sec:pain-points}
+
+Here we report the main reasons why participants struggled to use Tor Launcher, summarizing general behavioral trends and attitudes, and providing representative quotes from individual subjects.
+
 Participants spent a lot of time going back and forth on screens, looking for proxy information, and waiting for the connection to work or time out.
@@
 \begin{itemize}
-\item {\bfseries Unfamiliar concepts:} Participants found technical terms (i.e.
-relay, bridge, proxy, censor, ISP) confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}).
+\item {\bfseries Unfamiliar concepts:} Participants found technical terms (e.g., relay, bridge, proxy, censor, ISP) confusing, and were often unable to answer the questions that were designed to guide them (Figures~\ref{fig:old-bridge} and~\ref{fig:old-proxy}).
 \end{itemize}
@@
 \begin{itemize}
-\item {\bfseries Missing information:} They did not know how to choose a bridge by transport or which bridges worked in their environment (Figures~\ref{fig:old-bridge-combobox}).
+\item {\bfseries Missing information:} They did not know how to choose a bridge/transport or which bridges worked in their environment (Figures~\ref{fig:old-bridge-combobox}).
 \end{itemize}
@@
 \begin{itemize}
-\item {\bfseries Bad recovery:} Participants had to wait a couple minutes to know if their connection failed, and also were quite upset that they had to wait that long to find out that their connection failed.
+\item {\bfseries Bad recovery:} Participants had to wait up to several minutes to know if their connection failed, and were sometimes upset that they had to wait that long to find out that their connection failed.
 \end{itemize}

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Two small changes: typo fixes in intro; replace vague passive tense "is considered..."

@@
 
-Improving Tor Launcher has the obvious benefit of helping censored users connect to Tor, but this also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}).
+Improving Tor Launcher has the obvious benefit of helping censored users connect to Tor.
+It also benefits other Tor users since an increase in the overall number of users increases the anonymity set~\cite{dingledine2006anonymity}.
 Tor does not collect user interaction data from its real users, so we believe that usability testing research is critical to help users in heavily censored regimes and increase user adoption.
@@
 We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
-We recruited five participants per experimental condition to gather qualitative data; this is considered the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
+We recruited five participants per experimental condition to gather qualitative data; this has been suggested as the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
 We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
-We recruited twenty users per experimental condition to gather quantitative data; this is considered to be the minimum for yielding statistically significant measurements~\cite{howmanyusers}.
+We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistically significance~\cite{howmanyusers}.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Provide minor edits for section 6 (design)

@@
 
-\item{\bfseries Financial constraints}: Leveraging harder-to-block ``meek'' bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
+\item{\bfseries Financial constraints}: Leveraging harder-to-block \texttt{meek} bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
 \end{itemize}
@@
 We chose not to leverage user inputs such as their location, risk, or other preferences due to active and passive adversaries.
-We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to increase the chances of Tor adoption our design changes.
+We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.
 
@@
 \item{centered the text to make the design compatible for left to right and right to left languages.}
-\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies to not optionally configure them.}
+\item{clarified that configuration options were manual and for heavily censored environments (Figure~\ref{fig:new-first}) to discourage users who did not need bridges and proxies from configuring them.}
 \item{added a status bar on the proxy and bridge screens (Figure~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge}, and~\ref{fig:new-bridge-combobox}) to hint at future tasks.}
 \item{reordered proxy and bridge screens (Figures ~\ref{fig:new-proxy} and ~\ref{fig:new-nobridge}) in a topologically sequential order.
-This hints that proper proxy settings (if required, to set one up properly, and if not required, to be set up properly or not selected) are necessary to reach bridges.}
+This hints that proper proxy configuration is necessary to reach bridges.}
 \item{eliminated the bridge and proxy questions (Figure~\ref{fig:old-bridge} and~\ref{fig:old-proxy}) to reduce the number of screens.}
 \item{added auto-detection for proxies (Figure~\ref{fig:new-proxy}) in place of the proxy question.
-In theory, this can be done locally without leaking information onto the network or for infrastructural changes.}
+In theory, this can be done locally without infrastructural changes or leaking information to the network.}
 \item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the of the bridge question screen (Figure~\ref{fig:old-bridge}).}
-\item{gave a recommendation to use one of the three meek-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended obfs3-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
+\item{gave a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
 \item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Fix new typo
from 6505b122ffef1fe5e5020267175a83c2e7e87f6c

@@
 We performed our quantitative experiments at a behavioral laboratory many participants at a time, using instrumentation to capture evaluation metrics.
-We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistically significance~\cite{howmanyusers}.
+We recruited twenty users per experimental condition to gather quantitative data, based on estimates of the number needed for statistical significance~\cite{howmanyusers}.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Small changes to Sec 4-5.  Clarify design challenges in Sec 6.1.

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 If a censored bridge was chosen, the connection timeout takes several minutes.
-Error messages were often technical and did not give suggestions for next steps.
+Error messages were often technical and did not suggest how to fix the problem.
 \end{itemize}
@@
 
-As we performed the experiments, we distributed participants evenly across experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
+As we performed the experiments, we distributed participants evenly across three experimental conditions:  5~in E1, 5~in E2, and 6~in E3.
 We ensured that each condition had new and previous Tor Browser users, and tried for variation in gender and age.
@@
 We chose Wikipedia and CNN because of their likely familiarity~\cite{alexa}.
-After giving the instructions, the researchers left the room to minimize interactions and watched a live feed of the participant's screen.
+After giving the instructions, the researchers left the room to minimize interaction and watched a live feed of the participant's screen.
 
@@
 
-These were our general observations.
 Participants who could connect directly (E1) or use the recommended bridge had an easy time connecting (E2), but the participants who could not use many of the hardcoded bridges (E3) did not know what to do.
@@
 \item {\bfseries User consent}: Some oppressive regimes may detect and prosecute Tor usage, and therefore simply using Tor may carry risks.
-While we could help users by automating configuration settings, this would involve probing network configurations, which may alert authorities to Tor usage.
+While we could help users by automating configuration settings, this would involve probing network configurations and sending network traffic that could allow authorities to detect that the user is using Tor.
 Taking this risk without proper consent is not ethical.
@@
 
-\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor. We should allow users to leverage local information to reduce their risk.
+\item {\bfseries Passive adversaries}: A sufficiently powerful network adversary can detect that a user is connecting to Tor, unless the user chooses some very specific network configurations.
+We should enable informed users who wish to avoid this risk to do so.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Edit section 7 (quantitative study) for style

@@
 \label{sec:quantitative}
-We performed our quantitative experiments at a behavioral laboratory on many participants at a time, using instrumentation to capture evaluation metrics.
+We conducted our quantitative experiments at a behavioral laboratory with many participants in parallel, using instrumentation to capture evaluation metrics.
 We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.
@@
 We ran our experiment at Xlab~\cite{xlab}, an experimental social science laboratory.
-Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at other screens.
-At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with/without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
+Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at others' screens.
+At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
 We manually assigned interface--environment combinations to each computer.
 
-We received informed consent after talking about the study (Appendix~\ref{quantitative-script}).
+We received informed consent after describing the study (Appendix~\ref{quantitative-script}).
 We instructed participants to use Tor to complete their worksheet (Appendix~\ref{summative-worksheet}) and gave them 40 minutes to complete the task.
-Researchers maintained minimal interactions with the participants.
+Researchers maintained minimal interaction with the participants.
 After the experiment and exit survey (Appendix~\ref{quantitative-exit-survey}), we gave each participant \$30 for their time.
@@
 As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time.
-However, many, including users who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed.
+However, many, including participants who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed.
 Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3).
@@
 Participants who could have used any bridge (E2) all used the recommended bridge.
-Participants who needed a meek bridge or custom bridge (E3) chose a meek bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.
+Participants who needed a \texttt{meek} bridge or custom bridge (E3) chose a \texttt{meek} bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.
 
@@
 The configuration time of participants in E1 was dominated by the time waiting for a connection to be established to Tor because they generally chose the correct configuration right away.
-The configuration time of participants in E3 was also dominated by the time waiting for a connection to be established to Tor, because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their attempt between attempts.
+The configuration time of participants in E3 was also dominated by the time waiting for a connection to be established to Tor, because they usually needed to try multiple configuration options before connecting, but had to wait for the connection to time out or manually cancel their connection between attempts.
 The configuration time of participants in E2 was a modest fraction of their connection time, due to a combination of reasons that affected participants in E1 and E3.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Expand slightly on why we don't use meek more often.

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 
-\item{\bfseries Financial constraints}: Leveraging harder-to-block \texttt{meek} bridges, which make use of pay-per-use content delivery networks that are hard to block without imposing collateral damage (e.g., Amazon Web Services), can help, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
+\item{\bfseries Financial constraints}: The \texttt{meek} bridges are especially effective at avoiding censorship: they are harder to block without imposing significant collateral damage (e.g., to Amazon Web Services) and are harder to detect through passive monitoring~\cite{fifield2015blocking}.
+Leveraging these harder-to-block bridges can help users in heavily censored environments, but these relays cost the Tor Project magnitudes more than other relays and using them more would cost even more money.
 \end{itemize}

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style and made a sentence less awkward

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
-We used our observations from the qualitative study to design interface changes that would address common issues that participants encountered.
-We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.
+We used our qualitative study observations to design interface changes that would address encountered issues.
+We used quantitative testing to measure the impact of our proposed changes, as compared to the original interface.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style

@@
 We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and identify stumbling points in the interface.
-At the completion of the task, we interviewed our participants to gather explanatory data and their opinions.
+We interviewed our participants to gather explanatory data and their opinions.
 
@@
 \subsection{Procedure} 
-We ran the experiments in a small room with a desk and chair, where a monitor, keyboard, and a Windows computer were set up.
+We ran the experiments in a small room where a monitor, keyboard, and a Windows computer were set up.
 Using a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment.
-We ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen before each participant.
+Before each participant, we ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Add titles to captions for connection box plots

@@
 \caption{
+Connection times.
 Participants in E2 and E3 took a long time to connect.
@@
 \caption{
-Configuration times are much shorter than connection times, which means that most of the time was spent waiting for the connection to establish or time out.
-Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
+Configuration times (connection time with time on progress screen subtracted).
+The differences from Figure \ref{fig:time_to_success_clamped} (connection times) show that most of the time was spent waiting for the connection to establish or time out.
+%Non-finishing participants' configuration time was computed by subtracting the time on the progress screen from their assigned completion time.
 }

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Smoothing out wording in Secs 6.2-7.3.

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 Qualitative testing illuminates {\it why or how} the software is or is not usable, while quantitative testing measures {\it to what extent}.
-We used our qualitative study observations to design interface changes that would address encountered issues.
-We used quantitative testing to measure the impact of our proposed changes, as compared to the original interface.
+We used our observations from the qualitative study to design interface changes that would address common issues that participants encountered.
+We used our quantitative testing setup to measure the usability of our proposed changes, as compared to the original interface.
 
@@
 In theory, this can be done locally without infrastructural changes or leaking information to the network.}
-\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the of the bridge question screen (Figure~\ref{fig:old-bridge}).}
-\item{gave a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) in case the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
+\item{added the option to not use a bridge on the bridge screen (Figures~\ref{fig:new-nobridge}, ~\ref{fig:new-bridge} and ~\ref{fig:new-bridge-combobox}) to replace the function of the bridge question screen (Figure~\ref{fig:old-bridge}).}
+\item{added a recommendation to use one of the three \texttt{meek}-transport bridges (Figure~\ref{fig:new-bridge}) if the recommended \texttt{obfs3}-transport bridges were unreachable, which happens in heavily censored real environments and our simulated environment E3.}
 \item{added a summary screen (Figure~\ref{fig:new-summary}) that summarizes the settings before making a connection to Tor, since some participants from the previous study didn't know how they connected to Tor.}
@@
 
-Our interface was made to test changes in a laboratory testing.
-We acknowledge that our version would need refining (aligning text properly, using higher quality visual assets, etc.) before deployment.
+Our interface was intended as a proof of concept, so we could evaluate these changes in a laboratory testing.
+We acknowledge that further refinement (aligning text properly, using higher quality visual assets, etc.) would be needed before deployment.
 
@@
 We conducted our quantitative experiments at a behavioral laboratory with many participants in parallel, using instrumentation to capture evaluation metrics.
-We confirmed prior stumbling points and user behaviors and validated our proposed design improvements.
+These experiments confirmed previously-seen stumbling points and user behaviors and validated our proposed design improvements.
 
@@
 At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
-We manually assigned interface--environment combinations to each computer.
+We assigned each participant to one of six conditions (Table~\ref{table:participant-summary}), which determines their user interface (OLD or NEW) and censorship environment (E1, E2, or E3).
+We use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
 
@@
 \subsection{Results} 
-In this section, we use OLD to refer to the original interface (Figure~\ref{fig:old-interface}) and NEW to refer the version with our changes (Figure~\ref{fig:new-interface}).
-As seen in Table~\ref{table:participant-summary}, our design changes helped more users connect to Tor in less time.
-However, many, including participants who used the redesigned version, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed.
-Those that managed to connect took long to do so (>3 minutes in E2 and >20 minutes in E3).
-Figure~\ref{fig:all-participant-edges} summarizes each participant---showing if they connected to Tor, how long they took to do so, and where they spent their time.
+As seen in Table~\ref{table:participant-summary}, our design changes helped more participants connect to Tor in less time.
+However, many participants, including participants who used the new interface, still could not connect to Tor: 63\% (72 of 114) of first attempts failed and 79\% (363 of 458) of total attempts failed.
+Those who managed to connect often took a long time to do so (>3 minutes in E2 and >20 minutes in E3).
+Figure~\ref{fig:all-participant-edges} summarizes each participant, showing whether they successfully connected to Tor, how long they took to do so, and where they spent their time.
 Based on these results, we recommend that our changes be adapted in the meantime, but encourage a drastic redesign of the interface.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Use consistent capitalization for Tor Launcher

@@
 \label{sec:conclusion}
-We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor launcher.
+We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor Launcher.
 We believe that this is because the interface requires users to know technical terms, provides a lot of freedom for error, and does not give proper feedback.
@@
 We would like to thank the peer reviewers, especially our shepherd Jens Grossklags, for giving us valuable feedback on this paper.
-Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor launcher and internal constraints.
+Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor Launcher and internal constraints.
 This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (Secure Computing Research for Users' Benefit)~\cite{scrub}, and BLUES (Berkeley Laboratory for Usable and Experimental Security)~\cite{blues} laboratories, with support from

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 \label{sec:design} 
-We redesigned the interface according to usability best practices while addressing the pain points found in our qualitative usability study.
-We drafted a list of design considerations, prioritized the pain points to address, and iteratively made changes to the interface to get to our final design (Figure~\ref{fig:new-interface}).
+We redesigned the interface to address pain points found in our qualitative study. Figure~\ref{fig:new-interface} shows our final design.
 
@@
 While we could help users by automating configuration settings, this would involve probing network configurations and sending network traffic that could allow authorities to detect that the user is using Tor.
-Taking this risk without proper consent is not ethical.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Smoothing up wording in Sec 7

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 \label{sec:design} 
-We redesigned the interface to address pain points found in our qualitative study. Figure~\ref{fig:new-interface} shows our final design.
+We redesigned the interface according to usability best practices while addressing the pain points found in our qualitative usability study.
+We drafted a list of design considerations, prioritized the pain points to address, and iteratively made changes to the interface to get to our final design (Figure~\ref{fig:new-interface}).
 
@@
 While we could help users by automating configuration settings, this would involve probing network configurations and sending network traffic that could allow authorities to detect that the user is using Tor.
+Taking this risk without proper consent is not ethical.
 
@@
 Participants who could have used any bridge (E2) all used the recommended bridge.
-Participants who needed a \texttt{meek} bridge or custom bridge (E3) chose a \texttt{meek} bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.
+Participants who needed a \texttt{meek} bridge or custom bridge (E3) chose a \texttt{meek} bridge at random; the ones who tried to use a custom bridge did not format their inputs correctly and failed to connect to Tor.
 
@@
 \caption{
-A table showing participants' connections to Tor.
+Participants' connections to Tor.
 Note that none used the flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
@@
 
-However, the simulated censorship environment (and therefore, the difficulty of the configuration), was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+The simulated censorship environment (and therefore, the difficulty of the configuration) was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
 Figure~\ref{fig:time_to_success_clamped} shows that participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
-It would be ideal to have an interface that allows users to connect in the similar amounts of time, no matter what their configuration requirements; neither the OLD or NEW interface achieves this.
-
-Figure~\ref{fig:time_to_success_ecdf} shows a cumulative distribution of connection times.
-Everyone in E1 was able to connect right away; participants with the NEW interface doing so faster than participants with the OLD interface.
+Ideally, we would prefer an interface that allows users to connect in about the same amount of time, regardless of their configuration requirements; neither the OLD or NEW interface achieves this.
+
+Figure~\ref{fig:time_to_success_ecdf} shows the cumulative distribution of connection times.
+Everyone in E1 was able to connect right away; participants with the NEW interface were faster than participants with the OLD interface.
 Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time.
@@
 Participants in E2 and E3 took a long time to connect.
-The ``DNF'' (did not finish) shows how many did not connect.}
+The ``DNF'' (did not finish) shows how many were never able to successfully connect.}
 \label{fig:time_to_success_clamped}
@@
 \caption{
-Cumulative success rates over time. Those who did not connect were assigned an arbitrarily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution. 
+Cumulative success rates over time.
+Those who were never able to successfully connect were assigned an arbitrarily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution.
 }

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Don't use the word "talk"
prefer "discuss" and other more formal options

@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
+	\caption{The bridge help screen (BH) describes options for obtaining a custom bridge. ``Done'' leads back to the previous screen.}
 	\label{fig:old-bridge-help}
@@
 But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation.
-Here, we talk about the potential approaches to redesigning the interface:  \\
+Here, we discuss about the potential approaches to redesigning the interface:  \\
 
@@
 Tor Browser version~5.4.5 incorporated  changes based on our work.
-We also talked with Tor developers about automating connections to Tor, and they are now considering this as future work.
+We also discussed the possibility of automating connections to Tor with its developers, and they are now considering this as future work.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex

@@
 	\centering\captionsetup{width=1.5\linewidth}%
-	\caption{The bridge help screen (BH) describes options for obtaining a custom bridge. ``Done'' leads back to the previous screen.}
+	\caption{The bridge help screen (BH) talks about getting a custom bridge. ``Done'' leads back to the previous screen.}
 	\label{fig:old-bridge-help}
@@
 But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation.
-Here, we discuss about the potential approaches to redesigning the interface:  \\
+Here, we talk about the potential approaches to redesigning the interface:  \\
 
@@
 Tor Browser version~5.4.5 incorporated  changes based on our work.
-We also discussed the possibility of automating connections to Tor with its developers, and they are now considering this as future work.
+We also talked with Tor developers about automating connections to Tor, and they are now considering this as future work.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
wordsmith for style

@@
 We conducted our quantitative experiments at a behavioral laboratory with many participants in parallel, using instrumentation to capture evaluation metrics.
-These experiments confirmed previously-seen stumbling points and user behaviors and validated our proposed design improvements.
+These experiments confirmed previously-seen pain points and validated our proposed design improvements.
 
@@
 Xlab had 36 workstations with identical Windows~7 laptops, with workstation partitions to discourage participants from looking at others' screens.
-At the beginning of each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
+Before each session, we used a script to revert the computers to a clean image; download Firefox, Chrome, Internet Explorer, VLC media player, and Tor Browser 5.0.3 (instrumented versions that logged user interactions, with or without our proposed UI changes); set up one of the three simulated environments (E1, E2, or E3); and start recording the computer screen.
 We assigned each participant to one of six conditions (Table~\ref{table:participant-summary}), which determines their user interface (OLD or NEW) and censorship environment (E1, E2, or E3).
@@
 Participants who could have used any bridge (E2) all used the recommended bridge.
-Participants who needed a \texttt{meek} bridge or custom bridge (E3) chose a \texttt{meek} bridge at random; the ones who tried to use a custom bridge did not format their inputs correctly and failed to connect to Tor.
+Participants who needed a \texttt{meek} bridge or custom bridge (E3) chose a \texttt{meek} bridge at random; the ones who tried to use a custom bridge did not format their messages or inputs correctly and failed to connect to Tor.
 
@@
 \caption{
-Participants' connections to Tor.
+A table showing participants' connections to Tor.
 Note that none used the flashproxy, fte, fte-ipv6, obfs4, or scramblesuit bridges to connect. 
@@
 
-The simulated censorship environment (and therefore, the difficulty of the configuration) was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
+However, the simulated censorship environment (and therefore, the difficulty of the configuration), was the strongest factor in determining connection time (Kruskal--Wallis $\chi^2 = 80.5$, $\mbox{df} = 2$, $p < 10^{-15}$).
 Figure~\ref{fig:time_to_success_clamped} shows that participants in E2 took longer to connect than participants in E1, and participants in E3 took the longest to connect.
-Ideally, we would prefer an interface that allows users to connect in about the same amount of time, regardless of their configuration requirements; neither the OLD or NEW interface achieves this.
-
-Figure~\ref{fig:time_to_success_ecdf} shows the cumulative distribution of connection times.
-Everyone in E1 was able to connect right away; participants with the NEW interface were faster than participants with the OLD interface.
+It would be ideal to have an interface that allows users to connect in the similar amounts of time, no matter what their configuration requirements; neither the OLD or NEW interface achieves this.
+
+Figure~\ref{fig:time_to_success_ecdf} shows a cumulative distribution of connection times.
+Everyone in E1 was able to connect right away; participants with the NEW interface doing so faster than participants with the OLD interface.
 Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time.
@@
 Participants in E2 and E3 took a long time to connect.
-The ``DNF'' (did not finish) shows how many were never able to successfully connect.}
+The ``DNF'' (did not finish) shows how many did not connect.}
 \label{fig:time_to_success_clamped}
@@
 \caption{
-Cumulative success rates over time.
-Those who were never able to successfully connect were assigned an arbitrarily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution.
+Cumulative success rates over time. Those who did not connect were assigned an arbitrarily large finishing time greater than 40 minutes for the purpose of graphing this cumulative distribution. 
 }

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Clean up new style problem
that I introduced in ce120dbdeda19583a1525694f88898775129a572
Smoothing out wording in Sec 8 a little bit.  Elaborating on what we mean by smart automation.

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 \label{sec:recommendations}
-Our design resulted in shorter connection times and greater success,  but it could still be improved.
+Our design resulted in shorter connection times and greater success rates,  but it could still be improved.
 We do not recommend our exact design as the optimal design, although we believe it is an improvement.
@@
 But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation.
-Here, we talk about the potential approaches to redesigning the interface:  \\
+We see several promising approaches to improving the Tor launcher:  \\
 
 \begin{itemize}
-\item{\bfseries Design changes:} as demonstrated by our design iteration, tweaks in the interface can result in significant usability improvements.
-\item{\bfseries Naive automation:} a scheme that chooses bridges, waits for timeouts, and tries another bridge so users do not need to do this themselves.
+\item{\bfseries Design changes:} as demonstrated by our design iteration, incremental improvements to the interface can result in significant usability improvements.
+\item{\bfseries Naive automation:} the launcher could automatically choose a bridges, wait for timeout, and try another bridge on failure, so users do not need to do this themselves.
 We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually.
-\item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwidth constraints.
+\item{\bfseries Smart automation:} the launcher could initially connect to Tor via a hard-to-censor bridge, then contact a central server (over this Tor connection) to identify a bridge that will work for the user based on availability and bandwidth constraints, automatically choose that bridge, and re-connect to Tor using that bridge.
 We call this ``smart'' automation because this scheme involves communication with Tor servers, which choose a bridge that will work for the user on the first try.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Make the wording of recommended approaches consistent

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 But we see further room for improvement in success rate, connection time, and configuration time that could be made by leveraging user input and automation.
-Here, we discuss about the potential approaches to redesigning the interface:  \\
+Here, we discuss the potential approaches to redesigning the interface:  \\
 
 \begin{itemize}
-\item{\bfseries Design changes:} as demonstrated by our design iteration, tweaks in the interface can result in significant usability improvements.
-\item{\bfseries Naive automation:} a scheme that chooses bridges, waits for timeouts, and tries another bridge so users do not need to do this themselves.
+\item{\bfseries Design changes.} As demonstrated by our design iteration, tweaks in the interface can result in significant usability improvements.
+\item{\bfseries Naive automation.} The process of choosing bridges, waiting for timeouts, and trying another bridge could be automated.
 We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually.
-\item{\bfseries Smart automation:} a scheme that connects to a hard-to-censor bridge, which then automatically assigns a bridge that works for the user based on availability and bandwidth constraints.
+\item{\bfseries Smart automation.} Tor could connect by default to a hard-to-censor bridge, which would then automatically assign a different bridge that works for the user based on availability and bandwidth constraints.
 We call this ``smart'' automation because this scheme involves communication with Tor servers, which choose a bridge that will work for the user on the first try.

### 2017-03-20 pets2017-paper/pets2017-paper.tex

@@
 \begin{itemize}
-\item{\bfseries Design changes:} as demonstrated by our design iteration, incremental improvements to the interface can result in significant usability improvements.
-\item{\bfseries Naive automation:} the launcher could automatically choose a bridges, wait for timeout, and try another bridge on failure, so users do not need to do this themselves.
+\item{\bfseries Design changes:} As demonstrated by our design iteration, incremental improvements to the interface can result in significant usability improvements.
+\item{\bfseries Naive automation:} The launcher could automatically choose a bridges, wait for timeout, and try another bridge on failure, so users do not need to do this themselves.
 We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually.
-\item{\bfseries Smart automation:} the launcher could initially connect to Tor via a hard-to-censor bridge, then contact a central server (over this Tor connection) to identify a bridge that will work for the user based on availability and bandwidth constraints, automatically choose that bridge, and re-connect to Tor using that bridge.
+\item{\bfseries Smart automation:} The launcher could initially connect to Tor via a hard-to-censor bridge, then contact a central server (over this Tor connection) to identify a bridge that will work for the user based on availability and bandwidth constraints, automatically choose that bridge, and re-connect to Tor using that bridge.
 We call this ``smart'' automation because this scheme involves communication with Tor servers, which choose a bridge that will work for the user on the first try.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Fix a typo

@@
 \item{\bfseries Design changes:} As demonstrated by our design iteration, incremental improvements to the interface can result in significant usability improvements.
-\item{\bfseries Naive automation:} The launcher could automatically choose a bridges, wait for timeout, and try another bridge on failure, so users do not need to do this themselves.
+\item{\bfseries Naive automation:} The launcher could automatically choose a bridge, wait for a timeout, and try another bridge on failure, so users do not need to do this themselves.
 We call this ``naive'' automation, because this scheme does not leverage information about the user or network conditions and essentially just automates the trial and error process that users would otherwise have to do manually.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Acknowledge funders

--- 2017-03-20 pets2017-paper/pets2017-paper.tex
@@
 Tor Project employees Georg Koppen, Mike Perry, and Isabela Bagueros provided valuable insights about the history of Tor Launcher and internal constraints.
-This work was done in collaboration with Xlab (Experimental Social Science Laboratory)~\cite{xlab}, SCRUB (Secure Computing Research for Users' Benefit)~\cite{scrub}, and BLUES (Berkeley Laboratory for Usable and Experimental Security)~\cite{blues} laboratories, with support from
-Intel, the National Science Foundation,
-the Open Technology Fund through the Freedom2Connect Foundation, and from
-the US Department of State, Bureau of Democracy, Human Rights and Labor.
+We gratefully acknowledge assistance from the Xlab (Experimental Social Science Laboratory)~\cite{xlab} and
+financial support from Intel through the ISTC for Secure Computing,
+the National Science Foundation through award CNS-1318680,
+the Open Technology Fund through the Freedom2Connect Foundation,
+the US Department of State, Bureau of Democracy, Human Rights and Labor,
+the AFOSR under MURI award FA9550-12-1-0040,
+and the Hewlett Foundation through the Center for Long-Term Cybersecurity.
 

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Remove mention of active adversaries from Sec 6.1, per email thread.

@@
 
-\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions.
+%\item{\bfseries Active adversaries}: We could ask the user for their location, risk tolerance, or other preferences to help automatically make decisions.
 Leveraging user input works well, but third-party versions of Tor Browser that replicate the official version could use these inputs to profile users.
@@
 We kept the user involved so that they explicitly start a connection to Tor.
-We chose not to leverage user inputs such as their location, risk, or other preferences due to active and passive adversaries.
+We chose not to leverage user inputs such as their location, risk, or other preferences.
 We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.

### 2017-03-20 pets2017-paper/pets2017-paper.tex
Improve conclusion

@@
 
-Our experiment did not directly test configuring a proxy or a custom bridge. From observing participants, we suspect they struggle with these tasks.
+Our experiment did not directly test configuring a proxy or a custom bridge. From observing participants, we suspect they also struggle with these tasks.
 
@@
 \label{sec:conclusion}
-We measured why and how users have a hard time connecting to Tor through this usability evaluation of Tor Launcher.
-We believe that this is because the interface requires users to know technical terms, provides a lot of freedom for error, and does not give proper feedback.
+Our usability evaluation of Tor Launcher measured why and how users have a hard time connecting to Tor.
+We found that users struggle because the interface requires them to know technical terms, provides room for error, and does not give proper feedback.
 Users in heavily censored environments will likely not succeed in connecting to Tor without outside help.

### 2017-03-21 pets2017-paper/pets2017-paper.tex
Flip the meaning of e# and e#' in \ref{states} (Appendix A).
Looking at the graph, it seems all the children of the "bridge no" edge
have the '.
Make caption of fig:digraph consistent.
start → first
add bridge help
doesn't show any "quit" states.

@@
 A digraph illustrating the potential user paths through the interface.
-Non-leaf nodes are screens in the user interface (start, bridge 1, bridge 2, proxy 1, proxy 2, and progress).
-Leaf nodes are various end states (quit, success, or error).
+Non-leaf nodes are screens in the user interface (first, bridge~1, bridge~2, bridge help, proxy~1, proxy~2, and progress).
+Leaf nodes are various end states (success or error).
 Transitions between these nodes denote user actions.
@@
 Here we define the end state codes that appear in Figure~\ref{fig:digraph}.
-e\# and $\mbox{e\#}^\prime$ are equivalent, except that $\mbox{e\#}^\prime$ uses a bridge while e\# does not. \\
+e\# and $\mbox{e\#}^\prime$ are equivalent, except that e\# uses a bridge while $\mbox{e\#}^\prime$ does not. \\
 

### 2017-03-21 pets2017-paper/pets2017-paper.tex
wordsmith for style

@@
 \subsection{Procedure} 
-We ran the experiments in a small room where a monitor, keyboard, and a Windows computer were set up.
-Using a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer as browser options, and VLC media player~\cite{vlc} to record the screen during the experiment.
-Before each participant, we ran a script that set up one of the three simulated environments (E1, E2, or E3) and started recording the computer screen.
+We ran the experiments in a room with a monitor, keyboard, and a Windows computer.
+On a fresh install of the operating system, we installed Tor Browser 5.0.3 for testing, Chrome, Firefox, and Internet Explorer for browser options, and VLC media player~\cite{vlc} for recording the computer screen.
+Before each participant, we ran a script that simulated E1, E2, or E3 and started recording the computer screen.
 
@@
 
-We kept the user involved so that they explicitly start a connection to Tor.
-We chose not to leverage user inputs such as their location, risk, or other preferences.
+We kept the user involved in the configuration so that they explicitly start a connection to Tor (currently, the user needs to click a ``connect'' button before Tor Launcher makes a connection to Tor).
+%We chose not to leverage user inputs such as their location, risk, or other preferences, as this would require additional research on all these options before designing changes incorporating those. 
+And although some users in our qualitative study tried to configure unnecessary components, we still also allow all users to choose a manual configuration to give them a chance to connect to Tor securely the first time.
 We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.

### 2017-03-22 pets2017-paper/pets2017-paper.tex
Handle some of the recent todos:
-       Specifically, we describe how the initial evaluation --> delete “how”
-       Add conclusion section to roadmap at the end of introduction? Something like: we close with concluding remarks (section 11).
-       interview them about their experience after user --> after usage, or after the study
-       to establish or timeout --> time out (it’s the verb; not the noun)
-       interface for Tor had unique challenges --> has (since the challenges do not go away with this redesign)
-       4e, and 4h) --> visually there seems extra space in front of 4h; ta

@@
 
-Specifically, we describe how the initial evaluation of the interface (Section~\ref{sec:inspection}) and our observations of participants' interactions with it (Section~\ref{sec:qualitative}).
+Specifically, we describe the initial evaluation of the interface (Section~\ref{sec:inspection}) and our observations of participants' interactions with it (Section~\ref{sec:qualitative}).
 Based on the insights from our observations, we proposed several changes to the interface (Section~\ref{sec:design}) and measured how successfully and quickly users connect to Tor before and after changes (Section~\ref{sec:quantitative}).
-Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), and frame our study in the context of existing work (Section~\ref{sec:related}).
+Finally, we provide recommendations based on what we learned (Section~\ref{sec:recommendations}), we address limitations of our evaluation (Section~\ref{sec:limitations}), frame our study in the context of existing work (Section~\ref{sec:related}),
+and conclude (Section~\ref{sec:conclusion}).
 We hope that our usability evaluation serves as an informative case study and provides guidance on further improving Tor Launcher, as well as other privacy-enhancing technologies.
@@
 
-We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after user.
+We performed our qualitative experiments one participant at a time, so that we could observe their behaviors in real time and interview them about their experience after use.
 We recruited five participants per experimental condition to gather qualitative data; this has been suggested as the optimal number of measurements to maximize the cost-benefit ratio~\cite{howmanyusers}.
@@
 We defined configuration time as any time spent on the bridge and proxy screens, since users were most likely configuring bridges and proxies.
-We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or timeout and not necessarily interacting with the interface.
+We excluded any time spent on the progress screen, because users were most likely waiting for connections to establish or time out and not necessarily interacting with the interface.
 This should be as short as possible.
@@
 
-Designing an interface for Tor had unique challenges: \\
+Designing an interface for Tor has unique challenges: \\
 
@@
 \begin{itemize}
-\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and ~\ref{fig:new-progress})  to encourage users to read instructions.}
+\item{reduced the amount of text and technical terms in the text (Figures~\ref{fig:new-first},~\ref{fig:new-proxy},~\ref{fig:new-nobridge},~\ref{fig:new-bridge},~\ref{fig:new-bridge-combobox}, and~\ref{fig:new-progress})  to encourage users to read instructions.}
 \item{centered the text to make the design compatible for left to right and right to left languages.}

### 2017-03-22 pets2017-paper/pets2017-paper.tex
Remove duplicate paragraph
It appeared as a merge conflict after the order got swapped in
39bbc3a04db961e435e01a95550d8db268900d0b
handle rest of shepherd todos

@@
 to make it difficult to observe sources and destinations.
-Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through Tor, designed to minimize the configuration required before connecting.
-Although Tor was originally designed for anonymity, many now use it to circumvent Internet censorship.
+Tor Browser~\cite{torbrowser} is a modified Firefox browser that routes traffic through the Tor network.
+Although Tor and Tor Browser were originally designed for anonymity, many now use them to circumvent Internet censorship.
 Because of this, many countries block Tor relays specifically to prevent their citizens from circumventing censorship~\cite{winter2012great}.
@@
 \section{Methodology} 
-This section discusses our usability testing process, including the simulated censorship environments we used to require users to configure different network components to connect to Tor and the evaluation metrics  we collected.
+This section discusses our IRB-approved usability testing process, including the simulated censorship environments we used to require users to configure different network components to connect to Tor and the evaluation metrics  we collected.
 
@@
 %We chose not to leverage user inputs such as their location, risk, or other preferences, as this would require additional research on all these options before designing changes incorporating those. 
-And although some users in our qualitative study tried to configure unnecessary components, we still also allow all users to choose a manual configuration to give them a chance to connect to Tor securely the first time.
+And although some users in our qualitative study tried to configure unnecessary components in confusion, we still give users the freedom to configure optional components. 
 We limited our design changes to ones that do not require infrastructural changes or cause additional financial burden to make it easier for the Tor project to adopt them.
@@
 Most participants in E2 were able to connect right away, with participants with the NEW interface and OLD interface taking a similar amount of time.
-Participants in E3 took various amount of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.
+Participants in E3 took various amounts of time to succeed, with participants with the NEW interface connecting significantly faster than those with the OLD interface.
 
@@
 However, we noticed that some participants utilized this time to search for help in another browser while waiting for their connection to time out, so configuration time is not a perfect metric to measure participant engagement.
+
+Although none of the participants needed to configure a proxy to bypass censorship, participants still spent time trying to configure them.
+Participants the OLD interface spent more time configuring proxies than bridges and participants with the NEW interface spent about an equal amount of time configuring bridges and proxies even when the interface said that they didn't need one.
 

### 2017-03-23 pets2017-paper/pets2017-paper.tex
minor additions for formatting

@@
 We then conducted qualitative and quantitative usability tests.
+
+Qualitative testing is used to gain an understanding of underlying reasons, opinions, and motivations.
+We use qualitative testing to develop hypotheses about why people struggle to use the interface and devlop ideas for potential design modifications to the interface.
+
+Quantitative testing is used to quantify the problem by way of generating numerical data or data that can be transformed into useable statistics.
+We use quantitative testing to quantify how people interact with the interface to uncover user patterns.
+
 We believe both methods were necessary for a complete usability evaluation.
@@
 Re-routing participant traffic through other countries' networks also may introduce unforeseen risks to the participants out of our control and performing hundreds of connections in short intervals during experiments may draw unnecessary attention to Tor use in that country.
-The three environments are described in Table~\ref{tab:environments}.
+The three simulated censorship environments, which we refer to as E1, E2, and E3 throughout the paper, are summarized in Table~\ref{tab:environments}.
+E2's censorship is a superset of E1's; similarly, E3's censorship is a superset of E2's.
 
@@
 or a custom bridge.
-E2's blocking is a superset of E1's;
-similarly, E3's is a superset of E2's.
 }
@@
 \end{table}
-
-The simulated environments are not intended to imitate any particular country's network---though they do use the same techniques that are currently used by various censorship regimes.
-Rather, we designed simulated environments to have different requirements to connect to Tor.
-We believe this to be sufficient for the purpose of testing the configuration interface, since this requires the user to take the different interface paths we wanted to test (and matches the actions real users would need to take to circumvent various types of censorship).
 

### 2017-03-24 pets2017-paper/pets2017-paper.tex
Spell check.

@@
 Qualitative testing is used to gain an understanding of underlying reasons, opinions, and motivations.
-We use qualitative testing to develop hypotheses about why people struggle to use the interface and devlop ideas for potential design modifications to the interface.
-
-Quantitative testing is used to quantify the problem by way of generating numerical data or data that can be transformed into useable statistics.
+We use qualitative testing to develop hypotheses about why people struggle to use the interface and develop ideas for potential design modifications to the interface.
+
+Quantitative testing is used to quantify the problem by way of generating numerical data or data that can be transformed into usable statistics.
 We use quantitative testing to quantify how people interact with the interface to uncover user patterns.

### 2017-03-28 pets2017-paper/pets2017-paper.tex
kill an orphan, as requested by review

--- 2017-03-23 pets2017-paper/pets2017-paper.tex
@@
 
-We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation into the interface only if the impact of those changes is still unsatisfactory.
+We recommend a gradual approach that starts with deploying design changes, measuring the impact of those changes, and cautiously incorporating automation if the impact of those changes is still unsatisfactory.
 
